### 2024-06-01 ms_refs_fixed.Rmd
Add the manuscript files for Rmarkdown

---
title: "A general model for the evolution of nuptial gift-giving"
author: |
  | Anders P. Charmouh$^{1,4, 5}$, Trine Bilde$^{2}$, Greta Bocedi$^{1}$, A. Bradley Duthie$^{3}$
date: '[1] School of Biological Sciences, University of Aberdeen, UK. [2] Department of Biology, Aarhus University, Denmark. [3] Biological and Environmental Sciences, University of Stirling, UK.  [4] Bioinformatics Research Centre Aarhus University, University City 81, building 1872, 3rd floor, DK-8000 Aarhus C, Denmark [5] Email: apc@birc.au.dk'
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution-letters.csl
    reference_docx: docx_template.docx
  html_document: default
bibliography: nuptial_refs.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{natbib}
- \usepackage{lineno}
- \usepackage{caption}
- \usepackage[utf8]{inputenc}
- \bibliographystyle{amnatnat}
- \linenumbers
- \modulolinenumbers[2]
linestretch: 2
link-citations: yes
linkcolor: blue
csl: evolution-letters.csl
biblio-style: apalike
---

```{r, echo = FALSE}
library("knitr")
calc_beta <- function(M = 1, TF = 1, TM = 1){
  term1 <-   (M * (TF - TM))^2;
  term2 <-   (M * (TF - TM))^4;
  term3 <- 4*(M * (TF - TM))^2;
  ttrm  <- (term2 + term3)^(1/2);
  sol1  <- 0.5 * (term1 - ttrm) + 1;
  sol2  <- 0.5 * (term1 + ttrm) + 1;
  if(TF > TM){
    beta = max(c(sol1, sol2));
  }else{
    beta = min(c(sol1, sol2));
  }
  return(list = c(beta = beta, solution1 = sol1, solution2 = sol2));
}
get_beta <- function(M = 1, TF = 1, TM = 1){
  betas <- rep(NA, length = length(TM));
  for(i in 1:length(TM)){
    betas[i] <- calc_beta(M = M, TF = TF, TM = TM[i])[[1]];
  }
  return(betas);
}
PrGf <- function(Tm, a1){
  vals <- 1 - exp(-(1/a1)*Tm);
  return(vals);
}
PrFf <- function(Tm, a1, a2 = Inf){
  vals <- (1 - exp(-(1/a2)*Tm)) * exp(-(1/a1)*Tm);
  return(vals);
}
dWdT <- function(gamma, Tm, beta = 1, M = 100, a1 = 1){
  num1 <- gamma * (M*M + ((M*M*Tm + M*sqrt(beta))/a1) );
  dem1 <- exp((1/a1)*Tm);
  num2 <- (num1 / dem1) - M*M*(1 + gamma);
  den2 <- ((Tm * M) + sqrt(beta))^2;
  val  <- num2/den2;
  return(val);
}
dWdT_check <- function(gamma, beta = 1, M = 100, a1 = 1){
  term1 <- (gamma * M) / (a1*sqrt(beta));
  term2 <- (M*M) / beta;
  val   <- term1 - term2;
  return(val);
}
recursive_b <- function(B, D, Tf, Tm, crit = 0.0001, maxit = 9999){
  conv <- 1;
  iter <- 0;
  while(conv > crit & iter < maxit){
    Fe   <- D * (B / (1 + B));
    Me   <- (1 + B) / D;
    Bn   <- (Me / (Tm + Me)) / (Fe / (Tf + Fe));
    iter <- iter + 1;
    conv <- abs(Bn - B);
    B    <- Bn;
  }
  return(list(B = B, conv = conv, iter = iter));
}
calc_beta <- function(M = 1, TF = 1, TM = 1){
  vals <- recursive_b(B = 1, D = M, Tf = TF, Tm = TM);
  beta <- vals$B
  sol1 <- vals$conv;
  sol2 <- vals$iter;
  return(list = c(beta = beta, solution1 = sol1, solution2 = sol2));
}
get_beta <- function(M = 1, TF = 1, TM = 1){
  betas <- rep(NA, length = length(TM));
  for(i in 1:length(TM)){
    betas[i] <- calc_beta(M = M, TF = TF, TM = TM[i])[[1]];
  }
  return(betas);
}
gamma_m <- function(R = 1, beta = 1, alpha = 1/16, TF = 2){
  return(alpha * (R / (beta + 1)));
}
gamma_f <- function(R = 1, beta = 1, alpha = 1/16, TF = 2){
  topp <- exp(alpha / alpha);
  bott <- TF * R * (beta / (beta + 1)) * (exp(alpha/alpha) - 1);
  return(topp/bott);
}
PrGf <- function(Tm, a1){
  vals <- 1 - exp(-(1/a1)*Tm);
  return(vals);
}

PrLf <- function(Tm, a1){
  vals <- exp(-(1/a1)*Tm);
  return(vals);
}

W_mf <- function(gamma, Tm, beta, M, lambda = 1, PrG, PrL){
  top <- lambda * (PrG * (1 + gamma) + PrL);
  bot <- Tm + (sqrt(beta) / M); 
  val <- top/bot;
  return(val);
}

W_mf_full  <- function(gamma, Tm, beta_val, M, a1, lambda = 1){
  PrG_val  <- PrGf(Tm = Tm, a1 = a1);
  PrL_val  <- PrLf(Tm = Tm, a1 = a1);
  W_mf_val <- W_mf(gamma = gamma, Tm = Tm, beta = beta_val, M = M,
                   PrG = PrG_val, PrL = PrL_val, lambda = lambda);
  return(W_mf_val);
}

W_m  <- function(mom = 1, mim = 1, mof = 1, mif = 1, M = 1, TF, TM, gamma, 
                 a1, bb){
  WW <- W_mf_full(gamma = gamma, Tm = TM, beta_val = bb, M = M, a1 = a1);
  return(WW)
}

Wp <- function(M, beta, Tm, a1, gamma, lambda){
  t1   <- (M*M + ((M*M*Tm + M * sqrt(beta))/a1))
  topp <- lambda * (((gamma * t1) / exp(Tm/a1)) - (M*M*(1 + gamma)))
  bott <- (Tm * M + sqrt(beta))^2
  val  <- topp / bott;
  return(val);
}

findWpmin <- function(M, beta, a1, gamma, b0, b1, lambda = 1){
  bynum   <- ((b1 + b0)/2 - b0) / 1000;
  TMvals1 <- seq(from = b0, to = (b1 + b0)/2, by = bynum);
  TMvals2 <- seq(from = (b1 + b0)/2, to = b1, by = bynum);
  abm     <- 10000;
  while(bynum > 0 & abm > 0.00001){
    ab1 <- abs(Wp(M = M, beta = beta, Tm = TMvals1, a1 = a1, gamma = gamma,
                  lambda = lambda));
    ab2 <- abs(Wp(M = M, beta = beta, Tm = TMvals2, a1 = a1, gamma = gamma,
                  lambda = lambda));
    mn1 <- min(ab1);
    mn2 <- min(ab2);
    abm <- min(c(mn1, mn2));
    if(mn1 < mn2){
      b1  <- (b1 + b0)/2;
    }else{
      b0  <- (b1 + b0)/2;
    }
    bynum   <- ((b1 + b0)/2 - b0) / 1000;
    TMvals1 <- seq(from = b0, to = (b1 + b0)/2, by = bynum);
    TMvals2 <- seq(from = (b1 + b0)/2, to = b1, by = bynum);
  }
  return((b1 + b0)/2);
}
female_IBM_criteria <- function(MGf, MLf, lambda = 1, TF = 2){
  MM   <- MGf + MLf;
  gamF <- lambda / (TF * (MM - MLf));
  return(gamF);
}

male_IBM_criteria <- function(Male_M, alpha = 1, lambda = 1){
  return(lambda * alpha * Male_M);
}

simpleboot <- function(freqs, repli = 1000, alpha = 0.05){  
  vals  <- NULL;                             
  i     <- 0;                                    
  while(i < repli){                             
    boot  <- sample(x = freqs, size = length(freqs), replace = TRUE);     
    strap <- mean(boot);                      
    vals  <- c(vals,strap);                     
    i     <- i + 1;                          
  }                                           
  vals   <- sort(x = vals, decreasing = FALSE);    
  lowCI  <- vals[round( (alpha * 0.5) * repli )];    
  highCI <- vals[round( (1-(alpha*0.5) ) * repli)];     
  CIs    <- c(lowCI, highCI);        
  return(CIs);         
} 
```

**Key words:** Nuptial gifts, male search, mate interactions, modelling, *Pisaura*

Abstract
================================================================================

Nuptial gift-giving occurs in several taxonomic groups including insects, snails, birds, squid, arachnids and humans. 
Although this trait has evolved many times independently, no general framework has been developed to predict the conditions necessary for nuptial gift-giving to evolve. 
We use a time-in time-out model to derive analytical results describing the requirements necessary for selection to favour nuptial gift-giving. 
Specifically, selection will favour nuptial gift-giving if the fitness increase caused by gift-giving exceeds the product of expected gift search time and encounter rate of the opposite sex. 
Selection will favour choosiness in the opposite sex if the value of a nuptial gift exceeds the inverse of the time taken to produce offspring multiplied by the rate at which mates with nuptial gifts are encountered. 
Importantly, selection can differ between the sexes, potentially causing sexual conflict. 
We test these results using an individual-based model applied to a system of nuptial gift-giving spiders, *Pisaura mirabilis*, by estimating parameter values using experimental data from several studies. 
Our results provide a general framework for understanding when the evolution of nuptial gift-giving can occur and provide novel insight into the evolution of worthless nuptial gifts, occurring in multiple taxonomic groups with implications for understanding parental investment.

Lay summary
================================================================================

If you have ever bought a gift to impress a prospective partner, you are not alone. 
Such behaviour is not unique to humans, but giving gifts during courtship is common in many different animals, including some species of insects, snails, birds, squid and spiders. 
In animals, such gifts can be costly, but offering them may be worth it from an evolutionary perspective if they increase the reproductive success of the individual who provides them. 
While using gifts during courtship (often called nuptial gifts) is widespread among animals, it is not universal. 
Why have some groups of animals evolved to engage in nuptial gift-giving while others have not? 
We explore this question by building a mathematical model, using computer simulations, and using data from a nuptial gift-giving species of spider to see how receiving nuptial gifts might affect reproductive success. 
We find conditions under which selection should favour males to provide nuptial gifts and females should exhibit a preference for gifts. 
These conditions explain why some species engage in nuptial gift-giving while others do not. Interestingly, we find that these inequalities differ between males and female, illustrating that the evolutionary interest of the two sexes do not always overlap.

Teaser text
================================================================================

The results presented provide a general explanation of the evolution of nuptial gift-giving which is a behaviour pattern that has evolved many times independently in diverse parts of the animal kingdom. 
The explanation is general but at the same time quantitatively precise, thus giving a rigorous answer to the conundrum of why nuptial gift-giving occurs in some groups of animals but not in others. 
Since research on nuptial gift-giving has, and continues to, inspire an enormous amount of work, the results presented here are highly relevant to an active field of both theoretical and empirical research.

Introduction
================================================================================

Nuptial gift-giving occurs when the choosy sex (usually the female) receives gifts from the opposite sex (usually the male) during courtship. 
It is a widespread phenomenon, occurring within several diverse taxonomic groups such as insects, snails, birds, squid, arachnids and humans [@Lewis2014; @Lewis2012; @Albo2014]. 
Despite the ubiquity of this behaviour, little effort has been made to conceptualise the evolution of nuptial gift-giving within a general modelling framework [@Lewis2014; @Iwasa2022]. 
Recent models describing the evolution of nuptial gift-giving have focused on co-evolution between male nuptial gift-giving and female propensity to remate, and the evolutionarily stable nuptial gift sizes [@Iwasa2022; @Kamimura2021], but a general framework describing the conditions necessary for nuptial gift-giving to be initially favoured by selection is needed to understand when gift-giving should evolve.  
Nuptial gift-giving may allow males to increase fitness by acquiring additional mates, indirect benefits (by increasing the fitness of offspring), prolonged copulations, and success in sperm competition [@Lewis2014; @Albo2013; @Ghislandi2014]. 
However, this potential fitness increase comes at the expense of producing a nuptial gift, which may be costly in terms of time and resources. 
Females may increase their fitness by receiving nutritionally valuable nuptial gifts, but expressing a preference for males with gifts might result in a mating opportunity cost if available males without gifts are rejected. 
With respect to nuptial gift-giving, the evolutionary interests of both sexes may not always fully overlap. 
This can cause sexual conflict, which is a difference in the evolutionary interest between sexes that occurs when interaction between sexes results in a situation where neither sex can achieve an optimal outcome [@Parker2006]
That is, under some conditions, it might for example be optimal for females to receive nuptial gifts, but not optimal for males to produce them.

Much work has sought to explain how gift-giving tactics are maintained, with explanations including condition-dependent strategies, gift-giving as a way to decrease female aggression during copulation, or gifts as sensory traps [@Albo2019; @Lubin2007; @Ghislandi2018; @Toft2016]. 
An example of such a system is the nuptial gift-giving nursery-web spider *Pisaura mirabilis* where males may court females with or without nuptial gifts [@Bristowe1926]. 
Here, males may provide females with costly nuptial gifts in the form of captured arthropod prey, and females may exhibit preference for males with a nuptial gift by rejecting males without a nuptial gift [@Albo2013].

We develop a general framework for investigating the evolution of nuptial gift-giving and choosiness using a time-in, time-out modelling approach and an individual-based model [@Clutton-Brock1992]. 
Specifically, we derive conditions under which selection will favour male search for nuptial gifts and female rejection of gift-less males. 
We show that selection for searching and choosiness depends on whether a threshold fitness value of the nuptial gift is exceeded. 
Our model demonstrates the importance of nuptial gift cost, sex ratio, and mate encounter rate in determining the threshold above which selection will favour the evolution of nuptial gift-giving.
Importantly, we show that the threshold value differs for males and females. 
We test predictions of our analytical model by formulating an individual-based model, which further supports the main theoretical results of our analytical model. 
Further, we apply our model to an example system with nuptial gifts, the nursery web spider *Pisaura mirabilis*, where we use experimental data to estimate a key model parameter. 
Our results provide a general framework for understanding why nuptial gift-giving evolves in some systems and not in others, how the evolution of nuptial gift-giving can give rise to sexual conflict, and it provides insight into the evolution of worthless and deceitful nuptial gifts, which occur in several different taxonomic [@Ghislandi2014; @LeBas2005].

Results
================================================================================

Analytical model
--------------------------------------------------------------------------------

We use a time-in and time-out model [@Clutton-Brock1992; @Kokko2001; @Kokko2006] in which choosy (female) and non-choosy (male) individuals spend some period of time within the mating pool searching for a mate (time-in) followed by a period outside the mating pool (time-out).
During time-out, females spend some duration of time ($T_{\mathrm{f}}$) gestating or rearing (hereafter 'processing') offspring. 
We define the number of offspring produced by a female per reproductive cycle as $\lambda$.
Since females enter time-out after mating, this assumption is equivalent to assuming a system with sequential polyandry.
For simplicity, we assume male time to replenish sperm is negligible, but males can spend some duration of time ($T_{\mathrm{m}}$) out of the mating pool searching for nuptial gifts.

```{r echo = FALSE, out.width = "100%", fig.cap = "Conceptual figure inspired by Kokko and Ots (2006) illustrating how the modelling framework maps onto an example of a system wherein nuptial gifts are used, here \\textit{Pisaura mirabilis}. Males have a probability of obtaining a nuptial gift while in time-out, which will affect their probability of mating while in time-in. They return to the mating pool (time-in) at a rate determined by the time spent searching for a nuptial gifts ($T_{m}$) and leave the mating pool (i.e. enter time-out) following the female encounter rate, which is dependent on ratio of males to females ($\\beta$) and the encounter rate ($R$). The choosy sex (females) enter the mating pool at a rate depending in the time spent processing offspring ($T_{f}$) and leave the mating pool (i.e. enter time-out) at a rate that is dependent on $\\beta$ and $R$. Males and females undergo sex-specific mortality $\\mu$ during time-in and time-out. Image left to right: (1) male \\textit{P. mirabilis}. (2) male \\textit{P. mirabilis} presenting nuptial gift (white) to female. (3) Female \\textit{P. mirabilis} protecting offspring. Photos: Alamy."}
include_graphics("inst/img/conceptual_figure.png");
```

Criteria for male search and female choosiness
--------------------------------------------------------------------------------

The probability $G$ that a male succeeds in securing a nuptial gift is defined by,

<!--

$$G = 1 - e^{-\frac{1}{\alpha}T_{m}}.$$
--->

\begin{equation}
G = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.
\end{equation}

In Eq. 1, $\alpha$ defines the expected search time before encountering a nuptial gift.
Thus, the probability of finding a nuptial gift is higher the more time $T_{\mathrm{m}}$ is spent searching. 
During time-in, individuals encounter conspecifics at a rate of $R$.
A focal individual will therefore encounter conspecifics of the opposite sex at a rate of $R/2$ if the ratio of males to females in the mating pool $\beta$ is equal.
More generally, males will be encountered at a rate of $R\beta/(\beta+1)$, and females will be encountered at a rate of $R/(\beta+1)$.
An example of how the structure of the time-in time-out model applies to a system with nuptial gift-giving is given in Figure 1.
We assume that mating with a nuptial gift increases the fitness of each offspring by an increment of $\gamma$.
We proceed to find the thresholds $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$ above which males and females are favoured by selection to search for nuptial gifts and exhibit choosiness for nuptial gifts, respectively.
We show (see Methods) that the initial threshold value of $\gamma$ ($\gamma_{\mathrm{m}}$) necessary for males to increase their fitness by investing time searching for a nuptial gift (time that could otherwise be spent searching for a mate) is,

<!---

$$\gamma_{m} > \alpha \frac{M}{\sqrt{\beta}}.$$
--->

\begin{equation}
\gamma_{\mathrm{m}} > \alpha \frac{R}{\beta + 1}.
\end{equation}

Inequality 2 means that if nuptial gifts are not abundant and thus require a long time to find (i.e., high $\alpha$), or if males encounter many females per unit time (i.e., high $R / (1+\beta)$), then the nuptial gift must result in a high fitness increment for selection to favour gift-searching. 
In general, when ineq. 2 is satisfied, we predict selection to favour the evolution of nuptial gift-giving.

We can similarly predict the conditions for which there is selection for female choosiness. 
If $\gamma$ is sufficiently high, then females increase their fitness by rejecting males without gifts and mating only with males that provide nuptial gifts. 
To illustrate, we assume that all males in a population search for a duration of $T_{\mathrm{m}}$, in which case the threshold fitness increment for females ($\gamma_{\mathrm{f}}$) is,

<!---

$$\gamma_{f} > \frac{1}{T_{f} M \sqrt{\beta} \left(1 - e^{-\frac{1}{\alpha}T_{m}} \right)}.$$

--->

\begin{equation}
\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}} R \left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}} \right)}.
\end{equation}

Inequality 3 shows that as offspring processing time ($T_{\mathrm{f}}$), mate encounter rate ($R\beta / (\beta + 1)$), and the probability of a male finding a nuptial gift ($1 - \exp(-T_{\mathrm{m}}/\alpha)$ ) decreases, the threshold value of fitness above which selection will favour choosiness ($\gamma_{\mathrm{f}}$) increases.
This can be understood intuitively by realising that rejecting a prospective male represents an opportunity cost for the female. 
This opportunity cost becomes small if many males with gifts are encountered, hence the appearance of the rate at which males with gifts are encountered in the denominator.
Figure 2 shows how $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$ change with increasing $\alpha$. 
For $\gamma_{\mathrm{f}}$, we assume that males search for the expected time required to obtain a nuptial gift ($T_{\mathrm{m}} = \alpha$). 
Note that $\beta$ does not have a closed form solution given $R$, $T_{\mathrm{f}}$, and $T_{\mathrm{m}}$, so $\beta$ was calculated using recursion (see Methods).

```{r, echo = FALSE, fig.width = 8, fig.height = 4, fig.cap = "Fitness thresholds above which males increase their fitness by searching for nuptial gifts (blue line; Eq. 2) and females increase their fitness by rejecting males that do not offer gifts (red line; Eq. 3). Parameter space includes areas in which males do not search for nuptial gifts and females are not choosy (A), males search but females are not choosy (B), females would be choosy but males do not search (C), and males search and females are choosy (D). Arrows indicate the effect of increasing interaction rate ($R$), female time-out ($T_{f}$), and male search time ($T_{m}$). As an example, trajectories for $T_{f} = 2$, and $T_{m} = \\alpha$ are shown for values of $R=2$ (panel a) and $R = 1$ (panel b). Females are assumed to be the choosy sex, which is maintained as long as $\\alpha < T_{f}$."}
alpha_vals <- seq(from = 0.0001, to = 2, by = 0.0001);
par(mar = c(5, 5, 1, 1), mfrow = c(1, 2));
beta_vals <- get_beta(M = 2, TF = 2, TM = alpha_vals);
g_m <- gamma_m(R = 2, beta = beta_vals, alpha = alpha_vals, TF = 2);
g_f <- gamma_f(R = 2, beta = beta_vals, alpha = alpha_vals, TF = 2);
plot(x = alpha_vals, y = g_m, type = "l", lwd = 2, cex.lab = 1.25,
     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
     ylab = expression(paste("Fitness thresholds (", gamma[f], " & ", gamma[m], 
                             ")")),
     ylim = c(0, 2), col = "black", xaxs="i", yaxs="i");
points(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25,
     col = "black", lty = "solid");
g_v <- which(g_f > g_m);
g_w <- which(g_f <= g_m);
polygon(x = c(alpha_vals[g_v], rev(alpha_vals[g_v])), 
        y = c(g_m[g_v], rev(g_f[g_v])),
        border = NA, col = "grey70");
polygon(x = c(alpha_vals[g_w], rev(alpha_vals[g_w])), 
        y = c(g_m[g_w], rev(g_f[g_w])),
        border = NA, col = "grey20");
bott <- rep(0, times = length(alpha_vals));
topp <- c(g_m[g_v], g_f[g_w]);
polygon(x = c(alpha_vals, rev(alpha_vals)),
        y = c(topp, rev(bott)),
        border = NA, col = "grey90");
points(x = alpha_vals, y = g_m, type = "l", lwd = 2, cex.lab = 1.25,
       col = "blue");
points(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25,
       col = "red");
text(x = 0.8, y = 0.15, cex = 2, labels = "A");
text(x = 0.25, y = 0.4, cex = 1.5, labels = "B");
text(x = 1.8, y = 1.1, cex = 4, labels = "C", col = "white");
text(x = 0.2, y = 1.75, cex = 5, labels = "D");
arrows(x0 = alpha_vals[10000], x1 = alpha_vals[9000], col = "blue",
       y0 = g_m[10000], y1 = 0.9, length = 0.1, lwd = 2);
text(x = alpha_vals[8300], y = 1.0, labels = "R", col = "blue");
arrows(x0 = alpha_vals[15000], x1 = alpha_vals[15000], col = "red",
       y0 = g_f[15000], y1 = 0.5, length = 0.1, lwd = 2);
text(x = alpha_vals[15000], y = 0.415, labels = "R", col = "red");
arrows(x0 = alpha_vals[12000], x1 = alpha_vals[12000], col = "red",
       y0 = g_f[12000], y1 = 0.5, length = 0.1, lwd = 2);
text(x = alpha_vals[12000], y = 0.415, labels = expression(T[f]), col = "red");
arrows(x0 = alpha_vals[18000], x1 = alpha_vals[18000], col = "red",
       y0 = g_f[18000], y1 = 0.5, length = 0.1, lwd = 2);
text(x = alpha_vals[18000], y = 0.415, labels = expression(T[m]), col = "red");
text(x = 1, y = 1.9, labels = "R = 2", cex = 1.5);
text(x = 1.8, y = 1.915, labels = "a", cex = 1.5, col = "black");

par(mar = c(5, 1, 1, 5))
beta_vals <- get_beta(M = 1, TF = 2, TM = alpha_vals);
g_m <- gamma_m(R = 1, beta = beta_vals, alpha = alpha_vals, TF = 2);
g_f <- gamma_f(R = 1, beta = beta_vals, alpha = alpha_vals, TF = 2);
plot(x = alpha_vals, y = g_m, type = "l", lwd = 2, cex.lab = 1.25,
     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
     ylab = "",
     ylim = c(0, 2), col = "black", xaxs="i", yaxs="i", yaxt = "n");
points(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25,
     col = "black", lty = "solid");
g_v <- which(g_f > g_m);
g_w <- which(g_f <= g_m);
polygon(x = c(alpha_vals[g_v], rev(alpha_vals[g_v])), 
        y = c(g_m[g_v], rev(g_f[g_v])),
        border = NA, col = "grey70");
polygon(x = c(alpha_vals[g_w], rev(alpha_vals[g_w])), 
        y = c(g_m[g_w], rev(g_f[g_w])),
        border = NA, col = "grey20");
bott <- rep(0, times = length(alpha_vals));
topp <- c(g_m[g_v], g_f[g_w]);
polygon(x = c(alpha_vals, rev(alpha_vals)),
        y = c(topp, rev(bott)),
        border = NA, col = "grey90");
points(x = alpha_vals, y = g_m, type = "l", lwd = 2, cex.lab = 1.25,
       col = "blue");
points(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25,
       col = "red");
text(x = 1.7, y = 0.15, cex = 2, labels = "A");
text(x = 1, y = 0.7, cex = 2, labels = "B");
text(x = 0.2, y = 1.75, cex = 5, labels = "D");
text(x = 1, y = 1.9, labels = "R = 1", cex = 1.5);
text(x = 1.8, y = 1.915, labels = "b", cex = 1.5, col = "black");
```

The analytical framework predicts 4 zones, which are delineated by inequalities 2 and 3 and describe the initial thresholds for favouring search of nuptial gifts in males and choosiness for nuptial gifts in females (Figure 2).
Consequently, the modelling framework gives a description of the conditions under which nuptial gift-giving is expected to occur (Figure 2, Zone D) and the conditions under which only selection for male searching (Figure 2, Zone B) or female choosiness (Figure 2, Zone C) are predicted. 
These results therefore highlight the potential for sexual conflict over nuptial gift-giving.

Evolution of male search and female choosiness
--------------------------------------------------------------------------------

We use an individual-based model (IBM) to simulate the evolution of nuptial gift-giving and female choosiness from an ancestral condition in which neither exists. 
The IBM was written to satisfy the assumptions of our analytical time-in and time-out model as much as practical (see Supporting Information S1). 
Using the IBM, we modelled a spatially-implicit, finite population of females and males. 
At each time step, some individuals enter or remain within the mating pool (time-in), where they potentially interact and mate. 
After mating, males and females may leave the mating pool to search for nuptial gifts and to produce offspring, respectively (time-out). 
Mortality occurs with a fixed probability in each time step, then a ceiling regulation is applied to limit population growth (see Methods).

The rates at which males encounter females $R_{\mathrm{m}}$ and females encounter males with nuptial gifts $R_{\mathrm{f,G}}$ are calculated directly from the IBM, thereby modelling how these rates might be estimated from empirical data, so the male threshold for increasing fitness by searching is,

<!---

$$\gamma_{m, IBM} > \alpha M_{m}.$$

--->

\begin{equation}
\gamma_{\mathrm{m, IBM}} > \alpha R_{\mathrm{m}}.
\end{equation}

Similarly, female threshold for increasing fitness by choosiness is,

<!---

$$\gamma_{f, IBM} > \frac{1}{T_{m}M_{f,G}}.$$

--->

\begin{equation}
\gamma_{\mathrm{f, IBM}} > \frac{1}{T_{\mathrm{f}}R_{\mathrm{f,G}}}.
\end{equation}

Consequently, the IBM and the analytical model differ slightly (e.g., time is discrete in the IBM but continuous the analytical model, and in the IBM a fitness increment is applied to the focal female in the form of birthrate increase rather than offspring; see Supporting Information S1 for details). 
But the predicted thresholds are theoretically equivalent and yield predictions that are qualitatively the same (Figure 3).

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from 3200 replicate simulations with identical starting conditions. Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively (in agreement with Figure 2). Minor deviations between the analytical model and the simulation results are expected due to the finite population size and the substantial stochasticity inherent to the simulation model (for details, see Supporting Information S1). Approximately 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction. The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 2.0] and [0.1, 2.0], respectively, were used."}
SUMM         <- read.csv(file = "inst/summary_coevolving.csv")
alpha_vals   <- sort(unique(SUMM[,1]));  
TM_vals      <- tapply(X = SUMM[,3],  INDEX = SUMM[,1], FUN = mean);
m_vals       <- tapply(X = SUMM[,13], INDEX = SUMM[,1], FUN = mean);
beta_vals    <- tapply(X = SUMM[,14], INDEX = SUMM[,1], FUN = mean);
Male_M       <- tapply(X = SUMM[,15], INDEX = SUMM[,1], FUN = mean);
Female_M     <- tapply(X = SUMM[,16], INDEX = SUMM[,1], FUN = mean);
Mf_nupt      <- tapply(X = SUMM[,17], INDEX = SUMM[,1], FUN = mean);
Mf_nonupt    <- tapply(X = SUMM[,18], INDEX = SUMM[,1], FUN = mean);

g_m <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
g_f <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, TF = 2);

par(mar = c(5, 5, 1, 1)); 
plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
                             ")")),
     ylim = c(0, 2));

points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");

for(i in 1:dim(SUMM)[1]){
  if(SUMM[i, 4] > 0 & SUMM[i, 5] > 0){
    points(x = SUMM[i, 1], y = SUMM[i, 2], cex = 3, pch = 20, col = "blue");
  }
}

for(i in 1:dim(SUMM)[1]){
  if(SUMM[i, 7] > 0 & SUMM[i, 8] > 0){
    points(x = SUMM[i, 1], y = SUMM[i, 2], cex = 2, pch = 20, col = "red");
  }
}
```

Male thresholds $\gamma_{\mathrm{m, IBM}}$ given by ineq. 4 accurately predict the evolution of searching in the IBM across $\alpha$ values, and the female threshold $\gamma_{\mathrm{f, IBM}}$ (ineq. 5) accurately predicts the evolution of female choice (Figure 3). 
In other words, IBM simulations demonstrate that nuptial gift search in males, and choosiness in females, will evolve from an ancestral state of no searching and no choosiness in similar parameter space (Figure 3) as predicted by the analytical model (Figure 2).
We further ran the IBM with realistic values of $\gamma$, estimated using data from the *P. mirabilis* system wherein choosiness among females, and nuptial gift search among males, occur (Figure 4). 
We found that our IBM predicts both the evolution of choosiness and nuptial gift searching observed in the *P. mirabilis* system.

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "The joint evolution of male search and female choosiness using a nuptial gift fitness increment ($\\gamma$) that was estimated from experimental data for the species *P. mirabilis* (Tuni et al. 2013; mean $\\gamma = 3.29 \\pm$ SE via propagation of error for estimates of nuptial feeding a non-nuptial feeding groups: [1.47; 8.32]). Points show where the 95% confidence interval exceeds 0 for female choosiness (red) and male search (blue). Each point includes data from 100 replicate simulations with identical starting conditions. The red line shows the threshold above which females should be choosy and the blue line shows the threshold above which males should search. As predicted by the analytical model, both male search and female choosiness evolved for a range of $\\gamma$ values around the empirical estimates. This occurs because these values result in a $\\gamma$ above the fitness threshold necessary for selection to favour male search of nuptial gifts (blue line) and female choosiness (red line). Approximately 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction. The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the [0.2, 2.0], respectively, were used. The parameter $\\gamma$ was estimated as relative increase in offspring production such that $\\gamma$ is the factor by which fitness increases (relative to the baseline fitness) given a nuptial gift (See Supporting Information S5)."}
SUME         <- read.csv(file = "inst/summary_empirically_inspired.csv")
alpha_vals   <- sort(unique(SUME[,1]));  
TM_vals      <- tapply(X = SUME[,3],  INDEX = SUME[,1], FUN = mean);
m_vals       <- tapply(X = SUME[,13], INDEX = SUME[,1], FUN = mean);
beta_vals    <- tapply(X = SUME[,14], INDEX = SUME[,1], FUN = mean);
Male_M       <- tapply(X = SUME[,15], INDEX = SUME[,1], FUN = mean);
Female_M     <- tapply(X = SUME[,16], INDEX = SUME[,1], FUN = mean);
Mf_nupt      <- tapply(X = SUME[,17], INDEX = SUME[,1], FUN = mean);
Mf_nonupt    <- tapply(X = SUME[,18], INDEX = SUME[,1], FUN = mean);

g_m <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
g_f <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, TF = 2);

par(mar = c(5, 5, 1, 1)); 
plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
                             ")")),
     ylim = c(0, 5.5));

points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");

for(i in 1:dim(SUME)[1]){
  if(SUME[i, 4] > 0 & SUME[i, 5] > 0){
    points(x = SUME[i, 1], y = SUME[i, 2], cex = 3, pch = 20, col = "blue");
  }
}

for(i in 1:dim(SUME)[1]){
  if(SUME[i, 7] > 0 & SUME[i, 8] > 0){
    points(x = SUME[i, 1], y = SUME[i, 2], cex = 2, pch = 20, col = "red");
  }
}
```

Discussion
================================================================================

Nuptial gift-giving has arisen several times independently throughout the animal kingdom [@Lewis2012], so understanding how selection favours nuptial gift giving and choosiness is important for a broad range of mating systems. 
We provide a general framework that defines the necessary conditions for selection to favour the evolution of nuptial gift-giving. 
We show that males should give nuptial gifts if the value of a nuptial gift exceeds a threshold dependent on the encounter rate between males and females and the cost or time necessary to find or produce a nuptial gift (see ineq. 2). 
This result makes intuitive sense because if males rarely encounter females, time searching for a gift is a minor cost relative to mate search time. 
If males encounter many females, it is not worth seeking nuptial gifts unless gifts are very valuable since the male will meet many prospective mates, and nuptial gift search time might come at a cost of decreased mating opportunities. 
In practice, male biased sex ratios will not necessarily favour male search for nuptial gifts if the female encounter rate is very high, so the key variable is how often males and females encounter each other. 
If the search time or cost of finding a nuptial gift is high, nuptial gifts must be very valuable before search is favoured by selection.

Threshold fitness values
--------------------------------------------------

Importantly, we show that the threshold nuptial gift value at which females are favoured to express choosiness for nuptial gifts is rarely equivalent to the threshold value at which males are favoured to search for nuptial gifts, potentially leading to sexual conflict [@Oliveira2008; @Arnqvist2005a]. 
Here, we are defining sexual conflict as occurring when interactions between sexes result in situation where both sexes cannot achieve an optimal outcome simultaneously [@Parker2006].
As an example, sizable areas of parameter space exists wherein the female optimum would be to exhibit preference for (and receive) nuptial gifts, while the male optimum is to not search for (and give) nuptial gifts (see Figure 2, Zone C).
In many systems, ecological variables such as search time required to find a nuptial gift will likely depend on prey abundance,  which can vary substantially with time in some species with nuptial gift-giving [@Ghislandi2018]. 
Since several ecological variables likely affect the value of these thresholds, our results can be seen as providing some formalised description of why nuptial gift-giving only occurs in some but not all systems.

At first, the analytical model seems to suggests that nuptial gifts must cause a very high fitness increase (approximately 25\%) before male search and female choosiness is favoured by selection (Figure 2). 
Similarly the IBM model seems to suggest that a fitness benefit of approximately 50\% is required (see Figure 3). 
However, it is important to point out that these thresholds depend on multiple parameters.
For example, if female processing time ($T_{\mathrm{f}}$) is high, the female threshold for choosiness with respect to $\gamma$ drops such that male search and female choosiness are favoured at lower $\gamma$ (see Supporting formation S1). 
If $T_{f}$ is sufficiently high, then an initially rare gift-giving trait might therefore be favoured by selection even if the fitness benefit of a nuptial gift is low.
The effect that nuptial gifts have on fitness might vary across systems, or even populations.
Effects on female fecundity have been estimated in crickets, fireflies, butterflies, and spiders, but these estimates vary considerably between species suggesting a large positive effect to no effect at all [@Bergstrom2002; @Gao2019; @Maxwell2018; @Rooney2002].

When modelling nuptial gift evolution, the challenge is to construct a modelling framework that captures the frequency-dependent selection between male nuptial gift-giving and female preference for nuptial gifts, and we do this using a time-in, time-out model.
Recent studies have modelled some frequency-dependent aspect of nuptial gift giving using evolutionary game theory [@MaynardSmith1982; @Vincent2005]. 
Two such studies formulated a quantitative genetics model to study evolutionarily stable nuptial gift sizes in populations where the female propensity to remate was evolving [@Iwasa2022; @Kamimura2021].
The results obtained in these studies complement our results by giving equilibrium solutions to the evolutionary stable nuptial gift size, whereas we determine the general conditions under which nuptial gift-giving will evolve as given by the inequalities we derive.

Other modelling frameworks have made general predictions about sexually selected traits, and these predictions are not mutually exclusive to those made by our model.
For example, the good genes hypothesis predicts that costly traits such as nuptial gift-giving can be favoured since males enduring the cost of a nuptial gift signals to females that their genes confer high fitness precisely because they can afford this cost [@Kirkpatrick1996; @Byers2006; but see @Fromhage2022].
In other words, costly sexually selected traits are favoured because they are indicators of overall genetic quality [@Martinossi-Allibert2019]. 
Because of this, nuptial gift-giving could be a case of condition-dependence where engaging in nuptial gift-giving is only favourable for male in good condition (e.g., males capable of successful search [@Ghislandi2018; @MaynardSmith1982; @Engqvist2015]). 
In general, our model demonstrates how nuptial gift-giving initially evolves before other mechanisms, such as good gene effects, become relevant.

A nuptial gift can also constitute a dishonest signal of good body condition since worthless, deceptive nuptial gifts have evolved in several systems [@Ghislandi2014; @LeBas2005]. 
This is also the case in *P. mirabilis* where males will wrap plant parts or an empty exoskeleton in silk, as opposed to an arthropod prey, and use this as a nuptial gift [@Ghislandi2014; @Albo2011]. 
In such systems, worthless nuptial gifts have been shown to reduce the likelihood that a male is rejected by a female compared to the case where no nuptial gift is given. 
However, males offering worthless nuptial gifts may be at a slight disadvantage in sperm competition since worthless gifts result in a shorter copulation duration and hence less sperm transfer [@Albo2013; @Ghislandi2014]. 
Worthless gifts should not result in any paternal care benefits to the male since the offspring he may sire will not gain nutrition from a worthless nuptial gift.

Given our modelling framework, worthless nuptial gifts may be expected to evolve in cases where females are discriminating in favour of nuptial gifts, but the cost of search time for a true nuptial gift is very high such that selection will not favour male search.
This scenario would correspond to zone C of Figure 2 where the value of the nuptial gift exceeds the female fitness threshold for choosiness to be favoured, but due to high search time, selection will not favour male search for true nuptial gifts. 
Our model also predicts the possibility of the opposite scenario, in which males provide nuptial gifts, but females do not exhibit preference for nuptial gifts (zone B of Figure 2). 
Fascinatingly, an example of such system has been documented by a recent study of the genus *Trechaleoides*, which contains two species with true nuptial gift-giving, but a lack of preference for nuptial gifts among female [@Martinez2023].

The main drivers of male nuptial gift-giving are thought to be indirect fitness benefits and increased success in sperm competition, since providing a nuptial gift can result in longer copulation duration which is correlated with increased sperm transfer along with female cryptic choice promoting males who provide nuptial gifts [@Albo2013; @Albo2011].
However, nuptial gifts might also function to modulate female aggression and prevent sexual cannibalism [@Bilde2006]. 
In some systems, such as *P. mirabilis*, males have been shown to reduce the risk of being cannibalised by the female after mating when offering a nuptial gift, such that the nuptial gift may result in a "shield effect", protecting the male [@Toft2016].

The simulations parameterised with an experimentally estimated value of $\gamma$ showed evolution of nuptial gift searching in males and choosiness for nuptial gifts in females.
The model thus predicts that *P. mirabilis* living under conditions with the estimated fitness value of nuptial gifts should exhibit both search for nuptial gifts and choosiness for males with nuptial gifts, and this is what is observed in empirical populations.
Parameterising $\gamma$ with data from experimental studies may only yield a rough approximation of the true $\gamma$.
This is because the estimated value of $\gamma$ is based on data from current populations (rather than ancestral populations, which are being simulated), and because the literature is inconclusive as to how much (if any) effect nuptial gifts have on female fitness [@Maxwell2018].
The effect of nuptial gifts on female fecundity has been estimated in a variety of system such as crickets, fireflies, butterflies and spiders, but these estimates vary considerably between species suggesting a large positive effect to no effect at all [@Bergstrom2002; @Rooney2002; @Maxwell2018; @Gao2019].

Our model assumes something akin to sequential polyandry. 
That is, a system wherein female mating and reproduction with multiple males occurs in sequence, rather than multiple matings occurring before reproduction. 
In some systems with nuptial gift-giving, females have been documented to mate multiple times before reproduction occurs, including the genus of bark lice *Neotrogla* [@Kamimura2021], and even our example system of *P. mirabilis* where females will sometimes engage in multiple mating before reproducing, especially if starved because multiple mating may result in more nuptial gifts [@Toft2015; @Matzke2022].
It is unclear what effect (if any) assuming non-sequential polyandry would have on the threshold we derive. 
Under non-sequential polyandry, a viable strategy for females might be to accept any male (with or without gift) for fertilisation assurance, then exhibit a preference for nuptial gifts. 
This might make choosiness less costly since it would entail less of an opportunity cost to be choosy, and this could potentially make female preference for nuptial gifts more likely to evolve. 
Our model also assumes that males search in time out, rather than contribute to parental care, which is likely to be accurate for most systems but not all. 
Expanding the model to explore these possibilities would be a worthwhile goal for future research.

Overall, we found that a simple relationship between nuptial gift search time and mate encounter rate yields a threshold that determines whether selection will favour males that search for nuptial gifts. 
Similarly, we found that the threshold determining whether females will be favoured to reject males without nuptial gifts is also dependent on these variables, along with offspring processing time.
Together, these thresholds describe the conditions under which nuptial gift-giving is expected to evolve.
The applications of these thresholds are numerous. 
They can be used as a starting point for more complex or more system-specific models of nuptial gift-giving evolution. 
They can also provide novel insight into how populations can evolve to use worthless or token nuptial gifts.

Methods
================================================================================

Model
--------------------------------------------------------------------------------

Here we first present more detail for the derivation of fitness threshold values $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$.
We then present full details for IBM simulations (see Supporting Information S1). 
Code for simulations is available on GitHub (see "Data availability").

Derivation of fitness thresholds
--------------------------------------------------------------------------------

We use a time-in and time-out model in which females and males spend some time searching for a mate (time-in) followed by a period of cool down outside the mating pool (time-out; Figure 1).

After mating, females must spend some time processing offspring ($T_{\mathrm{f}}$). 
Male time to replenish sperm is assumed to be negligible, but males can spend time out of the mating pool to search for a nuptial gift ($T_{\mathrm{m}}$).
When males return from time-out, they encounter females with some probability that is a function of the rate at which an individual encounters conspecifics ($R$) and the sex ratio ($\beta$; males/females). 
Mortality occurs for females and males in ($\mu_{\mathrm{i,f}}$, $\mu_{\mathrm{i,m}}$) and out ($\mu_{\mathrm{o,f}}$, $\mu_{\mathrm{o,m}}$) of the mating pool. 
Following @Kokko2006, we assume $m_{\mathrm{i,f}} = m_{\mathrm{o,f}} = 1$ and $m_{\mathrm{i,m}} = m_{\mathrm{o,m}} = 1$. 
While this choice is arbitrary, we conducted a sensitivity analysis which shows that the mortality parameters have no influence on the propensity for male search and female choice to evolve (Supporting Information S2). 
First, we describe the fitness consequences of male search time for a nuptial gift. 
We then describe the fitness consequences of female choice to accept or reject males based on their provision of a nuptial gift.

Male fitness
--------------------------------------------------------------------------------

During time-out, males have the opportunity to search for a nuptial gift.
Males can adopt one of two strategies; either search or do not search for a nuptial gift. 
Males with the former strategy continue to search until they find a nuptial gift, while males that do not search will immediately re-enter the mating pool. 
In this case, time searching for a nuptial gift will come at the cost of mating opportunities but might increase offspring fitness offspring. 
We therefore need to model the expected length of time $E[T_{\mathrm{m}}]$ spent outside of the mating pool for males that search for nuptial gifts, which is simply $\alpha$. 
Note that we can integrate search time $t$ over the rate at which nuptial gifts are encountered ($\exp(-1/\alpha)$) to show $E[T_{\mathrm{m}}] = \alpha$,

$$E[T_{\mathrm{m}}] = \int_{0}^{\infty}e^{- \frac{1}{\alpha}t}dt = \alpha.$$

The rate at which a focal male that searches for a nuptial gift increases his fitness is therefore the fitness of his offspring $(1 + \gamma)$ divided by expected time spent searching for a nuptial gift ($\alpha$) plus time spent in the mating pool, $(\beta + 1)/R$ (recall that females produce $\lambda$ offspring),

$$W_{m,G} = \lambda \frac{1 + \gamma}{\alpha + \left( \frac{\beta + 1}{R} \right)}.$$

In contrast, a male that does not search for a nuptial gift has offspring with lower fitness, but spends less time outside of the mating pool,

$$W_{m,L} = \lambda \frac{1}{\left(\frac{\beta+1}{R} \right)} = \lambda \frac{R}{\beta + 1}.$$

We can then determine the conditions for which $W_{\mathrm{m},G} > W_{\mathrm{m},L}$, isolating $\gamma$ to find how large of a fitness benefit must be provided by the nuptial gift to make the search cost worthwhile, which simplifies to ineq. 2. 
When this inequality holds, males are favoured to search until they find a nuptial gift, which would result in an average search time of $\alpha$. 
When the male trait is continuous (i.e., males search for time period $T_{\mathrm{m}}$), it can be shown that the same threshold can be reached by evaluating the partial derivative of the male fitness function (Supporting Information S3). 
Hence, the thresholds are consistent under different assumptions concerning male searching strategy.
Selection will cause males to search for nuptial gifts if the fitness increase to offspring exceeds the product of search time and female encounter rate.

Female fitness
--------------------------------------------------------------------------------

During time-out, females process offspring over a duration of $T_{\mathrm{f}}$ (we assume that $T_{\mathrm{f}} > \alpha$, else females are not the choosy sex). 
When females re-enter the mating pool, they encounter males at a rate of $R\beta/(\beta + 1)$. 
If a female encounters a male with a nuptial gift, we assume that she will mate with him. 
But if a female encounters a male with no nuptial gift, then she might accept or reject the male. 
If she rejects the male, then she will remain in the mating pool. 
The rate at which a female encounters a male with a nuptial gift is,

$$R_{f,G} = R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right).$$

We can similarly model the rate at which a female encounters a gift-less male,

$$R_{f,L} = R \left(\frac{\beta}{\beta + 1}\right)\left(e^{-\frac{1}{\alpha}T_{m}}\right).$$

Note that we can recover the rate at which a female encounters any male,

$$R \left(\frac{\beta}{\beta + 1}\right) = R \left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + R \left(\frac{\beta}{\beta + 1}\right) \left(e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right).$$

If $R_{\mathrm{f},G}$ is sufficiently high and $R_{\mathrm{f},L}$ is sufficiently low, then finding a male with a gift will be easier than finding a male without one. 
Also, the expected time spent in the mating pool before a focal female encounters a male with a gift will be $1/R_{\mathrm{f},G}$, while the expected time spent in the mating pool before a focal female encounters any male will be $1 / (R_{\mathrm{f},G} + R_{\mathrm{f},L})$.
Finally, the rates at which a female encounters males with and without a gift, $R_{\mathrm{f},G}$ and $R_{\mathrm{f}, L}$, are different from the probabilities that a male encounter has or does not have a gift. 
The rate of encounter is no longer relevant in this case because we are assuming that an encounter has occurred. 
Hence, the probability of an encountered male having a gift is simply,

$$G = \frac{1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}} = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$

Similarly, the probability of an encountered male not having a gift is simply,

$$L = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$

The rate at which a female increases her fitness by being choosy and mating only when she encounters a male with a gift is,

<!---

$$W_{f, g} = \frac{1 + \gamma}{T_{F} + \frac{1}{M_{f,G}}}.$$

--->

\begin{equation}
W_{\mathrm{f}, G} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}} + \frac{1}{R_{\mathrm{f},G}}}.
\end{equation}

The top of the right-hand side of Eq. 6 gives the fitness increase, and the bottom gives the total time it takes to obtain this fitness. 
The $R_{\mathrm{f},G}$ is inverted because it represents the expected time to encountering a male with a gift. 
We can expand Eq. 6,

$$W_{\mathrm{f},G} = \lambda \frac{1 + \gamma}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right)}}.$$

If the focal female is not choosy and accepts the first male that she encounters, then the rate at which she increases her fitness is,

$$W_{\mathrm{f},l} = \lambda \frac{\left(1 + \gamma\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right) + e^{-\frac{1}{\alpha}T_{m}}}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)}}.$$

We then evaluate the conditions under which $W_{\mathrm{f}, G} > W_{\mathrm{f}, L}$. 
We isolate $\gamma$ to determine how much offspring fitness must be increase to make choosiness beneficial ($\gamma_{\mathrm{f}}$),

$$\gamma_{\mathrm{f}} > \frac{1 + \frac{1}{\beta}}{D T_{f} \left(1 - e^{-1\frac{1}{\alpha}T_{m}}\right)}.$$

The above can be expressed as Eq. 7 below,

<!---

$$\gamma_{f} > \frac{1}{T_{F}M\sqrt{\beta}\left(1 - e^{-\frac{1}{\alpha}T_{M}} \right)}.$$

--->

\begin{equation}
\gamma_{\mathrm{f}} > \frac{1}{ T_{f} R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right)}.
\end{equation}

Note that that the expression $R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right)$ defines the rate at which a female in the mating pool encounters males with nuptial gifts. 
Hence, female choosiness is ultimately determined by time spent out of the mating pool to process offspring ($T_{\mathrm{f}}$) and the rate at which a female in the mating pool encounters males with nuptial gifts.

Operational sex ratio
----------------------------

We assume that the sex ratio is equal upon maturation. 
Given this, Kokko and Monaghan [@Kokko2001] show that the operational sex ratio depends on the probability of finding an individual in 'time in',

<!---

$$\beta = \frac{\int_{t = 0}^{\infty} P_{IM}(t)dt}{\int_{t = 0}^{\infty} P_{IF}(t)dt}.$$

--->

\begin{equation}
\beta = \frac{\int_{t = 0}^{\infty} P_{IM}(t)dt}{\int_{t = 0}^{\infty} P_{IF}(t)dt}.
\end{equation}

In Eq. 8, $P_{IM}(t)$ and $P_{IF}(t)$ are the probabilities of finding a male and female in 'time in', respectively. 
There is no closed form solution to the operational sex ratio, so we used recursion to calculate $\beta$ values for a given $T_{\mathrm{f}}$, $T_{\mathrm{m}}$, and $R$ (see Supporting Information S4),

Individual-based model
------------------------------------------

We formulate an individual-based simulation model to test whether the predictions made by the analytical time-in time-out model are qualitatively the same under a similar simulation model. 
We use the individual-based model to test whether the prediction hold in finite populations (see Supporting Information S6). 
The IBM was written in C. 
All details of the initialisation, parameterisation and the specific simulations which we run, are described in the supporting information (see Supporting Information S1).

We use available experimental data on the effect of nuptial gifts on female offspring production to estimate the key parameter $\gamma$ (fitness increment from nuptial gift) and conducted a series of simulations where $\gamma$ was parameterised using this estimated value. 
Details of the estimation of $\gamma$ are described in the supporting information (see Supporting Information S5).

**Author contributions:** APC and ABD conceived the study. ABD constructed the modelling framework with input from APC. APC wrote the paper with input from ABD and ABD wrote the IBM model. TB and GB provided substantial comments on previous drafts and final text.

**Acknowledgements:** Anders P. Charmouh was supported by the University of Aberdeen. A. Bradley Duthie was supported by the University of Stirling. Trine Bilde was supported by The Danish Council for Independent Research grant number 4002-00328B. We thank Maria Albo for making available data from a previous study which was useful for parameter estimating.

**Data availability:** The simulation software was implemented in C and the full source code is available at https://github.com/bradduthie/Pisaura.

**Competing interests:** The authors declare no competing interests.

**References**

<div id="refs"></div>

\clearpage

Supporting Information
====================================

| Information                                                   | Page |
|---------------------------------------------------------------|------|
| S1: Description of the individual-based simulation model      |  26  |
| S2: Sensitivity analysis of mortality parameters in IBM       |  29  |
| S3: Alternative derivation of male fitness threshold          |  31  |
| S4: Operational sex ratio                                     |  33  |
| S5: Estimation of key model parameter using experimental data |  35  |
| S6: Separate evolution of male search and female choice       |  36  |

\clearpage

S1: Description of the individual-based simulation model
------------------------------------

Here we describe the details of initialisation, time-in (mating), time-out (reproduction and nuptial gift search), and mortality. 
We then summarise the simulations run and data collected.

*Initialisation*

Before the first time step, a population of $N = 1000$ individuals is initialised. 
Individuals are assigned unique IDs, and each is assigned to be female with a probability of $0.5$, else male. 
Each individual $i$ is initialised with a starting value of female offspring processing time ($T^{i}_{\mathrm{f}}$), rejection rate for females ($\rho^{i}$), and male search time ($T^{i}_{\mathrm{m}}$). 
For all simulations, initialised values are set to $T^{i}_{\mathrm{f}} = 2$, $\rho^{i} = 0$, and $T^{i}_{\mathrm{m}} = 0$. 
All individuals are initalised outside of the mating pool in the first time step $t = 1$. 
The first time step then proceeds with females immediately entering the mating pool and males either entering the mating pool or searching for nuptial gifts.

*Time-in*

At the start of each time step, females and males in the mating pool remain in it. 
Females will enter the mating pool after processing offspring, and males will enter it after searching for nuptial gifts (see 'Time-out' below). 
A fixed number of $\Psi = N\psi$ interactions between individuals occur in a single time step, where $N$ is population size and $\psi$ is a scaling parameter. 
Since an interaction includes two conspecifics, each individual is expected to encounter a conspecific $2\psi$ times per time step (i.e., $R = 2\psi$).
For each interaction, two individuals are randomly sampled, each with equal probability. 
If both sampled individuals are within the mating pool and of different sexes, then a mating encounter occurs. 
If the male does not have a nuptial gift, then the female will reject him with a probability of $\rho^{i}$; if rejection occurs, then both individuals stay in the mating pool. 
If rejection does not occur, or the male has a nuptial gift in the mating encounter, then the individuals mate. 
Females leave the mating pool and enter time-out to process offspring, and males leave and enter time-out to potentially search for new nuptial gifts (note that females and males might re-enter the mating pool immediately within the same time step given sufficiently low search time; see Time-out below).

*Time-out*

During time out, a focal female $i$ will produce $\lambda_{i} \sim Poisson(\lambda)$ offspring if no nuptial gift was provided or $\lambda_{i} \sim Poisson(\lambda + \gamma)$ if a gift was provided. 
Females remain outside of the mating pool to process offspring for $T^{i}_{\mathrm{f}}$ time steps, where $T^{i}_{\mathrm{f}}$ is sampled randomly for each individual from a Poisson distribution with a rate parameter of $T_{\mathrm{f}}$, $T^{i}_{\mathrm{f}} \sim Poisson(T_{\mathrm{f}})$. 
Offspring are added to the population immediately, with $\rho^{i}$ and $T^{i}_{\mathrm{m}}$ values that are the average of each parent plus some normally distributed error $\epsilon_{R}$ and $\epsilon_{T_{\mathrm{m}}}$. 
For example,

$$T^{\mathrm{offspring}}_{\mathrm{m}} \sim N\left(\frac{T^{\mathrm{mother}}_{\mathrm{m}}  + T^{\mathrm{father}}_{\mathrm{m}}}{2}, \epsilon_{T_{\mathrm{m}}} \right).$$

The variation generated by $\epsilon$ values simulates mutation upon which selection for traits can act. 
In all simulations, $\epsilon = 0$ if a trait is fixed and $\epsilon = 0.01$ if the trait evolves. 
Offspring sex is randomly assigned with equal probability as female or male. 
Female offspring are immediately placed in the mating pool, and male offspring are out of the mating pool to search for nuptial gifts. 
After a female has spent $T^{i}_{\mathrm{f}}$ time steps outside the mating pool, she will re-enter it.

A focal male $i$ outside the mating pool will enter it if they have searched for a fixed number of $T^{i}_{\mathrm{m}}$ time steps, which is also sampled randomly from a Poisson distribution, $T^{i}_{\mathrm{m}} \sim Poisson(T_{\mathrm{m}})$. 
If $T^{i}_{\mathrm{m}} = 0$, then the male immediately returns to the mating pool (in the same time step). 
If $T^{i}_{\mathrm{m}} > 0$, then the male must wait outside the mating pool for $T^{i}_{\mathrm{m}}$ time steps, but will enter the mating pool with a nuptial gift with a probability,

$$G^{i} = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.$$

Males must always spend $T^{i}_{\mathrm{m}}$ time steps outside of the mating pool regardless of whether or not they are successful in obtaining a nuptial gift.

*Mortality*

At the end of time step, mortality occurs first with a fixed probability for all adults in the population, then with a probability caused by carrying capacity $K$ applied to all individuals (adults and offspring). 
Mortality occurs in each time step with a fixed probability of $\mu$ regardless of the sex of the individual or its position in or out of the mating pool. 
If after this fixed mortality is applied, the total population size $N > K$, then individuals are removed at random with equal probability until $N = K$. 
Following adult mortality, a new time step begins with newly added offspring becoming adults.

*Simulations*

We ran simulations in which male search time and female choosiness evolved from an ancestral state of no searching and no choosiness. 
In all simulations, $N$ was initialised at 1000 and $K = 1000$. 
Simulations ran for $t_{max} = 40000$ time steps. 
We set $T_{\mathrm{f}} = 2$, $\psi = 3$, and $\lambda = 1$ for all simulations, and we simulated across a range of $\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}$ and $\gamma = \{0, 0.1, ..., 1.9, 2.0\}$ parameter values for 1600 replicates. 
Summary statistics for mean trait values, population size, sex ratios, proportion of females and males in and out of the mating pool, and mean number of encounters per female and male within the mating pool were all calculated in the last time step. 
The C code used for simulating these IBMs also allows for the reporting of statistics in each time step. 
Additionally, it can simulate explicit space and individual movement through the landscape. 
A neutral evolving trait was also modelled to ensure that the code functioned as intended, and processes were compartmentalised into individual functions to facilitate code testing. 
All code is publicly available on GitHub (https://github.com/bradduthie/Pisaura).

A set of simulations with a value of $\gamma$ calculated from empirical data was also conducted. 
Here, $\gamma$ was parameterised using data on egg production as a function of eating nuptial gifts (see below). 
Additional simulation sets with lower and upper bounds of the estimated $\gamma$ were subsequently run. 
In the simulation sets with experimentally derived parameter values, all other parameters were identical to previous simulation batches.

We can produce an estimate of the fitness increment obtained by females when receiving a gift ($\hat{\gamma}$) by using data on female *P. mirabilis* egg production and hatching success under different feeding regimes from [@Tuni2013a]. 
@Tuni2013a found differences in egg production and hatching success in female *P. mirabilis* under different feeding regimes. 
Assuming these differences in feeding regimes correspond to eating versus not eating nuptial gifts, the mean number of offspring produced by a female who eats nuptial gifts can be calculated (Table 1).

S2: Sensitivity analysis of parameters in IBM
------------------------------------

**Mortality**

We conducted a sensitivity analysis of the effect of the mortality parameters $\mu_{\mathrm{in}}$ and $\mu_{\mathrm{out}}$ (the probability of mortality in time in and time out, respectively, which we assumed to be equal for all individuals) on the evolution of male search and female choice using the IBM (See S1). 
The results revealed no correlation between the value of the mortality parameters and the evolution of male search or female choice (Fig. S2.1).

\captionsetup{labelformat=empty}

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.1: Evolution of both male search (blue) and female choice (red) under different combinations of the mortality rates $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$ (mortality in time in and out, respectively). The y-axis is the threshold fitness that leads to evolution of male search (blue) or female choice (red). The results show noise, but no correlation between the value of the mortality parameters and the propensity for male search and/or female choice to evolve. For each of the $25 \\times 20$ combinations of $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$, 1600 replicate simulations were run."}
SUMO <- read.csv("inst/SI_mortality.csv");
mort_combn   <- paste(SUMO[,1], SUMO[,2]);
mort_label   <- unique(paste(SUMO[,1], ", ", SUMO[,2], sep = ""));
TM_vals      <- tapply(X = SUMO[,4],  INDEX = mort_combn, FUN = mean);
m_vals       <- tapply(X = SUMO[,14], INDEX = mort_combn, FUN = mean);
beta_vals    <- tapply(X = SUMO[,15], INDEX = mort_combn, FUN = mean);
Male_M       <- tapply(X = SUMO[,16], INDEX = mort_combn, FUN = mean);
Female_M     <- tapply(X = SUMO[,17], INDEX = mort_combn, FUN = mean);
Mf_nupt      <- tapply(X = SUMO[,18], INDEX = mort_combn, FUN = mean);
Mf_nonupt    <- tapply(X = SUMO[,19], INDEX = mort_combn, FUN = mean);
male_search  <- as.numeric(which(SUMO[,5] > 0 & SUMO[,6] > 0));
fem_choose   <- as.numeric(which(SUMO[,8] > 0 & SUMO[,9] > 0));
mimmom       <- unique(cbind(SUMO[,1], SUMO[,2]));

mm <- SUMO[male_search,];
mp <- NULL;
for(i in 1:dim(mm)[1]){
  rval <- which(mm[i, 1] == mimmom[,1] & mm[i, 2] == mimmom[,2]);
  mp   <- rbind(mp, c(rval, mm[i, 3]));
}

ff <- SUMO[fem_choose,];
fp <- NULL;
for(i in 1:dim(ff)[1]){
    rval <- which(ff[i, 1] == mimmom[,1] & ff[i, 2] == mimmom[,2]);
    fp   <- rbind(fp, c(rval, ff[i, 3]));
}

par(mar = c(8, 5, 1, 1));
plot(x = mp[,1], y = mp[,2], pch = 20, ylim = c(0, 2), col = "blue",
     xlab = "", ylab = "", xaxt = "n", cex.lab = 1.25);
points(x = fp[,1], y = fp[,2], cex = 2.5, col = "red", pch = 20);
points(x = mp[,1], y = mp[,2], cex = 1.5, col = "blue", pch = 20);
axis(side = 1, labels = mort_label, at = 1:25, las = 2);
mtext(text = expression(paste("Mortality combination (",mu["in"],", ", 
                              mu["out"],")")), side = 1, line = 6.5, 
      cex = 1.25); 
mtext(text = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
                              ")")), side = 2, line = 2.5, cex = 1.25); 
```

\captionsetup{labelformat=default}

**Female processing time**

We also conducted a sensitivity analysis of female processing time $T_{\mathrm{f}}$. 
To do this, we ran simulations at default values, but with $T_{\mathrm{f}} = 0.4$ (Figure S4.2) and $T_{\mathrm{f}} = 10.0$ (Figures S4.3).

\captionsetup{labelformat=empty}

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.2 ($T_{\\mathrm{f}} = 0.4$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from 720 replicate simulations with identical starting conditions. Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively. Approximately 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction. The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=0.4$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.5, 1.5] and [0.1, 2.1], respectively, were used."}
SUMM_Tf0pt4 <- read.csv("inst/SI_Tf_0pt4.csv");

alpha_vals <- sort(unique(SUMM_Tf0pt4[,1]));
TM_vals    <- tapply(X = SUMM_Tf0pt4[,3],  INDEX = SUMM_Tf0pt4[,1], FUN = mean);
m_vals     <- tapply(X = SUMM_Tf0pt4[,13], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
beta_vals  <- tapply(X = SUMM_Tf0pt4[,14], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
Male_M     <- tapply(X = SUMM_Tf0pt4[,15], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
Female_M   <- tapply(X = SUMM_Tf0pt4[,16], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
Mf_nupt    <- tapply(X = SUMM_Tf0pt4[,17], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
Mf_nonupt  <- tapply(X = SUMM_Tf0pt4[,18], INDEX = SUMM_Tf0pt4[,1], FUN = mean);

g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
                            TF = 0.4);

par(mar = c(5, 5, 1, 1)); 
plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
                             ")")),
     ylim = c(0, 2.1));

points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
       lty = "dashed");

for(i in 1:dim(SUMM_Tf0pt4)[1]){
  if(SUMM_Tf0pt4[i, 4] > 0 & SUMM_Tf0pt4[i, 5] > 0){
    points(x = SUMM_Tf0pt4[i, 1], y = SUMM_Tf0pt4[i, 2], cex = 3, pch = 20, 
           col = "blue");
  }
}

for(i in 1:dim(SUMM_Tf0pt4)[1]){
  if(SUMM_Tf0pt4[i, 7] > 0 & SUMM_Tf0pt4[i, 8] > 0){
    points(x = SUMM_Tf0pt4[i, 1], y = SUMM_Tf0pt4[i, 2], cex = 2, pch = 20, 
           col = "red");
  }
}
```

\captionsetup{labelformat=default}

\captionsetup{labelformat=empty}

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.3 ($T_{\\mathrm{f}} = 10.0$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from 720 replicate simulations with identical starting conditions. Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively. Approximately 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction. The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=10.0$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.5, 1.5] and [0.1, 2.1], respectively, were used."}
SUMM_Tf10 <- read.csv("inst/SI_Tf_10pt0.csv");

alpha_vals <- sort(unique(SUMM_Tf10[,1]));
TM_vals    <- tapply(X = SUMM_Tf10[,3],  INDEX = SUMM_Tf10[,1], FUN = mean);
m_vals     <- tapply(X = SUMM_Tf10[,13], INDEX = SUMM_Tf10[,1], FUN = mean);
beta_vals  <- tapply(X = SUMM_Tf10[,14], INDEX = SUMM_Tf10[,1], FUN = mean);
Male_M     <- tapply(X = SUMM_Tf10[,15], INDEX = SUMM_Tf10[,1], FUN = mean);
Female_M   <- tapply(X = SUMM_Tf10[,16], INDEX = SUMM_Tf10[,1], FUN = mean);
Mf_nupt    <- tapply(X = SUMM_Tf10[,17], INDEX = SUMM_Tf10[,1], FUN = mean);
Mf_nonupt  <- tapply(X = SUMM_Tf10[,18], INDEX = SUMM_Tf10[,1], FUN = mean);

g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
                            TF = 10);

par(mar = c(5, 5, 1, 1)); 
plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
                             ")")),
     ylim = c(0, 2.1));

points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
       lty = "dashed");

for(i in 1:dim(SUMM_Tf10)[1]){
  if(SUMM_Tf10[i, 4] > 0 & SUMM_Tf10[i, 5] > 0){
    points(x = SUMM_Tf10[i, 1], y = SUMM_Tf10[i, 2], cex = 3, pch = 20, 
           col = "blue");
  }
}

for(i in 1:dim(SUMM_Tf10)[1]){
  if(SUMM_Tf10[i, 7] > 0 & SUMM_Tf10[i, 8] > 0){
    points(x = SUMM_Tf10[i, 1], y = SUMM_Tf10[i, 2], cex = 2, pch = 20, 
           col = "red");
  }
}
```

\captionsetup{labelformat=default}

**Interactions between conspecifics**

We conducted a sensitivity analysis on the encounter rate between conspecifics ($R$) by varying the value of $\psi$, where $R = 2\psi$ (see S1).
Under default simulations, $\psi = 3$ and $R = 6$.
We also ran simulations in which $\psi = 1$ (Figure S4.4) and $\psi = 6$ (Figure S4.5), with all other parameters being set to default values.

\captionsetup{labelformat=empty}

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.4 ($\\psi = 1$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from 720 replicate simulations with identical starting conditions. Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively. Approximately 1000 interactions occur between individuals in each time step, potentially resulting in a mating interaction. The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
SUMM_Nexp1   <- read.csv("inst/SI_Nexp_1.csv");

alpha_vals   <- sort(unique(SUMM_Nexp1[,1]));
TM_vals      <- tapply(X = SUMM_Nexp1[,3],  INDEX = SUMM_Nexp1[,1], FUN = mean);
m_vals       <- tapply(X = SUMM_Nexp1[,13], INDEX = SUMM_Nexp1[,1], FUN = mean);
beta_vals    <- tapply(X = SUMM_Nexp1[,14], INDEX = SUMM_Nexp1[,1], FUN = mean);
Male_M       <- tapply(X = SUMM_Nexp1[,15], INDEX = SUMM_Nexp1[,1], FUN = mean);
Female_M     <- tapply(X = SUMM_Nexp1[,16], INDEX = SUMM_Nexp1[,1], FUN = mean);
Mf_nupt      <- tapply(X = SUMM_Nexp1[,17], INDEX = SUMM_Nexp1[,1], FUN = mean);
Mf_nonupt    <- tapply(X = SUMM_Nexp1[,18], INDEX = SUMM_Nexp1[,1], FUN = mean);

g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
                            TF = 2);

par(mar = c(5, 5, 1, 1)); 
plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
                             ")")),
     ylim = c(0, 2.1));

points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
       lty = "dashed");

for(i in 1:dim(SUMM_Nexp1)[1]){
  if(SUMM_Nexp1[i, 4] > 0 & SUMM_Nexp1[i, 5] > 0){
    points(x = SUMM_Nexp1[i, 1], y = SUMM_Nexp1[i, 2], cex = 3, pch = 20, 
           col = "blue");
  }
}

for(i in 1:dim(SUMM_Nexp1)[1]){
  if(SUMM_Nexp1[i, 7] > 0 & SUMM_Nexp1[i, 8] > 0){
    points(x = SUMM_Nexp1[i, 1], y = SUMM_Nexp1[i, 2], cex = 2, pch = 20, 
           col = "red");
  }
}
```

\captionsetup{labelformat=default}

\captionsetup{labelformat=empty}

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.5 ($\\psi = 6$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from 720 replicate simulations with identical starting conditions. Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively. Approximately 6000 interactions occur between individuals in each time step, potentially resulting in a mating interaction. The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
SUMM_Nexp2   <- read.csv("inst/SI_Nexp_2.csv");

alpha_vals   <- sort(unique(SUMM_Nexp2[,1]));
TM_vals      <- tapply(X = SUMM_Nexp2[,3],  INDEX = SUMM_Nexp2[,1], FUN = mean);
m_vals       <- tapply(X = SUMM_Nexp2[,13], INDEX = SUMM_Nexp2[,1], FUN = mean);
beta_vals    <- tapply(X = SUMM_Nexp2[,14], INDEX = SUMM_Nexp2[,1], FUN = mean);
Male_M       <- tapply(X = SUMM_Nexp2[,15], INDEX = SUMM_Nexp2[,1], FUN = mean);
Female_M     <- tapply(X = SUMM_Nexp2[,16], INDEX = SUMM_Nexp2[,1], FUN = mean);
Mf_nupt      <- tapply(X = SUMM_Nexp2[,17], INDEX = SUMM_Nexp2[,1], FUN = mean);
Mf_nonupt    <- tapply(X = SUMM_Nexp2[,18], INDEX = SUMM_Nexp2[,1], FUN = mean);

g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
                            TF = 2);

par(mar = c(5, 5, 1, 1)); 
plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
                             ")")),
     ylim = c(0, 2.1));

points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
       lty = "dashed");

for(i in 1:dim(SUMM_Nexp2)[1]){
  if(SUMM_Nexp2[i, 4] > 0 & SUMM_Nexp2[i, 5] > 0){
    points(x = SUMM_Nexp2[i, 1], y = SUMM_Nexp2[i, 2], cex = 3, pch = 20, 
           col = "blue");
  }
}

for(i in 1:dim(SUMM_Nexp2)[1]){
  if(SUMM_Nexp2[i, 7] > 0 & SUMM_Nexp2[i, 8] > 0){
    points(x = SUMM_Nexp2[i, 1], y = SUMM_Nexp2[i, 2], cex = 2, pch = 20, 
           col = "red");
  }
}
```

\captionsetup{labelformat=default}

\clearpage

\captionsetup{labelformat=empty}

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.5 ($\\psi = 6$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from 720 replicate simulations with identical starting conditions. Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively. Approximately 6000 interactions occur between individuals in each time step, potentially resulting in a mating interaction. The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
SUMM_Nexp4   <- read.csv("inst/SI_Nexp_4.csv");

alpha_vals   <- sort(unique(SUMM_Nexp4[,1]));
TM_vals      <- tapply(X = SUMM_Nexp4[,3],  INDEX = SUMM_Nexp4[,1], FUN = mean);
m_vals       <- tapply(X = SUMM_Nexp4[,13], INDEX = SUMM_Nexp4[,1], FUN = mean);
beta_vals    <- tapply(X = SUMM_Nexp4[,14], INDEX = SUMM_Nexp4[,1], FUN = mean);
Male_M       <- tapply(X = SUMM_Nexp4[,15], INDEX = SUMM_Nexp4[,1], FUN = mean);
Female_M     <- tapply(X = SUMM_Nexp4[,16], INDEX = SUMM_Nexp4[,1], FUN = mean);
Mf_nupt      <- tapply(X = SUMM_Nexp4[,17], INDEX = SUMM_Nexp4[,1], FUN = mean);
Mf_nonupt    <- tapply(X = SUMM_Nexp4[,18], INDEX = SUMM_Nexp4[,1], FUN = mean);

g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
                            TF = 2);

par(mar = c(5, 5, 1, 1)); 
plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
                             ")")),
     ylim = c(0, 2.1));

points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
       lty = "dashed");

for(i in 1:dim(SUMM_Nexp4)[1]){
  if(SUMM_Nexp4[i, 4] > 0 & SUMM_Nexp4[i, 5] > 0){
    points(x = SUMM_Nexp4[i, 1], y = SUMM_Nexp4[i, 2], cex = 3, pch = 20, 
           col = "blue");
  }
}

for(i in 1:dim(SUMM_Nexp4)[1]){
  if(SUMM_Nexp4[i, 7] > 0 & SUMM_Nexp4[i, 8] > 0){
    points(x = SUMM_Nexp4[i, 1], y = SUMM_Nexp4[i, 2], cex = 2, pch = 20, 
           col = "red");
  }
}
```

\captionsetup{labelformat=default}

\clearpage

\captionsetup{labelformat=empty}

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.5 ($\\psi = 6$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$). Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search. Each point includes data from 720 replicate simulations with identical starting conditions. Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively. Approximately 6000 interactions occur between individuals in each time step, potentially resulting in a mating interaction. The number of individuals in the population remained at or near carrying capacity of $K = 1000$. Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
SUMM_Nexp6   <- read.csv("inst/SI_Nexp_6.csv");

alpha_vals   <- sort(unique(SUMM_Nexp6[,1]));
TM_vals      <- tapply(X = SUMM_Nexp6[,3],  INDEX = SUMM_Nexp6[,1], FUN = mean);
m_vals       <- tapply(X = SUMM_Nexp6[,13], INDEX = SUMM_Nexp6[,1], FUN = mean);
beta_vals    <- tapply(X = SUMM_Nexp6[,14], INDEX = SUMM_Nexp6[,1], FUN = mean);
Male_M       <- tapply(X = SUMM_Nexp6[,15], INDEX = SUMM_Nexp6[,1], FUN = mean);
Female_M     <- tapply(X = SUMM_Nexp6[,16], INDEX = SUMM_Nexp6[,1], FUN = mean);
Mf_nupt      <- tapply(X = SUMM_Nexp6[,17], INDEX = SUMM_Nexp6[,1], FUN = mean);
Mf_nonupt    <- tapply(X = SUMM_Nexp6[,18], INDEX = SUMM_Nexp6[,1], FUN = mean);

g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
                            TF = 2);

par(mar = c(5, 5, 1, 1)); 
plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
                             ")")),
     ylim = c(0, 2.1));

points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
       lty = "dashed");

for(i in 1:dim(SUMM_Nexp6)[1]){
  if(SUMM_Nexp6[i, 4] > 0 & SUMM_Nexp6[i, 5] > 0){
    points(x = SUMM_Nexp6[i, 1], y = SUMM_Nexp6[i, 2], cex = 3, pch = 20, 
           col = "blue");
  }
}

for(i in 1:dim(SUMM_Nexp6)[1]){
  if(SUMM_Nexp6[i, 7] > 0 & SUMM_Nexp6[i, 8] > 0){
    points(x = SUMM_Nexp6[i, 1], y = SUMM_Nexp6[i, 2], cex = 2, pch = 20, 
           col = "red");
  }
}
```

\captionsetup{labelformat=default}

\clearpage

\captionsetup{labelformat=empty}

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Caption here"}
SUMM_Tm05   <- read.csv("inst/SI_Tm_0pt5.csv");

alpha_vals   <- sort(unique(SUMM_Tm05[,1]));
TM_vals      <- tapply(X = SUMM_Tm05[,3],  INDEX = SUMM_Tm05[,1], FUN = mean);
m_vals       <- tapply(X = SUMM_Tm05[,13], INDEX = SUMM_Tm05[,1], FUN = mean);
beta_vals    <- tapply(X = SUMM_Tm05[,14], INDEX = SUMM_Tm05[,1], FUN = mean);
Male_M       <- tapply(X = SUMM_Tm05[,15], INDEX = SUMM_Tm05[,1], FUN = mean);
Female_M     <- tapply(X = SUMM_Tm05[,16], INDEX = SUMM_Tm05[,1], FUN = mean);
Mf_nupt      <- tapply(X = SUMM_Tm05[,17], INDEX = SUMM_Tm05[,1], FUN = mean);
Mf_nonupt    <- tapply(X = SUMM_Tm05[,18], INDEX = SUMM_Tm05[,1], FUN = mean);

g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
                            TF = 2);

par(mar = c(5, 5, 1, 1)); 
plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
                             ")")),
     ylim = c(0, 1.6));

points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
       lty = "dashed");

for(i in 1:dim(SUMM_Tm05)[1]){
  if(SUMM_Tm05[i, 4] > 0 & SUMM_Tm05[i, 5] > 0){
    points(x = SUMM_Tm05[i, 1], y = SUMM_Tm05[i, 2], cex = 3, pch = 20, 
           col = "blue");
  }
}

for(i in 1:dim(SUMM_Tm05)[1]){
  if(SUMM_Tm05[i, 7] > 0 & SUMM_Tm05[i, 8] > 0){
    points(x = SUMM_Tm05[i, 1], y = SUMM_Tm05[i, 2], cex = 2, pch = 20, 
           col = "red");
  }
}
```

\captionsetup{labelformat=default}

\clearpage

\captionsetup{labelformat=empty}

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Caption here"}
SUMM_Tm2p5   <- read.csv("inst/SI_Tm_2pt5.csv");

alpha_vals   <- sort(unique(SUMM_Tm2p5[,1]));
TM_vals      <- tapply(X = SUMM_Tm2p5[,3],  INDEX = SUMM_Tm2p5[,1], FUN = mean);
m_vals       <- tapply(X = SUMM_Tm2p5[,13], INDEX = SUMM_Tm2p5[,1], FUN = mean);
beta_vals    <- tapply(X = SUMM_Tm2p5[,14], INDEX = SUMM_Tm2p5[,1], FUN = mean);
Male_M       <- tapply(X = SUMM_Tm2p5[,15], INDEX = SUMM_Tm2p5[,1], FUN = mean);
Female_M     <- tapply(X = SUMM_Tm2p5[,16], INDEX = SUMM_Tm2p5[,1], FUN = mean);
Mf_nupt      <- tapply(X = SUMM_Tm2p5[,17], INDEX = SUMM_Tm2p5[,1], FUN = mean);
Mf_nonupt    <- tapply(X = SUMM_Tm2p5[,18], INDEX = SUMM_Tm2p5[,1], FUN = mean);

g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
                            TF = 2);

par(mar = c(5, 5, 1, 1)); 
plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
                             ")")),
     ylim = c(0, 1.6));

points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
       lty = "dashed");

for(i in 1:dim(SUMM_Tm2p5)[1]){
  if(SUMM_Tm2p5[i, 4] > 0 & SUMM_Tm2p5[i, 5] > 0){
    points(x = SUMM_Tm2p5[i, 1], y = SUMM_Tm2p5[i, 2], cex = 3, pch = 20, 
           col = "blue");
  }
}

for(i in 1:dim(SUMM_Tm2p5)[1]){
  if(SUMM_Tm2p5[i, 7] > 0 & SUMM_Tm2p5[i, 8] > 0){
    points(x = SUMM_Tm2p5[i, 1], y = SUMM_Tm2p5[i, 2], cex = 2, pch = 20, 
           col = "red");
  }
}
```

\captionsetup{labelformat=default}

\clearpage

S3: Alternative derivation of male fitness threshold
------------------------------------

In the main text, we assumed that males made the decision to search or not search for a nuptial gift.
The expected length of time for which searching males are expected to remain outside of the mating pool is $E[T_{\mathrm{m}}] = \alpha$ (see Methods).
Alternatively, we can assume that males search for a period of $T_{\mathrm{m}}$ and spend this full duration of $T_{\mathrm{m}}$ in the time-out phase, even if they succeed in finding a nuptial gift.
The probability that a male obtains a nuptial gift during this time is modelled in Eq. 1,

$$G = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$

In Eq. 1, $\alpha$ is the amount of time expected to pass before a male encounters a nuptial gift. 
We assume that a male will only enter the mating pool with no gift if they are unsuccessful in obtaining a gift, so the probability that a male obtains no gift after $T_{\mathrm{m}}$ is,

$$L = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$

For simplicity, we assume that the fitness increments to offspring associated with receiving a nuptial gift versus no nuptial gift are $1 + \gamma$ and 1, respectively. 
The rate at which males increase their fitness can then be defined as the expected fitness increment from their nuptial gift search divided by $T_{\mathrm{m}}$ plus the time spent in the mating pool waiting to encounter a mate,

$$W_{\mathrm{m}} = \lambda \frac{G\left(1 + \gamma\right) + L}{T_{\mathrm{m}} + \left( \frac{\beta + 1}{R} \right)}.$$

Our objective now is to determine the conditions under which a focal male increases its fitness by searching for a nuptial gift ($T_{\mathrm{m}}>0$) in a population of resident males that do not search ($T_{\mathrm{m}}=0$). 
Females are assumed to exhibit no choice in males with versus without nuptial gifts. Under such conditions, male fitness cannot be affected by female choice, so selection to increase $T_{\mathrm{m}}>0$ must be based solely on $\alpha$, $\beta$, $R$, and $\gamma$.

To determine under what conditions male inclusive fitness increases with nuptial gift search time, we can differentiate $W_{\mathrm{m}}$ with respect to $T_{\mathrm{m}}$,

$$\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda\frac{\gamma\left(\frac{\frac{T_{\mathrm{m}} + \frac{\beta + 1}{R}}{\alpha} + 1}{e^{\frac{1}{\alpha}T_{\mathrm{m}}}} - 1\right) - 1}{\left(T_{\mathrm{m}} + \frac{\beta + 1}{R} \right)^{2}}.$$

Because $T_{\mathrm{m}} = 0$, the above simplifies,

$$\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda \frac{\frac{R\gamma\left(\beta + 1\right)}{\alpha} - R^{2}}{\left(1 + \beta \right)^{2}}.$$

We can re-arrange the above,

$$\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)} - \lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}}.$$

Note that if $R = 0$ or $\lambda = 0$, then, trivially, no change in fitness occurs (since females and males cannot mate or do not produce offspring). 
Fitness is increased by searching for nuptial gifts when $\gamma$ is high, scaled by the expect search time needed to find a nuptial gift. 
A second term on the right-hand side is subtracted, which reflects a loss in fitness proportional to the encounter rate of potential mates in the mating pool.
The conditions under which male inclusive fitness increases by searching for a nuptial gift are found by setting $\partial W_{\mathrm{m}}/\partial T_{\mathrm{m}} = 0$ and solving for $\gamma$ to get Eq. 2 in the main text.

\clearpage

S4: Operational sex ratio
------------------------------------

We assume that the ratio of males to femalesis the same upon individual maturation.
Consequently, the operational sex ratio $\beta$ will be a function of $R$, $T_{f}$, and $T_{m}$ because these parameters determine the density of females and males in the mating pool versus outside of the mating pool.
We start with the definition of $\beta$ as being the probability of finding an individual in 'time in' [@Kokko2001],

$$\beta = \frac{\int_{t=0}^{\infty}P_{IM}(t)dt}{\int_{t=0}^{\infty}P_{IF}(t)dt}$$

We can substitute the equations for $P_{IM}(t)$ and $P_{IF}(t)$, which define the probabilities of males and females being within the mating pool at time $t$, respectively.

We can therefore calculate $\beta$ as below,

$$\beta = \frac{\left( \frac{\left(\frac{\beta + 1}{R}\right)}{T_{\mathrm{m}} + \left(\frac{\beta + 1}{R}\right)} \right)}{\left( \frac{\left(R \frac{\beta}{\beta + 1}\right)}{T_{\mathrm{f}} + \left(R \frac{\beta}{\beta + 1}\right)} \right)}.$$

This can be simplified,

$$\beta = \frac{\left(\beta\left(R + T_{f}\right) + T_{f}\right)\left(\beta + 1\right)}{\beta \left(R^{2}T_{m} + R\right) + \beta^{2}R}.$$

There is no closed form solution for $\beta$, but a recursive algorithm can be used to calculate $\beta$ to an arbitrary degree of precision.

```{r}
recursive_b <- function(B, D, Tf, Tm, crit = 0.0001, maxit = 9999){
  conv <- 1;
  iter <- 0;
  while(conv > crit & iter < maxit){
    Fe   <- D * (B / (1 + B));
    Me   <- (1 + B) / D;
    Bn   <- (Me / (Tm + Me)) / (Fe / (Tf + Fe));
    iter <- iter + 1;
    conv <- abs(Bn - B);
    B    <- Bn;
  }
  return(list(B = B, conv = conv, iter = iter));
}
```

We used the above function to calculate values of $\beta$ for the analytical model.

\clearpage

S5: Estimation of key model parameters using experimental data
-------------------------------------

Estimates showing mean number of offspring produced by female *Pisaura mirabilis* that ate nuptial gifts and females who did not. 
Means were calculated with raw data from @Tuni2013a and results are shown $\pm$ SE (Table 1).
Under these assumptions, the relative gain in fitness from receiving nuptial gifts for a female is,

$$\hat{\delta_\mathrm{f}} = \frac{25.74}{6.00} = 4.29$$

Since the baseline fitness is 1, the increase in fitness resulting from a nuptial gift then becomes,

$$\hat{\gamma} = \hat{\delta_{\mathrm{f}}} - 1 = 3.29.$$

The value 3.29 was used to parameterise $\gamma$ for a set of simulations (Figure 4 in the main text).

|                                 | Received nuptial gift | Received no nuptial gift |
|---------------------------------|-----------------------|--------------------------|
| Expected number of hatched eggs | $25.74 \pm 0.96$      | $6.00 \pm 2.1$           |

Table 1: Estimates showing mean number of offspring produced by female *Pisauras mirabilis* that ate nuptial gifts and females who did not. Means were calculated with raw data from @Tuni2013a and results are shown $\pm$ SE.

\clearpage

S6: Separate evolution of male search and female choice
-------------------------------------

We used the individual-based simulation model (see Supporting Information S1) to unpack the effect of coevolution on the evolution of male search and female choice. 
Specifically, we replicated the simulations shown in the main text under the condition where only one trait at a time was allowed to evolve and studied how this affected the trait evolution.

First, we submitted a set of simulations wherein male search did not evolve, but was fixed at different values (see Fig. S6.1). 
Next, we ran the same set of simulations wherein male search evolved, but female choice was not possible). 
The results thus show how each trait evolves in the absence of any coevolution (Fig. S6.1).

\captionsetup{labelformat=empty}

```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S6.1: The separate evolution of male search and female choosiness as a function of nuptial gift search time. Points show where the lower 95% confidence interval of male search (blue) and female choosiness (red) exceeds zero, indicating evolution of nuptial gift search or choosiness. Each point includes data from $2 \\times 1600$ replicate simulations with identical starting conditions. In the first batch, male search was constant and initialized at $T_{\\mathrm{m}} = \\alpha$, and female choice was evolving. In the second batch, male search was evolving, and there was no option for female choice. The parameters $T_{\\mathrm{f}}=2$, and $\\gamma$ and $\\alpha$ values were set within the range [0.1, 2.0] and [0.3, 1.7], respectively."}
SUMM_m <- read.csv("inst/summary_male_evolving.csv");
SUMM_f <- read.csv("inst/summary_female_evolving.csv");
# Males
TM_vals      <- tapply(X = SUMM_m[,3],  INDEX = SUMM_m[,1], FUN = mean);
m_vals       <- tapply(X = SUMM_m[,13], INDEX = SUMM_m[,1], FUN = mean);
beta_vals    <- tapply(X = SUMM_m[,14], INDEX = SUMM_m[,1], FUN = mean);
Male_M       <- tapply(X = SUMM_m[,15], INDEX = SUMM_m[,1], FUN = mean);
Female_M     <- tapply(X = SUMM_m[,16], INDEX = SUMM_m[,1], FUN = mean);
Mf_nupt      <- tapply(X = SUMM_m[,17], INDEX = SUMM_m[,1], FUN = mean);
Mf_nonupt    <- tapply(X = SUMM_m[,18], INDEX = SUMM_m[,1], FUN = mean);
alpha_vals   <- sort(unique(SUMM_m[,1]));

g_m <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);

# Females 
TM_vals      <- tapply(X = SUMM_f[,3],  INDEX = SUMM_f[,1], FUN = mean);
m_vals       <- tapply(X = SUMM_f[,13], INDEX = SUMM_f[,1], FUN = mean);
beta_vals    <- tapply(X = SUMM_f[,14], INDEX = SUMM_f[,1], FUN = mean);
Male_M       <- tapply(X = SUMM_f[,15], INDEX = SUMM_f[,1], FUN = mean);
Female_M     <- tapply(X = SUMM_f[,16], INDEX = SUMM_f[,1], FUN = mean);
Mf_nupt      <- tapply(X = SUMM_f[,17], INDEX = SUMM_f[,1], FUN = mean);
Mf_nonupt    <- tapply(X = SUMM_f[,18], INDEX = SUMM_f[,1], FUN = mean);
alpha_vals   <- sort(unique(SUMM_f[,1]));

g_f <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, TF = 2);

par(mar = c(5, 5, 1, 1)); 
plot(x = alpha_vals, y = g_m, type = "l", lwd = 2, cex.lab = 1.25,
     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
                             ")")),
     ylim = c(0, 2), col = "blue");

for(i in 1:dim(SUMM_m)[1]){
  if(SUMM_m[i, 4] > 0 & SUMM_m[i, 5] > 0){
    points(x = SUMM_m[i, 1], y = SUMM_m[i, 2], cex = 3, pch = 20, col = "blue");
  }
}

points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red");

for(i in 1:dim(SUMM_f)[1]){
  if(SUMM_f[i, 7] > 0 & SUMM_f[i, 8] > 0){
    points(x = SUMM_f[i, 1], y = SUMM_f[i, 2], cex = 2, pch = 20, col = "red");
  }
}
```

\captionsetup{labelformat=default}

### 2024-06-01 ms_refs_fixed.tex
Add the manuscript files for Rmarkdown

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={A general model for the evolution of nuptial gift-giving},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{lineno}
\usepackage{caption}
\usepackage[utf8]{inputenc}
\bibliographystyle{amnatnat}
\linenumbers
\modulolinenumbers[2]
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{A general model for the evolution of nuptial gift-giving}
\author{Anders P. Charmouh\(^{1,4, 5}\), Trine Bilde\(^{2}\), Greta
Bocedi\(^{1}\), A. Bradley Duthie\(^{3}\)}
\date{{[}1{]} School of Biological Sciences, University of Aberdeen, UK.
{[}2{]} Department of Biology, Aarhus University, Denmark. {[}3{]}
Biological and Environmental Sciences, University of Stirling, UK.
{[}4{]} Bioinformatics Research Centre Aarhus University, University
City 81, building 1872, 3rd floor, DK-8000 Aarhus C, Denmark {[}5{]}
Email: \href{mailto:apc@birc.au.dk}{\nolinkurl{apc@birc.au.dk}}}

\begin{document}
\maketitle

\setstretch{2}
\textbf{Key words:} Nuptial gifts, male search, mate interactions,
modelling, \emph{Pisaura}

\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

Nuptial gift-giving occurs in several taxonomic groups including
insects, snails, birds, squid, arachnids and humans. Although this trait
has evolved many times independently, no general framework has been
developed to predict the conditions necessary for nuptial gift-giving to
evolve. We use a time-in time-out model to derive analytical results
describing the requirements necessary for selection to favour nuptial
gift-giving. Specifically, selection will favour nuptial gift-giving if
the fitness increase caused by gift-giving exceeds the product of
expected gift search time and encounter rate of the opposite sex.
Selection will favour choosiness in the opposite sex if the value of a
nuptial gift exceeds the inverse of the time taken to produce offspring
multiplied by the rate at which mates with nuptial gifts are
encountered. Importantly, selection can differ between the sexes,
potentially causing sexual conflict. We test these results using an
individual-based model applied to a system of nuptial gift-giving
spiders, \emph{Pisaura mirabilis}, by estimating parameter values using
experimental data from several studies. Our results provide a general
framework for understanding when the evolution of nuptial gift-giving
can occur and provide novel insight into the evolution of worthless
nuptial gifts, occurring in multiple taxonomic groups with implications
for understanding parental investment.

\hypertarget{lay-summary}{%
\section{Lay summary}\label{lay-summary}}

If you have ever bought a gift to impress a prospective partner, you are
not alone. Such behaviour is not unique to humans, but giving gifts
during courtship is common in many different animals, including some
species of insects, snails, birds, squid and spiders. In animals, such
gifts can be costly, but offering them may be worth it from an
evolutionary perspective if they increase the reproductive success of
the individual who provides them. While using gifts during courtship
(often called nuptial gifts) is widespread among animals, it is not
universal. Why have some groups of animals evolved to engage in nuptial
gift-giving while others have not? We explore this question by building
a mathematical model, using computer simulations, and using data from a
nuptial gift-giving species of spider to see how receiving nuptial gifts
might affect reproductive success. We find conditions under which
selection should favour males to provide nuptial gifts and females
should exhibit a preference for gifts. These conditions explain why some
species engage in nuptial gift-giving while others do not.
Interestingly, we find that these inequalities differ between males and
female, illustrating that the evolutionary interest of the two sexes do
not always overlap.

\hypertarget{teaser-text}{%
\section{Teaser text}\label{teaser-text}}

The results presented provide a general explanation of the evolution of
nuptial gift-giving which is a behaviour pattern that has evolved many
times independently in diverse parts of the animal kingdom. The
explanation is general but at the same time quantitatively precise, thus
giving a rigorous answer to the conundrum of why nuptial gift-giving
occurs in some groups of animals but not in others. Since research on
nuptial gift-giving has, and continues to, inspire an enormous amount of
work, the results presented here are highly relevant to an active field
of both theoretical and empirical research.

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Nuptial gift-giving occurs when the choosy sex (usually the female)
receives gifts from the opposite sex (usually the male) during
courtship. It is a widespread phenomenon, occurring within several
diverse taxonomic groups such as insects, snails, birds, squid,
arachnids and humans (\protect\hyperlink{ref-Lewis2012}{Lewis \& South,
2012}; \protect\hyperlink{ref-Albo2014}{Albo \emph{et al.}, 2014};
\protect\hyperlink{ref-Lewis2014}{Lewis \emph{et al.}, 2014}). Despite
the ubiquity of this behaviour, little effort has been made to
conceptualise the evolution of nuptial gift-giving within a general
modelling framework (\protect\hyperlink{ref-Lewis2014}{Lewis \emph{et
al.}, 2014}; \protect\hyperlink{ref-Iwasa2022}{Iwasa \& Yamaguchi,
2022}). Recent models describing the evolution of nuptial gift-giving
have focused on co-evolution between male nuptial gift-giving and female
propensity to remate, and the evolutionarily stable nuptial gift sizes
(\protect\hyperlink{ref-Kamimura2021}{Kamimura \emph{et al.}, 2021};
\protect\hyperlink{ref-Iwasa2022}{Iwasa \& Yamaguchi, 2022}), but a
general framework describing the conditions necessary for nuptial
gift-giving to be initially favoured by selection is needed to
understand when gift-giving should evolve.\\
Nuptial gift-giving may allow males to increase fitness by acquiring
additional mates, indirect benefits (by increasing the fitness of
offspring), prolonged copulations, and success in sperm competition
(\protect\hyperlink{ref-Albo2013}{Albo \emph{et al.}, 2013};
\protect\hyperlink{ref-Ghislandi2014}{Ghislandi \emph{et al.}, 2014};
\protect\hyperlink{ref-Lewis2014}{Lewis \emph{et al.}, 2014}). However,
this potential fitness increase comes at the expense of producing a
nuptial gift, which may be costly in terms of time and resources.
Females may increase their fitness by receiving nutritionally valuable
nuptial gifts, but expressing a preference for males with gifts might
result in a mating opportunity cost if available males without gifts are
rejected. With respect to nuptial gift-giving, the evolutionary
interests of both sexes may not always fully overlap. This can cause
sexual conflict, which is a difference in the evolutionary interest
between sexes that occurs when interaction between sexes results in a
situation where neither sex can achieve an optimal outcome
(\protect\hyperlink{ref-Parker2006}{Parker, 2006}) That is, under some
conditions, it might for example be optimal for females to receive
nuptial gifts, but not optimal for males to produce them.

Much work has sought to explain how gift-giving tactics are maintained,
with explanations including condition-dependent strategies, gift-giving
as a way to decrease female aggression during copulation, or gifts as
sensory traps (\protect\hyperlink{ref-Lubin2007}{Lubin \& Bilde, 2007};
\protect\hyperlink{ref-Toft2016}{Toft \& Albo, 2016};
\protect\hyperlink{ref-Ghislandi2018}{Ghislandi \emph{et al.}, 2018};
\protect\hyperlink{ref-Albo2019}{Albo \emph{et al.}, 2019}). An example
of such a system is the nuptial gift-giving nursery-web spider
\emph{Pisaura mirabilis} where males may court females with or without
nuptial gifts (\protect\hyperlink{ref-Bristowe1926}{Bristowe \& Locket,
1926}). Here, males may provide females with costly nuptial gifts in the
form of captured arthropod prey, and females may exhibit preference for
males with a nuptial gift by rejecting males without a nuptial gift
(\protect\hyperlink{ref-Albo2013}{Albo \emph{et al.}, 2013}).

We develop a general framework for investigating the evolution of
nuptial gift-giving and choosiness using a time-in, time-out modelling
approach and an individual-based model
(\protect\hyperlink{ref-Clutton-Brock1992}{Clutton-Brock \& Parker,
1992}). Specifically, we derive conditions under which selection will
favour male search for nuptial gifts and female rejection of gift-less
males. We show that selection for searching and choosiness depends on
whether a threshold fitness value of the nuptial gift is exceeded. Our
model demonstrates the importance of nuptial gift cost, sex ratio, and
mate encounter rate in determining the threshold above which selection
will favour the evolution of nuptial gift-giving. Importantly, we show
that the threshold value differs for males and females. We test
predictions of our analytical model by formulating an individual-based
model, which further supports the main theoretical results of our
analytical model. Further, we apply our model to an example system with
nuptial gifts, the nursery web spider \emph{Pisaura mirabilis}, where we
use experimental data to estimate a key model parameter. Our results
provide a general framework for understanding why nuptial gift-giving
evolves in some systems and not in others, how the evolution of nuptial
gift-giving can give rise to sexual conflict, and it provides insight
into the evolution of worthless and deceitful nuptial gifts, which occur
in several different taxonomic (\protect\hyperlink{ref-LeBas2005}{LeBas
\& Hockham, 2005}; \protect\hyperlink{ref-Ghislandi2014}{Ghislandi
\emph{et al.}, 2014}).

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{analytical-model}{%
\subsection{Analytical model}\label{analytical-model}}

We use a time-in and time-out model
(\protect\hyperlink{ref-Clutton-Brock1992}{Clutton-Brock \& Parker,
1992}; \protect\hyperlink{ref-Kokko2001}{Kokko \& Monaghan, 2001};
\protect\hyperlink{ref-Kokko2006}{Kokko \& Ots, 2006}) in which choosy
(female) and non-choosy (male) individuals spend some period of time
within the mating pool searching for a mate (time-in) followed by a
period outside the mating pool (time-out). During time-out, females
spend some duration of time (\(T_{\mathrm{f}}\)) gestating or rearing
(hereafter `processing') offspring. We define the number of offspring
produced by a female per reproductive cycle as \(\lambda\). Since
females enter time-out after mating, this assumption is equivalent to
assuming a system with sequential polyandry. For simplicity, we assume
male time to replenish sperm is negligible, but males can spend some
duration of time (\(T_{\mathrm{m}}\)) out of the mating pool searching
for nuptial gifts.

\begin{figure}
\includegraphics[width=1\linewidth]{inst/img/conceptual_figure} \caption{Conceptual figure inspired by Kokko and Ots (2006) illustrating how the modelling framework maps onto an example of a system wherein nuptial gifts are used, here \textit{Pisaura mirabilis}. Males have a probability of obtaining a nuptial gift while in time-out, which will affect their probability of mating while in time-in. They return to the mating pool (time-in) at a rate determined by the time spent searching for a nuptial gifts ($T_{m}$) and leave the mating pool (i.e. enter time-out) following the female encounter rate, which is dependent on ratio of males to females ($\beta$) and the encounter rate ($R$). The choosy sex (females) enter the mating pool at a rate depending in the time spent processing offspring ($T_{f}$) and leave the mating pool (i.e. enter time-out) at a rate that is dependent on $\beta$ and $R$. Males and females undergo sex-specific mortality $\mu$ during time-in and time-out. Image left to right: (1) male \textit{P. mirabilis}. (2) male \textit{P. mirabilis} presenting nuptial gift (white) to female. (3) Female \textit{P. mirabilis} protecting offspring. Photos: Alamy.}\label{fig:unnamed-chunk-2}
\end{figure}

\hypertarget{criteria-for-male-search-and-female-choosiness}{%
\subsection{Criteria for male search and female
choosiness}\label{criteria-for-male-search-and-female-choosiness}}

The probability \(G\) that a male succeeds in securing a nuptial gift is
defined by,

\begin{equation}
G = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.
\end{equation}

In Eq. 1, \(\alpha\) defines the expected search time before
encountering a nuptial gift. Thus, the probability of finding a nuptial
gift is higher the more time \(T_{\mathrm{m}}\) is spent searching.
During time-in, individuals encounter conspecifics at a rate of \(R\). A
focal individual will therefore encounter conspecifics of the opposite
sex at a rate of \(R/2\) if the ratio of males to females in the mating
pool \(\beta\) is equal. More generally, males will be encountered at a
rate of \(R\beta/(\beta+1)\), and females will be encountered at a rate
of \(R/(\beta+1)\). An example of how the structure of the time-in
time-out model applies to a system with nuptial gift-giving is given in
Figure 1. We assume that mating with a nuptial gift increases the
fitness of each offspring by an increment of \(\gamma\). We proceed to
find the thresholds \(\gamma_{\mathrm{m}}\) and \(\gamma_{\mathrm{f}}\)
above which males and females are favoured by selection to search for
nuptial gifts and exhibit choosiness for nuptial gifts, respectively. We
show (see Methods) that the initial threshold value of \(\gamma\)
(\(\gamma_{\mathrm{m}}\)) necessary for males to increase their fitness
by investing time searching for a nuptial gift (time that could
otherwise be spent searching for a mate) is,

\begin{equation}
\gamma_{\mathrm{m}} > \alpha \frac{R}{\beta + 1}.
\end{equation}

Inequality 2 means that if nuptial gifts are not abundant and thus
require a long time to find (i.e., high \(\alpha\)), or if males
encounter many females per unit time (i.e., high \(R / (1+\beta)\)),
then the nuptial gift must result in a high fitness increment for
selection to favour gift-searching. In general, when ineq. 2 is
satisfied, we predict selection to favour the evolution of nuptial
gift-giving.

We can similarly predict the conditions for which there is selection for
female choosiness. If \(\gamma\) is sufficiently high, then females
increase their fitness by rejecting males without gifts and mating only
with males that provide nuptial gifts. To illustrate, we assume that all
males in a population search for a duration of \(T_{\mathrm{m}}\), in
which case the threshold fitness increment for females
(\(\gamma_{\mathrm{f}}\)) is,

\begin{equation}
\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}} R \left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}} \right)}.
\end{equation}

Inequality 3 shows that as offspring processing time
(\(T_{\mathrm{f}}\)), mate encounter rate (\(R\beta / (\beta + 1)\)),
and the probability of a male finding a nuptial gift
(\(1 - \exp(-T_{\mathrm{m}}/\alpha)\) ) decreases, the threshold value
of fitness above which selection will favour choosiness
(\(\gamma_{\mathrm{f}}\)) increases. This can be understood intuitively
by realising that rejecting a prospective male represents an opportunity
cost for the female. This opportunity cost becomes small if many males
with gifts are encountered, hence the appearance of the rate at which
males with gifts are encountered in the denominator. Figure 2 shows how
\(\gamma_{\mathrm{m}}\) and \(\gamma_{\mathrm{f}}\) change with
increasing \(\alpha\). For \(\gamma_{\mathrm{f}}\), we assume that males
search for the expected time required to obtain a nuptial gift
(\(T_{\mathrm{m}} = \alpha\)). Note that \(\beta\) does not have a
closed form solution given \(R\), \(T_{\mathrm{f}}\), and
\(T_{\mathrm{m}}\), so \(\beta\) was calculated using recursion (see
Methods).

\begin{figure}
\centering
\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{Fitness thresholds above which males increase their fitness by
searching for nuptial gifts (blue line; Eq. 2) and females increase
their fitness by rejecting males that do not offer gifts (red line; Eq.
3). Parameter space includes areas in which males do not search for
nuptial gifts and females are not choosy (A), males search but females
are not choosy (B), females would be choosy but males do not search (C),
and males search and females are choosy (D). Arrows indicate the effect
of increasing interaction rate (\(R\)), female time-out (\(T_{f}\)), and
male search time (\(T_{m}\)). As an example, trajectories for
\(T_{f} = 2\), and \(T_{m} = \alpha\) are shown for values of \(R=2\)
(panel a) and \(R = 1\) (panel b). Females are assumed to be the choosy
sex, which is maintained as long as \(\alpha < T_{f}\).}
\end{figure}

The analytical framework predicts 4 zones, which are delineated by
inequalities 2 and 3 and describe the initial thresholds for favouring
search of nuptial gifts in males and choosiness for nuptial gifts in
females (Figure 2). Consequently, the modelling framework gives a
description of the conditions under which nuptial gift-giving is
expected to occur (Figure 2, Zone D) and the conditions under which only
selection for male searching (Figure 2, Zone B) or female choosiness
(Figure 2, Zone C) are predicted. These results therefore highlight the
potential for sexual conflict over nuptial gift-giving.

\hypertarget{evolution-of-male-search-and-female-choosiness}{%
\subsection{Evolution of male search and female
choosiness}\label{evolution-of-male-search-and-female-choosiness}}

We use an individual-based model (IBM) to simulate the evolution of
nuptial gift-giving and female choosiness from an ancestral condition in
which neither exists. The IBM was written to satisfy the assumptions of
our analytical time-in and time-out model as much as practical (see
Supporting Information S1). Using the IBM, we modelled a
spatially-implicit, finite population of females and males. At each time
step, some individuals enter or remain within the mating pool (time-in),
where they potentially interact and mate. After mating, males and
females may leave the mating pool to search for nuptial gifts and to
produce offspring, respectively (time-out). Mortality occurs with a
fixed probability in each time step, then a ceiling regulation is
applied to limit population growth (see Methods).

The rates at which males encounter females \(R_{\mathrm{m}}\) and
females encounter males with nuptial gifts \(R_{\mathrm{f,G}}\) are
calculated directly from the IBM, thereby modelling how these rates
might be estimated from empirical data, so the male threshold for
increasing fitness by searching is,

\begin{equation}
\gamma_{\mathrm{m, IBM}} > \alpha R_{\mathrm{m}}.
\end{equation}

Similarly, female threshold for increasing fitness by choosiness is,

\begin{equation}
\gamma_{\mathrm{f, IBM}} > \frac{1}{T_{\mathrm{f}}R_{\mathrm{f,G}}}.
\end{equation}

Consequently, the IBM and the analytical model differ slightly (e.g.,
time is discrete in the IBM but continuous the analytical model, and in
the IBM a fitness increment is applied to the focal female in the form
of birthrate increase rather than offspring; see Supporting Information
S1 for details). But the predicted thresholds are theoretically
equivalent and yield predictions that are qualitatively the same (Figure
3).

\begin{figure}
\centering
\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{The coevolution of male search and female choosiness as a
function of nuptial gift search time (\(\alpha\)). Points show where the
lower 95\% confidence interval of female choosiness (red) and male
search (blue) exceeds zero, indicating evolution of choosiness or
nuptial gift search. Each point includes data from 3200 replicate
simulations with identical starting conditions. Red and blue lines show
thresholds above which the mathematical model predicts that females
should be choosy and males should search, respectively (in agreement
with Figure 2). Minor deviations between the analytical model and the
simulation results are expected due to the finite population size and
the substantial stochasticity inherent to the simulation model (for
details, see Supporting Information S1). Approximately 3000 interactions
occur between individuals in each time step, potentially resulting in a
mating interaction. The number of individuals in the population remained
at or near carrying capacity of \(K = 1000\). Expected female processing
time was set to \(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and
\(\alpha\) values in the range {[}0.0, 2.0{]} and {[}0.1, 2.0{]},
respectively, were used.}
\end{figure}

Male thresholds \(\gamma_{\mathrm{m, IBM}}\) given by ineq. 4 accurately
predict the evolution of searching in the IBM across \(\alpha\) values,
and the female threshold \(\gamma_{\mathrm{f, IBM}}\) (ineq. 5)
accurately predicts the evolution of female choice (Figure 3). In other
words, IBM simulations demonstrate that nuptial gift search in males,
and choosiness in females, will evolve from an ancestral state of no
searching and no choosiness in similar parameter space (Figure 3) as
predicted by the analytical model (Figure 2). We further ran the IBM
with realistic values of \(\gamma\), estimated using data from the
\emph{P. mirabilis} system wherein choosiness among females, and nuptial
gift search among males, occur (Figure 4). We found that our IBM
predicts both the evolution of choosiness and nuptial gift searching
observed in the \emph{P. mirabilis} system.

\begin{figure}
\centering
\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{The joint evolution of male search and female choosiness using
a nuptial gift fitness increment (\(\gamma\)) that was estimated from
experimental data for the species \emph{P. mirabilis} (Tuni et al.~2013;
mean \(\gamma = 3.29 \pm\) SE via propagation of error for estimates of
nuptial feeding a non-nuptial feeding groups: {[}1.47; 8.32{]}). Points
show where the 95\% confidence interval exceeds 0 for female choosiness
(red) and male search (blue). Each point includes data from 100
replicate simulations with identical starting conditions. The red line
shows the threshold above which females should be choosy and the blue
line shows the threshold above which males should search. As predicted
by the analytical model, both male search and female choosiness evolved
for a range of \(\gamma\) values around the empirical estimates. This
occurs because these values result in a \(\gamma\) above the fitness
threshold necessary for selection to favour male search of nuptial gifts
(blue line) and female choosiness (red line). Approximately 3000
interactions occur between individuals in each time step, potentially
resulting in a mating interaction. The number of individuals in the
population remained at or near carrying capacity of \(K = 1000\). Female
processing time was set to \(T_{\mathrm{f}}=2\) time steps, and
\(\gamma\) and \(\alpha\) values in the {[}0.2, 2.0{]}, respectively,
were used. The parameter \(\gamma\) was estimated as relative increase
in offspring production such that \(\gamma\) is the factor by which
fitness increases (relative to the baseline fitness) given a nuptial
gift (See Supporting Information S5).}
\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

Nuptial gift-giving has arisen several times independently throughout
the animal kingdom (\protect\hyperlink{ref-Lewis2012}{Lewis \& South,
2012}), so understanding how selection favours nuptial gift giving and
choosiness is important for a broad range of mating systems. We provide
a general framework that defines the necessary conditions for selection
to favour the evolution of nuptial gift-giving. We show that males
should give nuptial gifts if the value of a nuptial gift exceeds a
threshold dependent on the encounter rate between males and females and
the cost or time necessary to find or produce a nuptial gift (see ineq.
2). This result makes intuitive sense because if males rarely encounter
females, time searching for a gift is a minor cost relative to mate
search time. If males encounter many females, it is not worth seeking
nuptial gifts unless gifts are very valuable since the male will meet
many prospective mates, and nuptial gift search time might come at a
cost of decreased mating opportunities. In practice, male biased sex
ratios will not necessarily favour male search for nuptial gifts if the
female encounter rate is very high, so the key variable is how often
males and females encounter each other. If the search time or cost of
finding a nuptial gift is high, nuptial gifts must be very valuable
before search is favoured by selection.

\hypertarget{threshold-fitness-values}{%
\subsection{Threshold fitness values}\label{threshold-fitness-values}}

Importantly, we show that the threshold nuptial gift value at which
females are favoured to express choosiness for nuptial gifts is rarely
equivalent to the threshold value at which males are favoured to search
for nuptial gifts, potentially leading to sexual conflict
(\protect\hyperlink{ref-Arnqvist2005a}{Arnqvist \& Rowe, 2005};
\protect\hyperlink{ref-Oliveira2008}{Oliveira \emph{et al.}, 2008}).
Here, we are defining sexual conflict as occurring when interactions
between sexes result in situation where both sexes cannot achieve an
optimal outcome simultaneously
(\protect\hyperlink{ref-Parker2006}{Parker, 2006}). As an example,
sizable areas of parameter space exists wherein the female optimum would
be to exhibit preference for (and receive) nuptial gifts, while the male
optimum is to not search for (and give) nuptial gifts (see Figure 2,
Zone C). In many systems, ecological variables such as search time
required to find a nuptial gift will likely depend on prey abundance,
which can vary substantially with time in some species with nuptial
gift-giving (\protect\hyperlink{ref-Ghislandi2018}{Ghislandi \emph{et
al.}, 2018}). Since several ecological variables likely affect the value
of these thresholds, our results can be seen as providing some
formalised description of why nuptial gift-giving only occurs in some
but not all systems.

At first, the analytical model seems to suggests that nuptial gifts must
cause a very high fitness increase (approximately 25\%) before male
search and female choosiness is favoured by selection (Figure 2).
Similarly the IBM model seems to suggest that a fitness benefit of
approximately 50\% is required (see Figure 3). However, it is important
to point out that these thresholds depend on multiple parameters. For
example, if female processing time (\(T_{\mathrm{f}}\)) is high, the
female threshold for choosiness with respect to \(\gamma\) drops such
that male search and female choosiness are favoured at lower \(\gamma\)
(see Supporting formation S1). If \(T_{f}\) is sufficiently high, then
an initially rare gift-giving trait might therefore be favoured by
selection even if the fitness benefit of a nuptial gift is low. The
effect that nuptial gifts have on fitness might vary across systems, or
even populations. Effects on female fecundity have been estimated in
crickets, fireflies, butterflies, and spiders, but these estimates vary
considerably between species suggesting a large positive effect to no
effect at all (\protect\hyperlink{ref-Bergstrom2002}{Bergström \&
Wiklund, 2002}; \protect\hyperlink{ref-Rooney2002}{Rooney \& Lewis,
2002}; \protect\hyperlink{ref-Maxwell2018}{Maxwell \& Prokop, 2018};
\protect\hyperlink{ref-Gao2019}{Gao \emph{et al.}, 2019}).

When modelling nuptial gift evolution, the challenge is to construct a
modelling framework that captures the frequency-dependent selection
between male nuptial gift-giving and female preference for nuptial
gifts, and we do this using a time-in, time-out model. Recent studies
have modelled some frequency-dependent aspect of nuptial gift giving
using evolutionary game theory
(\protect\hyperlink{ref-MaynardSmith1982}{Maynard Smith, 1982};
\protect\hyperlink{ref-Vincent2005}{Vincent \& Brown, 2005}). Two such
studies formulated a quantitative genetics model to study evolutionarily
stable nuptial gift sizes in populations where the female propensity to
remate was evolving (\protect\hyperlink{ref-Kamimura2021}{Kamimura
\emph{et al.}, 2021}; \protect\hyperlink{ref-Iwasa2022}{Iwasa \&
Yamaguchi, 2022}). The results obtained in these studies complement our
results by giving equilibrium solutions to the evolutionary stable
nuptial gift size, whereas we determine the general conditions under
which nuptial gift-giving will evolve as given by the inequalities we
derive.

Other modelling frameworks have made general predictions about sexually
selected traits, and these predictions are not mutually exclusive to
those made by our model. For example, the good genes hypothesis predicts
that costly traits such as nuptial gift-giving can be favoured since
males enduring the cost of a nuptial gift signals to females that their
genes confer high fitness precisely because they can afford this cost
(\protect\hyperlink{ref-Kirkpatrick1996}{Kirkpatrick, 1996};
\protect\hyperlink{ref-Byers2006}{Byers \& Waits, 2006}; but see
\protect\hyperlink{ref-Fromhage2022}{Fromhage \& Henshaw, 2022}). In
other words, costly sexually selected traits are favoured because they
are indicators of overall genetic quality
(\protect\hyperlink{ref-Martinossi-Allibert2019}{Martinossi-Allibert
\emph{et al.}, 2019}). Because of this, nuptial gift-giving could be a
case of condition-dependence where engaging in nuptial gift-giving is
only favourable for male in good condition (e.g., males capable of
successful search (\protect\hyperlink{ref-MaynardSmith1982}{Maynard
Smith, 1982}; \protect\hyperlink{ref-Engqvist2015}{Engqvist \& Taborsky,
2015}; \protect\hyperlink{ref-Ghislandi2018}{Ghislandi \emph{et al.},
2018})). In general, our model demonstrates how nuptial gift-giving
initially evolves before other mechanisms, such as good gene effects,
become relevant.

A nuptial gift can also constitute a dishonest signal of good body
condition since worthless, deceptive nuptial gifts have evolved in
several systems (\protect\hyperlink{ref-LeBas2005}{LeBas \& Hockham,
2005}; \protect\hyperlink{ref-Ghislandi2014}{Ghislandi \emph{et al.},
2014}). This is also the case in \emph{P. mirabilis} where males will
wrap plant parts or an empty exoskeleton in silk, as opposed to an
arthropod prey, and use this as a nuptial gift
(\protect\hyperlink{ref-Albo2011}{Albo \emph{et al.}, 2011};
\protect\hyperlink{ref-Ghislandi2014}{Ghislandi \emph{et al.}, 2014}).
In such systems, worthless nuptial gifts have been shown to reduce the
likelihood that a male is rejected by a female compared to the case
where no nuptial gift is given. However, males offering worthless
nuptial gifts may be at a slight disadvantage in sperm competition since
worthless gifts result in a shorter copulation duration and hence less
sperm transfer (\protect\hyperlink{ref-Albo2013}{Albo \emph{et al.},
2013}; \protect\hyperlink{ref-Ghislandi2014}{Ghislandi \emph{et al.},
2014}). Worthless gifts should not result in any paternal care benefits
to the male since the offspring he may sire will not gain nutrition from
a worthless nuptial gift.

Given our modelling framework, worthless nuptial gifts may be expected
to evolve in cases where females are discriminating in favour of nuptial
gifts, but the cost of search time for a true nuptial gift is very high
such that selection will not favour male search. This scenario would
correspond to zone C of Figure 2 where the value of the nuptial gift
exceeds the female fitness threshold for choosiness to be favoured, but
due to high search time, selection will not favour male search for true
nuptial gifts. Our model also predicts the possibility of the opposite
scenario, in which males provide nuptial gifts, but females do not
exhibit preference for nuptial gifts (zone B of Figure 2).
Fascinatingly, an example of such system has been documented by a recent
study of the genus \emph{Trechaleoides}, which contains two species with
true nuptial gift-giving, but a lack of preference for nuptial gifts
among female (\protect\hyperlink{ref-Martinez2023}{Martínez Villar
\emph{et al.}, 2023}).

The main drivers of male nuptial gift-giving are thought to be indirect
fitness benefits and increased success in sperm competition, since
providing a nuptial gift can result in longer copulation duration which
is correlated with increased sperm transfer along with female cryptic
choice promoting males who provide nuptial gifts
(\protect\hyperlink{ref-Albo2011}{Albo \emph{et al.}, 2011},
\protect\hyperlink{ref-Albo2013}{2013}). However, nuptial gifts might
also function to modulate female aggression and prevent sexual
cannibalism (\protect\hyperlink{ref-Bilde2006}{Bilde \emph{et al.},
2006}). In some systems, such as \emph{P. mirabilis}, males have been
shown to reduce the risk of being cannibalised by the female after
mating when offering a nuptial gift, such that the nuptial gift may
result in a ``shield effect'', protecting the male
(\protect\hyperlink{ref-Toft2016}{Toft \& Albo, 2016}).

The simulations parameterised with an experimentally estimated value of
\(\gamma\) showed evolution of nuptial gift searching in males and
choosiness for nuptial gifts in females. The model thus predicts that
\emph{P. mirabilis} living under conditions with the estimated fitness
value of nuptial gifts should exhibit both search for nuptial gifts and
choosiness for males with nuptial gifts, and this is what is observed in
empirical populations. Parameterising \(\gamma\) with data from
experimental studies may only yield a rough approximation of the true
\(\gamma\). This is because the estimated value of \(\gamma\) is based
on data from current populations (rather than ancestral populations,
which are being simulated), and because the literature is inconclusive
as to how much (if any) effect nuptial gifts have on female fitness
(\protect\hyperlink{ref-Maxwell2018}{Maxwell \& Prokop, 2018}). The
effect of nuptial gifts on female fecundity has been estimated in a
variety of system such as crickets, fireflies, butterflies and spiders,
but these estimates vary considerably between species suggesting a large
positive effect to no effect at all
(\protect\hyperlink{ref-Bergstrom2002}{Bergström \& Wiklund, 2002};
\protect\hyperlink{ref-Rooney2002}{Rooney \& Lewis, 2002};
\protect\hyperlink{ref-Maxwell2018}{Maxwell \& Prokop, 2018};
\protect\hyperlink{ref-Gao2019}{Gao \emph{et al.}, 2019}).

Our model assumes something akin to sequential polyandry. That is, a
system wherein female mating and reproduction with multiple males occurs
in sequence, rather than multiple matings occurring before reproduction.
In some systems with nuptial gift-giving, females have been documented
to mate multiple times before reproduction occurs, including the genus
of bark lice \emph{Neotrogla}
(\protect\hyperlink{ref-Kamimura2021}{Kamimura \emph{et al.}, 2021}),
and even our example system of \emph{P. mirabilis} where females will
sometimes engage in multiple mating before reproducing, especially if
starved because multiple mating may result in more nuptial gifts
(\protect\hyperlink{ref-Toft2015}{Toft \& Albo, 2015};
\protect\hyperlink{ref-Matzke2022}{Matzke \emph{et al.}, 2022}). It is
unclear what effect (if any) assuming non-sequential polyandry would
have on the threshold we derive. Under non-sequential polyandry, a
viable strategy for females might be to accept any male (with or without
gift) for fertilisation assurance, then exhibit a preference for nuptial
gifts. This might make choosiness less costly since it would entail less
of an opportunity cost to be choosy, and this could potentially make
female preference for nuptial gifts more likely to evolve. Our model
also assumes that males search in time out, rather than contribute to
parental care, which is likely to be accurate for most systems but not
all. Expanding the model to explore these possibilities would be a
worthwhile goal for future research.

Overall, we found that a simple relationship between nuptial gift search
time and mate encounter rate yields a threshold that determines whether
selection will favour males that search for nuptial gifts. Similarly, we
found that the threshold determining whether females will be favoured to
reject males without nuptial gifts is also dependent on these variables,
along with offspring processing time. Together, these thresholds
describe the conditions under which nuptial gift-giving is expected to
evolve. The applications of these thresholds are numerous. They can be
used as a starting point for more complex or more system-specific models
of nuptial gift-giving evolution. They can also provide novel insight
into how populations can evolve to use worthless or token nuptial gifts.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{model}{%
\subsection{Model}\label{model}}

Here we first present more detail for the derivation of fitness
threshold values \(\gamma_{\mathrm{m}}\) and \(\gamma_{\mathrm{f}}\). We
then present full details for IBM simulations (see Supporting
Information S1). Code for simulations is available on GitHub (see ``Data
availability'').

\hypertarget{derivation-of-fitness-thresholds}{%
\subsection{Derivation of fitness
thresholds}\label{derivation-of-fitness-thresholds}}

We use a time-in and time-out model in which females and males spend
some time searching for a mate (time-in) followed by a period of cool
down outside the mating pool (time-out; Figure 1).

After mating, females must spend some time processing offspring
(\(T_{\mathrm{f}}\)). Male time to replenish sperm is assumed to be
negligible, but males can spend time out of the mating pool to search
for a nuptial gift (\(T_{\mathrm{m}}\)). When males return from
time-out, they encounter females with some probability that is a
function of the rate at which an individual encounters conspecifics
(\(R\)) and the sex ratio (\(\beta\); males/females). Mortality occurs
for females and males in (\(\mu_{\mathrm{i,f}}\),
\(\mu_{\mathrm{i,m}}\)) and out (\(\mu_{\mathrm{o,f}}\),
\(\mu_{\mathrm{o,m}}\)) of the mating pool. Following Kokko \& Ots
(\protect\hyperlink{ref-Kokko2006}{2006}), we assume
\(m_{\mathrm{i,f}} = m_{\mathrm{o,f}} = 1\) and
\(m_{\mathrm{i,m}} = m_{\mathrm{o,m}} = 1\). While this choice is
arbitrary, we conducted a sensitivity analysis which shows that the
mortality parameters have no influence on the propensity for male search
and female choice to evolve (Supporting Information S2). First, we
describe the fitness consequences of male search time for a nuptial
gift. We then describe the fitness consequences of female choice to
accept or reject males based on their provision of a nuptial gift.

\hypertarget{male-fitness}{%
\subsection{Male fitness}\label{male-fitness}}

During time-out, males have the opportunity to search for a nuptial
gift. Males can adopt one of two strategies; either search or do not
search for a nuptial gift. Males with the former strategy continue to
search until they find a nuptial gift, while males that do not search
will immediately re-enter the mating pool. In this case, time searching
for a nuptial gift will come at the cost of mating opportunities but
might increase offspring fitness offspring. We therefore need to model
the expected length of time \(E[T_{\mathrm{m}}]\) spent outside of the
mating pool for males that search for nuptial gifts, which is simply
\(\alpha\). Note that we can integrate search time \(t\) over the rate
at which nuptial gifts are encountered (\(\exp(-1/\alpha)\)) to show
\(E[T_{\mathrm{m}}] = \alpha\),

\[E[T_{\mathrm{m}}] = \int_{0}^{\infty}e^{- \frac{1}{\alpha}t}dt = \alpha.\]

The rate at which a focal male that searches for a nuptial gift
increases his fitness is therefore the fitness of his offspring
\((1 + \gamma)\) divided by expected time spent searching for a nuptial
gift (\(\alpha\)) plus time spent in the mating pool, \((\beta + 1)/R\)
(recall that females produce \(\lambda\) offspring),

\[W_{m,G} = \lambda \frac{1 + \gamma}{\alpha + \left( \frac{\beta + 1}{R} \right)}.\]

In contrast, a male that does not search for a nuptial gift has
offspring with lower fitness, but spends less time outside of the mating
pool,

\[W_{m,L} = \lambda \frac{1}{\left(\frac{\beta+1}{R} \right)} = \lambda \frac{R}{\beta + 1}.\]

We can then determine the conditions for which
\(W_{\mathrm{m},G} > W_{\mathrm{m},L}\), isolating \(\gamma\) to find
how large of a fitness benefit must be provided by the nuptial gift to
make the search cost worthwhile, which simplifies to ineq. 2. When this
inequality holds, males are favoured to search until they find a nuptial
gift, which would result in an average search time of \(\alpha\). When
the male trait is continuous (i.e., males search for time period
\(T_{\mathrm{m}}\)), it can be shown that the same threshold can be
reached by evaluating the partial derivative of the male fitness
function (Supporting Information S3). Hence, the thresholds are
consistent under different assumptions concerning male searching
strategy. Selection will cause males to search for nuptial gifts if the
fitness increase to offspring exceeds the product of search time and
female encounter rate.

\hypertarget{female-fitness}{%
\subsection{Female fitness}\label{female-fitness}}

During time-out, females process offspring over a duration of
\(T_{\mathrm{f}}\) (we assume that \(T_{\mathrm{f}} > \alpha\), else
females are not the choosy sex). When females re-enter the mating pool,
they encounter males at a rate of \(R\beta/(\beta + 1)\). If a female
encounters a male with a nuptial gift, we assume that she will mate with
him. But if a female encounters a male with no nuptial gift, then she
might accept or reject the male. If she rejects the male, then she will
remain in the mating pool. The rate at which a female encounters a male
with a nuptial gift is,

\[R_{f,G} = R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right).\]

We can similarly model the rate at which a female encounters a gift-less
male,

\[R_{f,L} = R \left(\frac{\beta}{\beta + 1}\right)\left(e^{-\frac{1}{\alpha}T_{m}}\right).\]

Note that we can recover the rate at which a female encounters any male,

\[R \left(\frac{\beta}{\beta + 1}\right) = R \left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + R \left(\frac{\beta}{\beta + 1}\right) \left(e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right).\]

If \(R_{\mathrm{f},G}\) is sufficiently high and \(R_{\mathrm{f},L}\) is
sufficiently low, then finding a male with a gift will be easier than
finding a male without one. Also, the expected time spent in the mating
pool before a focal female encounters a male with a gift will be
\(1/R_{\mathrm{f},G}\), while the expected time spent in the mating pool
before a focal female encounters any male will be
\(1 / (R_{\mathrm{f},G} + R_{\mathrm{f},L})\). Finally, the rates at
which a female encounters males with and without a gift,
\(R_{\mathrm{f},G}\) and \(R_{\mathrm{f}, L}\), are different from the
probabilities that a male encounter has or does not have a gift. The
rate of encounter is no longer relevant in this case because we are
assuming that an encounter has occurred. Hence, the probability of an
encountered male having a gift is simply,

\[G = \frac{1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}} = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]

Similarly, the probability of an encountered male not having a gift is
simply,

\[L = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]

The rate at which a female increases her fitness by being choosy and
mating only when she encounters a male with a gift is,

\begin{equation}
W_{\mathrm{f}, G} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}} + \frac{1}{R_{\mathrm{f},G}}}.
\end{equation}

The top of the right-hand side of Eq. 6 gives the fitness increase, and
the bottom gives the total time it takes to obtain this fitness. The
\(R_{\mathrm{f},G}\) is inverted because it represents the expected time
to encountering a male with a gift. We can expand Eq. 6,

\[W_{\mathrm{f},G} = \lambda \frac{1 + \gamma}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right)}}.\]

If the focal female is not choosy and accepts the first male that she
encounters, then the rate at which she increases her fitness is,

\[W_{\mathrm{f},l} = \lambda \frac{\left(1 + \gamma\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right) + e^{-\frac{1}{\alpha}T_{m}}}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)}}.\]

We then evaluate the conditions under which
\(W_{\mathrm{f}, G} > W_{\mathrm{f}, L}\). We isolate \(\gamma\) to
determine how much offspring fitness must be increase to make choosiness
beneficial (\(\gamma_{\mathrm{f}}\)),

\[\gamma_{\mathrm{f}} > \frac{1 + \frac{1}{\beta}}{D T_{f} \left(1 - e^{-1\frac{1}{\alpha}T_{m}}\right)}.\]

The above can be expressed as Eq. 7 below,

\begin{equation}
\gamma_{\mathrm{f}} > \frac{1}{ T_{f} R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right)}.
\end{equation}

Note that that the expression
\(R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right)\)
defines the rate at which a female in the mating pool encounters males
with nuptial gifts. Hence, female choosiness is ultimately determined by
time spent out of the mating pool to process offspring
(\(T_{\mathrm{f}}\)) and the rate at which a female in the mating pool
encounters males with nuptial gifts.

\hypertarget{operational-sex-ratio}{%
\subsection{Operational sex ratio}\label{operational-sex-ratio}}

We assume that the sex ratio is equal upon maturation. Given this, Kokko
and Monaghan (\protect\hyperlink{ref-Kokko2001}{Kokko \& Monaghan,
2001}) show that the operational sex ratio depends on the probability of
finding an individual in `time in',

\begin{equation}
\beta = \frac{\int_{t = 0}^{\infty} P_{IM}(t)dt}{\int_{t = 0}^{\infty} P_{IF}(t)dt}.
\end{equation}

In Eq. 8, \(P_{IM}(t)\) and \(P_{IF}(t)\) are the probabilities of
finding a male and female in `time in', respectively. There is no closed
form solution to the operational sex ratio, so we used recursion to
calculate \(\beta\) values for a given \(T_{\mathrm{f}}\),
\(T_{\mathrm{m}}\), and \(R\) (see Supporting Information S4),

\hypertarget{individual-based-model}{%
\subsection{Individual-based model}\label{individual-based-model}}

We formulate an individual-based simulation model to test whether the
predictions made by the analytical time-in time-out model are
qualitatively the same under a similar simulation model. We use the
individual-based model to test whether the prediction hold in finite
populations (see Supporting Information S6). The IBM was written in C.
All details of the initialisation, parameterisation and the specific
simulations which we run, are described in the supporting information
(see Supporting Information S1).

We use available experimental data on the effect of nuptial gifts on
female offspring production to estimate the key parameter \(\gamma\)
(fitness increment from nuptial gift) and conducted a series of
simulations where \(\gamma\) was parameterised using this estimated
value. Details of the estimation of \(\gamma\) are described in the
supporting information (see Supporting Information S5).

\textbf{Author contributions:} APC and ABD conceived the study. ABD
constructed the modelling framework with input from APC. APC wrote the
paper with input from ABD and ABD wrote the IBM model. TB and GB
provided substantial comments on previous drafts and final text.

\textbf{Acknowledgements:} Anders P. Charmouh was supported by the
University of Aberdeen. A. Bradley Duthie was supported by the
University of Stirling. Trine Bilde was supported by The Danish Council
for Independent Research grant number 4002-00328B. We thank Maria Albo
for making available data from a previous study which was useful for
parameter estimating.

\textbf{Data availability:} The simulation software was implemented in C
and the full source code is available at
\url{https://github.com/bradduthie/Pisaura}.

\textbf{Competing interests:} The authors declare no competing
interests.

\textbf{References}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Albo2013}{}}%
Albo, M.J., Bilde, T. \& Uhl, G. (2013)
\href{https://doi.org/10.1098/rspb.2013.1735}{{Sperm storage mediated by
cryptic female choice for nuptial gifts}}. \emph{Proceedings of the
Royal Society B: Biological Sciences}, \textbf{280}.

\leavevmode\vadjust pre{\hypertarget{ref-Albo2019}{}}%
Albo, M.J., Franco-Trecu, V., Wojciechowski, F.J., Toft, S. \& Bilde, T.
(2019) \href{https://doi.org/10.1093/beheco/arz040}{{Maintenance of
deceptive gifts in a natural spider population: Ecological and
demographic factors}}. \emph{Behavioral Ecology}, \textbf{30},
993--1000.

\leavevmode\vadjust pre{\hypertarget{ref-Albo2014}{}}%
Albo, M.J., Toft, S. \& Bilde, T. (2014) {Sexual selection, ecology, and
evolution of nuptial gifts in spiders}. In \emph{Sexual selection:
Perspectives and models from the neotropics} (ed. by Macedo, R.H. \&
Machado, G.). Academic Press, London, pp. 183--200.

\leavevmode\vadjust pre{\hypertarget{ref-Albo2011}{}}%
Albo, M.J., Winther, G., Tuni, C., Toft, S. \& Bilde, T. (2011)
\href{https://doi.org/10.1186/1471-2148-11-329}{{Worthless donations:
Male deception and female counter play in a nuptial gift-giving
spider}}. \emph{BMC Evolutionary Biology}, \textbf{11}.

\leavevmode\vadjust pre{\hypertarget{ref-Arnqvist2005a}{}}%
Arnqvist, G. \& Rowe, L. (2005) \emph{{Sexual Conflict}}. Princeton
University Press, Princeton, New Jersey.

\leavevmode\vadjust pre{\hypertarget{ref-Bergstrom2002}{}}%
Bergström, J. \& Wiklund, C. (2002) Effects of size and nuptial gifts on
butterfly reproduction: Can females compensate for a smaller size
through male-derived nutrients? \emph{Behavioral Ecology and
Sociobiology}, \textbf{52}, 296--302.

\leavevmode\vadjust pre{\hypertarget{ref-Bilde2006}{}}%
Bilde, T., Tuni, C., Elsayed, R., Pekár, S. \& Toft, S. (2006)
\href{https://doi.org/10.1098/rsbl.2005.0392}{{Death feigning in the
face of sexual cannibalism}}. \emph{Biology Letters}, \textbf{2},
23--25.

\leavevmode\vadjust pre{\hypertarget{ref-Bristowe1926}{}}%
Bristowe, W. \& Locket, G.H. (1926) {The courtship of British lycosid
spiders, and its probable significance}. \emph{Proceedings of the
Zoological Society of London}, \textbf{96}, 317--347.

\leavevmode\vadjust pre{\hypertarget{ref-Byers2006}{}}%
Byers, J.A. \& Waits, L. (2006)
\href{https://doi.org/10.1073/pnas.0608184103}{{Good genes sexual
selection in nature}}. \emph{Proceedings of the National Academy of
Sciences}, \textbf{103}, 16343--16345.

\leavevmode\vadjust pre{\hypertarget{ref-Clutton-Brock1992}{}}%
Clutton-Brock, T.H. \& Parker, G.A. (1992)
\href{https://doi.org/10.1086/417793}{{Potential reproductive rates and
the operation of sexual selection}}. \emph{Quarterly Review of Biology},
\textbf{67}, 437--456.

\leavevmode\vadjust pre{\hypertarget{ref-Engqvist2015}{}}%
Engqvist, L. \& Taborsky, M. (2015)
\href{https://doi.org/10.1098/rspb.2015.2945}{{The evolution of genetic
and conditional alternative reproductive tactics}}. \emph{Proceedings of
the Royal Society B: Biological Sciences}, \textbf{283}.

\leavevmode\vadjust pre{\hypertarget{ref-Fromhage2022}{}}%
Fromhage, L. \& Henshaw, J.M. (2022) The balance model of honest sexual
signaling. \emph{Evolution}, \textbf{76}, 445--454.

\leavevmode\vadjust pre{\hypertarget{ref-Gao2019}{}}%
Gao, Q., Turnell, B.R., Hua, B. \& Shaw, K.L. (2019) The effect of
nuptial gift number on fertilization success in a hawaiian swordtail
cricket. \emph{Behavioral Ecology and Sociobiology}, \textbf{73}, 1--9.

\leavevmode\vadjust pre{\hypertarget{ref-Ghislandi2014}{}}%
Ghislandi, P.G., Albo, M.J., Tuni, C. \& Bilden, T. (2014)
\href{https://www.ptonline.com/articles/how-to-get-better-mfi-results}{{Evolution
of deceit by worthless donations in a nuptial gift-giving spider}}.
\emph{Current Zoology}, \textbf{60}, 43--51.

\leavevmode\vadjust pre{\hypertarget{ref-Ghislandi2018}{}}%
Ghislandi, P.G., Pekár, S., Matzke, M., Schulte-Döinghaus, S., Bilde, T.
\& Tuni, C. (2018) \href{https://doi.org/10.1111/jeb.13284}{{Resource
availability, mating opportunity and sexual selection intensity
influence the expression of male alternative reproductive tactics}}.
\emph{Journal of Evolutionary Biology}, \textbf{31}, 1035--1046.

\leavevmode\vadjust pre{\hypertarget{ref-Iwasa2022}{}}%
Iwasa, Y. \& Yamaguchi, S. (2022)
\href{https://doi.org/10.1016/j.jtbi.2021.110939}{{Evolution of male
nuptial gift and female remating: A quantitative genetic model}}.
\emph{Journal of Theoretical Biology}, \textbf{533}, 110939.

\leavevmode\vadjust pre{\hypertarget{ref-Kamimura2021}{}}%
Kamimura, Y., Yoshizawa, K., Lienhard, C., Ferreira, R.L. \& Abe, J.
(2021) \href{https://doi.org/10.1186/s12862-021-01901-x}{{Evolution of
nuptial gifts and its coevolutionary dynamics with male-like persistence
traits of females for multiple mating}}. \emph{BMC Ecology and
Evolution}, \textbf{21}, 1--14.

\leavevmode\vadjust pre{\hypertarget{ref-Kirkpatrick1996}{}}%
Kirkpatrick, M. (1996) Good genes and direct selection in the evolution
of mating preferences. \emph{Evolution}, \textbf{50}, 2125--2140.

\leavevmode\vadjust pre{\hypertarget{ref-Kokko2001}{}}%
Kokko, H. \& Monaghan, P. (2001)
\href{https://doi.org/10.1046/j.1461-0248.2001.00212.x}{{Predicting the
direction of sexual selection}}. \emph{Ecology Letters}, \textbf{4},
159--165.

\leavevmode\vadjust pre{\hypertarget{ref-Kokko2006}{}}%
Kokko, H. \& Ots, I. (2006) {When not to avoid inbreeding}.
\emph{Evolution}, \textbf{60}, 467--475.

\leavevmode\vadjust pre{\hypertarget{ref-LeBas2005}{}}%
LeBas, N.R. \& Hockham, L.R. (2005) \href{https://doi.org/10.1016/j}{{An
invasion of cheats: the evolution of worthless nuptial gifts}}.
\emph{Current Biology}, \textbf{15}, 64--67.

\leavevmode\vadjust pre{\hypertarget{ref-Lewis2014}{}}%
Lewis, S.M., Vahed, K., Koene, J.M., Engqvist, L., Bussière, L.F.,
Perry, J.C., \emph{et al.} (2014)
\href{https://doi.org/10.1098/rsbl.2014.0336}{{Emerging issues in the
evolution of animal nuptial gifts}}. \emph{Biology Letters},
\textbf{10}, 3--5.

\leavevmode\vadjust pre{\hypertarget{ref-Lewis2012}{}}%
Lewis, S. \& South, A. (2012)
\emph{\href{https://doi.org/10.1016/B978-0-12-394288-3.00002-2}{{The
Evolution of Animal Nuptial Gifts}}}.

\leavevmode\vadjust pre{\hypertarget{ref-Lubin2007}{}}%
Lubin, Y. \& Bilde, T. (2007)
\href{https://doi.org/10.1016/S0065-3454(07)37003-4}{{The evolution of
sociality in spiders}}. \emph{Advances in the Study of Behavior},
\textbf{37}, 83--145.

\leavevmode\vadjust pre{\hypertarget{ref-Martinez2023}{}}%
Martínez Villar, M., Germil, M., Pavón-Peláez, C., Tomasco, I., Bilde,
T., Toft, S., \emph{et al.} (2023) Lack of female preference for nuptial
gifts may have led to loss of the male sexual trait. \emph{Evolutionary
Biology}, \textbf{50}, 318--331.

\leavevmode\vadjust pre{\hypertarget{ref-Martinossi-Allibert2019}{}}%
Martinossi-Allibert, I., Rueffler, C., Arnqvist, G. \& Berger, D. (2019)
\href{https://doi.org/10.1098/rspb.2018.2313}{The efficacy of good genes
sexual selection under environmental change}. \emph{Proceedings of the
Royal Society B: Biological Sciences}, \textbf{286}.

\leavevmode\vadjust pre{\hypertarget{ref-Matzke2022}{}}%
Matzke, M., Toft, S., Bechsgaard, J., Pold Vilstrup, A., Uhl, G.,
Künzel, S., \emph{et al.} (2022) Sperm competition intensity affects
sperm precedence patterns in a polyandrous gift-giving spider.
\emph{Molecular Ecology}, \textbf{31}, 2435--2452.

\leavevmode\vadjust pre{\hypertarget{ref-Maxwell2018}{}}%
Maxwell, M.R. \& Prokop, P. (2018) Fitness effects of nuptial gifts in
the spider \emph{pisaura mirabilis}: Examination under an alternative
feeding regime. \emph{The Journal of Arachnology}, \textbf{46},
404--412.

\leavevmode\vadjust pre{\hypertarget{ref-MaynardSmith1982}{}}%
Maynard Smith, J. (1982)
\emph{\href{https://www.ncbi.nlm.nih.gov/pubmed/13761767}{{Evolution and
the theory of games}}}. Cambridge University Press, Cambridge.

\leavevmode\vadjust pre{\hypertarget{ref-Oliveira2008}{}}%
Oliveira, R.F., Taborsky, M. \& Brockmann, H.J. (Eds.). (2008)
\emph{{Alternative reproductive tactics: an integrative approach}}.
Cambridge University Press, Cambridge.

\leavevmode\vadjust pre{\hypertarget{ref-Parker2006}{}}%
Parker, G.A. (2006) \href{https://doi.org/10.1098/rstb.2005.1785}{Sexual
conflict over mating and fertilization: An overview}.
\emph{Philosophical Transactions of the Royal Society B}, \textbf{361},
235--259.

\leavevmode\vadjust pre{\hypertarget{ref-Rooney2002}{}}%
Rooney, J. \& Lewis, S.M. (2002) Fitness advantage from nuptial gifts in
female fireflies. \emph{Ecological Entomology}, \textbf{27}, 373--377.

\leavevmode\vadjust pre{\hypertarget{ref-Toft2015}{}}%
Toft, S. \& Albo, M.J. (2015) Optimal numbers of matings: The
conditional balance between benefits and costs of mating for females of
a nuptial gift-giving spider. \emph{Journal of Evolutionary Biology},
\textbf{28}, 457--467.

\leavevmode\vadjust pre{\hypertarget{ref-Toft2016}{}}%
Toft, S. \& Albo, M.J. (2016)
\href{https://doi.org/10.1098/rsbl.2015.1082}{{The shield effect:
Nuptial gifts protect males against pre-copulatory sexual cannibalism}}.
\emph{Biology Letters}, \textbf{12}.

\leavevmode\vadjust pre{\hypertarget{ref-Tuni2013a}{}}%
Tuni, C., Albo, M.J. \& Bilde, T. (2013)
\href{https://doi.org/10.1111/jeb.12137}{{Polyandrous females acquire
indirect benefits in a nuptial feeding species}}. \emph{Journal of
Evolutionary Biology}, \textbf{26}, 1307--1316.

\leavevmode\vadjust pre{\hypertarget{ref-Vincent2005}{}}%
Vincent, T.L. \& Brown, J.S. (2005) \emph{{Evolutionary Game Theory,
Natural Selection, and Darwinian Dynamics}}. Cambridge University Press,
Cambridge.

\end{CSLReferences}

\clearpage

\hypertarget{supporting-information}{%
\section{Supporting Information}\label{supporting-information}}

\begin{longtable}[]{@{}ll@{}}
\toprule
Information & Page \\
\midrule
\endhead
S1: Description of the individual-based simulation model & 26 \\
S2: Sensitivity analysis of mortality parameters in IBM & 29 \\
S3: Alternative derivation of male fitness threshold & 31 \\
S4: Operational sex ratio & 33 \\
S5: Estimation of key model parameter using experimental data & 35 \\
S6: Separate evolution of male search and female choice & 36 \\
\bottomrule
\end{longtable}

\clearpage

\hypertarget{s1-description-of-the-individual-based-simulation-model}{%
\subsection{S1: Description of the individual-based simulation
model}\label{s1-description-of-the-individual-based-simulation-model}}

Here we describe the details of initialisation, time-in (mating),
time-out (reproduction and nuptial gift search), and mortality. We then
summarise the simulations run and data collected.

\emph{Initialisation}

Before the first time step, a population of \(N = 1000\) individuals is
initialised. Individuals are assigned unique IDs, and each is assigned
to be female with a probability of \(0.5\), else male. Each individual
\(i\) is initialised with a starting value of female offspring
processing time (\(T^{i}_{\mathrm{f}}\)), rejection rate for females
(\(\rho^{i}\)), and male search time (\(T^{i}_{\mathrm{m}}\)). For all
simulations, initialised values are set to \(T^{i}_{\mathrm{f}} = 2\),
\(\rho^{i} = 0\), and \(T^{i}_{\mathrm{m}} = 0\). All individuals are
initalised outside of the mating pool in the first time step \(t = 1\).
The first time step then proceeds with females immediately entering the
mating pool and males either entering the mating pool or searching for
nuptial gifts.

\emph{Time-in}

At the start of each time step, females and males in the mating pool
remain in it. Females will enter the mating pool after processing
offspring, and males will enter it after searching for nuptial gifts
(see `Time-out' below). A fixed number of \(\Psi = N\psi\) interactions
between individuals occur in a single time step, where \(N\) is
population size and \(\psi\) is a scaling parameter. Since an
interaction includes two conspecifics, each individual is expected to
encounter a conspecific \(2\psi\) times per time step (i.e.,
\(R = 2\psi\)). For each interaction, two individuals are randomly
sampled, each with equal probability. If both sampled individuals are
within the mating pool and of different sexes, then a mating encounter
occurs. If the male does not have a nuptial gift, then the female will
reject him with a probability of \(\rho^{i}\); if rejection occurs, then
both individuals stay in the mating pool. If rejection does not occur,
or the male has a nuptial gift in the mating encounter, then the
individuals mate. Females leave the mating pool and enter time-out to
process offspring, and males leave and enter time-out to potentially
search for new nuptial gifts (note that females and males might re-enter
the mating pool immediately within the same time step given sufficiently
low search time; see Time-out below).

\emph{Time-out}

During time out, a focal female \(i\) will produce
\(\lambda_{i} \sim Poisson(\lambda)\) offspring if no nuptial gift was
provided or \(\lambda_{i} \sim Poisson(\lambda + \gamma)\) if a gift was
provided. Females remain outside of the mating pool to process offspring
for \(T^{i}_{\mathrm{f}}\) time steps, where \(T^{i}_{\mathrm{f}}\) is
sampled randomly for each individual from a Poisson distribution with a
rate parameter of \(T_{\mathrm{f}}\),
\(T^{i}_{\mathrm{f}} \sim Poisson(T_{\mathrm{f}})\). Offspring are added
to the population immediately, with \(\rho^{i}\) and
\(T^{i}_{\mathrm{m}}\) values that are the average of each parent plus
some normally distributed error \(\epsilon_{R}\) and
\(\epsilon_{T_{\mathrm{m}}}\). For example,

\[T^{\mathrm{offspring}}_{\mathrm{m}} \sim N\left(\frac{T^{\mathrm{mother}}_{\mathrm{m}}  + T^{\mathrm{father}}_{\mathrm{m}}}{2}, \epsilon_{T_{\mathrm{m}}} \right).\]

The variation generated by \(\epsilon\) values simulates mutation upon
which selection for traits can act. In all simulations, \(\epsilon = 0\)
if a trait is fixed and \(\epsilon = 0.01\) if the trait evolves.
Offspring sex is randomly assigned with equal probability as female or
male. Female offspring are immediately placed in the mating pool, and
male offspring are out of the mating pool to search for nuptial gifts.
After a female has spent \(T^{i}_{\mathrm{f}}\) time steps outside the
mating pool, she will re-enter it.

A focal male \(i\) outside the mating pool will enter it if they have
searched for a fixed number of \(T^{i}_{\mathrm{m}}\) time steps, which
is also sampled randomly from a Poisson distribution,
\(T^{i}_{\mathrm{m}} \sim Poisson(T_{\mathrm{m}})\). If
\(T^{i}_{\mathrm{m}} = 0\), then the male immediately returns to the
mating pool (in the same time step). If \(T^{i}_{\mathrm{m}} > 0\), then
the male must wait outside the mating pool for \(T^{i}_{\mathrm{m}}\)
time steps, but will enter the mating pool with a nuptial gift with a
probability,

\[G^{i} = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.\]

Males must always spend \(T^{i}_{\mathrm{m}}\) time steps outside of the
mating pool regardless of whether or not they are successful in
obtaining a nuptial gift.

\emph{Mortality}

At the end of time step, mortality occurs first with a fixed probability
for all adults in the population, then with a probability caused by
carrying capacity \(K\) applied to all individuals (adults and
offspring). Mortality occurs in each time step with a fixed probability
of \(\mu\) regardless of the sex of the individual or its position in or
out of the mating pool. If after this fixed mortality is applied, the
total population size \(N > K\), then individuals are removed at random
with equal probability until \(N = K\). Following adult mortality, a new
time step begins with newly added offspring becoming adults.

\emph{Simulations}

We ran simulations in which male search time and female choosiness
evolved from an ancestral state of no searching and no choosiness. In
all simulations, \(N\) was initialised at 1000 and \(K = 1000\).
Simulations ran for \(t_{max} = 40000\) time steps. We set
\(T_{\mathrm{f}} = 2\), \(\psi = 3\), and \(\lambda = 1\) for all
simulations, and we simulated across a range of
\(\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}\) and
\(\gamma = \{0, 0.1, ..., 1.9, 2.0\}\) parameter values for 1600
replicates. Summary statistics for mean trait values, population size,
sex ratios, proportion of females and males in and out of the mating
pool, and mean number of encounters per female and male within the
mating pool were all calculated in the last time step. The C code used
for simulating these IBMs also allows for the reporting of statistics in
each time step. Additionally, it can simulate explicit space and
individual movement through the landscape. A neutral evolving trait was
also modelled to ensure that the code functioned as intended, and
processes were compartmentalised into individual functions to facilitate
code testing. All code is publicly available on GitHub
(\url{https://github.com/bradduthie/Pisaura}).

A set of simulations with a value of \(\gamma\) calculated from
empirical data was also conducted. Here, \(\gamma\) was parameterised
using data on egg production as a function of eating nuptial gifts (see
below). Additional simulation sets with lower and upper bounds of the
estimated \(\gamma\) were subsequently run. In the simulation sets with
experimentally derived parameter values, all other parameters were
identical to previous simulation batches.

We can produce an estimate of the fitness increment obtained by females
when receiving a gift (\(\hat{\gamma}\)) by using data on female
\emph{P. mirabilis} egg production and hatching success under different
feeding regimes from (\protect\hyperlink{ref-Tuni2013a}{Tuni \emph{et
al.}, 2013}). Tuni \emph{et al.}
(\protect\hyperlink{ref-Tuni2013a}{2013}) found differences in egg
production and hatching success in female \emph{P. mirabilis} under
different feeding regimes. Assuming these differences in feeding regimes
correspond to eating versus not eating nuptial gifts, the mean number of
offspring produced by a female who eats nuptial gifts can be calculated
(Table 1).

\hypertarget{s2-sensitivity-analysis-of-parameters-in-ibm}{%
\subsection{S2: Sensitivity analysis of parameters in
IBM}\label{s2-sensitivity-analysis-of-parameters-in-ibm}}

\textbf{Mortality}

We conducted a sensitivity analysis of the effect of the mortality
parameters \(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\) (the
probability of mortality in time in and time out, respectively, which we
assumed to be equal for all individuals) on the evolution of male search
and female choice using the IBM (See S1). The results revealed no
correlation between the value of the mortality parameters and the
evolution of male search or female choice (Fig. S2.1).

\captionsetup{labelformat=empty}

\begin{figure}
\centering
\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-6-1.pdf}
\caption{Figure S4.1: Evolution of both male search (blue) and female
choice (red) under different combinations of the mortality rates
\(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\) (mortality in time in
and out, respectively). The y-axis is the threshold fitness that leads
to evolution of male search (blue) or female choice (red). The results
show noise, but no correlation between the value of the mortality
parameters and the propensity for male search and/or female choice to
evolve. For each of the \(25 \times 20\) combinations of
\(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\), 1600 replicate
simulations were run.}
\end{figure}

\captionsetup{labelformat=default}

\textbf{Female processing time}

We also conducted a sensitivity analysis of female processing time
\(T_{\mathrm{f}}\). To do this, we ran simulations at default values,
but with \(T_{\mathrm{f}} = 0.4\) (Figure S4.2) and
\(T_{\mathrm{f}} = 10.0\) (Figures S4.3).

\captionsetup{labelformat=empty}

\begin{figure}
\centering
\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-7-1.pdf}
\caption{Figure S4.2 (\(T_{\mathrm{f}} = 0.4\)): The coevolution of male
search and female choosiness as a function of nuptial gift search time
(\(\alpha\)). Points show where the lower 95\% confidence interval of
female choosiness (red) and male search (blue) exceeds zero, indicating
evolution of choosiness or nuptial gift search. Each point includes data
from 720 replicate simulations with identical starting conditions. Red
and blue lines show thresholds above which the mathematical model
predicts that females should be choosy and males should search,
respectively. Approximately 3000 interactions occur between individuals
in each time step, potentially resulting in a mating interaction. The
number of individuals in the population remained at or near carrying
capacity of \(K = 1000\). Expected female processing time was set to
\(T_{\mathrm{f}}=0.4\) time steps, and \(\gamma\) and \(\alpha\) values
in the range {[}0.5, 1.5{]} and {[}0.1, 2.1{]}, respectively, were
used.}
\end{figure}

\captionsetup{labelformat=default}

\captionsetup{labelformat=empty}

\begin{figure}
\centering
\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-8-1.pdf}
\caption{Figure S4.3 (\(T_{\mathrm{f}} = 10.0\)): The coevolution of
male search and female choosiness as a function of nuptial gift search
time (\(\alpha\)). Points show where the lower 95\% confidence interval
of female choosiness (red) and male search (blue) exceeds zero,
indicating evolution of choosiness or nuptial gift search. Each point
includes data from 720 replicate simulations with identical starting
conditions. Red and blue lines show thresholds above which the
mathematical model predicts that females should be choosy and males
should search, respectively. Approximately 3000 interactions occur
between individuals in each time step, potentially resulting in a mating
interaction. The number of individuals in the population remained at or
near carrying capacity of \(K = 1000\). Expected female processing time
was set to \(T_{\mathrm{f}}=10.0\) time steps, and \(\gamma\) and
\(\alpha\) values in the range {[}0.5, 1.5{]} and {[}0.1, 2.1{]},
respectively, were used.}
\end{figure}

\captionsetup{labelformat=default}

\textbf{Interactions between conspecifics}

We conducted a sensitivity analysis on the encounter rate between
conspecifics (\(R\)) by varying the value of \(\psi\), where
\(R = 2\psi\) (see S1). Under default simulations, \(\psi = 3\) and
\(R = 6\). We also ran simulations in which \(\psi = 1\) (Figure S4.4)
and \(\psi = 6\) (Figure S4.5), with all other parameters being set to
default values.

\captionsetup{labelformat=empty}

\begin{figure}
\centering
\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-9-1.pdf}
\caption{Figure S4.4 (\(\psi = 1\)): The coevolution of male search and
female choosiness as a function of nuptial gift search time
(\(\alpha\)). Points show where the lower 95\% confidence interval of
where male search (blue) exceeds zero, indicating evolution of
choosiness or nuptial gift search. Each point includes data from 720
replicate simulations with identical starting conditions. Red and blue
lines show thresholds above which the mathematical model predicts that
females should be choosy and males should search, respectively.
Approximately 1000 interactions occur between individuals in each time
step, potentially resulting in a mating interaction. The number of
individuals in the population remained at or near carrying capacity of
\(K = 1000\). Expected female processing time was set to
\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]}, respectively, were used.}
\end{figure}

\captionsetup{labelformat=default}

\captionsetup{labelformat=empty}

\begin{figure}
\centering
\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-10-1.pdf}
\caption{Figure S4.5 (\(\psi = 6\)): The coevolution of male search and
female choosiness as a function of nuptial gift search time
(\(\alpha\)). Points show where the lower 95\% confidence interval of
where male search (blue) exceeds zero, indicating evolution of
choosiness or nuptial gift search. Each point includes data from 720
replicate simulations with identical starting conditions. Red and blue
lines show thresholds above which the mathematical model predicts that
females should be choosy and males should search, respectively.
Approximately 6000 interactions occur between individuals in each time
step, potentially resulting in a mating interaction. The number of
individuals in the population remained at or near carrying capacity of
\(K = 1000\). Expected female processing time was set to
\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]}, respectively, were used.}
\end{figure}

\captionsetup{labelformat=default}

\clearpage

\captionsetup{labelformat=empty}

\begin{figure}
\centering
\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-11-1.pdf}
\caption{Figure S4.5 (\(\psi = 6\)): The coevolution of male search and
female choosiness as a function of nuptial gift search time
(\(\alpha\)). Points show where the lower 95\% confidence interval of
where male search (blue) exceeds zero, indicating evolution of
choosiness or nuptial gift search. Each point includes data from 720
replicate simulations with identical starting conditions. Red and blue
lines show thresholds above which the mathematical model predicts that
females should be choosy and males should search, respectively.
Approximately 6000 interactions occur between individuals in each time
step, potentially resulting in a mating interaction. The number of
individuals in the population remained at or near carrying capacity of
\(K = 1000\). Expected female processing time was set to
\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]}, respectively, were used.}
\end{figure}

\captionsetup{labelformat=default}

\clearpage

\captionsetup{labelformat=empty}

\begin{figure}
\centering
\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-12-1.pdf}
\caption{Figure S4.5 (\(\psi = 6\)): The coevolution of male search and
female choosiness as a function of nuptial gift search time
(\(\alpha\)). Points show where the lower 95\% confidence interval of
where male search (blue) exceeds zero, indicating evolution of
choosiness or nuptial gift search. Each point includes data from 720
replicate simulations with identical starting conditions. Red and blue
lines show thresholds above which the mathematical model predicts that
females should be choosy and males should search, respectively.
Approximately 6000 interactions occur between individuals in each time
step, potentially resulting in a mating interaction. The number of
individuals in the population remained at or near carrying capacity of
\(K = 1000\). Expected female processing time was set to
\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]}, respectively, were used.}
\end{figure}

\captionsetup{labelformat=default}

\clearpage

\captionsetup{labelformat=empty}

\begin{figure}
\centering
\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-13-1.pdf}
\caption{Caption here}
\end{figure}

\captionsetup{labelformat=default}

\clearpage

\captionsetup{labelformat=empty}

\begin{figure}
\centering
\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-14-1.pdf}
\caption{Caption here}
\end{figure}

\captionsetup{labelformat=default}

\clearpage

\hypertarget{s3-alternative-derivation-of-male-fitness-threshold}{%
\subsection{S3: Alternative derivation of male fitness
threshold}\label{s3-alternative-derivation-of-male-fitness-threshold}}

In the main text, we assumed that males made the decision to search or
not search for a nuptial gift. The expected length of time for which
searching males are expected to remain outside of the mating pool is
\(E[T_{\mathrm{m}}] = \alpha\) (see Methods). Alternatively, we can
assume that males search for a period of \(T_{\mathrm{m}}\) and spend
this full duration of \(T_{\mathrm{m}}\) in the time-out phase, even if
they succeed in finding a nuptial gift. The probability that a male
obtains a nuptial gift during this time is modelled in Eq. 1,

\[G = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]

In Eq. 1, \(\alpha\) is the amount of time expected to pass before a
male encounters a nuptial gift. We assume that a male will only enter
the mating pool with no gift if they are unsuccessful in obtaining a
gift, so the probability that a male obtains no gift after
\(T_{\mathrm{m}}\) is,

\[L = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]

For simplicity, we assume that the fitness increments to offspring
associated with receiving a nuptial gift versus no nuptial gift are
\(1 + \gamma\) and 1, respectively. The rate at which males increase
their fitness can then be defined as the expected fitness increment from
their nuptial gift search divided by \(T_{\mathrm{m}}\) plus the time
spent in the mating pool waiting to encounter a mate,

\[W_{\mathrm{m}} = \lambda \frac{G\left(1 + \gamma\right) + L}{T_{\mathrm{m}} + \left( \frac{\beta + 1}{R} \right)}.\]

Our objective now is to determine the conditions under which a focal
male increases its fitness by searching for a nuptial gift
(\(T_{\mathrm{m}}>0\)) in a population of resident males that do not
search (\(T_{\mathrm{m}}=0\)). Females are assumed to exhibit no choice
in males with versus without nuptial gifts. Under such conditions, male
fitness cannot be affected by female choice, so selection to increase
\(T_{\mathrm{m}}>0\) must be based solely on \(\alpha\), \(\beta\),
\(R\), and \(\gamma\).

To determine under what conditions male inclusive fitness increases with
nuptial gift search time, we can differentiate \(W_{\mathrm{m}}\) with
respect to \(T_{\mathrm{m}}\),

\[\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda\frac{\gamma\left(\frac{\frac{T_{\mathrm{m}} + \frac{\beta + 1}{R}}{\alpha} + 1}{e^{\frac{1}{\alpha}T_{\mathrm{m}}}} - 1\right) - 1}{\left(T_{\mathrm{m}} + \frac{\beta + 1}{R} \right)^{2}}.\]

Because \(T_{\mathrm{m}} = 0\), the above simplifies,

\[\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda \frac{\frac{R\gamma\left(\beta + 1\right)}{\alpha} - R^{2}}{\left(1 + \beta \right)^{2}}.\]

We can re-arrange the above,

\[\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)} - \lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}}.\]

Note that if \(R = 0\) or \(\lambda = 0\), then, trivially, no change in
fitness occurs (since females and males cannot mate or do not produce
offspring). Fitness is increased by searching for nuptial gifts when
\(\gamma\) is high, scaled by the expect search time needed to find a
nuptial gift. A second term on the right-hand side is subtracted, which
reflects a loss in fitness proportional to the encounter rate of
potential mates in the mating pool. The conditions under which male
inclusive fitness increases by searching for a nuptial gift are found by
setting \(\partial W_{\mathrm{m}}/\partial T_{\mathrm{m}} = 0\) and
solving for \(\gamma\) to get Eq. 2 in the main text.

\clearpage

\hypertarget{s4-operational-sex-ratio}{%
\subsection{S4: Operational sex ratio}\label{s4-operational-sex-ratio}}

We assume that the ratio of males to femalesis the same upon individual
maturation. Consequently, the operational sex ratio \(\beta\) will be a
function of \(R\), \(T_{f}\), and \(T_{m}\) because these parameters
determine the density of females and males in the mating pool versus
outside of the mating pool. We start with the definition of \(\beta\) as
being the probability of finding an individual in `time in'
(\protect\hyperlink{ref-Kokko2001}{Kokko \& Monaghan, 2001}),

\[\beta = \frac{\int_{t=0}^{\infty}P_{IM}(t)dt}{\int_{t=0}^{\infty}P_{IF}(t)dt}\]

We can substitute the equations for \(P_{IM}(t)\) and \(P_{IF}(t)\),
which define the probabilities of males and females being within the
mating pool at time \(t\), respectively.

We can therefore calculate \(\beta\) as below,

\[\beta = \frac{\left( \frac{\left(\frac{\beta + 1}{R}\right)}{T_{\mathrm{m}} + \left(\frac{\beta + 1}{R}\right)} \right)}{\left( \frac{\left(R \frac{\beta}{\beta + 1}\right)}{T_{\mathrm{f}} + \left(R \frac{\beta}{\beta + 1}\right)} \right)}.\]

This can be simplified,

\[\beta = \frac{\left(\beta\left(R + T_{f}\right) + T_{f}\right)\left(\beta + 1\right)}{\beta \left(R^{2}T_{m} + R\right) + \beta^{2}R}.\]

There is no closed form solution for \(\beta\), but a recursive
algorithm can be used to calculate \(\beta\) to an arbitrary degree of
precision.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{recursive\_b }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(B, D, Tf, Tm, }\AttributeTok{crit =} \FloatTok{0.0001}\NormalTok{, }\AttributeTok{maxit =} \DecValTok{9999}\NormalTok{)\{}
\NormalTok{  conv }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{;}
\NormalTok{  iter }\OtherTok{\textless{}{-}} \DecValTok{0}\NormalTok{;}
  \ControlFlowTok{while}\NormalTok{(conv }\SpecialCharTok{\textgreater{}}\NormalTok{ crit }\SpecialCharTok{\&}\NormalTok{ iter }\SpecialCharTok{\textless{}}\NormalTok{ maxit)\{}
\NormalTok{    Fe   }\OtherTok{\textless{}{-}}\NormalTok{ D }\SpecialCharTok{*}\NormalTok{ (B }\SpecialCharTok{/}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+}\NormalTok{ B));}
\NormalTok{    Me   }\OtherTok{\textless{}{-}}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+}\NormalTok{ B) }\SpecialCharTok{/}\NormalTok{ D;}
\NormalTok{    Bn   }\OtherTok{\textless{}{-}}\NormalTok{ (Me }\SpecialCharTok{/}\NormalTok{ (Tm }\SpecialCharTok{+}\NormalTok{ Me)) }\SpecialCharTok{/}\NormalTok{ (Fe }\SpecialCharTok{/}\NormalTok{ (Tf }\SpecialCharTok{+}\NormalTok{ Fe));}
\NormalTok{    iter }\OtherTok{\textless{}{-}}\NormalTok{ iter }\SpecialCharTok{+} \DecValTok{1}\NormalTok{;}
\NormalTok{    conv }\OtherTok{\textless{}{-}} \FunctionTok{abs}\NormalTok{(Bn }\SpecialCharTok{{-}}\NormalTok{ B);}
\NormalTok{    B    }\OtherTok{\textless{}{-}}\NormalTok{ Bn;}
\NormalTok{  \}}
  \FunctionTok{return}\NormalTok{(}\FunctionTok{list}\NormalTok{(}\AttributeTok{B =}\NormalTok{ B, }\AttributeTok{conv =}\NormalTok{ conv, }\AttributeTok{iter =}\NormalTok{ iter));}
\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

We used the above function to calculate values of \(\beta\) for the
analytical model.

\clearpage

\hypertarget{s5-estimation-of-key-model-parameters-using-experimental-data}{%
\subsection{S5: Estimation of key model parameters using experimental
data}\label{s5-estimation-of-key-model-parameters-using-experimental-data}}

Estimates showing mean number of offspring produced by female
\emph{Pisaura mirabilis} that ate nuptial gifts and females who did not.
Means were calculated with raw data from Tuni \emph{et al.}
(\protect\hyperlink{ref-Tuni2013a}{2013}) and results are shown \(\pm\)
SE (Table 1). Under these assumptions, the relative gain in fitness from
receiving nuptial gifts for a female is,

\[\hat{\delta_\mathrm{f}} = \frac{25.74}{6.00} = 4.29\]

Since the baseline fitness is 1, the increase in fitness resulting from
a nuptial gift then becomes,

\[\hat{\gamma} = \hat{\delta_{\mathrm{f}}} - 1 = 3.29.\]

The value 3.29 was used to parameterise \(\gamma\) for a set of
simulations (Figure 4 in the main text).

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4024}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2805}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3171}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Received nuptial gift
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Received no nuptial gift
\end{minipage} \\
\midrule
\endhead
Expected number of hatched eggs & \(25.74 \pm 0.96\) &
\(6.00 \pm 2.1\) \\
\bottomrule
\end{longtable}

Table 1: Estimates showing mean number of offspring produced by female
\emph{Pisauras mirabilis} that ate nuptial gifts and females who did
not. Means were calculated with raw data from Tuni \emph{et al.}
(\protect\hyperlink{ref-Tuni2013a}{2013}) and results are shown \(\pm\)
SE.

\clearpage

\hypertarget{s6-separate-evolution-of-male-search-and-female-choice}{%
\subsection{S6: Separate evolution of male search and female
choice}\label{s6-separate-evolution-of-male-search-and-female-choice}}

We used the individual-based simulation model (see Supporting
Information S1) to unpack the effect of coevolution on the evolution of
male search and female choice. Specifically, we replicated the
simulations shown in the main text under the condition where only one
trait at a time was allowed to evolve and studied how this affected the
trait evolution.

First, we submitted a set of simulations wherein male search did not
evolve, but was fixed at different values (see Fig. S6.1). Next, we ran
the same set of simulations wherein male search evolved, but female
choice was not possible). The results thus show how each trait evolves
in the absence of any coevolution (Fig. S6.1).

\captionsetup{labelformat=empty}

\begin{figure}
\centering
\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-16-1.pdf}
\caption{Figure S6.1: The separate evolution of male search and female
choosiness as a function of nuptial gift search time. Points show where
the lower 95\% confidence interval of male search (blue) and female
choosiness (red) exceeds zero, indicating evolution of nuptial gift
search or choosiness. Each point includes data from \(2 imes 1600\)
replicate simulations with identical starting conditions. In the first
batch, male search was constant and initialized at
\(T_{\mathrm{m}} = \alpha\), and female choice was evolving. In the
second batch, male search was evolving, and there was no option for
female choice. The parameters \(T_{\mathrm{f}}=2\), and \(\gamma\) and
\(\alpha\) values were set within the range {[}0.1, 2.0{]} and {[}0.3,
1.7{]}, respectively.}
\end{figure}

\captionsetup{labelformat=default}

\end{document}

### 2024-06-01 response_to_review.md
Add response to most recent reviewer comments

Reviewer Commment
=========================================================

Review nuptial gift giving round 2

This is my second round of review on this manuscript. I was enthusiastic during the first round, but had spotted some confusions that I would have liked to see clarified. I have to say that I am a little bit underwhelmed with this new version of the manuscript. While the authors have clearly put efforts into answering some of my numerous comments, I feel like some important concerns on the logic of the model and presentation of the results have been politely left aside. The author’s logic may still be correct (or not), but it is not more explicit in this new version than it was in the first one. I will not give a detailed review here but only insist on those points that I am surprised to see unchanged. This is rather disappointing as I was looking forward to the updated version of an interesting study that I would like to see published.

I did not received the new version without track changes, so I had to open the word document and accept the track changes to work on it. The line numbering I am using in my comment is of the word document with accepted track changes.

Author Response
=========================================================

Reviewer Commment
=========================================================

I have three main concerns. I give an overview here and then detailed comments referring to the
first round of review.

1.) I do not agree with the way that encounter rates are calculated as a function of the sex-ratio in the population. The way it is now, global encounter rates (population density) vary with the sex ratio so that for example when the sex ratio is extremely biased encounter rates become arbitrarily high. My view is that the relative encounter rates when comparing males and females are correct, but the sex-specific encounter rates are wrong. I may be the one who is confused here, but then the logic of how these encounter rates are calculated should be spelled out. If over-estimating encounter rates does not affect the outcome of the model because only the relative encounter rates are important, this is also fine but needs to be spelled out that way. See my point below. I do not think that this is a trivial point, since the evolution of gift searching is likely to modify the time-outs and thus the sex ratio in the mating pool. If encounter rates are not calculated correctly, this could bias the fitness threshold for the evolution of the trait.

Author Response
=========================================================

We greatly appreciate the persistence and the patience of Reviewer 1. We were getting hung up on the interaction rates being consistent with previous literature, but Reviewer 1 is completely correct that only the relative encounter rates were correct while the absolute sex-specific encounter rates are what really matters. Their explanation in their most recent review makes this very clear.

We have revised our model exactly as they have suggested, starting with the absolute encounter rate 'R' instead of 'M' to calculate the absolute rate at which a focal individual encounters a potential mate. Fortunately, the very intuitive thresholds for females and males are preserved; i.e., the theoretical results do not change at all qualitatively. The thresholds are slightly different and linear rather than curvilinear. This is reflected in a new Figure 2. Unfortunately, given this new formulation, there is no closed form solution for beta, but values of beta are easy to calculate through recursion to an arbitrary degree of precision.

Fortunately, no changes to the individual-based model needed to be made because the encounter rates were calculated directly from model output.

Reviewer Commment
=========================================================

2.) I do not understand the discrepancies between the IBM and the analytical model and I feel
like they are being downplayed. For example, the female fitness threshold is qualitatively
different, see my detailed comment and figure below.

Author Response
=========================================================

Again, we are very grateful for Reviewer 1's thoughtful critique. Addressing this concern has helped us reflect on our results and communicate them much more strongly. Discrepancies between the IBM and the analytical model were not intentionally downplayed. We actually now think that they were unintentionally exaggerated by the parameter space that we were illustrating in analytical model (our accidental reversal of threshold colours didn't help). We have resolved this by turning Figure 2 into a two-panel figure, with the second panel now illustrating an area of parameter space that is much more in line with the IBM results of Figure 3.

Figure 2a now shows the parameter space in the old Figure 2, with the four zones corresponding to four different evolutionary outcomes as before, determined by thresholds for male nuptial gift search (blue) and female choosiness (red). The new Figure 2b shows what happens as conspecific interaction rate (see Reviewer 1's first concern) is decreased from 2 to 1. In this case, zone C (where females would be choosy but males do not search) disappears because the thresholds no longer cross along the range of the x-axis. We are left with three zones: (A) no searching or choosiness, (B) searching but no choosiness, and (D) searching and choosiness. These zones are qualitatively identical to the pattern produced by the IBM in Figure 3, and they are almost exactly predicted by the thresholds shown in Figure 3.

We hope that Reviewer 1 agrees that this new presentation illustrates that the female fitness threshold is not qualitatively different between the analytical model and the IBM. Nevertheless, there are two small quantitative differences for female choosiness that are worth noting. The first is that the female threshold in the IBM (red line of Figure 3) is curved rather than linear. This is because we cannot actually control the interaction rate (R) in the IBM; it isn't fixed as in Figure 2, so we use estimations of the interaction rate to build the threshold line from inequality 5. This threshold line does a good job of predicting when choosiness will evolve, but it is a bit conservative for high nuptial gift search times (alpha; Figure 3). This is likely because the IBM allows for coevolution between male search and female choosiness, which does not exist for the anlaytical model in Figure 2. Note that when female and male traits are fixed while the other evolves (Figure S6.1), the choosiness threshold line appears to be too ambitious -- though this is likely because a much higher sample size is needed for confidence intervals to not overlap zero when parameter values are just over the choosiness threshold in the IBM (simulation time has been a recurring challenge for this manuscript -- each point in Figure 3 represents 3200 replicate simulations, while Figure S6.1 represents 1600).

Reviewer Commment
=========================================================

3.) I think the gamma parameter (increase in offspring relative fitness) needs to reach very high values for gift giving to evolve and I would like to see that discussed (imagine a population genetics or evolutionary dynamics paper where the mutant invading the population has a fitness 6 times higher than the resident). This is very important since the smaller the range of gamma the more differences between the IBM and the analytical model are visible.

Author Response
=========================================================

We agree that Figures 2 and 3 might give readers the misleading impression that very high values of gamma are required for the evolution of male search (and subsequent female choosiness). This is an important point and provides a further rationale for exploring a wider area of parameter space, which the reviewer also suggested. In the supporting information, we now include results from our individual-based model that show an area of parameter space in which male searching evolves at low values of gamma. This complements the analytical model in showing that the evolution of searching is possible given sufficiently low M (now D), even if alpha is low (Figure 2, equation 2). This is even further solidified by our correction of the analytical model brought about by the reviewer's first point, which shows a linear relationship (instead of a curvilinear one) between search time and fitness thresholds -- we're very grateful for these suggestions from the reviewer! We now include two new paragraphs in the Discussion to elaborate on why searching and choosiness are still likely to evolve in some systems, even when gamma is not extremely high (line X). We have also included a whole new section of supporting information which demonstrates that both traits can evolve even when gamma is very low (line X).

Reviewer Commment
=========================================================

4.) New concern: given the discrepancies between the analytical model and IBM as it is, I think that the parameter space should be properly explored. How do Tm,M,Tm, affect the two models? The little arrows on Figure 2 are not enough.

Author Response
=========================================================

We appreciate this new concern, but we hope that our response to Reviewer concerns 1 and 2 demonstrate that there is no major discrepancy between the analytical model and the IBM. Both models indeed illustrate the same qualitative results, so we have provided two separate models leading to identical conclusions about the evolution of nuptial gift searching and choosiness.

Nevertheless, we have taken Reviewer 1's suggestions and tried to explore more of the parameter space for the IBM. A major challenge here has been the computational time needed to run simulations. Even using a compiled programming language (C) and with access to a computing cluster, a full search of parameter space has proved challenging. Inevitably, IBM results will underestimate when gift-giving and choosiness evolve, but evolution should not happen under calculated thresholds.

We have explored how  varying Tm, Tf and M (now R) affected the female and male fitness threshold. Specifically, we re-created figure 3 from the main text under new values of Tm, Tf and M. We explored values both above and below the values used in the main text.

We found that inequality 2 & 3 of the analytical model do indeed give predictions consistent with calculated thresholds as to changes in Tm, Tf and R. That is, increases in Tm, Tf and R were found to decrease the female fitness threshold and increases in M were found to increase the male fitness threshold, and this is in agreement with the arrows on figure 2 in the main text. We have written a section of supporting information for these results (see Supporting Information S2). With more time, we could run more of these simulations.

### 2024-06-02 ms_refs_fixed.Rmd
Make some edits to the introduction based on reviewer comments

@@
 Despite the ubiquity of this behaviour, little effort has been made to conceptualise the evolution of nuptial gift-giving within a general modelling framework [@Lewis2014; @Iwasa2022]. 
-Recent models describing the evolution of nuptial gift-giving have focused on co-evolution between male nuptial gift-giving and female propensity to remate, and the evolutionarily stable nuptial gift sizes [@Iwasa2022; @Kamimura2021], but a general framework describing the conditions necessary for nuptial gift-giving to be initially favoured by selection is needed to understand when gift-giving should evolve.
+Recent models describing the evolution of nuptial gift-giving have focused on co-evolution between male nuptial gift-giving and female propensity to remate, and evolutionarily stable nuptial gift sizes [@Iwasa2022; @Kamimura2021], but a general framework describing the conditions necessary for nuptial gift-giving to be initially favoured by selection is needed to understand when gift-giving should evolve.
+
 Nuptial gift-giving may allow males to increase fitness by acquiring additional mates, indirect benefits (by increasing the fitness of offspring), prolonged copulations, and success in sperm competition [@Lewis2014; @Albo2013; @Ghislandi2014].
@@
 With respect to nuptial gift-giving, the evolutionary interests of both sexes may not always fully overlap. 
-This can cause sexual conflict, which is a difference in the evolutionary interest between sexes that occurs when interaction between sexes results in a situation where neither sex can achieve an optimal outcome [@Parker2006]
-That is, under some conditions, it might for example be optimal for females to receive nuptial gifts, but not optimal for males to produce them.
+This can cause sexual conflict, which is a difference in the evolutionary interest between sexes that occurs when interaction between sexes results in a situation where neither sex can achieve an optimal outcome [@Parker2006].
+That is, under some conditions, it might for example be optimal for males but not females to mate if females do not benefit from mating with males without nuptial gifts.
 
 Much work has sought to explain how gift-giving tactics are maintained, with explanations including condition-dependent strategies, gift-giving as a way to decrease female aggression during copulation, or gifts as sensory traps [@Albo2019; @Lubin2007; @Ghislandi2018; @Toft2016].
-An example of such a system is the nuptial gift-giving nursery-web spider *Pisaura mirabilis* where males may court females with or without nuptial gifts [@Bristowe1926]. 
+An example of such a system is the nuptial gift-giving nursery-web spider *Pisaura mirabilis* where males may court females with or without nuptial gifts [@Bristowe1926; @Tuni2013a]. 
 Here, males may provide females with costly nuptial gifts in the form of captured arthropod prey, and females may exhibit preference for males with a nuptial gift by rejecting males without a nuptial gift [@Albo2013].
@@
 Males have a probability of obtaining a nuptial gift while in time-out, which will affect their probability of mating while in time-in.
-They return to the mating pool (time-in) at a rate determined by the time spent searching for a nuptial gifts ($T_{m}$) and leave the mating pool (i.e.
-enter time-out) following the female encounter rate, which is dependent on ratio of males to females ($\\beta$) and the encounter rate ($R$).
-The choosy sex (females) enter the mating pool at a rate depending in the time spent processing offspring ($T_{f}$) and leave the mating pool (i.e.
+They return to the mating pool (time-in) at a rate determined by the time spent searching for a nuptial gifts ($T_{\\mathrm{m}}$) and leave the mating pool (i.e.
+enter time-out) following the female encounter rate, which is dependent on the ratio of males to females ($\\beta$) and the encounter rate ($R$).
+The choosy sex (females) enter the mating pool at a rate depending on the time spent processing offspring ($T_{\\mathrm{f}}$) and leave the mating pool (i.e.
 enter time-out) at a rate that is dependent on $\\beta$ and $R$.
@@
 ```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "The joint evolution of male search and female choosiness using a nuptial gift fitness increment ($\\gamma$) that was estimated from experimental data for the species *P.
-mirabilis* (Tuni et al.
-2013; mean $\\gamma = 3.29 \\pm$ SE via propagation of error for estimates of nuptial feeding a non-nuptial feeding groups: [1.47; 8.32]).
+mirabilis* (mean $\\gamma = 3.29 \\pm$ SE via propagation of error for estimates of nuptial feeding a non-nuptial feeding groups: [1.47; 8.32]).
 Points show where the 95% confidence interval exceeds 0 for female choosiness (red) and male search (blue).

### 2024-06-02 ms_refs_fixed.tex
Make some edits to the introduction based on reviewer comments

@@
 have focused on co-evolution between male nuptial gift-giving and female
-propensity to remate, and the evolutionarily stable nuptial gift sizes
+propensity to remate, and evolutionarily stable nuptial gift sizes
 (\protect\hyperlink{ref-Kamimura2021}{Kamimura \emph{et al.}, 2021};
@@
 gift-giving to be initially favoured by selection is needed to
-understand when gift-giving should evolve.\\
+understand when gift-giving should evolve.
+
 Nuptial gift-giving may allow males to increase fitness by acquiring
@@
 situation where neither sex can achieve an optimal outcome
-(\protect\hyperlink{ref-Parker2006}{Parker, 2006}) That is, under some
-conditions, it might for example be optimal for females to receive
-nuptial gifts, but not optimal for males to produce them.
+(\protect\hyperlink{ref-Parker2006}{Parker, 2006}). That is, under some
+conditions, it might for example be optimal for males but not females to
+mate if females do not benefit from mating with males without nuptial
+gifts.
 
@@
 nuptial gifts (\protect\hyperlink{ref-Bristowe1926}{Bristowe \& Locket,
-1926}). Here, males may provide females with costly nuptial gifts in the
-form of captured arthropod prey, and females may exhibit preference for
-males with a nuptial gift by rejecting males without a nuptial gift
+1926}; \protect\hyperlink{ref-Tuni2013a}{Tuni \emph{et al.}, 2013}).
+Here, males may provide females with costly nuptial gifts in the form of
+captured arthropod prey, and females may exhibit preference for males
+with a nuptial gift by rejecting males without a nuptial gift
 (\protect\hyperlink{ref-Albo2013}{Albo \emph{et al.}, 2013}).
@@
 Males have a probability of obtaining a nuptial gift while in time-out, which will affect their probability of mating while in time-in.
-They return to the mating pool (time-in) at a rate determined by the time spent searching for a nuptial gifts ($T_{m}$) and leave the mating pool (i.e.
-enter time-out) following the female encounter rate, which is dependent on ratio of males to females ($\beta$) and the encounter rate ($R$).
-The choosy sex (females) enter the mating pool at a rate depending in the time spent processing offspring ($T_{f}$) and leave the mating pool (i.e.
+They return to the mating pool (time-in) at a rate determined by the time spent searching for a nuptial gifts ($T_{\mathrm{m}}$) and leave the mating pool (i.e.
+enter time-out) following the female encounter rate, which is dependent on the ratio of males to females ($\beta$) and the encounter rate ($R$).
+The choosy sex (females) enter the mating pool at a rate depending on the time spent processing offspring ($T_{\mathrm{f}}$) and leave the mating pool (i.e.
 enter time-out) at a rate that is dependent on $\beta$ and $R$.
@@
 a nuptial gift fitness increment (\(\gamma\)) that was estimated from
-experimental data for the species \emph{P. mirabilis} (Tuni et al.~2013;
-mean \(\gamma = 3.29 \pm\) SE via propagation of error for estimates of
+experimental data for the species \emph{P. mirabilis} (mean
+\(\gamma = 3.29 \pm\) SE via propagation of error for estimates of
 nuptial feeding a non-nuptial feeding groups: {[}1.47; 8.32{]}). Points
@@
 choosiness (red) exceeds zero, indicating evolution of nuptial gift
-search or choosiness. Each point includes data from \(2 imes 1600\)
+search or choosiness. Each point includes data from \(2 \times 1600\)
 replicate simulations with identical starting conditions. In the first

### 2024-06-02 ms_refs_fixed.Rmd
Make some edits according to reviewer comments on the Results

@@
 During time-in, individuals encounter conspecifics at a rate of $R$.
-A focal individual will therefore encounter conspecifics of the opposite sex at a rate of $R/2$ if the ratio of males to females in the mating pool $\beta$ is equal.
+A focal individual will therefore encounter conspecifics of the opposite sex at a rate of $R/2$ if the ratio of males to females in the mating pool ($\beta$) is equal.
 More generally, males will be encountered at a rate of $R\beta/(\beta+1)$, and females will be encountered at a rate of $R/(\beta+1)$.
@@
 We assume that mating with a nuptial gift increases the fitness of each offspring by an increment of $\gamma$.
-We proceed to find the thresholds $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$ above which males and females are favoured by selection to search for nuptial gifts and exhibit choosiness for nuptial gifts, respectively.
+We proceed to find the thresholds $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$ above which males and females are favoured by selection to search for mates with nuptial gifts and exhibit choosiness for nuptial gifts, respectively.
 We show (see Methods) that the initial threshold value of $\gamma$ ($\gamma_{\mathrm{m}}$) necessary for males to increase their fitness by investing time searching for a nuptial gift (time that could otherwise be spent searching for a mate) is,
@@
 
-Inequality 3 shows that as offspring processing time ($T_{\mathrm{f}}$), mate encounter rate ($R\beta / (\beta + 1)$), and the probability of a male finding a nuptial gift ($1 - \exp(-T_{\mathrm{m}}/\alpha)$ ) decreases, the threshold value of fitness above which selection will favour choosiness ($\gamma_{\mathrm{f}}$) increases.
+Inequality 3 shows that as offspring processing time ($T_{\mathrm{f}}$), mate encounter rate ($R\beta / (\beta + 1)$), or the probability of a male finding a nuptial gift ($1 - \exp(-T_{\mathrm{m}}/\alpha)$ ) decreases, the threshold value of fitness above which selection will favour choosiness ($\gamma_{\mathrm{f}}$) increases.
 This can be understood intuitively by realising that rejecting a prospective male represents an opportunity cost for the female. 
@@
 
-```{r, echo = FALSE, fig.width = 8, fig.height = 4, fig.cap = "Fitness thresholds above which males increase their fitness by searching for nuptial gifts (blue line; Eq.
-2) and females increase their fitness by rejecting males that do not offer gifts (red line; Eq.
+```{r, echo = FALSE, fig.width = 8, fig.height = 4, fig.cap = "Fitness thresholds above which males increase their fitness by searching for nuptial gifts (blue lines; Eq.
+2) and females increase their fitness by rejecting males that do not offer gifts (red lines; Eq.
 3).
 Parameter space includes areas in which males do not search for nuptial gifts and females are not choosy (A), males search but females are not choosy (B), females would be choosy but males do not search (C), and males search and females are choosy (D).
-Arrows indicate the effect of increasing interaction rate ($R$), female time-out ($T_{f}$), and male search time ($T_{m}$).
-As an example, trajectories for $T_{f} = 2$, and $T_{m} = \\alpha$ are shown for values of $R=2$ (panel a) and $R = 1$ (panel b).
-Females are assumed to be the choosy sex, which is maintained as long as $\\alpha < T_{f}$."}
+Arrows in panel a indicate the effect of increasing interaction rate ($R$), female time-out ($T_{\\mathrm{f}}$), and male search time ($T_{\\mathrm{m}}$).
+As an example, trajectories for $T_{\\mathrm{f}} = 2$, and $T_{\\mathrm{m}} = \\alpha$ are shown for values of $R=2$ (panel a) and $R = 1$ (panel b).
+Females are assumed to be the choosy sex, which is maintained as long as $\\alpha < T_{\\mathrm{f}}$."}
 alpha_vals <- seq(from = 0.0001, to = 2, by = 0.0001);
@@
 
-The analytical framework predicts 4 zones, which are delineated by inequalities 2 and 3 and describe the initial thresholds for favouring search of nuptial gifts in males and choosiness for nuptial gifts in females (Figure 2).
-Consequently, the modelling framework gives a description of the conditions under which nuptial gift-giving is expected to occur (Figure 2, Zone D) and the conditions under which only selection for male searching (Figure 2, Zone B) or female choosiness (Figure 2, Zone C) are predicted.
+The analytical framework predicts 4 zones, which are delineated by inequalities 2 and 3 and describe the initial thresholds for favouring search of nuptial gifts in males and choosiness for nuptial gifts in females (Figure 2a).
+Consequently, the modelling framework gives a description of the conditions under which nuptial gift-giving is expected to occur (Figure 2a, Zone D) and the conditions under which only selection for male searching (Figure 2a, Zone B) or female choosiness (Figure 2a, Zone C) are predicted.
 These results therefore highlight the potential for sexual conflict over nuptial gift-giving.
@@
 
-We use an individual-based model (IBM) to simulate the evolution of nuptial gift-giving and female choosiness from an ancestral condition in which neither exists. 
+We used an individual-based model (IBM) to simulate the evolution of nuptial gift-giving and female choosiness from an ancestral condition in which neither exists. 
 The IBM was written to satisfy the assumptions of our analytical time-in and time-out model as much as practical (see Supporting Information S1). 
@@
 
-The rates at which males encounter females $R_{\mathrm{m}}$ and females encounter males with nuptial gifts $R_{\mathrm{f,G}}$ are calculated directly from the IBM, thereby modelling how these rates might be estimated from empirical data, so the male threshold for increasing fitness by searching is,
+The rates at which females are encountered by males $R_{\mathrm{f},\mathrm{m}}$ and males with nuptial gifts $R_{\mathrm{m_{G}}, \mathrm{f}}$ are encountered by females are both calculated directly from the IBM, thereby modelling how these rates might be estimated from empirical data, so the male threshold for increasing fitness by searching is,
 
@@
 \begin{equation}
-\gamma_{\mathrm{m, IBM}} > \alpha R_{\mathrm{m}}.
+\gamma_{\mathrm{m, IBM}} > \alpha R_{\mathrm{f},\mathrm{m}}.
 \end{equation}
@@
 \begin{equation}
-\gamma_{\mathrm{f, IBM}} > \frac{1}{T_{\mathrm{f}}R_{\mathrm{f,G}}}.
+\gamma_{\mathrm{f, IBM}} > \frac{1}{T_{\mathrm{f}}R_{\mathrm{m_{G}}, \mathrm{f}}}.
 \end{equation}
 
-Consequently, the IBM and the analytical model differ slightly (e.g., time is discrete in the IBM but continuous the analytical model, and in the IBM a fitness increment is applied to the focal female in the form of birthrate increase rather than offspring; see Supporting Information S1 for details).
+Consequently, the IBM and the analytical model differ slightly (e.g., time is discrete in the IBM but continuous the analytical model, and in the IBM, a fitness increment is applied to the focal female in the form of birthrate increase rather than offspring fitness; see Supporting Information S1 for details).
 But the predicted thresholds are theoretically equivalent and yield predictions that are qualitatively the same (Figure 3).
@@
 Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively (in agreement with Figure 2).
-Minor deviations between the analytical model and the simulation results are expected due to the finite population size and the substantial stochasticity inherent to the simulation model (for details, see Supporting Information S1).
-Approximately 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction.
+Minor deviations between the analytical model and the simulation results are expected due to the finite population size, the substantial stochasticity inherent to the simulation model, and the potential for coevolution (for details, see Supporting Information S1).
 The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
+In each time step, approximately 3000 total pair-wise interactions occurred ($R = 6$).
 Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 2.0] and [0.1, 2.0], respectively, were used."}
@@
 4 accurately predict the evolution of searching in the IBM across $\alpha$ values, and the female threshold $\gamma_{\mathrm{f, IBM}}$ (ineq.
-5) accurately predicts the evolution of female choice (Figure 3).
-In other words, IBM simulations demonstrate that nuptial gift search in males, and choosiness in females, will evolve from an ancestral state of no searching and no choosiness in similar parameter space (Figure 3) as predicted by the analytical model (Figure 2).
+5) predicts the evolution of female choice (Figure 3).
+In other words, IBM simulations demonstrate that nuptial gift search in males, and choosiness in females, will evolve from an ancestral state of no searching and no choosiness in similar parameter space (Figure 3) as predicted by the analytical model (Figure 2b).
 We further ran the IBM with realistic values of $\gamma$, estimated using data from the *P. mirabilis* system wherein choosiness among females, and nuptial gift search among males, occur (Figure 4). 
@@
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "The joint evolution of male search and female choosiness using a nuptial gift fitness increment ($\\gamma$) that was estimated from experimental data for the species *P.
-mirabilis* (mean $\\gamma = 3.29 \\pm$ SE via propagation of error for estimates of nuptial feeding a non-nuptial feeding groups: [1.47; 8.32]).
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "The joint evolution of male search and female choosiness using a nuptial gift fitness increment ($\\gamma$) that was estimated from experimental data for the species *Pisaura mirabilis* (mean $\\gamma = 3.29 \\pm$ SE via propagation of error for estimates of nuptial feeding a non-nuptial feeding groups: [1.47; 8.32]).
 Points show where the 95% confidence interval exceeds 0 for female choosiness (red) and male search (blue).
@@
 This occurs because these values result in a $\\gamma$ above the fitness threshold necessary for selection to favour male search of nuptial gifts (blue line) and female choosiness (red line).
-Approximately 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction.
 The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
+In each time step, approximately 3000 total pair-wise interactions occurred ($R = 6$).
 Female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the [0.2, 2.0], respectively, were used.

### 2024-06-02 ms_refs_fixed.tex
Make some edits according to reviewer comments on the Results

@@
 sex at a rate of \(R/2\) if the ratio of males to females in the mating
-pool \(\beta\) is equal. More generally, males will be encountered at a
-rate of \(R\beta/(\beta+1)\), and females will be encountered at a rate
-of \(R/(\beta+1)\). An example of how the structure of the time-in
+pool (\(\beta\)) is equal. More generally, males will be encountered at
+a rate of \(R\beta/(\beta+1)\), and females will be encountered at a
+rate of \(R/(\beta+1)\). An example of how the structure of the time-in
 time-out model applies to a system with nuptial gift-giving is given in
@@
 above which males and females are favoured by selection to search for
-nuptial gifts and exhibit choosiness for nuptial gifts, respectively. We
-show (see Methods) that the initial threshold value of \(\gamma\)
-(\(\gamma_{\mathrm{m}}\)) necessary for males to increase their fitness
-by investing time searching for a nuptial gift (time that could
-otherwise be spent searching for a mate) is,
+mates with nuptial gifts and exhibit choosiness for nuptial gifts,
+respectively. We show (see Methods) that the initial threshold value of
+\(\gamma\) (\(\gamma_{\mathrm{m}}\)) necessary for males to increase
+their fitness by investing time searching for a nuptial gift (time that
+could otherwise be spent searching for a mate) is,
 
@@
 Inequality 3 shows that as offspring processing time
-(\(T_{\mathrm{f}}\)), mate encounter rate (\(R\beta / (\beta + 1)\)),
-and the probability of a male finding a nuptial gift
+(\(T_{\mathrm{f}}\)), mate encounter rate (\(R\beta / (\beta + 1)\)), or
+the probability of a male finding a nuptial gift
 (\(1 - \exp(-T_{\mathrm{m}}/\alpha)\) ) decreases, the threshold value
@@
 \caption{Fitness thresholds above which males increase their fitness by
-searching for nuptial gifts (blue line; Eq. 2) and females increase
-their fitness by rejecting males that do not offer gifts (red line; Eq.
+searching for nuptial gifts (blue lines; Eq. 2) and females increase
+their fitness by rejecting males that do not offer gifts (red lines; Eq.
 3). Parameter space includes areas in which males do not search for
@@
 are not choosy (B), females would be choosy but males do not search (C),
-and males search and females are choosy (D). Arrows indicate the effect
-of increasing interaction rate (\(R\)), female time-out (\(T_{f}\)), and
-male search time (\(T_{m}\)). As an example, trajectories for
-\(T_{f} = 2\), and \(T_{m} = \alpha\) are shown for values of \(R=2\)
-(panel a) and \(R = 1\) (panel b). Females are assumed to be the choosy
-sex, which is maintained as long as \(\alpha < T_{f}\).}
+and males search and females are choosy (D). Arrows in panel a indicate
+the effect of increasing interaction rate (\(R\)), female time-out
+(\(T_{\mathrm{f}}\)), and male search time (\(T_{\mathrm{m}}\)). As an
+example, trajectories for \(T_{\mathrm{f}} = 2\), and
+\(T_{\mathrm{m}} = \alpha\) are shown for values of \(R=2\) (panel a)
+and \(R = 1\) (panel b). Females are assumed to be the choosy sex, which
+is maintained as long as \(\alpha < T_{\mathrm{f}}\).}
 \end{figure}
@@
 search of nuptial gifts in males and choosiness for nuptial gifts in
-females (Figure 2). Consequently, the modelling framework gives a
+females (Figure 2a). Consequently, the modelling framework gives a
 description of the conditions under which nuptial gift-giving is
-expected to occur (Figure 2, Zone D) and the conditions under which only
-selection for male searching (Figure 2, Zone B) or female choosiness
-(Figure 2, Zone C) are predicted. These results therefore highlight the
-potential for sexual conflict over nuptial gift-giving.
+expected to occur (Figure 2a, Zone D) and the conditions under which
+only selection for male searching (Figure 2a, Zone B) or female
+choosiness (Figure 2a, Zone C) are predicted. These results therefore
+highlight the potential for sexual conflict over nuptial gift-giving.
 
@@
 
-We use an individual-based model (IBM) to simulate the evolution of
+We used an individual-based model (IBM) to simulate the evolution of
 nuptial gift-giving and female choosiness from an ancestral condition in
@@
 
-The rates at which males encounter females \(R_{\mathrm{m}}\) and
-females encounter males with nuptial gifts \(R_{\mathrm{f,G}}\) are
-calculated directly from the IBM, thereby modelling how these rates
-might be estimated from empirical data, so the male threshold for
-increasing fitness by searching is,
+The rates at which males encounter females \(R_{\mathrm{f},\mathrm{m}}\)
+and females encounter males with nuptial gifts
+\(R_{\mathrm{m_{G}}, \mathrm{f}}\) are calculated directly from the IBM,
+thereby modelling how these rates might be estimated from empirical
+data, so the male threshold for increasing fitness by searching is,
 
 \begin{equation}
-\gamma_{\mathrm{m, IBM}} > \alpha R_{\mathrm{m}}.
+\gamma_{\mathrm{m, IBM}} > \alpha R_{\mathrm{f},\mathrm{m}}.
 \end{equation}
@@
 \begin{equation}
-\gamma_{\mathrm{f, IBM}} > \frac{1}{T_{\mathrm{f}}R_{\mathrm{f,G}}}.
+\gamma_{\mathrm{f, IBM}} > \frac{1}{T_{\mathrm{f}}R_{\mathrm{m_{G}}, \mathrm{f}}}.
 \end{equation}

### 2024-06-02 ms_refs_fixed.Rmd
Add a paragraph in the Discussion that addresses the similarities and differences between the analytical model and the IBM

@@
 The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-In each time step, approximately 3000 total pair-wise interactions occurred ($R = 6$).
+In each time step, up to 3000 total pair-wise interactions occurred.
 Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 2.0] and [0.1, 2.0], respectively, were used."}
@@
 The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-In each time step, approximately 3000 total pair-wise interactions occurred ($R = 6$).
+In each time step, up to 3000 total pair-wise interactions occurred.
 Female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the [0.2, 2.0], respectively, were used.
@@
 Here, we are defining sexual conflict as occurring when interactions between sexes result in situation where both sexes cannot achieve an optimal outcome simultaneously [@Parker2006].
-As an example, sizable areas of parameter space exists wherein the female optimum would be to exhibit preference for (and receive) nuptial gifts, while the male optimum is to not search for (and give) nuptial gifts (see Figure 2, Zone C).
+As an example, sizable areas of parameter space exists wherein the female optimum would be to exhibit preference for (and receive) nuptial gifts, while the male optimum is to not search for (and give) nuptial gifts (see Figure 2a, Zone C).
+This will lead to mate encounters in which gift-less males will benefit from mating, but females will not.
 In many systems, ecological variables such as search time required to find a nuptial gift will likely depend on prey abundance,  which can vary substantially with time in some species with nuptial gift-giving [@Ghislandi2018].
@@
 Similarly the IBM model seems to suggest that a fitness benefit of approximately 50\% is required (see Figure 3). 
-However, it is important to point out that these thresholds depend on multiple parameters.
-For example, if female processing time ($T_{\mathrm{f}}$) is high, the female threshold for choosiness with respect to $\gamma$ drops such that male search and female choosiness are favoured at lower $\gamma$ (see Supporting formation S1).
-If $T_{f}$ is sufficiently high, then an initially rare gift-giving trait might therefore be favoured by selection even if the fitness benefit of a nuptial gift is low.
-The effect that nuptial gifts have on fitness might vary across systems, or even populations.
+However, it is important to recognise that these thresholds depend on multiple parameters.
+For example, if female processing time ($T_{\mathrm{f}}$) is high, the female threshold for choosiness with respect to $\gamma$ drops such that male search and female choosiness are favoured at lower $\gamma$ (see Supporting Information S2).
+If $T_{\mathrm{f}}$ is sufficiently high, then an initially rare gift-giving trait might be favoured by selection even if the fitness benefit of a nuptial gift is low.
+The effect that nuptial gifts have on fitness might vary across species, or even populations.
 Effects on female fecundity have been estimated in crickets, fireflies, butterflies, and spiders, but these estimates vary considerably between species suggesting a large positive effect to no effect at all [@Bergstrom2002; @Gao2019; @Maxwell2018; @Rooney2002].
+
+We modelled the evolution of nuptial gift-giving using both a mathematical model and an individual-based model.
+Our mathematical model makes simple assumptions about the relationship between nuptial gift search time ($\alpha$), conspecific encounter rate ($R$), female processing time ($T_{\mathrm{f}}$), and the fitness increment of a nuptial gift for offspring fitness ($\gamma$).
+It then derives the threshold $\gamma$ values above which males increase their fitness by searching ($T_{\mathrm{m}} > 0$) for a nuptial gift ($\gamma_{\mathrm{m}}$) and females increase their fitness by choosing to reject males without gifts ($\gamma_{\mathrm{f}}$).
+In contrast, our IBM models individuals over discrete time steps, and key processes of nuptial gift acquisition, conspecific encounters, and female processing are stochastic and varying among individuals.
+The mathematical model and IBM make qualitatively identical predictions (compare Figure 2b versus Figure 3), but differences between the two models inevitably lead to quantitative differences for $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$ thresholds.
+For example, $\gamma_{\mathrm{f}}$ increased more rapidly with increasing $\alpha$ in the IBM compared to the analytical model.
+Some differences are expected to occur due to stochastic effects inherent to IBMs [e.g., @Wilson2003].
+Other differences are more likely caused by more subtle assumptions between, and limitations of, the two models.
+In general, the IBM did not do a good job of controlling for conspecific interaction rate, making it difficult to directly compare $R$ between models.
+The IBM also allowed for coevolution between male search and female choosiness (Figure 3), which was not allowed in the analytical model (Figure 2).
+It was not our goal to exactly recover the quantitative predictions of the analytical model in our IBM.
+Future development of the IBM could further bridge the gap between models while also developing new theory on how aspects of the system such as explicit space, individual life history, or genetics affect the evolution of nuptial gift-giving behaviour.
+
+Nuptial gift-giving theory
+--------------------------------------------------
 
@@
 Recent studies have modelled some frequency-dependent aspect of nuptial gift giving using evolutionary game theory [@MaynardSmith1982; @Vincent2005]. 
-Two such studies formulated a quantitative genetics model to study evolutionarily stable nuptial gift sizes in populations where the female propensity to remate was evolving [@Iwasa2022; @Kamimura2021].
+Two such studies formulated a quantitative genetics model to study evolutionarily stable nuptial gift sizes in populations where the female propensity to re-mate was evolving [@Iwasa2022; @Kamimura2021].
 The results obtained in these studies complement our results by giving equilibrium solutions to the evolutionary stable nuptial gift size, whereas we determine the general conditions under which nuptial gift-giving will evolve as given by the inequalities we derive.

### 2024-06-02 ms_refs_fixed.Rmd
Edit the methods section in response to review and model updates

@@
 
-When modelling nuptial gift evolution, the challenge is to construct a modelling framework that captures the frequency-dependent selection between male nuptial gift-giving and female preference for nuptial gifts, and we do this using a time-in, time-out model.
+When modelling nuptial gift evolution, the challenge is to construct a framework that captures the frequency-dependent selection between male nuptial gift-giving and female choosiness for nuptial gifts, and we do this using a time-in, time-out model.
 Recent studies have modelled some frequency-dependent aspect of nuptial gift giving using evolutionary game theory [@MaynardSmith1982; @Vincent2005]. 
@@
 mirabilis*, males have been shown to reduce the risk of being cannibalised by the female after mating when offering a nuptial gift, such that the nuptial gift may result in a "shield effect", protecting the male [@Toft2016].
+
+Empirical predictions
+--------------------------------------------------
 
@@
 This might make choosiness less costly since it would entail less of an opportunity cost to be choosy, and this could potentially make female preference for nuptial gifts more likely to evolve. 
-Our model also assumes that males search in time out, rather than contribute to parental care, which is likely to be accurate for most systems but not all. 
+Our model also assumes that males search in time-out, rather than contribute to parental care, which is likely to be accurate for most systems but not all. 
 Expanding the model to explore these possibilities would be a worthwhile goal for future research.
+
+Conclusion
+--------------------------------------------------
 
@@
 Here we first present more detail for the derivation of fitness threshold values $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$.
-We then present full details for IBM simulations (see Supporting Information S1). 
+We then present IBM simulations (see Supporting Information S1 for full details). 
 Code for simulations is available on GitHub (see "Data availability").
@@
 After mating, females must spend some time processing offspring ($T_{\mathrm{f}}$). 
-Male time to replenish sperm is assumed to be negligible, but males can spend time out of the mating pool to search for a nuptial gift ($T_{\mathrm{m}}$).
+Male time to replenish sperm is assumed to be negligible, but males can spend time out of the mating pool ($T_{\mathrm{m}}$) to search for a nuptial gift.
 When males return from time-out, they encounter females with some probability that is a function of the rate at which an individual encounters conspecifics ($R$) and the sex ratio ($\beta$; males/females).
@@
 Males with the former strategy continue to search until they find a nuptial gift, while males that do not search will immediately re-enter the mating pool. 
-In this case, time searching for a nuptial gift will come at the cost of mating opportunities but might increase offspring fitness offspring. 
+In this case, time searching for a nuptial gift will come at the cost of mating opportunities but might increase offspring fitness. 
 We therefore need to model the expected length of time $E[T_{\mathrm{m}}]$ spent outside of the mating pool for males that search for nuptial gifts, which is simply $\alpha$. 
@@
 
-The rate at which a focal male that searches for a nuptial gift increases his fitness is therefore the fitness of his offspring $(1 + \gamma)$ divided by expected time spent searching for a nuptial gift ($\alpha$) plus time spent in the mating pool, $(\beta + 1)/R$ (recall that females produce $\lambda$ offspring),
-
-$$W_{m,G} = \lambda \frac{1 + \gamma}{\alpha + \left( \frac{\beta + 1}{R} \right)}.$$
-
-In contrast, a male that does not search for a nuptial gift has offspring with lower fitness, but spends less time outside of the mating pool,
-
-$$W_{m,L} = \lambda \frac{1}{\left(\frac{\beta+1}{R} \right)} = \lambda \frac{R}{\beta + 1}.$$
-
-We can then determine the conditions for which $W_{\mathrm{m},G} > W_{\mathrm{m},L}$, isolating $\gamma$ to find how large of a fitness benefit must be provided by the nuptial gift to make the search cost worthwhile, which simplifies to ineq.
+The rate at which a focal male that searches for a nuptial gift ($\mathrm{M_{G}}$) increases his fitness is therefore the fitness of his offspring $(1 + \gamma)$ divided by expected time spent searching for a nuptial gift ($\alpha$) plus time spent in the mating pool, $(\beta + 1)/R$ (recall that females produce $\lambda$ offspring),
+
+$$W_{\mathrm{M_{G}}} = \lambda \frac{1 + \gamma}{\alpha + \left( \frac{\beta + 1}{R} \right)}.$$
+
+In contrast, a male that does not search for a nuptial gift ($\mathrm{M_{L}}$) has offspring with lower fitness, but spends less time outside of the mating pool,
+
+$$W_{\mathrm{M_{L}}} = \lambda \frac{1}{\left(\frac{\beta+1}{R} \right)} = \lambda \frac{R}{\beta + 1}.$$
+
+We can then determine the conditions for which $W_{\mathrm{M_{G}}} > W_{\mathrm{M_{L}}}$, isolating $\gamma$ to find how large of a fitness benefit must be provided by the nuptial gift to make the search cost worthwhile, which simplifies to ineq.
 2.
@@
 
-$$R_{f,G} = R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right).$$
+$$R_{\mathrm{F_{G}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right).$$
 
@@
 
-$$R_{f,L} = R \left(\frac{\beta}{\beta + 1}\right)\left(e^{-\frac{1}{\alpha}T_{m}}\right).$$
+$$R_{\mathrm{F_{L}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(e^{-\frac{1}{\alpha}T_{m}}\right).$$
 
@@
 
-If $R_{\mathrm{f},G}$ is sufficiently high and $R_{\mathrm{f},L}$ is sufficiently low, then finding a male with a gift will be easier than finding a male without one. 
-Also, the expected time spent in the mating pool before a focal female encounters a male with a gift will be $1/R_{\mathrm{f},G}$, while the expected time spent in the mating pool before a focal female encounters any male will be $1 / (R_{\mathrm{f},G} + R_{\mathrm{f},L})$.
-Finally, the rates at which a female encounters males with and without a gift, $R_{\mathrm{f},G}$ and $R_{\mathrm{f}, L}$, are different from the probabilities that a male encounter has or does not have a gift.
+If $R_{\mathrm{F_{G}}}$ is sufficiently high and $R_{\mathrm{F_{L}}}$ is sufficiently low, then finding a male with a gift will be easier than finding a male without one. 
+Also, the expected time spent in the mating pool before a focal female encounters a male with a gift will be $1/R_{\mathrm{F_{G}}}$, while the expected time spent in the mating pool before a focal female encounters any male will be $1 / (R_{\mathrm{F_{G}}} + R_{\mathrm{F_{L}}})$.
+Finally, the rates at which a female encounters males with and without a gift, $R_{\mathrm{F_{G}}}$ and $R_{\mathrm{F_{L}}}$, are different from the probabilities that a male encounter has or does not have a gift.
 The rate of encounter is no longer relevant in this case because we are assuming that an encounter has occurred. 
@@
 
-$$G = \frac{1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}} = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
+$$P(G) = \frac{1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}} = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
 
@@
 
-$$L = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
+$$P(L) = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
 
@@
 \begin{equation}
-W_{\mathrm{f}, G} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}} + \frac{1}{R_{\mathrm{f},G}}}.
+W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}} + \frac{1}{\mathrm{F_{G}}}.
 \end{equation}
@@
 The top of the right-hand side of Eq. 6 gives the fitness increase, and the bottom gives the total time it takes to obtain this fitness. 
-The $R_{\mathrm{f},G}$ is inverted because it represents the expected time to encountering a male with a gift. 
+The $R_{\mathrm{F_{G}}}$ is inverted because it represents the expected time to encountering a male with a gift. 
 We can expand Eq. 6,
 
-$$W_{\mathrm{f},G} = \lambda \frac{1 + \gamma}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right)}}.$$
+$$W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right)}}.$$
 
@@
 
-$$W_{\mathrm{f},l} = \lambda \frac{\left(1 + \gamma\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right) + e^{-\frac{1}{\alpha}T_{m}}}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)}}.$$
-
-We then evaluate the conditions under which $W_{\mathrm{f}, G} > W_{\mathrm{f}, L}$. 
-We isolate $\gamma$ to determine how much offspring fitness must be increase to make choosiness beneficial ($\gamma_{\mathrm{f}}$),
+$$W_{\mathrm{F_{G,L}}} = \lambda \frac{\left(1 + \gamma\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)}}.$$
+
+We then evaluate the conditions under which $W_{\mathrm{F_{G}}} > W_{\mathrm{F_{G,L}}}$. 
+We isolate $\gamma$ to determine how much offspring fitness must be increased to make choosiness beneficial ($\gamma_{\mathrm{f}}$),
 
@@
 We assume that the sex ratio is equal upon maturation. 
-Given this, Kokko and Monaghan [@Kokko2001] show that the operational sex ratio depends on the probability of finding an individual in 'time in',
+Given this, @Kokko2001 show that the operational sex ratio depends on the probability of finding an individual in time-in,
 
@@
 
-In Eq. 8, $P_{IM}(t)$ and $P_{IF}(t)$ are the probabilities of finding a male and female in 'time in', respectively. 
+In Eq. 8, $P_{IM}(t)$ and $P_{IF}(t)$ are the probabilities of finding a male and female in time-in, respectively. 
 There is no closed form solution to the operational sex ratio, so we used recursion to calculate $\beta$ values for a given $T_{\mathrm{f}}$, $T_{\mathrm{m}}$, and $R$ (see Supporting Information S4),
@@
 We formulate an individual-based simulation model to test whether the predictions made by the analytical time-in time-out model are qualitatively the same under a similar simulation model. 
-We use the individual-based model to test whether the prediction hold in finite populations (see Supporting Information S6). 
+We use the individual-based model to test whether the prediction hold in finite populations. 
 The IBM was written in C. 
-All details of the initialisation, parameterisation and the specific simulations which we run, are described in the supporting information (see Supporting Information S1).
+All details of the initialisation, parameterisation and the specific simulations which we run, are described in Supporting Information S1.
 
 We use available experimental data on the effect of nuptial gifts on female offspring production to estimate the key parameter $\gamma$ (fitness increment from nuptial gift) and conducted a series of simulations where $\gamma$ was parameterised using this estimated value.
-Details of the estimation of $\gamma$ are described in the supporting information (see Supporting Information S5).
+Details of the estimation of $\gamma$ are described in Supporting Information S5.
+Separate evolution of male search and female choice (i.e., without co-evolution) is simulated in Supporting Information S6.
 
@@
 
-**Data availability:** The simulation software was implemented in C and the full source code is available at https://github.com/bradduthie/Pisaura.
+**Data availability:** The simulation software was implemented in C and the full source code is available at https://github.com/bradduthie/nuptial_gift_evolution.
 
@@
 Individuals are assigned unique IDs, and each is assigned to be female with a probability of $0.5$, else male. 
-Each individual $i$ is initialised with a starting value of female offspring processing time ($T^{i}_{\mathrm{f}}$), rejection rate for females ($\rho^{i}$), and male search time ($T^{i}_{\mathrm{m}}$).
+Each individual $i$ is initialised with a starting value of female offspring processing time ($T^{i}_{\mathrm{f}}$), rejection probability of gift-less males ($\rho^{i}$), and male search time ($T^{i}_{\mathrm{m}}$).
 For all simulations, initialised values are set to $T^{i}_{\mathrm{f}} = 2$, $\rho^{i} = 0$, and $T^{i}_{\mathrm{m}} = 0$. 
@@
 
-During time out, a focal female $i$ will produce $\lambda_{i} \sim Poisson(\lambda)$ offspring if no nuptial gift was provided or $\lambda_{i} \sim Poisson(\lambda + \gamma)$ if a gift was provided. 
+During time-out, a focal female $i$ will produce $\lambda_{i} \sim Poisson(\lambda)$ offspring if no nuptial gift was provided or $\lambda_{i} \sim Poisson(\lambda + \gamma)$ if a gift was provided. 
 Females remain outside of the mating pool to process offspring for $T^{i}_{\mathrm{f}}$ time steps, where $T^{i}_{\mathrm{f}}$ is sampled randomly for each individual from a Poisson distribution with a rate parameter of $T_{\mathrm{f}}$, $T^{i}_{\mathrm{f}} \sim Poisson(T_{\mathrm{f}})$.
@@
 A neutral evolving trait was also modelled to ensure that the code functioned as intended, and processes were compartmentalised into individual functions to facilitate code testing. 
-All code is publicly available on GitHub (https://github.com/bradduthie/Pisaura).
+All code is publicly available on GitHub (https://github.com/bradduthie/nuptial_gift_evolution).
 
@@
 
-We conducted a sensitivity analysis of the effect of the mortality parameters $\mu_{\mathrm{in}}$ and $\mu_{\mathrm{out}}$ (the probability of mortality in time in and time out, respectively, which we assumed to be equal for all individuals) on the evolution of male search and female choice using the IBM (See S1).
+We conducted a sensitivity analysis of the effect of the mortality parameters $\mu_{\mathrm{in}}$ and $\mu_{\mathrm{out}}$ (the probability of mortality in time-in and time-out, respectively, which we assumed to be equal for all individuals) on the evolution of male search and female choice using the IBM (See S1).
 The results revealed no correlation between the value of the mortality parameters and the evolution of male search or female choice (Fig. S2.1).
@@
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.1: Evolution of both male search (blue) and female choice (red) under different combinations of the mortality rates $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$ (mortality in time in and out, respectively).
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.1: Evolution of both male search (blue) and female choice (red) under different combinations of the mortality rates $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$ (mortality in time-in and out, respectively).
 The y-axis is the threshold fitness that leads to evolution of male search (blue) or female choice (red).
@@
 Consequently, the operational sex ratio $\beta$ will be a function of $R$, $T_{f}$, and $T_{m}$ because these parameters determine the density of females and males in the mating pool versus outside of the mating pool.
-We start with the definition of $\beta$ as being the probability of finding an individual in 'time in' [@Kokko2001],
+We start with the definition of $\beta$ as being the probability of finding an individual in time-in [@Kokko2001],
 

### 2024-06-03 ms_refs_fixed.Rmd
Edit the supporting information to update based on reviewer comments and some minor corrections given the IBM

@@
 \begin{equation}
-W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}} + \frac{1}{\mathrm{F_{G}}}.
+W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}}} + \frac{1}{\mathrm{F_{G}}}.
 \end{equation}
@@
 \begin{equation}
-\gamma_{\mathrm{f}} > \frac{1}{ T_{f} R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right)}.
+\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}}} R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right).
 \end{equation}
@@
 |---------------------------------------------------------------|------|
-| S1: Description of the individual-based simulation model      |  26  |
-| S2: Sensitivity analysis of mortality parameters in IBM       |  29  |
-| S3: Alternative derivation of male fitness threshold          |  31  |
-| S4: Operational sex ratio                                     |  33  |
-| S5: Estimation of key model parameter using experimental data |  35  |
-| S6: Separate evolution of male search and female choice       |  36  |
+| S1: Description of the individual-based simulation model      |  27  |
+| S2: Sensitivity analysis of mortality parameters in IBM       |  30  |
+| S3: Alternative derivation of male fitness threshold          |  41  |
+| S4: Operational sex ratio                                     |  43  |
+| S5: Estimation of key model parameter using experimental data |  45  |
+| S6: Separate evolution of male search and female choice       |  46  |
 
@@
 Females will enter the mating pool after processing offspring, and males will enter it after searching for nuptial gifts (see 'Time-out' below). 
-A fixed number of $\Psi = N\psi$ interactions between individuals occur in a single time step, where $N$ is population size and $\psi$ is a scaling parameter. 
-Since an interaction includes two conspecifics, each individual is expected to encounter a conspecific $2\psi$ times per time step (i.e., $R = 2\psi$).
-For each interaction, two individuals are randomly sampled, each with equal probability. 
-If both sampled individuals are within the mating pool and of different sexes, then a mating encounter occurs. 
+Up to $\Psi = N\psi$ interactions between individuals can occur in a single time step, where $N$ is population size and $\psi$ is a scaling parameter. 
+In each time step, $\Psi$ pairs of individuals are selected at random to interact.
+For each interaction, two different individuals are randomly selected from the population with equal probability.
+If the selected individuals are of different sexes, and both are in the mating pool, then a mating encounter occurs.
 If the male does not have a nuptial gift, then the female will reject him with a probability of $\rho^{i}$; if rejection occurs, then both individuals stay in the mating pool. 
@@
 
-During time-out, a focal female $i$ will produce $\lambda_{i} \sim Poisson(\lambda)$ offspring if no nuptial gift was provided or $\lambda_{i} \sim Poisson(\lambda + \gamma)$ if a gift was provided. 
-Females remain outside of the mating pool to process offspring for $T^{i}_{\mathrm{f}}$ time steps, where $T^{i}_{\mathrm{f}}$ is sampled randomly for each individual from a Poisson distribution with a rate parameter of $T_{\mathrm{f}}$, $T^{i}_{\mathrm{f}} \sim Poisson(T_{\mathrm{f}})$.
+During time-out, offspring production and time outside of the mating pool are realised for each female by sampling from a Poisson distribution.
+A focal female $i$ will produce $Poisson(\lambda)$ offspring if no nuptial gift was provided or $Poisson(\lambda + \gamma)$ if a gift was provided. 
+Females remain outside of the mating pool to process offspring for $Poisson(T^{i}_{\mathrm{f}})$ time steps. 
 Offspring are added to the population immediately, with $\rho^{i}$ and $T^{i}_{\mathrm{m}}$ values that are the average of each parent plus some normally distributed error $\epsilon_{R}$ and $\epsilon_{T_{\mathrm{m}}}$.
@@
 
-$$T^{\mathrm{offspring}}_{\mathrm{m}} \sim N\left(\frac{T^{\mathrm{mother}}_{\mathrm{m}}  + T^{\mathrm{father}}_{\mathrm{m}}}{2}, \epsilon_{T_{\mathrm{m}}} \right).$$
+$$T^{\mathrm{offspring}}_{\mathrm{m}} \sim \frac{T^{\mathrm{mother}}_{\mathrm{m}}  + T^{\mathrm{father}}_{\mathrm{m}}}{2} + N\left(0, \epsilon_{T_{\mathrm{m}}} \right).$$
 
@@
 Offspring sex is randomly assigned with equal probability as female or male. 
-Female offspring are immediately placed in the mating pool, and male offspring are out of the mating pool to search for nuptial gifts. 
+Female offspring are immediately placed in the mating pool, and male offspring are out of the mating pool to potentially search for nuptial gifts. 
 After a female has spent $T^{i}_{\mathrm{f}}$ time steps outside the mating pool, she will re-enter it.
 
-A focal male $i$ outside the mating pool will enter it if they have searched for a fixed number of $T^{i}_{\mathrm{m}}$ time steps, which is also sampled randomly from a Poisson distribution, $T^{i}_{\mathrm{m}} \sim Poisson(T_{\mathrm{m}})$.
+A focal male $i$ outside the mating pool will enter it if he has searched for a fixed number of $T^{i}_{\mathrm{m}}$ time steps, which is also sampled randomly from a Poisson distribution, $Poisson(T^{i}_{\mathrm{m}})$.
 If $T^{i}_{\mathrm{m}} = 0$, then the male immediately returns to the mating pool (in the same time step). 
-If $T^{i}_{\mathrm{m}} > 0$, then the male must wait outside the mating pool for $T^{i}_{\mathrm{m}}$ time steps, but will enter the mating pool with a nuptial gift with a probability,
-
-$$G^{i} = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.$$
+If $T^{i}_{\mathrm{m}} > 0$, then the male must wait outside the mating pool for $Poisson(T^{i}_{\mathrm{m}})$ time steps, but will enter the mating pool with a nuptial gift with a probability,
+
+$$P(G^{i}) = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.$$
 
@@
 
-At the end of time step, mortality occurs first with a fixed probability for all adults in the population, then with a probability caused by carrying capacity $K$ applied to all individuals (adults and offspring).
+At the end of each time step, mortality occurs first with a fixed probability for all adults in the population, then with a probability caused by carrying capacity $K$ applied to all individuals (adults and offspring).
 Mortality occurs in each time step with a fixed probability of $\mu$ regardless of the sex of the individual or its position in or out of the mating pool. 
@@
 Simulations ran for $t_{max} = 40000$ time steps. 
-We set $T_{\mathrm{f}} = 2$, $\psi = 3$, and $\lambda = 1$ for all simulations, and we simulated across a range of $\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}$ and $\gamma = \{0, 0.1, ..., 1.9, 2.0\}$ parameter values for 1600 replicates.
+We set $T_{\mathrm{f}} = 2$, $\psi = 3$, and $\lambda = 1$ for all simulations, and we simulated across a range of $\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}$ and $\gamma = \{0, 0.1, ..., 1.9, 2.0\}$ parameter values for 3200 replicates.
 Summary statistics for mean trait values, population size, sex ratios, proportion of females and males in and out of the mating pool, and mean number of encounters per female and male within the mating pool were all calculated in the last time step.
@@
 
-A set of simulations with a value of $\gamma$ calculated from empirical data was also conducted. 
+A set of simulations with a value of $\gamma$ calculated from empirical data was also conducted (100 replicates). 
 Here, $\gamma$ was parameterised using data on egg production as a function of eating nuptial gifts (see below). 
@@
 
-**Mortality**
+We investigated the sensitivity of our results to individual mortality during time-in ($\mu_{\mathrm{in}}$) and time-out ($\mu_{\mathrm{out}}$), female processing time ($T_{\mathrm{f}}$), potential for interactions between conspecifics ($\psi$), and initialised male search time ($T_{\mathrm{m}}$).
+Across all of these simulations, there were challenges with statistical power.
+Evidence for the evolution of male search (blue points in figures) and female choosiness (red points in figures) was determined by the lower 95\% bootstrapped confidence interval of $T_{\mathrm{m}}$ and $T_{\mathrm{f}}$ values being greater than zero, respectively.
+This required a lot of replicate simulations in the main text (Figure 3), especially for values just above predicted thresholds and for female choosiness.
+Computation time was a limiting factor, even using a compiled language (C) and with access to a computing cluster.
+Absence of points above threshold values are not necessarily evidence that evolution of male search or female choosiness is not predicted to evolve in these regions of parameter space, but it does indicate that evolution of these traits is not necessarily assured given the stochasticity inherent to the IBM.
+Additional simulations can be conducted using the C code in the 'src' folder of the GitHub repository (https://github.com/bradduthie/nuptial_gift_evolution).
+Below, we explain the parameter values used in the sensitivity analysis in more detail.
+
+*Mortality*
 
@@
 The results revealed no correlation between the value of the mortality parameters and the evolution of male search or female choice (Fig. S2.1).
+
+*Female processing time*
+
+We also conducted a sensitivity analysis of female processing time $T_{\mathrm{f}}$. 
+To do this, we ran simulations at default values, but with $T_{\mathrm{f}} = 0.4$ (Figure S4.2) and $T_{\mathrm{f}} = 10.0$ (Figures S4.3).
+
+*Interactions between conspecifics*
+
+We conducted a sensitivity analysis on the encounter rate between conspecifics ($R$) by varying the value of $\psi$ (see S1).
+Under default simulations, $\psi = 3$.
+We also ran simulations in which $\psi = 1$ (Figure S4.4), $\psi = 2$ (Figure S4.5), $\psi = 4$ (Figure S4.6), and $\psi = 6$ (Figure S4.7), with all other parameters being set to default values.
+
+*Initialised male search time*
+
+Lastly, we conducted a sensitivity analysis on initialised male search time ($T_{\mathrm{m}}$).
+To do this, we ran simulations at default values, but initialised all males at $T_{\mathrm{m}} = 0.5$ (Figure S4.8) or $T_{\mathrm{m}} = 2.5$ (S4.9). 
+Note that under these initialisation conditions, it no longer makes sense to test whether or not $T_{\mathrm{m}}$ evolves to positive values, so we do not show predicted male search thresholds and focus only on female choosiness.
+Interestingly, while predictions given initialised $T_{\mathrm{m}} = 0.5$ are quite close for female choosiness thresholds, female choosiness does not appear to evolve given $T_{\mathrm{m}} = 2.5$.
+This might be due to low selection pressure to reject males without gifts due to their low frequency.
+In other words, while females would benefit from a strategy of rejecting gift-less males, a lack of realised encounters with gift-less males preclude the evolution of sustained selection for choosiness.
+
+\clearpage
 
@@
 
-**Female processing time**
-
-We also conducted a sensitivity analysis of female processing time $T_{\mathrm{f}}$. 
-To do this, we ran simulations at default values, but with $T_{\mathrm{f}} = 0.4$ (Figure S4.2) and $T_{\mathrm{f}} = 10.0$ (Figures S4.3).
+\clearpage
 
@@
 Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Approximately 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction.
+Up to 3000 interactions occur between individuals in each time step ($\\psi = 3$), potentially resulting in a mating interaction.
 The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
@@
 
+\clearpage
+
 \captionsetup{labelformat=empty}
@@
 
-**Interactions between conspecifics**
-
-We conducted a sensitivity analysis on the encounter rate between conspecifics ($R$) by varying the value of $\psi$, where $R = 2\psi$ (see S1).
-Under default simulations, $\psi = 3$ and $R = 6$.
-We also ran simulations in which $\psi = 1$ (Figure S4.4) and $\psi = 6$ (Figure S4.5), with all other parameters being set to default values.
+\clearpage
 
@@
 Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Approximately 1000 interactions occur between individuals in each time step, potentially resulting in a mating interaction.
+Up to 1000 interactions occur between individuals in each time step ($\\psi = 1$), potentially resulting in a mating interaction.
 The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
@@
 
+\clearpage
+
 \captionsetup{labelformat=empty}
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.5 ($\\psi = 6$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.5 ($\\psi = 2$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
 Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
@@
 Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Approximately 6000 interactions occur between individuals in each time step, potentially resulting in a mating interaction.
+Up to 2000 interactions occur between individuals in each time step ($\\psi = 2$), potentially resulting in a mating interaction.
 The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
@@
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.5 ($\\psi = 6$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.6 ($\\psi = 4$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
 Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
@@
 Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Approximately 6000 interactions occur between individuals in each time step, potentially resulting in a mating interaction.
+Up to 4000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 4$).
 The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
@@
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.5 ($\\psi = 6$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.7 ($\\psi = 6$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
 Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
@@
 Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Approximately 6000 interactions occur between individuals in each time step, potentially resulting in a mating interaction.
+Up to 6000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 6$).
 The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
@@
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Caption here"}
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.8 ($T_{\\mathrm{m}} = 0.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
+Each point includes data from 1600 replicate simulations with identical starting conditions.
+The red line shows the threshold above which the mathematical model predicts that females should be choosy (male thresholds for search are not shown because simulations were initialised with males already searching for nuptial gifts).
+Up to 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 3$).
+The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
+Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
 SUMM_Tm05   <- read.csv("inst/SI_Tm_0pt5.csv");
@@
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Caption here"}
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.9 ($T_{\\mathrm{m}} = 2.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
+Each point includes data from 1600 replicate simulations with identical starting conditions.
+The red line shows the threshold above which the mathematical model predicts that females should be choosy (male thresholds for search are not shown because simulations were initialised with males already searching for nuptial gifts).
+Up to 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 3$).
+The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
+Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
 SUMM_Tm2p5   <- read.csv("inst/SI_Tm_2pt5.csv");
@@
 
-$$G = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
+$$P(G) = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
 
@@
 
-$$L = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
-
-For simplicity, we assume that the fitness increments to offspring associated with receiving a nuptial gift versus no nuptial gift are $1 + \gamma$ and 1, respectively. 
+$$P(L) = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
+
+We assume that the fitness increments to offspring associated with receiving a nuptial gift versus no nuptial gift are $1 + \gamma$ and 1, respectively. 
 The rate at which males increase their fitness can then be defined as the expected fitness increment from their nuptial gift search divided by $T_{\mathrm{m}}$ plus the time spent in the mating pool waiting to encounter a mate,
 
-$$W_{\mathrm{m}} = \lambda \frac{G\left(1 + \gamma\right) + L}{T_{\mathrm{m}} + \left( \frac{\beta + 1}{R} \right)}.$$
+$$W_{\mathrm{m}} = \lambda \frac{P(G)\left(1 + \gamma\right) + P(L)}{T_{\mathrm{m}} + \left( \frac{\beta + 1}{R} \right)}.$$
 
@@
 
-We assume that the ratio of males to femalesis the same upon individual maturation.
-Consequently, the operational sex ratio $\beta$ will be a function of $R$, $T_{f}$, and $T_{m}$ because these parameters determine the density of females and males in the mating pool versus outside of the mating pool.
+We assume that the ratio of males to females is the same upon individual maturation.
+Consequently, the operational sex ratio $\beta$ will be a function of $R$, $T_{\mathrm{f}}$, and $T_{\mathrm{m}}$ because these parameters determine the density of females and males in the mating pool versus outside of the mating pool.
 We start with the definition of $\beta$ as being the probability of finding an individual in time-in [@Kokko2001],
@@
 
-Estimates showing mean number of offspring produced by female *Pisaura mirabilis* that ate nuptial gifts and females who did not. 
+Estimates showing the mean number of offspring produced by female *Pisaura mirabilis* that ate nuptial gifts and females who did not. 
 Means were calculated with raw data from @Tuni2013a and results are shown $\pm$ SE (Table 1).
@@
 
-Table 1: Estimates showing mean number of offspring produced by female *Pisauras mirabilis* that ate nuptial gifts and females who did not.
+Table 1: Estimates showing mean number of offspring produced by female *P.
+mirabilis* that ate nuptial gifts and females who did not.
 Means were calculated with raw data from @Tuni2013a and results are shown $\pm$ SE.
@@
 We used the individual-based simulation model (see Supporting Information S1) to unpack the effect of coevolution on the evolution of male search and female choice. 
-Specifically, we replicated the simulations shown in the main text under the condition where only one trait at a time was allowed to evolve and studied how this affected the trait evolution.
+Here we replicated the simulations shown in the main text under the condition where only one trait at a time was allowed to evolve and studied how this affected the trait evolution.
 
 First, we submitted a set of simulations wherein male search did not evolve, but was fixed at different values (see Fig. S6.1). 
-Next, we ran the same set of simulations wherein male search evolved, but female choice was not possible). 
+Next, we ran the same set of simulations wherein male search evolved, but female choice was not possible. 
 The results thus show how each trait evolves in the absence of any coevolution (Fig. S6.1).

### 2024-06-03 ms_refs_fixed.tex
Edit the supporting information to update based on reviewer comments and some minor corrections given the IBM

@@
 
-The rates at which males encounter females \(R_{\mathrm{f},\mathrm{m}}\)
-and females encounter males with nuptial gifts
-\(R_{\mathrm{m_{G}}, \mathrm{f}}\) are calculated directly from the IBM,
-thereby modelling how these rates might be estimated from empirical
-data, so the male threshold for increasing fitness by searching is,
+The rates at which females are encountered by males
+\(R_{\mathrm{f},\mathrm{m}}\) and males with nuptial gifts
+\(R_{\mathrm{m_{G}}, \mathrm{f}}\) are encountered by females are both
+calculated directly from the IBM, thereby modelling how these rates
+might be estimated from empirical data, so the male threshold for
+increasing fitness by searching is,
 
@@
 time is discrete in the IBM but continuous the analytical model, and in
-the IBM a fitness increment is applied to the focal female in the form
-of birthrate increase rather than offspring; see Supporting Information
-S1 for details). But the predicted thresholds are theoretically
-equivalent and yield predictions that are qualitatively the same (Figure
-3).
+the IBM, a fitness increment is applied to the focal female in the form
+of birthrate increase rather than offspring fitness; see Supporting
+Information S1 for details). But the predicted thresholds are
+theoretically equivalent and yield predictions that are qualitatively
+the same (Figure 3).
 
@@
 with Figure 2). Minor deviations between the analytical model and the
-simulation results are expected due to the finite population size and
-the substantial stochasticity inherent to the simulation model (for
-details, see Supporting Information S1). Approximately 3000 interactions
-occur between individuals in each time step, potentially resulting in a
-mating interaction. The number of individuals in the population remained
-at or near carrying capacity of \(K = 1000\). Expected female processing
-time was set to \(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and
-\(\alpha\) values in the range {[}0.0, 2.0{]} and {[}0.1, 2.0{]},
-respectively, were used.}
+simulation results are expected due to the finite population size, the
+substantial stochasticity inherent to the simulation model, and the
+potential for coevolution (for details, see Supporting Information S1).
+The number of individuals in the population remained at or near carrying
+capacity of \(K = 1000\). In each time step, up to 3000 total pair-wise
+interactions occurred. Expected female processing time was set to
+\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
+the range {[}0.0, 2.0{]} and {[}0.1, 2.0{]}, respectively, were used.}
 \end{figure}
@@
 predict the evolution of searching in the IBM across \(\alpha\) values,
-and the female threshold \(\gamma_{\mathrm{f, IBM}}\) (ineq. 5)
-accurately predicts the evolution of female choice (Figure 3). In other
-words, IBM simulations demonstrate that nuptial gift search in males,
-and choosiness in females, will evolve from an ancestral state of no
+and the female threshold \(\gamma_{\mathrm{f, IBM}}\) (ineq. 5) predicts
+the evolution of female choice (Figure 3). In other words, IBM
+simulations demonstrate that nuptial gift search in males, and
+choosiness in females, will evolve from an ancestral state of no
 searching and no choosiness in similar parameter space (Figure 3) as
-predicted by the analytical model (Figure 2). We further ran the IBM
+predicted by the analytical model (Figure 2b). We further ran the IBM
 with realistic values of \(\gamma\), estimated using data from the
@@
 a nuptial gift fitness increment (\(\gamma\)) that was estimated from
-experimental data for the species \emph{P. mirabilis} (mean
+experimental data for the species \emph{Pisaura mirabilis} (mean
 \(\gamma = 3.29 \pm\) SE via propagation of error for estimates of
@@
 threshold necessary for selection to favour male search of nuptial gifts
-(blue line) and female choosiness (red line). Approximately 3000
-interactions occur between individuals in each time step, potentially
-resulting in a mating interaction. The number of individuals in the
-population remained at or near carrying capacity of \(K = 1000\). Female
-processing time was set to \(T_{\mathrm{f}}=2\) time steps, and
+(blue line) and female choosiness (red line). The number of individuals
+in the population remained at or near carrying capacity of \(K = 1000\).
+In each time step, up to 3000 total pair-wise interactions occurred.
+Female processing time was set to \(T_{\mathrm{f}}=2\) time steps, and
 \(\gamma\) and \(\alpha\) values in the {[}0.2, 2.0{]}, respectively,
@@
 be to exhibit preference for (and receive) nuptial gifts, while the male
-optimum is to not search for (and give) nuptial gifts (see Figure 2,
-Zone C). In many systems, ecological variables such as search time
-required to find a nuptial gift will likely depend on prey abundance,
-which can vary substantially with time in some species with nuptial
-gift-giving (\protect\hyperlink{ref-Ghislandi2018}{Ghislandi \emph{et
-al.}, 2018}). Since several ecological variables likely affect the value
-of these thresholds, our results can be seen as providing some
-formalised description of why nuptial gift-giving only occurs in some
-but not all systems.
+optimum is to not search for (and give) nuptial gifts (see Figure 2a,
+Zone C). This will lead to mate encounters in which gift-less males will
+benefit from mating, but females will not. In many systems, ecological
+variables such as search time required to find a nuptial gift will
+likely depend on prey abundance, which can vary substantially with time
+in some species with nuptial gift-giving
+(\protect\hyperlink{ref-Ghislandi2018}{Ghislandi \emph{et al.}, 2018}).
+Since several ecological variables likely affect the value of these
+thresholds, our results can be seen as providing some formalised
+description of why nuptial gift-giving only occurs in some but not all
+systems.
 
@@
 approximately 50\% is required (see Figure 3). However, it is important
-to point out that these thresholds depend on multiple parameters. For
+to recognise that these thresholds depend on multiple parameters. For
 example, if female processing time (\(T_{\mathrm{f}}\)) is high, the
@@
 that male search and female choosiness are favoured at lower \(\gamma\)
-(see Supporting formation S1). If \(T_{f}\) is sufficiently high, then
-an initially rare gift-giving trait might therefore be favoured by
+(see Supporting Information S2). If \(T_{\mathrm{f}}\) is sufficiently
+high, then an initially rare gift-giving trait might be favoured by
 selection even if the fitness benefit of a nuptial gift is low. The
-effect that nuptial gifts have on fitness might vary across systems, or
+effect that nuptial gifts have on fitness might vary across species, or
 even populations. Effects on female fecundity have been estimated in
@@
 
+We modelled the evolution of nuptial gift-giving using both a
+mathematical model and an individual-based model. Our mathematical model
+makes simple assumptions about the relationship between nuptial gift
+search time (\(\alpha\)), conspecific encounter rate (\(R\)), female
+processing time (\(T_{\mathrm{f}}\)), and the fitness increment of a
+nuptial gift for offspring fitness (\(\gamma\)). It then derives the
+threshold \(\gamma\) values above which males increase their fitness by
+searching (\(T_{\mathrm{m}} > 0\)) for a nuptial gift
+(\(\gamma_{\mathrm{m}}\)) and females increase their fitness by choosing
+to reject males without gifts (\(\gamma_{\mathrm{f}}\)). In contrast,
+our IBM models individuals over discrete time steps, and key processes
+of nuptial gift acquisition, conspecific encounters, and female
+processing are stochastic and varying among individuals. The
+mathematical model and IBM make qualitatively identical predictions
+(compare Figure 2b versus Figure 3), but differences between the two
+models inevitably lead to quantitative differences for
+\(\gamma_{\mathrm{m}}\) and \(\gamma_{\mathrm{f}}\) thresholds. For
+example, \(\gamma_{\mathrm{f}}\) increased more rapidly with increasing
+\(\alpha\) in the IBM compared to the analytical model. Some differences
+are expected to occur due to stochastic effects inherent to IBMs (e.g.,
+\protect\hyperlink{ref-Wilson2003}{Wilson \emph{et al.}, 2003}). Other
+differences are more likely caused by more subtle assumptions between,
+and limitations of, the two models. In general, the IBM did not do a
+good job of controlling for conspecific interaction rate, making it
+difficult to directly compare \(R\) between models. The IBM also allowed
+for coevolution between male search and female choosiness (Figure 3),
+which was not allowed in the analytical model (Figure 2). It was not our
+goal to exactly recover the quantitative predictions of the analytical
+model in our IBM. Future development of the IBM could further bridge the
+gap between models while also developing new theory on how aspects of
+the system such as explicit space, individual life history, or genetics
+affect the evolution of nuptial gift-giving behaviour.
+
+\hypertarget{nuptial-gift-giving-theory}{%
+\subsection{Nuptial gift-giving
+theory}\label{nuptial-gift-giving-theory}}
+
 When modelling nuptial gift evolution, the challenge is to construct a
-modelling framework that captures the frequency-dependent selection
-between male nuptial gift-giving and female preference for nuptial
-gifts, and we do this using a time-in, time-out model. Recent studies
-have modelled some frequency-dependent aspect of nuptial gift giving
-using evolutionary game theory
-(\protect\hyperlink{ref-MaynardSmith1982}{Maynard Smith, 1982};
-\protect\hyperlink{ref-Vincent2005}{Vincent \& Brown, 2005}). Two such
-studies formulated a quantitative genetics model to study evolutionarily
-stable nuptial gift sizes in populations where the female propensity to
-remate was evolving (\protect\hyperlink{ref-Kamimura2021}{Kamimura
-\emph{et al.}, 2021}; \protect\hyperlink{ref-Iwasa2022}{Iwasa \&
-Yamaguchi, 2022}). The results obtained in these studies complement our
-results by giving equilibrium solutions to the evolutionary stable
-nuptial gift size, whereas we determine the general conditions under
-which nuptial gift-giving will evolve as given by the inequalities we
-derive.
+framework that captures the frequency-dependent selection between male
+nuptial gift-giving and female choosiness for nuptial gifts, and we do
+this using a time-in, time-out model. Recent studies have modelled some
+frequency-dependent aspect of nuptial gift giving using evolutionary
+game theory (\protect\hyperlink{ref-MaynardSmith1982}{Maynard Smith,
+1982}; \protect\hyperlink{ref-Vincent2005}{Vincent \& Brown, 2005}). Two
+such studies formulated a quantitative genetics model to study
+evolutionarily stable nuptial gift sizes in populations where the female
+propensity to re-mate was evolving
+(\protect\hyperlink{ref-Kamimura2021}{Kamimura \emph{et al.}, 2021};
+\protect\hyperlink{ref-Iwasa2022}{Iwasa \& Yamaguchi, 2022}). The
+results obtained in these studies complement our results by giving
+equilibrium solutions to the evolutionary stable nuptial gift size,
+whereas we determine the general conditions under which nuptial
+gift-giving will evolve as given by the inequalities we derive.
 
@@
 
+\hypertarget{empirical-predictions}{%
+\subsection{Empirical predictions}\label{empirical-predictions}}
+
 The simulations parameterised with an experimentally estimated value of
@@
 female preference for nuptial gifts more likely to evolve. Our model
-also assumes that males search in time out, rather than contribute to
+also assumes that males search in time-out, rather than contribute to
 parental care, which is likely to be accurate for most systems but not
@@
 worthwhile goal for future research.
+
+\hypertarget{conclusion}{%
+\subsection{Conclusion}\label{conclusion}}
 
@@
 threshold values \(\gamma_{\mathrm{m}}\) and \(\gamma_{\mathrm{f}}\). We
-then present full details for IBM simulations (see Supporting
-Information S1). Code for simulations is available on GitHub (see ``Data
+then present IBM simulations (see Supporting Information S1 for full
+details). Code for simulations is available on GitHub (see ``Data
 availability'').
@@
 (\(T_{\mathrm{f}}\)). Male time to replenish sperm is assumed to be
-negligible, but males can spend time out of the mating pool to search
-for a nuptial gift (\(T_{\mathrm{m}}\)). When males return from
-time-out, they encounter females with some probability that is a
+negligible, but males can spend time out of the mating pool
+(\(T_{\mathrm{m}}\)) to search for a nuptial gift. When males return
+from time-out, they encounter females with some probability that is a
 function of the rate at which an individual encounters conspecifics
@@
 for a nuptial gift will come at the cost of mating opportunities but
-might increase offspring fitness offspring. We therefore need to model
-the expected length of time \(E[T_{\mathrm{m}}]\) spent outside of the
+might increase offspring fitness. We therefore need to model the
+expected length of time \(E[T_{\mathrm{m}}]\) spent outside of the
 mating pool for males that search for nuptial gifts, which is simply
@@
 The rate at which a focal male that searches for a nuptial gift
-increases his fitness is therefore the fitness of his offspring
-\((1 + \gamma)\) divided by expected time spent searching for a nuptial
-gift (\(\alpha\)) plus time spent in the mating pool, \((\beta + 1)/R\)
-(recall that females produce \(\lambda\) offspring),
-
-\[W_{m,G} = \lambda \frac{1 + \gamma}{\alpha + \left( \frac{\beta + 1}{R} \right)}.\]
-
-In contrast, a male that does not search for a nuptial gift has
-offspring with lower fitness, but spends less time outside of the mating
-pool,
-
-\[W_{m,L} = \lambda \frac{1}{\left(\frac{\beta+1}{R} \right)} = \lambda \frac{R}{\beta + 1}.\]
+(\(\mathrm{M_{G}}\)) increases his fitness is therefore the fitness of
+his offspring \((1 + \gamma)\) divided by expected time spent searching
+for a nuptial gift (\(\alpha\)) plus time spent in the mating pool,
+\((\beta + 1)/R\) (recall that females produce \(\lambda\) offspring),
+
+\[W_{\mathrm{M_{G}}} = \lambda \frac{1 + \gamma}{\alpha + \left( \frac{\beta + 1}{R} \right)}.\]
+
+In contrast, a male that does not search for a nuptial gift
+(\(\mathrm{M_{L}}\)) has offspring with lower fitness, but spends less
+time outside of the mating pool,
+
+\[W_{\mathrm{M_{L}}} = \lambda \frac{1}{\left(\frac{\beta+1}{R} \right)} = \lambda \frac{R}{\beta + 1}.\]
 
 We can then determine the conditions for which
-\(W_{\mathrm{m},G} > W_{\mathrm{m},L}\), isolating \(\gamma\) to find
-how large of a fitness benefit must be provided by the nuptial gift to
-make the search cost worthwhile, which simplifies to ineq. 2. When this
-inequality holds, males are favoured to search until they find a nuptial
-gift, which would result in an average search time of \(\alpha\). When
-the male trait is continuous (i.e., males search for time period
-\(T_{\mathrm{m}}\)), it can be shown that the same threshold can be
-reached by evaluating the partial derivative of the male fitness
+\(W_{\mathrm{M_{G}}} > W_{\mathrm{M_{L}}}\), isolating \(\gamma\) to
+find how large of a fitness benefit must be provided by the nuptial gift
+to make the search cost worthwhile, which simplifies to ineq. 2. When
+this inequality holds, males are favoured to search until they find a
+nuptial gift, which would result in an average search time of
+\(\alpha\). When the male trait is continuous (i.e., males search for
+time period \(T_{\mathrm{m}}\)), it can be shown that the same threshold
+can be reached by evaluating the partial derivative of the male fitness
 function (Supporting Information S3). Hence, the thresholds are
@@
 
-\[R_{f,G} = R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right).\]
+\[R_{\mathrm{F_{G}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right).\]
 
@@
 
-\[R_{f,L} = R \left(\frac{\beta}{\beta + 1}\right)\left(e^{-\frac{1}{\alpha}T_{m}}\right).\]
+\[R_{\mathrm{F_{L}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(e^{-\frac{1}{\alpha}T_{m}}\right).\]
 
@@
 
-If \(R_{\mathrm{f},G}\) is sufficiently high and \(R_{\mathrm{f},L}\) is
-sufficiently low, then finding a male with a gift will be easier than
-finding a male without one. Also, the expected time spent in the mating
-pool before a focal female encounters a male with a gift will be
-\(1/R_{\mathrm{f},G}\), while the expected time spent in the mating pool
-before a focal female encounters any male will be
-\(1 / (R_{\mathrm{f},G} + R_{\mathrm{f},L})\). Finally, the rates at
-which a female encounters males with and without a gift,
-\(R_{\mathrm{f},G}\) and \(R_{\mathrm{f}, L}\), are different from the
-probabilities that a male encounter has or does not have a gift. The
+If \(R_{\mathrm{F_{G}}}\) is sufficiently high and
+\(R_{\mathrm{F_{L}}}\) is sufficiently low, then finding a male with a
+gift will be easier than finding a male without one. Also, the expected
+time spent in the mating pool before a focal female encounters a male
+with a gift will be \(1/R_{\mathrm{F_{G}}}\), while the expected time
+spent in the mating pool before a focal female encounters any male will
+be \(1 / (R_{\mathrm{F_{G}}} + R_{\mathrm{F_{L}}})\). Finally, the rates
+at which a female encounters males with and without a gift,
+\(R_{\mathrm{F_{G}}}\) and \(R_{\mathrm{F_{L}}}\), are different from
+the probabilities that a male encounter has or does not have a gift. The
 rate of encounter is no longer relevant in this case because we are
@@
 
-\[G = \frac{1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}} = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
+\[P(G) = \frac{1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}} = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
 
@@
 
-\[L = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
+\[P(L) = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
 
@@
 \begin{equation}
-W_{\mathrm{f}, G} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}} + \frac{1}{R_{\mathrm{f},G}}}.
+W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}}} + \frac{1}{\mathrm{F_{G}}}.
 \end{equation}
@@
 the bottom gives the total time it takes to obtain this fitness. The
-\(R_{\mathrm{f},G}\) is inverted because it represents the expected time
-to encountering a male with a gift. We can expand Eq. 6,
-
-\[W_{\mathrm{f},G} = \lambda \frac{1 + \gamma}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right)}}.\]
+\(R_{\mathrm{F_{G}}}\) is inverted because it represents the expected
+time to encountering a male with a gift. We can expand Eq. 6,
+
+\[W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right)}}.\]
 
@@
 
-\[W_{\mathrm{f},l} = \lambda \frac{\left(1 + \gamma\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right) + e^{-\frac{1}{\alpha}T_{m}}}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)}}.\]
+\[W_{\mathrm{F_{G,L}}} = \lambda \frac{\left(1 + \gamma\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)}}.\]
 
 We then evaluate the conditions under which
-\(W_{\mathrm{f}, G} > W_{\mathrm{f}, L}\). We isolate \(\gamma\) to
-determine how much offspring fitness must be increase to make choosiness
-beneficial (\(\gamma_{\mathrm{f}}\)),
+\(W_{\mathrm{F_{G}}} > W_{\mathrm{F_{G,L}}}\). We isolate \(\gamma\) to
+determine how much offspring fitness must be increased to make
+choosiness beneficial (\(\gamma_{\mathrm{f}}\)),
 
@@
 We assume that the sex ratio is equal upon maturation. Given this, Kokko
-and Monaghan (\protect\hyperlink{ref-Kokko2001}{Kokko \& Monaghan,
-2001}) show that the operational sex ratio depends on the probability of
-finding an individual in `time in',
+\& Monaghan (\protect\hyperlink{ref-Kokko2001}{2001}) show that the
+operational sex ratio depends on the probability of finding an
+individual in time-in,
 
@@
 In Eq. 8, \(P_{IM}(t)\) and \(P_{IF}(t)\) are the probabilities of
-finding a male and female in `time in', respectively. There is no closed
+finding a male and female in time-in, respectively. There is no closed
 form solution to the operational sex ratio, so we used recursion to
@@
 individual-based model to test whether the prediction hold in finite
-populations (see Supporting Information S6). The IBM was written in C.
-All details of the initialisation, parameterisation and the specific
-simulations which we run, are described in the supporting information
-(see Supporting Information S1).
+populations. The IBM was written in C. All details of the
+initialisation, parameterisation and the specific simulations which we
+run, are described in Supporting Information S1.
 
@@
 simulations where \(\gamma\) was parameterised using this estimated
-value. Details of the estimation of \(\gamma\) are described in the
-supporting information (see Supporting Information S5).
+value. Details of the estimation of \(\gamma\) are described in
+Supporting Information S5. Separate evolution of male search and female
+choice (i.e., without co-evolution) is simulated in Supporting
+Information S6.
 
@@
 and the full source code is available at
-\url{https://github.com/bradduthie/Pisaura}.
+\url{https://github.com/bradduthie/nuptial_gift_evolution}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Wilson2003}{}}%
+Wilson, W.G., Morris, W.F. \& Bronstein, J.L. (2003) {Coexistence of
+mutualists and exploiters on spatial landscapes}. \emph{Ecological
+Monographs}, \textbf{73}, 397--413.
+
 \end{CSLReferences}
@@
 \endhead
-S1: Description of the individual-based simulation model & 26 \\
-S2: Sensitivity analysis of mortality parameters in IBM & 29 \\
-S3: Alternative derivation of male fitness threshold & 31 \\
-S4: Operational sex ratio & 33 \\
-S5: Estimation of key model parameter using experimental data & 35 \\
-S6: Separate evolution of male search and female choice & 36 \\
+S1: Description of the individual-based simulation model & 27 \\
+S2: Sensitivity analysis of mortality parameters in IBM & 30 \\
+S3: Alternative derivation of male fitness threshold & 41 \\
+S4: Operational sex ratio & 43 \\
+S5: Estimation of key model parameter using experimental data & 45 \\
+S6: Separate evolution of male search and female choice & 46 \\
 \bottomrule
@@
 \(i\) is initialised with a starting value of female offspring
-processing time (\(T^{i}_{\mathrm{f}}\)), rejection rate for females
-(\(\rho^{i}\)), and male search time (\(T^{i}_{\mathrm{m}}\)). For all
-simulations, initialised values are set to \(T^{i}_{\mathrm{f}} = 2\),
-\(\rho^{i} = 0\), and \(T^{i}_{\mathrm{m}} = 0\). All individuals are
-initalised outside of the mating pool in the first time step \(t = 1\).
-The first time step then proceeds with females immediately entering the
-mating pool and males either entering the mating pool or searching for
-nuptial gifts.
+processing time (\(T^{i}_{\mathrm{f}}\)), rejection probability of
+gift-less males (\(\rho^{i}\)), and male search time
+(\(T^{i}_{\mathrm{m}}\)). For all simulations, initialised values are
+set to \(T^{i}_{\mathrm{f}} = 2\), \(\rho^{i} = 0\), and
+\(T^{i}_{\mathrm{m}} = 0\). All individuals are initalised outside of
+the mating pool in the first time step \(t = 1\). The first time step
+then proceeds with females immediately entering the mating pool and
+males either entering the mating pool or searching for nuptial gifts.
 
@@
 offspring, and males will enter it after searching for nuptial gifts
-(see `Time-out' below). A fixed number of \(\Psi = N\psi\) interactions
-between individuals occur in a single time step, where \(N\) is
-population size and \(\psi\) is a scaling parameter. Since an
-interaction includes two conspecifics, each individual is expected to
-encounter a conspecific \(2\psi\) times per time step (i.e.,
-\(R = 2\psi\)). For each interaction, two individuals are randomly
-sampled, each with equal probability. If both sampled individuals are
-within the mating pool and of different sexes, then a mating encounter
-occurs. If the male does not have a nuptial gift, then the female will
-reject him with a probability of \(\rho^{i}\); if rejection occurs, then
-both individuals stay in the mating pool. If rejection does not occur,
-or the male has a nuptial gift in the mating encounter, then the
-individuals mate. Females leave the mating pool and enter time-out to
-process offspring, and males leave and enter time-out to potentially
+(see `Time-out' below). Up to \(\Psi = N\psi\) interactions between
+individuals can occur in a single time step, where \(N\) is population
+size and \(\psi\) is a scaling parameter. In each time step, \(\Psi\)
+pairs of individuals are selected at random to interact. For each
+interaction, two different individuals are randomly selected from the
+population with equal probability. If the selected individuals are of
+different sexes, and both are in the mating pool, then a mating
+encounter occurs. If the male does not have a nuptial gift, then the
+female will reject him with a probability of \(\rho^{i}\); if rejection
+occurs, then both individuals stay in the mating pool. If rejection does
+not occur, or the male has a nuptial gift in the mating encounter, then
+the individuals mate. Females leave the mating pool and enter time-out
+to process offspring, and males leave and enter time-out to potentially
 search for new nuptial gifts (note that females and males might re-enter
@@
 
-During time out, a focal female \(i\) will produce
-\(\lambda_{i} \sim Poisson(\lambda)\) offspring if no nuptial gift was
-provided or \(\lambda_{i} \sim Poisson(\lambda + \gamma)\) if a gift was
-provided. Females remain outside of the mating pool to process offspring
-for \(T^{i}_{\mathrm{f}}\) time steps, where \(T^{i}_{\mathrm{f}}\) is
-sampled randomly for each individual from a Poisson distribution with a
-rate parameter of \(T_{\mathrm{f}}\),
-\(T^{i}_{\mathrm{f}} \sim Poisson(T_{\mathrm{f}})\). Offspring are added
-to the population immediately, with \(\rho^{i}\) and
-\(T^{i}_{\mathrm{m}}\) values that are the average of each parent plus
-some normally distributed error \(\epsilon_{R}\) and
-\(\epsilon_{T_{\mathrm{m}}}\). For example,
-
-\[T^{\mathrm{offspring}}_{\mathrm{m}} \sim N\left(\frac{T^{\mathrm{mother}}_{\mathrm{m}}  + T^{\mathrm{father}}_{\mathrm{m}}}{2}, \epsilon_{T_{\mathrm{m}}} \right).\]
+During time-out, offspring production and time outside of the mating
+pool are realised for each female by sampling from a Poisson
+distribution. A focal female \(i\) will produce \(Poisson(\lambda)\)
+offspring if no nuptial gift was provided or
+\(Poisson(\lambda + \gamma)\) if a gift was provided. Females remain
+outside of the mating pool to process offspring for
+\(Poisson(T^{i}_{\mathrm{f}})\) time steps. Offspring are added to the
+population immediately, with \(\rho^{i}\) and \(T^{i}_{\mathrm{m}}\)
+values that are the average of each parent plus some normally
+distributed error \(\epsilon_{R}\) and \(\epsilon_{T_{\mathrm{m}}}\).
+For example,
+
+\[T^{\mathrm{offspring}}_{\mathrm{m}} \sim \frac{T^{\mathrm{mother}}_{\mathrm{m}}  + T^{\mathrm{father}}_{\mathrm{m}}}{2} + N\left(0, \epsilon_{T_{\mathrm{m}}} \right).\]
 
@@
 male. Female offspring are immediately placed in the mating pool, and
-male offspring are out of the mating pool to search for nuptial gifts.
-After a female has spent \(T^{i}_{\mathrm{f}}\) time steps outside the
-mating pool, she will re-enter it.
-
-A focal male \(i\) outside the mating pool will enter it if they have
+male offspring are out of the mating pool to potentially search for
+nuptial gifts. After a female has spent \(T^{i}_{\mathrm{f}}\) time
+steps outside the mating pool, she will re-enter it.
+
+A focal male \(i\) outside the mating pool will enter it if he has
 searched for a fixed number of \(T^{i}_{\mathrm{m}}\) time steps, which
 is also sampled randomly from a Poisson distribution,
-\(T^{i}_{\mathrm{m}} \sim Poisson(T_{\mathrm{m}})\). If
-\(T^{i}_{\mathrm{m}} = 0\), then the male immediately returns to the
-mating pool (in the same time step). If \(T^{i}_{\mathrm{m}} > 0\), then
-the male must wait outside the mating pool for \(T^{i}_{\mathrm{m}}\)
-time steps, but will enter the mating pool with a nuptial gift with a
-probability,
-
-\[G^{i} = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.\]
+\(Poisson(T^{i}_{\mathrm{m}})\). If \(T^{i}_{\mathrm{m}} = 0\), then the
+male immediately returns to the mating pool (in the same time step). If
+\(T^{i}_{\mathrm{m}} > 0\), then the male must wait outside the mating
+pool for \(Poisson(T^{i}_{\mathrm{m}})\) time steps, but will enter the
+mating pool with a nuptial gift with a probability,
+
+\[P(G^{i}) = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.\]
 
@@
 
-At the end of time step, mortality occurs first with a fixed probability
-for all adults in the population, then with a probability caused by
-carrying capacity \(K\) applied to all individuals (adults and
+At the end of each time step, mortality occurs first with a fixed
+probability for all adults in the population, then with a probability
+caused by carrying capacity \(K\) applied to all individuals (adults and
 offspring). Mortality occurs in each time step with a fixed probability
@@
 \(\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}\) and
-\(\gamma = \{0, 0.1, ..., 1.9, 2.0\}\) parameter values for 1600
+\(\gamma = \{0, 0.1, ..., 1.9, 2.0\}\) parameter values for 3200
 replicates. Summary statistics for mean trait values, population size,
@@
 code testing. All code is publicly available on GitHub
-(\url{https://github.com/bradduthie/Pisaura}).
+(\url{https://github.com/bradduthie/nuptial_gift_evolution}).
 
 A set of simulations with a value of \(\gamma\) calculated from
-empirical data was also conducted. Here, \(\gamma\) was parameterised
-using data on egg production as a function of eating nuptial gifts (see
-below). Additional simulation sets with lower and upper bounds of the
-estimated \(\gamma\) were subsequently run. In the simulation sets with
-experimentally derived parameter values, all other parameters were
-identical to previous simulation batches.
+empirical data was also conducted (100 replicates). Here, \(\gamma\) was
+parameterised using data on egg production as a function of eating
+nuptial gifts (see below). Additional simulation sets with lower and
+upper bounds of the estimated \(\gamma\) were subsequently run. In the
+simulation sets with experimentally derived parameter values, all other
+parameters were identical to previous simulation batches.
 
@@
 
-\textbf{Mortality}
+We investigated the sensitivity of our results to individual mortality
+during time-in (\(\mu_{\mathrm{in}}\)) and time-out
+(\(\mu_{\mathrm{out}}\)), female processing time (\(T_{\mathrm{f}}\)),
+potential for interactions between conspecifics (\(\psi\)), and
+initialised male search time (\(T_{\mathrm{m}}\)). Across all of these
+simulations, there were challenges with statistical power. Evidence for
+the evolution of male search (blue points in figures) and female
+choosiness (red points in figures) was determined by the lower 95\%
+bootstrapped confidence interval of \(T_{\mathrm{m}}\) and
+\(T_{\mathrm{f}}\) values being greater than zero, respectively. This
+required a lot of replicate simulations in the main text (Figure 3),
+especially for values just above predicted thresholds and for female
+choosiness. Computation time was a limiting factor, even using a
+compiled language (C) and with access to a computing cluster. Absence of
+points above threshold values are not necessarily evidence that
+evolution of male search or female choosiness is not predicted to evolve
+in these regions of parameter space, but it does indicate that evolution
+of these traits is not necessarily assured given the stochasticity
+inherent to the IBM. Additional simulations can be conducted using the C
+code in the `src' folder of the GitHub repository
+(\url{https://github.com/bradduthie/nuptial_gift_evolution}). Below, we
+explain the parameter values used in the sensitivity analysis in more
+detail.
+
+\emph{Mortality}
 
@@
 parameters \(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\) (the
-probability of mortality in time in and time out, respectively, which we
+probability of mortality in time-in and time-out, respectively, which we
 assumed to be equal for all individuals) on the evolution of male search
@@
 evolution of male search or female choice (Fig. S2.1).
+
+\emph{Female processing time}
+
+We also conducted a sensitivity analysis of female processing time
+\(T_{\mathrm{f}}\). To do this, we ran simulations at default values,
+but with \(T_{\mathrm{f}} = 0.4\) (Figure S4.2) and
+\(T_{\mathrm{f}} = 10.0\) (Figures S4.3).
+
+\emph{Interactions between conspecifics}
+
+We conducted a sensitivity analysis on the encounter rate between
+conspecifics (\(R\)) by varying the value of \(\psi\) (see S1). Under
+default simulations, \(\psi = 3\). We also ran simulations in which
+\(\psi = 1\) (Figure S4.4), \(\psi = 2\) (Figure S4.5), \(\psi = 4\)
+(Figure S4.6), and \(\psi = 6\) (Figure S4.7), with all other parameters
+being set to default values.
+
+\emph{Initialised male search time}
+
+Lastly, we conducted a sensitivity analysis on initialised male search
+time (\(T_{\mathrm{m}}\)). To do this, we ran simulations at default
+values, but initialised all males at \(T_{\mathrm{m}} = 0.5\) (Figure
+S4.8) or \(T_{\mathrm{m}} = 2.5\) (S4.9). Note that under these
+initialisation conditions, it no longer makes sense to test whether or
+not \(T_{\mathrm{m}}\) evolves to positive values, so we do not show
+predicted male search thresholds and focus only on female choosiness.
+Interestingly, while predictions given initialised
+\(T_{\mathrm{m}} = 0.5\) are quite close for female choosiness
+thresholds, female choosiness does not appear to evolve given
+\(T_{\mathrm{m}} = 2.5\). This might be due to low selection pressure to
+reject males without gifts due to their low frequency. In other words,
+while females would benefit from a strategy of rejecting gift-less
+males, a lack of realised encounters with gift-less males preclude the
+evolution of sustained selection for choosiness.
+
+\clearpage
 
@@
 choice (red) under different combinations of the mortality rates
-\(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\) (mortality in time in
+\(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\) (mortality in time-in
 and out, respectively). The y-axis is the threshold fitness that leads
@@
 
-\textbf{Female processing time}
-
-We also conducted a sensitivity analysis of female processing time
-\(T_{\mathrm{f}}\). To do this, we ran simulations at default values,
-but with \(T_{\mathrm{f}} = 0.4\) (Figure S4.2) and
-\(T_{\mathrm{f}} = 10.0\) (Figures S4.3).
+\clearpage
 
@@
 predicts that females should be choosy and males should search,
-respectively. Approximately 3000 interactions occur between individuals
-in each time step, potentially resulting in a mating interaction. The
-number of individuals in the population remained at or near carrying
+respectively. Up to 3000 interactions occur between individuals in each
+time step (\(\psi = 3\)), potentially resulting in a mating interaction.
+The number of individuals in the population remained at or near carrying
 capacity of \(K = 1000\). Expected female processing time was set to
@@
 \captionsetup{labelformat=default}
+
+\clearpage
 
@@
 mathematical model predicts that females should be choosy and males
-should search, respectively. Approximately 3000 interactions occur
-between individuals in each time step, potentially resulting in a mating
-interaction. The number of individuals in the population remained at or
-near carrying capacity of \(K = 1000\). Expected female processing time
-was set to \(T_{\mathrm{f}}=10.0\) time steps, and \(\gamma\) and
+should search, respectively. Up to 3000 interactions occur between
+individuals in each time step (\(\psi = 3\)), potentially resulting in a
+mating interaction. The number of individuals in the population remained
+at or near carrying capacity of \(K = 1000\). Expected female processing
+time was set to \(T_{\mathrm{f}}=10.0\) time steps, and \(\gamma\) and
 \(\alpha\) values in the range {[}0.5, 1.5{]} and {[}0.1, 2.1{]},
@@
 
-\textbf{Interactions between conspecifics}
-
-We conducted a sensitivity analysis on the encounter rate between
-conspecifics (\(R\)) by varying the value of \(\psi\), where
-\(R = 2\psi\) (see S1). Under default simulations, \(\psi = 3\) and
-\(R = 6\). We also ran simulations in which \(\psi = 1\) (Figure S4.4)
-and \(\psi = 6\) (Figure S4.5), with all other parameters being set to
-default values.
+\clearpage
 
@@
 lines show thresholds above which the mathematical model predicts that
-females should be choosy and males should search, respectively.
-Approximately 1000 interactions occur between individuals in each time
-step, potentially resulting in a mating interaction. The number of
-individuals in the population remained at or near carrying capacity of
-\(K = 1000\). Expected female processing time was set to
+females should be choosy and males should search, respectively. Up to
+1000 interactions occur between individuals in each time step
+(\(\psi = 1\)), potentially resulting in a mating interaction. The
+number of individuals in the population remained at or near carrying
+capacity of \(K = 1000\). Expected female processing time was set to
 \(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
@@
 \includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-10-1.pdf}
-\caption{Figure S4.5 (\(\psi = 6\)): The coevolution of male search and
+\caption{Figure S4.5 (\(\psi = 2\)): The coevolution of male search and
 female choosiness as a function of nuptial gift search time
@@
 lines show thresholds above which the mathematical model predicts that
-females should be choosy and males should search, respectively.
-Approximately 6000 interactions occur between individuals in each time
-step, potentially resulting in a mating interaction. The number of
-individuals in the population remained at or near carrying capacity of
-\(K = 1000\). Expected female processing time was set to
+females should be choosy and males should search, respectively. Up to
+2000 interactions occur between individuals in each time step
+(\(\psi = 2\)), potentially resulting in a mating interaction. The
+number of individuals in the population remained at or near carrying
+capacity of \(K = 1000\). Expected female processing time was set to
 \(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
@@
 \includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-11-1.pdf}
-\caption{Figure S4.5 (\(\psi = 6\)): The coevolution of male search and
+\caption{Figure S4.6 (\(\psi = 4\)): The coevolution of male search and
 female choosiness as a function of nuptial gift search time
@@
 lines show thresholds above which the mathematical model predicts that
-females should be choosy and males should search, respectively.
-Approximately 6000 interactions occur between individuals in each time
-step, potentially resulting in a mating interaction. The number of
-individuals in the population remained at or near carrying capacity of
-\(K = 1000\). Expected female processing time was set to
+females should be choosy and males should search, respectively. Up to
+4000 interactions occur between individuals in each time step,
+potentially resulting in a mating interaction (\(\psi = 4\)). The number
+of individuals in the population remained at or near carrying capacity
+of \(K = 1000\). Expected female processing time was set to
 \(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
@@
 \includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-12-1.pdf}
-\caption{Figure S4.5 (\(\psi = 6\)): The coevolution of male search and
+\caption{Figure S4.7 (\(\psi = 6\)): The coevolution of male search and
 female choosiness as a function of nuptial gift search time
@@
 lines show thresholds above which the mathematical model predicts that
-females should be choosy and males should search, respectively.
-Approximately 6000 interactions occur between individuals in each time
-step, potentially resulting in a mating interaction. The number of
-individuals in the population remained at or near carrying capacity of
-\(K = 1000\). Expected female processing time was set to
+females should be choosy and males should search, respectively. Up to
+6000 interactions occur between individuals in each time step,
+potentially resulting in a mating interaction (\(\psi = 6\)). The number
+of individuals in the population remained at or near carrying capacity
+of \(K = 1000\). Expected female processing time was set to
 \(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
@@
 \includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-13-1.pdf}
-\caption{Caption here}
+\caption{Figure S4.8 (\(T_{\mathrm{m}} = 0.5\)): The coevolution of male
+search and female choosiness as a function of nuptial gift search time
+(\(\alpha\)). Points show where the lower 95\% confidence interval of
+where male search (blue) exceeds zero, indicating evolution of
+choosiness or nuptial gift search. Each point includes data from 1600
+replicate simulations with identical starting conditions. The red line
+shows the threshold above which the mathematical model predicts that
+females should be choosy (male thresholds for search are not shown
+because simulations were initialised with males already searching for
+nuptial gifts). Up to 3000 interactions occur between individuals in
+each time step, potentially resulting in a mating interaction
+(\(\psi = 3\)). The number of individuals in the population remained at
+or near carrying capacity of \(K = 1000\). Expected female processing
+time was set to \(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and
+\(\alpha\) values in the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]},
+respectively, were used.}
 \end{figure}
@@
 \includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-14-1.pdf}
-\caption{Caption here}
+\caption{Figure S4.9 (\(T_{\mathrm{m}} = 2.5\)): The coevolution of male
+search and female choosiness as a function of nuptial gift search time
+(\(\alpha\)). Points show where the lower 95\% confidence interval of
+where male search (blue) exceeds zero, indicating evolution of
+choosiness or nuptial gift search. Each point includes data from 1600
+replicate simulations with identical starting conditions. The red line
+shows the threshold above which the mathematical model predicts that
+females should be choosy (male thresholds for search are not shown
+because simulations were initialised with males already searching for
+nuptial gifts). Up to 3000 interactions occur between individuals in
+each time step, potentially resulting in a mating interaction
+(\(\psi = 3\)). The number of individuals in the population remained at
+or near carrying capacity of \(K = 1000\). Expected female processing
+time was set to \(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and
+\(\alpha\) values in the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]},
+respectively, were used.}
 \end{figure}
@@
 
-\[G = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
+\[P(G) = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
 
@@
 
-\[L = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
-
-For simplicity, we assume that the fitness increments to offspring
-associated with receiving a nuptial gift versus no nuptial gift are
-\(1 + \gamma\) and 1, respectively. The rate at which males increase
-their fitness can then be defined as the expected fitness increment from
-their nuptial gift search divided by \(T_{\mathrm{m}}\) plus the time
-spent in the mating pool waiting to encounter a mate,
-
-\[W_{\mathrm{m}} = \lambda \frac{G\left(1 + \gamma\right) + L}{T_{\mathrm{m}} + \left( \frac{\beta + 1}{R} \right)}.\]
+\[P(L) = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
+
+We assume that the fitness increments to offspring associated with
+receiving a nuptial gift versus no nuptial gift are \(1 + \gamma\) and
+1, respectively. The rate at which males increase their fitness can then
+be defined as the expected fitness increment from their nuptial gift
+search divided by \(T_{\mathrm{m}}\) plus the time spent in the mating
+pool waiting to encounter a mate,
+
+\[W_{\mathrm{m}} = \lambda \frac{P(G)\left(1 + \gamma\right) + P(L)}{T_{\mathrm{m}} + \left( \frac{\beta + 1}{R} \right)}.\]
 
@@
 
-We assume that the ratio of males to femalesis the same upon individual
+We assume that the ratio of males to females is the same upon individual
 maturation. Consequently, the operational sex ratio \(\beta\) will be a
-function of \(R\), \(T_{f}\), and \(T_{m}\) because these parameters
-determine the density of females and males in the mating pool versus
-outside of the mating pool. We start with the definition of \(\beta\) as
-being the probability of finding an individual in `time in'
-(\protect\hyperlink{ref-Kokko2001}{Kokko \& Monaghan, 2001}),
+function of \(R\), \(T_{\mathrm{f}}\), and \(T_{\mathrm{m}}\) because
+these parameters determine the density of females and males in the
+mating pool versus outside of the mating pool. We start with the
+definition of \(\beta\) as being the probability of finding an
+individual in time-in (\protect\hyperlink{ref-Kokko2001}{Kokko \&
+Monaghan, 2001}),
 
@@
 
-Estimates showing mean number of offspring produced by female
+Estimates showing the mean number of offspring produced by female
 \emph{Pisaura mirabilis} that ate nuptial gifts and females who did not.
@@
 Table 1: Estimates showing mean number of offspring produced by female
-\emph{Pisauras mirabilis} that ate nuptial gifts and females who did
-not. Means were calculated with raw data from Tuni \emph{et al.}
+\emph{P. mirabilis} that ate nuptial gifts and females who did not.
+Means were calculated with raw data from Tuni \emph{et al.}
 (\protect\hyperlink{ref-Tuni2013a}{2013}) and results are shown \(\pm\)
@@
 Information S1) to unpack the effect of coevolution on the evolution of
-male search and female choice. Specifically, we replicated the
-simulations shown in the main text under the condition where only one
-trait at a time was allowed to evolve and studied how this affected the
-trait evolution.
+male search and female choice. Here we replicated the simulations shown
+in the main text under the condition where only one trait at a time was
+allowed to evolve and studied how this affected the trait evolution.
 
@@
 the same set of simulations wherein male search evolved, but female
-choice was not possible). The results thus show how each trait evolves
-in the absence of any coevolution (Fig. S6.1).
+choice was not possible. The results thus show how each trait evolves in
+the absence of any coevolution (Fig. S6.1).
 

### 2024-06-07 ms_refs_fixed.Rmd
incorporate the updated SI into the new manuscript

@@
 output:
+  html_document: default
   pdf_document:
@@
     reference_docx: docx_template.docx
-  html_document: default
 bibliography: nuptial_refs.bib
@@
 
-Empirical predictions
+Empirical implications
 --------------------------------------------------
@@
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.2 ($T_{\\mathrm{f}} = 0.4$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.2 ($T_{\\mathrm{f}} = 0.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
 Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 720 replicate simulations with identical starting conditions.
+Each point includes data from approximately 1600 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates).
 Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
@@
 The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=0.4$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.5, 1.5] and [0.1, 2.1], respectively, were used."}
-SUMM_Tf0pt4 <- read.csv("inst/SI_Tf_0pt4.csv");
+Expected female processing time was set to $T_{\\mathrm{f}}=0.5$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.5, 1.5] and [0.1, 2.1], respectively, were used."}
+SUMM_Tf0pt4 <- read.csv("inst/SI_Tf_0pt5.csv");
 
@@
 g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 0.4);
+                            TF = 0.5);
 
@@
 Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 720 replicate simulations with identical starting conditions.
+Each point includes data from approximately 1600 replicate simulations with identical starting conditions (some parameter combinations include fewer replicates).
 Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
@@
 Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 720 replicate simulations with identical starting conditions.
+Each point includes data from approximately 1600 replicate simulations with identical starting conditions (some parameter combinations had fewer replicates, minimum 400).
 Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
@@
 Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 720 replicate simulations with identical starting conditions.
+Each point includes data from 1600 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates).
 Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.

### 2024-06-07 ms_refs_fixed.tex
incorporate the updated SI into the new manuscript

@@
 
-\hypertarget{empirical-predictions}{%
-\subsection{Empirical predictions}\label{empirical-predictions}}
+\hypertarget{empirical-implications}{%
+\subsection{Empirical implications}\label{empirical-implications}}
 
@@
 \includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-7-1.pdf}
-\caption{Figure S4.2 (\(T_{\mathrm{f}} = 0.4\)): The coevolution of male
+\caption{Figure S4.2 (\(T_{\mathrm{f}} = 0.5\)): The coevolution of male
 search and female choosiness as a function of nuptial gift search time
@@
 evolution of choosiness or nuptial gift search. Each point includes data
-from 720 replicate simulations with identical starting conditions. Red
-and blue lines show thresholds above which the mathematical model
-predicts that females should be choosy and males should search,
-respectively. Up to 3000 interactions occur between individuals in each
-time step (\(\psi = 3\)), potentially resulting in a mating interaction.
-The number of individuals in the population remained at or near carrying
+from approximately 1600 replicate simulations with identical starting
+conditions (some parameter combinations have fewer replicates). Red and
+blue lines show thresholds above which the mathematical model predicts
+that females should be choosy and males should search, respectively. Up
+to 3000 interactions occur between individuals in each time step
+(\(\psi = 3\)), potentially resulting in a mating interaction. The
+number of individuals in the population remained at or near carrying
 capacity of \(K = 1000\). Expected female processing time was set to
-\(T_{\mathrm{f}}=0.4\) time steps, and \(\gamma\) and \(\alpha\) values
+\(T_{\mathrm{f}}=0.5\) time steps, and \(\gamma\) and \(\alpha\) values
 in the range {[}0.5, 1.5{]} and {[}0.1, 2.1{]}, respectively, were
@@
 indicating evolution of choosiness or nuptial gift search. Each point
-includes data from 720 replicate simulations with identical starting
-conditions. Red and blue lines show thresholds above which the
+includes data from approximately 1600 replicate simulations with
+identical starting conditions (some parameter combinations include fewer
+replicates). Red and blue lines show thresholds above which the
 mathematical model predicts that females should be choosy and males
@@
 where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 720
-replicate simulations with identical starting conditions. Red and blue
-lines show thresholds above which the mathematical model predicts that
-females should be choosy and males should search, respectively. Up to
-1000 interactions occur between individuals in each time step
-(\(\psi = 1\)), potentially resulting in a mating interaction. The
-number of individuals in the population remained at or near carrying
+choosiness or nuptial gift search. Each point includes data from
+approximately 1600 replicate simulations with identical starting
+conditions (some parameter combinations had fewer replicates, minimum
+400). Red and blue lines show thresholds above which the mathematical
+model predicts that females should be choosy and males should search,
+respectively. Up to 1000 interactions occur between individuals in each
+time step (\(\psi = 1\)), potentially resulting in a mating interaction.
+The number of individuals in the population remained at or near carrying
 capacity of \(K = 1000\). Expected female processing time was set to
@@
 where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 720
-replicate simulations with identical starting conditions. Red and blue
-lines show thresholds above which the mathematical model predicts that
-females should be choosy and males should search, respectively. Up to
-2000 interactions occur between individuals in each time step
-(\(\psi = 2\)), potentially resulting in a mating interaction. The
-number of individuals in the population remained at or near carrying
-capacity of \(K = 1000\). Expected female processing time was set to
-\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
-the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]}, respectively, were used.}
+choosiness or nuptial gift search. Each point includes data from 1600
+replicate simulations with identical starting conditions (some parameter
+combinations have fewer replicates). Red and blue lines show thresholds
+above which the mathematical model predicts that females should be
+choosy and males should search, respectively. Up to 2000 interactions
+occur between individuals in each time step (\(\psi = 2\)), potentially
+resulting in a mating interaction. The number of individuals in the
+population remained at or near carrying capacity of \(K = 1000\).
+Expected female processing time was set to \(T_{\mathrm{f}}=2\) time
+steps, and \(\gamma\) and \(\alpha\) values in the range {[}0.0, 1.4{]}
+and {[}0.1, 1.2{]}, respectively, were used.}
 \end{figure}
@@
 where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 720
-replicate simulations with identical starting conditions. Red and blue
-lines show thresholds above which the mathematical model predicts that
-females should be choosy and males should search, respectively. Up to
-4000 interactions occur between individuals in each time step,
-potentially resulting in a mating interaction (\(\psi = 4\)). The number
-of individuals in the population remained at or near carrying capacity
-of \(K = 1000\). Expected female processing time was set to
-\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
-the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]}, respectively, were used.}
+choosiness or nuptial gift search. Each point includes data from 1600
+replicate simulations with identical starting conditions (some parameter
+combinations have fewer replicates). Red and blue lines show thresholds
+above which the mathematical model predicts that females should be
+choosy and males should search, respectively. Up to 4000 interactions
+occur between individuals in each time step, potentially resulting in a
+mating interaction (\(\psi = 4\)). The number of individuals in the
+population remained at or near carrying capacity of \(K = 1000\).
+Expected female processing time was set to \(T_{\mathrm{f}}=2\) time
+steps, and \(\gamma\) and \(\alpha\) values in the range {[}0.0, 1.4{]}
+and {[}0.1, 1.2{]}, respectively, were used.}
 \end{figure}
@@
 where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 720
-replicate simulations with identical starting conditions. Red and blue
-lines show thresholds above which the mathematical model predicts that
-females should be choosy and males should search, respectively. Up to
-6000 interactions occur between individuals in each time step,
-potentially resulting in a mating interaction (\(\psi = 6\)). The number
-of individuals in the population remained at or near carrying capacity
-of \(K = 1000\). Expected female processing time was set to
-\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
-the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]}, respectively, were used.}
+choosiness or nuptial gift search. Each point includes data from 1600
+replicate simulations with identical starting conditions (some parameter
+combinations have fewer replicates). Red and blue lines show thresholds
+above which the mathematical model predicts that females should be
+choosy and males should search, respectively. Up to 6000 interactions
+occur between individuals in each time step, potentially resulting in a
+mating interaction (\(\psi = 6\)). The number of individuals in the
+population remained at or near carrying capacity of \(K = 1000\).
+Expected female processing time was set to \(T_{\mathrm{f}}=2\) time
+steps, and \(\gamma\) and \(\alpha\) values in the range {[}0.0, 1.4{]}
+and {[}0.1, 1.2{]}, respectively, were used.}
 \end{figure}

### 2024-06-15 ms_refs_fixed.Rmd
Tweak the supporting information captions to fix the replicate number

@@
 output:
-  html_document: default
   pdf_document:
@@
     keep_tex: yes
+  html_document: default
   word_document:
@@
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.1: Evolution of both male search (blue) and female choice (red) under different combinations of the mortality rates $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$ (mortality in time-in and out, respectively).
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.1: Evolution of both male search (blue) and female choice (red) under different combinations of the mortality rates $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$ (mortality in time-in and out, respectively).
 The y-axis is the threshold fitness that leads to evolution of male search (blue) or female choice (red).
@@
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.2 ($T_{\\mathrm{f}} = 0.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.2 ($T_{\\mathrm{f}} = 0.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
 Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
@@
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.3 ($T_{\\mathrm{f}} = 10.0$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.3 ($T_{\\mathrm{f}} = 10.0$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
 Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
@@
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.4 ($\\psi = 1$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.4 ($\\psi = 1$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
 Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from approximately 1600 replicate simulations with identical starting conditions (some parameter combinations had fewer replicates, minimum 400).
+Each point includes data from approximately 100 replicate simulations with identical starting conditions (some parameter combinations had fewer replicates, minimum 400).
 Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
@@
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.5 ($\\psi = 2$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.5 ($\\psi = 2$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
 Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 1600 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates).
+Each point includes data from 100 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates).
 Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
@@
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.6 ($\\psi = 4$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.6 ($\\psi = 4$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
 Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 1600 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates).
+Each point includes data from 100 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates).
 Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
@@
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.7 ($\\psi = 6$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.7 ($\\psi = 6$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
 Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 1600 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates).
+Each point includes data from 100 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates).
 Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
@@
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.8 ($T_{\\mathrm{m}} = 0.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.8 ($T_{\\mathrm{m}} = 0.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
 Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
@@
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.9 ($T_{\\mathrm{m}} = 2.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.9 ($T_{\\mathrm{m}} = 2.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
 Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.

### 2024-06-15 ms.tex
Rename the files to just 'ms' reflecting the main manuscript

--- 2024-06-07 ms_refs_fixed.tex
@@
 \includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-6-1.pdf}
-\caption{Figure S4.1: Evolution of both male search (blue) and female
+\caption{Figure S2.1: Evolution of both male search (blue) and female
 choice (red) under different combinations of the mortality rates
@@
 \includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-7-1.pdf}
-\caption{Figure S4.2 (\(T_{\mathrm{f}} = 0.5\)): The coevolution of male
+\caption{Figure S2.2 (\(T_{\mathrm{f}} = 0.5\)): The coevolution of male
 search and female choosiness as a function of nuptial gift search time
@@
 \includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-8-1.pdf}
-\caption{Figure S4.3 (\(T_{\mathrm{f}} = 10.0\)): The coevolution of
+\caption{Figure S2.3 (\(T_{\mathrm{f}} = 10.0\)): The coevolution of
 male search and female choosiness as a function of nuptial gift search
@@
 \includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-9-1.pdf}
-\caption{Figure S4.4 (\(\psi = 1\)): The coevolution of male search and
+\caption{Figure S2.4 (\(\psi = 1\)): The coevolution of male search and
 female choosiness as a function of nuptial gift search time
@@
 choosiness or nuptial gift search. Each point includes data from
-approximately 1600 replicate simulations with identical starting
+approximately 100 replicate simulations with identical starting
 conditions (some parameter combinations had fewer replicates, minimum
@@
 \includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-10-1.pdf}
-\caption{Figure S4.5 (\(\psi = 2\)): The coevolution of male search and
+\caption{Figure S2.5 (\(\psi = 2\)): The coevolution of male search and
 female choosiness as a function of nuptial gift search time
@@
 where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 1600
+choosiness or nuptial gift search. Each point includes data from 100
 replicate simulations with identical starting conditions (some parameter
@@
 \includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-11-1.pdf}
-\caption{Figure S4.6 (\(\psi = 4\)): The coevolution of male search and
+\caption{Figure S2.6 (\(\psi = 4\)): The coevolution of male search and
 female choosiness as a function of nuptial gift search time
@@
 \includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-12-1.pdf}
-\caption{Figure S4.7 (\(\psi = 6\)): The coevolution of male search and
+\caption{Figure S2.7 (\(\psi = 6\)): The coevolution of male search and
 female choosiness as a function of nuptial gift search time
@@
 \includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-13-1.pdf}
-\caption{Figure S4.8 (\(T_{\mathrm{m}} = 0.5\)): The coevolution of male
+\caption{Figure S2.8 (\(T_{\mathrm{m}} = 0.5\)): The coevolution of male
 search and female choosiness as a function of nuptial gift search time
@@
 \includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-14-1.pdf}
-\caption{Figure S4.9 (\(T_{\mathrm{m}} = 2.5\)): The coevolution of male
+\caption{Figure S2.9 (\(T_{\mathrm{m}} = 2.5\)): The coevolution of male
 search and female choosiness as a function of nuptial gift search time

### 2024-06-15 ms_biorxiv.Rmd
Make a biorxiv version for pre-print

--- 2024-06-15 ms_refs_fixed.Rmd
@@
 - \bibliographystyle{amnatnat}
-- \linenumbers
-- \modulolinenumbers[2]
-linestretch: 2
+linestretch: 1
 link-citations: yes
@@
 
-Abstract
-================================================================================
+********************************************************************************
 
@@
 
-Lay summary
-================================================================================
-
-If you have ever bought a gift to impress a prospective partner, you are not alone. 
-Such behaviour is not unique to humans, but giving gifts during courtship is common in many different animals, including some species of insects, snails, birds, squid and spiders. 
-In animals, such gifts can be costly, but offering them may be worth it from an evolutionary perspective if they increase the reproductive success of the individual who provides them. 
-While using gifts during courtship (often called nuptial gifts) is widespread among animals, it is not universal. 
-Why have some groups of animals evolved to engage in nuptial gift-giving while others have not? 
-We explore this question by building a mathematical model, using computer simulations, and using data from a nuptial gift-giving species of spider to see how receiving nuptial gifts might affect reproductive success.
-We find conditions under which selection should favour males to provide nuptial gifts and females should exhibit a preference for gifts. 
-These conditions explain why some species engage in nuptial gift-giving while others do not.
-Interestingly, we find that these inequalities differ between males and female, illustrating that the evolutionary interest of the two sexes do not always overlap.
-
-Teaser text
-================================================================================
-
-The results presented provide a general explanation of the evolution of nuptial gift-giving which is a behaviour pattern that has evolved many times independently in diverse parts of the animal kingdom.
-The explanation is general but at the same time quantitatively precise, thus giving a rigorous answer to the conundrum of why nuptial gift-giving occurs in some groups of animals but not in others. 
-Since research on nuptial gift-giving has, and continues to, inspire an enormous amount of work, the results presented here are highly relevant to an active field of both theoretical and empirical research.
+********************************************************************************
 
@@
 |---------------------------------------------------------------|------|
-| S1: Description of the individual-based simulation model      |  27  |
-| S2: Sensitivity analysis of mortality parameters in IBM       |  30  |
-| S3: Alternative derivation of male fitness threshold          |  41  |
-| S4: Operational sex ratio                                     |  43  |
-| S5: Estimation of key model parameter using experimental data |  45  |
-| S6: Separate evolution of male search and female choice       |  46  |
+| S1: Description of the individual-based simulation model      |  18  |
+| S2: Sensitivity analysis of mortality parameters in IBM       |  20  |
+| S3: Alternative derivation of male fitness threshold          |  29  |
+| S4: Operational sex ratio                                     |  32  |
+| S5: Estimation of key model parameter using experimental data |  33  |
+| S6: Separate evolution of male search and female choice       |  34  |
 
@@
 Assuming these differences in feeding regimes correspond to eating versus not eating nuptial gifts, the mean number of offspring produced by a female who eats nuptial gifts can be calculated (Table 1).
+
+\clearpage
 

### 2024-06-15 ms_biorxiv.tex
Make a biorxiv version for pre-print

--- 2024-06-15 ms.tex
@@
 \bibliographystyle{amnatnat}
-\linenumbers
-\modulolinenumbers[2]
 \ifLuaTeX
@@
 
-\setstretch{2}
+\setstretch{1}
 \textbf{Key words:} Nuptial gifts, male search, mate interactions,
@@
 
-\hypertarget{abstract}{%
-\section{Abstract}\label{abstract}}
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
 
@@
 
-\hypertarget{lay-summary}{%
-\section{Lay summary}\label{lay-summary}}
-
-If you have ever bought a gift to impress a prospective partner, you are
-not alone. Such behaviour is not unique to humans, but giving gifts
-during courtship is common in many different animals, including some
-species of insects, snails, birds, squid and spiders. In animals, such
-gifts can be costly, but offering them may be worth it from an
-evolutionary perspective if they increase the reproductive success of
-the individual who provides them. While using gifts during courtship
-(often called nuptial gifts) is widespread among animals, it is not
-universal. Why have some groups of animals evolved to engage in nuptial
-gift-giving while others have not? We explore this question by building
-a mathematical model, using computer simulations, and using data from a
-nuptial gift-giving species of spider to see how receiving nuptial gifts
-might affect reproductive success. We find conditions under which
-selection should favour males to provide nuptial gifts and females
-should exhibit a preference for gifts. These conditions explain why some
-species engage in nuptial gift-giving while others do not.
-Interestingly, we find that these inequalities differ between males and
-female, illustrating that the evolutionary interest of the two sexes do
-not always overlap.
-
-\hypertarget{teaser-text}{%
-\section{Teaser text}\label{teaser-text}}
-
-The results presented provide a general explanation of the evolution of
-nuptial gift-giving which is a behaviour pattern that has evolved many
-times independently in diverse parts of the animal kingdom. The
-explanation is general but at the same time quantitatively precise, thus
-giving a rigorous answer to the conundrum of why nuptial gift-giving
-occurs in some groups of animals but not in others. Since research on
-nuptial gift-giving has, and continues to, inspire an enormous amount of
-work, the results presented here are highly relevant to an active field
-of both theoretical and empirical research.
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
 
@@
 \centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-3-1.pdf}
+\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-3-1.pdf}
 \caption{Fitness thresholds above which males increase their fitness by
@@
 \centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-4-1.pdf}
+\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-4-1.pdf}
 \caption{The coevolution of male search and female choosiness as a
@@
 \centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-5-1.pdf}
+\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-5-1.pdf}
 \caption{The joint evolution of male search and female choosiness using
@@
 \endhead
-S1: Description of the individual-based simulation model & 27 \\
-S2: Sensitivity analysis of mortality parameters in IBM & 30 \\
-S3: Alternative derivation of male fitness threshold & 41 \\
-S4: Operational sex ratio & 43 \\
-S5: Estimation of key model parameter using experimental data & 45 \\
-S6: Separate evolution of male search and female choice & 46 \\
+S1: Description of the individual-based simulation model & 18 \\
+S2: Sensitivity analysis of mortality parameters in IBM & 20 \\
+S3: Alternative derivation of male fitness threshold & 29 \\
+S4: Operational sex ratio & 32 \\
+S5: Estimation of key model parameter using experimental data & 33 \\
+S6: Separate evolution of male search and female choice & 34 \\
 \bottomrule
@@
 (Table 1).
+
+\clearpage
 
@@
 \centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-6-1.pdf}
+\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-6-1.pdf}
 \caption{Figure S2.1: Evolution of both male search (blue) and female
@@
 \centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-7-1.pdf}
+\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-7-1.pdf}
 \caption{Figure S2.2 (\(T_{\mathrm{f}} = 0.5\)): The coevolution of male
@@
 \centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-8-1.pdf}
+\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-8-1.pdf}
 \caption{Figure S2.3 (\(T_{\mathrm{f}} = 10.0\)): The coevolution of
@@
 \centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-9-1.pdf}
+\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-9-1.pdf}
 \caption{Figure S2.4 (\(\psi = 1\)): The coevolution of male search and
@@
 \centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-10-1.pdf}
+\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-10-1.pdf}
 \caption{Figure S2.5 (\(\psi = 2\)): The coevolution of male search and
@@
 \centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-11-1.pdf}
+\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-11-1.pdf}
 \caption{Figure S2.6 (\(\psi = 4\)): The coevolution of male search and
@@
 \centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-12-1.pdf}
+\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-12-1.pdf}
 \caption{Figure S2.7 (\(\psi = 6\)): The coevolution of male search and
@@
 \centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-13-1.pdf}
+\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-13-1.pdf}
 \caption{Figure S2.8 (\(T_{\mathrm{m}} = 0.5\)): The coevolution of male
@@
 \centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-14-1.pdf}
+\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-14-1.pdf}
 \caption{Figure S2.9 (\(T_{\mathrm{m}} = 2.5\)): The coevolution of male
@@
 \centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-16-1.pdf}
+\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-16-1.pdf}
 \caption{Figure S6.1: The separate evolution of male search and female

### 2024-06-15 SI.Rmd
Make the supporting information files

--- 2024-06-15 ms_biorxiv.Rmd
@@
 ---
-title: "A general model for the evolution of nuptial gift-giving"
+title: "A general model for the evolution of nuptial gift-giving: Supporting Information"
 author: |
@@
 
-**Key words:** Nuptial gifts, male search, mate interactions, modelling, *Pisaura*
-
-********************************************************************************
-
-Nuptial gift-giving occurs in several taxonomic groups including insects, snails, birds, squid, arachnids and humans. 
-Although this trait has evolved many times independently, no general framework has been developed to predict the conditions necessary for nuptial gift-giving to evolve. 
-We use a time-in time-out model to derive analytical results describing the requirements necessary for selection to favour nuptial gift-giving. 
-Specifically, selection will favour nuptial gift-giving if the fitness increase caused by gift-giving exceeds the product of expected gift search time and encounter rate of the opposite sex. 
-Selection will favour choosiness in the opposite sex if the value of a nuptial gift exceeds the inverse of the time taken to produce offspring multiplied by the rate at which mates with nuptial gifts are encountered.
-Importantly, selection can differ between the sexes, potentially causing sexual conflict. 
-We test these results using an individual-based model applied to a system of nuptial gift-giving spiders, *Pisaura mirabilis*, by estimating parameter values using experimental data from several studies.
-Our results provide a general framework for understanding when the evolution of nuptial gift-giving can occur and provide novel insight into the evolution of worthless nuptial gifts, occurring in multiple taxonomic groups with implications for understanding parental investment.
-
-********************************************************************************
-
-Introduction
-================================================================================
-
-Nuptial gift-giving occurs when the choosy sex (usually the female) receives gifts from the opposite sex (usually the male) during courtship. 
-It is a widespread phenomenon, occurring within several diverse taxonomic groups such as insects, snails, birds, squid, arachnids and humans [@Lewis2014; @Lewis2012; @Albo2014]. 
-Despite the ubiquity of this behaviour, little effort has been made to conceptualise the evolution of nuptial gift-giving within a general modelling framework [@Lewis2014; @Iwasa2022]. 
-Recent models describing the evolution of nuptial gift-giving have focused on co-evolution between male nuptial gift-giving and female propensity to remate, and evolutionarily stable nuptial gift sizes [@Iwasa2022; @Kamimura2021], but a general framework describing the conditions necessary for nuptial gift-giving to be initially favoured by selection is needed to understand when gift-giving should evolve.
-
-Nuptial gift-giving may allow males to increase fitness by acquiring additional mates, indirect benefits (by increasing the fitness of offspring), prolonged copulations, and success in sperm competition [@Lewis2014; @Albo2013; @Ghislandi2014].
-However, this potential fitness increase comes at the expense of producing a nuptial gift, which may be costly in terms of time and resources. 
-Females may increase their fitness by receiving nutritionally valuable nuptial gifts, but expressing a preference for males with gifts might result in a mating opportunity cost if available males without gifts are rejected.
-With respect to nuptial gift-giving, the evolutionary interests of both sexes may not always fully overlap. 
-This can cause sexual conflict, which is a difference in the evolutionary interest between sexes that occurs when interaction between sexes results in a situation where neither sex can achieve an optimal outcome [@Parker2006].
-That is, under some conditions, it might for example be optimal for males but not females to mate if females do not benefit from mating with males without nuptial gifts.
-
-Much work has sought to explain how gift-giving tactics are maintained, with explanations including condition-dependent strategies, gift-giving as a way to decrease female aggression during copulation, or gifts as sensory traps [@Albo2019; @Lubin2007; @Ghislandi2018; @Toft2016].
-An example of such a system is the nuptial gift-giving nursery-web spider *Pisaura mirabilis* where males may court females with or without nuptial gifts [@Bristowe1926; @Tuni2013a]. 
-Here, males may provide females with costly nuptial gifts in the form of captured arthropod prey, and females may exhibit preference for males with a nuptial gift by rejecting males without a nuptial gift [@Albo2013].
-
-We develop a general framework for investigating the evolution of nuptial gift-giving and choosiness using a time-in, time-out modelling approach and an individual-based model [@Clutton-Brock1992]. 
-Specifically, we derive conditions under which selection will favour male search for nuptial gifts and female rejection of gift-less males. 
-We show that selection for searching and choosiness depends on whether a threshold fitness value of the nuptial gift is exceeded. 
-Our model demonstrates the importance of nuptial gift cost, sex ratio, and mate encounter rate in determining the threshold above which selection will favour the evolution of nuptial gift-giving.
-Importantly, we show that the threshold value differs for males and females. 
-We test predictions of our analytical model by formulating an individual-based model, which further supports the main theoretical results of our analytical model. 
-Further, we apply our model to an example system with nuptial gifts, the nursery web spider *Pisaura mirabilis*, where we use experimental data to estimate a key model parameter. 
-Our results provide a general framework for understanding why nuptial gift-giving evolves in some systems and not in others, how the evolution of nuptial gift-giving can give rise to sexual conflict, and it provides insight into the evolution of worthless and deceitful nuptial gifts, which occur in several different taxonomic [@Ghislandi2014; @LeBas2005].
-
-Results
-================================================================================
-
-Analytical model
---------------------------------------------------------------------------------
-
-We use a time-in and time-out model [@Clutton-Brock1992; @Kokko2001; @Kokko2006] in which choosy (female) and non-choosy (male) individuals spend some period of time within the mating pool searching for a mate (time-in) followed by a period outside the mating pool (time-out).
-During time-out, females spend some duration of time ($T_{\mathrm{f}}$) gestating or rearing (hereafter 'processing') offspring. 
-We define the number of offspring produced by a female per reproductive cycle as $\lambda$.
-Since females enter time-out after mating, this assumption is equivalent to assuming a system with sequential polyandry.
-For simplicity, we assume male time to replenish sperm is negligible, but males can spend some duration of time ($T_{\mathrm{m}}$) out of the mating pool searching for nuptial gifts.
-
-```{r echo = FALSE, out.width = "100%", fig.cap = "Conceptual figure inspired by Kokko and Ots (2006) illustrating how the modelling framework maps onto an example of a system wherein nuptial gifts are used, here \\textit{Pisaura mirabilis}.
-Males have a probability of obtaining a nuptial gift while in time-out, which will affect their probability of mating while in time-in.
-They return to the mating pool (time-in) at a rate determined by the time spent searching for a nuptial gifts ($T_{\\mathrm{m}}$) and leave the mating pool (i.e.
-enter time-out) following the female encounter rate, which is dependent on the ratio of males to females ($\\beta$) and the encounter rate ($R$).
-The choosy sex (females) enter the mating pool at a rate depending on the time spent processing offspring ($T_{\\mathrm{f}}$) and leave the mating pool (i.e.
-enter time-out) at a rate that is dependent on $\\beta$ and $R$.
-Males and females undergo sex-specific mortality $\\mu$ during time-in and time-out.
-Image left to right: (1) male \\textit{P.
-mirabilis}.
-(2) male \\textit{P.
-mirabilis} presenting nuptial gift (white) to female.
-(3) Female \\textit{P.
-mirabilis} protecting offspring.
-Photos: Alamy."}
-include_graphics("inst/img/conceptual_figure.png");
-```
-
-Criteria for male search and female choosiness
---------------------------------------------------------------------------------
-
-The probability $G$ that a male succeeds in securing a nuptial gift is defined by,
-
-<!--
-
-$$G = 1 - e^{-\frac{1}{\alpha}T_{m}}.$$
---->
-
-\begin{equation}
-G = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.
-\end{equation}
-
-In Eq. 1, $\alpha$ defines the expected search time before encountering a nuptial gift.
-Thus, the probability of finding a nuptial gift is higher the more time $T_{\mathrm{m}}$ is spent searching. 
-During time-in, individuals encounter conspecifics at a rate of $R$.
-A focal individual will therefore encounter conspecifics of the opposite sex at a rate of $R/2$ if the ratio of males to females in the mating pool ($\beta$) is equal.
-More generally, males will be encountered at a rate of $R\beta/(\beta+1)$, and females will be encountered at a rate of $R/(\beta+1)$.
-An example of how the structure of the time-in time-out model applies to a system with nuptial gift-giving is given in Figure 1.
-We assume that mating with a nuptial gift increases the fitness of each offspring by an increment of $\gamma$.
-We proceed to find the thresholds $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$ above which males and females are favoured by selection to search for mates with nuptial gifts and exhibit choosiness for nuptial gifts, respectively.
-We show (see Methods) that the initial threshold value of $\gamma$ ($\gamma_{\mathrm{m}}$) necessary for males to increase their fitness by investing time searching for a nuptial gift (time that could otherwise be spent searching for a mate) is,
-
-<!---
-
-$$\gamma_{m} > \alpha \frac{M}{\sqrt{\beta}}.$$
---->
-
-\begin{equation}
-\gamma_{\mathrm{m}} > \alpha \frac{R}{\beta + 1}.
-\end{equation}
-
-Inequality 2 means that if nuptial gifts are not abundant and thus require a long time to find (i.e., high $\alpha$), or if males encounter many females per unit time (i.e., high $R / (1+\beta)$), then the nuptial gift must result in a high fitness increment for selection to favour gift-searching.
-In general, when ineq. 2 is satisfied, we predict selection to favour the evolution of nuptial gift-giving.
-
-We can similarly predict the conditions for which there is selection for female choosiness. 
-If $\gamma$ is sufficiently high, then females increase their fitness by rejecting males without gifts and mating only with males that provide nuptial gifts. 
-To illustrate, we assume that all males in a population search for a duration of $T_{\mathrm{m}}$, in which case the threshold fitness increment for females ($\gamma_{\mathrm{f}}$) is,
-
-<!---
-
-$$\gamma_{f} > \frac{1}{T_{f} M \sqrt{\beta} \left(1 - e^{-\frac{1}{\alpha}T_{m}} \right)}.$$
-
---->
-
-\begin{equation}
-\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}} R \left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}} \right)}.
-\end{equation}
-
-Inequality 3 shows that as offspring processing time ($T_{\mathrm{f}}$), mate encounter rate ($R\beta / (\beta + 1)$), or the probability of a male finding a nuptial gift ($1 - \exp(-T_{\mathrm{m}}/\alpha)$ ) decreases, the threshold value of fitness above which selection will favour choosiness ($\gamma_{\mathrm{f}}$) increases.
-This can be understood intuitively by realising that rejecting a prospective male represents an opportunity cost for the female. 
-This opportunity cost becomes small if many males with gifts are encountered, hence the appearance of the rate at which males with gifts are encountered in the denominator.
-Figure 2 shows how $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$ change with increasing $\alpha$. 
-For $\gamma_{\mathrm{f}}$, we assume that males search for the expected time required to obtain a nuptial gift ($T_{\mathrm{m}} = \alpha$). 
-Note that $\beta$ does not have a closed form solution given $R$, $T_{\mathrm{f}}$, and $T_{\mathrm{m}}$, so $\beta$ was calculated using recursion (see Methods).
-
-```{r, echo = FALSE, fig.width = 8, fig.height = 4, fig.cap = "Fitness thresholds above which males increase their fitness by searching for nuptial gifts (blue lines; Eq.
-2) and females increase their fitness by rejecting males that do not offer gifts (red lines; Eq.
-3).
-Parameter space includes areas in which males do not search for nuptial gifts and females are not choosy (A), males search but females are not choosy (B), females would be choosy but males do not search (C), and males search and females are choosy (D).
-Arrows in panel a indicate the effect of increasing interaction rate ($R$), female time-out ($T_{\\mathrm{f}}$), and male search time ($T_{\\mathrm{m}}$).
-As an example, trajectories for $T_{\\mathrm{f}} = 2$, and $T_{\\mathrm{m}} = \\alpha$ are shown for values of $R=2$ (panel a) and $R = 1$ (panel b).
-Females are assumed to be the choosy sex, which is maintained as long as $\\alpha < T_{\\mathrm{f}}$."}
-alpha_vals <- seq(from = 0.0001, to = 2, by = 0.0001);
-par(mar = c(5, 5, 1, 1), mfrow = c(1, 2));
-beta_vals <- get_beta(M = 2, TF = 2, TM = alpha_vals);
-g_m <- gamma_m(R = 2, beta = beta_vals, alpha = alpha_vals, TF = 2);
-g_f <- gamma_f(R = 2, beta = beta_vals, alpha = alpha_vals, TF = 2);
-plot(x = alpha_vals, y = g_m, type = "l", lwd = 2, cex.lab = 1.25,
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness thresholds (", gamma[f], " & ", gamma[m], 
-                             ")")),
-     ylim = c(0, 2), col = "black", xaxs="i", yaxs="i");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25,
-     col = "black", lty = "solid");
-g_v <- which(g_f > g_m);
-g_w <- which(g_f <= g_m);
-polygon(x = c(alpha_vals[g_v], rev(alpha_vals[g_v])), 
-        y = c(g_m[g_v], rev(g_f[g_v])),
-        border = NA, col = "grey70");
-polygon(x = c(alpha_vals[g_w], rev(alpha_vals[g_w])), 
-        y = c(g_m[g_w], rev(g_f[g_w])),
-        border = NA, col = "grey20");
-bott <- rep(0, times = length(alpha_vals));
-topp <- c(g_m[g_v], g_f[g_w]);
-polygon(x = c(alpha_vals, rev(alpha_vals)),
-        y = c(topp, rev(bott)),
-        border = NA, col = "grey90");
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, cex.lab = 1.25,
-       col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25,
-       col = "red");
-text(x = 0.8, y = 0.15, cex = 2, labels = "A");
-text(x = 0.25, y = 0.4, cex = 1.5, labels = "B");
-text(x = 1.8, y = 1.1, cex = 4, labels = "C", col = "white");
-text(x = 0.2, y = 1.75, cex = 5, labels = "D");
-arrows(x0 = alpha_vals[10000], x1 = alpha_vals[9000], col = "blue",
-       y0 = g_m[10000], y1 = 0.9, length = 0.1, lwd = 2);
-text(x = alpha_vals[8300], y = 1.0, labels = "R", col = "blue");
-arrows(x0 = alpha_vals[15000], x1 = alpha_vals[15000], col = "red",
-       y0 = g_f[15000], y1 = 0.5, length = 0.1, lwd = 2);
-text(x = alpha_vals[15000], y = 0.415, labels = "R", col = "red");
-arrows(x0 = alpha_vals[12000], x1 = alpha_vals[12000], col = "red",
-       y0 = g_f[12000], y1 = 0.5, length = 0.1, lwd = 2);
-text(x = alpha_vals[12000], y = 0.415, labels = expression(T[f]), col = "red");
-arrows(x0 = alpha_vals[18000], x1 = alpha_vals[18000], col = "red",
-       y0 = g_f[18000], y1 = 0.5, length = 0.1, lwd = 2);
-text(x = alpha_vals[18000], y = 0.415, labels = expression(T[m]), col = "red");
-text(x = 1, y = 1.9, labels = "R = 2", cex = 1.5);
-text(x = 1.8, y = 1.915, labels = "a", cex = 1.5, col = "black");
-
-par(mar = c(5, 1, 1, 5))
-beta_vals <- get_beta(M = 1, TF = 2, TM = alpha_vals);
-g_m <- gamma_m(R = 1, beta = beta_vals, alpha = alpha_vals, TF = 2);
-g_f <- gamma_f(R = 1, beta = beta_vals, alpha = alpha_vals, TF = 2);
-plot(x = alpha_vals, y = g_m, type = "l", lwd = 2, cex.lab = 1.25,
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = "",
-     ylim = c(0, 2), col = "black", xaxs="i", yaxs="i", yaxt = "n");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25,
-     col = "black", lty = "solid");
-g_v <- which(g_f > g_m);
-g_w <- which(g_f <= g_m);
-polygon(x = c(alpha_vals[g_v], rev(alpha_vals[g_v])), 
-        y = c(g_m[g_v], rev(g_f[g_v])),
-        border = NA, col = "grey70");
-polygon(x = c(alpha_vals[g_w], rev(alpha_vals[g_w])), 
-        y = c(g_m[g_w], rev(g_f[g_w])),
-        border = NA, col = "grey20");
-bott <- rep(0, times = length(alpha_vals));
-topp <- c(g_m[g_v], g_f[g_w]);
-polygon(x = c(alpha_vals, rev(alpha_vals)),
-        y = c(topp, rev(bott)),
-        border = NA, col = "grey90");
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, cex.lab = 1.25,
-       col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25,
-       col = "red");
-text(x = 1.7, y = 0.15, cex = 2, labels = "A");
-text(x = 1, y = 0.7, cex = 2, labels = "B");
-text(x = 0.2, y = 1.75, cex = 5, labels = "D");
-text(x = 1, y = 1.9, labels = "R = 1", cex = 1.5);
-text(x = 1.8, y = 1.915, labels = "b", cex = 1.5, col = "black");
-```
-
-The analytical framework predicts 4 zones, which are delineated by inequalities 2 and 3 and describe the initial thresholds for favouring search of nuptial gifts in males and choosiness for nuptial gifts in females (Figure 2a).
-Consequently, the modelling framework gives a description of the conditions under which nuptial gift-giving is expected to occur (Figure 2a, Zone D) and the conditions under which only selection for male searching (Figure 2a, Zone B) or female choosiness (Figure 2a, Zone C) are predicted.
-These results therefore highlight the potential for sexual conflict over nuptial gift-giving.
-
-Evolution of male search and female choosiness
---------------------------------------------------------------------------------
-
-We used an individual-based model (IBM) to simulate the evolution of nuptial gift-giving and female choosiness from an ancestral condition in which neither exists. 
-The IBM was written to satisfy the assumptions of our analytical time-in and time-out model as much as practical (see Supporting Information S1). 
-Using the IBM, we modelled a spatially-implicit, finite population of females and males. 
-At each time step, some individuals enter or remain within the mating pool (time-in), where they potentially interact and mate. 
-After mating, males and females may leave the mating pool to search for nuptial gifts and to produce offspring, respectively (time-out). 
-Mortality occurs with a fixed probability in each time step, then a ceiling regulation is applied to limit population growth (see Methods).
-
-The rates at which females are encountered by males $R_{\mathrm{f},\mathrm{m}}$ and males with nuptial gifts $R_{\mathrm{m_{G}}, \mathrm{f}}$ are encountered by females are both calculated directly from the IBM, thereby modelling how these rates might be estimated from empirical data, so the male threshold for increasing fitness by searching is,
-
-<!---
-
-$$\gamma_{m, IBM} > \alpha M_{m}.$$
-
---->
-
-\begin{equation}
-\gamma_{\mathrm{m, IBM}} > \alpha R_{\mathrm{f},\mathrm{m}}.
-\end{equation}
-
-Similarly, female threshold for increasing fitness by choosiness is,
-
-<!---
-
-$$\gamma_{f, IBM} > \frac{1}{T_{m}M_{f,G}}.$$
-
---->
-
-\begin{equation}
-\gamma_{\mathrm{f, IBM}} > \frac{1}{T_{\mathrm{f}}R_{\mathrm{m_{G}}, \mathrm{f}}}.
-\end{equation}
-
-Consequently, the IBM and the analytical model differ slightly (e.g., time is discrete in the IBM but continuous the analytical model, and in the IBM, a fitness increment is applied to the focal female in the form of birthrate increase rather than offspring fitness; see Supporting Information S1 for details).
-But the predicted thresholds are theoretically equivalent and yield predictions that are qualitatively the same (Figure 3).
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 3200 replicate simulations with identical starting conditions.
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively (in agreement with Figure 2).
-Minor deviations between the analytical model and the simulation results are expected due to the finite population size, the substantial stochasticity inherent to the simulation model, and the potential for coevolution (for details, see Supporting Information S1).
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-In each time step, up to 3000 total pair-wise interactions occurred.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 2.0] and [0.1, 2.0], respectively, were used."}
-SUMM         <- read.csv(file = "inst/summary_coevolving.csv")
-alpha_vals   <- sort(unique(SUMM[,1]));  
-TM_vals      <- tapply(X = SUMM[,3],  INDEX = SUMM[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM[,13], INDEX = SUMM[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM[,14], INDEX = SUMM[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM[,15], INDEX = SUMM[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM[,16], INDEX = SUMM[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM[,17], INDEX = SUMM[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM[,18], INDEX = SUMM[,1], FUN = mean);
-
-g_m <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-
-for(i in 1:dim(SUMM)[1]){
-  if(SUMM[i, 4] > 0 & SUMM[i, 5] > 0){
-    points(x = SUMM[i, 1], y = SUMM[i, 2], cex = 3, pch = 20, col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM)[1]){
-  if(SUMM[i, 7] > 0 & SUMM[i, 8] > 0){
-    points(x = SUMM[i, 1], y = SUMM[i, 2], cex = 2, pch = 20, col = "red");
-  }
-}
-```
-
-Male thresholds $\gamma_{\mathrm{m, IBM}}$ given by ineq.
-4 accurately predict the evolution of searching in the IBM across $\alpha$ values, and the female threshold $\gamma_{\mathrm{f, IBM}}$ (ineq.
-5) predicts the evolution of female choice (Figure 3).
-In other words, IBM simulations demonstrate that nuptial gift search in males, and choosiness in females, will evolve from an ancestral state of no searching and no choosiness in similar parameter space (Figure 3) as predicted by the analytical model (Figure 2b).
-We further ran the IBM with realistic values of $\gamma$, estimated using data from the *P. mirabilis* system wherein choosiness among females, and nuptial gift search among males, occur (Figure 4). 
-We found that our IBM predicts both the evolution of choosiness and nuptial gift searching observed in the *P. mirabilis* system.
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "The joint evolution of male search and female choosiness using a nuptial gift fitness increment ($\\gamma$) that was estimated from experimental data for the species *Pisaura mirabilis* (mean $\\gamma = 3.29 \\pm$ SE via propagation of error for estimates of nuptial feeding a non-nuptial feeding groups: [1.47; 8.32]).
-Points show where the 95% confidence interval exceeds 0 for female choosiness (red) and male search (blue).
-Each point includes data from 100 replicate simulations with identical starting conditions.
-The red line shows the threshold above which females should be choosy and the blue line shows the threshold above which males should search.
-As predicted by the analytical model, both male search and female choosiness evolved for a range of $\\gamma$ values around the empirical estimates.
-This occurs because these values result in a $\\gamma$ above the fitness threshold necessary for selection to favour male search of nuptial gifts (blue line) and female choosiness (red line).
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-In each time step, up to 3000 total pair-wise interactions occurred.
-Female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the [0.2, 2.0], respectively, were used.
-The parameter $\\gamma$ was estimated as relative increase in offspring production such that $\\gamma$ is the factor by which fitness increases (relative to the baseline fitness) given a nuptial gift (See Supporting Information S5)."}
-SUME         <- read.csv(file = "inst/summary_empirically_inspired.csv")
-alpha_vals   <- sort(unique(SUME[,1]));  
-TM_vals      <- tapply(X = SUME[,3],  INDEX = SUME[,1], FUN = mean);
-m_vals       <- tapply(X = SUME[,13], INDEX = SUME[,1], FUN = mean);
-beta_vals    <- tapply(X = SUME[,14], INDEX = SUME[,1], FUN = mean);
-Male_M       <- tapply(X = SUME[,15], INDEX = SUME[,1], FUN = mean);
-Female_M     <- tapply(X = SUME[,16], INDEX = SUME[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUME[,17], INDEX = SUME[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUME[,18], INDEX = SUME[,1], FUN = mean);
-
-g_m <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 5.5));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-
-for(i in 1:dim(SUME)[1]){
-  if(SUME[i, 4] > 0 & SUME[i, 5] > 0){
-    points(x = SUME[i, 1], y = SUME[i, 2], cex = 3, pch = 20, col = "blue");
-  }
-}
-
-for(i in 1:dim(SUME)[1]){
-  if(SUME[i, 7] > 0 & SUME[i, 8] > 0){
-    points(x = SUME[i, 1], y = SUME[i, 2], cex = 2, pch = 20, col = "red");
-  }
-}
-```
-
-Discussion
-================================================================================
-
-Nuptial gift-giving has arisen several times independently throughout the animal kingdom [@Lewis2012], so understanding how selection favours nuptial gift giving and choosiness is important for a broad range of mating systems.
-We provide a general framework that defines the necessary conditions for selection to favour the evolution of nuptial gift-giving. 
-We show that males should give nuptial gifts if the value of a nuptial gift exceeds a threshold dependent on the encounter rate between males and females and the cost or time necessary to find or produce a nuptial gift (see ineq.
-2).
-This result makes intuitive sense because if males rarely encounter females, time searching for a gift is a minor cost relative to mate search time. 
-If males encounter many females, it is not worth seeking nuptial gifts unless gifts are very valuable since the male will meet many prospective mates, and nuptial gift search time might come at a cost of decreased mating opportunities.
-In practice, male biased sex ratios will not necessarily favour male search for nuptial gifts if the female encounter rate is very high, so the key variable is how often males and females encounter each other.
-If the search time or cost of finding a nuptial gift is high, nuptial gifts must be very valuable before search is favoured by selection.
-
-Threshold fitness values
---------------------------------------------------
-
-Importantly, we show that the threshold nuptial gift value at which females are favoured to express choosiness for nuptial gifts is rarely equivalent to the threshold value at which males are favoured to search for nuptial gifts, potentially leading to sexual conflict [@Oliveira2008; @Arnqvist2005a].
-Here, we are defining sexual conflict as occurring when interactions between sexes result in situation where both sexes cannot achieve an optimal outcome simultaneously [@Parker2006].
-As an example, sizable areas of parameter space exists wherein the female optimum would be to exhibit preference for (and receive) nuptial gifts, while the male optimum is to not search for (and give) nuptial gifts (see Figure 2a, Zone C).
-This will lead to mate encounters in which gift-less males will benefit from mating, but females will not.
-In many systems, ecological variables such as search time required to find a nuptial gift will likely depend on prey abundance,  which can vary substantially with time in some species with nuptial gift-giving [@Ghislandi2018].
-Since several ecological variables likely affect the value of these thresholds, our results can be seen as providing some formalised description of why nuptial gift-giving only occurs in some but not all systems.
-
-At first, the analytical model seems to suggests that nuptial gifts must cause a very high fitness increase (approximately 25\%) before male search and female choosiness is favoured by selection (Figure 2).
-Similarly the IBM model seems to suggest that a fitness benefit of approximately 50\% is required (see Figure 3). 
-However, it is important to recognise that these thresholds depend on multiple parameters.
-For example, if female processing time ($T_{\mathrm{f}}$) is high, the female threshold for choosiness with respect to $\gamma$ drops such that male search and female choosiness are favoured at lower $\gamma$ (see Supporting Information S2).
-If $T_{\mathrm{f}}$ is sufficiently high, then an initially rare gift-giving trait might be favoured by selection even if the fitness benefit of a nuptial gift is low.
-The effect that nuptial gifts have on fitness might vary across species, or even populations.
-Effects on female fecundity have been estimated in crickets, fireflies, butterflies, and spiders, but these estimates vary considerably between species suggesting a large positive effect to no effect at all [@Bergstrom2002; @Gao2019; @Maxwell2018; @Rooney2002].
-
-We modelled the evolution of nuptial gift-giving using both a mathematical model and an individual-based model.
-Our mathematical model makes simple assumptions about the relationship between nuptial gift search time ($\alpha$), conspecific encounter rate ($R$), female processing time ($T_{\mathrm{f}}$), and the fitness increment of a nuptial gift for offspring fitness ($\gamma$).
-It then derives the threshold $\gamma$ values above which males increase their fitness by searching ($T_{\mathrm{m}} > 0$) for a nuptial gift ($\gamma_{\mathrm{m}}$) and females increase their fitness by choosing to reject males without gifts ($\gamma_{\mathrm{f}}$).
-In contrast, our IBM models individuals over discrete time steps, and key processes of nuptial gift acquisition, conspecific encounters, and female processing are stochastic and varying among individuals.
-The mathematical model and IBM make qualitatively identical predictions (compare Figure 2b versus Figure 3), but differences between the two models inevitably lead to quantitative differences for $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$ thresholds.
-For example, $\gamma_{\mathrm{f}}$ increased more rapidly with increasing $\alpha$ in the IBM compared to the analytical model.
-Some differences are expected to occur due to stochastic effects inherent to IBMs [e.g., @Wilson2003].
-Other differences are more likely caused by more subtle assumptions between, and limitations of, the two models.
-In general, the IBM did not do a good job of controlling for conspecific interaction rate, making it difficult to directly compare $R$ between models.
-The IBM also allowed for coevolution between male search and female choosiness (Figure 3), which was not allowed in the analytical model (Figure 2).
-It was not our goal to exactly recover the quantitative predictions of the analytical model in our IBM.
-Future development of the IBM could further bridge the gap between models while also developing new theory on how aspects of the system such as explicit space, individual life history, or genetics affect the evolution of nuptial gift-giving behaviour.
-
-Nuptial gift-giving theory
---------------------------------------------------
-
-When modelling nuptial gift evolution, the challenge is to construct a framework that captures the frequency-dependent selection between male nuptial gift-giving and female choosiness for nuptial gifts, and we do this using a time-in, time-out model.
-Recent studies have modelled some frequency-dependent aspect of nuptial gift giving using evolutionary game theory [@MaynardSmith1982; @Vincent2005]. 
-Two such studies formulated a quantitative genetics model to study evolutionarily stable nuptial gift sizes in populations where the female propensity to re-mate was evolving [@Iwasa2022; @Kamimura2021].
-The results obtained in these studies complement our results by giving equilibrium solutions to the evolutionary stable nuptial gift size, whereas we determine the general conditions under which nuptial gift-giving will evolve as given by the inequalities we derive.
-
-Other modelling frameworks have made general predictions about sexually selected traits, and these predictions are not mutually exclusive to those made by our model.
-For example, the good genes hypothesis predicts that costly traits such as nuptial gift-giving can be favoured since males enduring the cost of a nuptial gift signals to females that their genes confer high fitness precisely because they can afford this cost [@Kirkpatrick1996; @Byers2006; but see @Fromhage2022].
-In other words, costly sexually selected traits are favoured because they are indicators of overall genetic quality [@Martinossi-Allibert2019]. 
-Because of this, nuptial gift-giving could be a case of condition-dependence where engaging in nuptial gift-giving is only favourable for male in good condition (e.g., males capable of successful search [@Ghislandi2018; @MaynardSmith1982; @Engqvist2015]).
-In general, our model demonstrates how nuptial gift-giving initially evolves before other mechanisms, such as good gene effects, become relevant.
-
-A nuptial gift can also constitute a dishonest signal of good body condition since worthless, deceptive nuptial gifts have evolved in several systems [@Ghislandi2014; @LeBas2005]. 
-This is also the case in *P. mirabilis* where males will wrap plant parts or an empty exoskeleton in silk, as opposed to an arthropod prey, and use this as a nuptial gift [@Ghislandi2014; @Albo2011]. 
-In such systems, worthless nuptial gifts have been shown to reduce the likelihood that a male is rejected by a female compared to the case where no nuptial gift is given. 
-However, males offering worthless nuptial gifts may be at a slight disadvantage in sperm competition since worthless gifts result in a shorter copulation duration and hence less sperm transfer [@Albo2013; @Ghislandi2014].
-Worthless gifts should not result in any paternal care benefits to the male since the offspring he may sire will not gain nutrition from a worthless nuptial gift.
-
-Given our modelling framework, worthless nuptial gifts may be expected to evolve in cases where females are discriminating in favour of nuptial gifts, but the cost of search time for a true nuptial gift is very high such that selection will not favour male search.
-This scenario would correspond to zone C of Figure 2 where the value of the nuptial gift exceeds the female fitness threshold for choosiness to be favoured, but due to high search time, selection will not favour male search for true nuptial gifts.
-Our model also predicts the possibility of the opposite scenario, in which males provide nuptial gifts, but females do not exhibit preference for nuptial gifts (zone B of Figure 2). 
-Fascinatingly, an example of such system has been documented by a recent study of the genus *Trechaleoides*, which contains two species with true nuptial gift-giving, but a lack of preference for nuptial gifts among female [@Martinez2023].
-
-The main drivers of male nuptial gift-giving are thought to be indirect fitness benefits and increased success in sperm competition, since providing a nuptial gift can result in longer copulation duration which is correlated with increased sperm transfer along with female cryptic choice promoting males who provide nuptial gifts [@Albo2013; @Albo2011].
-However, nuptial gifts might also function to modulate female aggression and prevent sexual cannibalism [@Bilde2006]. 
-In some systems, such as *P.
-mirabilis*, males have been shown to reduce the risk of being cannibalised by the female after mating when offering a nuptial gift, such that the nuptial gift may result in a "shield effect", protecting the male [@Toft2016].
-
-Empirical implications
---------------------------------------------------
-
-The simulations parameterised with an experimentally estimated value of $\gamma$ showed evolution of nuptial gift searching in males and choosiness for nuptial gifts in females.
-The model thus predicts that *P.
-mirabilis* living under conditions with the estimated fitness value of nuptial gifts should exhibit both search for nuptial gifts and choosiness for males with nuptial gifts, and this is what is observed in empirical populations.
-Parameterising $\gamma$ with data from experimental studies may only yield a rough approximation of the true $\gamma$.
-This is because the estimated value of $\gamma$ is based on data from current populations (rather than ancestral populations, which are being simulated), and because the literature is inconclusive as to how much (if any) effect nuptial gifts have on female fitness [@Maxwell2018].
-The effect of nuptial gifts on female fecundity has been estimated in a variety of system such as crickets, fireflies, butterflies and spiders, but these estimates vary considerably between species suggesting a large positive effect to no effect at all [@Bergstrom2002; @Rooney2002; @Maxwell2018; @Gao2019].
-
-Our model assumes something akin to sequential polyandry. 
-That is, a system wherein female mating and reproduction with multiple males occurs in sequence, rather than multiple matings occurring before reproduction. 
-In some systems with nuptial gift-giving, females have been documented to mate multiple times before reproduction occurs, including the genus of bark lice *Neotrogla* [@Kamimura2021], and even our example system of *P.
-mirabilis* where females will sometimes engage in multiple mating before reproducing, especially if starved because multiple mating may result in more nuptial gifts [@Toft2015; @Matzke2022].
-It is unclear what effect (if any) assuming non-sequential polyandry would have on the threshold we derive. 
-Under non-sequential polyandry, a viable strategy for females might be to accept any male (with or without gift) for fertilisation assurance, then exhibit a preference for nuptial gifts. 
-This might make choosiness less costly since it would entail less of an opportunity cost to be choosy, and this could potentially make female preference for nuptial gifts more likely to evolve. 
-Our model also assumes that males search in time-out, rather than contribute to parental care, which is likely to be accurate for most systems but not all. 
-Expanding the model to explore these possibilities would be a worthwhile goal for future research.
-
-Conclusion
---------------------------------------------------
-
-Overall, we found that a simple relationship between nuptial gift search time and mate encounter rate yields a threshold that determines whether selection will favour males that search for nuptial gifts.
-Similarly, we found that the threshold determining whether females will be favoured to reject males without nuptial gifts is also dependent on these variables, along with offspring processing time.
-Together, these thresholds describe the conditions under which nuptial gift-giving is expected to evolve.
-The applications of these thresholds are numerous. 
-They can be used as a starting point for more complex or more system-specific models of nuptial gift-giving evolution. 
-They can also provide novel insight into how populations can evolve to use worthless or token nuptial gifts.
-
-Methods
-================================================================================
-
-Model
---------------------------------------------------------------------------------
-
-Here we first present more detail for the derivation of fitness threshold values $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$.
-We then present IBM simulations (see Supporting Information S1 for full details). 
-Code for simulations is available on GitHub (see "Data availability").
-
-Derivation of fitness thresholds
---------------------------------------------------------------------------------
-
-We use a time-in and time-out model in which females and males spend some time searching for a mate (time-in) followed by a period of cool down outside the mating pool (time-out; Figure 1).
-
-After mating, females must spend some time processing offspring ($T_{\mathrm{f}}$). 
-Male time to replenish sperm is assumed to be negligible, but males can spend time out of the mating pool ($T_{\mathrm{m}}$) to search for a nuptial gift.
-When males return from time-out, they encounter females with some probability that is a function of the rate at which an individual encounters conspecifics ($R$) and the sex ratio ($\beta$; males/females).
-Mortality occurs for females and males in ($\mu_{\mathrm{i,f}}$, $\mu_{\mathrm{i,m}}$) and out ($\mu_{\mathrm{o,f}}$, $\mu_{\mathrm{o,m}}$) of the mating pool. 
-Following @Kokko2006, we assume $m_{\mathrm{i,f}} = m_{\mathrm{o,f}} = 1$ and $m_{\mathrm{i,m}} = m_{\mathrm{o,m}} = 1$. 
-While this choice is arbitrary, we conducted a sensitivity analysis which shows that the mortality parameters have no influence on the propensity for male search and female choice to evolve (Supporting Information S2).
-First, we describe the fitness consequences of male search time for a nuptial gift. 
-We then describe the fitness consequences of female choice to accept or reject males based on their provision of a nuptial gift.
-
-Male fitness
---------------------------------------------------------------------------------
-
-During time-out, males have the opportunity to search for a nuptial gift.
-Males can adopt one of two strategies; either search or do not search for a nuptial gift. 
-Males with the former strategy continue to search until they find a nuptial gift, while males that do not search will immediately re-enter the mating pool. 
-In this case, time searching for a nuptial gift will come at the cost of mating opportunities but might increase offspring fitness. 
-We therefore need to model the expected length of time $E[T_{\mathrm{m}}]$ spent outside of the mating pool for males that search for nuptial gifts, which is simply $\alpha$. 
-Note that we can integrate search time $t$ over the rate at which nuptial gifts are encountered ($\exp(-1/\alpha)$) to show $E[T_{\mathrm{m}}] = \alpha$,
-
-$$E[T_{\mathrm{m}}] = \int_{0}^{\infty}e^{- \frac{1}{\alpha}t}dt = \alpha.$$
-
-The rate at which a focal male that searches for a nuptial gift ($\mathrm{M_{G}}$) increases his fitness is therefore the fitness of his offspring $(1 + \gamma)$ divided by expected time spent searching for a nuptial gift ($\alpha$) plus time spent in the mating pool, $(\beta + 1)/R$ (recall that females produce $\lambda$ offspring),
-
-$$W_{\mathrm{M_{G}}} = \lambda \frac{1 + \gamma}{\alpha + \left( \frac{\beta + 1}{R} \right)}.$$
-
-In contrast, a male that does not search for a nuptial gift ($\mathrm{M_{L}}$) has offspring with lower fitness, but spends less time outside of the mating pool,
-
-$$W_{\mathrm{M_{L}}} = \lambda \frac{1}{\left(\frac{\beta+1}{R} \right)} = \lambda \frac{R}{\beta + 1}.$$
-
-We can then determine the conditions for which $W_{\mathrm{M_{G}}} > W_{\mathrm{M_{L}}}$, isolating $\gamma$ to find how large of a fitness benefit must be provided by the nuptial gift to make the search cost worthwhile, which simplifies to ineq.
-2.
-When this inequality holds, males are favoured to search until they find a nuptial gift, which would result in an average search time of $\alpha$. 
-When the male trait is continuous (i.e., males search for time period $T_{\mathrm{m}}$), it can be shown that the same threshold can be reached by evaluating the partial derivative of the male fitness function (Supporting Information S3).
-Hence, the thresholds are consistent under different assumptions concerning male searching strategy.
-Selection will cause males to search for nuptial gifts if the fitness increase to offspring exceeds the product of search time and female encounter rate.
-
-Female fitness
---------------------------------------------------------------------------------
-
-During time-out, females process offspring over a duration of $T_{\mathrm{f}}$ (we assume that $T_{\mathrm{f}} > \alpha$, else females are not the choosy sex). 
-When females re-enter the mating pool, they encounter males at a rate of $R\beta/(\beta + 1)$. 
-If a female encounters a male with a nuptial gift, we assume that she will mate with him. 
-But if a female encounters a male with no nuptial gift, then she might accept or reject the male. 
-If she rejects the male, then she will remain in the mating pool. 
-The rate at which a female encounters a male with a nuptial gift is,
-
-$$R_{\mathrm{F_{G}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right).$$
-
-We can similarly model the rate at which a female encounters a gift-less male,
-
-$$R_{\mathrm{F_{L}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(e^{-\frac{1}{\alpha}T_{m}}\right).$$
-
-Note that we can recover the rate at which a female encounters any male,
-
-$$R \left(\frac{\beta}{\beta + 1}\right) = R \left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + R \left(\frac{\beta}{\beta + 1}\right) \left(e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right).$$
-
-If $R_{\mathrm{F_{G}}}$ is sufficiently high and $R_{\mathrm{F_{L}}}$ is sufficiently low, then finding a male with a gift will be easier than finding a male without one. 
-Also, the expected time spent in the mating pool before a focal female encounters a male with a gift will be $1/R_{\mathrm{F_{G}}}$, while the expected time spent in the mating pool before a focal female encounters any male will be $1 / (R_{\mathrm{F_{G}}} + R_{\mathrm{F_{L}}})$.
-Finally, the rates at which a female encounters males with and without a gift, $R_{\mathrm{F_{G}}}$ and $R_{\mathrm{F_{L}}}$, are different from the probabilities that a male encounter has or does not have a gift.
-The rate of encounter is no longer relevant in this case because we are assuming that an encounter has occurred. 
-Hence, the probability of an encountered male having a gift is simply,
-
-$$P(G) = \frac{1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}} = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
-
-Similarly, the probability of an encountered male not having a gift is simply,
-
-$$P(L) = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
-
-The rate at which a female increases her fitness by being choosy and mating only when she encounters a male with a gift is,
-
-<!---
-
-$$W_{f, g} = \frac{1 + \gamma}{T_{F} + \frac{1}{M_{f,G}}}.$$
-
---->
-
-\begin{equation}
-W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}}} + \frac{1}{\mathrm{F_{G}}}.
-\end{equation}
-
-The top of the right-hand side of Eq. 6 gives the fitness increase, and the bottom gives the total time it takes to obtain this fitness. 
-The $R_{\mathrm{F_{G}}}$ is inverted because it represents the expected time to encountering a male with a gift. 
-We can expand Eq. 6,
-
-$$W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right)}}.$$
-
-If the focal female is not choosy and accepts the first male that she encounters, then the rate at which she increases her fitness is,
-
-$$W_{\mathrm{F_{G,L}}} = \lambda \frac{\left(1 + \gamma\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)}}.$$
-
-We then evaluate the conditions under which $W_{\mathrm{F_{G}}} > W_{\mathrm{F_{G,L}}}$. 
-We isolate $\gamma$ to determine how much offspring fitness must be increased to make choosiness beneficial ($\gamma_{\mathrm{f}}$),
-
-$$\gamma_{\mathrm{f}} > \frac{1 + \frac{1}{\beta}}{D T_{f} \left(1 - e^{-1\frac{1}{\alpha}T_{m}}\right)}.$$
-
-The above can be expressed as Eq. 7 below,
-
-<!---
-
-$$\gamma_{f} > \frac{1}{T_{F}M\sqrt{\beta}\left(1 - e^{-\frac{1}{\alpha}T_{M}} \right)}.$$
-
---->
-
-\begin{equation}
-\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}}} R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right).
-\end{equation}
-
-Note that that the expression $R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right)$ defines the rate at which a female in the mating pool encounters males with nuptial gifts.
-Hence, female choosiness is ultimately determined by time spent out of the mating pool to process offspring ($T_{\mathrm{f}}$) and the rate at which a female in the mating pool encounters males with nuptial gifts.
-
-Operational sex ratio
-----------------------------
-
-We assume that the sex ratio is equal upon maturation. 
-Given this, @Kokko2001 show that the operational sex ratio depends on the probability of finding an individual in time-in,
-
-<!---
-
-$$\beta = \frac{\int_{t = 0}^{\infty} P_{IM}(t)dt}{\int_{t = 0}^{\infty} P_{IF}(t)dt}.$$
-
---->
-
-\begin{equation}
-\beta = \frac{\int_{t = 0}^{\infty} P_{IM}(t)dt}{\int_{t = 0}^{\infty} P_{IF}(t)dt}.
-\end{equation}
-
-In Eq. 8, $P_{IM}(t)$ and $P_{IF}(t)$ are the probabilities of finding a male and female in time-in, respectively. 
-There is no closed form solution to the operational sex ratio, so we used recursion to calculate $\beta$ values for a given $T_{\mathrm{f}}$, $T_{\mathrm{m}}$, and $R$ (see Supporting Information S4),
-
-Individual-based model
-------------------------------------------
-
-We formulate an individual-based simulation model to test whether the predictions made by the analytical time-in time-out model are qualitatively the same under a similar simulation model. 
-We use the individual-based model to test whether the prediction hold in finite populations. 
-The IBM was written in C. 
-All details of the initialisation, parameterisation and the specific simulations which we run, are described in Supporting Information S1.
-
-We use available experimental data on the effect of nuptial gifts on female offspring production to estimate the key parameter $\gamma$ (fitness increment from nuptial gift) and conducted a series of simulations where $\gamma$ was parameterised using this estimated value.
-Details of the estimation of $\gamma$ are described in Supporting Information S5.
-Separate evolution of male search and female choice (i.e., without co-evolution) is simulated in Supporting Information S6.
-
-**Author contributions:** APC and ABD conceived the study.
-ABD constructed the modelling framework with input from APC.
-APC wrote the paper with input from ABD and ABD wrote the IBM model.
-TB and GB provided substantial comments on previous drafts and final text.
-
-**Acknowledgements:** Anders P.
-Charmouh was supported by the University of Aberdeen.
-A.
-Bradley Duthie was supported by the University of Stirling.
-Trine Bilde was supported by The Danish Council for Independent Research grant number 4002-00328B.
-We thank Maria Albo for making available data from a previous study which was useful for parameter estimating.
-
-**Data availability:** The simulation software was implemented in C and the full source code is available at https://github.com/bradduthie/nuptial_gift_evolution.
-
-**Competing interests:** The authors declare no competing interests.
-
-**References**
-
-<div id="refs"></div>
-
-\clearpage
-
-Supporting Information
+Table of Contents
 ====================================
@@
 |---------------------------------------------------------------|------|
-| S1: Description of the individual-based simulation model      |  18  |
-| S2: Sensitivity analysis of mortality parameters in IBM       |  20  |
-| S3: Alternative derivation of male fitness threshold          |  29  |
-| S4: Operational sex ratio                                     |  32  |
-| S5: Estimation of key model parameter using experimental data |  33  |
-| S6: Separate evolution of male search and female choice       |  34  |
+| S1: Description of the individual-based simulation model      |  2   |
+| S2: Sensitivity analysis of mortality parameters in IBM       |  4   |
+| S3: Alternative derivation of male fitness threshold          |  14  |
+| S4: Operational sex ratio                                     |  16  |
+| S5: Estimation of key model parameter using experimental data |  17  |
+| S6: Separate evolution of male search and female choice       |  18  |
+| References                                                    |  19  |
 
@@
 \captionsetup{labelformat=default}
+
+\clearpage
+
+References
+=============================================

### 2024-06-15 SI.tex
Make the supporting information files

--- 2024-06-15 ms_biorxiv.tex
@@
 \hypersetup{
-  pdftitle={A general model for the evolution of nuptial gift-giving},
+  pdftitle={A general model for the evolution of nuptial gift-giving: Supporting Information},
   colorlinks=true,
@@
 
-\title{A general model for the evolution of nuptial gift-giving}
+\title{A general model for the evolution of nuptial gift-giving:
+Supporting Information}
 \author{Anders P. Charmouh\(^{1,4, 5}\), Trine Bilde\(^{2}\), Greta
@@
 \setstretch{1}
-\textbf{Key words:} Nuptial gifts, male search, mate interactions,
-modelling, \emph{Pisaura}
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-Nuptial gift-giving occurs in several taxonomic groups including
-insects, snails, birds, squid, arachnids and humans. Although this trait
-has evolved many times independently, no general framework has been
-developed to predict the conditions necessary for nuptial gift-giving to
-evolve. We use a time-in time-out model to derive analytical results
-describing the requirements necessary for selection to favour nuptial
-gift-giving. Specifically, selection will favour nuptial gift-giving if
-the fitness increase caused by gift-giving exceeds the product of
-expected gift search time and encounter rate of the opposite sex.
-Selection will favour choosiness in the opposite sex if the value of a
-nuptial gift exceeds the inverse of the time taken to produce offspring
-multiplied by the rate at which mates with nuptial gifts are
-encountered. Importantly, selection can differ between the sexes,
-potentially causing sexual conflict. We test these results using an
-individual-based model applied to a system of nuptial gift-giving
-spiders, \emph{Pisaura mirabilis}, by estimating parameter values using
-experimental data from several studies. Our results provide a general
-framework for understanding when the evolution of nuptial gift-giving
-can occur and provide novel insight into the evolution of worthless
-nuptial gifts, occurring in multiple taxonomic groups with implications
-for understanding parental investment.
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Nuptial gift-giving occurs when the choosy sex (usually the female)
-receives gifts from the opposite sex (usually the male) during
-courtship. It is a widespread phenomenon, occurring within several
-diverse taxonomic groups such as insects, snails, birds, squid,
-arachnids and humans (\protect\hyperlink{ref-Lewis2012}{Lewis \& South,
-2012}; \protect\hyperlink{ref-Albo2014}{Albo \emph{et al.}, 2014};
-\protect\hyperlink{ref-Lewis2014}{Lewis \emph{et al.}, 2014}). Despite
-the ubiquity of this behaviour, little effort has been made to
-conceptualise the evolution of nuptial gift-giving within a general
-modelling framework (\protect\hyperlink{ref-Lewis2014}{Lewis \emph{et
-al.}, 2014}; \protect\hyperlink{ref-Iwasa2022}{Iwasa \& Yamaguchi,
-2022}). Recent models describing the evolution of nuptial gift-giving
-have focused on co-evolution between male nuptial gift-giving and female
-propensity to remate, and evolutionarily stable nuptial gift sizes
-(\protect\hyperlink{ref-Kamimura2021}{Kamimura \emph{et al.}, 2021};
-\protect\hyperlink{ref-Iwasa2022}{Iwasa \& Yamaguchi, 2022}), but a
-general framework describing the conditions necessary for nuptial
-gift-giving to be initially favoured by selection is needed to
-understand when gift-giving should evolve.
-
-Nuptial gift-giving may allow males to increase fitness by acquiring
-additional mates, indirect benefits (by increasing the fitness of
-offspring), prolonged copulations, and success in sperm competition
-(\protect\hyperlink{ref-Albo2013}{Albo \emph{et al.}, 2013};
-\protect\hyperlink{ref-Ghislandi2014}{Ghislandi \emph{et al.}, 2014};
-\protect\hyperlink{ref-Lewis2014}{Lewis \emph{et al.}, 2014}). However,
-this potential fitness increase comes at the expense of producing a
-nuptial gift, which may be costly in terms of time and resources.
-Females may increase their fitness by receiving nutritionally valuable
-nuptial gifts, but expressing a preference for males with gifts might
-result in a mating opportunity cost if available males without gifts are
-rejected. With respect to nuptial gift-giving, the evolutionary
-interests of both sexes may not always fully overlap. This can cause
-sexual conflict, which is a difference in the evolutionary interest
-between sexes that occurs when interaction between sexes results in a
-situation where neither sex can achieve an optimal outcome
-(\protect\hyperlink{ref-Parker2006}{Parker, 2006}). That is, under some
-conditions, it might for example be optimal for males but not females to
-mate if females do not benefit from mating with males without nuptial
-gifts.
-
-Much work has sought to explain how gift-giving tactics are maintained,
-with explanations including condition-dependent strategies, gift-giving
-as a way to decrease female aggression during copulation, or gifts as
-sensory traps (\protect\hyperlink{ref-Lubin2007}{Lubin \& Bilde, 2007};
-\protect\hyperlink{ref-Toft2016}{Toft \& Albo, 2016};
-\protect\hyperlink{ref-Ghislandi2018}{Ghislandi \emph{et al.}, 2018};
-\protect\hyperlink{ref-Albo2019}{Albo \emph{et al.}, 2019}). An example
-of such a system is the nuptial gift-giving nursery-web spider
-\emph{Pisaura mirabilis} where males may court females with or without
-nuptial gifts (\protect\hyperlink{ref-Bristowe1926}{Bristowe \& Locket,
-1926}; \protect\hyperlink{ref-Tuni2013a}{Tuni \emph{et al.}, 2013}).
-Here, males may provide females with costly nuptial gifts in the form of
-captured arthropod prey, and females may exhibit preference for males
-with a nuptial gift by rejecting males without a nuptial gift
-(\protect\hyperlink{ref-Albo2013}{Albo \emph{et al.}, 2013}).
-
-We develop a general framework for investigating the evolution of
-nuptial gift-giving and choosiness using a time-in, time-out modelling
-approach and an individual-based model
-(\protect\hyperlink{ref-Clutton-Brock1992}{Clutton-Brock \& Parker,
-1992}). Specifically, we derive conditions under which selection will
-favour male search for nuptial gifts and female rejection of gift-less
-males. We show that selection for searching and choosiness depends on
-whether a threshold fitness value of the nuptial gift is exceeded. Our
-model demonstrates the importance of nuptial gift cost, sex ratio, and
-mate encounter rate in determining the threshold above which selection
-will favour the evolution of nuptial gift-giving. Importantly, we show
-that the threshold value differs for males and females. We test
-predictions of our analytical model by formulating an individual-based
-model, which further supports the main theoretical results of our
-analytical model. Further, we apply our model to an example system with
-nuptial gifts, the nursery web spider \emph{Pisaura mirabilis}, where we
-use experimental data to estimate a key model parameter. Our results
-provide a general framework for understanding why nuptial gift-giving
-evolves in some systems and not in others, how the evolution of nuptial
-gift-giving can give rise to sexual conflict, and it provides insight
-into the evolution of worthless and deceitful nuptial gifts, which occur
-in several different taxonomic (\protect\hyperlink{ref-LeBas2005}{LeBas
-\& Hockham, 2005}; \protect\hyperlink{ref-Ghislandi2014}{Ghislandi
-\emph{et al.}, 2014}).
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{analytical-model}{%
-\subsection{Analytical model}\label{analytical-model}}
-
-We use a time-in and time-out model
-(\protect\hyperlink{ref-Clutton-Brock1992}{Clutton-Brock \& Parker,
-1992}; \protect\hyperlink{ref-Kokko2001}{Kokko \& Monaghan, 2001};
-\protect\hyperlink{ref-Kokko2006}{Kokko \& Ots, 2006}) in which choosy
-(female) and non-choosy (male) individuals spend some period of time
-within the mating pool searching for a mate (time-in) followed by a
-period outside the mating pool (time-out). During time-out, females
-spend some duration of time (\(T_{\mathrm{f}}\)) gestating or rearing
-(hereafter `processing') offspring. We define the number of offspring
-produced by a female per reproductive cycle as \(\lambda\). Since
-females enter time-out after mating, this assumption is equivalent to
-assuming a system with sequential polyandry. For simplicity, we assume
-male time to replenish sperm is negligible, but males can spend some
-duration of time (\(T_{\mathrm{m}}\)) out of the mating pool searching
-for nuptial gifts.
-
-\begin{figure}
-\includegraphics[width=1\linewidth]{inst/img/conceptual_figure} \caption{Conceptual figure inspired by Kokko and Ots (2006) illustrating how the modelling framework maps onto an example of a system wherein nuptial gifts are used, here \textit{Pisaura mirabilis}.
-Males have a probability of obtaining a nuptial gift while in time-out, which will affect their probability of mating while in time-in.
-They return to the mating pool (time-in) at a rate determined by the time spent searching for a nuptial gifts ($T_{\mathrm{m}}$) and leave the mating pool (i.e.
-enter time-out) following the female encounter rate, which is dependent on the ratio of males to females ($\beta$) and the encounter rate ($R$).
-The choosy sex (females) enter the mating pool at a rate depending on the time spent processing offspring ($T_{\mathrm{f}}$) and leave the mating pool (i.e.
-enter time-out) at a rate that is dependent on $\beta$ and $R$.
-Males and females undergo sex-specific mortality $\mu$ during time-in and time-out.
-Image left to right: (1) male \textit{P.
-mirabilis}.
-(2) male \textit{P.
-mirabilis} presenting nuptial gift (white) to female.
-(3) Female \textit{P.
-mirabilis} protecting offspring.
-Photos: Alamy.}\label{fig:unnamed-chunk-2}
-\end{figure}
-
-\hypertarget{criteria-for-male-search-and-female-choosiness}{%
-\subsection{Criteria for male search and female
-choosiness}\label{criteria-for-male-search-and-female-choosiness}}
-
-The probability \(G\) that a male succeeds in securing a nuptial gift is
-defined by,
-
-\begin{equation}
-G = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.
-\end{equation}
-
-In Eq. 1, \(\alpha\) defines the expected search time before
-encountering a nuptial gift. Thus, the probability of finding a nuptial
-gift is higher the more time \(T_{\mathrm{m}}\) is spent searching.
-During time-in, individuals encounter conspecifics at a rate of \(R\). A
-focal individual will therefore encounter conspecifics of the opposite
-sex at a rate of \(R/2\) if the ratio of males to females in the mating
-pool (\(\beta\)) is equal. More generally, males will be encountered at
-a rate of \(R\beta/(\beta+1)\), and females will be encountered at a
-rate of \(R/(\beta+1)\). An example of how the structure of the time-in
-time-out model applies to a system with nuptial gift-giving is given in
-Figure 1. We assume that mating with a nuptial gift increases the
-fitness of each offspring by an increment of \(\gamma\). We proceed to
-find the thresholds \(\gamma_{\mathrm{m}}\) and \(\gamma_{\mathrm{f}}\)
-above which males and females are favoured by selection to search for
-mates with nuptial gifts and exhibit choosiness for nuptial gifts,
-respectively. We show (see Methods) that the initial threshold value of
-\(\gamma\) (\(\gamma_{\mathrm{m}}\)) necessary for males to increase
-their fitness by investing time searching for a nuptial gift (time that
-could otherwise be spent searching for a mate) is,
-
-\begin{equation}
-\gamma_{\mathrm{m}} > \alpha \frac{R}{\beta + 1}.
-\end{equation}
-
-Inequality 2 means that if nuptial gifts are not abundant and thus
-require a long time to find (i.e., high \(\alpha\)), or if males
-encounter many females per unit time (i.e., high \(R / (1+\beta)\)),
-then the nuptial gift must result in a high fitness increment for
-selection to favour gift-searching. In general, when ineq. 2 is
-satisfied, we predict selection to favour the evolution of nuptial
-gift-giving.
-
-We can similarly predict the conditions for which there is selection for
-female choosiness. If \(\gamma\) is sufficiently high, then females
-increase their fitness by rejecting males without gifts and mating only
-with males that provide nuptial gifts. To illustrate, we assume that all
-males in a population search for a duration of \(T_{\mathrm{m}}\), in
-which case the threshold fitness increment for females
-(\(\gamma_{\mathrm{f}}\)) is,
-
-\begin{equation}
-\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}} R \left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}} \right)}.
-\end{equation}
-
-Inequality 3 shows that as offspring processing time
-(\(T_{\mathrm{f}}\)), mate encounter rate (\(R\beta / (\beta + 1)\)), or
-the probability of a male finding a nuptial gift
-(\(1 - \exp(-T_{\mathrm{m}}/\alpha)\) ) decreases, the threshold value
-of fitness above which selection will favour choosiness
-(\(\gamma_{\mathrm{f}}\)) increases. This can be understood intuitively
-by realising that rejecting a prospective male represents an opportunity
-cost for the female. This opportunity cost becomes small if many males
-with gifts are encountered, hence the appearance of the rate at which
-males with gifts are encountered in the denominator. Figure 2 shows how
-\(\gamma_{\mathrm{m}}\) and \(\gamma_{\mathrm{f}}\) change with
-increasing \(\alpha\). For \(\gamma_{\mathrm{f}}\), we assume that males
-search for the expected time required to obtain a nuptial gift
-(\(T_{\mathrm{m}} = \alpha\)). Note that \(\beta\) does not have a
-closed form solution given \(R\), \(T_{\mathrm{f}}\), and
-\(T_{\mathrm{m}}\), so \(\beta\) was calculated using recursion (see
-Methods).
-
-\begin{figure}
-\centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-3-1.pdf}
-\caption{Fitness thresholds above which males increase their fitness by
-searching for nuptial gifts (blue lines; Eq. 2) and females increase
-their fitness by rejecting males that do not offer gifts (red lines; Eq.
-3). Parameter space includes areas in which males do not search for
-nuptial gifts and females are not choosy (A), males search but females
-are not choosy (B), females would be choosy but males do not search (C),
-and males search and females are choosy (D). Arrows in panel a indicate
-the effect of increasing interaction rate (\(R\)), female time-out
-(\(T_{\mathrm{f}}\)), and male search time (\(T_{\mathrm{m}}\)). As an
-example, trajectories for \(T_{\mathrm{f}} = 2\), and
-\(T_{\mathrm{m}} = \alpha\) are shown for values of \(R=2\) (panel a)
-and \(R = 1\) (panel b). Females are assumed to be the choosy sex, which
-is maintained as long as \(\alpha < T_{\mathrm{f}}\).}
-\end{figure}
-
-The analytical framework predicts 4 zones, which are delineated by
-inequalities 2 and 3 and describe the initial thresholds for favouring
-search of nuptial gifts in males and choosiness for nuptial gifts in
-females (Figure 2a). Consequently, the modelling framework gives a
-description of the conditions under which nuptial gift-giving is
-expected to occur (Figure 2a, Zone D) and the conditions under which
-only selection for male searching (Figure 2a, Zone B) or female
-choosiness (Figure 2a, Zone C) are predicted. These results therefore
-highlight the potential for sexual conflict over nuptial gift-giving.
-
-\hypertarget{evolution-of-male-search-and-female-choosiness}{%
-\subsection{Evolution of male search and female
-choosiness}\label{evolution-of-male-search-and-female-choosiness}}
-
-We used an individual-based model (IBM) to simulate the evolution of
-nuptial gift-giving and female choosiness from an ancestral condition in
-which neither exists. The IBM was written to satisfy the assumptions of
-our analytical time-in and time-out model as much as practical (see
-Supporting Information S1). Using the IBM, we modelled a
-spatially-implicit, finite population of females and males. At each time
-step, some individuals enter or remain within the mating pool (time-in),
-where they potentially interact and mate. After mating, males and
-females may leave the mating pool to search for nuptial gifts and to
-produce offspring, respectively (time-out). Mortality occurs with a
-fixed probability in each time step, then a ceiling regulation is
-applied to limit population growth (see Methods).
-
-The rates at which females are encountered by males
-\(R_{\mathrm{f},\mathrm{m}}\) and males with nuptial gifts
-\(R_{\mathrm{m_{G}}, \mathrm{f}}\) are encountered by females are both
-calculated directly from the IBM, thereby modelling how these rates
-might be estimated from empirical data, so the male threshold for
-increasing fitness by searching is,
-
-\begin{equation}
-\gamma_{\mathrm{m, IBM}} > \alpha R_{\mathrm{f},\mathrm{m}}.
-\end{equation}
-
-Similarly, female threshold for increasing fitness by choosiness is,
-
-\begin{equation}
-\gamma_{\mathrm{f, IBM}} > \frac{1}{T_{\mathrm{f}}R_{\mathrm{m_{G}}, \mathrm{f}}}.
-\end{equation}
-
-Consequently, the IBM and the analytical model differ slightly (e.g.,
-time is discrete in the IBM but continuous the analytical model, and in
-the IBM, a fitness increment is applied to the focal female in the form
-of birthrate increase rather than offspring fitness; see Supporting
-Information S1 for details). But the predicted thresholds are
-theoretically equivalent and yield predictions that are qualitatively
-the same (Figure 3).
-
-\begin{figure}
-\centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-4-1.pdf}
-\caption{The coevolution of male search and female choosiness as a
-function of nuptial gift search time (\(\alpha\)). Points show where the
-lower 95\% confidence interval of female choosiness (red) and male
-search (blue) exceeds zero, indicating evolution of choosiness or
-nuptial gift search. Each point includes data from 3200 replicate
-simulations with identical starting conditions. Red and blue lines show
-thresholds above which the mathematical model predicts that females
-should be choosy and males should search, respectively (in agreement
-with Figure 2). Minor deviations between the analytical model and the
-simulation results are expected due to the finite population size, the
-substantial stochasticity inherent to the simulation model, and the
-potential for coevolution (for details, see Supporting Information S1).
-The number of individuals in the population remained at or near carrying
-capacity of \(K = 1000\). In each time step, up to 3000 total pair-wise
-interactions occurred. Expected female processing time was set to
-\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
-the range {[}0.0, 2.0{]} and {[}0.1, 2.0{]}, respectively, were used.}
-\end{figure}
-
-Male thresholds \(\gamma_{\mathrm{m, IBM}}\) given by ineq. 4 accurately
-predict the evolution of searching in the IBM across \(\alpha\) values,
-and the female threshold \(\gamma_{\mathrm{f, IBM}}\) (ineq. 5) predicts
-the evolution of female choice (Figure 3). In other words, IBM
-simulations demonstrate that nuptial gift search in males, and
-choosiness in females, will evolve from an ancestral state of no
-searching and no choosiness in similar parameter space (Figure 3) as
-predicted by the analytical model (Figure 2b). We further ran the IBM
-with realistic values of \(\gamma\), estimated using data from the
-\emph{P. mirabilis} system wherein choosiness among females, and nuptial
-gift search among males, occur (Figure 4). We found that our IBM
-predicts both the evolution of choosiness and nuptial gift searching
-observed in the \emph{P. mirabilis} system.
-
-\begin{figure}
-\centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-5-1.pdf}
-\caption{The joint evolution of male search and female choosiness using
-a nuptial gift fitness increment (\(\gamma\)) that was estimated from
-experimental data for the species \emph{Pisaura mirabilis} (mean
-\(\gamma = 3.29 \pm\) SE via propagation of error for estimates of
-nuptial feeding a non-nuptial feeding groups: {[}1.47; 8.32{]}). Points
-show where the 95\% confidence interval exceeds 0 for female choosiness
-(red) and male search (blue). Each point includes data from 100
-replicate simulations with identical starting conditions. The red line
-shows the threshold above which females should be choosy and the blue
-line shows the threshold above which males should search. As predicted
-by the analytical model, both male search and female choosiness evolved
-for a range of \(\gamma\) values around the empirical estimates. This
-occurs because these values result in a \(\gamma\) above the fitness
-threshold necessary for selection to favour male search of nuptial gifts
-(blue line) and female choosiness (red line). The number of individuals
-in the population remained at or near carrying capacity of \(K = 1000\).
-In each time step, up to 3000 total pair-wise interactions occurred.
-Female processing time was set to \(T_{\mathrm{f}}=2\) time steps, and
-\(\gamma\) and \(\alpha\) values in the {[}0.2, 2.0{]}, respectively,
-were used. The parameter \(\gamma\) was estimated as relative increase
-in offspring production such that \(\gamma\) is the factor by which
-fitness increases (relative to the baseline fitness) given a nuptial
-gift (See Supporting Information S5).}
-\end{figure}
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-Nuptial gift-giving has arisen several times independently throughout
-the animal kingdom (\protect\hyperlink{ref-Lewis2012}{Lewis \& South,
-2012}), so understanding how selection favours nuptial gift giving and
-choosiness is important for a broad range of mating systems. We provide
-a general framework that defines the necessary conditions for selection
-to favour the evolution of nuptial gift-giving. We show that males
-should give nuptial gifts if the value of a nuptial gift exceeds a
-threshold dependent on the encounter rate between males and females and
-the cost or time necessary to find or produce a nuptial gift (see ineq.
-2). This result makes intuitive sense because if males rarely encounter
-females, time searching for a gift is a minor cost relative to mate
-search time. If males encounter many females, it is not worth seeking
-nuptial gifts unless gifts are very valuable since the male will meet
-many prospective mates, and nuptial gift search time might come at a
-cost of decreased mating opportunities. In practice, male biased sex
-ratios will not necessarily favour male search for nuptial gifts if the
-female encounter rate is very high, so the key variable is how often
-males and females encounter each other. If the search time or cost of
-finding a nuptial gift is high, nuptial gifts must be very valuable
-before search is favoured by selection.
-
-\hypertarget{threshold-fitness-values}{%
-\subsection{Threshold fitness values}\label{threshold-fitness-values}}
-
-Importantly, we show that the threshold nuptial gift value at which
-females are favoured to express choosiness for nuptial gifts is rarely
-equivalent to the threshold value at which males are favoured to search
-for nuptial gifts, potentially leading to sexual conflict
-(\protect\hyperlink{ref-Arnqvist2005a}{Arnqvist \& Rowe, 2005};
-\protect\hyperlink{ref-Oliveira2008}{Oliveira \emph{et al.}, 2008}).
-Here, we are defining sexual conflict as occurring when interactions
-between sexes result in situation where both sexes cannot achieve an
-optimal outcome simultaneously
-(\protect\hyperlink{ref-Parker2006}{Parker, 2006}). As an example,
-sizable areas of parameter space exists wherein the female optimum would
-be to exhibit preference for (and receive) nuptial gifts, while the male
-optimum is to not search for (and give) nuptial gifts (see Figure 2a,
-Zone C). This will lead to mate encounters in which gift-less males will
-benefit from mating, but females will not. In many systems, ecological
-variables such as search time required to find a nuptial gift will
-likely depend on prey abundance, which can vary substantially with time
-in some species with nuptial gift-giving
-(\protect\hyperlink{ref-Ghislandi2018}{Ghislandi \emph{et al.}, 2018}).
-Since several ecological variables likely affect the value of these
-thresholds, our results can be seen as providing some formalised
-description of why nuptial gift-giving only occurs in some but not all
-systems.
-
-At first, the analytical model seems to suggests that nuptial gifts must
-cause a very high fitness increase (approximately 25\%) before male
-search and female choosiness is favoured by selection (Figure 2).
-Similarly the IBM model seems to suggest that a fitness benefit of
-approximately 50\% is required (see Figure 3). However, it is important
-to recognise that these thresholds depend on multiple parameters. For
-example, if female processing time (\(T_{\mathrm{f}}\)) is high, the
-female threshold for choosiness with respect to \(\gamma\) drops such
-that male search and female choosiness are favoured at lower \(\gamma\)
-(see Supporting Information S2). If \(T_{\mathrm{f}}\) is sufficiently
-high, then an initially rare gift-giving trait might be favoured by
-selection even if the fitness benefit of a nuptial gift is low. The
-effect that nuptial gifts have on fitness might vary across species, or
-even populations. Effects on female fecundity have been estimated in
-crickets, fireflies, butterflies, and spiders, but these estimates vary
-considerably between species suggesting a large positive effect to no
-effect at all (\protect\hyperlink{ref-Bergstrom2002}{Bergström \&
-Wiklund, 2002}; \protect\hyperlink{ref-Rooney2002}{Rooney \& Lewis,
-2002}; \protect\hyperlink{ref-Maxwell2018}{Maxwell \& Prokop, 2018};
-\protect\hyperlink{ref-Gao2019}{Gao \emph{et al.}, 2019}).
-
-We modelled the evolution of nuptial gift-giving using both a
-mathematical model and an individual-based model. Our mathematical model
-makes simple assumptions about the relationship between nuptial gift
-search time (\(\alpha\)), conspecific encounter rate (\(R\)), female
-processing time (\(T_{\mathrm{f}}\)), and the fitness increment of a
-nuptial gift for offspring fitness (\(\gamma\)). It then derives the
-threshold \(\gamma\) values above which males increase their fitness by
-searching (\(T_{\mathrm{m}} > 0\)) for a nuptial gift
-(\(\gamma_{\mathrm{m}}\)) and females increase their fitness by choosing
-to reject males without gifts (\(\gamma_{\mathrm{f}}\)). In contrast,
-our IBM models individuals over discrete time steps, and key processes
-of nuptial gift acquisition, conspecific encounters, and female
-processing are stochastic and varying among individuals. The
-mathematical model and IBM make qualitatively identical predictions
-(compare Figure 2b versus Figure 3), but differences between the two
-models inevitably lead to quantitative differences for
-\(\gamma_{\mathrm{m}}\) and \(\gamma_{\mathrm{f}}\) thresholds. For
-example, \(\gamma_{\mathrm{f}}\) increased more rapidly with increasing
-\(\alpha\) in the IBM compared to the analytical model. Some differences
-are expected to occur due to stochastic effects inherent to IBMs (e.g.,
-\protect\hyperlink{ref-Wilson2003}{Wilson \emph{et al.}, 2003}). Other
-differences are more likely caused by more subtle assumptions between,
-and limitations of, the two models. In general, the IBM did not do a
-good job of controlling for conspecific interaction rate, making it
-difficult to directly compare \(R\) between models. The IBM also allowed
-for coevolution between male search and female choosiness (Figure 3),
-which was not allowed in the analytical model (Figure 2). It was not our
-goal to exactly recover the quantitative predictions of the analytical
-model in our IBM. Future development of the IBM could further bridge the
-gap between models while also developing new theory on how aspects of
-the system such as explicit space, individual life history, or genetics
-affect the evolution of nuptial gift-giving behaviour.
-
-\hypertarget{nuptial-gift-giving-theory}{%
-\subsection{Nuptial gift-giving
-theory}\label{nuptial-gift-giving-theory}}
-
-When modelling nuptial gift evolution, the challenge is to construct a
-framework that captures the frequency-dependent selection between male
-nuptial gift-giving and female choosiness for nuptial gifts, and we do
-this using a time-in, time-out model. Recent studies have modelled some
-frequency-dependent aspect of nuptial gift giving using evolutionary
-game theory (\protect\hyperlink{ref-MaynardSmith1982}{Maynard Smith,
-1982}; \protect\hyperlink{ref-Vincent2005}{Vincent \& Brown, 2005}). Two
-such studies formulated a quantitative genetics model to study
-evolutionarily stable nuptial gift sizes in populations where the female
-propensity to re-mate was evolving
-(\protect\hyperlink{ref-Kamimura2021}{Kamimura \emph{et al.}, 2021};
-\protect\hyperlink{ref-Iwasa2022}{Iwasa \& Yamaguchi, 2022}). The
-results obtained in these studies complement our results by giving
-equilibrium solutions to the evolutionary stable nuptial gift size,
-whereas we determine the general conditions under which nuptial
-gift-giving will evolve as given by the inequalities we derive.
-
-Other modelling frameworks have made general predictions about sexually
-selected traits, and these predictions are not mutually exclusive to
-those made by our model. For example, the good genes hypothesis predicts
-that costly traits such as nuptial gift-giving can be favoured since
-males enduring the cost of a nuptial gift signals to females that their
-genes confer high fitness precisely because they can afford this cost
-(\protect\hyperlink{ref-Kirkpatrick1996}{Kirkpatrick, 1996};
-\protect\hyperlink{ref-Byers2006}{Byers \& Waits, 2006}; but see
-\protect\hyperlink{ref-Fromhage2022}{Fromhage \& Henshaw, 2022}). In
-other words, costly sexually selected traits are favoured because they
-are indicators of overall genetic quality
-(\protect\hyperlink{ref-Martinossi-Allibert2019}{Martinossi-Allibert
-\emph{et al.}, 2019}). Because of this, nuptial gift-giving could be a
-case of condition-dependence where engaging in nuptial gift-giving is
-only favourable for male in good condition (e.g., males capable of
-successful search (\protect\hyperlink{ref-MaynardSmith1982}{Maynard
-Smith, 1982}; \protect\hyperlink{ref-Engqvist2015}{Engqvist \& Taborsky,
-2015}; \protect\hyperlink{ref-Ghislandi2018}{Ghislandi \emph{et al.},
-2018})). In general, our model demonstrates how nuptial gift-giving
-initially evolves before other mechanisms, such as good gene effects,
-become relevant.
-
-A nuptial gift can also constitute a dishonest signal of good body
-condition since worthless, deceptive nuptial gifts have evolved in
-several systems (\protect\hyperlink{ref-LeBas2005}{LeBas \& Hockham,
-2005}; \protect\hyperlink{ref-Ghislandi2014}{Ghislandi \emph{et al.},
-2014}). This is also the case in \emph{P. mirabilis} where males will
-wrap plant parts or an empty exoskeleton in silk, as opposed to an
-arthropod prey, and use this as a nuptial gift
-(\protect\hyperlink{ref-Albo2011}{Albo \emph{et al.}, 2011};
-\protect\hyperlink{ref-Ghislandi2014}{Ghislandi \emph{et al.}, 2014}).
-In such systems, worthless nuptial gifts have been shown to reduce the
-likelihood that a male is rejected by a female compared to the case
-where no nuptial gift is given. However, males offering worthless
-nuptial gifts may be at a slight disadvantage in sperm competition since
-worthless gifts result in a shorter copulation duration and hence less
-sperm transfer (\protect\hyperlink{ref-Albo2013}{Albo \emph{et al.},
-2013}; \protect\hyperlink{ref-Ghislandi2014}{Ghislandi \emph{et al.},
-2014}). Worthless gifts should not result in any paternal care benefits
-to the male since the offspring he may sire will not gain nutrition from
-a worthless nuptial gift.
-
-Given our modelling framework, worthless nuptial gifts may be expected
-to evolve in cases where females are discriminating in favour of nuptial
-gifts, but the cost of search time for a true nuptial gift is very high
-such that selection will not favour male search. This scenario would
-correspond to zone C of Figure 2 where the value of the nuptial gift
-exceeds the female fitness threshold for choosiness to be favoured, but
-due to high search time, selection will not favour male search for true
-nuptial gifts. Our model also predicts the possibility of the opposite
-scenario, in which males provide nuptial gifts, but females do not
-exhibit preference for nuptial gifts (zone B of Figure 2).
-Fascinatingly, an example of such system has been documented by a recent
-study of the genus \emph{Trechaleoides}, which contains two species with
-true nuptial gift-giving, but a lack of preference for nuptial gifts
-among female (\protect\hyperlink{ref-Martinez2023}{Martínez Villar
-\emph{et al.}, 2023}).
-
-The main drivers of male nuptial gift-giving are thought to be indirect
-fitness benefits and increased success in sperm competition, since
-providing a nuptial gift can result in longer copulation duration which
-is correlated with increased sperm transfer along with female cryptic
-choice promoting males who provide nuptial gifts
-(\protect\hyperlink{ref-Albo2011}{Albo \emph{et al.}, 2011},
-\protect\hyperlink{ref-Albo2013}{2013}). However, nuptial gifts might
-also function to modulate female aggression and prevent sexual
-cannibalism (\protect\hyperlink{ref-Bilde2006}{Bilde \emph{et al.},
-2006}). In some systems, such as \emph{P. mirabilis}, males have been
-shown to reduce the risk of being cannibalised by the female after
-mating when offering a nuptial gift, such that the nuptial gift may
-result in a ``shield effect'', protecting the male
-(\protect\hyperlink{ref-Toft2016}{Toft \& Albo, 2016}).
-
-\hypertarget{empirical-implications}{%
-\subsection{Empirical implications}\label{empirical-implications}}
-
-The simulations parameterised with an experimentally estimated value of
-\(\gamma\) showed evolution of nuptial gift searching in males and
-choosiness for nuptial gifts in females. The model thus predicts that
-\emph{P. mirabilis} living under conditions with the estimated fitness
-value of nuptial gifts should exhibit both search for nuptial gifts and
-choosiness for males with nuptial gifts, and this is what is observed in
-empirical populations. Parameterising \(\gamma\) with data from
-experimental studies may only yield a rough approximation of the true
-\(\gamma\). This is because the estimated value of \(\gamma\) is based
-on data from current populations (rather than ancestral populations,
-which are being simulated), and because the literature is inconclusive
-as to how much (if any) effect nuptial gifts have on female fitness
-(\protect\hyperlink{ref-Maxwell2018}{Maxwell \& Prokop, 2018}). The
-effect of nuptial gifts on female fecundity has been estimated in a
-variety of system such as crickets, fireflies, butterflies and spiders,
-but these estimates vary considerably between species suggesting a large
-positive effect to no effect at all
-(\protect\hyperlink{ref-Bergstrom2002}{Bergström \& Wiklund, 2002};
-\protect\hyperlink{ref-Rooney2002}{Rooney \& Lewis, 2002};
-\protect\hyperlink{ref-Maxwell2018}{Maxwell \& Prokop, 2018};
-\protect\hyperlink{ref-Gao2019}{Gao \emph{et al.}, 2019}).
-
-Our model assumes something akin to sequential polyandry. That is, a
-system wherein female mating and reproduction with multiple males occurs
-in sequence, rather than multiple matings occurring before reproduction.
-In some systems with nuptial gift-giving, females have been documented
-to mate multiple times before reproduction occurs, including the genus
-of bark lice \emph{Neotrogla}
-(\protect\hyperlink{ref-Kamimura2021}{Kamimura \emph{et al.}, 2021}),
-and even our example system of \emph{P. mirabilis} where females will
-sometimes engage in multiple mating before reproducing, especially if
-starved because multiple mating may result in more nuptial gifts
-(\protect\hyperlink{ref-Toft2015}{Toft \& Albo, 2015};
-\protect\hyperlink{ref-Matzke2022}{Matzke \emph{et al.}, 2022}). It is
-unclear what effect (if any) assuming non-sequential polyandry would
-have on the threshold we derive. Under non-sequential polyandry, a
-viable strategy for females might be to accept any male (with or without
-gift) for fertilisation assurance, then exhibit a preference for nuptial
-gifts. This might make choosiness less costly since it would entail less
-of an opportunity cost to be choosy, and this could potentially make
-female preference for nuptial gifts more likely to evolve. Our model
-also assumes that males search in time-out, rather than contribute to
-parental care, which is likely to be accurate for most systems but not
-all. Expanding the model to explore these possibilities would be a
-worthwhile goal for future research.
-
-\hypertarget{conclusion}{%
-\subsection{Conclusion}\label{conclusion}}
-
-Overall, we found that a simple relationship between nuptial gift search
-time and mate encounter rate yields a threshold that determines whether
-selection will favour males that search for nuptial gifts. Similarly, we
-found that the threshold determining whether females will be favoured to
-reject males without nuptial gifts is also dependent on these variables,
-along with offspring processing time. Together, these thresholds
-describe the conditions under which nuptial gift-giving is expected to
-evolve. The applications of these thresholds are numerous. They can be
-used as a starting point for more complex or more system-specific models
-of nuptial gift-giving evolution. They can also provide novel insight
-into how populations can evolve to use worthless or token nuptial gifts.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-\hypertarget{model}{%
-\subsection{Model}\label{model}}
-
-Here we first present more detail for the derivation of fitness
-threshold values \(\gamma_{\mathrm{m}}\) and \(\gamma_{\mathrm{f}}\). We
-then present IBM simulations (see Supporting Information S1 for full
-details). Code for simulations is available on GitHub (see ``Data
-availability'').
-
-\hypertarget{derivation-of-fitness-thresholds}{%
-\subsection{Derivation of fitness
-thresholds}\label{derivation-of-fitness-thresholds}}
-
-We use a time-in and time-out model in which females and males spend
-some time searching for a mate (time-in) followed by a period of cool
-down outside the mating pool (time-out; Figure 1).
-
-After mating, females must spend some time processing offspring
-(\(T_{\mathrm{f}}\)). Male time to replenish sperm is assumed to be
-negligible, but males can spend time out of the mating pool
-(\(T_{\mathrm{m}}\)) to search for a nuptial gift. When males return
-from time-out, they encounter females with some probability that is a
-function of the rate at which an individual encounters conspecifics
-(\(R\)) and the sex ratio (\(\beta\); males/females). Mortality occurs
-for females and males in (\(\mu_{\mathrm{i,f}}\),
-\(\mu_{\mathrm{i,m}}\)) and out (\(\mu_{\mathrm{o,f}}\),
-\(\mu_{\mathrm{o,m}}\)) of the mating pool. Following Kokko \& Ots
-(\protect\hyperlink{ref-Kokko2006}{2006}), we assume
-\(m_{\mathrm{i,f}} = m_{\mathrm{o,f}} = 1\) and
-\(m_{\mathrm{i,m}} = m_{\mathrm{o,m}} = 1\). While this choice is
-arbitrary, we conducted a sensitivity analysis which shows that the
-mortality parameters have no influence on the propensity for male search
-and female choice to evolve (Supporting Information S2). First, we
-describe the fitness consequences of male search time for a nuptial
-gift. We then describe the fitness consequences of female choice to
-accept or reject males based on their provision of a nuptial gift.
-
-\hypertarget{male-fitness}{%
-\subsection{Male fitness}\label{male-fitness}}
-
-During time-out, males have the opportunity to search for a nuptial
-gift. Males can adopt one of two strategies; either search or do not
-search for a nuptial gift. Males with the former strategy continue to
-search until they find a nuptial gift, while males that do not search
-will immediately re-enter the mating pool. In this case, time searching
-for a nuptial gift will come at the cost of mating opportunities but
-might increase offspring fitness. We therefore need to model the
-expected length of time \(E[T_{\mathrm{m}}]\) spent outside of the
-mating pool for males that search for nuptial gifts, which is simply
-\(\alpha\). Note that we can integrate search time \(t\) over the rate
-at which nuptial gifts are encountered (\(\exp(-1/\alpha)\)) to show
-\(E[T_{\mathrm{m}}] = \alpha\),
-
-\[E[T_{\mathrm{m}}] = \int_{0}^{\infty}e^{- \frac{1}{\alpha}t}dt = \alpha.\]
-
-The rate at which a focal male that searches for a nuptial gift
-(\(\mathrm{M_{G}}\)) increases his fitness is therefore the fitness of
-his offspring \((1 + \gamma)\) divided by expected time spent searching
-for a nuptial gift (\(\alpha\)) plus time spent in the mating pool,
-\((\beta + 1)/R\) (recall that females produce \(\lambda\) offspring),
-
-\[W_{\mathrm{M_{G}}} = \lambda \frac{1 + \gamma}{\alpha + \left( \frac{\beta + 1}{R} \right)}.\]
-
-In contrast, a male that does not search for a nuptial gift
-(\(\mathrm{M_{L}}\)) has offspring with lower fitness, but spends less
-time outside of the mating pool,
-
-\[W_{\mathrm{M_{L}}} = \lambda \frac{1}{\left(\frac{\beta+1}{R} \right)} = \lambda \frac{R}{\beta + 1}.\]
-
-We can then determine the conditions for which
-\(W_{\mathrm{M_{G}}} > W_{\mathrm{M_{L}}}\), isolating \(\gamma\) to
-find how large of a fitness benefit must be provided by the nuptial gift
-to make the search cost worthwhile, which simplifies to ineq. 2. When
-this inequality holds, males are favoured to search until they find a
-nuptial gift, which would result in an average search time of
-\(\alpha\). When the male trait is continuous (i.e., males search for
-time period \(T_{\mathrm{m}}\)), it can be shown that the same threshold
-can be reached by evaluating the partial derivative of the male fitness
-function (Supporting Information S3). Hence, the thresholds are
-consistent under different assumptions concerning male searching
-strategy. Selection will cause males to search for nuptial gifts if the
-fitness increase to offspring exceeds the product of search time and
-female encounter rate.
-
-\hypertarget{female-fitness}{%
-\subsection{Female fitness}\label{female-fitness}}
-
-During time-out, females process offspring over a duration of
-\(T_{\mathrm{f}}\) (we assume that \(T_{\mathrm{f}} > \alpha\), else
-females are not the choosy sex). When females re-enter the mating pool,
-they encounter males at a rate of \(R\beta/(\beta + 1)\). If a female
-encounters a male with a nuptial gift, we assume that she will mate with
-him. But if a female encounters a male with no nuptial gift, then she
-might accept or reject the male. If she rejects the male, then she will
-remain in the mating pool. The rate at which a female encounters a male
-with a nuptial gift is,
-
-\[R_{\mathrm{F_{G}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right).\]
-
-We can similarly model the rate at which a female encounters a gift-less
-male,
-
-\[R_{\mathrm{F_{L}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(e^{-\frac{1}{\alpha}T_{m}}\right).\]
-
-Note that we can recover the rate at which a female encounters any male,
-
-\[R \left(\frac{\beta}{\beta + 1}\right) = R \left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + R \left(\frac{\beta}{\beta + 1}\right) \left(e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right).\]
-
-If \(R_{\mathrm{F_{G}}}\) is sufficiently high and
-\(R_{\mathrm{F_{L}}}\) is sufficiently low, then finding a male with a
-gift will be easier than finding a male without one. Also, the expected
-time spent in the mating pool before a focal female encounters a male
-with a gift will be \(1/R_{\mathrm{F_{G}}}\), while the expected time
-spent in the mating pool before a focal female encounters any male will
-be \(1 / (R_{\mathrm{F_{G}}} + R_{\mathrm{F_{L}}})\). Finally, the rates
-at which a female encounters males with and without a gift,
-\(R_{\mathrm{F_{G}}}\) and \(R_{\mathrm{F_{L}}}\), are different from
-the probabilities that a male encounter has or does not have a gift. The
-rate of encounter is no longer relevant in this case because we are
-assuming that an encounter has occurred. Hence, the probability of an
-encountered male having a gift is simply,
-
-\[P(G) = \frac{1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}} = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
-
-Similarly, the probability of an encountered male not having a gift is
-simply,
-
-\[P(L) = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
-
-The rate at which a female increases her fitness by being choosy and
-mating only when she encounters a male with a gift is,
-
-\begin{equation}
-W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}}} + \frac{1}{\mathrm{F_{G}}}.
-\end{equation}
-
-The top of the right-hand side of Eq. 6 gives the fitness increase, and
-the bottom gives the total time it takes to obtain this fitness. The
-\(R_{\mathrm{F_{G}}}\) is inverted because it represents the expected
-time to encountering a male with a gift. We can expand Eq. 6,
-
-\[W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right)}}.\]
-
-If the focal female is not choosy and accepts the first male that she
-encounters, then the rate at which she increases her fitness is,
-
-\[W_{\mathrm{F_{G,L}}} = \lambda \frac{\left(1 + \gamma\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)}}.\]
-
-We then evaluate the conditions under which
-\(W_{\mathrm{F_{G}}} > W_{\mathrm{F_{G,L}}}\). We isolate \(\gamma\) to
-determine how much offspring fitness must be increased to make
-choosiness beneficial (\(\gamma_{\mathrm{f}}\)),
-
-\[\gamma_{\mathrm{f}} > \frac{1 + \frac{1}{\beta}}{D T_{f} \left(1 - e^{-1\frac{1}{\alpha}T_{m}}\right)}.\]
-
-The above can be expressed as Eq. 7 below,
-
-\begin{equation}
-\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}}} R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right).
-\end{equation}
-
-Note that that the expression
-\(R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right)\)
-defines the rate at which a female in the mating pool encounters males
-with nuptial gifts. Hence, female choosiness is ultimately determined by
-time spent out of the mating pool to process offspring
-(\(T_{\mathrm{f}}\)) and the rate at which a female in the mating pool
-encounters males with nuptial gifts.
-
-\hypertarget{operational-sex-ratio}{%
-\subsection{Operational sex ratio}\label{operational-sex-ratio}}
-
-We assume that the sex ratio is equal upon maturation. Given this, Kokko
-\& Monaghan (\protect\hyperlink{ref-Kokko2001}{2001}) show that the
-operational sex ratio depends on the probability of finding an
-individual in time-in,
-
-\begin{equation}
-\beta = \frac{\int_{t = 0}^{\infty} P_{IM}(t)dt}{\int_{t = 0}^{\infty} P_{IF}(t)dt}.
-\end{equation}
-
-In Eq. 8, \(P_{IM}(t)\) and \(P_{IF}(t)\) are the probabilities of
-finding a male and female in time-in, respectively. There is no closed
-form solution to the operational sex ratio, so we used recursion to
-calculate \(\beta\) values for a given \(T_{\mathrm{f}}\),
-\(T_{\mathrm{m}}\), and \(R\) (see Supporting Information S4),
-
-\hypertarget{individual-based-model}{%
-\subsection{Individual-based model}\label{individual-based-model}}
-
-We formulate an individual-based simulation model to test whether the
-predictions made by the analytical time-in time-out model are
-qualitatively the same under a similar simulation model. We use the
-individual-based model to test whether the prediction hold in finite
-populations. The IBM was written in C. All details of the
-initialisation, parameterisation and the specific simulations which we
-run, are described in Supporting Information S1.
-
-We use available experimental data on the effect of nuptial gifts on
-female offspring production to estimate the key parameter \(\gamma\)
-(fitness increment from nuptial gift) and conducted a series of
-simulations where \(\gamma\) was parameterised using this estimated
-value. Details of the estimation of \(\gamma\) are described in
-Supporting Information S5. Separate evolution of male search and female
-choice (i.e., without co-evolution) is simulated in Supporting
-Information S6.
-
-\textbf{Author contributions:} APC and ABD conceived the study. ABD
-constructed the modelling framework with input from APC. APC wrote the
-paper with input from ABD and ABD wrote the IBM model. TB and GB
-provided substantial comments on previous drafts and final text.
-
-\textbf{Acknowledgements:} Anders P. Charmouh was supported by the
-University of Aberdeen. A. Bradley Duthie was supported by the
-University of Stirling. Trine Bilde was supported by The Danish Council
-for Independent Research grant number 4002-00328B. We thank Maria Albo
-for making available data from a previous study which was useful for
-parameter estimating.
-
-\textbf{Data availability:} The simulation software was implemented in C
-and the full source code is available at
-\url{https://github.com/bradduthie/nuptial_gift_evolution}.
-
-\textbf{Competing interests:} The authors declare no competing
-interests.
-
-\textbf{References}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Albo2013}{}}%
-Albo, M.J., Bilde, T. \& Uhl, G. (2013)
-\href{https://doi.org/10.1098/rspb.2013.1735}{{Sperm storage mediated by
-cryptic female choice for nuptial gifts}}. \emph{Proceedings of the
-Royal Society B: Biological Sciences}, \textbf{280}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Albo2019}{}}%
-Albo, M.J., Franco-Trecu, V., Wojciechowski, F.J., Toft, S. \& Bilde, T.
-(2019) \href{https://doi.org/10.1093/beheco/arz040}{{Maintenance of
-deceptive gifts in a natural spider population: Ecological and
-demographic factors}}. \emph{Behavioral Ecology}, \textbf{30},
-993--1000.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Albo2014}{}}%
-Albo, M.J., Toft, S. \& Bilde, T. (2014) {Sexual selection, ecology, and
-evolution of nuptial gifts in spiders}. In \emph{Sexual selection:
-Perspectives and models from the neotropics} (ed. by Macedo, R.H. \&
-Machado, G.). Academic Press, London, pp. 183--200.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Albo2011}{}}%
-Albo, M.J., Winther, G., Tuni, C., Toft, S. \& Bilde, T. (2011)
-\href{https://doi.org/10.1186/1471-2148-11-329}{{Worthless donations:
-Male deception and female counter play in a nuptial gift-giving
-spider}}. \emph{BMC Evolutionary Biology}, \textbf{11}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Arnqvist2005a}{}}%
-Arnqvist, G. \& Rowe, L. (2005) \emph{{Sexual Conflict}}. Princeton
-University Press, Princeton, New Jersey.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bergstrom2002}{}}%
-Bergström, J. \& Wiklund, C. (2002) Effects of size and nuptial gifts on
-butterfly reproduction: Can females compensate for a smaller size
-through male-derived nutrients? \emph{Behavioral Ecology and
-Sociobiology}, \textbf{52}, 296--302.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bilde2006}{}}%
-Bilde, T., Tuni, C., Elsayed, R., Pekár, S. \& Toft, S. (2006)
-\href{https://doi.org/10.1098/rsbl.2005.0392}{{Death feigning in the
-face of sexual cannibalism}}. \emph{Biology Letters}, \textbf{2},
-23--25.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bristowe1926}{}}%
-Bristowe, W. \& Locket, G.H. (1926) {The courtship of British lycosid
-spiders, and its probable significance}. \emph{Proceedings of the
-Zoological Society of London}, \textbf{96}, 317--347.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Byers2006}{}}%
-Byers, J.A. \& Waits, L. (2006)
-\href{https://doi.org/10.1073/pnas.0608184103}{{Good genes sexual
-selection in nature}}. \emph{Proceedings of the National Academy of
-Sciences}, \textbf{103}, 16343--16345.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Clutton-Brock1992}{}}%
-Clutton-Brock, T.H. \& Parker, G.A. (1992)
-\href{https://doi.org/10.1086/417793}{{Potential reproductive rates and
-the operation of sexual selection}}. \emph{Quarterly Review of Biology},
-\textbf{67}, 437--456.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Engqvist2015}{}}%
-Engqvist, L. \& Taborsky, M. (2015)
-\href{https://doi.org/10.1098/rspb.2015.2945}{{The evolution of genetic
-and conditional alternative reproductive tactics}}. \emph{Proceedings of
-the Royal Society B: Biological Sciences}, \textbf{283}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Fromhage2022}{}}%
-Fromhage, L. \& Henshaw, J.M. (2022) The balance model of honest sexual
-signaling. \emph{Evolution}, \textbf{76}, 445--454.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gao2019}{}}%
-Gao, Q., Turnell, B.R., Hua, B. \& Shaw, K.L. (2019) The effect of
-nuptial gift number on fertilization success in a hawaiian swordtail
-cricket. \emph{Behavioral Ecology and Sociobiology}, \textbf{73}, 1--9.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Ghislandi2014}{}}%
-Ghislandi, P.G., Albo, M.J., Tuni, C. \& Bilden, T. (2014)
-\href{https://www.ptonline.com/articles/how-to-get-better-mfi-results}{{Evolution
-of deceit by worthless donations in a nuptial gift-giving spider}}.
-\emph{Current Zoology}, \textbf{60}, 43--51.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Ghislandi2018}{}}%
-Ghislandi, P.G., Pekár, S., Matzke, M., Schulte-Döinghaus, S., Bilde, T.
-\& Tuni, C. (2018) \href{https://doi.org/10.1111/jeb.13284}{{Resource
-availability, mating opportunity and sexual selection intensity
-influence the expression of male alternative reproductive tactics}}.
-\emph{Journal of Evolutionary Biology}, \textbf{31}, 1035--1046.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Iwasa2022}{}}%
-Iwasa, Y. \& Yamaguchi, S. (2022)
-\href{https://doi.org/10.1016/j.jtbi.2021.110939}{{Evolution of male
-nuptial gift and female remating: A quantitative genetic model}}.
-\emph{Journal of Theoretical Biology}, \textbf{533}, 110939.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kamimura2021}{}}%
-Kamimura, Y., Yoshizawa, K., Lienhard, C., Ferreira, R.L. \& Abe, J.
-(2021) \href{https://doi.org/10.1186/s12862-021-01901-x}{{Evolution of
-nuptial gifts and its coevolutionary dynamics with male-like persistence
-traits of females for multiple mating}}. \emph{BMC Ecology and
-Evolution}, \textbf{21}, 1--14.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kirkpatrick1996}{}}%
-Kirkpatrick, M. (1996) Good genes and direct selection in the evolution
-of mating preferences. \emph{Evolution}, \textbf{50}, 2125--2140.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kokko2001}{}}%
-Kokko, H. \& Monaghan, P. (2001)
-\href{https://doi.org/10.1046/j.1461-0248.2001.00212.x}{{Predicting the
-direction of sexual selection}}. \emph{Ecology Letters}, \textbf{4},
-159--165.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kokko2006}{}}%
-Kokko, H. \& Ots, I. (2006) {When not to avoid inbreeding}.
-\emph{Evolution}, \textbf{60}, 467--475.
-
-\leavevmode\vadjust pre{\hypertarget{ref-LeBas2005}{}}%
-LeBas, N.R. \& Hockham, L.R. (2005) \href{https://doi.org/10.1016/j}{{An
-invasion of cheats: the evolution of worthless nuptial gifts}}.
-\emph{Current Biology}, \textbf{15}, 64--67.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lewis2014}{}}%
-Lewis, S.M., Vahed, K., Koene, J.M., Engqvist, L., Bussière, L.F.,
-Perry, J.C., \emph{et al.} (2014)
-\href{https://doi.org/10.1098/rsbl.2014.0336}{{Emerging issues in the
-evolution of animal nuptial gifts}}. \emph{Biology Letters},
-\textbf{10}, 3--5.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lewis2012}{}}%
-Lewis, S. \& South, A. (2012)
-\emph{\href{https://doi.org/10.1016/B978-0-12-394288-3.00002-2}{{The
-Evolution of Animal Nuptial Gifts}}}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lubin2007}{}}%
-Lubin, Y. \& Bilde, T. (2007)
-\href{https://doi.org/10.1016/S0065-3454(07)37003-4}{{The evolution of
-sociality in spiders}}. \emph{Advances in the Study of Behavior},
-\textbf{37}, 83--145.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Martinez2023}{}}%
-Martínez Villar, M., Germil, M., Pavón-Peláez, C., Tomasco, I., Bilde,
-T., Toft, S., \emph{et al.} (2023) Lack of female preference for nuptial
-gifts may have led to loss of the male sexual trait. \emph{Evolutionary
-Biology}, \textbf{50}, 318--331.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Martinossi-Allibert2019}{}}%
-Martinossi-Allibert, I., Rueffler, C., Arnqvist, G. \& Berger, D. (2019)
-\href{https://doi.org/10.1098/rspb.2018.2313}{The efficacy of good genes
-sexual selection under environmental change}. \emph{Proceedings of the
-Royal Society B: Biological Sciences}, \textbf{286}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Matzke2022}{}}%
-Matzke, M., Toft, S., Bechsgaard, J., Pold Vilstrup, A., Uhl, G.,
-Künzel, S., \emph{et al.} (2022) Sperm competition intensity affects
-sperm precedence patterns in a polyandrous gift-giving spider.
-\emph{Molecular Ecology}, \textbf{31}, 2435--2452.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Maxwell2018}{}}%
-Maxwell, M.R. \& Prokop, P. (2018) Fitness effects of nuptial gifts in
-the spider \emph{pisaura mirabilis}: Examination under an alternative
-feeding regime. \emph{The Journal of Arachnology}, \textbf{46},
-404--412.
-
-\leavevmode\vadjust pre{\hypertarget{ref-MaynardSmith1982}{}}%
-Maynard Smith, J. (1982)
-\emph{\href{https://www.ncbi.nlm.nih.gov/pubmed/13761767}{{Evolution and
-the theory of games}}}. Cambridge University Press, Cambridge.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Oliveira2008}{}}%
-Oliveira, R.F., Taborsky, M. \& Brockmann, H.J. (Eds.). (2008)
-\emph{{Alternative reproductive tactics: an integrative approach}}.
-Cambridge University Press, Cambridge.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Parker2006}{}}%
-Parker, G.A. (2006) \href{https://doi.org/10.1098/rstb.2005.1785}{Sexual
-conflict over mating and fertilization: An overview}.
-\emph{Philosophical Transactions of the Royal Society B}, \textbf{361},
-235--259.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Rooney2002}{}}%
-Rooney, J. \& Lewis, S.M. (2002) Fitness advantage from nuptial gifts in
-female fireflies. \emph{Ecological Entomology}, \textbf{27}, 373--377.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Toft2015}{}}%
-Toft, S. \& Albo, M.J. (2015) Optimal numbers of matings: The
-conditional balance between benefits and costs of mating for females of
-a nuptial gift-giving spider. \emph{Journal of Evolutionary Biology},
-\textbf{28}, 457--467.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Toft2016}{}}%
-Toft, S. \& Albo, M.J. (2016)
-\href{https://doi.org/10.1098/rsbl.2015.1082}{{The shield effect:
-Nuptial gifts protect males against pre-copulatory sexual cannibalism}}.
-\emph{Biology Letters}, \textbf{12}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Tuni2013a}{}}%
-Tuni, C., Albo, M.J. \& Bilde, T. (2013)
-\href{https://doi.org/10.1111/jeb.12137}{{Polyandrous females acquire
-indirect benefits in a nuptial feeding species}}. \emph{Journal of
-Evolutionary Biology}, \textbf{26}, 1307--1316.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Vincent2005}{}}%
-Vincent, T.L. \& Brown, J.S. (2005) \emph{{Evolutionary Game Theory,
-Natural Selection, and Darwinian Dynamics}}. Cambridge University Press,
-Cambridge.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wilson2003}{}}%
-Wilson, W.G., Morris, W.F. \& Bronstein, J.L. (2003) {Coexistence of
-mutualists and exploiters on spatial landscapes}. \emph{Ecological
-Monographs}, \textbf{73}, 397--413.
-
-\end{CSLReferences}
-
-\clearpage
-
-\hypertarget{supporting-information}{%
-\section{Supporting Information}\label{supporting-information}}
+\hypertarget{table-of-contents}{%
+\section{Table of Contents}\label{table-of-contents}}
 
@@
 \endhead
-S1: Description of the individual-based simulation model & 18 \\
-S2: Sensitivity analysis of mortality parameters in IBM & 20 \\
-S3: Alternative derivation of male fitness threshold & 29 \\
-S4: Operational sex ratio & 32 \\
-S5: Estimation of key model parameter using experimental data & 33 \\
-S6: Separate evolution of male search and female choice & 34 \\
+S1: Description of the individual-based simulation model & 2 \\
+S2: Sensitivity analysis of mortality parameters in IBM & 4 \\
+S3: Alternative derivation of male fitness threshold & 14 \\
+S4: Operational sex ratio & 16 \\
+S5: Estimation of key model parameter using experimental data & 17 \\
+S6: Separate evolution of male search and female choice & 18 \\
+References & 19 \\
 \bottomrule
@@
 \centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-6-1.pdf}
+\includegraphics{SI_files/figure-latex/unnamed-chunk-2-1.pdf}
 \caption{Figure S2.1: Evolution of both male search (blue) and female
@@
 \centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-7-1.pdf}
+\includegraphics{SI_files/figure-latex/unnamed-chunk-3-1.pdf}
 \caption{Figure S2.2 (\(T_{\mathrm{f}} = 0.5\)): The coevolution of male
@@
 \centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-8-1.pdf}
+\includegraphics{SI_files/figure-latex/unnamed-chunk-4-1.pdf}
 \caption{Figure S2.3 (\(T_{\mathrm{f}} = 10.0\)): The coevolution of
@@
 \centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-9-1.pdf}
+\includegraphics{SI_files/figure-latex/unnamed-chunk-5-1.pdf}
 \caption{Figure S2.4 (\(\psi = 1\)): The coevolution of male search and
@@
 \centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-10-1.pdf}
+\includegraphics{SI_files/figure-latex/unnamed-chunk-6-1.pdf}
 \caption{Figure S2.5 (\(\psi = 2\)): The coevolution of male search and
@@
 \centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-11-1.pdf}
+\includegraphics{SI_files/figure-latex/unnamed-chunk-7-1.pdf}
 \caption{Figure S2.6 (\(\psi = 4\)): The coevolution of male search and
@@
 \centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-12-1.pdf}
+\includegraphics{SI_files/figure-latex/unnamed-chunk-8-1.pdf}
 \caption{Figure S2.7 (\(\psi = 6\)): The coevolution of male search and
@@
 \centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-13-1.pdf}
+\includegraphics{SI_files/figure-latex/unnamed-chunk-9-1.pdf}
 \caption{Figure S2.8 (\(T_{\mathrm{m}} = 0.5\)): The coevolution of male
@@
 \centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-14-1.pdf}
+\includegraphics{SI_files/figure-latex/unnamed-chunk-10-1.pdf}
 \caption{Figure S2.9 (\(T_{\mathrm{m}} = 2.5\)): The coevolution of male
@@
 \centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-16-1.pdf}
+\includegraphics{SI_files/figure-latex/unnamed-chunk-12-1.pdf}
 \caption{Figure S6.1: The separate evolution of male search and female
@@
 
+\clearpage
+
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-Kokko2001}{}}%
+Kokko, H. \& Monaghan, P. (2001)
+\href{https://doi.org/10.1046/j.1461-0248.2001.00212.x}{{Predicting the
+direction of sexual selection}}. \emph{Ecology Letters}, \textbf{4},
+159--165.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Tuni2013a}{}}%
+Tuni, C., Albo, M.J. \& Bilde, T. (2013)
+\href{https://doi.org/10.1111/jeb.12137}{{Polyandrous females acquire
+indirect benefits in a nuptial feeding species}}. \emph{Journal of
+Evolutionary Biology}, \textbf{26}, 1307--1316.
+
+\end{CSLReferences}
+
 \end{document}

### 2024-06-15 SI.Rmd
Separate the manuscript from the supporting information

@@
 output:
-  pdf_document:
-    fig_caption: yes
-    keep_tex: yes
-  html_document: default
   word_document:
@@
     reference_docx: docx_template.docx
+  html_document: default
+  pdf_document:
+    fig_caption: yes
+    keep_tex: yes
 bibliography: nuptial_refs.bib

### 2024-06-15 ms.Rmd
Separate the manuscript from the supporting information

--- 2024-06-03 ms_refs_fixed.Rmd
@@
 output:
-  pdf_document:
-    fig_caption: yes
-    keep_tex: yes
   word_document:
@@
   html_document: default
+  pdf_document:
+    fig_caption: yes
+    keep_tex: yes
 bibliography: nuptial_refs.bib
@@
 <div id="refs"></div>
-
-\clearpage
-
-Supporting Information
-====================================
-
-| Information                                                   | Page |
-|---------------------------------------------------------------|------|
-| S1: Description of the individual-based simulation model      |  27  |
-| S2: Sensitivity analysis of mortality parameters in IBM       |  30  |
-| S3: Alternative derivation of male fitness threshold          |  41  |
-| S4: Operational sex ratio                                     |  43  |
-| S5: Estimation of key model parameter using experimental data |  45  |
-| S6: Separate evolution of male search and female choice       |  46  |
-
-\clearpage
-
-S1: Description of the individual-based simulation model
-------------------------------------
-
-Here we describe the details of initialisation, time-in (mating), time-out (reproduction and nuptial gift search), and mortality. 
-We then summarise the simulations run and data collected.
-
-*Initialisation*
-
-Before the first time step, a population of $N = 1000$ individuals is initialised. 
-Individuals are assigned unique IDs, and each is assigned to be female with a probability of $0.5$, else male. 
-Each individual $i$ is initialised with a starting value of female offspring processing time ($T^{i}_{\mathrm{f}}$), rejection probability of gift-less males ($\rho^{i}$), and male search time ($T^{i}_{\mathrm{m}}$).
-For all simulations, initialised values are set to $T^{i}_{\mathrm{f}} = 2$, $\rho^{i} = 0$, and $T^{i}_{\mathrm{m}} = 0$. 
-All individuals are initalised outside of the mating pool in the first time step $t = 1$. 
-The first time step then proceeds with females immediately entering the mating pool and males either entering the mating pool or searching for nuptial gifts.
-
-*Time-in*
-
-At the start of each time step, females and males in the mating pool remain in it. 
-Females will enter the mating pool after processing offspring, and males will enter it after searching for nuptial gifts (see 'Time-out' below). 
-Up to $\Psi = N\psi$ interactions between individuals can occur in a single time step, where $N$ is population size and $\psi$ is a scaling parameter. 
-In each time step, $\Psi$ pairs of individuals are selected at random to interact.
-For each interaction, two different individuals are randomly selected from the population with equal probability.
-If the selected individuals are of different sexes, and both are in the mating pool, then a mating encounter occurs.
-If the male does not have a nuptial gift, then the female will reject him with a probability of $\rho^{i}$; if rejection occurs, then both individuals stay in the mating pool. 
-If rejection does not occur, or the male has a nuptial gift in the mating encounter, then the individuals mate. 
-Females leave the mating pool and enter time-out to process offspring, and males leave and enter time-out to potentially search for new nuptial gifts (note that females and males might re-enter the mating pool immediately within the same time step given sufficiently low search time; see Time-out below).
-
-*Time-out*
-
-During time-out, offspring production and time outside of the mating pool are realised for each female by sampling from a Poisson distribution.
-A focal female $i$ will produce $Poisson(\lambda)$ offspring if no nuptial gift was provided or $Poisson(\lambda + \gamma)$ if a gift was provided. 
-Females remain outside of the mating pool to process offspring for $Poisson(T^{i}_{\mathrm{f}})$ time steps. 
-Offspring are added to the population immediately, with $\rho^{i}$ and $T^{i}_{\mathrm{m}}$ values that are the average of each parent plus some normally distributed error $\epsilon_{R}$ and $\epsilon_{T_{\mathrm{m}}}$.
-For example,
-
-$$T^{\mathrm{offspring}}_{\mathrm{m}} \sim \frac{T^{\mathrm{mother}}_{\mathrm{m}}  + T^{\mathrm{father}}_{\mathrm{m}}}{2} + N\left(0, \epsilon_{T_{\mathrm{m}}} \right).$$
-
-The variation generated by $\epsilon$ values simulates mutation upon which selection for traits can act. 
-In all simulations, $\epsilon = 0$ if a trait is fixed and $\epsilon = 0.01$ if the trait evolves. 
-Offspring sex is randomly assigned with equal probability as female or male. 
-Female offspring are immediately placed in the mating pool, and male offspring are out of the mating pool to potentially search for nuptial gifts. 
-After a female has spent $T^{i}_{\mathrm{f}}$ time steps outside the mating pool, she will re-enter it.
-
-A focal male $i$ outside the mating pool will enter it if he has searched for a fixed number of $T^{i}_{\mathrm{m}}$ time steps, which is also sampled randomly from a Poisson distribution, $Poisson(T^{i}_{\mathrm{m}})$.
-If $T^{i}_{\mathrm{m}} = 0$, then the male immediately returns to the mating pool (in the same time step). 
-If $T^{i}_{\mathrm{m}} > 0$, then the male must wait outside the mating pool for $Poisson(T^{i}_{\mathrm{m}})$ time steps, but will enter the mating pool with a nuptial gift with a probability,
-
-$$P(G^{i}) = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.$$
-
-Males must always spend $T^{i}_{\mathrm{m}}$ time steps outside of the mating pool regardless of whether or not they are successful in obtaining a nuptial gift.
-
-*Mortality*
-
-At the end of each time step, mortality occurs first with a fixed probability for all adults in the population, then with a probability caused by carrying capacity $K$ applied to all individuals (adults and offspring).
-Mortality occurs in each time step with a fixed probability of $\mu$ regardless of the sex of the individual or its position in or out of the mating pool. 
-If after this fixed mortality is applied, the total population size $N > K$, then individuals are removed at random with equal probability until $N = K$. 
-Following adult mortality, a new time step begins with newly added offspring becoming adults.
-
-*Simulations*
-
-We ran simulations in which male search time and female choosiness evolved from an ancestral state of no searching and no choosiness. 
-In all simulations, $N$ was initialised at 1000 and $K = 1000$. 
-Simulations ran for $t_{max} = 40000$ time steps. 
-We set $T_{\mathrm{f}} = 2$, $\psi = 3$, and $\lambda = 1$ for all simulations, and we simulated across a range of $\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}$ and $\gamma = \{0, 0.1, ..., 1.9, 2.0\}$ parameter values for 3200 replicates.
-Summary statistics for mean trait values, population size, sex ratios, proportion of females and males in and out of the mating pool, and mean number of encounters per female and male within the mating pool were all calculated in the last time step.
-The C code used for simulating these IBMs also allows for the reporting of statistics in each time step. 
-Additionally, it can simulate explicit space and individual movement through the landscape. 
-A neutral evolving trait was also modelled to ensure that the code functioned as intended, and processes were compartmentalised into individual functions to facilitate code testing. 
-All code is publicly available on GitHub (https://github.com/bradduthie/nuptial_gift_evolution).
-
-A set of simulations with a value of $\gamma$ calculated from empirical data was also conducted (100 replicates). 
-Here, $\gamma$ was parameterised using data on egg production as a function of eating nuptial gifts (see below). 
-Additional simulation sets with lower and upper bounds of the estimated $\gamma$ were subsequently run. 
-In the simulation sets with experimentally derived parameter values, all other parameters were identical to previous simulation batches.
-
-We can produce an estimate of the fitness increment obtained by females when receiving a gift ($\hat{\gamma}$) by using data on female *P.
-mirabilis* egg production and hatching success under different feeding regimes from [@Tuni2013a].
-@Tuni2013a found differences in egg production and hatching success in female *P. mirabilis* under different feeding regimes. 
-Assuming these differences in feeding regimes correspond to eating versus not eating nuptial gifts, the mean number of offspring produced by a female who eats nuptial gifts can be calculated (Table 1).
-
-S2: Sensitivity analysis of parameters in IBM
-------------------------------------
-
-We investigated the sensitivity of our results to individual mortality during time-in ($\mu_{\mathrm{in}}$) and time-out ($\mu_{\mathrm{out}}$), female processing time ($T_{\mathrm{f}}$), potential for interactions between conspecifics ($\psi$), and initialised male search time ($T_{\mathrm{m}}$).
-Across all of these simulations, there were challenges with statistical power.
-Evidence for the evolution of male search (blue points in figures) and female choosiness (red points in figures) was determined by the lower 95\% bootstrapped confidence interval of $T_{\mathrm{m}}$ and $T_{\mathrm{f}}$ values being greater than zero, respectively.
-This required a lot of replicate simulations in the main text (Figure 3), especially for values just above predicted thresholds and for female choosiness.
-Computation time was a limiting factor, even using a compiled language (C) and with access to a computing cluster.
-Absence of points above threshold values are not necessarily evidence that evolution of male search or female choosiness is not predicted to evolve in these regions of parameter space, but it does indicate that evolution of these traits is not necessarily assured given the stochasticity inherent to the IBM.
-Additional simulations can be conducted using the C code in the 'src' folder of the GitHub repository (https://github.com/bradduthie/nuptial_gift_evolution).
-Below, we explain the parameter values used in the sensitivity analysis in more detail.
-
-*Mortality*
-
-We conducted a sensitivity analysis of the effect of the mortality parameters $\mu_{\mathrm{in}}$ and $\mu_{\mathrm{out}}$ (the probability of mortality in time-in and time-out, respectively, which we assumed to be equal for all individuals) on the evolution of male search and female choice using the IBM (See S1).
-The results revealed no correlation between the value of the mortality parameters and the evolution of male search or female choice (Fig. S2.1).
-
-*Female processing time*
-
-We also conducted a sensitivity analysis of female processing time $T_{\mathrm{f}}$. 
-To do this, we ran simulations at default values, but with $T_{\mathrm{f}} = 0.4$ (Figure S4.2) and $T_{\mathrm{f}} = 10.0$ (Figures S4.3).
-
-*Interactions between conspecifics*
-
-We conducted a sensitivity analysis on the encounter rate between conspecifics ($R$) by varying the value of $\psi$ (see S1).
-Under default simulations, $\psi = 3$.
-We also ran simulations in which $\psi = 1$ (Figure S4.4), $\psi = 2$ (Figure S4.5), $\psi = 4$ (Figure S4.6), and $\psi = 6$ (Figure S4.7), with all other parameters being set to default values.
-
-*Initialised male search time*
-
-Lastly, we conducted a sensitivity analysis on initialised male search time ($T_{\mathrm{m}}$).
-To do this, we ran simulations at default values, but initialised all males at $T_{\mathrm{m}} = 0.5$ (Figure S4.8) or $T_{\mathrm{m}} = 2.5$ (S4.9). 
-Note that under these initialisation conditions, it no longer makes sense to test whether or not $T_{\mathrm{m}}$ evolves to positive values, so we do not show predicted male search thresholds and focus only on female choosiness.
-Interestingly, while predictions given initialised $T_{\mathrm{m}} = 0.5$ are quite close for female choosiness thresholds, female choosiness does not appear to evolve given $T_{\mathrm{m}} = 2.5$.
-This might be due to low selection pressure to reject males without gifts due to their low frequency.
-In other words, while females would benefit from a strategy of rejecting gift-less males, a lack of realised encounters with gift-less males preclude the evolution of sustained selection for choosiness.
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.1: Evolution of both male search (blue) and female choice (red) under different combinations of the mortality rates $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$ (mortality in time-in and out, respectively).
-The y-axis is the threshold fitness that leads to evolution of male search (blue) or female choice (red).
-The results show noise, but no correlation between the value of the mortality parameters and the propensity for male search and/or female choice to evolve.
-For each of the $25 \\times 20$ combinations of $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$, 1600 replicate simulations were run."}
-SUMO <- read.csv("inst/SI_mortality.csv");
-mort_combn   <- paste(SUMO[,1], SUMO[,2]);
-mort_label   <- unique(paste(SUMO[,1], ", ", SUMO[,2], sep = ""));
-TM_vals      <- tapply(X = SUMO[,4],  INDEX = mort_combn, FUN = mean);
-m_vals       <- tapply(X = SUMO[,14], INDEX = mort_combn, FUN = mean);
-beta_vals    <- tapply(X = SUMO[,15], INDEX = mort_combn, FUN = mean);
-Male_M       <- tapply(X = SUMO[,16], INDEX = mort_combn, FUN = mean);
-Female_M     <- tapply(X = SUMO[,17], INDEX = mort_combn, FUN = mean);
-Mf_nupt      <- tapply(X = SUMO[,18], INDEX = mort_combn, FUN = mean);
-Mf_nonupt    <- tapply(X = SUMO[,19], INDEX = mort_combn, FUN = mean);
-male_search  <- as.numeric(which(SUMO[,5] > 0 & SUMO[,6] > 0));
-fem_choose   <- as.numeric(which(SUMO[,8] > 0 & SUMO[,9] > 0));
-mimmom       <- unique(cbind(SUMO[,1], SUMO[,2]));
-
-mm <- SUMO[male_search,];
-mp <- NULL;
-for(i in 1:dim(mm)[1]){
-  rval <- which(mm[i, 1] == mimmom[,1] & mm[i, 2] == mimmom[,2]);
-  mp   <- rbind(mp, c(rval, mm[i, 3]));
-}
-
-ff <- SUMO[fem_choose,];
-fp <- NULL;
-for(i in 1:dim(ff)[1]){
-    rval <- which(ff[i, 1] == mimmom[,1] & ff[i, 2] == mimmom[,2]);
-    fp   <- rbind(fp, c(rval, ff[i, 3]));
-}
-
-par(mar = c(8, 5, 1, 1));
-plot(x = mp[,1], y = mp[,2], pch = 20, ylim = c(0, 2), col = "blue",
-     xlab = "", ylab = "", xaxt = "n", cex.lab = 1.25);
-points(x = fp[,1], y = fp[,2], cex = 2.5, col = "red", pch = 20);
-points(x = mp[,1], y = mp[,2], cex = 1.5, col = "blue", pch = 20);
-axis(side = 1, labels = mort_label, at = 1:25, las = 2);
-mtext(text = expression(paste("Mortality combination (",mu["in"],", ", 
-                              mu["out"],")")), side = 1, line = 6.5, 
-      cex = 1.25); 
-mtext(text = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                              ")")), side = 2, line = 2.5, cex = 1.25); 
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.2 ($T_{\\mathrm{f}} = 0.4$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 720 replicate simulations with identical starting conditions.
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Up to 3000 interactions occur between individuals in each time step ($\\psi = 3$), potentially resulting in a mating interaction.
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=0.4$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.5, 1.5] and [0.1, 2.1], respectively, were used."}
-SUMM_Tf0pt4 <- read.csv("inst/SI_Tf_0pt4.csv");
-
-alpha_vals <- sort(unique(SUMM_Tf0pt4[,1]));
-TM_vals    <- tapply(X = SUMM_Tf0pt4[,3],  INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-m_vals     <- tapply(X = SUMM_Tf0pt4[,13], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-beta_vals  <- tapply(X = SUMM_Tf0pt4[,14], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-Male_M     <- tapply(X = SUMM_Tf0pt4[,15], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-Female_M   <- tapply(X = SUMM_Tf0pt4[,16], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-Mf_nupt    <- tapply(X = SUMM_Tf0pt4[,17], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-Mf_nonupt  <- tapply(X = SUMM_Tf0pt4[,18], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 0.4);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2.1));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Tf0pt4)[1]){
-  if(SUMM_Tf0pt4[i, 4] > 0 & SUMM_Tf0pt4[i, 5] > 0){
-    points(x = SUMM_Tf0pt4[i, 1], y = SUMM_Tf0pt4[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Tf0pt4)[1]){
-  if(SUMM_Tf0pt4[i, 7] > 0 & SUMM_Tf0pt4[i, 8] > 0){
-    points(x = SUMM_Tf0pt4[i, 1], y = SUMM_Tf0pt4[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.3 ($T_{\\mathrm{f}} = 10.0$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 720 replicate simulations with identical starting conditions.
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Up to 3000 interactions occur between individuals in each time step ($\\psi = 3$), potentially resulting in a mating interaction.
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=10.0$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.5, 1.5] and [0.1, 2.1], respectively, were used."}
-SUMM_Tf10 <- read.csv("inst/SI_Tf_10pt0.csv");
-
-alpha_vals <- sort(unique(SUMM_Tf10[,1]));
-TM_vals    <- tapply(X = SUMM_Tf10[,3],  INDEX = SUMM_Tf10[,1], FUN = mean);
-m_vals     <- tapply(X = SUMM_Tf10[,13], INDEX = SUMM_Tf10[,1], FUN = mean);
-beta_vals  <- tapply(X = SUMM_Tf10[,14], INDEX = SUMM_Tf10[,1], FUN = mean);
-Male_M     <- tapply(X = SUMM_Tf10[,15], INDEX = SUMM_Tf10[,1], FUN = mean);
-Female_M   <- tapply(X = SUMM_Tf10[,16], INDEX = SUMM_Tf10[,1], FUN = mean);
-Mf_nupt    <- tapply(X = SUMM_Tf10[,17], INDEX = SUMM_Tf10[,1], FUN = mean);
-Mf_nonupt  <- tapply(X = SUMM_Tf10[,18], INDEX = SUMM_Tf10[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 10);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2.1));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Tf10)[1]){
-  if(SUMM_Tf10[i, 4] > 0 & SUMM_Tf10[i, 5] > 0){
-    points(x = SUMM_Tf10[i, 1], y = SUMM_Tf10[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Tf10)[1]){
-  if(SUMM_Tf10[i, 7] > 0 & SUMM_Tf10[i, 8] > 0){
-    points(x = SUMM_Tf10[i, 1], y = SUMM_Tf10[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.4 ($\\psi = 1$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 720 replicate simulations with identical starting conditions.
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Up to 1000 interactions occur between individuals in each time step ($\\psi = 1$), potentially resulting in a mating interaction.
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
-SUMM_Nexp1   <- read.csv("inst/SI_Nexp_1.csv");
-
-alpha_vals   <- sort(unique(SUMM_Nexp1[,1]));
-TM_vals      <- tapply(X = SUMM_Nexp1[,3],  INDEX = SUMM_Nexp1[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_Nexp1[,13], INDEX = SUMM_Nexp1[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_Nexp1[,14], INDEX = SUMM_Nexp1[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_Nexp1[,15], INDEX = SUMM_Nexp1[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_Nexp1[,16], INDEX = SUMM_Nexp1[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_Nexp1[,17], INDEX = SUMM_Nexp1[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_Nexp1[,18], INDEX = SUMM_Nexp1[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2.1));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Nexp1)[1]){
-  if(SUMM_Nexp1[i, 4] > 0 & SUMM_Nexp1[i, 5] > 0){
-    points(x = SUMM_Nexp1[i, 1], y = SUMM_Nexp1[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Nexp1)[1]){
-  if(SUMM_Nexp1[i, 7] > 0 & SUMM_Nexp1[i, 8] > 0){
-    points(x = SUMM_Nexp1[i, 1], y = SUMM_Nexp1[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.5 ($\\psi = 2$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 720 replicate simulations with identical starting conditions.
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Up to 2000 interactions occur between individuals in each time step ($\\psi = 2$), potentially resulting in a mating interaction.
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
-SUMM_Nexp2   <- read.csv("inst/SI_Nexp_2.csv");
-
-alpha_vals   <- sort(unique(SUMM_Nexp2[,1]));
-TM_vals      <- tapply(X = SUMM_Nexp2[,3],  INDEX = SUMM_Nexp2[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_Nexp2[,13], INDEX = SUMM_Nexp2[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_Nexp2[,14], INDEX = SUMM_Nexp2[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_Nexp2[,15], INDEX = SUMM_Nexp2[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_Nexp2[,16], INDEX = SUMM_Nexp2[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_Nexp2[,17], INDEX = SUMM_Nexp2[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_Nexp2[,18], INDEX = SUMM_Nexp2[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2.1));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Nexp2)[1]){
-  if(SUMM_Nexp2[i, 4] > 0 & SUMM_Nexp2[i, 5] > 0){
-    points(x = SUMM_Nexp2[i, 1], y = SUMM_Nexp2[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Nexp2)[1]){
-  if(SUMM_Nexp2[i, 7] > 0 & SUMM_Nexp2[i, 8] > 0){
-    points(x = SUMM_Nexp2[i, 1], y = SUMM_Nexp2[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.6 ($\\psi = 4$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 720 replicate simulations with identical starting conditions.
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Up to 4000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 4$).
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
-SUMM_Nexp4   <- read.csv("inst/SI_Nexp_4.csv");
-
-alpha_vals   <- sort(unique(SUMM_Nexp4[,1]));
-TM_vals      <- tapply(X = SUMM_Nexp4[,3],  INDEX = SUMM_Nexp4[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_Nexp4[,13], INDEX = SUMM_Nexp4[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_Nexp4[,14], INDEX = SUMM_Nexp4[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_Nexp4[,15], INDEX = SUMM_Nexp4[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_Nexp4[,16], INDEX = SUMM_Nexp4[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_Nexp4[,17], INDEX = SUMM_Nexp4[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_Nexp4[,18], INDEX = SUMM_Nexp4[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2.1));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Nexp4)[1]){
-  if(SUMM_Nexp4[i, 4] > 0 & SUMM_Nexp4[i, 5] > 0){
-    points(x = SUMM_Nexp4[i, 1], y = SUMM_Nexp4[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Nexp4)[1]){
-  if(SUMM_Nexp4[i, 7] > 0 & SUMM_Nexp4[i, 8] > 0){
-    points(x = SUMM_Nexp4[i, 1], y = SUMM_Nexp4[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.7 ($\\psi = 6$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 720 replicate simulations with identical starting conditions.
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Up to 6000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 6$).
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
-SUMM_Nexp6   <- read.csv("inst/SI_Nexp_6.csv");
-
-alpha_vals   <- sort(unique(SUMM_Nexp6[,1]));
-TM_vals      <- tapply(X = SUMM_Nexp6[,3],  INDEX = SUMM_Nexp6[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_Nexp6[,13], INDEX = SUMM_Nexp6[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_Nexp6[,14], INDEX = SUMM_Nexp6[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_Nexp6[,15], INDEX = SUMM_Nexp6[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_Nexp6[,16], INDEX = SUMM_Nexp6[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_Nexp6[,17], INDEX = SUMM_Nexp6[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_Nexp6[,18], INDEX = SUMM_Nexp6[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2.1));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Nexp6)[1]){
-  if(SUMM_Nexp6[i, 4] > 0 & SUMM_Nexp6[i, 5] > 0){
-    points(x = SUMM_Nexp6[i, 1], y = SUMM_Nexp6[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Nexp6)[1]){
-  if(SUMM_Nexp6[i, 7] > 0 & SUMM_Nexp6[i, 8] > 0){
-    points(x = SUMM_Nexp6[i, 1], y = SUMM_Nexp6[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.8 ($T_{\\mathrm{m}} = 0.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 1600 replicate simulations with identical starting conditions.
-The red line shows the threshold above which the mathematical model predicts that females should be choosy (male thresholds for search are not shown because simulations were initialised with males already searching for nuptial gifts).
-Up to 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 3$).
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
-SUMM_Tm05   <- read.csv("inst/SI_Tm_0pt5.csv");
-
-alpha_vals   <- sort(unique(SUMM_Tm05[,1]));
-TM_vals      <- tapply(X = SUMM_Tm05[,3],  INDEX = SUMM_Tm05[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_Tm05[,13], INDEX = SUMM_Tm05[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_Tm05[,14], INDEX = SUMM_Tm05[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_Tm05[,15], INDEX = SUMM_Tm05[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_Tm05[,16], INDEX = SUMM_Tm05[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_Tm05[,17], INDEX = SUMM_Tm05[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_Tm05[,18], INDEX = SUMM_Tm05[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 1.6));
-
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Tm05)[1]){
-  if(SUMM_Tm05[i, 4] > 0 & SUMM_Tm05[i, 5] > 0){
-    points(x = SUMM_Tm05[i, 1], y = SUMM_Tm05[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Tm05)[1]){
-  if(SUMM_Tm05[i, 7] > 0 & SUMM_Tm05[i, 8] > 0){
-    points(x = SUMM_Tm05[i, 1], y = SUMM_Tm05[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.9 ($T_{\\mathrm{m}} = 2.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 1600 replicate simulations with identical starting conditions.
-The red line shows the threshold above which the mathematical model predicts that females should be choosy (male thresholds for search are not shown because simulations were initialised with males already searching for nuptial gifts).
-Up to 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 3$).
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
-SUMM_Tm2p5   <- read.csv("inst/SI_Tm_2pt5.csv");
-
-alpha_vals   <- sort(unique(SUMM_Tm2p5[,1]));
-TM_vals      <- tapply(X = SUMM_Tm2p5[,3],  INDEX = SUMM_Tm2p5[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_Tm2p5[,13], INDEX = SUMM_Tm2p5[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_Tm2p5[,14], INDEX = SUMM_Tm2p5[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_Tm2p5[,15], INDEX = SUMM_Tm2p5[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_Tm2p5[,16], INDEX = SUMM_Tm2p5[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_Tm2p5[,17], INDEX = SUMM_Tm2p5[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_Tm2p5[,18], INDEX = SUMM_Tm2p5[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 1.6));
-
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Tm2p5)[1]){
-  if(SUMM_Tm2p5[i, 4] > 0 & SUMM_Tm2p5[i, 5] > 0){
-    points(x = SUMM_Tm2p5[i, 1], y = SUMM_Tm2p5[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Tm2p5)[1]){
-  if(SUMM_Tm2p5[i, 7] > 0 & SUMM_Tm2p5[i, 8] > 0){
-    points(x = SUMM_Tm2p5[i, 1], y = SUMM_Tm2p5[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-S3: Alternative derivation of male fitness threshold
-------------------------------------
-
-In the main text, we assumed that males made the decision to search or not search for a nuptial gift.
-The expected length of time for which searching males are expected to remain outside of the mating pool is $E[T_{\mathrm{m}}] = \alpha$ (see Methods).
-Alternatively, we can assume that males search for a period of $T_{\mathrm{m}}$ and spend this full duration of $T_{\mathrm{m}}$ in the time-out phase, even if they succeed in finding a nuptial gift.
-The probability that a male obtains a nuptial gift during this time is modelled in Eq. 1,
-
-$$P(G) = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
-
-In Eq. 1, $\alpha$ is the amount of time expected to pass before a male encounters a nuptial gift. 
-We assume that a male will only enter the mating pool with no gift if they are unsuccessful in obtaining a gift, so the probability that a male obtains no gift after $T_{\mathrm{m}}$ is,
-
-$$P(L) = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
-
-We assume that the fitness increments to offspring associated with receiving a nuptial gift versus no nuptial gift are $1 + \gamma$ and 1, respectively. 
-The rate at which males increase their fitness can then be defined as the expected fitness increment from their nuptial gift search divided by $T_{\mathrm{m}}$ plus the time spent in the mating pool waiting to encounter a mate,
-
-$$W_{\mathrm{m}} = \lambda \frac{P(G)\left(1 + \gamma\right) + P(L)}{T_{\mathrm{m}} + \left( \frac{\beta + 1}{R} \right)}.$$
-
-Our objective now is to determine the conditions under which a focal male increases its fitness by searching for a nuptial gift ($T_{\mathrm{m}}>0$) in a population of resident males that do not search ($T_{\mathrm{m}}=0$).
-Females are assumed to exhibit no choice in males with versus without nuptial gifts.
-Under such conditions, male fitness cannot be affected by female choice, so selection to increase $T_{\mathrm{m}}>0$ must be based solely on $\alpha$, $\beta$, $R$, and $\gamma$.
-
-To determine under what conditions male inclusive fitness increases with nuptial gift search time, we can differentiate $W_{\mathrm{m}}$ with respect to $T_{\mathrm{m}}$,
-
-$$\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda\frac{\gamma\left(\frac{\frac{T_{\mathrm{m}} + \frac{\beta + 1}{R}}{\alpha} + 1}{e^{\frac{1}{\alpha}T_{\mathrm{m}}}} - 1\right) - 1}{\left(T_{\mathrm{m}} + \frac{\beta + 1}{R} \right)^{2}}.$$
-
-Because $T_{\mathrm{m}} = 0$, the above simplifies,
-
-$$\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda \frac{\frac{R\gamma\left(\beta + 1\right)}{\alpha} - R^{2}}{\left(1 + \beta \right)^{2}}.$$
-
-We can re-arrange the above,
-
-$$\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)} - \lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}}.$$
-
-Note that if $R = 0$ or $\lambda = 0$, then, trivially, no change in fitness occurs (since females and males cannot mate or do not produce offspring). 
-Fitness is increased by searching for nuptial gifts when $\gamma$ is high, scaled by the expect search time needed to find a nuptial gift. 
-A second term on the right-hand side is subtracted, which reflects a loss in fitness proportional to the encounter rate of potential mates in the mating pool.
-The conditions under which male inclusive fitness increases by searching for a nuptial gift are found by setting $\partial W_{\mathrm{m}}/\partial T_{\mathrm{m}} = 0$ and solving for $\gamma$ to get Eq.
-2 in the main text.
-
-\clearpage
-
-S4: Operational sex ratio
-------------------------------------
-
-We assume that the ratio of males to females is the same upon individual maturation.
-Consequently, the operational sex ratio $\beta$ will be a function of $R$, $T_{\mathrm{f}}$, and $T_{\mathrm{m}}$ because these parameters determine the density of females and males in the mating pool versus outside of the mating pool.
-We start with the definition of $\beta$ as being the probability of finding an individual in time-in [@Kokko2001],
-
-$$\beta = \frac{\int_{t=0}^{\infty}P_{IM}(t)dt}{\int_{t=0}^{\infty}P_{IF}(t)dt}$$
-
-We can substitute the equations for $P_{IM}(t)$ and $P_{IF}(t)$, which define the probabilities of males and females being within the mating pool at time $t$, respectively.
-
-We can therefore calculate $\beta$ as below,
-
-$$\beta = \frac{\left( \frac{\left(\frac{\beta + 1}{R}\right)}{T_{\mathrm{m}} + \left(\frac{\beta + 1}{R}\right)} \right)}{\left( \frac{\left(R \frac{\beta}{\beta + 1}\right)}{T_{\mathrm{f}} + \left(R \frac{\beta}{\beta + 1}\right)} \right)}.$$
-
-This can be simplified,
-
-$$\beta = \frac{\left(\beta\left(R + T_{f}\right) + T_{f}\right)\left(\beta + 1\right)}{\beta \left(R^{2}T_{m} + R\right) + \beta^{2}R}.$$
-
-There is no closed form solution for $\beta$, but a recursive algorithm can be used to calculate $\beta$ to an arbitrary degree of precision.
-
-```{r}
-recursive_b <- function(B, D, Tf, Tm, crit = 0.0001, maxit = 9999){
-  conv <- 1;
-  iter <- 0;
-  while(conv > crit & iter < maxit){
-    Fe   <- D * (B / (1 + B));
-    Me   <- (1 + B) / D;
-    Bn   <- (Me / (Tm + Me)) / (Fe / (Tf + Fe));
-    iter <- iter + 1;
-    conv <- abs(Bn - B);
-    B    <- Bn;
-  }
-  return(list(B = B, conv = conv, iter = iter));
-}
-```
-
-We used the above function to calculate values of $\beta$ for the analytical model.
-
-\clearpage
-
-S5: Estimation of key model parameters using experimental data
--------------------------------------
-
-Estimates showing the mean number of offspring produced by female *Pisaura mirabilis* that ate nuptial gifts and females who did not. 
-Means were calculated with raw data from @Tuni2013a and results are shown $\pm$ SE (Table 1).
-Under these assumptions, the relative gain in fitness from receiving nuptial gifts for a female is,
-
-$$\hat{\delta_\mathrm{f}} = \frac{25.74}{6.00} = 4.29$$
-
-Since the baseline fitness is 1, the increase in fitness resulting from a nuptial gift then becomes,
-
-$$\hat{\gamma} = \hat{\delta_{\mathrm{f}}} - 1 = 3.29.$$
-
-The value 3.29 was used to parameterise $\gamma$ for a set of simulations (Figure 4 in the main text).
-
-|                                 | Received nuptial gift | Received no nuptial gift |
-|---------------------------------|-----------------------|--------------------------|
-| Expected number of hatched eggs | $25.74 \pm 0.96$      | $6.00 \pm 2.1$           |
-
-Table 1: Estimates showing mean number of offspring produced by female *P.
-mirabilis* that ate nuptial gifts and females who did not.
-Means were calculated with raw data from @Tuni2013a and results are shown $\pm$ SE.
-
-\clearpage
-
-S6: Separate evolution of male search and female choice
--------------------------------------
-
-We used the individual-based simulation model (see Supporting Information S1) to unpack the effect of coevolution on the evolution of male search and female choice. 
-Here we replicated the simulations shown in the main text under the condition where only one trait at a time was allowed to evolve and studied how this affected the trait evolution.
-
-First, we submitted a set of simulations wherein male search did not evolve, but was fixed at different values (see Fig. S6.1). 
-Next, we ran the same set of simulations wherein male search evolved, but female choice was not possible. 
-The results thus show how each trait evolves in the absence of any coevolution (Fig. S6.1).
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S6.1: The separate evolution of male search and female choosiness as a function of nuptial gift search time.
-Points show where the lower 95% confidence interval of male search (blue) and female choosiness (red) exceeds zero, indicating evolution of nuptial gift search or choosiness.
-Each point includes data from $2 \\times 1600$ replicate simulations with identical starting conditions.
-In the first batch, male search was constant and initialized at $T_{\\mathrm{m}} = \\alpha$, and female choice was evolving.
-In the second batch, male search was evolving, and there was no option for female choice.
-The parameters $T_{\\mathrm{f}}=2$, and $\\gamma$ and $\\alpha$ values were set within the range [0.1, 2.0] and [0.3, 1.7], respectively."}
-SUMM_m <- read.csv("inst/summary_male_evolving.csv");
-SUMM_f <- read.csv("inst/summary_female_evolving.csv");
-# Males
-TM_vals      <- tapply(X = SUMM_m[,3],  INDEX = SUMM_m[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_m[,13], INDEX = SUMM_m[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_m[,14], INDEX = SUMM_m[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_m[,15], INDEX = SUMM_m[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_m[,16], INDEX = SUMM_m[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_m[,17], INDEX = SUMM_m[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_m[,18], INDEX = SUMM_m[,1], FUN = mean);
-alpha_vals   <- sort(unique(SUMM_m[,1]));
-
-g_m <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-
-# Females 
-TM_vals      <- tapply(X = SUMM_f[,3],  INDEX = SUMM_f[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_f[,13], INDEX = SUMM_f[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_f[,14], INDEX = SUMM_f[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_f[,15], INDEX = SUMM_f[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_f[,16], INDEX = SUMM_f[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_f[,17], INDEX = SUMM_f[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_f[,18], INDEX = SUMM_f[,1], FUN = mean);
-alpha_vals   <- sort(unique(SUMM_f[,1]));
-
-g_f <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_m, type = "l", lwd = 2, cex.lab = 1.25,
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2), col = "blue");
-
-for(i in 1:dim(SUMM_m)[1]){
-  if(SUMM_m[i, 4] > 0 & SUMM_m[i, 5] > 0){
-    points(x = SUMM_m[i, 1], y = SUMM_m[i, 2], cex = 3, pch = 20, col = "blue");
-  }
-}
-
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red");
-
-for(i in 1:dim(SUMM_f)[1]){
-  if(SUMM_f[i, 7] > 0 & SUMM_f[i, 8] > 0){
-    points(x = SUMM_f[i, 1], y = SUMM_f[i, 2], cex = 2, pch = 20, col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}

### 2024-06-15 ms.tex
Separate the manuscript from the supporting information

--- 2024-06-03 ms_refs_fixed.tex
@@
 \usepackage[margin=1in]{geometry}
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{248,248,248}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 \centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-3-1.pdf}
+\includegraphics{ms_files/figure-latex/unnamed-chunk-3-1.pdf}
 \caption{Fitness thresholds above which males increase their fitness by
@@
 \centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-4-1.pdf}
+\includegraphics{ms_files/figure-latex/unnamed-chunk-4-1.pdf}
 \caption{The coevolution of male search and female choosiness as a
@@
 \centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-5-1.pdf}
+\includegraphics{ms_files/figure-latex/unnamed-chunk-5-1.pdf}
 \caption{The joint evolution of male search and female choosiness using
@@
 
-\clearpage
-
-\hypertarget{supporting-information}{%
-\section{Supporting Information}\label{supporting-information}}
-
-\begin{longtable}[]{@{}ll@{}}
-\toprule
-Information & Page \\
-\midrule
-\endhead
-S1: Description of the individual-based simulation model & 27 \\
-S2: Sensitivity analysis of mortality parameters in IBM & 30 \\
-S3: Alternative derivation of male fitness threshold & 41 \\
-S4: Operational sex ratio & 43 \\
-S5: Estimation of key model parameter using experimental data & 45 \\
-S6: Separate evolution of male search and female choice & 46 \\
-\bottomrule
-\end{longtable}
-
-\clearpage
-
-\hypertarget{s1-description-of-the-individual-based-simulation-model}{%
-\subsection{S1: Description of the individual-based simulation
-model}\label{s1-description-of-the-individual-based-simulation-model}}
-
-Here we describe the details of initialisation, time-in (mating),
-time-out (reproduction and nuptial gift search), and mortality. We then
-summarise the simulations run and data collected.
-
-\emph{Initialisation}
-
-Before the first time step, a population of \(N = 1000\) individuals is
-initialised. Individuals are assigned unique IDs, and each is assigned
-to be female with a probability of \(0.5\), else male. Each individual
-\(i\) is initialised with a starting value of female offspring
-processing time (\(T^{i}_{\mathrm{f}}\)), rejection probability of
-gift-less males (\(\rho^{i}\)), and male search time
-(\(T^{i}_{\mathrm{m}}\)). For all simulations, initialised values are
-set to \(T^{i}_{\mathrm{f}} = 2\), \(\rho^{i} = 0\), and
-\(T^{i}_{\mathrm{m}} = 0\). All individuals are initalised outside of
-the mating pool in the first time step \(t = 1\). The first time step
-then proceeds with females immediately entering the mating pool and
-males either entering the mating pool or searching for nuptial gifts.
-
-\emph{Time-in}
-
-At the start of each time step, females and males in the mating pool
-remain in it. Females will enter the mating pool after processing
-offspring, and males will enter it after searching for nuptial gifts
-(see `Time-out' below). Up to \(\Psi = N\psi\) interactions between
-individuals can occur in a single time step, where \(N\) is population
-size and \(\psi\) is a scaling parameter. In each time step, \(\Psi\)
-pairs of individuals are selected at random to interact. For each
-interaction, two different individuals are randomly selected from the
-population with equal probability. If the selected individuals are of
-different sexes, and both are in the mating pool, then a mating
-encounter occurs. If the male does not have a nuptial gift, then the
-female will reject him with a probability of \(\rho^{i}\); if rejection
-occurs, then both individuals stay in the mating pool. If rejection does
-not occur, or the male has a nuptial gift in the mating encounter, then
-the individuals mate. Females leave the mating pool and enter time-out
-to process offspring, and males leave and enter time-out to potentially
-search for new nuptial gifts (note that females and males might re-enter
-the mating pool immediately within the same time step given sufficiently
-low search time; see Time-out below).
-
-\emph{Time-out}
-
-During time-out, offspring production and time outside of the mating
-pool are realised for each female by sampling from a Poisson
-distribution. A focal female \(i\) will produce \(Poisson(\lambda)\)
-offspring if no nuptial gift was provided or
-\(Poisson(\lambda + \gamma)\) if a gift was provided. Females remain
-outside of the mating pool to process offspring for
-\(Poisson(T^{i}_{\mathrm{f}})\) time steps. Offspring are added to the
-population immediately, with \(\rho^{i}\) and \(T^{i}_{\mathrm{m}}\)
-values that are the average of each parent plus some normally
-distributed error \(\epsilon_{R}\) and \(\epsilon_{T_{\mathrm{m}}}\).
-For example,
-
-\[T^{\mathrm{offspring}}_{\mathrm{m}} \sim \frac{T^{\mathrm{mother}}_{\mathrm{m}}  + T^{\mathrm{father}}_{\mathrm{m}}}{2} + N\left(0, \epsilon_{T_{\mathrm{m}}} \right).\]
-
-The variation generated by \(\epsilon\) values simulates mutation upon
-which selection for traits can act. In all simulations, \(\epsilon = 0\)
-if a trait is fixed and \(\epsilon = 0.01\) if the trait evolves.
-Offspring sex is randomly assigned with equal probability as female or
-male. Female offspring are immediately placed in the mating pool, and
-male offspring are out of the mating pool to potentially search for
-nuptial gifts. After a female has spent \(T^{i}_{\mathrm{f}}\) time
-steps outside the mating pool, she will re-enter it.
-
-A focal male \(i\) outside the mating pool will enter it if he has
-searched for a fixed number of \(T^{i}_{\mathrm{m}}\) time steps, which
-is also sampled randomly from a Poisson distribution,
-\(Poisson(T^{i}_{\mathrm{m}})\). If \(T^{i}_{\mathrm{m}} = 0\), then the
-male immediately returns to the mating pool (in the same time step). If
-\(T^{i}_{\mathrm{m}} > 0\), then the male must wait outside the mating
-pool for \(Poisson(T^{i}_{\mathrm{m}})\) time steps, but will enter the
-mating pool with a nuptial gift with a probability,
-
-\[P(G^{i}) = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.\]
-
-Males must always spend \(T^{i}_{\mathrm{m}}\) time steps outside of the
-mating pool regardless of whether or not they are successful in
-obtaining a nuptial gift.
-
-\emph{Mortality}
-
-At the end of each time step, mortality occurs first with a fixed
-probability for all adults in the population, then with a probability
-caused by carrying capacity \(K\) applied to all individuals (adults and
-offspring). Mortality occurs in each time step with a fixed probability
-of \(\mu\) regardless of the sex of the individual or its position in or
-out of the mating pool. If after this fixed mortality is applied, the
-total population size \(N > K\), then individuals are removed at random
-with equal probability until \(N = K\). Following adult mortality, a new
-time step begins with newly added offspring becoming adults.
-
-\emph{Simulations}
-
-We ran simulations in which male search time and female choosiness
-evolved from an ancestral state of no searching and no choosiness. In
-all simulations, \(N\) was initialised at 1000 and \(K = 1000\).
-Simulations ran for \(t_{max} = 40000\) time steps. We set
-\(T_{\mathrm{f}} = 2\), \(\psi = 3\), and \(\lambda = 1\) for all
-simulations, and we simulated across a range of
-\(\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}\) and
-\(\gamma = \{0, 0.1, ..., 1.9, 2.0\}\) parameter values for 3200
-replicates. Summary statistics for mean trait values, population size,
-sex ratios, proportion of females and males in and out of the mating
-pool, and mean number of encounters per female and male within the
-mating pool were all calculated in the last time step. The C code used
-for simulating these IBMs also allows for the reporting of statistics in
-each time step. Additionally, it can simulate explicit space and
-individual movement through the landscape. A neutral evolving trait was
-also modelled to ensure that the code functioned as intended, and
-processes were compartmentalised into individual functions to facilitate
-code testing. All code is publicly available on GitHub
-(\url{https://github.com/bradduthie/nuptial_gift_evolution}).
-
-A set of simulations with a value of \(\gamma\) calculated from
-empirical data was also conducted (100 replicates). Here, \(\gamma\) was
-parameterised using data on egg production as a function of eating
-nuptial gifts (see below). Additional simulation sets with lower and
-upper bounds of the estimated \(\gamma\) were subsequently run. In the
-simulation sets with experimentally derived parameter values, all other
-parameters were identical to previous simulation batches.
-
-We can produce an estimate of the fitness increment obtained by females
-when receiving a gift (\(\hat{\gamma}\)) by using data on female
-\emph{P. mirabilis} egg production and hatching success under different
-feeding regimes from (\protect\hyperlink{ref-Tuni2013a}{Tuni \emph{et
-al.}, 2013}). Tuni \emph{et al.}
-(\protect\hyperlink{ref-Tuni2013a}{2013}) found differences in egg
-production and hatching success in female \emph{P. mirabilis} under
-different feeding regimes. Assuming these differences in feeding regimes
-correspond to eating versus not eating nuptial gifts, the mean number of
-offspring produced by a female who eats nuptial gifts can be calculated
-(Table 1).
-
-\hypertarget{s2-sensitivity-analysis-of-parameters-in-ibm}{%
-\subsection{S2: Sensitivity analysis of parameters in
-IBM}\label{s2-sensitivity-analysis-of-parameters-in-ibm}}
-
-We investigated the sensitivity of our results to individual mortality
-during time-in (\(\mu_{\mathrm{in}}\)) and time-out
-(\(\mu_{\mathrm{out}}\)), female processing time (\(T_{\mathrm{f}}\)),
-potential for interactions between conspecifics (\(\psi\)), and
-initialised male search time (\(T_{\mathrm{m}}\)). Across all of these
-simulations, there were challenges with statistical power. Evidence for
-the evolution of male search (blue points in figures) and female
-choosiness (red points in figures) was determined by the lower 95\%
-bootstrapped confidence interval of \(T_{\mathrm{m}}\) and
-\(T_{\mathrm{f}}\) values being greater than zero, respectively. This
-required a lot of replicate simulations in the main text (Figure 3),
-especially for values just above predicted thresholds and for female
-choosiness. Computation time was a limiting factor, even using a
-compiled language (C) and with access to a computing cluster. Absence of
-points above threshold values are not necessarily evidence that
-evolution of male search or female choosiness is not predicted to evolve
-in these regions of parameter space, but it does indicate that evolution
-of these traits is not necessarily assured given the stochasticity
-inherent to the IBM. Additional simulations can be conducted using the C
-code in the `src' folder of the GitHub repository
-(\url{https://github.com/bradduthie/nuptial_gift_evolution}). Below, we
-explain the parameter values used in the sensitivity analysis in more
-detail.
-
-\emph{Mortality}
-
-We conducted a sensitivity analysis of the effect of the mortality
-parameters \(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\) (the
-probability of mortality in time-in and time-out, respectively, which we
-assumed to be equal for all individuals) on the evolution of male search
-and female choice using the IBM (See S1). The results revealed no
-correlation between the value of the mortality parameters and the
-evolution of male search or female choice (Fig. S2.1).
-
-\emph{Female processing time}
-
-We also conducted a sensitivity analysis of female processing time
-\(T_{\mathrm{f}}\). To do this, we ran simulations at default values,
-but with \(T_{\mathrm{f}} = 0.4\) (Figure S4.2) and
-\(T_{\mathrm{f}} = 10.0\) (Figures S4.3).
-
-\emph{Interactions between conspecifics}
-
-We conducted a sensitivity analysis on the encounter rate between
-conspecifics (\(R\)) by varying the value of \(\psi\) (see S1). Under
-default simulations, \(\psi = 3\). We also ran simulations in which
-\(\psi = 1\) (Figure S4.4), \(\psi = 2\) (Figure S4.5), \(\psi = 4\)
-(Figure S4.6), and \(\psi = 6\) (Figure S4.7), with all other parameters
-being set to default values.
-
-\emph{Initialised male search time}
-
-Lastly, we conducted a sensitivity analysis on initialised male search
-time (\(T_{\mathrm{m}}\)). To do this, we ran simulations at default
-values, but initialised all males at \(T_{\mathrm{m}} = 0.5\) (Figure
-S4.8) or \(T_{\mathrm{m}} = 2.5\) (S4.9). Note that under these
-initialisation conditions, it no longer makes sense to test whether or
-not \(T_{\mathrm{m}}\) evolves to positive values, so we do not show
-predicted male search thresholds and focus only on female choosiness.
-Interestingly, while predictions given initialised
-\(T_{\mathrm{m}} = 0.5\) are quite close for female choosiness
-thresholds, female choosiness does not appear to evolve given
-\(T_{\mathrm{m}} = 2.5\). This might be due to low selection pressure to
-reject males without gifts due to their low frequency. In other words,
-while females would benefit from a strategy of rejecting gift-less
-males, a lack of realised encounters with gift-less males preclude the
-evolution of sustained selection for choosiness.
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-6-1.pdf}
-\caption{Figure S4.1: Evolution of both male search (blue) and female
-choice (red) under different combinations of the mortality rates
-\(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\) (mortality in time-in
-and out, respectively). The y-axis is the threshold fitness that leads
-to evolution of male search (blue) or female choice (red). The results
-show noise, but no correlation between the value of the mortality
-parameters and the propensity for male search and/or female choice to
-evolve. For each of the \(25 \times 20\) combinations of
-\(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\), 1600 replicate
-simulations were run.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-7-1.pdf}
-\caption{Figure S4.2 (\(T_{\mathrm{f}} = 0.4\)): The coevolution of male
-search and female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-female choosiness (red) and male search (blue) exceeds zero, indicating
-evolution of choosiness or nuptial gift search. Each point includes data
-from 720 replicate simulations with identical starting conditions. Red
-and blue lines show thresholds above which the mathematical model
-predicts that females should be choosy and males should search,
-respectively. Up to 3000 interactions occur between individuals in each
-time step (\(\psi = 3\)), potentially resulting in a mating interaction.
-The number of individuals in the population remained at or near carrying
-capacity of \(K = 1000\). Expected female processing time was set to
-\(T_{\mathrm{f}}=0.4\) time steps, and \(\gamma\) and \(\alpha\) values
-in the range {[}0.5, 1.5{]} and {[}0.1, 2.1{]}, respectively, were
-used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-8-1.pdf}
-\caption{Figure S4.3 (\(T_{\mathrm{f}} = 10.0\)): The coevolution of
-male search and female choosiness as a function of nuptial gift search
-time (\(\alpha\)). Points show where the lower 95\% confidence interval
-of female choosiness (red) and male search (blue) exceeds zero,
-indicating evolution of choosiness or nuptial gift search. Each point
-includes data from 720 replicate simulations with identical starting
-conditions. Red and blue lines show thresholds above which the
-mathematical model predicts that females should be choosy and males
-should search, respectively. Up to 3000 interactions occur between
-individuals in each time step (\(\psi = 3\)), potentially resulting in a
-mating interaction. The number of individuals in the population remained
-at or near carrying capacity of \(K = 1000\). Expected female processing
-time was set to \(T_{\mathrm{f}}=10.0\) time steps, and \(\gamma\) and
-\(\alpha\) values in the range {[}0.5, 1.5{]} and {[}0.1, 2.1{]},
-respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-9-1.pdf}
-\caption{Figure S4.4 (\(\psi = 1\)): The coevolution of male search and
-female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 720
-replicate simulations with identical starting conditions. Red and blue
-lines show thresholds above which the mathematical model predicts that
-females should be choosy and males should search, respectively. Up to
-1000 interactions occur between individuals in each time step
-(\(\psi = 1\)), potentially resulting in a mating interaction. The
-number of individuals in the population remained at or near carrying
-capacity of \(K = 1000\). Expected female processing time was set to
-\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
-the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]}, respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-10-1.pdf}
-\caption{Figure S4.5 (\(\psi = 2\)): The coevolution of male search and
-female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 720
-replicate simulations with identical starting conditions. Red and blue
-lines show thresholds above which the mathematical model predicts that
-females should be choosy and males should search, respectively. Up to
-2000 interactions occur between individuals in each time step
-(\(\psi = 2\)), potentially resulting in a mating interaction. The
-number of individuals in the population remained at or near carrying
-capacity of \(K = 1000\). Expected female processing time was set to
-\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
-the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]}, respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-11-1.pdf}
-\caption{Figure S4.6 (\(\psi = 4\)): The coevolution of male search and
-female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 720
-replicate simulations with identical starting conditions. Red and blue
-lines show thresholds above which the mathematical model predicts that
-females should be choosy and males should search, respectively. Up to
-4000 interactions occur between individuals in each time step,
-potentially resulting in a mating interaction (\(\psi = 4\)). The number
-of individuals in the population remained at or near carrying capacity
-of \(K = 1000\). Expected female processing time was set to
-\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
-the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]}, respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-12-1.pdf}
-\caption{Figure S4.7 (\(\psi = 6\)): The coevolution of male search and
-female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 720
-replicate simulations with identical starting conditions. Red and blue
-lines show thresholds above which the mathematical model predicts that
-females should be choosy and males should search, respectively. Up to
-6000 interactions occur between individuals in each time step,
-potentially resulting in a mating interaction (\(\psi = 6\)). The number
-of individuals in the population remained at or near carrying capacity
-of \(K = 1000\). Expected female processing time was set to
-\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
-the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]}, respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-13-1.pdf}
-\caption{Figure S4.8 (\(T_{\mathrm{m}} = 0.5\)): The coevolution of male
-search and female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 1600
-replicate simulations with identical starting conditions. The red line
-shows the threshold above which the mathematical model predicts that
-females should be choosy (male thresholds for search are not shown
-because simulations were initialised with males already searching for
-nuptial gifts). Up to 3000 interactions occur between individuals in
-each time step, potentially resulting in a mating interaction
-(\(\psi = 3\)). The number of individuals in the population remained at
-or near carrying capacity of \(K = 1000\). Expected female processing
-time was set to \(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and
-\(\alpha\) values in the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]},
-respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-14-1.pdf}
-\caption{Figure S4.9 (\(T_{\mathrm{m}} = 2.5\)): The coevolution of male
-search and female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 1600
-replicate simulations with identical starting conditions. The red line
-shows the threshold above which the mathematical model predicts that
-females should be choosy (male thresholds for search are not shown
-because simulations were initialised with males already searching for
-nuptial gifts). Up to 3000 interactions occur between individuals in
-each time step, potentially resulting in a mating interaction
-(\(\psi = 3\)). The number of individuals in the population remained at
-or near carrying capacity of \(K = 1000\). Expected female processing
-time was set to \(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and
-\(\alpha\) values in the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]},
-respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\hypertarget{s3-alternative-derivation-of-male-fitness-threshold}{%
-\subsection{S3: Alternative derivation of male fitness
-threshold}\label{s3-alternative-derivation-of-male-fitness-threshold}}
-
-In the main text, we assumed that males made the decision to search or
-not search for a nuptial gift. The expected length of time for which
-searching males are expected to remain outside of the mating pool is
-\(E[T_{\mathrm{m}}] = \alpha\) (see Methods). Alternatively, we can
-assume that males search for a period of \(T_{\mathrm{m}}\) and spend
-this full duration of \(T_{\mathrm{m}}\) in the time-out phase, even if
-they succeed in finding a nuptial gift. The probability that a male
-obtains a nuptial gift during this time is modelled in Eq. 1,
-
-\[P(G) = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
-
-In Eq. 1, \(\alpha\) is the amount of time expected to pass before a
-male encounters a nuptial gift. We assume that a male will only enter
-the mating pool with no gift if they are unsuccessful in obtaining a
-gift, so the probability that a male obtains no gift after
-\(T_{\mathrm{m}}\) is,
-
-\[P(L) = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
-
-We assume that the fitness increments to offspring associated with
-receiving a nuptial gift versus no nuptial gift are \(1 + \gamma\) and
-1, respectively. The rate at which males increase their fitness can then
-be defined as the expected fitness increment from their nuptial gift
-search divided by \(T_{\mathrm{m}}\) plus the time spent in the mating
-pool waiting to encounter a mate,
-
-\[W_{\mathrm{m}} = \lambda \frac{P(G)\left(1 + \gamma\right) + P(L)}{T_{\mathrm{m}} + \left( \frac{\beta + 1}{R} \right)}.\]
-
-Our objective now is to determine the conditions under which a focal
-male increases its fitness by searching for a nuptial gift
-(\(T_{\mathrm{m}}>0\)) in a population of resident males that do not
-search (\(T_{\mathrm{m}}=0\)). Females are assumed to exhibit no choice
-in males with versus without nuptial gifts. Under such conditions, male
-fitness cannot be affected by female choice, so selection to increase
-\(T_{\mathrm{m}}>0\) must be based solely on \(\alpha\), \(\beta\),
-\(R\), and \(\gamma\).
-
-To determine under what conditions male inclusive fitness increases with
-nuptial gift search time, we can differentiate \(W_{\mathrm{m}}\) with
-respect to \(T_{\mathrm{m}}\),
-
-\[\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda\frac{\gamma\left(\frac{\frac{T_{\mathrm{m}} + \frac{\beta + 1}{R}}{\alpha} + 1}{e^{\frac{1}{\alpha}T_{\mathrm{m}}}} - 1\right) - 1}{\left(T_{\mathrm{m}} + \frac{\beta + 1}{R} \right)^{2}}.\]
-
-Because \(T_{\mathrm{m}} = 0\), the above simplifies,
-
-\[\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda \frac{\frac{R\gamma\left(\beta + 1\right)}{\alpha} - R^{2}}{\left(1 + \beta \right)^{2}}.\]
-
-We can re-arrange the above,
-
-\[\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)} - \lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}}.\]
-
-Note that if \(R = 0\) or \(\lambda = 0\), then, trivially, no change in
-fitness occurs (since females and males cannot mate or do not produce
-offspring). Fitness is increased by searching for nuptial gifts when
-\(\gamma\) is high, scaled by the expect search time needed to find a
-nuptial gift. A second term on the right-hand side is subtracted, which
-reflects a loss in fitness proportional to the encounter rate of
-potential mates in the mating pool. The conditions under which male
-inclusive fitness increases by searching for a nuptial gift are found by
-setting \(\partial W_{\mathrm{m}}/\partial T_{\mathrm{m}} = 0\) and
-solving for \(\gamma\) to get Eq. 2 in the main text.
-
-\clearpage
-
-\hypertarget{s4-operational-sex-ratio}{%
-\subsection{S4: Operational sex ratio}\label{s4-operational-sex-ratio}}
-
-We assume that the ratio of males to females is the same upon individual
-maturation. Consequently, the operational sex ratio \(\beta\) will be a
-function of \(R\), \(T_{\mathrm{f}}\), and \(T_{\mathrm{m}}\) because
-these parameters determine the density of females and males in the
-mating pool versus outside of the mating pool. We start with the
-definition of \(\beta\) as being the probability of finding an
-individual in time-in (\protect\hyperlink{ref-Kokko2001}{Kokko \&
-Monaghan, 2001}),
-
-\[\beta = \frac{\int_{t=0}^{\infty}P_{IM}(t)dt}{\int_{t=0}^{\infty}P_{IF}(t)dt}\]
-
-We can substitute the equations for \(P_{IM}(t)\) and \(P_{IF}(t)\),
-which define the probabilities of males and females being within the
-mating pool at time \(t\), respectively.
-
-We can therefore calculate \(\beta\) as below,
-
-\[\beta = \frac{\left( \frac{\left(\frac{\beta + 1}{R}\right)}{T_{\mathrm{m}} + \left(\frac{\beta + 1}{R}\right)} \right)}{\left( \frac{\left(R \frac{\beta}{\beta + 1}\right)}{T_{\mathrm{f}} + \left(R \frac{\beta}{\beta + 1}\right)} \right)}.\]
-
-This can be simplified,
-
-\[\beta = \frac{\left(\beta\left(R + T_{f}\right) + T_{f}\right)\left(\beta + 1\right)}{\beta \left(R^{2}T_{m} + R\right) + \beta^{2}R}.\]
-
-There is no closed form solution for \(\beta\), but a recursive
-algorithm can be used to calculate \(\beta\) to an arbitrary degree of
-precision.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{recursive\_b }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(B, D, Tf, Tm, }\AttributeTok{crit =} \FloatTok{0.0001}\NormalTok{, }\AttributeTok{maxit =} \DecValTok{9999}\NormalTok{)\{}
-\NormalTok{  conv }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{;}
-\NormalTok{  iter }\OtherTok{\textless{}{-}} \DecValTok{0}\NormalTok{;}
-  \ControlFlowTok{while}\NormalTok{(conv }\SpecialCharTok{\textgreater{}}\NormalTok{ crit }\SpecialCharTok{\&}\NormalTok{ iter }\SpecialCharTok{\textless{}}\NormalTok{ maxit)\{}
-\NormalTok{    Fe   }\OtherTok{\textless{}{-}}\NormalTok{ D }\SpecialCharTok{*}\NormalTok{ (B }\SpecialCharTok{/}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+}\NormalTok{ B));}
-\NormalTok{    Me   }\OtherTok{\textless{}{-}}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+}\NormalTok{ B) }\SpecialCharTok{/}\NormalTok{ D;}
-\NormalTok{    Bn   }\OtherTok{\textless{}{-}}\NormalTok{ (Me }\SpecialCharTok{/}\NormalTok{ (Tm }\SpecialCharTok{+}\NormalTok{ Me)) }\SpecialCharTok{/}\NormalTok{ (Fe }\SpecialCharTok{/}\NormalTok{ (Tf }\SpecialCharTok{+}\NormalTok{ Fe));}
-\NormalTok{    iter }\OtherTok{\textless{}{-}}\NormalTok{ iter }\SpecialCharTok{+} \DecValTok{1}\NormalTok{;}
-\NormalTok{    conv }\OtherTok{\textless{}{-}} \FunctionTok{abs}\NormalTok{(Bn }\SpecialCharTok{{-}}\NormalTok{ B);}
-\NormalTok{    B    }\OtherTok{\textless{}{-}}\NormalTok{ Bn;}
-\NormalTok{  \}}
-  \FunctionTok{return}\NormalTok{(}\FunctionTok{list}\NormalTok{(}\AttributeTok{B =}\NormalTok{ B, }\AttributeTok{conv =}\NormalTok{ conv, }\AttributeTok{iter =}\NormalTok{ iter));}
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
-We used the above function to calculate values of \(\beta\) for the
-analytical model.
-
-\clearpage
-
-\hypertarget{s5-estimation-of-key-model-parameters-using-experimental-data}{%
-\subsection{S5: Estimation of key model parameters using experimental
-data}\label{s5-estimation-of-key-model-parameters-using-experimental-data}}
-
-Estimates showing the mean number of offspring produced by female
-\emph{Pisaura mirabilis} that ate nuptial gifts and females who did not.
-Means were calculated with raw data from Tuni \emph{et al.}
-(\protect\hyperlink{ref-Tuni2013a}{2013}) and results are shown \(\pm\)
-SE (Table 1). Under these assumptions, the relative gain in fitness from
-receiving nuptial gifts for a female is,
-
-\[\hat{\delta_\mathrm{f}} = \frac{25.74}{6.00} = 4.29\]
-
-Since the baseline fitness is 1, the increase in fitness resulting from
-a nuptial gift then becomes,
-
-\[\hat{\gamma} = \hat{\delta_{\mathrm{f}}} - 1 = 3.29.\]
-
-The value 3.29 was used to parameterise \(\gamma\) for a set of
-simulations (Figure 4 in the main text).
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4024}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2805}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3171}}@{}}
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Received nuptial gift
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Received no nuptial gift
-\end{minipage} \\
-\midrule
-\endhead
-Expected number of hatched eggs & \(25.74 \pm 0.96\) &
-\(6.00 \pm 2.1\) \\
-\bottomrule
-\end{longtable}
-
-Table 1: Estimates showing mean number of offspring produced by female
-\emph{P. mirabilis} that ate nuptial gifts and females who did not.
-Means were calculated with raw data from Tuni \emph{et al.}
-(\protect\hyperlink{ref-Tuni2013a}{2013}) and results are shown \(\pm\)
-SE.
-
-\clearpage
-
-\hypertarget{s6-separate-evolution-of-male-search-and-female-choice}{%
-\subsection{S6: Separate evolution of male search and female
-choice}\label{s6-separate-evolution-of-male-search-and-female-choice}}
-
-We used the individual-based simulation model (see Supporting
-Information S1) to unpack the effect of coevolution on the evolution of
-male search and female choice. Here we replicated the simulations shown
-in the main text under the condition where only one trait at a time was
-allowed to evolve and studied how this affected the trait evolution.
-
-First, we submitted a set of simulations wherein male search did not
-evolve, but was fixed at different values (see Fig. S6.1). Next, we ran
-the same set of simulations wherein male search evolved, but female
-choice was not possible. The results thus show how each trait evolves in
-the absence of any coevolution (Fig. S6.1).
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_refs_fixed_files/figure-latex/unnamed-chunk-16-1.pdf}
-\caption{Figure S6.1: The separate evolution of male search and female
-choosiness as a function of nuptial gift search time. Points show where
-the lower 95\% confidence interval of male search (blue) and female
-choosiness (red) exceeds zero, indicating evolution of nuptial gift
-search or choosiness. Each point includes data from \(2 \times 1600\)
-replicate simulations with identical starting conditions. In the first
-batch, male search was constant and initialized at
-\(T_{\mathrm{m}} = \alpha\), and female choice was evolving. In the
-second batch, male search was evolving, and there was no option for
-female choice. The parameters \(T_{\mathrm{f}}=2\), and \(\gamma\) and
-\(\alpha\) values were set within the range {[}0.1, 2.0{]} and {[}0.3,
-1.7{]}, respectively.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
 \end{document}

### 2024-06-15 ms_biorxiv.Rmd
Make the HTML in line with the biorxiv version

@@
     keep_tex: yes
-  html_document: default
   word_document:

### 2024-06-15 index.Rmd
Remove the table of contents

--- 2024-06-15 ms_biorxiv.Rmd
@@
 
-| Information                                                   | Page |
-|---------------------------------------------------------------|------|
-| S1: Description of the individual-based simulation model      |  18  |
-| S2: Sensitivity analysis of mortality parameters in IBM       |  20  |
-| S3: Alternative derivation of male fitness threshold          |  29  |
-| S4: Operational sex ratio                                     |  32  |
-| S5: Estimation of key model parameter using experimental data |  33  |
-| S6: Separate evolution of male search and female choice       |  34  |
-
-\clearpage
-
 S1: Description of the individual-based simulation model

### 2024-11-29 SI.Rmd
Fixed up traits and manuscript. Traits are not binary anymore, but are diploid

--- 2024-06-15 SI.Rmd
@@
 gamma_f <- function(R = 1, beta = 1, alpha = 1/16, TF = 2){
-  topp <- exp(alpha / alpha);
-  bott <- TF * R * (beta / (beta + 1)) * (exp(alpha/alpha) - 1);
+  topp <- 1;
+  bott <- TF * R * (beta / (beta + 1)) * (1 - exp(-alpha/alpha));
   return(topp/bott);
@@
 |---------------------------------------------------------------|------|
-| S1: Description of the individual-based simulation model      |  2   |
-| S2: Sensitivity analysis of mortality parameters in IBM       |  4   |
-| S3: Alternative derivation of male fitness threshold          |  14  |
-| S4: Operational sex ratio                                     |  16  |
-| S5: Estimation of key model parameter using experimental data |  17  |
-| S6: Separate evolution of male search and female choice       |  18  |
-| References                                                    |  19  |
+| S1: Alternative derivation of male fitness threshold          |  2   |
+| S2: Operational sex ratio                                     |  4   |
+| S3: Sensitivity analysis of parameters in IBM                 |  5   |
+| S4: Separate evolution of male search and female choice       |  12  |
+| References                                                    |  13  |
 
@@
 
-S1: Description of the individual-based simulation model
-------------------------------------
-
-Here we describe the details of initialisation, time-in (mating), time-out (reproduction and nuptial gift search), and mortality. 
-We then summarise the simulations run and data collected.
-
-*Initialisation*
-
-Before the first time step, a population of $N = 1000$ individuals is initialised. 
-Individuals are assigned unique IDs, and each is assigned to be female with a probability of $0.5$, else male. 
-Each individual $i$ is initialised with a starting value of female offspring processing time ($T^{i}_{\mathrm{f}}$), rejection probability of gift-less males ($\rho^{i}$), and male search time ($T^{i}_{\mathrm{m}}$).
-For all simulations, initialised values are set to $T^{i}_{\mathrm{f}} = 2$, $\rho^{i} = 0$, and $T^{i}_{\mathrm{m}} = 0$. 
-All individuals are initalised outside of the mating pool in the first time step $t = 1$. 
-The first time step then proceeds with females immediately entering the mating pool and males either entering the mating pool or searching for nuptial gifts.
-
-*Time-in*
-
-At the start of each time step, females and males in the mating pool remain in it. 
-Females will enter the mating pool after processing offspring, and males will enter it after searching for nuptial gifts (see 'Time-out' below). 
-Up to $\Psi = N\psi$ interactions between individuals can occur in a single time step, where $N$ is population size and $\psi$ is a scaling parameter. 
-In each time step, $\Psi$ pairs of individuals are selected at random to interact.
-For each interaction, two different individuals are randomly selected from the population with equal probability.
-If the selected individuals are of different sexes, and both are in the mating pool, then a mating encounter occurs.
-If the male does not have a nuptial gift, then the female will reject him with a probability of $\rho^{i}$; if rejection occurs, then both individuals stay in the mating pool. 
-If rejection does not occur, or the male has a nuptial gift in the mating encounter, then the individuals mate. 
-Females leave the mating pool and enter time-out to process offspring, and males leave and enter time-out to potentially search for new nuptial gifts (note that females and males might re-enter the mating pool immediately within the same time step given sufficiently low search time; see Time-out below).
-
-*Time-out*
-
-During time-out, offspring production and time outside of the mating pool are realised for each female by sampling from a Poisson distribution.
-A focal female $i$ will produce $Poisson(\lambda)$ offspring if no nuptial gift was provided or $Poisson(\lambda + \gamma)$ if a gift was provided. 
-Females remain outside of the mating pool to process offspring for $Poisson(T^{i}_{\mathrm{f}})$ time steps. 
-Offspring are added to the population immediately, with $\rho^{i}$ and $T^{i}_{\mathrm{m}}$ values that are the average of each parent plus some normally distributed error $\epsilon_{R}$ and $\epsilon_{T_{\mathrm{m}}}$.
-For example,
-
-$$T^{\mathrm{offspring}}_{\mathrm{m}} \sim \frac{T^{\mathrm{mother}}_{\mathrm{m}}  + T^{\mathrm{father}}_{\mathrm{m}}}{2} + N\left(0, \epsilon_{T_{\mathrm{m}}} \right).$$
-
-The variation generated by $\epsilon$ values simulates mutation upon which selection for traits can act. 
-In all simulations, $\epsilon = 0$ if a trait is fixed and $\epsilon = 0.01$ if the trait evolves. 
-Offspring sex is randomly assigned with equal probability as female or male. 
-Female offspring are immediately placed in the mating pool, and male offspring are out of the mating pool to potentially search for nuptial gifts. 
-After a female has spent $T^{i}_{\mathrm{f}}$ time steps outside the mating pool, she will re-enter it.
-
-A focal male $i$ outside the mating pool will enter it if he has searched for a fixed number of $T^{i}_{\mathrm{m}}$ time steps, which is also sampled randomly from a Poisson distribution, $Poisson(T^{i}_{\mathrm{m}})$.
-If $T^{i}_{\mathrm{m}} = 0$, then the male immediately returns to the mating pool (in the same time step). 
-If $T^{i}_{\mathrm{m}} > 0$, then the male must wait outside the mating pool for $Poisson(T^{i}_{\mathrm{m}})$ time steps, but will enter the mating pool with a nuptial gift with a probability,
-
-$$P(G^{i}) = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.$$
-
-Males must always spend $T^{i}_{\mathrm{m}}$ time steps outside of the mating pool regardless of whether or not they are successful in obtaining a nuptial gift.
-
-*Mortality*
-
-At the end of each time step, mortality occurs first with a fixed probability for all adults in the population, then with a probability caused by carrying capacity $K$ applied to all individuals (adults and offspring).
-Mortality occurs in each time step with a fixed probability of $\mu$ regardless of the sex of the individual or its position in or out of the mating pool. 
-If after this fixed mortality is applied, the total population size $N > K$, then individuals are removed at random with equal probability until $N = K$. 
-Following adult mortality, a new time step begins with newly added offspring becoming adults.
-
-*Simulations*
-
-We ran simulations in which male search time and female choosiness evolved from an ancestral state of no searching and no choosiness. 
-In all simulations, $N$ was initialised at 1000 and $K = 1000$. 
-Simulations ran for $t_{max} = 40000$ time steps. 
-We set $T_{\mathrm{f}} = 2$, $\psi = 3$, and $\lambda = 1$ for all simulations, and we simulated across a range of $\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}$ and $\gamma = \{0, 0.1, ..., 1.9, 2.0\}$ parameter values for 3200 replicates.
-Summary statistics for mean trait values, population size, sex ratios, proportion of females and males in and out of the mating pool, and mean number of encounters per female and male within the mating pool were all calculated in the last time step.
-The C code used for simulating these IBMs also allows for the reporting of statistics in each time step. 
-Additionally, it can simulate explicit space and individual movement through the landscape. 
-A neutral evolving trait was also modelled to ensure that the code functioned as intended, and processes were compartmentalised into individual functions to facilitate code testing. 
-All code is publicly available on GitHub (https://github.com/bradduthie/nuptial_gift_evolution).
-
-A set of simulations with a value of $\gamma$ calculated from empirical data was also conducted (100 replicates). 
-Here, $\gamma$ was parameterised using data on egg production as a function of eating nuptial gifts (see below). 
-Additional simulation sets with lower and upper bounds of the estimated $\gamma$ were subsequently run. 
-In the simulation sets with experimentally derived parameter values, all other parameters were identical to previous simulation batches.
-
-We can produce an estimate of the fitness increment obtained by females when receiving a gift ($\hat{\gamma}$) by using data on female *P.
-mirabilis* egg production and hatching success under different feeding regimes from [@Tuni2013a].
-@Tuni2013a found differences in egg production and hatching success in female *P. mirabilis* under different feeding regimes. 
-Assuming these differences in feeding regimes correspond to eating versus not eating nuptial gifts, the mean number of offspring produced by a female who eats nuptial gifts can be calculated (Table 1).
-
-\clearpage
-
-S2: Sensitivity analysis of parameters in IBM
-------------------------------------
-
-We investigated the sensitivity of our results to individual mortality during time-in ($\mu_{\mathrm{in}}$) and time-out ($\mu_{\mathrm{out}}$), female processing time ($T_{\mathrm{f}}$), potential for interactions between conspecifics ($\psi$), and initialised male search time ($T_{\mathrm{m}}$).
-Across all of these simulations, there were challenges with statistical power.
-Evidence for the evolution of male search (blue points in figures) and female choosiness (red points in figures) was determined by the lower 95\% bootstrapped confidence interval of $T_{\mathrm{m}}$ and $T_{\mathrm{f}}$ values being greater than zero, respectively.
-This required a lot of replicate simulations in the main text (Figure 3), especially for values just above predicted thresholds and for female choosiness.
-Computation time was a limiting factor, even using a compiled language (C) and with access to a computing cluster.
-Absence of points above threshold values are not necessarily evidence that evolution of male search or female choosiness is not predicted to evolve in these regions of parameter space, but it does indicate that evolution of these traits is not necessarily assured given the stochasticity inherent to the IBM.
-Additional simulations can be conducted using the C code in the 'src' folder of the GitHub repository (https://github.com/bradduthie/nuptial_gift_evolution).
-Below, we explain the parameter values used in the sensitivity analysis in more detail.
-
-*Mortality*
-
-We conducted a sensitivity analysis of the effect of the mortality parameters $\mu_{\mathrm{in}}$ and $\mu_{\mathrm{out}}$ (the probability of mortality in time-in and time-out, respectively, which we assumed to be equal for all individuals) on the evolution of male search and female choice using the IBM (See S1).
-The results revealed no correlation between the value of the mortality parameters and the evolution of male search or female choice (Fig. S2.1).
-
-*Female processing time*
-
-We also conducted a sensitivity analysis of female processing time $T_{\mathrm{f}}$. 
-To do this, we ran simulations at default values, but with $T_{\mathrm{f}} = 0.4$ (Figure S4.2) and $T_{\mathrm{f}} = 10.0$ (Figures S4.3).
-
-*Interactions between conspecifics*
-
-We conducted a sensitivity analysis on the encounter rate between conspecifics ($R$) by varying the value of $\psi$ (see S1).
-Under default simulations, $\psi = 3$.
-We also ran simulations in which $\psi = 1$ (Figure S4.4), $\psi = 2$ (Figure S4.5), $\psi = 4$ (Figure S4.6), and $\psi = 6$ (Figure S4.7), with all other parameters being set to default values.
-
-*Initialised male search time*
-
-Lastly, we conducted a sensitivity analysis on initialised male search time ($T_{\mathrm{m}}$).
-To do this, we ran simulations at default values, but initialised all males at $T_{\mathrm{m}} = 0.5$ (Figure S4.8) or $T_{\mathrm{m}} = 2.5$ (S4.9). 
-Note that under these initialisation conditions, it no longer makes sense to test whether or not $T_{\mathrm{m}}$ evolves to positive values, so we do not show predicted male search thresholds and focus only on female choosiness.
-Interestingly, while predictions given initialised $T_{\mathrm{m}} = 0.5$ are quite close for female choosiness thresholds, female choosiness does not appear to evolve given $T_{\mathrm{m}} = 2.5$.
-This might be due to low selection pressure to reject males without gifts due to their low frequency.
-In other words, while females would benefit from a strategy of rejecting gift-less males, a lack of realised encounters with gift-less males preclude the evolution of sustained selection for choosiness.
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.1: Evolution of both male search (blue) and female choice (red) under different combinations of the mortality rates $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$ (mortality in time-in and out, respectively).
-The y-axis is the threshold fitness that leads to evolution of male search (blue) or female choice (red).
-The results show noise, but no correlation between the value of the mortality parameters and the propensity for male search and/or female choice to evolve.
-For each of the $25 \\times 20$ combinations of $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$, 1600 replicate simulations were run."}
-SUMO <- read.csv("inst/SI_mortality.csv");
-mort_combn   <- paste(SUMO[,1], SUMO[,2]);
-mort_label   <- unique(paste(SUMO[,1], ", ", SUMO[,2], sep = ""));
-TM_vals      <- tapply(X = SUMO[,4],  INDEX = mort_combn, FUN = mean);
-m_vals       <- tapply(X = SUMO[,14], INDEX = mort_combn, FUN = mean);
-beta_vals    <- tapply(X = SUMO[,15], INDEX = mort_combn, FUN = mean);
-Male_M       <- tapply(X = SUMO[,16], INDEX = mort_combn, FUN = mean);
-Female_M     <- tapply(X = SUMO[,17], INDEX = mort_combn, FUN = mean);
-Mf_nupt      <- tapply(X = SUMO[,18], INDEX = mort_combn, FUN = mean);
-Mf_nonupt    <- tapply(X = SUMO[,19], INDEX = mort_combn, FUN = mean);
-male_search  <- as.numeric(which(SUMO[,5] > 0 & SUMO[,6] > 0));
-fem_choose   <- as.numeric(which(SUMO[,8] > 0 & SUMO[,9] > 0));
-mimmom       <- unique(cbind(SUMO[,1], SUMO[,2]));
-
-mm <- SUMO[male_search,];
-mp <- NULL;
-for(i in 1:dim(mm)[1]){
-  rval <- which(mm[i, 1] == mimmom[,1] & mm[i, 2] == mimmom[,2]);
-  mp   <- rbind(mp, c(rval, mm[i, 3]));
-}
-
-ff <- SUMO[fem_choose,];
-fp <- NULL;
-for(i in 1:dim(ff)[1]){
-    rval <- which(ff[i, 1] == mimmom[,1] & ff[i, 2] == mimmom[,2]);
-    fp   <- rbind(fp, c(rval, ff[i, 3]));
-}
-
-par(mar = c(8, 5, 1, 1));
-plot(x = mp[,1], y = mp[,2], pch = 20, ylim = c(0, 2), col = "blue",
-     xlab = "", ylab = "", xaxt = "n", cex.lab = 1.25);
-points(x = fp[,1], y = fp[,2], cex = 2.5, col = "red", pch = 20);
-points(x = mp[,1], y = mp[,2], cex = 1.5, col = "blue", pch = 20);
-axis(side = 1, labels = mort_label, at = 1:25, las = 2);
-mtext(text = expression(paste("Mortality combination (",mu["in"],", ", 
-                              mu["out"],")")), side = 1, line = 6.5, 
-      cex = 1.25); 
-mtext(text = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                              ")")), side = 2, line = 2.5, cex = 1.25); 
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.2 ($T_{\\mathrm{f}} = 0.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from approximately 1600 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates).
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Up to 3000 interactions occur between individuals in each time step ($\\psi = 3$), potentially resulting in a mating interaction.
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=0.5$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.5, 1.5] and [0.1, 2.1], respectively, were used."}
-SUMM_Tf0pt4 <- read.csv("inst/SI_Tf_0pt5.csv");
-
-alpha_vals <- sort(unique(SUMM_Tf0pt4[,1]));
-TM_vals    <- tapply(X = SUMM_Tf0pt4[,3],  INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-m_vals     <- tapply(X = SUMM_Tf0pt4[,13], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-beta_vals  <- tapply(X = SUMM_Tf0pt4[,14], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-Male_M     <- tapply(X = SUMM_Tf0pt4[,15], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-Female_M   <- tapply(X = SUMM_Tf0pt4[,16], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-Mf_nupt    <- tapply(X = SUMM_Tf0pt4[,17], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-Mf_nonupt  <- tapply(X = SUMM_Tf0pt4[,18], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 0.5);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2.1));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Tf0pt4)[1]){
-  if(SUMM_Tf0pt4[i, 4] > 0 & SUMM_Tf0pt4[i, 5] > 0){
-    points(x = SUMM_Tf0pt4[i, 1], y = SUMM_Tf0pt4[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Tf0pt4)[1]){
-  if(SUMM_Tf0pt4[i, 7] > 0 & SUMM_Tf0pt4[i, 8] > 0){
-    points(x = SUMM_Tf0pt4[i, 1], y = SUMM_Tf0pt4[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.3 ($T_{\\mathrm{f}} = 10.0$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from approximately 1600 replicate simulations with identical starting conditions (some parameter combinations include fewer replicates).
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Up to 3000 interactions occur between individuals in each time step ($\\psi = 3$), potentially resulting in a mating interaction.
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=10.0$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.5, 1.5] and [0.1, 2.1], respectively, were used."}
-SUMM_Tf10 <- read.csv("inst/SI_Tf_10pt0.csv");
-
-alpha_vals <- sort(unique(SUMM_Tf10[,1]));
-TM_vals    <- tapply(X = SUMM_Tf10[,3],  INDEX = SUMM_Tf10[,1], FUN = mean);
-m_vals     <- tapply(X = SUMM_Tf10[,13], INDEX = SUMM_Tf10[,1], FUN = mean);
-beta_vals  <- tapply(X = SUMM_Tf10[,14], INDEX = SUMM_Tf10[,1], FUN = mean);
-Male_M     <- tapply(X = SUMM_Tf10[,15], INDEX = SUMM_Tf10[,1], FUN = mean);
-Female_M   <- tapply(X = SUMM_Tf10[,16], INDEX = SUMM_Tf10[,1], FUN = mean);
-Mf_nupt    <- tapply(X = SUMM_Tf10[,17], INDEX = SUMM_Tf10[,1], FUN = mean);
-Mf_nonupt  <- tapply(X = SUMM_Tf10[,18], INDEX = SUMM_Tf10[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 10);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2.1));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Tf10)[1]){
-  if(SUMM_Tf10[i, 4] > 0 & SUMM_Tf10[i, 5] > 0){
-    points(x = SUMM_Tf10[i, 1], y = SUMM_Tf10[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Tf10)[1]){
-  if(SUMM_Tf10[i, 7] > 0 & SUMM_Tf10[i, 8] > 0){
-    points(x = SUMM_Tf10[i, 1], y = SUMM_Tf10[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.4 ($\\psi = 1$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from approximately 100 replicate simulations with identical starting conditions (some parameter combinations had fewer replicates, minimum 400).
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Up to 1000 interactions occur between individuals in each time step ($\\psi = 1$), potentially resulting in a mating interaction.
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
-SUMM_Nexp1   <- read.csv("inst/SI_Nexp_1.csv");
-
-alpha_vals   <- sort(unique(SUMM_Nexp1[,1]));
-TM_vals      <- tapply(X = SUMM_Nexp1[,3],  INDEX = SUMM_Nexp1[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_Nexp1[,13], INDEX = SUMM_Nexp1[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_Nexp1[,14], INDEX = SUMM_Nexp1[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_Nexp1[,15], INDEX = SUMM_Nexp1[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_Nexp1[,16], INDEX = SUMM_Nexp1[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_Nexp1[,17], INDEX = SUMM_Nexp1[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_Nexp1[,18], INDEX = SUMM_Nexp1[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2.1));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Nexp1)[1]){
-  if(SUMM_Nexp1[i, 4] > 0 & SUMM_Nexp1[i, 5] > 0){
-    points(x = SUMM_Nexp1[i, 1], y = SUMM_Nexp1[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Nexp1)[1]){
-  if(SUMM_Nexp1[i, 7] > 0 & SUMM_Nexp1[i, 8] > 0){
-    points(x = SUMM_Nexp1[i, 1], y = SUMM_Nexp1[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.5 ($\\psi = 2$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 100 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates).
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Up to 2000 interactions occur between individuals in each time step ($\\psi = 2$), potentially resulting in a mating interaction.
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
-SUMM_Nexp2   <- read.csv("inst/SI_Nexp_2.csv");
-
-alpha_vals   <- sort(unique(SUMM_Nexp2[,1]));
-TM_vals      <- tapply(X = SUMM_Nexp2[,3],  INDEX = SUMM_Nexp2[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_Nexp2[,13], INDEX = SUMM_Nexp2[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_Nexp2[,14], INDEX = SUMM_Nexp2[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_Nexp2[,15], INDEX = SUMM_Nexp2[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_Nexp2[,16], INDEX = SUMM_Nexp2[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_Nexp2[,17], INDEX = SUMM_Nexp2[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_Nexp2[,18], INDEX = SUMM_Nexp2[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2.1));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Nexp2)[1]){
-  if(SUMM_Nexp2[i, 4] > 0 & SUMM_Nexp2[i, 5] > 0){
-    points(x = SUMM_Nexp2[i, 1], y = SUMM_Nexp2[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Nexp2)[1]){
-  if(SUMM_Nexp2[i, 7] > 0 & SUMM_Nexp2[i, 8] > 0){
-    points(x = SUMM_Nexp2[i, 1], y = SUMM_Nexp2[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.6 ($\\psi = 4$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 100 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates).
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Up to 4000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 4$).
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
-SUMM_Nexp4   <- read.csv("inst/SI_Nexp_4.csv");
-
-alpha_vals   <- sort(unique(SUMM_Nexp4[,1]));
-TM_vals      <- tapply(X = SUMM_Nexp4[,3],  INDEX = SUMM_Nexp4[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_Nexp4[,13], INDEX = SUMM_Nexp4[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_Nexp4[,14], INDEX = SUMM_Nexp4[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_Nexp4[,15], INDEX = SUMM_Nexp4[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_Nexp4[,16], INDEX = SUMM_Nexp4[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_Nexp4[,17], INDEX = SUMM_Nexp4[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_Nexp4[,18], INDEX = SUMM_Nexp4[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2.1));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Nexp4)[1]){
-  if(SUMM_Nexp4[i, 4] > 0 & SUMM_Nexp4[i, 5] > 0){
-    points(x = SUMM_Nexp4[i, 1], y = SUMM_Nexp4[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Nexp4)[1]){
-  if(SUMM_Nexp4[i, 7] > 0 & SUMM_Nexp4[i, 8] > 0){
-    points(x = SUMM_Nexp4[i, 1], y = SUMM_Nexp4[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.7 ($\\psi = 6$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 100 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates).
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Up to 6000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 6$).
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
-SUMM_Nexp6   <- read.csv("inst/SI_Nexp_6.csv");
-
-alpha_vals   <- sort(unique(SUMM_Nexp6[,1]));
-TM_vals      <- tapply(X = SUMM_Nexp6[,3],  INDEX = SUMM_Nexp6[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_Nexp6[,13], INDEX = SUMM_Nexp6[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_Nexp6[,14], INDEX = SUMM_Nexp6[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_Nexp6[,15], INDEX = SUMM_Nexp6[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_Nexp6[,16], INDEX = SUMM_Nexp6[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_Nexp6[,17], INDEX = SUMM_Nexp6[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_Nexp6[,18], INDEX = SUMM_Nexp6[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2.1));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Nexp6)[1]){
-  if(SUMM_Nexp6[i, 4] > 0 & SUMM_Nexp6[i, 5] > 0){
-    points(x = SUMM_Nexp6[i, 1], y = SUMM_Nexp6[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Nexp6)[1]){
-  if(SUMM_Nexp6[i, 7] > 0 & SUMM_Nexp6[i, 8] > 0){
-    points(x = SUMM_Nexp6[i, 1], y = SUMM_Nexp6[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.8 ($T_{\\mathrm{m}} = 0.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 1600 replicate simulations with identical starting conditions.
-The red line shows the threshold above which the mathematical model predicts that females should be choosy (male thresholds for search are not shown because simulations were initialised with males already searching for nuptial gifts).
-Up to 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 3$).
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
-SUMM_Tm05   <- read.csv("inst/SI_Tm_0pt5.csv");
-
-alpha_vals   <- sort(unique(SUMM_Tm05[,1]));
-TM_vals      <- tapply(X = SUMM_Tm05[,3],  INDEX = SUMM_Tm05[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_Tm05[,13], INDEX = SUMM_Tm05[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_Tm05[,14], INDEX = SUMM_Tm05[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_Tm05[,15], INDEX = SUMM_Tm05[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_Tm05[,16], INDEX = SUMM_Tm05[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_Tm05[,17], INDEX = SUMM_Tm05[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_Tm05[,18], INDEX = SUMM_Tm05[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 1.6));
-
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Tm05)[1]){
-  if(SUMM_Tm05[i, 4] > 0 & SUMM_Tm05[i, 5] > 0){
-    points(x = SUMM_Tm05[i, 1], y = SUMM_Tm05[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Tm05)[1]){
-  if(SUMM_Tm05[i, 7] > 0 & SUMM_Tm05[i, 8] > 0){
-    points(x = SUMM_Tm05[i, 1], y = SUMM_Tm05[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.9 ($T_{\\mathrm{m}} = 2.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 1600 replicate simulations with identical starting conditions.
-The red line shows the threshold above which the mathematical model predicts that females should be choosy (male thresholds for search are not shown because simulations were initialised with males already searching for nuptial gifts).
-Up to 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 3$).
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
-SUMM_Tm2p5   <- read.csv("inst/SI_Tm_2pt5.csv");
-
-alpha_vals   <- sort(unique(SUMM_Tm2p5[,1]));
-TM_vals      <- tapply(X = SUMM_Tm2p5[,3],  INDEX = SUMM_Tm2p5[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_Tm2p5[,13], INDEX = SUMM_Tm2p5[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_Tm2p5[,14], INDEX = SUMM_Tm2p5[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_Tm2p5[,15], INDEX = SUMM_Tm2p5[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_Tm2p5[,16], INDEX = SUMM_Tm2p5[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_Tm2p5[,17], INDEX = SUMM_Tm2p5[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_Tm2p5[,18], INDEX = SUMM_Tm2p5[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 1.6));
-
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Tm2p5)[1]){
-  if(SUMM_Tm2p5[i, 4] > 0 & SUMM_Tm2p5[i, 5] > 0){
-    points(x = SUMM_Tm2p5[i, 1], y = SUMM_Tm2p5[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Tm2p5)[1]){
-  if(SUMM_Tm2p5[i, 7] > 0 & SUMM_Tm2p5[i, 8] > 0){
-    points(x = SUMM_Tm2p5[i, 1], y = SUMM_Tm2p5[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-S3: Alternative derivation of male fitness threshold
+S1: Alternative derivation of male fitness threshold
 ------------------------------------
@@
 In the main text, we assumed that males made the decision to search or not search for a nuptial gift.
-The expected length of time for which searching males are expected to remain outside of the mating pool is $E[T_{\mathrm{m}}] = \alpha$ (see Methods).
-Alternatively, we can assume that males search for a period of $T_{\mathrm{m}}$ and spend this full duration of $T_{\mathrm{m}}$ in the time-out phase, even if they succeed in finding a nuptial gift.
+The expected length of time for which searching males are expected to remain outside of the mating pool is $E[T_{\mathrm{m}}] = \alpha$ (see Model).
+Alternatively, we can assume that males search for a period of $T_{\mathrm{m}}$ and spend this full duration of $T_{\mathrm{m}}$ in the time-out phase, even if they succeed in finding a nuptial gift (as we assumed in our IBM).
 The probability that a male obtains a nuptial gift during this time is modelled in Eq. 1,
@@
 
-We assume that the fitness increments to offspring associated with receiving a nuptial gift versus no nuptial gift are $1 + \gamma$ and 1, respectively. 
+We assume that the fitness increment in reproductive success associated with receiving a nuptial gift versus no nuptial gift are $\lambda(1 + \gamma)$ and $\lambda$, respectively. 
 The rate at which males increase their fitness can then be defined as the expected fitness increment from their nuptial gift search divided by $T_{\mathrm{m}}$ plus the time spent in the mating pool waiting to encounter a mate,
@@
 
-Our objective now is to determine the conditions under which a focal male increases its fitness by searching for a nuptial gift ($T_{\mathrm{m}}>0$) in a population of resident males that do not search ($T_{\mathrm{m}}=0$).
-Females are assumed to exhibit no choice in males with versus without nuptial gifts.
+Our objective now is to determine the conditions under which a focal male increases his fitness by searching for a nuptial gift ($T_{\mathrm{m}}>0$) in a population of resident males that do not search ($T_{\mathrm{m}}=0$).
+Females are assumed to exhibit no choosiness for males with versus without nuptial gifts.
 Under such conditions, male fitness cannot be affected by female choice, so selection to increase $T_{\mathrm{m}}>0$ must be based solely on $\alpha$, $\beta$, $R$, and $\gamma$.
@@
 A second term on the right-hand side is subtracted, which reflects a loss in fitness proportional to the encounter rate of potential mates in the mating pool.
-The conditions under which male inclusive fitness increases by searching for a nuptial gift are found by setting $\partial W_{\mathrm{m}}/\partial T_{\mathrm{m}} = 0$ and solving for $\gamma$ to get Eq.
-2 in the main text.
+The conditions under which male inclusive fitness increases by searching for a nuptial gift are found by setting $\partial W_{\mathrm{m}}/\partial T_{\mathrm{m}} = 0$ and solving for $\gamma$ to recover Eq.
+2 from the main text,
+
+$$0 = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)} - \lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}},$$
+
+$$\lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}} = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)},$$
+
+$$\frac{R}{{\left(1 + \beta \right)^{2}}} =  \frac{\gamma}{\alpha\left(\beta+1\right)},$$
+
+$$\frac{R}{{\left(1 + \beta \right)}} =  \frac{\gamma}{\alpha},$$
+
+$$\gamma = \alpha \frac{R }{\beta + 1}.$$
 
@@
 
-S4: Operational sex ratio
+S2: Operational sex ratio
 ------------------------------------
@@
 
-S5: Estimation of key model parameters using experimental data
--------------------------------------
+S3: Sensitivity analysis of parameters in IBM
+------------------------------------
 
-Estimates showing the mean number of offspring produced by female *Pisaura mirabilis* that ate nuptial gifts and females who did not. 
-Means were calculated with raw data from @Tuni2013a and results are shown $\pm$ SE (Table 1).
-Under these assumptions, the relative gain in fitness from receiving nuptial gifts for a female is,
+We investigated the sensitivity of our results to individual mortality during time-in ($\mu_{\mathrm{in}}$) and time-out ($\mu_{\mathrm{out}}$), female processing time ($T_{\mathrm{f}}$), and the potential for interactions between conspecifics ($\psi$).
+Across all of these simulations, there were challenges with statistical power.
+Evidence for the evolution of male search (blue points in figures) and female choosiness (red points in figures) was determined by the lower 95\% bootstrapped confidence interval of $T_{\mathrm{m}}$ and $T_{\mathrm{f}}$ values being greater than zero, respectively.
+This required a lot of replicate simulations in the main text (Figure 3), especially for values just above predicted thresholds and for female choosiness.
+Computation time was a limiting factor, even using a compiled language (C) and with access to a computing cluster.
+Absence of points above threshold values are not necessarily evidence that evolution of male search or female choosiness is not predicted to evolve in these regions of parameter space, but it does indicate that evolution of these traits is not necessarily assured given the stochasticity inherent to the IBM.
+Additional simulations can be conducted using the C code in the 'src' folder of the GitHub repository (https://github.com/bradduthie/nuptial_gift_evolution).
+Below, we explain the parameter values used in the sensitivity analysis in more detail.
 
-$$\hat{\delta_\mathrm{f}} = \frac{25.74}{6.00} = 4.29$$
+*Mortality*
 
-Since the baseline fitness is 1, the increase in fitness resulting from a nuptial gift then becomes,
+We conducted a sensitivity analysis of the effect of the mortality parameters $\mu_{\mathrm{in}}$ and $\mu_{\mathrm{out}}$ (the probability of mortality in time-in and time-out, respectively, which we assumed to be equal for all individuals) on the evolution of male search and female choice using the IBM.
+The results revealed no correlation between the value of the mortality parameters and the evolution of male search or female choice (Fig. S2.1).
 
-$$\hat{\gamma} = \hat{\delta_{\mathrm{f}}} - 1 = 3.29.$$
+*Female processing time*
 
-The value 3.29 was used to parameterise $\gamma$ for a set of simulations (Figure 4 in the main text).
+We also conducted a sensitivity analysis of female processing time $T_{\mathrm{f}}$. 
+To do this, we ran simulations at default values, but with $T_{\mathrm{f}} = 10.0$ (Figures S2.2).
 
-|                                 | Received nuptial gift | Received no nuptial gift |
-|---------------------------------|-----------------------|--------------------------|
-| Expected number of hatched eggs | $25.74 \pm 0.96$      | $6.00 \pm 2.1$           |
+*Interactions between conspecifics*
 
-Table 1: Estimates showing mean number of offspring produced by female *P.
-mirabilis* that ate nuptial gifts and females who did not.
-Means were calculated with raw data from @Tuni2013a and results are shown $\pm$ SE.
+We conducted a sensitivity analysis on the encounter rate between conspecifics ($R$) by varying the value of our scaling parameter $\psi$.
+Under default simulations, $\psi = 3$.
+We also ran simulations in which $\psi = 1$ (Figure S2.3), $\psi = 2$ (Figure S3.4), $\psi = 4$ (Figure S3.5), and $\psi = 6$ (Figure S3.6), with all other parameters being set to default values.
 
@@
 
-S6: Separate evolution of male search and female choice
--------------------------------------
+\captionsetup{labelformat=empty}
 
-We used the individual-based simulation model (see Supporting Information S1) to unpack the effect of coevolution on the evolution of male search and female choice. 
-Here we replicated the simulations shown in the main text under the condition where only one trait at a time was allowed to evolve and studied how this affected the trait evolution.
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.1: Evolution of both male search (blue) and female choice (red) under different combinations of the mortality rates $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$ (mortality in time-in and out, respectively).
+The y-axis is the threshold fitness that leads to evolution of male search (blue) or female choice (red).
+The results show noise, but no correlation between the value of the mortality parameters and the propensity for male search and/or female choice to evolve.
+For each of the $25 \\times 20$ combinations of $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$, 3000 replicate simulations were run."}
+SUMO         <- read.csv("inst/summary_mortality.csv");
+alpha_vals   <- sort(unique(SUMO[,3]));
+mort_combn   <- paste(SUMO[,1], SUMO[,2]);
+mort_label   <- unique(paste(SUMO[,1], ", ", SUMO[,2], sep = ""));
+TM_vals      <- tapply(X = SUMO[,5],  INDEX = mort_combn, FUN = mean);
+m_vals       <- tapply(X = SUMO[,14], INDEX = mort_combn, FUN = mean);
+beta_vals    <- tapply(X = SUMO[,15], INDEX = mort_combn, FUN = mean);
+Male_M       <- tapply(X = SUMO[,16], INDEX = mort_combn, FUN = mean);
+Female_M     <- tapply(X = SUMO[,17], INDEX = mort_combn, FUN = mean);
+Mf_nupt      <- tapply(X = SUMO[,18], INDEX = mort_combn, FUN = mean);
+Mf_nonupt    <- tapply(X = SUMO[,19], INDEX = mort_combn, FUN = mean);
+male_search  <- as.numeric(which(SUMO[,5] > 0 & SUMO[,6] > 0));
+fem_choose   <- as.numeric(which(SUMO[,8] > 0 & SUMO[,9] > 0));
+mimmom       <- unique(cbind(SUMO$mim, SUMO$mom));
 
-First, we submitted a set of simulations wherein male search did not evolve, but was fixed at different values (see Fig. S6.1). 
-Next, we ran the same set of simulations wherein male search evolved, but female choice was not possible. 
-The results thus show how each trait evolves in the absence of any coevolution (Fig. S6.1).
+mm <- SUMO[male_search,]
+mp <- NULL;
+for(i in 1:dim(mm)[1]){
+  rval <- which(mm[i, 1] == mimmom[,1] & mm[i, 2] == mimmom[,2]);
+  mp   <- rbind(mp, c(rval, mm[i, 4]));
+}
+
+ff <- SUMO[fem_choose,]
+fp <- NULL;
+for(i in 1:dim(ff)[1]){
+  rval <- which(ff[i, 1] == mimmom[,1] & ff[i, 2] == mimmom[,2]);
+  fp   <- rbind(fp, c(rval, ff[i, 4]));
+}
+
+par(mar = c(8, 5, 1, 1));
+plot(x = mp[,1], y = mp[,2], pch = 20, ylim = c(0, 2), col = "blue",
+     xlab = "", ylab = "", xaxt = "n", cex.lab = 1.25);
+points(x = fp[,1], y = fp[,2], cex = 2.5, col = "red", pch = 20);
+points(x = mp[,1], y = mp[,2], cex = 1.5, col = "blue", pch = 20);
+axis(side = 1, labels = mort_label, at = 1:25, las = 2);
+mtext(text = expression(paste("Mortality combination (",mu["in"],", ", 
+                              mu["out"],")")), side = 1, line = 6.5, 
+      cex = 1.25); 
+mtext(text = expression(paste("Fitness threshold (", gamma[f], " & ", 
+                              gamma[m], ")")), side = 2, line = 2.5, 
+      cex = 1.25); 
+```
+
+\captionsetup{labelformat=default}
+
+\clearpage
 
@@
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S6.1: The separate evolution of male search and female choosiness as a function of nuptial gift search time.
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.3 ($T_{\\mathrm{f}} = 10.0$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
+Each point includes data from 3000 replicate simulations with identical starting conditions.
+Up to 3000 interactions occur between individuals in each time step ($\\psi = 3$), potentially resulting in a mating interaction.
+The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
+Expected female processing time was set to $T_{\\mathrm{f}}=10.0$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.1, 2.0] and [0.0, 2.0], respectively, were used."}
+SUMM_Tf10 <- read.csv("inst/SI_Tf_10pt0.csv");
+
+alpha_vals <- sort(unique(SUMM_Tf10[,1]));
+TM_vals    <- tapply(X = SUMM_Tf10[,3],  INDEX = SUMM_Tf10[,1], FUN = mean);
+m_vals     <- tapply(X = SUMM_Tf10[,13], INDEX = SUMM_Tf10[,1], FUN = mean);
+beta_vals  <- tapply(X = SUMM_Tf10[,14], INDEX = SUMM_Tf10[,1], FUN = mean);
+Male_M     <- tapply(X = SUMM_Tf10[,15], INDEX = SUMM_Tf10[,1], FUN = mean);
+Female_M   <- tapply(X = SUMM_Tf10[,16], INDEX = SUMM_Tf10[,1], FUN = mean);
+Mf_nupt    <- tapply(X = SUMM_Tf10[,17], INDEX = SUMM_Tf10[,1], FUN = mean);
+Mf_nonupt  <- tapply(X = SUMM_Tf10[,18], INDEX = SUMM_Tf10[,1], FUN = mean);
+
+g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
+g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
+                            TF = 10);
+
+par(mar = c(5, 5, 1, 1)); 
+plot(x = alpha_vals, y = g_f, type = "n", lwd = 2, cex.lab = 1.25, col = "red",
+     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
+     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
+                             ")")),
+     ylim = c(0, 2.0));
+
+#points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
+#points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
+#       lty = "dashed");
+
+for(i in 1:dim(SUMM_Tf10)[1]){
+  if(SUMM_Tf10[i, 4] > 0 & SUMM_Tf10[i, 5] > 0){
+    points(x = SUMM_Tf10[i, 1], y = SUMM_Tf10[i, 2], cex = 3, pch = 20, 
+           col = "blue");
+  }
+}
+
+for(i in 1:dim(SUMM_Tf10)[1]){
+  if(SUMM_Tf10[i, 7] > 0 & SUMM_Tf10[i, 8] > 0){
+    points(x = SUMM_Tf10[i, 1], y = SUMM_Tf10[i, 2], cex = 2, pch = 20, 
+           col = "red");
+  }
+}
+```
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.4 ($\\psi = 1$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
+Each point includes data from 3000 replicate simulations with identical starting conditions.
+Up to 1000 interactions occur between individuals in each time step ($\\psi = 1$), potentially resulting in a mating interaction.
+The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
+Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 2.0] and [0.1, 2.0], respectively, were used."}
+SUMM_Nexp1   <- read.csv("inst/SI_Nexp_1.csv");
+
+alpha_vals   <- sort(unique(SUMM_Nexp1[,1]));
+TM_vals      <- tapply(X = SUMM_Nexp1[,3],  INDEX = SUMM_Nexp1[,1], FUN = mean);
+m_vals       <- tapply(X = SUMM_Nexp1[,13], INDEX = SUMM_Nexp1[,1], FUN = mean);
+beta_vals    <- tapply(X = SUMM_Nexp1[,14], INDEX = SUMM_Nexp1[,1], FUN = mean);
+Male_M       <- tapply(X = SUMM_Nexp1[,15], INDEX = SUMM_Nexp1[,1], FUN = mean);
+Female_M     <- tapply(X = SUMM_Nexp1[,16], INDEX = SUMM_Nexp1[,1], FUN = mean);
+Mf_nupt      <- tapply(X = SUMM_Nexp1[,17], INDEX = SUMM_Nexp1[,1], FUN = mean);
+Mf_nonupt    <- tapply(X = SUMM_Nexp1[,18], INDEX = SUMM_Nexp1[,1], FUN = mean);
+
+g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
+g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
+                            TF = 2);
+
+par(mar = c(5, 5, 1, 1)); 
+plot(x = alpha_vals, y = g_f, type = "n", lwd = 2, cex.lab = 1.25, col = "red",
+     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
+     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
+                             ")")),
+     ylim = c(0, 2.0));
+
+# points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
+# points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
+#        lty = "dashed");
+
+for(i in 1:dim(SUMM_Nexp1)[1]){
+  if(SUMM_Nexp1[i, 4] > 0 & SUMM_Nexp1[i, 5] > 0){
+    points(x = SUMM_Nexp1[i, 1], y = SUMM_Nexp1[i, 2], cex = 3, pch = 20, 
+           col = "blue");
+  }
+}
+
+for(i in 1:dim(SUMM_Nexp1)[1]){
+  if(SUMM_Nexp1[i, 7] > 0 & SUMM_Nexp1[i, 8] > 0){
+    points(x = SUMM_Nexp1[i, 1], y = SUMM_Nexp1[i, 2], cex = 2, pch = 20, 
+           col = "red");
+  }
+}
+```
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.5 ($\\psi = 2$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
+Each point includes data from 3000 replicate simulations with identical starting conditions.
+Up to 2000 interactions occur between individuals in each time step ($\\psi = 2$), potentially resulting in a mating interaction.
+The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
+Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 2.0] and [0.1, 2.0], respectively, were used."}
+SUMM_Nexp2   <- read.csv("inst/SI_Nexp_2.csv");
+
+alpha_vals   <- sort(unique(SUMM_Nexp2[,1]));
+TM_vals      <- tapply(X = SUMM_Nexp2[,3],  INDEX = SUMM_Nexp2[,1], FUN = mean);
+m_vals       <- tapply(X = SUMM_Nexp2[,13], INDEX = SUMM_Nexp2[,1], FUN = mean);
+beta_vals    <- tapply(X = SUMM_Nexp2[,14], INDEX = SUMM_Nexp2[,1], FUN = mean);
+Male_M       <- tapply(X = SUMM_Nexp2[,15], INDEX = SUMM_Nexp2[,1], FUN = mean);
+Female_M     <- tapply(X = SUMM_Nexp2[,16], INDEX = SUMM_Nexp2[,1], FUN = mean);
+Mf_nupt      <- tapply(X = SUMM_Nexp2[,17], INDEX = SUMM_Nexp2[,1], FUN = mean);
+Mf_nonupt    <- tapply(X = SUMM_Nexp2[,18], INDEX = SUMM_Nexp2[,1], FUN = mean);
+
+g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
+g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
+                            TF = 2);
+
+par(mar = c(5, 5, 1, 1)); 
+plot(x = alpha_vals, y = g_f, type = "n", lwd = 2, cex.lab = 1.25, col = "red",
+     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
+     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
+                             ")")),
+     ylim = c(0, 2.0));
+
+# points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
+# points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
+#        lty = "dashed");
+
+for(i in 1:dim(SUMM_Nexp2)[1]){
+  if(SUMM_Nexp2[i, 4] > 0 & SUMM_Nexp2[i, 5] > 0){
+    points(x = SUMM_Nexp2[i, 1], y = SUMM_Nexp2[i, 2], cex = 3, pch = 20, 
+           col = "blue");
+  }
+}
+
+for(i in 1:dim(SUMM_Nexp2)[1]){
+  if(SUMM_Nexp2[i, 7] > 0 & SUMM_Nexp2[i, 8] > 0){
+    points(x = SUMM_Nexp2[i, 1], y = SUMM_Nexp2[i, 2], cex = 2, pch = 20, 
+           col = "red");
+  }
+}
+```
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.6 ($\\psi = 4$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
+Each point includes data from 3000 replicate simulations with identical starting conditions.
+Up to 4000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 4$).
+The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
+Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 2.0] and [0.1, 2.0], respectively, were used."}
+SUMM_Nexp4   <- read.csv("inst/SI_Nexp_4.csv");
+
+alpha_vals   <- sort(unique(SUMM_Nexp4[,1]));
+TM_vals      <- tapply(X = SUMM_Nexp4[,3],  INDEX = SUMM_Nexp4[,1], FUN = mean);
+m_vals       <- tapply(X = SUMM_Nexp4[,13], INDEX = SUMM_Nexp4[,1], FUN = mean);
+beta_vals    <- tapply(X = SUMM_Nexp4[,14], INDEX = SUMM_Nexp4[,1], FUN = mean);
+Male_M       <- tapply(X = SUMM_Nexp4[,15], INDEX = SUMM_Nexp4[,1], FUN = mean);
+Female_M     <- tapply(X = SUMM_Nexp4[,16], INDEX = SUMM_Nexp4[,1], FUN = mean);
+Mf_nupt      <- tapply(X = SUMM_Nexp4[,17], INDEX = SUMM_Nexp4[,1], FUN = mean);
+Mf_nonupt    <- tapply(X = SUMM_Nexp4[,18], INDEX = SUMM_Nexp4[,1], FUN = mean);
+
+g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
+g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
+                            TF = 2);
+
+par(mar = c(5, 5, 1, 1)); 
+plot(x = alpha_vals, y = g_f, type = "n", lwd = 2, cex.lab = 1.25, col = "red",
+     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
+     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
+                             ")")),
+     ylim = c(0, 2.0));
+
+# points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
+# points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
+#        lty = "dashed");
+
+for(i in 1:dim(SUMM_Nexp4)[1]){
+  if(SUMM_Nexp4[i, 4] > 0 & SUMM_Nexp4[i, 5] > 0){
+    points(x = SUMM_Nexp4[i, 1], y = SUMM_Nexp4[i, 2], cex = 3, pch = 20, 
+           col = "blue");
+  }
+}
+
+for(i in 1:dim(SUMM_Nexp4)[1]){
+  if(SUMM_Nexp4[i, 7] > 0 & SUMM_Nexp4[i, 8] > 0){
+    points(x = SUMM_Nexp4[i, 1], y = SUMM_Nexp4[i, 2], cex = 2, pch = 20, 
+           col = "red");
+  }
+}
+```
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.7 ($\\psi = 6$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
+Each point includes data from 3000 replicate simulations with identical starting conditions.
+Up to 6000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 6$).
+The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
+Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 2.0] and [0.1, 2.0], respectively, were used."}
+SUMM_Nexp6   <- read.csv("inst/SI_Nexp_6.csv");
+
+alpha_vals   <- sort(unique(SUMM_Nexp6[,1]));
+TM_vals      <- tapply(X = SUMM_Nexp6[,3],  INDEX = SUMM_Nexp6[,1], FUN = mean);
+m_vals       <- tapply(X = SUMM_Nexp6[,13], INDEX = SUMM_Nexp6[,1], FUN = mean);
+beta_vals    <- tapply(X = SUMM_Nexp6[,14], INDEX = SUMM_Nexp6[,1], FUN = mean);
+Male_M       <- tapply(X = SUMM_Nexp6[,15], INDEX = SUMM_Nexp6[,1], FUN = mean);
+Female_M     <- tapply(X = SUMM_Nexp6[,16], INDEX = SUMM_Nexp6[,1], FUN = mean);
+Mf_nupt      <- tapply(X = SUMM_Nexp6[,17], INDEX = SUMM_Nexp6[,1], FUN = mean);
+Mf_nonupt    <- tapply(X = SUMM_Nexp6[,18], INDEX = SUMM_Nexp6[,1], FUN = mean);
+
+g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
+g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
+                            TF = 2);
+
+par(mar = c(5, 5, 1, 1)); 
+plot(x = alpha_vals, y = g_f, type = "n", lwd = 2, cex.lab = 1.25, col = "red",
+     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
+     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
+                             ")")),
+     ylim = c(0, 2.0));
+
+# points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
+# points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
+#        lty = "dashed");
+
+for(i in 1:dim(SUMM_Nexp6)[1]){
+  if(SUMM_Nexp6[i, 4] > 0 & SUMM_Nexp6[i, 5] > 0){
+    points(x = SUMM_Nexp6[i, 1], y = SUMM_Nexp6[i, 2], cex = 3, pch = 20, 
+           col = "blue");
+  }
+}
+
+for(i in 1:dim(SUMM_Nexp6)[1]){
+  if(SUMM_Nexp6[i, 7] > 0 & SUMM_Nexp6[i, 8] > 0){
+    points(x = SUMM_Nexp6[i, 1], y = SUMM_Nexp6[i, 2], cex = 2, pch = 20, 
+           col = "red");
+  }
+}
+```
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+S4: Separate evolution of male search and female choice
+-------------------------------------
+
+We used the individual-based simulation model to unpack the effect of coevolution on the evolution of male search and female choice. 
+Here we replicated the simulations shown in the main text under the condition where only one trait at a time was allowed to evolve and studied how this affected the trait evolution.
+
+First, we submitted a set of simulations wherein male search did not evolve, but was fixed at different values. 
+Next, we ran the same set of simulations wherein male search evolved, but female choice was not possible. 
+The results thus show how each trait evolves in the absence of any coevolution (Fig. S4.1).
+
+\captionsetup{labelformat=empty}
+
+```{r echo = FALSE, eval = TRUE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.1: The separate evolution of male search and female choosiness as a function of nuptial gift search time.
 Points show where the lower 95% confidence interval of male search (blue) and female choosiness (red) exceeds zero, indicating evolution of nuptial gift search or choosiness.
-Each point includes data from $2 \\times 1600$ replicate simulations with identical starting conditions.
+Each point includes data from $2 \\times 3000$ replicate simulations with identical starting conditions.
 In the first batch, male search was constant and initialized at $T_{\\mathrm{m}} = \\alpha$, and female choice was evolving.
 In the second batch, male search was evolving, and there was no option for female choice.
-The parameters $T_{\\mathrm{f}}=2$, and $\\gamma$ and $\\alpha$ values were set within the range [0.1, 2.0] and [0.3, 1.7], respectively."}
+The parameters $T_{\\mathrm{f}}=2$, and $\\gamma$ and $\\alpha$ values were set within the range [0.1, 2.0] and [0.0, 2.0], respectively."}
 SUMM_m <- read.csv("inst/summary_male_evolving.csv");
@@
 
+alpha_vals   <- sort(unique(SUMM_m[,1]));
 par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_m, type = "l", lwd = 2, cex.lab = 1.25,
+plot(x = alpha_vals, y = g_m, type = "n", lwd = 2, cex.lab = 1.25,
      xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
@@
 
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red");
+# points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red");
 

### 2024-11-29 SI.tex
Fixed up traits and manuscript. Traits are not binary anymore, but are diploid

@@
 \endhead
-S1: Description of the individual-based simulation model & 2 \\
-S2: Sensitivity analysis of mortality parameters in IBM & 4 \\
-S3: Alternative derivation of male fitness threshold & 14 \\
-S4: Operational sex ratio & 16 \\
-S5: Estimation of key model parameter using experimental data & 17 \\
-S6: Separate evolution of male search and female choice & 18 \\
-References & 19 \\
+S1: Alternative derivation of male fitness threshold & 2 \\
+S2: Operational sex ratio & 4 \\
+S3: Sensitivity analysis of parameters in IBM & 5 \\
+S4: Separate evolution of male search and female choice & 12 \\
+References & 13 \\
 \bottomrule
@@
 
-\hypertarget{s1-description-of-the-individual-based-simulation-model}{%
-\subsection{S1: Description of the individual-based simulation
-model}\label{s1-description-of-the-individual-based-simulation-model}}
-
-Here we describe the details of initialisation, time-in (mating),
-time-out (reproduction and nuptial gift search), and mortality. We then
-summarise the simulations run and data collected.
-
-\emph{Initialisation}
-
-Before the first time step, a population of \(N = 1000\) individuals is
-initialised. Individuals are assigned unique IDs, and each is assigned
-to be female with a probability of \(0.5\), else male. Each individual
-\(i\) is initialised with a starting value of female offspring
-processing time (\(T^{i}_{\mathrm{f}}\)), rejection probability of
-gift-less males (\(\rho^{i}\)), and male search time
-(\(T^{i}_{\mathrm{m}}\)). For all simulations, initialised values are
-set to \(T^{i}_{\mathrm{f}} = 2\), \(\rho^{i} = 0\), and
-\(T^{i}_{\mathrm{m}} = 0\). All individuals are initalised outside of
-the mating pool in the first time step \(t = 1\). The first time step
-then proceeds with females immediately entering the mating pool and
-males either entering the mating pool or searching for nuptial gifts.
-
-\emph{Time-in}
-
-At the start of each time step, females and males in the mating pool
-remain in it. Females will enter the mating pool after processing
-offspring, and males will enter it after searching for nuptial gifts
-(see `Time-out' below). Up to \(\Psi = N\psi\) interactions between
-individuals can occur in a single time step, where \(N\) is population
-size and \(\psi\) is a scaling parameter. In each time step, \(\Psi\)
-pairs of individuals are selected at random to interact. For each
-interaction, two different individuals are randomly selected from the
-population with equal probability. If the selected individuals are of
-different sexes, and both are in the mating pool, then a mating
-encounter occurs. If the male does not have a nuptial gift, then the
-female will reject him with a probability of \(\rho^{i}\); if rejection
-occurs, then both individuals stay in the mating pool. If rejection does
-not occur, or the male has a nuptial gift in the mating encounter, then
-the individuals mate. Females leave the mating pool and enter time-out
-to process offspring, and males leave and enter time-out to potentially
-search for new nuptial gifts (note that females and males might re-enter
-the mating pool immediately within the same time step given sufficiently
-low search time; see Time-out below).
-
-\emph{Time-out}
-
-During time-out, offspring production and time outside of the mating
-pool are realised for each female by sampling from a Poisson
-distribution. A focal female \(i\) will produce \(Poisson(\lambda)\)
-offspring if no nuptial gift was provided or
-\(Poisson(\lambda + \gamma)\) if a gift was provided. Females remain
-outside of the mating pool to process offspring for
-\(Poisson(T^{i}_{\mathrm{f}})\) time steps. Offspring are added to the
-population immediately, with \(\rho^{i}\) and \(T^{i}_{\mathrm{m}}\)
-values that are the average of each parent plus some normally
-distributed error \(\epsilon_{R}\) and \(\epsilon_{T_{\mathrm{m}}}\).
-For example,
-
-\[T^{\mathrm{offspring}}_{\mathrm{m}} \sim \frac{T^{\mathrm{mother}}_{\mathrm{m}}  + T^{\mathrm{father}}_{\mathrm{m}}}{2} + N\left(0, \epsilon_{T_{\mathrm{m}}} \right).\]
-
-The variation generated by \(\epsilon\) values simulates mutation upon
-which selection for traits can act. In all simulations, \(\epsilon = 0\)
-if a trait is fixed and \(\epsilon = 0.01\) if the trait evolves.
-Offspring sex is randomly assigned with equal probability as female or
-male. Female offspring are immediately placed in the mating pool, and
-male offspring are out of the mating pool to potentially search for
-nuptial gifts. After a female has spent \(T^{i}_{\mathrm{f}}\) time
-steps outside the mating pool, she will re-enter it.
-
-A focal male \(i\) outside the mating pool will enter it if he has
-searched for a fixed number of \(T^{i}_{\mathrm{m}}\) time steps, which
-is also sampled randomly from a Poisson distribution,
-\(Poisson(T^{i}_{\mathrm{m}})\). If \(T^{i}_{\mathrm{m}} = 0\), then the
-male immediately returns to the mating pool (in the same time step). If
-\(T^{i}_{\mathrm{m}} > 0\), then the male must wait outside the mating
-pool for \(Poisson(T^{i}_{\mathrm{m}})\) time steps, but will enter the
-mating pool with a nuptial gift with a probability,
-
-\[P(G^{i}) = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.\]
-
-Males must always spend \(T^{i}_{\mathrm{m}}\) time steps outside of the
-mating pool regardless of whether or not they are successful in
-obtaining a nuptial gift.
-
-\emph{Mortality}
-
-At the end of each time step, mortality occurs first with a fixed
-probability for all adults in the population, then with a probability
-caused by carrying capacity \(K\) applied to all individuals (adults and
-offspring). Mortality occurs in each time step with a fixed probability
-of \(\mu\) regardless of the sex of the individual or its position in or
-out of the mating pool. If after this fixed mortality is applied, the
-total population size \(N > K\), then individuals are removed at random
-with equal probability until \(N = K\). Following adult mortality, a new
-time step begins with newly added offspring becoming adults.
-
-\emph{Simulations}
-
-We ran simulations in which male search time and female choosiness
-evolved from an ancestral state of no searching and no choosiness. In
-all simulations, \(N\) was initialised at 1000 and \(K = 1000\).
-Simulations ran for \(t_{max} = 40000\) time steps. We set
-\(T_{\mathrm{f}} = 2\), \(\psi = 3\), and \(\lambda = 1\) for all
-simulations, and we simulated across a range of
-\(\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}\) and
-\(\gamma = \{0, 0.1, ..., 1.9, 2.0\}\) parameter values for 3200
-replicates. Summary statistics for mean trait values, population size,
-sex ratios, proportion of females and males in and out of the mating
-pool, and mean number of encounters per female and male within the
-mating pool were all calculated in the last time step. The C code used
-for simulating these IBMs also allows for the reporting of statistics in
-each time step. Additionally, it can simulate explicit space and
-individual movement through the landscape. A neutral evolving trait was
-also modelled to ensure that the code functioned as intended, and
-processes were compartmentalised into individual functions to facilitate
-code testing. All code is publicly available on GitHub
-(\url{https://github.com/bradduthie/nuptial_gift_evolution}).
-
-A set of simulations with a value of \(\gamma\) calculated from
-empirical data was also conducted (100 replicates). Here, \(\gamma\) was
-parameterised using data on egg production as a function of eating
-nuptial gifts (see below). Additional simulation sets with lower and
-upper bounds of the estimated \(\gamma\) were subsequently run. In the
-simulation sets with experimentally derived parameter values, all other
-parameters were identical to previous simulation batches.
-
-We can produce an estimate of the fitness increment obtained by females
-when receiving a gift (\(\hat{\gamma}\)) by using data on female
-\emph{P. mirabilis} egg production and hatching success under different
-feeding regimes from (\protect\hyperlink{ref-Tuni2013a}{Tuni \emph{et
-al.}, 2013}). Tuni \emph{et al.}
-(\protect\hyperlink{ref-Tuni2013a}{2013}) found differences in egg
-production and hatching success in female \emph{P. mirabilis} under
-different feeding regimes. Assuming these differences in feeding regimes
-correspond to eating versus not eating nuptial gifts, the mean number of
-offspring produced by a female who eats nuptial gifts can be calculated
-(Table 1).
-
-\clearpage
-
-\hypertarget{s2-sensitivity-analysis-of-parameters-in-ibm}{%
-\subsection{S2: Sensitivity analysis of parameters in
-IBM}\label{s2-sensitivity-analysis-of-parameters-in-ibm}}
-
-We investigated the sensitivity of our results to individual mortality
-during time-in (\(\mu_{\mathrm{in}}\)) and time-out
-(\(\mu_{\mathrm{out}}\)), female processing time (\(T_{\mathrm{f}}\)),
-potential for interactions between conspecifics (\(\psi\)), and
-initialised male search time (\(T_{\mathrm{m}}\)). Across all of these
-simulations, there were challenges with statistical power. Evidence for
-the evolution of male search (blue points in figures) and female
-choosiness (red points in figures) was determined by the lower 95\%
-bootstrapped confidence interval of \(T_{\mathrm{m}}\) and
-\(T_{\mathrm{f}}\) values being greater than zero, respectively. This
-required a lot of replicate simulations in the main text (Figure 3),
-especially for values just above predicted thresholds and for female
-choosiness. Computation time was a limiting factor, even using a
-compiled language (C) and with access to a computing cluster. Absence of
-points above threshold values are not necessarily evidence that
-evolution of male search or female choosiness is not predicted to evolve
-in these regions of parameter space, but it does indicate that evolution
-of these traits is not necessarily assured given the stochasticity
-inherent to the IBM. Additional simulations can be conducted using the C
-code in the `src' folder of the GitHub repository
-(\url{https://github.com/bradduthie/nuptial_gift_evolution}). Below, we
-explain the parameter values used in the sensitivity analysis in more
-detail.
-
-\emph{Mortality}
-
-We conducted a sensitivity analysis of the effect of the mortality
-parameters \(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\) (the
-probability of mortality in time-in and time-out, respectively, which we
-assumed to be equal for all individuals) on the evolution of male search
-and female choice using the IBM (See S1). The results revealed no
-correlation between the value of the mortality parameters and the
-evolution of male search or female choice (Fig. S2.1).
-
-\emph{Female processing time}
-
-We also conducted a sensitivity analysis of female processing time
-\(T_{\mathrm{f}}\). To do this, we ran simulations at default values,
-but with \(T_{\mathrm{f}} = 0.4\) (Figure S4.2) and
-\(T_{\mathrm{f}} = 10.0\) (Figures S4.3).
-
-\emph{Interactions between conspecifics}
-
-We conducted a sensitivity analysis on the encounter rate between
-conspecifics (\(R\)) by varying the value of \(\psi\) (see S1). Under
-default simulations, \(\psi = 3\). We also ran simulations in which
-\(\psi = 1\) (Figure S4.4), \(\psi = 2\) (Figure S4.5), \(\psi = 4\)
-(Figure S4.6), and \(\psi = 6\) (Figure S4.7), with all other parameters
-being set to default values.
-
-\emph{Initialised male search time}
-
-Lastly, we conducted a sensitivity analysis on initialised male search
-time (\(T_{\mathrm{m}}\)). To do this, we ran simulations at default
-values, but initialised all males at \(T_{\mathrm{m}} = 0.5\) (Figure
-S4.8) or \(T_{\mathrm{m}} = 2.5\) (S4.9). Note that under these
-initialisation conditions, it no longer makes sense to test whether or
-not \(T_{\mathrm{m}}\) evolves to positive values, so we do not show
-predicted male search thresholds and focus only on female choosiness.
-Interestingly, while predictions given initialised
-\(T_{\mathrm{m}} = 0.5\) are quite close for female choosiness
-thresholds, female choosiness does not appear to evolve given
-\(T_{\mathrm{m}} = 2.5\). This might be due to low selection pressure to
-reject males without gifts due to their low frequency. In other words,
-while females would benefit from a strategy of rejecting gift-less
-males, a lack of realised encounters with gift-less males preclude the
-evolution of sustained selection for choosiness.
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{SI_files/figure-latex/unnamed-chunk-2-1.pdf}
-\caption{Figure S2.1: Evolution of both male search (blue) and female
-choice (red) under different combinations of the mortality rates
-\(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\) (mortality in time-in
-and out, respectively). The y-axis is the threshold fitness that leads
-to evolution of male search (blue) or female choice (red). The results
-show noise, but no correlation between the value of the mortality
-parameters and the propensity for male search and/or female choice to
-evolve. For each of the \(25 \times 20\) combinations of
-\(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\), 1600 replicate
-simulations were run.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{SI_files/figure-latex/unnamed-chunk-3-1.pdf}
-\caption{Figure S2.2 (\(T_{\mathrm{f}} = 0.5\)): The coevolution of male
-search and female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-female choosiness (red) and male search (blue) exceeds zero, indicating
-evolution of choosiness or nuptial gift search. Each point includes data
-from approximately 1600 replicate simulations with identical starting
-conditions (some parameter combinations have fewer replicates). Red and
-blue lines show thresholds above which the mathematical model predicts
-that females should be choosy and males should search, respectively. Up
-to 3000 interactions occur between individuals in each time step
-(\(\psi = 3\)), potentially resulting in a mating interaction. The
-number of individuals in the population remained at or near carrying
-capacity of \(K = 1000\). Expected female processing time was set to
-\(T_{\mathrm{f}}=0.5\) time steps, and \(\gamma\) and \(\alpha\) values
-in the range {[}0.5, 1.5{]} and {[}0.1, 2.1{]}, respectively, were
-used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{SI_files/figure-latex/unnamed-chunk-4-1.pdf}
-\caption{Figure S2.3 (\(T_{\mathrm{f}} = 10.0\)): The coevolution of
-male search and female choosiness as a function of nuptial gift search
-time (\(\alpha\)). Points show where the lower 95\% confidence interval
-of female choosiness (red) and male search (blue) exceeds zero,
-indicating evolution of choosiness or nuptial gift search. Each point
-includes data from approximately 1600 replicate simulations with
-identical starting conditions (some parameter combinations include fewer
-replicates). Red and blue lines show thresholds above which the
-mathematical model predicts that females should be choosy and males
-should search, respectively. Up to 3000 interactions occur between
-individuals in each time step (\(\psi = 3\)), potentially resulting in a
-mating interaction. The number of individuals in the population remained
-at or near carrying capacity of \(K = 1000\). Expected female processing
-time was set to \(T_{\mathrm{f}}=10.0\) time steps, and \(\gamma\) and
-\(\alpha\) values in the range {[}0.5, 1.5{]} and {[}0.1, 2.1{]},
-respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{SI_files/figure-latex/unnamed-chunk-5-1.pdf}
-\caption{Figure S2.4 (\(\psi = 1\)): The coevolution of male search and
-female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from
-approximately 100 replicate simulations with identical starting
-conditions (some parameter combinations had fewer replicates, minimum
-400). Red and blue lines show thresholds above which the mathematical
-model predicts that females should be choosy and males should search,
-respectively. Up to 1000 interactions occur between individuals in each
-time step (\(\psi = 1\)), potentially resulting in a mating interaction.
-The number of individuals in the population remained at or near carrying
-capacity of \(K = 1000\). Expected female processing time was set to
-\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
-the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]}, respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{SI_files/figure-latex/unnamed-chunk-6-1.pdf}
-\caption{Figure S2.5 (\(\psi = 2\)): The coevolution of male search and
-female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 100
-replicate simulations with identical starting conditions (some parameter
-combinations have fewer replicates). Red and blue lines show thresholds
-above which the mathematical model predicts that females should be
-choosy and males should search, respectively. Up to 2000 interactions
-occur between individuals in each time step (\(\psi = 2\)), potentially
-resulting in a mating interaction. The number of individuals in the
-population remained at or near carrying capacity of \(K = 1000\).
-Expected female processing time was set to \(T_{\mathrm{f}}=2\) time
-steps, and \(\gamma\) and \(\alpha\) values in the range {[}0.0, 1.4{]}
-and {[}0.1, 1.2{]}, respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{SI_files/figure-latex/unnamed-chunk-7-1.pdf}
-\caption{Figure S2.6 (\(\psi = 4\)): The coevolution of male search and
-female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 100
-replicate simulations with identical starting conditions (some parameter
-combinations have fewer replicates). Red and blue lines show thresholds
-above which the mathematical model predicts that females should be
-choosy and males should search, respectively. Up to 4000 interactions
-occur between individuals in each time step, potentially resulting in a
-mating interaction (\(\psi = 4\)). The number of individuals in the
-population remained at or near carrying capacity of \(K = 1000\).
-Expected female processing time was set to \(T_{\mathrm{f}}=2\) time
-steps, and \(\gamma\) and \(\alpha\) values in the range {[}0.0, 1.4{]}
-and {[}0.1, 1.2{]}, respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{SI_files/figure-latex/unnamed-chunk-8-1.pdf}
-\caption{Figure S2.7 (\(\psi = 6\)): The coevolution of male search and
-female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 100
-replicate simulations with identical starting conditions (some parameter
-combinations have fewer replicates). Red and blue lines show thresholds
-above which the mathematical model predicts that females should be
-choosy and males should search, respectively. Up to 6000 interactions
-occur between individuals in each time step, potentially resulting in a
-mating interaction (\(\psi = 6\)). The number of individuals in the
-population remained at or near carrying capacity of \(K = 1000\).
-Expected female processing time was set to \(T_{\mathrm{f}}=2\) time
-steps, and \(\gamma\) and \(\alpha\) values in the range {[}0.0, 1.4{]}
-and {[}0.1, 1.2{]}, respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{SI_files/figure-latex/unnamed-chunk-9-1.pdf}
-\caption{Figure S2.8 (\(T_{\mathrm{m}} = 0.5\)): The coevolution of male
-search and female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 1600
-replicate simulations with identical starting conditions. The red line
-shows the threshold above which the mathematical model predicts that
-females should be choosy (male thresholds for search are not shown
-because simulations were initialised with males already searching for
-nuptial gifts). Up to 3000 interactions occur between individuals in
-each time step, potentially resulting in a mating interaction
-(\(\psi = 3\)). The number of individuals in the population remained at
-or near carrying capacity of \(K = 1000\). Expected female processing
-time was set to \(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and
-\(\alpha\) values in the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]},
-respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{SI_files/figure-latex/unnamed-chunk-10-1.pdf}
-\caption{Figure S2.9 (\(T_{\mathrm{m}} = 2.5\)): The coevolution of male
-search and female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 1600
-replicate simulations with identical starting conditions. The red line
-shows the threshold above which the mathematical model predicts that
-females should be choosy (male thresholds for search are not shown
-because simulations were initialised with males already searching for
-nuptial gifts). Up to 3000 interactions occur between individuals in
-each time step, potentially resulting in a mating interaction
-(\(\psi = 3\)). The number of individuals in the population remained at
-or near carrying capacity of \(K = 1000\). Expected female processing
-time was set to \(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and
-\(\alpha\) values in the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]},
-respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\hypertarget{s3-alternative-derivation-of-male-fitness-threshold}{%
-\subsection{S3: Alternative derivation of male fitness
-threshold}\label{s3-alternative-derivation-of-male-fitness-threshold}}
+\hypertarget{s1-alternative-derivation-of-male-fitness-threshold}{%
+\subsection{S1: Alternative derivation of male fitness
+threshold}\label{s1-alternative-derivation-of-male-fitness-threshold}}
 
@@
 searching males are expected to remain outside of the mating pool is
-\(E[T_{\mathrm{m}}] = \alpha\) (see Methods). Alternatively, we can
-assume that males search for a period of \(T_{\mathrm{m}}\) and spend
-this full duration of \(T_{\mathrm{m}}\) in the time-out phase, even if
-they succeed in finding a nuptial gift. The probability that a male
-obtains a nuptial gift during this time is modelled in Eq. 1,
+\(E[T_{\mathrm{m}}] = \alpha\) (see Model). Alternatively, we can assume
+that males search for a period of \(T_{\mathrm{m}}\) and spend this full
+duration of \(T_{\mathrm{m}}\) in the time-out phase, even if they
+succeed in finding a nuptial gift (as we assumed in our IBM). The
+probability that a male obtains a nuptial gift during this time is
+modelled in Eq. 1,
 
@@
 
-We assume that the fitness increments to offspring associated with
-receiving a nuptial gift versus no nuptial gift are \(1 + \gamma\) and
-1, respectively. The rate at which males increase their fitness can then
-be defined as the expected fitness increment from their nuptial gift
-search divided by \(T_{\mathrm{m}}\) plus the time spent in the mating
-pool waiting to encounter a mate,
+We assume that the fitness increment in reproductive success associated
+with receiving a nuptial gift versus no nuptial gift are
+\(\lambda(1 + \gamma)\) and \(\lambda\), respectively. The rate at which
+males increase their fitness can then be defined as the expected fitness
+increment from their nuptial gift search divided by \(T_{\mathrm{m}}\)
+plus the time spent in the mating pool waiting to encounter a mate,
 
@@
 Our objective now is to determine the conditions under which a focal
-male increases its fitness by searching for a nuptial gift
+male increases his fitness by searching for a nuptial gift
 (\(T_{\mathrm{m}}>0\)) in a population of resident males that do not
-search (\(T_{\mathrm{m}}=0\)). Females are assumed to exhibit no choice
-in males with versus without nuptial gifts. Under such conditions, male
-fitness cannot be affected by female choice, so selection to increase
-\(T_{\mathrm{m}}>0\) must be based solely on \(\alpha\), \(\beta\),
-\(R\), and \(\gamma\).
+search (\(T_{\mathrm{m}}=0\)). Females are assumed to exhibit no
+choosiness for males with versus without nuptial gifts. Under such
+conditions, male fitness cannot be affected by female choice, so
+selection to increase \(T_{\mathrm{m}}>0\) must be based solely on
+\(\alpha\), \(\beta\), \(R\), and \(\gamma\).
 
@@
 setting \(\partial W_{\mathrm{m}}/\partial T_{\mathrm{m}} = 0\) and
-solving for \(\gamma\) to get Eq. 2 in the main text.
+solving for \(\gamma\) to recover Eq. 2 from the main text,
+
+\[0 = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)} - \lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}},\]
+
+\[\lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}} = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)},\]
+
+\[\frac{R}{{\left(1 + \beta \right)^{2}}} =  \frac{\gamma}{\alpha\left(\beta+1\right)},\]
+
+\[\frac{R}{{\left(1 + \beta \right)}} =  \frac{\gamma}{\alpha},\]
+
+\[\gamma = \alpha \frac{R }{\beta + 1}.\]
 
@@
 
-\hypertarget{s4-operational-sex-ratio}{%
-\subsection{S4: Operational sex ratio}\label{s4-operational-sex-ratio}}
+\hypertarget{s2-operational-sex-ratio}{%
+\subsection{S2: Operational sex ratio}\label{s2-operational-sex-ratio}}
 
@@
 
-\hypertarget{s5-estimation-of-key-model-parameters-using-experimental-data}{%
-\subsection{S5: Estimation of key model parameters using experimental
-data}\label{s5-estimation-of-key-model-parameters-using-experimental-data}}
+\hypertarget{s3-sensitivity-analysis-of-parameters-in-ibm}{%
+\subsection{S3: Sensitivity analysis of parameters in
+IBM}\label{s3-sensitivity-analysis-of-parameters-in-ibm}}
 
-Estimates showing the mean number of offspring produced by female
-\emph{Pisaura mirabilis} that ate nuptial gifts and females who did not.
-Means were calculated with raw data from Tuni \emph{et al.}
-(\protect\hyperlink{ref-Tuni2013a}{2013}) and results are shown \(\pm\)
-SE (Table 1). Under these assumptions, the relative gain in fitness from
-receiving nuptial gifts for a female is,
+We investigated the sensitivity of our results to individual mortality
+during time-in (\(\mu_{\mathrm{in}}\)) and time-out
+(\(\mu_{\mathrm{out}}\)), female processing time (\(T_{\mathrm{f}}\)),
+and the potential for interactions between conspecifics (\(\psi\)).
+Across all of these simulations, there were challenges with statistical
+power. Evidence for the evolution of male search (blue points in
+figures) and female choosiness (red points in figures) was determined by
+the lower 95\% bootstrapped confidence interval of \(T_{\mathrm{m}}\)
+and \(T_{\mathrm{f}}\) values being greater than zero, respectively.
+This required a lot of replicate simulations in the main text (Figure
+3), especially for values just above predicted thresholds and for female
+choosiness. Computation time was a limiting factor, even using a
+compiled language (C) and with access to a computing cluster. Absence of
+points above threshold values are not necessarily evidence that
+evolution of male search or female choosiness is not predicted to evolve
+in these regions of parameter space, but it does indicate that evolution
+of these traits is not necessarily assured given the stochasticity
+inherent to the IBM. Additional simulations can be conducted using the C
+code in the `src' folder of the GitHub repository
+(\url{https://github.com/bradduthie/nuptial_gift_evolution}). Below, we
+explain the parameter values used in the sensitivity analysis in more
+detail.
 
-\[\hat{\delta_\mathrm{f}} = \frac{25.74}{6.00} = 4.29\]
+\emph{Mortality}
 
-Since the baseline fitness is 1, the increase in fitness resulting from
-a nuptial gift then becomes,
+We conducted a sensitivity analysis of the effect of the mortality
+parameters \(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\) (the
+probability of mortality in time-in and time-out, respectively, which we
+assumed to be equal for all individuals) on the evolution of male search
+and female choice using the IBM. The results revealed no correlation
+between the value of the mortality parameters and the evolution of male
+search or female choice (Fig. S2.1).
 
-\[\hat{\gamma} = \hat{\delta_{\mathrm{f}}} - 1 = 3.29.\]
+\emph{Female processing time}
 
-The value 3.29 was used to parameterise \(\gamma\) for a set of
-simulations (Figure 4 in the main text).
+We also conducted a sensitivity analysis of female processing time
+\(T_{\mathrm{f}}\). To do this, we ran simulations at default values,
+but with \(T_{\mathrm{f}} = 10.0\) (Figures S2.2).
 
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4024}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2805}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3171}}@{}}
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Received nuptial gift
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Received no nuptial gift
-\end{minipage} \\
-\midrule
-\endhead
-Expected number of hatched eggs & \(25.74 \pm 0.96\) &
-\(6.00 \pm 2.1\) \\
-\bottomrule
-\end{longtable}
+\emph{Interactions between conspecifics}
 
-Table 1: Estimates showing mean number of offspring produced by female
-\emph{P. mirabilis} that ate nuptial gifts and females who did not.
-Means were calculated with raw data from Tuni \emph{et al.}
-(\protect\hyperlink{ref-Tuni2013a}{2013}) and results are shown \(\pm\)
-SE.
+We conducted a sensitivity analysis on the encounter rate between
+conspecifics (\(R\)) by varying the value of our scaling parameter
+\(\psi\). Under default simulations, \(\psi = 3\). We also ran
+simulations in which \(\psi = 1\) (Figure S2.3), \(\psi = 2\) (Figure
+S3.4), \(\psi = 4\) (Figure S3.5), and \(\psi = 6\) (Figure S3.6), with
+all other parameters being set to default values.
 
 \clearpage
-
-\hypertarget{s6-separate-evolution-of-male-search-and-female-choice}{%
-\subsection{S6: Separate evolution of male search and female
-choice}\label{s6-separate-evolution-of-male-search-and-female-choice}}
-
-We used the individual-based simulation model (see Supporting
-Information S1) to unpack the effect of coevolution on the evolution of
-male search and female choice. Here we replicated the simulations shown
-in the main text under the condition where only one trait at a time was
-allowed to evolve and studied how this affected the trait evolution.
-
-First, we submitted a set of simulations wherein male search did not
-evolve, but was fixed at different values (see Fig. S6.1). Next, we ran
-the same set of simulations wherein male search evolved, but female
-choice was not possible. The results thus show how each trait evolves in
-the absence of any coevolution (Fig. S6.1).
 
@@
 \centering
-\includegraphics{SI_files/figure-latex/unnamed-chunk-12-1.pdf}
-\caption{Figure S6.1: The separate evolution of male search and female
+\includegraphics{SI_files/figure-latex/unnamed-chunk-3-1.pdf}
+\caption{Figure S2.1: Evolution of both male search (blue) and female
+choice (red) under different combinations of the mortality rates
+\(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\) (mortality in time-in
+and out, respectively). The y-axis is the threshold fitness that leads
+to evolution of male search (blue) or female choice (red). The results
+show noise, but no correlation between the value of the mortality
+parameters and the propensity for male search and/or female choice to
+evolve. For each of the \(25 \times 20\) combinations of
+\(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\), 1600 replicate
+simulations were run.}
+\end{figure}
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+\begin{figure}
+\centering
+\includegraphics{SI_files/figure-latex/unnamed-chunk-4-1.pdf}
+\caption{Figure S2.3 (\(T_{\mathrm{f}} = 10.0\)): The coevolution of
+male search and female choosiness as a function of nuptial gift search
+time (\(\alpha\)). Points show where the lower 95\% confidence interval
+of female choosiness (red) and male search (blue) exceeds zero,
+indicating evolution of choosiness or nuptial gift search. Each point
+includes data from 3000 replicate simulations with identical starting
+conditions. Up to 3000 interactions occur between individuals in each
+time step (\(\psi = 3\)), potentially resulting in a mating interaction.
+The number of individuals in the population remained at or near carrying
+capacity of \(K = 1000\). Expected female processing time was set to
+\(T_{\mathrm{f}}=10.0\) time steps, and \(\gamma\) and \(\alpha\) values
+in the range {[}0.1, 2.0{]} and {[}0.0, 2.0{]}, respectively, were
+used.}
+\end{figure}
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+\begin{figure}
+\centering
+\includegraphics{SI_files/figure-latex/unnamed-chunk-5-1.pdf}
+\caption{Figure S2.4 (\(\psi = 1\)): The coevolution of male search and
+female choosiness as a function of nuptial gift search time
+(\(\alpha\)). Points show where the lower 95\% confidence interval of
+where male search (blue) exceeds zero, indicating evolution of
+choosiness or nuptial gift search. Each point includes data from 3000
+replicate simulations with identical starting conditions. Up to 1000
+interactions occur between individuals in each time step (\(\psi = 1\)),
+potentially resulting in a mating interaction. The number of individuals
+in the population remained at or near carrying capacity of \(K = 1000\).
+Expected female processing time was set to \(T_{\mathrm{f}}=2\) time
+steps, and \(\gamma\) and \(\alpha\) values in the range {[}0.0, 2.0{]}
+and {[}0.1, 2.0{]}, respectively, were used.}
+\end{figure}
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+\begin{figure}
+\centering
+\includegraphics{SI_files/figure-latex/unnamed-chunk-6-1.pdf}
+\caption{Figure S2.5 (\(\psi = 2\)): The coevolution of male search and
+female choosiness as a function of nuptial gift search time
+(\(\alpha\)). Points show where the lower 95\% confidence interval of
+where male search (blue) exceeds zero, indicating evolution of
+choosiness or nuptial gift search. Each point includes data from 3000
+replicate simulations with identical starting conditions. Up to 2000
+interactions occur between individuals in each time step (\(\psi = 2\)),
+potentially resulting in a mating interaction. The number of individuals
+in the population remained at or near carrying capacity of \(K = 1000\).
+Expected female processing time was set to \(T_{\mathrm{f}}=2\) time
+steps, and \(\gamma\) and \(\alpha\) values in the range {[}0.0, 2.0{]}
+and {[}0.1, 2.0{]}, respectively, were used.}
+\end{figure}
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+\begin{figure}
+\centering
+\includegraphics{SI_files/figure-latex/unnamed-chunk-7-1.pdf}
+\caption{Figure S2.6 (\(\psi = 4\)): The coevolution of male search and
+female choosiness as a function of nuptial gift search time
+(\(\alpha\)). Points show where the lower 95\% confidence interval of
+where male search (blue) exceeds zero, indicating evolution of
+choosiness or nuptial gift search. Each point includes data from 3000
+replicate simulations with identical starting conditions. Up to 4000
+interactions occur between individuals in each time step, potentially
+resulting in a mating interaction (\(\psi = 4\)). The number of
+individuals in the population remained at or near carrying capacity of
+\(K = 1000\). Expected female processing time was set to
+\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
+the range {[}0.0, 2.0{]} and {[}0.1, 2.0{]}, respectively, were used.}
+\end{figure}
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+\begin{figure}
+\centering
+\includegraphics{SI_files/figure-latex/unnamed-chunk-8-1.pdf}
+\caption{Figure S2.7 (\(\psi = 6\)): The coevolution of male search and
+female choosiness as a function of nuptial gift search time
+(\(\alpha\)). Points show where the lower 95\% confidence interval of
+where male search (blue) exceeds zero, indicating evolution of
+choosiness or nuptial gift search. Each point includes data from 3000
+replicate simulations with identical starting conditions. Up to 6000
+interactions occur between individuals in each time step, potentially
+resulting in a mating interaction (\(\psi = 6\)). The number of
+individuals in the population remained at or near carrying capacity of
+\(K = 1000\). Expected female processing time was set to
+\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
+the range {[}0.0, 2.0{]} and {[}0.1, 2.0{]}, respectively, were used.}
+\end{figure}
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\hypertarget{s4-separate-evolution-of-male-search-and-female-choice}{%
+\subsection{S4: Separate evolution of male search and female
+choice}\label{s4-separate-evolution-of-male-search-and-female-choice}}
+
+We used the individual-based simulation model to unpack the effect of
+coevolution on the evolution of male search and female choice. Here we
+replicated the simulations shown in the main text under the condition
+where only one trait at a time was allowed to evolve and studied how
+this affected the trait evolution.
+
+First, we submitted a set of simulations wherein male search did not
+evolve, but was fixed at different values. Next, we ran the same set of
+simulations wherein male search evolved, but female choice was not
+possible. The results thus show how each trait evolves in the absence of
+any coevolution (Fig. S4.1).
+
+\captionsetup{labelformat=empty}
+
+\begin{figure}
+\centering
+\includegraphics{SI_files/figure-latex/unnamed-chunk-9-1.pdf}
+\caption{Figure S4.1: The separate evolution of male search and female
 choosiness as a function of nuptial gift search time. Points show where
@@
 choosiness (red) exceeds zero, indicating evolution of nuptial gift
-search or choosiness. Each point includes data from \(2 \times 1600\)
+search or choosiness. Each point includes data from \(2 \times 3000\)
 replicate simulations with identical starting conditions. In the first
@@
 female choice. The parameters \(T_{\mathrm{f}}=2\), and \(\gamma\) and
-\(\alpha\) values were set within the range {[}0.1, 2.0{]} and {[}0.3,
-1.7{]}, respectively.}
+\(\alpha\) values were set within the range {[}0.1, 2.0{]} and {[}0.0,
+2.0{]}, respectively.}
 \end{figure}
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Tuni2013a}{}}%
-Tuni, C., Albo, M.J. \& Bilde, T. (2013)
-\href{https://doi.org/10.1111/jeb.12137}{{Polyandrous females acquire
-indirect benefits in a nuptial feeding species}}. \emph{Journal of
-Evolutionary Biology}, \textbf{26}, 1307--1316.
-
 \end{CSLReferences}

### 2024-11-29 index.Rmd
Fixed up traits and manuscript. Traits are not binary anymore, but are diploid

--- 2024-06-15 ms_biorxiv.Rmd
@@
 Selection will favour choosiness in the opposite sex if the value of a nuptial gift exceeds the inverse of the time taken to produce offspring multiplied by the rate at which mates with nuptial gifts are encountered.
-Importantly, selection can differ between the sexes, potentially causing sexual conflict. 
-We test these results using an individual-based model applied to a system of nuptial gift-giving spiders, *Pisaura mirabilis*, by estimating parameter values using experimental data from several studies.
+Selection can differ between the sexes, potentially causing sexual conflict. 
+We further investigate these results using an individual-based model inspired by a system of nuptial gift-giving spiders, *Pisaura mirabilis*, by estimating the fitness benefit of nuptial gift-giving using experimental data from several studies.
 Our results provide a general framework for understanding when the evolution of nuptial gift-giving can occur and provide novel insight into the evolution of worthless nuptial gifts, occurring in multiple taxonomic groups with implications for understanding parental investment.
@@
 Despite the ubiquity of this behaviour, little effort has been made to conceptualise the evolution of nuptial gift-giving within a general modelling framework [@Lewis2014; @Iwasa2022]. 
-Recent models describing the evolution of nuptial gift-giving have focused on co-evolution between male nuptial gift-giving and female propensity to remate, and evolutionarily stable nuptial gift sizes [@Iwasa2022; @Kamimura2021], but a general framework describing the conditions necessary for nuptial gift-giving to be initially favoured by selection is needed to understand when gift-giving should evolve.
-
-Nuptial gift-giving may allow males to increase fitness by acquiring additional mates, indirect benefits (by increasing the fitness of offspring), prolonged copulations, and success in sperm competition [@Lewis2014; @Albo2013; @Ghislandi2014].
+Recent models describing the evolution of nuptial gift-giving have focused on co-evolution between male nuptial gift-giving and female propensity to remate, and evolutionarily stable nuptial gift sizes [@Iwasa2022; @Kamimura2021], but a general framework describing the conditions under which nuptial gift-giving can be initially favoured by selection is needed to understand when gift-giving should evolve.
+
+Nuptial gift-giving may allow males to increase fitness by acquiring additional mates, indirect benefits (by increasing offspring fitness), prolonged copulations, and success in sperm competition [@Lewis2014; @Albo2013; @Ghislandi2014].
 However, this potential fitness increase comes at the expense of producing a nuptial gift, which may be costly in terms of time and resources. 
@@
 With respect to nuptial gift-giving, the evolutionary interests of both sexes may not always fully overlap. 
-This can cause sexual conflict, which is a difference in the evolutionary interest between sexes that occurs when interaction between sexes results in a situation where neither sex can achieve an optimal outcome [@Parker2006].
-That is, under some conditions, it might for example be optimal for males but not females to mate if females do not benefit from mating with males without nuptial gifts.
+This can cause sexual conflict, which is a difference in the fitness interests between sexes that occurs when an interaction results in a situation where individuals cannot both achieve an optimal outcome [@Parker2006].
+For example, under some conditions, it might be optimal for males but not females to mate if females do not benefit from mating with males without nuptial gifts.
 
 Much work has sought to explain how gift-giving tactics are maintained, with explanations including condition-dependent strategies, gift-giving as a way to decrease female aggression during copulation, or gifts as sensory traps [@Albo2019; @Lubin2007; @Ghislandi2018; @Toft2016].
-An example of such a system is the nuptial gift-giving nursery-web spider *Pisaura mirabilis* where males may court females with or without nuptial gifts [@Bristowe1926; @Tuni2013a]. 
+An example of such a system is the nuptial gift-giving nursery-web spider *Pisaura mirabilis*, where males may court females with or without nuptial gifts [@Bristowe1926; @Tuni2013a]. 
 Here, males may provide females with costly nuptial gifts in the form of captured arthropod prey, and females may exhibit preference for males with a nuptial gift by rejecting males without a nuptial gift [@Albo2013].
@@
 Our model demonstrates the importance of nuptial gift cost, sex ratio, and mate encounter rate in determining the threshold above which selection will favour the evolution of nuptial gift-giving.
-Importantly, we show that the threshold value differs for males and females. 
-We test predictions of our analytical model by formulating an individual-based model, which further supports the main theoretical results of our analytical model. 
-Further, we apply our model to an example system with nuptial gifts, the nursery web spider *Pisaura mirabilis*, where we use experimental data to estimate a key model parameter. 
+Importantly, we show that the threshold value differs for male searching and female choosiness. 
+We complement the predictions of our analytical model by formulating an individual-based model, which further supports the main theoretical results. 
+We apply our model to an example system with nuptial gifts, the nursery web spider *Pisaura mirabilis*, where we use experimental data to estimate a key model parameter. 
 Our results provide a general framework for understanding why nuptial gift-giving evolves in some systems and not in others, how the evolution of nuptial gift-giving can give rise to sexual conflict, and it provides insight into the evolution of worthless and deceitful nuptial gifts, which occur in several different taxonomic [@Ghislandi2014; @LeBas2005].
 
-Results
+Model
 ================================================================================
-
-Analytical model
---------------------------------------------------------------------------------
 
@@
 We define the number of offspring produced by a female per reproductive cycle as $\lambda$.
-Since females enter time-out after mating, this assumption is equivalent to assuming a system with sequential polyandry.
-For simplicity, we assume male time to replenish sperm is negligible, but males can spend some duration of time ($T_{\mathrm{m}}$) out of the mating pool searching for nuptial gifts.
+Since females enter time-out after mating, this is equivalent to assuming a system with sequential polyandry.
+For simplicity, we assume male time to replenish sperm is negligible, but males can spend some duration of time out of the mating pool searching for nuptial gifts.
+We define $T_{\mathrm{m}}$ as the time until a gift is found by a searching male.
 
@@
 
-Criteria for male search and female choosiness
---------------------------------------------------------------------------------
-
-The probability $G$ that a male succeeds in securing a nuptial gift is defined by,
-
-<!--
-
-$$G = 1 - e^{-\frac{1}{\alpha}T_{m}}.$$
---->
-
-\begin{equation}
-G = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.
-\end{equation}
-
-In Eq. 1, $\alpha$ defines the expected search time before encountering a nuptial gift.
-Thus, the probability of finding a nuptial gift is higher the more time $T_{\mathrm{m}}$ is spent searching. 
+Analytical model
+-------------------------------------------------------------------------------
+
+The probability that a male succeeds in securing a nuptial gift ($G$) after a duration of $T_{\mathrm{m}}$ is defined by,
+
+$$P(G) = 1 - e^{-\frac{1}{\alpha}T_{m}}.
+\tag{1}
+$$
+
+In Eq. 1, $\alpha$ defines expected search time before encountering a nuptial gift.
+Thus, the probability of finding a nuptial gift is higher the more time is spent searching. 
 During time-in, individuals encounter conspecifics at a rate of $R$.
@@
 An example of how the structure of the time-in time-out model applies to a system with nuptial gift-giving is given in Figure 1.
-We assume that mating with a nuptial gift increases the fitness of each offspring by an increment of $\gamma$.
-We proceed to find the thresholds $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$ above which males and females are favoured by selection to search for mates with nuptial gifts and exhibit choosiness for nuptial gifts, respectively.
-We show (see Methods) that the initial threshold value of $\gamma$ ($\gamma_{\mathrm{m}}$) necessary for males to increase their fitness by investing time searching for a nuptial gift (time that could otherwise be spent searching for a mate) is,
+We assume that mating with a nuptial gift increases expected offspring production by an increment of $\gamma$.
+Mortality occurs for females and males in ($\mu_{\mathrm{i,f}}$, $\mu_{\mathrm{i,m}}$) and out ($\mu_{\mathrm{o,f}}$, $\mu_{\mathrm{o,m}}$) of the mating pool. 
+Following @Kokko2006, we assume $m_{\mathrm{i,f}} = m_{\mathrm{o,f}} = 1$ and $m_{\mathrm{i,m}} = m_{\mathrm{o,m}} = 1$.
+
+First, we find the fitness of males that search versus do not search for a nuptial gift. 
+We then describe the fitness consequences of female choice to accept or reject males based on their provision of a nuptial gift.
+We can then calculate the thresholds $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$ above which males and females are favoured by selection to search for nuptial gifts and exhibit choosiness for nuptial gifts, respectively.
+
+*Male fitness*
+
+During time-out, males can search for a nuptial gift.
+Males can adopt one of two strategies; either search or do not search for a nuptial gift. 
+Males with the searching strategy continue to search until they find a nuptial gift, while males that do not search immediately re-enter the mating pool. 
+Consequently, time searching for a nuptial gift will come at the cost of mating opportunities but might increase offspring fitness. 
+We therefore need to model the expected length of time spent outside of the mating pool for males that search for nuptial gifts ($E[T_{\mathrm{m}}]$), which equals $\alpha$. 
+We can integrate search time $t$ over the rate at which nuptial gifts are encountered ($\exp(-1/\alpha)$) to show $E[T_{\mathrm{m}}] = \alpha$,
+
+$$E[T_{\mathrm{m}}] = \int_{0}^{\infty}e^{- \frac{1}{\alpha}t}dt = \alpha.$$
+
+The rate at which a focal male that searches for a nuptial gift increases his fitness is therefore his reproductive output $\lambda(1 + \gamma)$ divided by expected time spent searching for a nuptial gift ($\alpha$) plus time spent in the mating pool, $(\beta + 1)/R$,
+
+$$W_{\mathrm{M_{G}}} = \lambda \frac{1 + \gamma}{\alpha + \left( \frac{\beta + 1}{R} \right)}.$$
+
+In contrast, a male that does not search for a nuptial gift has fewer offspring, but spends less time outside of the mating pool,
+
+$$W_{\mathrm{M_{L}}} = \lambda \frac{1}{\left(\frac{\beta+1}{R} \right)} = \lambda \frac{R}{\beta + 1}.$$
+
+We can determine the conditions for which $W_{\mathrm{M_{G}}} > W_{\mathrm{M_{L}}}$, isolating $\gamma$ to find how large of a fitness benefit must be provided by the nuptial gift to make the search cost worthwhile, which simplifies to,
+
+$$\gamma_{\mathrm{m}} > \alpha \frac{R}{\beta + 1}.
+\tag{2}
+$$
+
+When this inequality holds, males are favoured to search until they find a nuptial gift, which would result in an average search time of $\alpha$. 
+If the male trait is instead continuous (i.e., males search for time period $T_{\mathrm{m}}$), it can be shown that the same threshold can be reached by evaluating the partial derivative of the male fitness function (Supporting Information S1).
+Hence, the thresholds are consistent under different assumptions concerning male searching strategy.
+Selection will cause males to search for nuptial gifts if the fitness increase to offspring exceeds the product of search time and female encounter rate.
+
+*Female fitness*
+
+During time-out, females process offspring over a duration of $T_{\mathrm{f}}$ (we assume that $T_{\mathrm{f}} > \alpha$, else females are not the choosy sex). 
+When females re-enter the mating pool, they encounter males at a rate of $R\beta/(\beta + 1)$. 
+If a female encounters a male with a nuptial gift, we assume that she will mate with him. 
+But if a female encounters a male with no nuptial gift, then she might accept or reject the male. 
+If she rejects the male, then she will remain in the mating pool. 
+The rate at which a female encounters a male with a nuptial gift is,
+
+$$R_{\mathrm{F_{G}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right).$$
+
+Expected time spent in the mating pool before a focal female encounters a male with a gift will be $1/R_{\mathrm{F_{G}}}$.
+The rate at which a female increases her fitness by being choosy and mating only when she encounters a male with a gift is,
+
+$$W_{f, g} = \lambda \frac{1 + \gamma}{T_{F} + \frac{1}{R_{\mathrm{F,G}}}}.
+\tag{4}
+$$
+
+The top of the right-hand side of Eq. 4 gives her fitness increase, and the bottom gives the total time it takes to obtain this fitness. 
+The $R_{\mathrm{F_{G}}}$ is inverted because it represents the expected time to encountering a male with a gift. 
+We can expand Eq. 6,
+
+$$W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right)}}.$$
+
+If the focal female is not choosy and accepts the first male that she encounters, then the rate at which she increases her fitness is,
+
+$$W_{\mathrm{F_{G,L}}} = \lambda \frac{\left(1 + \gamma\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)}}.$$
+
+We then evaluate the conditions under which $W_{\mathrm{F_{G}}} > W_{\mathrm{F_{G,L}}}$. 
+We can isolate $\gamma$ to determine how much offspring fitness must be increased to make choosiness beneficial ($\gamma_{\mathrm{f}}$),
+
+$$\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}} R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right)}.
+\tag{5}
+$$
+
+Note that that the expression $R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right)$ defines the rate at which a female in the mating pool encounters males with nuptial gifts.
+Hence, female choosiness is ultimately determined by time spent out of the mating pool to process offspring ($T_{\mathrm{f}}$) and the rate at which a female in the mating pool encounters males with nuptial gifts.
+
+*Operational sex ratio*
+
+We assume that the sex ratio is equal upon maturation. 
+Given this, @Kokko2001 show that the operational sex ratio depends on the probability of finding an individual in time-in,
+
+$$\beta = \frac{\int_{t = 0}^{\infty} P_{IM}(t)dt}{\int_{t = 0}^{\infty} P_{IF}(t)dt}.
+\tag{6}
+$$
+
+In Eq. 6, $P_{IM}(t)$ and $P_{IF}(t)$ are the probabilities of finding a male and female in time-in, respectively. 
+There is no closed form solution to the operational sex ratio, so we used recursion to calculate $\beta$ values for a given $T_{\mathrm{f}}$, $T_{\mathrm{m}}$, and $R$ (see Supporting Information S2),
+
+Individual-based model
+------------------------------------------
+
+We formulate an individual-based time-in time-out simulation model to complement the predictions made by our analytical time-in time-out model above and further allow for coevolution between male search behaviour and female choosiness.
+Here we describe the details of initialisation, time-in (mating), time-out (reproduction and nuptial gift search), and mortality. 
+We then summarise the simulations run and data collected.
+
+*Initialisation*
+
+Before the first time step, a population of $N = 1000$ individuals is initialised. 
+Individuals are assigned to be female with a probability of $0.5$, else male. 
+Female offspring processing time for a focal individual $i$ is fixed at $T^{i}_{\mathrm{f}} = 2$.
+Each individual is initialised with a diploid genotype that underlies female rejection probability of gift-less males ($\rho^{i}$), and a diploid genotype that underlies male search time ($T^{i}_{\mathrm{m}}$).
+Alleles can take any real value and combine additively to determine $\rho^{i}$ and $T^{i}_{\mathrm{m}}$.
+For all simulations, initialised values are set to , $\rho^{i} = 0$, and $T^{i}_{\mathrm{m}} = 0$. 
+All individuals are initialised outside of the mating pool in the first time step $t = 1$. 
+The first time step then proceeds with females immediately entering the mating pool and males either entering the mating pool or searching for nuptial gifts.
+
+*Time-in*
+
+At the start of each time step, females and males in the mating pool remain in it. 
+Females outside the mating pool enter the mating pool after processing offspring, and males enter it after searching for nuptial gifts (see 'Time-out' below). 
+Up to $\Psi = N\psi$ interactions between individuals can occur in a single time step, where $\psi$ is a scaling parameter. 
+In each time step, $\Psi$ pairs of individuals are selected at random to interact.
+For each interaction, two different individuals are randomly selected from the population with equal probability.
+If the selected individuals are of different sexes, and both are in the mating pool, then a mating encounter occurs.
+If the male does not have a nuptial gift, then a focal female $i$ will reject him with a probability of $\rho^{i}$; if rejection occurs, then both individuals stay in the mating pool. 
+If rejection does not occur, or the male has a nuptial gift in the mating encounter, then the individuals mate. 
+Females then leave the mating pool and enter time-out to process offspring, and males leave and enter time-out to potentially search for new nuptial gifts (note that females and males might re-enter the mating pool immediately within the same time step given sufficiently low search time; see Time-out below).
+
+*Time-out*
+
+During time-out, offspring production and time outside of the mating pool are realised for each female by sampling from a Poisson distribution.
+A focal female $i$ will produce $\mathrm{Poisson}(\lambda)$ offspring if no nuptial gift was provided or $\mathrm{Poisson}(\lambda + \gamma)$ if a gift was provided. 
+Females remain outside of the mating pool to process offspring for $\mathrm{Poisson}(T^{i}_{\mathrm{f}})$ time steps. 
+Offspring are added to the population immediately, with one $\rho^{i}$ and one $T^{i}_{\mathrm{m}}$ allele sampled from each parent with complete recombination.
+Mutation occurs independently for each allele with a probability of $\epsilon = 0.001$, and if mutation occurs, then a new allele value is sampled from a normal distribution mean centred on the existing value with a standard deviation of $\sigma_{\epsilon} = 0.1$.
+Offspring sex is randomly assigned with equal probability as female or male. 
+Female offspring are immediately placed in the mating pool, and male offspring are out of the mating pool to potentially search for nuptial gifts. 
+After a female has spent $\mathrm{Poisson}(T^{i}_{\mathrm{f}})$ time steps outside the mating pool, she will re-enter it.
+
+A focal male $i$ outside the mating pool will enter it if he has searched for a fixed number of $T^{i}_{\mathrm{m}}$ time steps, which is also sampled randomly from a Poisson distribution, $\mathrm{Poisson}(T^{i}_{\mathrm{m}})$.
+If $T^{i}_{\mathrm{m}} = 0$, then the male immediately returns to the mating pool (in the same time step). 
+If $T^{i}_{\mathrm{m}} > 0$, then the male must wait outside the mating pool for $\mathrm{Poisson}(T^{i}_{\mathrm{m}})$ time steps, but will enter the mating pool with a nuptial gift with a probability,
+
+$$P(G^{i}) = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.$$
+
+Males must always spend $\mathrm{Poisson}(T^{i}_{\mathrm{m}})$ time steps outside of the mating pool regardless of whether or not they are successful in obtaining a nuptial gift.
+
+*Mortality*
+
+At the end of each time step, mortality occurs first with a fixed probability for all adults in the population, then with a probability caused by carrying capacity $K = 1000$ applied to all individuals (adults and offspring).
+Mortality occurs in each time step with a fixed probability of $\mu$ regardless of the sex of the individual or its position in or out of the mating pool. 
+If after this fixed mortality is applied, the total population size $N > K$, then individuals are removed at random with equal probability until $N = K$. 
+Following adult mortality, a new time step begins with newly added offspring becoming adults.
+
+*Simulations*
+
+We ran simulations in which male search time and female choosiness evolved from an ancestral state of no searching and no choosiness. 
+In all simulations, $N$ was initialised at 1000 and $K = 1000$. 
+Simulations ran for $t_{max} = 10000$ time steps. 
+We set $T_{\mathrm{f}} = 2$, $\psi = 3$, and $\lambda = 1$ for all simulations, and we simulated across a range of $\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}$ and $\gamma = \{0, 0.1, ..., 1.9, 2.0\}$ parameter values for 3000 replicates.
+Summary statistics for mean trait values, population size, sex ratios, proportion of females and males in and out of the mating pool, and mean number of encounters per female and male within the mating pool were all calculated in the last time step.
+The C code used for simulating these IBMs also allows for the reporting of summary statistics in each time step. 
+Additionally, it can simulate explicit space and individual movement through the landscape. 
+A neutral evolving trait was also modelled to ensure that the code functioned as intended, and processes were compartmentalised into individual functions to facilitate code testing. 
+All code is publicly available on GitHub (https://github.com/bradduthie/nuptial_gift_evolution).
 
@@
 
-$$\gamma_{m} > \alpha \frac{M}{\sqrt{\beta}}.$$
+A set of simulations with a value of $\gamma$ calculated from empirical data was also conducted (100 replicates). 
+Here, $\gamma$ was parameterised using data on egg production as a function of eating nuptial gifts (see below). 
+Additional simulation sets with lower and upper bounds of the estimated $\gamma$ were subsequently run. 
+In the simulation sets with experimentally derived parameter values, all other parameters were identical to previous simulation batches.
+
 --->
 
-\begin{equation}
-\gamma_{\mathrm{m}} > \alpha \frac{R}{\beta + 1}.
-\end{equation}
-
-Inequality 2 means that if nuptial gifts are not abundant and thus require a long time to find (i.e., high $\alpha$), or if males encounter many females per unit time (i.e., high $R / (1+\beta)$), then the nuptial gift must result in a high fitness increment for selection to favour gift-searching.
-In general, when ineq. 2 is satisfied, we predict selection to favour the evolution of nuptial gift-giving.
-
-We can similarly predict the conditions for which there is selection for female choosiness. 
-If $\gamma$ is sufficiently high, then females increase their fitness by rejecting males without gifts and mating only with males that provide nuptial gifts. 
-To illustrate, we assume that all males in a population search for a duration of $T_{\mathrm{m}}$, in which case the threshold fitness increment for females ($\gamma_{\mathrm{f}}$) is,
-
-<!---
-
-$$\gamma_{f} > \frac{1}{T_{f} M \sqrt{\beta} \left(1 - e^{-\frac{1}{\alpha}T_{m}} \right)}.$$
-
---->
-
-\begin{equation}
-\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}} R \left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}} \right)}.
-\end{equation}
-
-Inequality 3 shows that as offspring processing time ($T_{\mathrm{f}}$), mate encounter rate ($R\beta / (\beta + 1)$), or the probability of a male finding a nuptial gift ($1 - \exp(-T_{\mathrm{m}}/\alpha)$ ) decreases, the threshold value of fitness above which selection will favour choosiness ($\gamma_{\mathrm{f}}$) increases.
-This can be understood intuitively by realising that rejecting a prospective male represents an opportunity cost for the female. 
-This opportunity cost becomes small if many males with gifts are encountered, hence the appearance of the rate at which males with gifts are encountered in the denominator.
-Figure 2 shows how $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$ change with increasing $\alpha$. 
-For $\gamma_{\mathrm{f}}$, we assume that males search for the expected time required to obtain a nuptial gift ($T_{\mathrm{m}} = \alpha$). 
-Note that $\beta$ does not have a closed form solution given $R$, $T_{\mathrm{f}}$, and $T_{\mathrm{m}}$, so $\beta$ was calculated using recursion (see Methods).
+*Application to gift-giving spiders*
+
+We can produce an estimate of the fitness increment obtained by females when receiving a gift ($\hat{\gamma}$) by using data on female *P. mirabilis* egg production and hatching success [@Tuni2013a]. 
+@Tuni2013a found differences in egg production and hatching success in female *P. mirabilis* under different feeding regimes. 
+Assuming these differences in feeding regimes correspond to eating versus not eating nuptial gifts, the mean number of offspring produced by a female who eats nuptial gifts can be calculated.
+We calculate these means using raw data from @Tuni2013a and find that mean offspring produced by females receiving nuptial gifts is $25.74 \pm 0.96$, while offspring produced by females without a nuptial gift is $6.00 \pm 2.1$.
+Consequently, the relative gain in fitness from receiving a nuptial gift for a female is estimated to be $\hat{\delta_\mathrm{f}} = 25.74 / 6.00 = 4.29$.
+Since the baseline fitness is 1, the increase in fitness resulting from a nuptial gift then becomes $\hat{\gamma} = \hat{\delta_{\mathrm{f}}} - 1 = 3.29.$
+
+Results
+====================================
+
+Our model predicts 4 zones that are delineated by inequalities 2 and 5 and describe the initial thresholds for the evolution of searching for nuptial gifts in males and choosiness for nuptial gifts in females.
+Figure 2a illustrates conditions under which no searching or choosiness evolves (zone A), only search (zone B) or choosiness (zone C) evolve, or both searching and choosiness evolve (zone D).
+Blue and red threshold lines in Figure 2 are defined by Eq. 2 and Eq. 5, respectively.
+Figure 2b illustrates the expansion of zone B as encounter rate decreases, which is consistent with the results of our IBM (Figure 3).
 
@@
 Parameter space includes areas in which males do not search for nuptial gifts and females are not choosy (A), males search but females are not choosy (B), females would be choosy but males do not search (C), and males search and females are choosy (D).
-Arrows in panel a indicate the effect of increasing interaction rate ($R$), female time-out ($T_{\\mathrm{f}}$), and male search time ($T_{\\mathrm{m}}$).
+Arrows in panel a indicate the effect of increasing encounter rate ($R$), female time-out ($T_{\\mathrm{f}}$), and male search time ($T_{\\mathrm{m}}$).
 As an example, trajectories for $T_{\\mathrm{f}} = 2$, and $T_{\\mathrm{m}} = \\alpha$ are shown for values of $R=2$ (panel a) and $R = 1$ (panel b).
@@
 
-The analytical framework predicts 4 zones, which are delineated by inequalities 2 and 3 and describe the initial thresholds for favouring search of nuptial gifts in males and choosiness for nuptial gifts in females (Figure 2a).
-Consequently, the modelling framework gives a description of the conditions under which nuptial gift-giving is expected to occur (Figure 2a, Zone D) and the conditions under which only selection for male searching (Figure 2a, Zone B) or female choosiness (Figure 2a, Zone C) are predicted.
-These results therefore highlight the potential for sexual conflict over nuptial gift-giving.
-
-Evolution of male search and female choosiness
---------------------------------------------------------------------------------
-
-We used an individual-based model (IBM) to simulate the evolution of nuptial gift-giving and female choosiness from an ancestral condition in which neither exists. 
-The IBM was written to satisfy the assumptions of our analytical time-in and time-out model as much as practical (see Supporting Information S1). 
-Using the IBM, we modelled a spatially-implicit, finite population of females and males. 
-At each time step, some individuals enter or remain within the mating pool (time-in), where they potentially interact and mate. 
-After mating, males and females may leave the mating pool to search for nuptial gifts and to produce offspring, respectively (time-out). 
-Mortality occurs with a fixed probability in each time step, then a ceiling regulation is applied to limit population growth (see Methods).
-
-The rates at which females are encountered by males $R_{\mathrm{f},\mathrm{m}}$ and males with nuptial gifts $R_{\mathrm{m_{G}}, \mathrm{f}}$ are encountered by females are both calculated directly from the IBM, thereby modelling how these rates might be estimated from empirical data, so the male threshold for increasing fitness by searching is,
-
-<!---
-
-$$\gamma_{m, IBM} > \alpha M_{m}.$$
-
---->
-
-\begin{equation}
-\gamma_{\mathrm{m, IBM}} > \alpha R_{\mathrm{f},\mathrm{m}}.
-\end{equation}
-
-Similarly, female threshold for increasing fitness by choosiness is,
-
-<!---
-
-$$\gamma_{f, IBM} > \frac{1}{T_{m}M_{f,G}}.$$
-
---->
-
-\begin{equation}
-\gamma_{\mathrm{f, IBM}} > \frac{1}{T_{\mathrm{f}}R_{\mathrm{m_{G}}, \mathrm{f}}}.
-\end{equation}
-
-Consequently, the IBM and the analytical model differ slightly (e.g., time is discrete in the IBM but continuous the analytical model, and in the IBM, a fitness increment is applied to the focal female in the form of birthrate increase rather than offspring fitness; see Supporting Information S1 for details).
-But the predicted thresholds are theoretically equivalent and yield predictions that are qualitatively the same (Figure 3).
+For males, if nuptial gifts are not abundant and thus require a long time to find (i.e., high $\alpha$), or if males encounter many females per unit time (i.e., high $R / (1+\beta)$), then the nuptial gift must result in a high fitness increment for selection to favour searching.
+For females, if $\gamma$ is sufficiently high, fitness is increased by rejecting males without gifts and mating only with males that provide nuptial gifts. 
+As offspring processing time ($T_{\mathrm{f}}$), mate encounter rate ($R\beta / (\beta + 1)$), or the probability of a male finding a nuptial gift ($1 - \exp(-T_{\mathrm{m}}/\alpha)$ ) decrease, the threshold value of fitness above which selection will favour choosiness ($\gamma_{\mathrm{f}}$) increases.
+This can be understood intuitively by realising that rejecting a prospective male represents an opportunity cost for the female.
 
@@
 Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 3200 replicate simulations with identical starting conditions.
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively (in agreement with Figure 2).
-Minor deviations between the analytical model and the simulation results are expected due to the finite population size, the substantial stochasticity inherent to the simulation model, and the potential for coevolution (for details, see Supporting Information S1).
+Each point includes data from 3000 replicate simulations with identical starting conditions.
+Zones are identified that correspond to areas where males search and females are choosy (D), males search but females are not choosy (B), and males do not search and females are not choosy (A), as also depicted in Figure 2.
 The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
@@
 Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 2.0] and [0.1, 2.0], respectively, were used."}
-SUMM         <- read.csv(file = "inst/summary_coevolving.csv")
+SUMM         <- read.csv(file = "inst/summary_coevolving.csv");
 alpha_vals   <- sort(unique(SUMM[,1]));  
@@
 par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
+plot(x = alpha_vals, y = g_f, type = "n", lwd = 2, cex.lab = 1.25, col = "red",
      xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
@@
 
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
+# points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
 
@@
 }
+points(x = 0.3, y = 1.7, cex = 14, pch = 22, bg = "red", col = "black");
+text(x = 0.3, y = 1.7, labels = "D", cex = 4);
+points(x = 1, y = 1.3, cex = 14, pch = 22, bg = "blue", col = "black");
+text(x = 1, y = 1.3, labels = "B", cex = 4, col = "white");
+points(x = 1.5, y = 0.5, cex = 14, pch = 22, bg = "white", col = "black");
+text(x = 1.5, y = 0.5, labels = "A", cex = 4);
 ```
 
-Male thresholds $\gamma_{\mathrm{m, IBM}}$ given by ineq.
-4 accurately predict the evolution of searching in the IBM across $\alpha$ values, and the female threshold $\gamma_{\mathrm{f, IBM}}$ (ineq.
-5) predicts the evolution of female choice (Figure 3).
+Individual-based model results recover zones A, B, and D (Figure 3). 
 In other words, IBM simulations demonstrate that nuptial gift search in males, and choosiness in females, will evolve from an ancestral state of no searching and no choosiness in similar parameter space (Figure 3) as predicted by the analytical model (Figure 2b).
-We further ran the IBM with realistic values of $\gamma$, estimated using data from the *P. mirabilis* system wherein choosiness among females, and nuptial gift search among males, occur (Figure 4). 
-We found that our IBM predicts both the evolution of choosiness and nuptial gift searching observed in the *P. mirabilis* system.
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "The joint evolution of male search and female choosiness using a nuptial gift fitness increment ($\\gamma$) that was estimated from experimental data for the species *Pisaura mirabilis* (mean $\\gamma = 3.29 \\pm$ SE via propagation of error for estimates of nuptial feeding a non-nuptial feeding groups: [1.47; 8.32]).
-Points show where the 95% confidence interval exceeds 0 for female choosiness (red) and male search (blue).
-Each point includes data from 100 replicate simulations with identical starting conditions.
-The red line shows the threshold above which females should be choosy and the blue line shows the threshold above which males should search.
-As predicted by the analytical model, both male search and female choosiness evolved for a range of $\\gamma$ values around the empirical estimates.
-This occurs because these values result in a $\\gamma$ above the fitness threshold necessary for selection to favour male search of nuptial gifts (blue line) and female choosiness (red line).
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-In each time step, up to 3000 total pair-wise interactions occurred.
-Female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the [0.2, 2.0], respectively, were used.
-The parameter $\\gamma$ was estimated as relative increase in offspring production such that $\\gamma$ is the factor by which fitness increases (relative to the baseline fitness) given a nuptial gift (See Supporting Information S5)."}
-SUME         <- read.csv(file = "inst/summary_empirically_inspired.csv")
-alpha_vals   <- sort(unique(SUME[,1]));  
-TM_vals      <- tapply(X = SUME[,3],  INDEX = SUME[,1], FUN = mean);
-m_vals       <- tapply(X = SUME[,13], INDEX = SUME[,1], FUN = mean);
-beta_vals    <- tapply(X = SUME[,14], INDEX = SUME[,1], FUN = mean);
-Male_M       <- tapply(X = SUME[,15], INDEX = SUME[,1], FUN = mean);
-Female_M     <- tapply(X = SUME[,16], INDEX = SUME[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUME[,17], INDEX = SUME[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUME[,18], INDEX = SUME[,1], FUN = mean);
-
-g_m <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 5.5));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-
-for(i in 1:dim(SUME)[1]){
-  if(SUME[i, 4] > 0 & SUME[i, 5] > 0){
-    points(x = SUME[i, 1], y = SUME[i, 2], cex = 3, pch = 20, col = "blue");
-  }
-}
-
-for(i in 1:dim(SUME)[1]){
-  if(SUME[i, 7] > 0 & SUME[i, 8] > 0){
-    points(x = SUME[i, 1], y = SUME[i, 2], cex = 2, pch = 20, col = "red");
-  }
-}
-```
+Further, although it was not possible to parameterise our model for the  *P.
+mirabilis* system in detail, our calculated value of $\hat{\gamma} = 3.29$ is consistent with the evolution of nuptial gift searching and choosiness recovered by our analytical model and IBM.
 
@@
 We provide a general framework that defines the necessary conditions for selection to favour the evolution of nuptial gift-giving. 
-We show that males should give nuptial gifts if the value of a nuptial gift exceeds a threshold dependent on the encounter rate between males and females and the cost or time necessary to find or produce a nuptial gift (see ineq.
-2).
+We show that males should give nuptial gifts if the value of a nuptial gift exceeds a threshold dependent on the encounter rate between females and males and the cost or time necessary to find or produce a nuptial gift.
 This result makes intuitive sense because if males rarely encounter females, time searching for a gift is a minor cost relative to mate search time. 
@@
 If the search time or cost of finding a nuptial gift is high, nuptial gifts must be very valuable before search is favoured by selection.
+We also show that females should express choosiness for males with nuptial gifts if the value of the nuptial gift exceeds the inverse of the product of offspring processing time and encounter rate with males holding gifts.
 
@@
 
-Importantly, we show that the threshold nuptial gift value at which females are favoured to express choosiness for nuptial gifts is rarely equivalent to the threshold value at which males are favoured to search for nuptial gifts, potentially leading to sexual conflict [@Oliveira2008; @Arnqvist2005a].
+We show that the threshold nuptial gift value at which females are favoured to express choosiness for nuptial gifts is rarely equivalent to the threshold value at which males are favoured to search for nuptial gifts, potentially leading to sexual conflict [@Oliveira2008; @Arnqvist2005a].
 Here, we are defining sexual conflict as occurring when interactions between sexes result in situation where both sexes cannot achieve an optimal outcome simultaneously [@Parker2006].
 As an example, sizable areas of parameter space exists wherein the female optimum would be to exhibit preference for (and receive) nuptial gifts, while the male optimum is to not search for (and give) nuptial gifts (see Figure 2a, Zone C).
-This will lead to mate encounters in which gift-less males will benefit from mating, but females will not.
+This will lead to mate encounters in which gift-less males will benefit from mating, but females will not (i.e., evolutionary interests do not always overlap with respect to mating strategy between the sexes).
 In many systems, ecological variables such as search time required to find a nuptial gift will likely depend on prey abundance,  which can vary substantially with time in some species with nuptial gift-giving [@Ghislandi2018].
@@
 However, it is important to recognise that these thresholds depend on multiple parameters.
-For example, if female processing time ($T_{\mathrm{f}}$) is high, the female threshold for choosiness with respect to $\gamma$ drops such that male search and female choosiness are favoured at lower $\gamma$ (see Supporting Information S2).
+For example, if female processing time ($T_{\mathrm{f}}$) is high, the female threshold for choosiness with respect to $\gamma$ drops such that male search and female choosiness are favoured at lower $\gamma$.
 If $T_{\mathrm{f}}$ is sufficiently high, then an initially rare gift-giving trait might be favoured by selection even if the fitness benefit of a nuptial gift is low.
@@
 We modelled the evolution of nuptial gift-giving using both a mathematical model and an individual-based model.
-Our mathematical model makes simple assumptions about the relationship between nuptial gift search time ($\alpha$), conspecific encounter rate ($R$), female processing time ($T_{\mathrm{f}}$), and the fitness increment of a nuptial gift for offspring fitness ($\gamma$).
+Our mathematical model makes simple assumptions about the relationship between nuptial gift search time ($\alpha$), conspecific encounter rate ($R$), female processing time ($T_{\mathrm{f}}$), and the fitness increment of a nuptial gift for reproductive output ($\gamma$).
 It then derives the threshold $\gamma$ values above which males increase their fitness by searching ($T_{\mathrm{m}} > 0$) for a nuptial gift ($\gamma_{\mathrm{m}}$) and females increase their fitness by choosing to reject males without gifts ($\gamma_{\mathrm{f}}$).
 In contrast, our IBM models individuals over discrete time steps, and key processes of nuptial gift acquisition, conspecific encounters, and female processing are stochastic and varying among individuals.
-The mathematical model and IBM make qualitatively identical predictions (compare Figure 2b versus Figure 3), but differences between the two models inevitably lead to quantitative differences for $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$ thresholds.
+The mathematical model and IBM make qualitatively identical predictions (compare Figure 2b versus Figure 3), but differences between the two models inevitably lead to quantitative differences.
 For example, $\gamma_{\mathrm{f}}$ increased more rapidly with increasing $\alpha$ in the IBM compared to the analytical model.
@@
 
+@Kokko2013 considered the evolution of female choosiness as a function of mating and mortality rates and found that choosiness may generally be a costly trait which is not always expected to evolve. 
+Our results suggest that this is also the case when coevolution with the relevant male trait is taken into account. 
+Numerous studies have modelled mate choice as a function of a single variable or effect [for review, see @Edward2015], such as direct benefits, indirect benefits or so-called chase-away sexual selection [@Holland1998; @Kokko2003].
+Our results describe the evolution of mating choice from a different perspective by taking ecological variables and coevolution into account at the same time.
+
 Other modelling frameworks have made general predictions about sexually selected traits, and these predictions are not mutually exclusive to those made by our model.
@@
 Our model also predicts the possibility of the opposite scenario, in which males provide nuptial gifts, but females do not exhibit preference for nuptial gifts (zone B of Figure 2). 
-Fascinatingly, an example of such system has been documented by a recent study of the genus *Trechaleoides*, which contains two species with true nuptial gift-giving, but a lack of preference for nuptial gifts among female [@Martinez2023].
+Interestingly, an example of such system has been documented by a recent study of the genus *Trechaleoides*, which contains two species with true nuptial gift-giving, but a lack of preference for nuptial gifts among female [@Martinez2023].
 
@@
 
-The simulations parameterised with an experimentally estimated value of $\gamma$ showed evolution of nuptial gift searching in males and choosiness for nuptial gifts in females.
+For experimentally estimated value of $\gamma$, simulations showed evolution of nuptial gift searching in males and choosiness for nuptial gifts in females.
 The model thus predicts that *P.
@@
 
-Our model assumes something akin to sequential polyandry. 
+Our model assumes sequential polyandry. 
 That is, a system wherein female mating and reproduction with multiple males occurs in sequence, rather than multiple matings occurring before reproduction. 
@@
 
-Methods
-================================================================================
-
-Model
---------------------------------------------------------------------------------
-
-Here we first present more detail for the derivation of fitness threshold values $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$.
-We then present IBM simulations (see Supporting Information S1 for full details). 
-Code for simulations is available on GitHub (see "Data availability").
-
-Derivation of fitness thresholds
---------------------------------------------------------------------------------
-
-We use a time-in and time-out model in which females and males spend some time searching for a mate (time-in) followed by a period of cool down outside the mating pool (time-out; Figure 1).
-
-After mating, females must spend some time processing offspring ($T_{\mathrm{f}}$). 
-Male time to replenish sperm is assumed to be negligible, but males can spend time out of the mating pool ($T_{\mathrm{m}}$) to search for a nuptial gift.
-When males return from time-out, they encounter females with some probability that is a function of the rate at which an individual encounters conspecifics ($R$) and the sex ratio ($\beta$; males/females).
-Mortality occurs for females and males in ($\mu_{\mathrm{i,f}}$, $\mu_{\mathrm{i,m}}$) and out ($\mu_{\mathrm{o,f}}$, $\mu_{\mathrm{o,m}}$) of the mating pool. 
-Following @Kokko2006, we assume $m_{\mathrm{i,f}} = m_{\mathrm{o,f}} = 1$ and $m_{\mathrm{i,m}} = m_{\mathrm{o,m}} = 1$. 
-While this choice is arbitrary, we conducted a sensitivity analysis which shows that the mortality parameters have no influence on the propensity for male search and female choice to evolve (Supporting Information S2).
-First, we describe the fitness consequences of male search time for a nuptial gift. 
-We then describe the fitness consequences of female choice to accept or reject males based on their provision of a nuptial gift.
-
-Male fitness
---------------------------------------------------------------------------------
-
-During time-out, males have the opportunity to search for a nuptial gift.
-Males can adopt one of two strategies; either search or do not search for a nuptial gift. 
-Males with the former strategy continue to search until they find a nuptial gift, while males that do not search will immediately re-enter the mating pool. 
-In this case, time searching for a nuptial gift will come at the cost of mating opportunities but might increase offspring fitness. 
-We therefore need to model the expected length of time $E[T_{\mathrm{m}}]$ spent outside of the mating pool for males that search for nuptial gifts, which is simply $\alpha$. 
-Note that we can integrate search time $t$ over the rate at which nuptial gifts are encountered ($\exp(-1/\alpha)$) to show $E[T_{\mathrm{m}}] = \alpha$,
-
-$$E[T_{\mathrm{m}}] = \int_{0}^{\infty}e^{- \frac{1}{\alpha}t}dt = \alpha.$$
-
-The rate at which a focal male that searches for a nuptial gift ($\mathrm{M_{G}}$) increases his fitness is therefore the fitness of his offspring $(1 + \gamma)$ divided by expected time spent searching for a nuptial gift ($\alpha$) plus time spent in the mating pool, $(\beta + 1)/R$ (recall that females produce $\lambda$ offspring),
-
-$$W_{\mathrm{M_{G}}} = \lambda \frac{1 + \gamma}{\alpha + \left( \frac{\beta + 1}{R} \right)}.$$
-
-In contrast, a male that does not search for a nuptial gift ($\mathrm{M_{L}}$) has offspring with lower fitness, but spends less time outside of the mating pool,
-
-$$W_{\mathrm{M_{L}}} = \lambda \frac{1}{\left(\frac{\beta+1}{R} \right)} = \lambda \frac{R}{\beta + 1}.$$
-
-We can then determine the conditions for which $W_{\mathrm{M_{G}}} > W_{\mathrm{M_{L}}}$, isolating $\gamma$ to find how large of a fitness benefit must be provided by the nuptial gift to make the search cost worthwhile, which simplifies to ineq.
-2.
-When this inequality holds, males are favoured to search until they find a nuptial gift, which would result in an average search time of $\alpha$. 
-When the male trait is continuous (i.e., males search for time period $T_{\mathrm{m}}$), it can be shown that the same threshold can be reached by evaluating the partial derivative of the male fitness function (Supporting Information S3).
-Hence, the thresholds are consistent under different assumptions concerning male searching strategy.
-Selection will cause males to search for nuptial gifts if the fitness increase to offspring exceeds the product of search time and female encounter rate.
-
-Female fitness
---------------------------------------------------------------------------------
-
-During time-out, females process offspring over a duration of $T_{\mathrm{f}}$ (we assume that $T_{\mathrm{f}} > \alpha$, else females are not the choosy sex). 
-When females re-enter the mating pool, they encounter males at a rate of $R\beta/(\beta + 1)$. 
-If a female encounters a male with a nuptial gift, we assume that she will mate with him. 
-But if a female encounters a male with no nuptial gift, then she might accept or reject the male. 
-If she rejects the male, then she will remain in the mating pool. 
-The rate at which a female encounters a male with a nuptial gift is,
-
-$$R_{\mathrm{F_{G}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right).$$
-
-We can similarly model the rate at which a female encounters a gift-less male,
-
-$$R_{\mathrm{F_{L}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(e^{-\frac{1}{\alpha}T_{m}}\right).$$
-
-Note that we can recover the rate at which a female encounters any male,
-
-$$R \left(\frac{\beta}{\beta + 1}\right) = R \left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + R \left(\frac{\beta}{\beta + 1}\right) \left(e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right).$$
-
-If $R_{\mathrm{F_{G}}}$ is sufficiently high and $R_{\mathrm{F_{L}}}$ is sufficiently low, then finding a male with a gift will be easier than finding a male without one. 
-Also, the expected time spent in the mating pool before a focal female encounters a male with a gift will be $1/R_{\mathrm{F_{G}}}$, while the expected time spent in the mating pool before a focal female encounters any male will be $1 / (R_{\mathrm{F_{G}}} + R_{\mathrm{F_{L}}})$.
-Finally, the rates at which a female encounters males with and without a gift, $R_{\mathrm{F_{G}}}$ and $R_{\mathrm{F_{L}}}$, are different from the probabilities that a male encounter has or does not have a gift.
-The rate of encounter is no longer relevant in this case because we are assuming that an encounter has occurred. 
-Hence, the probability of an encountered male having a gift is simply,
-
-$$P(G) = \frac{1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}} = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
-
-Similarly, the probability of an encountered male not having a gift is simply,
-
-$$P(L) = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
-
-The rate at which a female increases her fitness by being choosy and mating only when she encounters a male with a gift is,
-
-<!---
-
-$$W_{f, g} = \frac{1 + \gamma}{T_{F} + \frac{1}{M_{f,G}}}.$$
-
---->
-
-\begin{equation}
-W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}}} + \frac{1}{\mathrm{F_{G}}}.
-\end{equation}
-
-The top of the right-hand side of Eq. 6 gives the fitness increase, and the bottom gives the total time it takes to obtain this fitness. 
-The $R_{\mathrm{F_{G}}}$ is inverted because it represents the expected time to encountering a male with a gift. 
-We can expand Eq. 6,
-
-$$W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right)}}.$$
-
-If the focal female is not choosy and accepts the first male that she encounters, then the rate at which she increases her fitness is,
-
-$$W_{\mathrm{F_{G,L}}} = \lambda \frac{\left(1 + \gamma\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)}}.$$
-
-We then evaluate the conditions under which $W_{\mathrm{F_{G}}} > W_{\mathrm{F_{G,L}}}$. 
-We isolate $\gamma$ to determine how much offspring fitness must be increased to make choosiness beneficial ($\gamma_{\mathrm{f}}$),
-
-$$\gamma_{\mathrm{f}} > \frac{1 + \frac{1}{\beta}}{D T_{f} \left(1 - e^{-1\frac{1}{\alpha}T_{m}}\right)}.$$
-
-The above can be expressed as Eq. 7 below,
-
-<!---
-
-$$\gamma_{f} > \frac{1}{T_{F}M\sqrt{\beta}\left(1 - e^{-\frac{1}{\alpha}T_{M}} \right)}.$$
-
---->
-
-\begin{equation}
-\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}}} R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right).
-\end{equation}
-
-Note that that the expression $R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right)$ defines the rate at which a female in the mating pool encounters males with nuptial gifts.
-Hence, female choosiness is ultimately determined by time spent out of the mating pool to process offspring ($T_{\mathrm{f}}$) and the rate at which a female in the mating pool encounters males with nuptial gifts.
-
-Operational sex ratio
-----------------------------
-
-We assume that the sex ratio is equal upon maturation. 
-Given this, @Kokko2001 show that the operational sex ratio depends on the probability of finding an individual in time-in,
-
-<!---
-
-$$\beta = \frac{\int_{t = 0}^{\infty} P_{IM}(t)dt}{\int_{t = 0}^{\infty} P_{IF}(t)dt}.$$
-
---->
-
-\begin{equation}
-\beta = \frac{\int_{t = 0}^{\infty} P_{IM}(t)dt}{\int_{t = 0}^{\infty} P_{IF}(t)dt}.
-\end{equation}
-
-In Eq. 8, $P_{IM}(t)$ and $P_{IF}(t)$ are the probabilities of finding a male and female in time-in, respectively. 
-There is no closed form solution to the operational sex ratio, so we used recursion to calculate $\beta$ values for a given $T_{\mathrm{f}}$, $T_{\mathrm{m}}$, and $R$ (see Supporting Information S4),
-
-Individual-based model
-------------------------------------------
-
-We formulate an individual-based simulation model to test whether the predictions made by the analytical time-in time-out model are qualitatively the same under a similar simulation model. 
-We use the individual-based model to test whether the prediction hold in finite populations. 
-The IBM was written in C. 
-All details of the initialisation, parameterisation and the specific simulations which we run, are described in Supporting Information S1.
-
-We use available experimental data on the effect of nuptial gifts on female offspring production to estimate the key parameter $\gamma$ (fitness increment from nuptial gift) and conducted a series of simulations where $\gamma$ was parameterised using this estimated value.
-Details of the estimation of $\gamma$ are described in Supporting Information S5.
-Separate evolution of male search and female choice (i.e., without co-evolution) is simulated in Supporting Information S6.
-
 **Author contributions:** APC and ABD conceived the study.
@@
 
-| Information                                                   | Page |
-|---------------------------------------------------------------|------|
-| S1: Description of the individual-based simulation model      |  18  |
-| S2: Sensitivity analysis of mortality parameters in IBM       |  20  |
-| S3: Alternative derivation of male fitness threshold          |  29  |
-| S4: Operational sex ratio                                     |  32  |
-| S5: Estimation of key model parameter using experimental data |  33  |
-| S6: Separate evolution of male search and female choice       |  34  |
-
-\clearpage
-
-S1: Description of the individual-based simulation model
+S1: Alternative derivation of male fitness threshold
 ------------------------------------
 
-Here we describe the details of initialisation, time-in (mating), time-out (reproduction and nuptial gift search), and mortality. 
-We then summarise the simulations run and data collected.
-
-*Initialisation*
-
-Before the first time step, a population of $N = 1000$ individuals is initialised. 
-Individuals are assigned unique IDs, and each is assigned to be female with a probability of $0.5$, else male. 
-Each individual $i$ is initialised with a starting value of female offspring processing time ($T^{i}_{\mathrm{f}}$), rejection probability of gift-less males ($\rho^{i}$), and male search time ($T^{i}_{\mathrm{m}}$).
-For all simulations, initialised values are set to $T^{i}_{\mathrm{f}} = 2$, $\rho^{i} = 0$, and $T^{i}_{\mathrm{m}} = 0$. 
-All individuals are initalised outside of the mating pool in the first time step $t = 1$. 
-The first time step then proceeds with females immediately entering the mating pool and males either entering the mating pool or searching for nuptial gifts.
-
-*Time-in*
-
-At the start of each time step, females and males in the mating pool remain in it. 
-Females will enter the mating pool after processing offspring, and males will enter it after searching for nuptial gifts (see 'Time-out' below). 
-Up to $\Psi = N\psi$ interactions between individuals can occur in a single time step, where $N$ is population size and $\psi$ is a scaling parameter. 
-In each time step, $\Psi$ pairs of individuals are selected at random to interact.
-For each interaction, two different individuals are randomly selected from the population with equal probability.
-If the selected individuals are of different sexes, and both are in the mating pool, then a mating encounter occurs.
-If the male does not have a nuptial gift, then the female will reject him with a probability of $\rho^{i}$; if rejection occurs, then both individuals stay in the mating pool. 
-If rejection does not occur, or the male has a nuptial gift in the mating encounter, then the individuals mate. 
-Females leave the mating pool and enter time-out to process offspring, and males leave and enter time-out to potentially search for new nuptial gifts (note that females and males might re-enter the mating pool immediately within the same time step given sufficiently low search time; see Time-out below).
-
-*Time-out*
-
-During time-out, offspring production and time outside of the mating pool are realised for each female by sampling from a Poisson distribution.
-A focal female $i$ will produce $Poisson(\lambda)$ offspring if no nuptial gift was provided or $Poisson(\lambda + \gamma)$ if a gift was provided. 
-Females remain outside of the mating pool to process offspring for $Poisson(T^{i}_{\mathrm{f}})$ time steps. 
-Offspring are added to the population immediately, with $\rho^{i}$ and $T^{i}_{\mathrm{m}}$ values that are the average of each parent plus some normally distributed error $\epsilon_{R}$ and $\epsilon_{T_{\mathrm{m}}}$.
-For example,
-
-$$T^{\mathrm{offspring}}_{\mathrm{m}} \sim \frac{T^{\mathrm{mother}}_{\mathrm{m}}  + T^{\mathrm{father}}_{\mathrm{m}}}{2} + N\left(0, \epsilon_{T_{\mathrm{m}}} \right).$$
-
-The variation generated by $\epsilon$ values simulates mutation upon which selection for traits can act. 
-In all simulations, $\epsilon = 0$ if a trait is fixed and $\epsilon = 0.01$ if the trait evolves. 
-Offspring sex is randomly assigned with equal probability as female or male. 
-Female offspring are immediately placed in the mating pool, and male offspring are out of the mating pool to potentially search for nuptial gifts. 
-After a female has spent $T^{i}_{\mathrm{f}}$ time steps outside the mating pool, she will re-enter it.
-
-A focal male $i$ outside the mating pool will enter it if he has searched for a fixed number of $T^{i}_{\mathrm{m}}$ time steps, which is also sampled randomly from a Poisson distribution, $Poisson(T^{i}_{\mathrm{m}})$.
-If $T^{i}_{\mathrm{m}} = 0$, then the male immediately returns to the mating pool (in the same time step). 
-If $T^{i}_{\mathrm{m}} > 0$, then the male must wait outside the mating pool for $Poisson(T^{i}_{\mathrm{m}})$ time steps, but will enter the mating pool with a nuptial gift with a probability,
-
-$$P(G^{i}) = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.$$
-
-Males must always spend $T^{i}_{\mathrm{m}}$ time steps outside of the mating pool regardless of whether or not they are successful in obtaining a nuptial gift.
-
-*Mortality*
-
-At the end of each time step, mortality occurs first with a fixed probability for all adults in the population, then with a probability caused by carrying capacity $K$ applied to all individuals (adults and offspring).
-Mortality occurs in each time step with a fixed probability of $\mu$ regardless of the sex of the individual or its position in or out of the mating pool. 
-If after this fixed mortality is applied, the total population size $N > K$, then individuals are removed at random with equal probability until $N = K$. 
-Following adult mortality, a new time step begins with newly added offspring becoming adults.
-
-*Simulations*
-
-We ran simulations in which male search time and female choosiness evolved from an ancestral state of no searching and no choosiness. 
-In all simulations, $N$ was initialised at 1000 and $K = 1000$. 
-Simulations ran for $t_{max} = 40000$ time steps. 
-We set $T_{\mathrm{f}} = 2$, $\psi = 3$, and $\lambda = 1$ for all simulations, and we simulated across a range of $\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}$ and $\gamma = \{0, 0.1, ..., 1.9, 2.0\}$ parameter values for 3200 replicates.
-Summary statistics for mean trait values, population size, sex ratios, proportion of females and males in and out of the mating pool, and mean number of encounters per female and male within the mating pool were all calculated in the last time step.
-The C code used for simulating these IBMs also allows for the reporting of statistics in each time step. 
-Additionally, it can simulate explicit space and individual movement through the landscape. 
-A neutral evolving trait was also modelled to ensure that the code functioned as intended, and processes were compartmentalised into individual functions to facilitate code testing. 
-All code is publicly available on GitHub (https://github.com/bradduthie/nuptial_gift_evolution).
-
-A set of simulations with a value of $\gamma$ calculated from empirical data was also conducted (100 replicates). 
-Here, $\gamma$ was parameterised using data on egg production as a function of eating nuptial gifts (see below). 
-Additional simulation sets with lower and upper bounds of the estimated $\gamma$ were subsequently run. 
-In the simulation sets with experimentally derived parameter values, all other parameters were identical to previous simulation batches.
-
-We can produce an estimate of the fitness increment obtained by females when receiving a gift ($\hat{\gamma}$) by using data on female *P.
-mirabilis* egg production and hatching success under different feeding regimes from [@Tuni2013a].
-@Tuni2013a found differences in egg production and hatching success in female *P. mirabilis* under different feeding regimes. 
-Assuming these differences in feeding regimes correspond to eating versus not eating nuptial gifts, the mean number of offspring produced by a female who eats nuptial gifts can be calculated (Table 1).
-
-\clearpage
-
-S2: Sensitivity analysis of parameters in IBM
-------------------------------------
-
-We investigated the sensitivity of our results to individual mortality during time-in ($\mu_{\mathrm{in}}$) and time-out ($\mu_{\mathrm{out}}$), female processing time ($T_{\mathrm{f}}$), potential for interactions between conspecifics ($\psi$), and initialised male search time ($T_{\mathrm{m}}$).
-Across all of these simulations, there were challenges with statistical power.
-Evidence for the evolution of male search (blue points in figures) and female choosiness (red points in figures) was determined by the lower 95\% bootstrapped confidence interval of $T_{\mathrm{m}}$ and $T_{\mathrm{f}}$ values being greater than zero, respectively.
-This required a lot of replicate simulations in the main text (Figure 3), especially for values just above predicted thresholds and for female choosiness.
-Computation time was a limiting factor, even using a compiled language (C) and with access to a computing cluster.
-Absence of points above threshold values are not necessarily evidence that evolution of male search or female choosiness is not predicted to evolve in these regions of parameter space, but it does indicate that evolution of these traits is not necessarily assured given the stochasticity inherent to the IBM.
-Additional simulations can be conducted using the C code in the 'src' folder of the GitHub repository (https://github.com/bradduthie/nuptial_gift_evolution).
-Below, we explain the parameter values used in the sensitivity analysis in more detail.
-
-*Mortality*
-
-We conducted a sensitivity analysis of the effect of the mortality parameters $\mu_{\mathrm{in}}$ and $\mu_{\mathrm{out}}$ (the probability of mortality in time-in and time-out, respectively, which we assumed to be equal for all individuals) on the evolution of male search and female choice using the IBM (See S1).
-The results revealed no correlation between the value of the mortality parameters and the evolution of male search or female choice (Fig. S2.1).
-
-*Female processing time*
-
-We also conducted a sensitivity analysis of female processing time $T_{\mathrm{f}}$. 
-To do this, we ran simulations at default values, but with $T_{\mathrm{f}} = 0.4$ (Figure S4.2) and $T_{\mathrm{f}} = 10.0$ (Figures S4.3).
-
-*Interactions between conspecifics*
-
-We conducted a sensitivity analysis on the encounter rate between conspecifics ($R$) by varying the value of $\psi$ (see S1).
-Under default simulations, $\psi = 3$.
-We also ran simulations in which $\psi = 1$ (Figure S4.4), $\psi = 2$ (Figure S4.5), $\psi = 4$ (Figure S4.6), and $\psi = 6$ (Figure S4.7), with all other parameters being set to default values.
-
-*Initialised male search time*
-
-Lastly, we conducted a sensitivity analysis on initialised male search time ($T_{\mathrm{m}}$).
-To do this, we ran simulations at default values, but initialised all males at $T_{\mathrm{m}} = 0.5$ (Figure S4.8) or $T_{\mathrm{m}} = 2.5$ (S4.9). 
-Note that under these initialisation conditions, it no longer makes sense to test whether or not $T_{\mathrm{m}}$ evolves to positive values, so we do not show predicted male search thresholds and focus only on female choosiness.
-Interestingly, while predictions given initialised $T_{\mathrm{m}} = 0.5$ are quite close for female choosiness thresholds, female choosiness does not appear to evolve given $T_{\mathrm{m}} = 2.5$.
-This might be due to low selection pressure to reject males without gifts due to their low frequency.
-In other words, while females would benefit from a strategy of rejecting gift-less males, a lack of realised encounters with gift-less males preclude the evolution of sustained selection for choosiness.
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.1: Evolution of both male search (blue) and female choice (red) under different combinations of the mortality rates $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$ (mortality in time-in and out, respectively).
-The y-axis is the threshold fitness that leads to evolution of male search (blue) or female choice (red).
-The results show noise, but no correlation between the value of the mortality parameters and the propensity for male search and/or female choice to evolve.
-For each of the $25 \\times 20$ combinations of $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$, 1600 replicate simulations were run."}
-SUMO <- read.csv("inst/SI_mortality.csv");
-mort_combn   <- paste(SUMO[,1], SUMO[,2]);
-mort_label   <- unique(paste(SUMO[,1], ", ", SUMO[,2], sep = ""));
-TM_vals      <- tapply(X = SUMO[,4],  INDEX = mort_combn, FUN = mean);
-m_vals       <- tapply(X = SUMO[,14], INDEX = mort_combn, FUN = mean);
-beta_vals    <- tapply(X = SUMO[,15], INDEX = mort_combn, FUN = mean);
-Male_M       <- tapply(X = SUMO[,16], INDEX = mort_combn, FUN = mean);
-Female_M     <- tapply(X = SUMO[,17], INDEX = mort_combn, FUN = mean);
-Mf_nupt      <- tapply(X = SUMO[,18], INDEX = mort_combn, FUN = mean);
-Mf_nonupt    <- tapply(X = SUMO[,19], INDEX = mort_combn, FUN = mean);
-male_search  <- as.numeric(which(SUMO[,5] > 0 & SUMO[,6] > 0));
-fem_choose   <- as.numeric(which(SUMO[,8] > 0 & SUMO[,9] > 0));
-mimmom       <- unique(cbind(SUMO[,1], SUMO[,2]));
-
-mm <- SUMO[male_search,];
-mp <- NULL;
-for(i in 1:dim(mm)[1]){
-  rval <- which(mm[i, 1] == mimmom[,1] & mm[i, 2] == mimmom[,2]);
-  mp   <- rbind(mp, c(rval, mm[i, 3]));
-}
-
-ff <- SUMO[fem_choose,];
-fp <- NULL;
-for(i in 1:dim(ff)[1]){
-    rval <- which(ff[i, 1] == mimmom[,1] & ff[i, 2] == mimmom[,2]);
-    fp   <- rbind(fp, c(rval, ff[i, 3]));
-}
-
-par(mar = c(8, 5, 1, 1));
-plot(x = mp[,1], y = mp[,2], pch = 20, ylim = c(0, 2), col = "blue",
-     xlab = "", ylab = "", xaxt = "n", cex.lab = 1.25);
-points(x = fp[,1], y = fp[,2], cex = 2.5, col = "red", pch = 20);
-points(x = mp[,1], y = mp[,2], cex = 1.5, col = "blue", pch = 20);
-axis(side = 1, labels = mort_label, at = 1:25, las = 2);
-mtext(text = expression(paste("Mortality combination (",mu["in"],", ", 
-                              mu["out"],")")), side = 1, line = 6.5, 
-      cex = 1.25); 
-mtext(text = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                              ")")), side = 2, line = 2.5, cex = 1.25); 
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.2 ($T_{\\mathrm{f}} = 0.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from approximately 1600 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates).
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Up to 3000 interactions occur between individuals in each time step ($\\psi = 3$), potentially resulting in a mating interaction.
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=0.5$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.5, 1.5] and [0.1, 2.1], respectively, were used."}
-SUMM_Tf0pt4 <- read.csv("inst/SI_Tf_0pt5.csv");
-
-alpha_vals <- sort(unique(SUMM_Tf0pt4[,1]));
-TM_vals    <- tapply(X = SUMM_Tf0pt4[,3],  INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-m_vals     <- tapply(X = SUMM_Tf0pt4[,13], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-beta_vals  <- tapply(X = SUMM_Tf0pt4[,14], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-Male_M     <- tapply(X = SUMM_Tf0pt4[,15], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-Female_M   <- tapply(X = SUMM_Tf0pt4[,16], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-Mf_nupt    <- tapply(X = SUMM_Tf0pt4[,17], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-Mf_nonupt  <- tapply(X = SUMM_Tf0pt4[,18], INDEX = SUMM_Tf0pt4[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 0.5);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2.1));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Tf0pt4)[1]){
-  if(SUMM_Tf0pt4[i, 4] > 0 & SUMM_Tf0pt4[i, 5] > 0){
-    points(x = SUMM_Tf0pt4[i, 1], y = SUMM_Tf0pt4[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Tf0pt4)[1]){
-  if(SUMM_Tf0pt4[i, 7] > 0 & SUMM_Tf0pt4[i, 8] > 0){
-    points(x = SUMM_Tf0pt4[i, 1], y = SUMM_Tf0pt4[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.3 ($T_{\\mathrm{f}} = 10.0$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from approximately 1600 replicate simulations with identical starting conditions (some parameter combinations include fewer replicates).
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Up to 3000 interactions occur between individuals in each time step ($\\psi = 3$), potentially resulting in a mating interaction.
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=10.0$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.5, 1.5] and [0.1, 2.1], respectively, were used."}
-SUMM_Tf10 <- read.csv("inst/SI_Tf_10pt0.csv");
-
-alpha_vals <- sort(unique(SUMM_Tf10[,1]));
-TM_vals    <- tapply(X = SUMM_Tf10[,3],  INDEX = SUMM_Tf10[,1], FUN = mean);
-m_vals     <- tapply(X = SUMM_Tf10[,13], INDEX = SUMM_Tf10[,1], FUN = mean);
-beta_vals  <- tapply(X = SUMM_Tf10[,14], INDEX = SUMM_Tf10[,1], FUN = mean);
-Male_M     <- tapply(X = SUMM_Tf10[,15], INDEX = SUMM_Tf10[,1], FUN = mean);
-Female_M   <- tapply(X = SUMM_Tf10[,16], INDEX = SUMM_Tf10[,1], FUN = mean);
-Mf_nupt    <- tapply(X = SUMM_Tf10[,17], INDEX = SUMM_Tf10[,1], FUN = mean);
-Mf_nonupt  <- tapply(X = SUMM_Tf10[,18], INDEX = SUMM_Tf10[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 10);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2.1));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Tf10)[1]){
-  if(SUMM_Tf10[i, 4] > 0 & SUMM_Tf10[i, 5] > 0){
-    points(x = SUMM_Tf10[i, 1], y = SUMM_Tf10[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Tf10)[1]){
-  if(SUMM_Tf10[i, 7] > 0 & SUMM_Tf10[i, 8] > 0){
-    points(x = SUMM_Tf10[i, 1], y = SUMM_Tf10[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.4 ($\\psi = 1$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from approximately 100 replicate simulations with identical starting conditions (some parameter combinations had fewer replicates, minimum 400).
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Up to 1000 interactions occur between individuals in each time step ($\\psi = 1$), potentially resulting in a mating interaction.
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
-SUMM_Nexp1   <- read.csv("inst/SI_Nexp_1.csv");
-
-alpha_vals   <- sort(unique(SUMM_Nexp1[,1]));
-TM_vals      <- tapply(X = SUMM_Nexp1[,3],  INDEX = SUMM_Nexp1[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_Nexp1[,13], INDEX = SUMM_Nexp1[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_Nexp1[,14], INDEX = SUMM_Nexp1[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_Nexp1[,15], INDEX = SUMM_Nexp1[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_Nexp1[,16], INDEX = SUMM_Nexp1[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_Nexp1[,17], INDEX = SUMM_Nexp1[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_Nexp1[,18], INDEX = SUMM_Nexp1[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2.1));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Nexp1)[1]){
-  if(SUMM_Nexp1[i, 4] > 0 & SUMM_Nexp1[i, 5] > 0){
-    points(x = SUMM_Nexp1[i, 1], y = SUMM_Nexp1[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Nexp1)[1]){
-  if(SUMM_Nexp1[i, 7] > 0 & SUMM_Nexp1[i, 8] > 0){
-    points(x = SUMM_Nexp1[i, 1], y = SUMM_Nexp1[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.5 ($\\psi = 2$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 100 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates).
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Up to 2000 interactions occur between individuals in each time step ($\\psi = 2$), potentially resulting in a mating interaction.
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
-SUMM_Nexp2   <- read.csv("inst/SI_Nexp_2.csv");
-
-alpha_vals   <- sort(unique(SUMM_Nexp2[,1]));
-TM_vals      <- tapply(X = SUMM_Nexp2[,3],  INDEX = SUMM_Nexp2[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_Nexp2[,13], INDEX = SUMM_Nexp2[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_Nexp2[,14], INDEX = SUMM_Nexp2[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_Nexp2[,15], INDEX = SUMM_Nexp2[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_Nexp2[,16], INDEX = SUMM_Nexp2[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_Nexp2[,17], INDEX = SUMM_Nexp2[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_Nexp2[,18], INDEX = SUMM_Nexp2[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2.1));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Nexp2)[1]){
-  if(SUMM_Nexp2[i, 4] > 0 & SUMM_Nexp2[i, 5] > 0){
-    points(x = SUMM_Nexp2[i, 1], y = SUMM_Nexp2[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Nexp2)[1]){
-  if(SUMM_Nexp2[i, 7] > 0 & SUMM_Nexp2[i, 8] > 0){
-    points(x = SUMM_Nexp2[i, 1], y = SUMM_Nexp2[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.6 ($\\psi = 4$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 100 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates).
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Up to 4000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 4$).
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
-SUMM_Nexp4   <- read.csv("inst/SI_Nexp_4.csv");
-
-alpha_vals   <- sort(unique(SUMM_Nexp4[,1]));
-TM_vals      <- tapply(X = SUMM_Nexp4[,3],  INDEX = SUMM_Nexp4[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_Nexp4[,13], INDEX = SUMM_Nexp4[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_Nexp4[,14], INDEX = SUMM_Nexp4[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_Nexp4[,15], INDEX = SUMM_Nexp4[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_Nexp4[,16], INDEX = SUMM_Nexp4[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_Nexp4[,17], INDEX = SUMM_Nexp4[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_Nexp4[,18], INDEX = SUMM_Nexp4[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2.1));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Nexp4)[1]){
-  if(SUMM_Nexp4[i, 4] > 0 & SUMM_Nexp4[i, 5] > 0){
-    points(x = SUMM_Nexp4[i, 1], y = SUMM_Nexp4[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Nexp4)[1]){
-  if(SUMM_Nexp4[i, 7] > 0 & SUMM_Nexp4[i, 8] > 0){
-    points(x = SUMM_Nexp4[i, 1], y = SUMM_Nexp4[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.7 ($\\psi = 6$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 100 replicate simulations with identical starting conditions (some parameter combinations have fewer replicates).
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively.
-Up to 6000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 6$).
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
-SUMM_Nexp6   <- read.csv("inst/SI_Nexp_6.csv");
-
-alpha_vals   <- sort(unique(SUMM_Nexp6[,1]));
-TM_vals      <- tapply(X = SUMM_Nexp6[,3],  INDEX = SUMM_Nexp6[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_Nexp6[,13], INDEX = SUMM_Nexp6[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_Nexp6[,14], INDEX = SUMM_Nexp6[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_Nexp6[,15], INDEX = SUMM_Nexp6[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_Nexp6[,16], INDEX = SUMM_Nexp6[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_Nexp6[,17], INDEX = SUMM_Nexp6[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_Nexp6[,18], INDEX = SUMM_Nexp6[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 2.1));
-
-points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Nexp6)[1]){
-  if(SUMM_Nexp6[i, 4] > 0 & SUMM_Nexp6[i, 5] > 0){
-    points(x = SUMM_Nexp6[i, 1], y = SUMM_Nexp6[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Nexp6)[1]){
-  if(SUMM_Nexp6[i, 7] > 0 & SUMM_Nexp6[i, 8] > 0){
-    points(x = SUMM_Nexp6[i, 1], y = SUMM_Nexp6[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.8 ($T_{\\mathrm{m}} = 0.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 1600 replicate simulations with identical starting conditions.
-The red line shows the threshold above which the mathematical model predicts that females should be choosy (male thresholds for search are not shown because simulations were initialised with males already searching for nuptial gifts).
-Up to 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 3$).
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
-SUMM_Tm05   <- read.csv("inst/SI_Tm_0pt5.csv");
-
-alpha_vals   <- sort(unique(SUMM_Tm05[,1]));
-TM_vals      <- tapply(X = SUMM_Tm05[,3],  INDEX = SUMM_Tm05[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_Tm05[,13], INDEX = SUMM_Tm05[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_Tm05[,14], INDEX = SUMM_Tm05[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_Tm05[,15], INDEX = SUMM_Tm05[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_Tm05[,16], INDEX = SUMM_Tm05[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_Tm05[,17], INDEX = SUMM_Tm05[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_Tm05[,18], INDEX = SUMM_Tm05[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 1.6));
-
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Tm05)[1]){
-  if(SUMM_Tm05[i, 4] > 0 & SUMM_Tm05[i, 5] > 0){
-    points(x = SUMM_Tm05[i, 1], y = SUMM_Tm05[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Tm05)[1]){
-  if(SUMM_Tm05[i, 7] > 0 & SUMM_Tm05[i, 8] > 0){
-    points(x = SUMM_Tm05[i, 1], y = SUMM_Tm05[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.9 ($T_{\\mathrm{m}} = 2.5$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
-Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 1600 replicate simulations with identical starting conditions.
-The red line shows the threshold above which the mathematical model predicts that females should be choosy (male thresholds for search are not shown because simulations were initialised with males already searching for nuptial gifts).
-Up to 3000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 3$).
-The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
-Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 1.4] and [0.1, 1.2], respectively, were used."}
-SUMM_Tm2p5   <- read.csv("inst/SI_Tm_2pt5.csv");
-
-alpha_vals   <- sort(unique(SUMM_Tm2p5[,1]));
-TM_vals      <- tapply(X = SUMM_Tm2p5[,3],  INDEX = SUMM_Tm2p5[,1], FUN = mean);
-m_vals       <- tapply(X = SUMM_Tm2p5[,13], INDEX = SUMM_Tm2p5[,1], FUN = mean);
-beta_vals    <- tapply(X = SUMM_Tm2p5[,14], INDEX = SUMM_Tm2p5[,1], FUN = mean);
-Male_M       <- tapply(X = SUMM_Tm2p5[,15], INDEX = SUMM_Tm2p5[,1], FUN = mean);
-Female_M     <- tapply(X = SUMM_Tm2p5[,16], INDEX = SUMM_Tm2p5[,1], FUN = mean);
-Mf_nupt      <- tapply(X = SUMM_Tm2p5[,17], INDEX = SUMM_Tm2p5[,1], FUN = mean);
-Mf_nonupt    <- tapply(X = SUMM_Tm2p5[,18], INDEX = SUMM_Tm2p5[,1], FUN = mean);
-
-g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
-g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
-                            TF = 2);
-
-par(mar = c(5, 5, 1, 1)); 
-plot(x = alpha_vals, y = g_f, type = "l", lwd = 2, cex.lab = 1.25, col = "red",
-     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
-     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
-                             ")")),
-     ylim = c(0, 1.6));
-
-points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-       lty = "dashed");
-
-for(i in 1:dim(SUMM_Tm2p5)[1]){
-  if(SUMM_Tm2p5[i, 4] > 0 & SUMM_Tm2p5[i, 5] > 0){
-    points(x = SUMM_Tm2p5[i, 1], y = SUMM_Tm2p5[i, 2], cex = 3, pch = 20, 
-           col = "blue");
-  }
-}
-
-for(i in 1:dim(SUMM_Tm2p5)[1]){
-  if(SUMM_Tm2p5[i, 7] > 0 & SUMM_Tm2p5[i, 8] > 0){
-    points(x = SUMM_Tm2p5[i, 1], y = SUMM_Tm2p5[i, 2], cex = 2, pch = 20, 
-           col = "red");
-  }
-}
-```
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-S3: Alternative derivation of male fitness threshold
-------------------------------------
-
 In the main text, we assumed that males made the decision to search or not search for a nuptial gift.
-The expected length of time for which searching males are expected to remain outside of the mating pool is $E[T_{\mathrm{m}}] = \alpha$ (see Methods).
-Alternatively, we can assume that males search for a period of $T_{\mathrm{m}}$ and spend this full duration of $T_{\mathrm{m}}$ in the time-out phase, even if they succeed in finding a nuptial gift.
+The expected length of time for which searching males are expected to remain outside of the mating pool is $E[T_{\mathrm{m}}] = \alpha$ (see Model).
+Alternatively, we can assume that males search for a period of $T_{\mathrm{m}}$ and spend this full duration of $T_{\mathrm{m}}$ in the time-out phase, even if they succeed in finding a nuptial gift (as we assumed in our IBM).
 The probability that a male obtains a nuptial gift during this time is modelled in Eq. 1,
@@
 
-S5: Estimation of key model parameters using experimental data
+S3: Sensitivity analysis of parameters in IBM
+------------------------------------
+
+We investigated the sensitivity of our results to individual mortality during time-in ($\mu_{\mathrm{in}}$) and time-out ($\mu_{\mathrm{out}}$), female processing time ($T_{\mathrm{f}}$), and the potential for interactions between conspecifics ($\psi$).
+Across all of these simulations, there were challenges with statistical power.
+Evidence for the evolution of male search (blue points in figures) and female choosiness (red points in figures) was determined by the lower 95\% bootstrapped confidence interval of $T_{\mathrm{m}}$ and $T_{\mathrm{f}}$ values being greater than zero, respectively.
+This required a lot of replicate simulations in the main text (Figure 3), especially for values just above predicted thresholds and for female choosiness.
+Computation time was a limiting factor, even using a compiled language (C) and with access to a computing cluster.
+Absence of points above threshold values are not necessarily evidence that evolution of male search or female choosiness is not predicted to evolve in these regions of parameter space, but it does indicate that evolution of these traits is not necessarily assured given the stochasticity inherent to the IBM.
+Additional simulations can be conducted using the C code in the 'src' folder of the GitHub repository (https://github.com/bradduthie/nuptial_gift_evolution).
+Below, we explain the parameter values used in the sensitivity analysis in more detail.
+
+*Mortality*
+
+We conducted a sensitivity analysis of the effect of the mortality parameters $\mu_{\mathrm{in}}$ and $\mu_{\mathrm{out}}$ (the probability of mortality in time-in and time-out, respectively, which we assumed to be equal for all individuals) on the evolution of male search and female choice using the IBM.
+The results revealed no correlation between the value of the mortality parameters and the evolution of male search or female choice (Fig. S2.1).
+
+*Female processing time*
+
+We also conducted a sensitivity analysis of female processing time $T_{\mathrm{f}}$. 
+To do this, we ran simulations at default values, but with $T_{\mathrm{f}} = 10.0$ (Figures S2.2).
+
+*Interactions between conspecifics*
+
+We conducted a sensitivity analysis on the encounter rate between conspecifics ($R$) by varying the value of our scaling parameter $\psi$.
+Under default simulations, $\psi = 3$.
+We also ran simulations in which $\psi = 1$ (Figure S2.3), $\psi = 2$ (Figure S3.4), $\psi = 4$ (Figure S3.5), and $\psi = 6$ (Figure S3.6), with all other parameters being set to default values.
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.1: Evolution of both male search (blue) and female choice (red) under different combinations of the mortality rates $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$ (mortality in time-in and out, respectively).
+The y-axis is the threshold fitness that leads to evolution of male search (blue) or female choice (red).
+The results show noise, but no correlation between the value of the mortality parameters and the propensity for male search and/or female choice to evolve.
+For each of the $25 \\times 20$ combinations of $\\mu_{\\mathrm{in}}$ and $\\mu_{\\mathrm{out}}$, 3000 replicate simulations were run."}
+SUMO         <- read.csv("inst/summary_mortality.csv");
+alpha_vals   <- sort(unique(SUMO[,3]));
+mort_combn   <- paste(SUMO[,1], SUMO[,2]);
+mort_label   <- unique(paste(SUMO[,1], ", ", SUMO[,2], sep = ""));
+TM_vals      <- tapply(X = SUMO[,5],  INDEX = mort_combn, FUN = mean);
+m_vals       <- tapply(X = SUMO[,14], INDEX = mort_combn, FUN = mean);
+beta_vals    <- tapply(X = SUMO[,15], INDEX = mort_combn, FUN = mean);
+Male_M       <- tapply(X = SUMO[,16], INDEX = mort_combn, FUN = mean);
+Female_M     <- tapply(X = SUMO[,17], INDEX = mort_combn, FUN = mean);
+Mf_nupt      <- tapply(X = SUMO[,18], INDEX = mort_combn, FUN = mean);
+Mf_nonupt    <- tapply(X = SUMO[,19], INDEX = mort_combn, FUN = mean);
+male_search  <- as.numeric(which(SUMO[,5] > 0 & SUMO[,6] > 0));
+fem_choose   <- as.numeric(which(SUMO[,8] > 0 & SUMO[,9] > 0));
+mimmom       <- unique(cbind(SUMO$mim, SUMO$mom));
+
+mm <- SUMO[male_search,]
+mp <- NULL;
+for(i in 1:dim(mm)[1]){
+  rval <- which(mm[i, 1] == mimmom[,1] & mm[i, 2] == mimmom[,2]);
+  mp   <- rbind(mp, c(rval, mm[i, 4]));
+}
+
+ff <- SUMO[fem_choose,]
+fp <- NULL;
+for(i in 1:dim(ff)[1]){
+  rval <- which(ff[i, 1] == mimmom[,1] & ff[i, 2] == mimmom[,2]);
+  fp   <- rbind(fp, c(rval, ff[i, 4]));
+}
+
+par(mar = c(8, 5, 1, 1));
+plot(x = mp[,1], y = mp[,2], pch = 20, ylim = c(0, 2), col = "blue",
+     xlab = "", ylab = "", xaxt = "n", cex.lab = 1.25);
+points(x = fp[,1], y = fp[,2], cex = 2.5, col = "red", pch = 20);
+points(x = mp[,1], y = mp[,2], cex = 1.5, col = "blue", pch = 20);
+axis(side = 1, labels = mort_label, at = 1:25, las = 2);
+mtext(text = expression(paste("Mortality combination (",mu["in"],", ", 
+                              mu["out"],")")), side = 1, line = 6.5, 
+      cex = 1.25); 
+mtext(text = expression(paste("Fitness threshold (", gamma[f], " & ", 
+                              gamma[m], ")")), side = 2, line = 2.5, 
+      cex = 1.25); 
+```
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.3 ($T_{\\mathrm{f}} = 10.0$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
+Each point includes data from 3000 replicate simulations with identical starting conditions.
+Up to 3000 interactions occur between individuals in each time step ($\\psi = 3$), potentially resulting in a mating interaction.
+The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
+Expected female processing time was set to $T_{\\mathrm{f}}=10.0$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.1, 2.0] and [0.0, 2.0], respectively, were used."}
+SUMM_Tf10 <- read.csv("inst/SI_Tf_10pt0.csv");
+
+alpha_vals <- sort(unique(SUMM_Tf10[,1]));
+TM_vals    <- tapply(X = SUMM_Tf10[,3],  INDEX = SUMM_Tf10[,1], FUN = mean);
+m_vals     <- tapply(X = SUMM_Tf10[,13], INDEX = SUMM_Tf10[,1], FUN = mean);
+beta_vals  <- tapply(X = SUMM_Tf10[,14], INDEX = SUMM_Tf10[,1], FUN = mean);
+Male_M     <- tapply(X = SUMM_Tf10[,15], INDEX = SUMM_Tf10[,1], FUN = mean);
+Female_M   <- tapply(X = SUMM_Tf10[,16], INDEX = SUMM_Tf10[,1], FUN = mean);
+Mf_nupt    <- tapply(X = SUMM_Tf10[,17], INDEX = SUMM_Tf10[,1], FUN = mean);
+Mf_nonupt  <- tapply(X = SUMM_Tf10[,18], INDEX = SUMM_Tf10[,1], FUN = mean);
+
+g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
+g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
+                            TF = 10);
+
+par(mar = c(5, 5, 1, 1)); 
+plot(x = alpha_vals, y = g_f, type = "n", lwd = 2, cex.lab = 1.25, col = "red",
+     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
+     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
+                             ")")),
+     ylim = c(0, 2.0));
+
+#points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
+#points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
+#       lty = "dashed");
+
+for(i in 1:dim(SUMM_Tf10)[1]){
+  if(SUMM_Tf10[i, 4] > 0 & SUMM_Tf10[i, 5] > 0){
+    points(x = SUMM_Tf10[i, 1], y = SUMM_Tf10[i, 2], cex = 3, pch = 20, 
+           col = "blue");
+  }
+}
+
+for(i in 1:dim(SUMM_Tf10)[1]){
+  if(SUMM_Tf10[i, 7] > 0 & SUMM_Tf10[i, 8] > 0){
+    points(x = SUMM_Tf10[i, 1], y = SUMM_Tf10[i, 2], cex = 2, pch = 20, 
+           col = "red");
+  }
+}
+```
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.4 ($\\psi = 1$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
+Each point includes data from 3000 replicate simulations with identical starting conditions.
+Up to 1000 interactions occur between individuals in each time step ($\\psi = 1$), potentially resulting in a mating interaction.
+The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
+Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 2.0] and [0.1, 2.0], respectively, were used."}
+SUMM_Nexp1   <- read.csv("inst/SI_Nexp_1.csv");
+
+alpha_vals   <- sort(unique(SUMM_Nexp1[,1]));
+TM_vals      <- tapply(X = SUMM_Nexp1[,3],  INDEX = SUMM_Nexp1[,1], FUN = mean);
+m_vals       <- tapply(X = SUMM_Nexp1[,13], INDEX = SUMM_Nexp1[,1], FUN = mean);
+beta_vals    <- tapply(X = SUMM_Nexp1[,14], INDEX = SUMM_Nexp1[,1], FUN = mean);
+Male_M       <- tapply(X = SUMM_Nexp1[,15], INDEX = SUMM_Nexp1[,1], FUN = mean);
+Female_M     <- tapply(X = SUMM_Nexp1[,16], INDEX = SUMM_Nexp1[,1], FUN = mean);
+Mf_nupt      <- tapply(X = SUMM_Nexp1[,17], INDEX = SUMM_Nexp1[,1], FUN = mean);
+Mf_nonupt    <- tapply(X = SUMM_Nexp1[,18], INDEX = SUMM_Nexp1[,1], FUN = mean);
+
+g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
+g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
+                            TF = 2);
+
+par(mar = c(5, 5, 1, 1)); 
+plot(x = alpha_vals, y = g_f, type = "n", lwd = 2, cex.lab = 1.25, col = "red",
+     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
+     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
+                             ")")),
+     ylim = c(0, 2.0));
+
+# points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
+# points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
+#        lty = "dashed");
+
+for(i in 1:dim(SUMM_Nexp1)[1]){
+  if(SUMM_Nexp1[i, 4] > 0 & SUMM_Nexp1[i, 5] > 0){
+    points(x = SUMM_Nexp1[i, 1], y = SUMM_Nexp1[i, 2], cex = 3, pch = 20, 
+           col = "blue");
+  }
+}
+
+for(i in 1:dim(SUMM_Nexp1)[1]){
+  if(SUMM_Nexp1[i, 7] > 0 & SUMM_Nexp1[i, 8] > 0){
+    points(x = SUMM_Nexp1[i, 1], y = SUMM_Nexp1[i, 2], cex = 2, pch = 20, 
+           col = "red");
+  }
+}
+```
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.5 ($\\psi = 2$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
+Each point includes data from 3000 replicate simulations with identical starting conditions.
+Up to 2000 interactions occur between individuals in each time step ($\\psi = 2$), potentially resulting in a mating interaction.
+The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
+Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 2.0] and [0.1, 2.0], respectively, were used."}
+SUMM_Nexp2   <- read.csv("inst/SI_Nexp_2.csv");
+
+alpha_vals   <- sort(unique(SUMM_Nexp2[,1]));
+TM_vals      <- tapply(X = SUMM_Nexp2[,3],  INDEX = SUMM_Nexp2[,1], FUN = mean);
+m_vals       <- tapply(X = SUMM_Nexp2[,13], INDEX = SUMM_Nexp2[,1], FUN = mean);
+beta_vals    <- tapply(X = SUMM_Nexp2[,14], INDEX = SUMM_Nexp2[,1], FUN = mean);
+Male_M       <- tapply(X = SUMM_Nexp2[,15], INDEX = SUMM_Nexp2[,1], FUN = mean);
+Female_M     <- tapply(X = SUMM_Nexp2[,16], INDEX = SUMM_Nexp2[,1], FUN = mean);
+Mf_nupt      <- tapply(X = SUMM_Nexp2[,17], INDEX = SUMM_Nexp2[,1], FUN = mean);
+Mf_nonupt    <- tapply(X = SUMM_Nexp2[,18], INDEX = SUMM_Nexp2[,1], FUN = mean);
+
+g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
+g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
+                            TF = 2);
+
+par(mar = c(5, 5, 1, 1)); 
+plot(x = alpha_vals, y = g_f, type = "n", lwd = 2, cex.lab = 1.25, col = "red",
+     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
+     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
+                             ")")),
+     ylim = c(0, 2.0));
+
+# points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
+# points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
+#        lty = "dashed");
+
+for(i in 1:dim(SUMM_Nexp2)[1]){
+  if(SUMM_Nexp2[i, 4] > 0 & SUMM_Nexp2[i, 5] > 0){
+    points(x = SUMM_Nexp2[i, 1], y = SUMM_Nexp2[i, 2], cex = 3, pch = 20, 
+           col = "blue");
+  }
+}
+
+for(i in 1:dim(SUMM_Nexp2)[1]){
+  if(SUMM_Nexp2[i, 7] > 0 & SUMM_Nexp2[i, 8] > 0){
+    points(x = SUMM_Nexp2[i, 1], y = SUMM_Nexp2[i, 2], cex = 2, pch = 20, 
+           col = "red");
+  }
+}
+```
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.6 ($\\psi = 4$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
+Each point includes data from 3000 replicate simulations with identical starting conditions.
+Up to 4000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 4$).
+The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
+Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 2.0] and [0.1, 2.0], respectively, were used."}
+SUMM_Nexp4   <- read.csv("inst/SI_Nexp_4.csv");
+
+alpha_vals   <- sort(unique(SUMM_Nexp4[,1]));
+TM_vals      <- tapply(X = SUMM_Nexp4[,3],  INDEX = SUMM_Nexp4[,1], FUN = mean);
+m_vals       <- tapply(X = SUMM_Nexp4[,13], INDEX = SUMM_Nexp4[,1], FUN = mean);
+beta_vals    <- tapply(X = SUMM_Nexp4[,14], INDEX = SUMM_Nexp4[,1], FUN = mean);
+Male_M       <- tapply(X = SUMM_Nexp4[,15], INDEX = SUMM_Nexp4[,1], FUN = mean);
+Female_M     <- tapply(X = SUMM_Nexp4[,16], INDEX = SUMM_Nexp4[,1], FUN = mean);
+Mf_nupt      <- tapply(X = SUMM_Nexp4[,17], INDEX = SUMM_Nexp4[,1], FUN = mean);
+Mf_nonupt    <- tapply(X = SUMM_Nexp4[,18], INDEX = SUMM_Nexp4[,1], FUN = mean);
+
+g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
+g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
+                            TF = 2);
+
+par(mar = c(5, 5, 1, 1)); 
+plot(x = alpha_vals, y = g_f, type = "n", lwd = 2, cex.lab = 1.25, col = "red",
+     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
+     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
+                             ")")),
+     ylim = c(0, 2.0));
+
+# points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
+# points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
+#        lty = "dashed");
+
+for(i in 1:dim(SUMM_Nexp4)[1]){
+  if(SUMM_Nexp4[i, 4] > 0 & SUMM_Nexp4[i, 5] > 0){
+    points(x = SUMM_Nexp4[i, 1], y = SUMM_Nexp4[i, 2], cex = 3, pch = 20, 
+           col = "blue");
+  }
+}
+
+for(i in 1:dim(SUMM_Nexp4)[1]){
+  if(SUMM_Nexp4[i, 7] > 0 & SUMM_Nexp4[i, 8] > 0){
+    points(x = SUMM_Nexp4[i, 1], y = SUMM_Nexp4[i, 2], cex = 2, pch = 20, 
+           col = "red");
+  }
+}
+```
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S2.7 ($\\psi = 6$): The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+Points show where the lower 95% confidence interval of where male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
+Each point includes data from 3000 replicate simulations with identical starting conditions.
+Up to 6000 interactions occur between individuals in each time step, potentially resulting in a mating interaction ($\\psi = 6$).
+The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
+Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 2.0] and [0.1, 2.0], respectively, were used."}
+SUMM_Nexp6   <- read.csv("inst/SI_Nexp_6.csv");
+
+alpha_vals   <- sort(unique(SUMM_Nexp6[,1]));
+TM_vals      <- tapply(X = SUMM_Nexp6[,3],  INDEX = SUMM_Nexp6[,1], FUN = mean);
+m_vals       <- tapply(X = SUMM_Nexp6[,13], INDEX = SUMM_Nexp6[,1], FUN = mean);
+beta_vals    <- tapply(X = SUMM_Nexp6[,14], INDEX = SUMM_Nexp6[,1], FUN = mean);
+Male_M       <- tapply(X = SUMM_Nexp6[,15], INDEX = SUMM_Nexp6[,1], FUN = mean);
+Female_M     <- tapply(X = SUMM_Nexp6[,16], INDEX = SUMM_Nexp6[,1], FUN = mean);
+Mf_nupt      <- tapply(X = SUMM_Nexp6[,17], INDEX = SUMM_Nexp6[,1], FUN = mean);
+Mf_nonupt    <- tapply(X = SUMM_Nexp6[,18], INDEX = SUMM_Nexp6[,1], FUN = mean);
+
+g_m  <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
+g_f  <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, 
+                            TF = 2);
+
+par(mar = c(5, 5, 1, 1)); 
+plot(x = alpha_vals, y = g_f, type = "n", lwd = 2, cex.lab = 1.25, col = "red",
+     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
+     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
+                             ")")),
+     ylim = c(0, 2.0));
+
+# points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
+# points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
+#        lty = "dashed");
+
+for(i in 1:dim(SUMM_Nexp6)[1]){
+  if(SUMM_Nexp6[i, 4] > 0 & SUMM_Nexp6[i, 5] > 0){
+    points(x = SUMM_Nexp6[i, 1], y = SUMM_Nexp6[i, 2], cex = 3, pch = 20, 
+           col = "blue");
+  }
+}
+
+for(i in 1:dim(SUMM_Nexp6)[1]){
+  if(SUMM_Nexp6[i, 7] > 0 & SUMM_Nexp6[i, 8] > 0){
+    points(x = SUMM_Nexp6[i, 1], y = SUMM_Nexp6[i, 2], cex = 2, pch = 20, 
+           col = "red");
+  }
+}
+```
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+S4: Separate evolution of male search and female choice
 -------------------------------------
 
-Estimates showing the mean number of offspring produced by female *Pisaura mirabilis* that ate nuptial gifts and females who did not. 
-Means were calculated with raw data from @Tuni2013a and results are shown $\pm$ SE (Table 1).
-Under these assumptions, the relative gain in fitness from receiving nuptial gifts for a female is,
-
-$$\hat{\delta_\mathrm{f}} = \frac{25.74}{6.00} = 4.29$$
-
-Since the baseline fitness is 1, the increase in fitness resulting from a nuptial gift then becomes,
-
-$$\hat{\gamma} = \hat{\delta_{\mathrm{f}}} - 1 = 3.29.$$
-
-The value 3.29 was used to parameterise $\gamma$ for a set of simulations (Figure 4 in the main text).
-
-|                                 | Received nuptial gift | Received no nuptial gift |
-|---------------------------------|-----------------------|--------------------------|
-| Expected number of hatched eggs | $25.74 \pm 0.96$      | $6.00 \pm 2.1$           |
-
-Table 1: Estimates showing mean number of offspring produced by female *P.
-mirabilis* that ate nuptial gifts and females who did not.
-Means were calculated with raw data from @Tuni2013a and results are shown $\pm$ SE.
-
-\clearpage
-
-S6: Separate evolution of male search and female choice
--------------------------------------
-
-We used the individual-based simulation model (see Supporting Information S1) to unpack the effect of coevolution on the evolution of male search and female choice. 
+We used the individual-based simulation model to unpack the effect of coevolution on the evolution of male search and female choice. 
 Here we replicated the simulations shown in the main text under the condition where only one trait at a time was allowed to evolve and studied how this affected the trait evolution.
 
-First, we submitted a set of simulations wherein male search did not evolve, but was fixed at different values (see Fig. S6.1). 
+First, we submitted a set of simulations wherein male search did not evolve, but was fixed at different values. 
 Next, we ran the same set of simulations wherein male search evolved, but female choice was not possible. 
-The results thus show how each trait evolves in the absence of any coevolution (Fig. S6.1).
+The results thus show how each trait evolves in the absence of any coevolution (Fig. S4.1).
 
@@
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Figure S6.1: The separate evolution of male search and female choosiness as a function of nuptial gift search time.
+```{r echo = FALSE, eval = TRUE, fig.width = 6, fig.height = 6, fig.cap = "Figure S4.1: The separate evolution of male search and female choosiness as a function of nuptial gift search time.
 Points show where the lower 95% confidence interval of male search (blue) and female choosiness (red) exceeds zero, indicating evolution of nuptial gift search or choosiness.
-Each point includes data from $2 \\times 1600$ replicate simulations with identical starting conditions.
+Each point includes data from $2 \\times 3000$ replicate simulations with identical starting conditions.
 In the first batch, male search was constant and initialized at $T_{\\mathrm{m}} = \\alpha$, and female choice was evolving.
 In the second batch, male search was evolving, and there was no option for female choice.
-The parameters $T_{\\mathrm{f}}=2$, and $\\gamma$ and $\\alpha$ values were set within the range [0.1, 2.0] and [0.3, 1.7], respectively."}
+The parameters $T_{\\mathrm{f}}=2$, and $\\gamma$ and $\\alpha$ values were set within the range [0.1, 2.0] and [0.0, 2.0], respectively."}
 SUMM_m <- read.csv("inst/summary_male_evolving.csv");

### 2024-11-29 index.tex
Fixed up traits and manuscript. Traits are not binary anymore, but are diploid

--- 2024-06-15 ms_biorxiv.tex
@@
 \newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 multiplied by the rate at which mates with nuptial gifts are
-encountered. Importantly, selection can differ between the sexes,
-potentially causing sexual conflict. We test these results using an
-individual-based model applied to a system of nuptial gift-giving
-spiders, \emph{Pisaura mirabilis}, by estimating parameter values using
-experimental data from several studies. Our results provide a general
-framework for understanding when the evolution of nuptial gift-giving
-can occur and provide novel insight into the evolution of worthless
-nuptial gifts, occurring in multiple taxonomic groups with implications
-for understanding parental investment.
+encountered. Selection can differ between the sexes, potentially causing
+sexual conflict. We further investigate these results using an
+individual-based model inspired by a system of nuptial gift-giving
+spiders, \emph{Pisaura mirabilis}, by estimating the fitness benefit of
+nuptial gift-giving using experimental data from several studies. Our
+results provide a general framework for understanding when the evolution
+of nuptial gift-giving can occur and provide novel insight into the
+evolution of worthless nuptial gifts, occurring in multiple taxonomic
+groups with implications for understanding parental investment.
 
@@
 \protect\hyperlink{ref-Iwasa2022}{Iwasa \& Yamaguchi, 2022}), but a
-general framework describing the conditions necessary for nuptial
-gift-giving to be initially favoured by selection is needed to
+general framework describing the conditions under which nuptial
+gift-giving can be initially favoured by selection is needed to
 understand when gift-giving should evolve.
@@
 Nuptial gift-giving may allow males to increase fitness by acquiring
-additional mates, indirect benefits (by increasing the fitness of
-offspring), prolonged copulations, and success in sperm competition
+additional mates, indirect benefits (by increasing offspring fitness),
+prolonged copulations, and success in sperm competition
 (\protect\hyperlink{ref-Albo2013}{Albo \emph{et al.}, 2013};
@@
 interests of both sexes may not always fully overlap. This can cause
-sexual conflict, which is a difference in the evolutionary interest
-between sexes that occurs when interaction between sexes results in a
-situation where neither sex can achieve an optimal outcome
-(\protect\hyperlink{ref-Parker2006}{Parker, 2006}). That is, under some
-conditions, it might for example be optimal for males but not females to
-mate if females do not benefit from mating with males without nuptial
-gifts.
+sexual conflict, which is a difference in the fitness interests between
+sexes that occurs when an interaction results in a situation where
+individuals cannot both achieve an optimal outcome
+(\protect\hyperlink{ref-Parker2006}{Parker, 2006}). For example, under
+some conditions, it might be optimal for males but not females to mate
+if females do not benefit from mating with males without nuptial gifts.
 
@@
 of such a system is the nuptial gift-giving nursery-web spider
-\emph{Pisaura mirabilis} where males may court females with or without
+\emph{Pisaura mirabilis}, where males may court females with or without
 nuptial gifts (\protect\hyperlink{ref-Bristowe1926}{Bristowe \& Locket,
@@
 will favour the evolution of nuptial gift-giving. Importantly, we show
-that the threshold value differs for males and females. We test
-predictions of our analytical model by formulating an individual-based
-model, which further supports the main theoretical results of our
-analytical model. Further, we apply our model to an example system with
+that the threshold value differs for male searching and female
+choosiness. We complement the predictions of our analytical model by
+formulating an individual-based model, which further supports the main
+theoretical results. We apply our model to an example system with
 nuptial gifts, the nursery web spider \emph{Pisaura mirabilis}, where we
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{analytical-model}{%
-\subsection{Analytical model}\label{analytical-model}}
+\hypertarget{model}{%
+\section{Model}\label{model}}
 
@@
 produced by a female per reproductive cycle as \(\lambda\). Since
-females enter time-out after mating, this assumption is equivalent to
-assuming a system with sequential polyandry. For simplicity, we assume
-male time to replenish sperm is negligible, but males can spend some
-duration of time (\(T_{\mathrm{m}}\)) out of the mating pool searching
-for nuptial gifts.
+females enter time-out after mating, this is equivalent to assuming a
+system with sequential polyandry. For simplicity, we assume male time to
+replenish sperm is negligible, but males can spend some duration of time
+out of the mating pool searching for nuptial gifts. We define
+\(T_{\mathrm{m}}\) as the time until a gift is found by a searching
+male.
 
@@
 
-\hypertarget{criteria-for-male-search-and-female-choosiness}{%
-\subsection{Criteria for male search and female
-choosiness}\label{criteria-for-male-search-and-female-choosiness}}
-
-The probability \(G\) that a male succeeds in securing a nuptial gift is
-defined by,
-
-\begin{equation}
-G = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.
-\end{equation}
-
-In Eq. 1, \(\alpha\) defines the expected search time before
-encountering a nuptial gift. Thus, the probability of finding a nuptial
-gift is higher the more time \(T_{\mathrm{m}}\) is spent searching.
-During time-in, individuals encounter conspecifics at a rate of \(R\). A
-focal individual will therefore encounter conspecifics of the opposite
-sex at a rate of \(R/2\) if the ratio of males to females in the mating
-pool (\(\beta\)) is equal. More generally, males will be encountered at
-a rate of \(R\beta/(\beta+1)\), and females will be encountered at a
-rate of \(R/(\beta+1)\). An example of how the structure of the time-in
-time-out model applies to a system with nuptial gift-giving is given in
-Figure 1. We assume that mating with a nuptial gift increases the
-fitness of each offspring by an increment of \(\gamma\). We proceed to
-find the thresholds \(\gamma_{\mathrm{m}}\) and \(\gamma_{\mathrm{f}}\)
-above which males and females are favoured by selection to search for
-mates with nuptial gifts and exhibit choosiness for nuptial gifts,
-respectively. We show (see Methods) that the initial threshold value of
-\(\gamma\) (\(\gamma_{\mathrm{m}}\)) necessary for males to increase
-their fitness by investing time searching for a nuptial gift (time that
-could otherwise be spent searching for a mate) is,
-
-\begin{equation}
-\gamma_{\mathrm{m}} > \alpha \frac{R}{\beta + 1}.
-\end{equation}
-
-Inequality 2 means that if nuptial gifts are not abundant and thus
-require a long time to find (i.e., high \(\alpha\)), or if males
-encounter many females per unit time (i.e., high \(R / (1+\beta)\)),
-then the nuptial gift must result in a high fitness increment for
-selection to favour gift-searching. In general, when ineq. 2 is
-satisfied, we predict selection to favour the evolution of nuptial
-gift-giving.
-
-We can similarly predict the conditions for which there is selection for
-female choosiness. If \(\gamma\) is sufficiently high, then females
-increase their fitness by rejecting males without gifts and mating only
-with males that provide nuptial gifts. To illustrate, we assume that all
-males in a population search for a duration of \(T_{\mathrm{m}}\), in
-which case the threshold fitness increment for females
-(\(\gamma_{\mathrm{f}}\)) is,
-
-\begin{equation}
-\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}} R \left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}} \right)}.
-\end{equation}
-
-Inequality 3 shows that as offspring processing time
-(\(T_{\mathrm{f}}\)), mate encounter rate (\(R\beta / (\beta + 1)\)), or
-the probability of a male finding a nuptial gift
-(\(1 - \exp(-T_{\mathrm{m}}/\alpha)\) ) decreases, the threshold value
-of fitness above which selection will favour choosiness
-(\(\gamma_{\mathrm{f}}\)) increases. This can be understood intuitively
-by realising that rejecting a prospective male represents an opportunity
-cost for the female. This opportunity cost becomes small if many males
-with gifts are encountered, hence the appearance of the rate at which
-males with gifts are encountered in the denominator. Figure 2 shows how
-\(\gamma_{\mathrm{m}}\) and \(\gamma_{\mathrm{f}}\) change with
-increasing \(\alpha\). For \(\gamma_{\mathrm{f}}\), we assume that males
-search for the expected time required to obtain a nuptial gift
-(\(T_{\mathrm{m}} = \alpha\)). Note that \(\beta\) does not have a
-closed form solution given \(R\), \(T_{\mathrm{f}}\), and
-\(T_{\mathrm{m}}\), so \(\beta\) was calculated using recursion (see
-Methods).
+\hypertarget{analytical-model}{%
+\subsection{Analytical model}\label{analytical-model}}
+
+The probability that a male succeeds in securing a nuptial gift (\(G\))
+after a duration of \(T_{\mathrm{m}}\) is defined by,
+
+\[P(G) = 1 - e^{-\frac{1}{\alpha}T_{m}}.
+\tag{1}
+\]
+
+In Eq. 1, \(\alpha\) defines expected search time before encountering a
+nuptial gift. Thus, the probability of finding a nuptial gift is higher
+the more time is spent searching. During time-in, individuals encounter
+conspecifics at a rate of \(R\). A focal individual will therefore
+encounter conspecifics of the opposite sex at a rate of \(R/2\) if the
+ratio of males to females in the mating pool (\(\beta\)) is equal. More
+generally, males will be encountered at a rate of \(R\beta/(\beta+1)\),
+and females will be encountered at a rate of \(R/(\beta+1)\). An example
+of how the structure of the time-in time-out model applies to a system
+with nuptial gift-giving is given in Figure 1. We assume that mating
+with a nuptial gift increases expected offspring production by an
+increment of \(\gamma\). Mortality occurs for females and males in
+(\(\mu_{\mathrm{i,f}}\), \(\mu_{\mathrm{i,m}}\)) and out
+(\(\mu_{\mathrm{o,f}}\), \(\mu_{\mathrm{o,m}}\)) of the mating pool.
+Following Kokko \& Ots (\protect\hyperlink{ref-Kokko2006}{2006}), we
+assume \(m_{\mathrm{i,f}} = m_{\mathrm{o,f}} = 1\) and
+\(m_{\mathrm{i,m}} = m_{\mathrm{o,m}} = 1\).
+
+First, we find the fitness of males that search versus do not search for
+a nuptial gift. We then describe the fitness consequences of female
+choice to accept or reject males based on their provision of a nuptial
+gift. We can then calculate the thresholds \(\gamma_{\mathrm{m}}\) and
+\(\gamma_{\mathrm{f}}\) above which males and females are favoured by
+selection to search for nuptial gifts and exhibit choosiness for nuptial
+gifts, respectively.
+
+\emph{Male fitness}
+
+During time-out, males can search for a nuptial gift. Males can adopt
+one of two strategies; either search or do not search for a nuptial
+gift. Males with the searching strategy continue to search until they
+find a nuptial gift, while males that do not search immediately re-enter
+the mating pool. Consequently, time searching for a nuptial gift will
+come at the cost of mating opportunities but might increase offspring
+fitness. We therefore need to model the expected length of time spent
+outside of the mating pool for males that search for nuptial gifts
+(\(E[T_{\mathrm{m}}]\)), which equals \(\alpha\). We can integrate
+search time \(t\) over the rate at which nuptial gifts are encountered
+(\(\exp(-1/\alpha)\)) to show \(E[T_{\mathrm{m}}] = \alpha\),
+
+\[E[T_{\mathrm{m}}] = \int_{0}^{\infty}e^{- \frac{1}{\alpha}t}dt = \alpha.\]
+
+The rate at which a focal male that searches for a nuptial gift
+increases his fitness is therefore his reproductive output
+\(\lambda(1 + \gamma)\) divided by expected time spent searching for a
+nuptial gift (\(\alpha\)) plus time spent in the mating pool,
+\((\beta + 1)/R\),
+
+\[W_{\mathrm{M_{G}}} = \lambda \frac{1 + \gamma}{\alpha + \left( \frac{\beta + 1}{R} \right)}.\]
+
+In contrast, a male that does not search for a nuptial gift has fewer
+offspring, but spends less time outside of the mating pool,
+
+\[W_{\mathrm{M_{L}}} = \lambda \frac{1}{\left(\frac{\beta+1}{R} \right)} = \lambda \frac{R}{\beta + 1}.\]
+
+We can determine the conditions for which
+\(W_{\mathrm{M_{G}}} > W_{\mathrm{M_{L}}}\), isolating \(\gamma\) to
+find how large of a fitness benefit must be provided by the nuptial gift
+to make the search cost worthwhile, which simplifies to,
+
+\[\gamma_{\mathrm{m}} > \alpha \frac{R}{\beta + 1}.
+\tag{2}
+\]
+
+When this inequality holds, males are favoured to search until they find
+a nuptial gift, which would result in an average search time of
+\(\alpha\). If the male trait is instead continuous (i.e., males search
+for time period \(T_{\mathrm{m}}\)), it can be shown that the same
+threshold can be reached by evaluating the partial derivative of the
+male fitness function (Supporting Information S1). Hence, the thresholds
+are consistent under different assumptions concerning male searching
+strategy. Selection will cause males to search for nuptial gifts if the
+fitness increase to offspring exceeds the product of search time and
+female encounter rate.
+
+\emph{Female fitness}
+
+During time-out, females process offspring over a duration of
+\(T_{\mathrm{f}}\) (we assume that \(T_{\mathrm{f}} > \alpha\), else
+females are not the choosy sex). When females re-enter the mating pool,
+they encounter males at a rate of \(R\beta/(\beta + 1)\). If a female
+encounters a male with a nuptial gift, we assume that she will mate with
+him. But if a female encounters a male with no nuptial gift, then she
+might accept or reject the male. If she rejects the male, then she will
+remain in the mating pool. The rate at which a female encounters a male
+with a nuptial gift is,
+
+\[R_{\mathrm{F_{G}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right).\]
+
+Expected time spent in the mating pool before a focal female encounters
+a male with a gift will be \(1/R_{\mathrm{F_{G}}}\). The rate at which a
+female increases her fitness by being choosy and mating only when she
+encounters a male with a gift is,
+
+\[W_{f, g} = \lambda \frac{1 + \gamma}{T_{F} + \frac{1}{R_{\mathrm{F,G}}}}.
+\tag{4}
+\]
+
+The top of the right-hand side of Eq. 4 gives her fitness increase, and
+the bottom gives the total time it takes to obtain this fitness. The
+\(R_{\mathrm{F_{G}}}\) is inverted because it represents the expected
+time to encountering a male with a gift. We can expand Eq. 6,
+
+\[W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right)}}.\]
+
+If the focal female is not choosy and accepts the first male that she
+encounters, then the rate at which she increases her fitness is,
+
+\[W_{\mathrm{F_{G,L}}} = \lambda \frac{\left(1 + \gamma\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)}}.\]
+
+We then evaluate the conditions under which
+\(W_{\mathrm{F_{G}}} > W_{\mathrm{F_{G,L}}}\). We can isolate \(\gamma\)
+to determine how much offspring fitness must be increased to make
+choosiness beneficial (\(\gamma_{\mathrm{f}}\)),
+
+\[\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}} R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right)}.
+\tag{5}
+\]
+
+Note that that the expression
+\(R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right)\)
+defines the rate at which a female in the mating pool encounters males
+with nuptial gifts. Hence, female choosiness is ultimately determined by
+time spent out of the mating pool to process offspring
+(\(T_{\mathrm{f}}\)) and the rate at which a female in the mating pool
+encounters males with nuptial gifts.
+
+\emph{Operational sex ratio}
+
+We assume that the sex ratio is equal upon maturation. Given this, Kokko
+\& Monaghan (\protect\hyperlink{ref-Kokko2001}{2001}) show that the
+operational sex ratio depends on the probability of finding an
+individual in time-in,
+
+\[\beta = \frac{\int_{t = 0}^{\infty} P_{IM}(t)dt}{\int_{t = 0}^{\infty} P_{IF}(t)dt}.
+\tag{6}
+\]
+
+In Eq. 6, \(P_{IM}(t)\) and \(P_{IF}(t)\) are the probabilities of
+finding a male and female in time-in, respectively. There is no closed
+form solution to the operational sex ratio, so we used recursion to
+calculate \(\beta\) values for a given \(T_{\mathrm{f}}\),
+\(T_{\mathrm{m}}\), and \(R\) (see Supporting Information S2),
+
+\hypertarget{individual-based-model}{%
+\subsection{Individual-based model}\label{individual-based-model}}
+
+We formulate an individual-based time-in time-out simulation model to
+complement the predictions made by our analytical time-in time-out model
+above and further allow for coevolution between male search behaviour
+and female choosiness. Here we describe the details of initialisation,
+time-in (mating), time-out (reproduction and nuptial gift search), and
+mortality. We then summarise the simulations run and data collected.
+
+\emph{Initialisation}
+
+Before the first time step, a population of \(N = 1000\) individuals is
+initialised. Individuals are assigned to be female with a probability of
+\(0.5\), else male. Female offspring processing time for a focal
+individual \(i\) is fixed at \(T^{i}_{\mathrm{f}} = 2\). Each individual
+is initialised with a diploid genotype that underlies female rejection
+probability of gift-less males (\(\rho^{i}\)), and a diploid genotype
+that underlies male search time (\(T^{i}_{\mathrm{m}}\)). Alleles can
+take any real value and combine additively to determine \(\rho^{i}\) and
+\(T^{i}_{\mathrm{m}}\). For all simulations, initialised values are set
+to , \(\rho^{i} = 0\), and \(T^{i}_{\mathrm{m}} = 0\). All individuals
+are initialised outside of the mating pool in the first time step
+\(t = 1\). The first time step then proceeds with females immediately
+entering the mating pool and males either entering the mating pool or
+searching for nuptial gifts.
+
+\emph{Time-in}
+
+At the start of each time step, females and males in the mating pool
+remain in it. Females outside the mating pool enter the mating pool
+after processing offspring, and males enter it after searching for
+nuptial gifts (see `Time-out' below). Up to \(\Psi = N\psi\)
+interactions between individuals can occur in a single time step, where
+\(\psi\) is a scaling parameter. In each time step, \(\Psi\) pairs of
+individuals are selected at random to interact. For each interaction,
+two different individuals are randomly selected from the population with
+equal probability. If the selected individuals are of different sexes,
+and both are in the mating pool, then a mating encounter occurs. If the
+male does not have a nuptial gift, then a focal female \(i\) will reject
+him with a probability of \(\rho^{i}\); if rejection occurs, then both
+individuals stay in the mating pool. If rejection does not occur, or the
+male has a nuptial gift in the mating encounter, then the individuals
+mate. Females then leave the mating pool and enter time-out to process
+offspring, and males leave and enter time-out to potentially search for
+new nuptial gifts (note that females and males might re-enter the mating
+pool immediately within the same time step given sufficiently low search
+time; see Time-out below).
+
+\emph{Time-out}
+
+During time-out, offspring production and time outside of the mating
+pool are realised for each female by sampling from a Poisson
+distribution. A focal female \(i\) will produce
+\(\mathrm{Poisson}(\lambda)\) offspring if no nuptial gift was provided
+or \(\mathrm{Poisson}(\lambda + \gamma)\) if a gift was provided.
+Females remain outside of the mating pool to process offspring for
+\(\mathrm{Poisson}(T^{i}_{\mathrm{f}})\) time steps. Offspring are added
+to the population immediately, with one \(\rho^{i}\) and one
+\(T^{i}_{\mathrm{m}}\) allele sampled from each parent with complete
+recombination. Mutation occurs independently for each allele with a
+probability of \(\epsilon = 0.001\), and if mutation occurs, then a new
+allele value is sampled from a normal distribution mean centred on the
+existing value with a standard deviation of \(\sigma_{\epsilon} = 0.1\).
+Offspring sex is randomly assigned with equal probability as female or
+male. Female offspring are immediately placed in the mating pool, and
+male offspring are out of the mating pool to potentially search for
+nuptial gifts. After a female has spent
+\(\mathrm{Poisson}(T^{i}_{\mathrm{f}})\) time steps outside the mating
+pool, she will re-enter it.
+
+A focal male \(i\) outside the mating pool will enter it if he has
+searched for a fixed number of \(T^{i}_{\mathrm{m}}\) time steps, which
+is also sampled randomly from a Poisson distribution,
+\(\mathrm{Poisson}(T^{i}_{\mathrm{m}})\). If \(T^{i}_{\mathrm{m}} = 0\),
+then the male immediately returns to the mating pool (in the same time
+step). If \(T^{i}_{\mathrm{m}} > 0\), then the male must wait outside
+the mating pool for \(\mathrm{Poisson}(T^{i}_{\mathrm{m}})\) time steps,
+but will enter the mating pool with a nuptial gift with a probability,
+
+\[P(G^{i}) = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.\]
+
+Males must always spend \(\mathrm{Poisson}(T^{i}_{\mathrm{m}})\) time
+steps outside of the mating pool regardless of whether or not they are
+successful in obtaining a nuptial gift.
+
+\emph{Mortality}
+
+At the end of each time step, mortality occurs first with a fixed
+probability for all adults in the population, then with a probability
+caused by carrying capacity \(K = 1000\) applied to all individuals
+(adults and offspring). Mortality occurs in each time step with a fixed
+probability of \(\mu\) regardless of the sex of the individual or its
+position in or out of the mating pool. If after this fixed mortality is
+applied, the total population size \(N > K\), then individuals are
+removed at random with equal probability until \(N = K\). Following
+adult mortality, a new time step begins with newly added offspring
+becoming adults.
+
+\emph{Simulations}
+
+We ran simulations in which male search time and female choosiness
+evolved from an ancestral state of no searching and no choosiness. In
+all simulations, \(N\) was initialised at 1000 and \(K = 1000\).
+Simulations ran for \(t_{max} = 10000\) time steps. We set
+\(T_{\mathrm{f}} = 2\), \(\psi = 3\), and \(\lambda = 1\) for all
+simulations, and we simulated across a range of
+\(\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}\) and
+\(\gamma = \{0, 0.1, ..., 1.9, 2.0\}\) parameter values for 3000
+replicates. Summary statistics for mean trait values, population size,
+sex ratios, proportion of females and males in and out of the mating
+pool, and mean number of encounters per female and male within the
+mating pool were all calculated in the last time step. The C code used
+for simulating these IBMs also allows for the reporting of summary
+statistics in each time step. Additionally, it can simulate explicit
+space and individual movement through the landscape. A neutral evolving
+trait was also modelled to ensure that the code functioned as intended,
+and processes were compartmentalised into individual functions to
+facilitate code testing. All code is publicly available on GitHub
+(\url{https://github.com/bradduthie/nuptial_gift_evolution}).
+
+\emph{Application to gift-giving spiders}
+
+We can produce an estimate of the fitness increment obtained by females
+when receiving a gift (\(\hat{\gamma}\)) by using data on female
+\emph{P. mirabilis} egg production and hatching success
+(\protect\hyperlink{ref-Tuni2013a}{Tuni \emph{et al.}, 2013}). Tuni
+\emph{et al.} (\protect\hyperlink{ref-Tuni2013a}{2013}) found
+differences in egg production and hatching success in female \emph{P.
+mirabilis} under different feeding regimes. Assuming these differences
+in feeding regimes correspond to eating versus not eating nuptial gifts,
+the mean number of offspring produced by a female who eats nuptial gifts
+can be calculated. We calculate these means using raw data from Tuni
+\emph{et al.} (\protect\hyperlink{ref-Tuni2013a}{2013}) and find that
+mean offspring produced by females receiving nuptial gifts is
+\(25.74 \pm 0.96\), while offspring produced by females without a
+nuptial gift is \(6.00 \pm 2.1\). Consequently, the relative gain in
+fitness from receiving a nuptial gift for a female is estimated to be
+\(\hat{\delta_\mathrm{f}} = 25.74 / 6.00 = 4.29\). Since the baseline
+fitness is 1, the increase in fitness resulting from a nuptial gift then
+becomes \(\hat{\gamma} = \hat{\delta_{\mathrm{f}}} - 1 = 3.29.\)
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+Our model predicts 4 zones that are delineated by inequalities 2 and 5
+and describe the initial thresholds for the evolution of searching for
+nuptial gifts in males and choosiness for nuptial gifts in females.
+Figure 2a illustrates conditions under which no searching or choosiness
+evolves (zone A), only search (zone B) or choosiness (zone C) evolve, or
+both searching and choosiness evolve (zone D). Blue and red threshold
+lines in Figure 2 are defined by Eq. 2 and Eq. 5, respectively. Figure
+2b illustrates the expansion of zone B as encounter rate decreases,
+which is consistent with the results of our IBM (Figure 3).
 
@@
 \centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-3-1.pdf}
+\includegraphics{index_files/figure-latex/unnamed-chunk-3-1.pdf}
 \caption{Fitness thresholds above which males increase their fitness by
@@
 and males search and females are choosy (D). Arrows in panel a indicate
-the effect of increasing interaction rate (\(R\)), female time-out
+the effect of increasing encounter rate (\(R\)), female time-out
 (\(T_{\mathrm{f}}\)), and male search time (\(T_{\mathrm{m}}\)). As an
@@
 
-The analytical framework predicts 4 zones, which are delineated by
-inequalities 2 and 3 and describe the initial thresholds for favouring
-search of nuptial gifts in males and choosiness for nuptial gifts in
-females (Figure 2a). Consequently, the modelling framework gives a
-description of the conditions under which nuptial gift-giving is
-expected to occur (Figure 2a, Zone D) and the conditions under which
-only selection for male searching (Figure 2a, Zone B) or female
-choosiness (Figure 2a, Zone C) are predicted. These results therefore
-highlight the potential for sexual conflict over nuptial gift-giving.
-
-\hypertarget{evolution-of-male-search-and-female-choosiness}{%
-\subsection{Evolution of male search and female
-choosiness}\label{evolution-of-male-search-and-female-choosiness}}
-
-We used an individual-based model (IBM) to simulate the evolution of
-nuptial gift-giving and female choosiness from an ancestral condition in
-which neither exists. The IBM was written to satisfy the assumptions of
-our analytical time-in and time-out model as much as practical (see
-Supporting Information S1). Using the IBM, we modelled a
-spatially-implicit, finite population of females and males. At each time
-step, some individuals enter or remain within the mating pool (time-in),
-where they potentially interact and mate. After mating, males and
-females may leave the mating pool to search for nuptial gifts and to
-produce offspring, respectively (time-out). Mortality occurs with a
-fixed probability in each time step, then a ceiling regulation is
-applied to limit population growth (see Methods).
-
-The rates at which females are encountered by males
-\(R_{\mathrm{f},\mathrm{m}}\) and males with nuptial gifts
-\(R_{\mathrm{m_{G}}, \mathrm{f}}\) are encountered by females are both
-calculated directly from the IBM, thereby modelling how these rates
-might be estimated from empirical data, so the male threshold for
-increasing fitness by searching is,
-
-\begin{equation}
-\gamma_{\mathrm{m, IBM}} > \alpha R_{\mathrm{f},\mathrm{m}}.
-\end{equation}
-
-Similarly, female threshold for increasing fitness by choosiness is,
-
-\begin{equation}
-\gamma_{\mathrm{f, IBM}} > \frac{1}{T_{\mathrm{f}}R_{\mathrm{m_{G}}, \mathrm{f}}}.
-\end{equation}
-
-Consequently, the IBM and the analytical model differ slightly (e.g.,
-time is discrete in the IBM but continuous the analytical model, and in
-the IBM, a fitness increment is applied to the focal female in the form
-of birthrate increase rather than offspring fitness; see Supporting
-Information S1 for details). But the predicted thresholds are
-theoretically equivalent and yield predictions that are qualitatively
-the same (Figure 3).
+For males, if nuptial gifts are not abundant and thus require a long
+time to find (i.e., high \(\alpha\)), or if males encounter many females
+per unit time (i.e., high \(R / (1+\beta)\)), then the nuptial gift must
+result in a high fitness increment for selection to favour searching.
+For females, if \(\gamma\) is sufficiently high, fitness is increased by
+rejecting males without gifts and mating only with males that provide
+nuptial gifts. As offspring processing time (\(T_{\mathrm{f}}\)), mate
+encounter rate (\(R\beta / (\beta + 1)\)), or the probability of a male
+finding a nuptial gift (\(1 - \exp(-T_{\mathrm{m}}/\alpha)\) ) decrease,
+the threshold value of fitness above which selection will favour
+choosiness (\(\gamma_{\mathrm{f}}\)) increases. This can be understood
+intuitively by realising that rejecting a prospective male represents an
+opportunity cost for the female.
 
@@
 \centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-4-1.pdf}
+\includegraphics{index_files/figure-latex/unnamed-chunk-4-1.pdf}
 \caption{The coevolution of male search and female choosiness as a
@@
 search (blue) exceeds zero, indicating evolution of choosiness or
-nuptial gift search. Each point includes data from 3200 replicate
-simulations with identical starting conditions. Red and blue lines show
-thresholds above which the mathematical model predicts that females
-should be choosy and males should search, respectively (in agreement
-with Figure 2). Minor deviations between the analytical model and the
-simulation results are expected due to the finite population size, the
-substantial stochasticity inherent to the simulation model, and the
-potential for coevolution (for details, see Supporting Information S1).
-The number of individuals in the population remained at or near carrying
-capacity of \(K = 1000\). In each time step, up to 3000 total pair-wise
-interactions occurred. Expected female processing time was set to
+nuptial gift search. Each point includes data from 3000 replicate
+simulations with identical starting conditions. Zones are identified
+that correspond to areas where males search and females are choosy (D),
+males search but females are not choosy (B), and males do not search and
+females are not choosy (A), as also depicted in Figure 2. The number of
+individuals in the population remained at or near carrying capacity of
+\(K = 1000\). In each time step, up to 3000 total pair-wise interactions
+occurred. Expected female processing time was set to
 \(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
@@
 
-Male thresholds \(\gamma_{\mathrm{m, IBM}}\) given by ineq. 4 accurately
-predict the evolution of searching in the IBM across \(\alpha\) values,
-and the female threshold \(\gamma_{\mathrm{f, IBM}}\) (ineq. 5) predicts
-the evolution of female choice (Figure 3). In other words, IBM
-simulations demonstrate that nuptial gift search in males, and
-choosiness in females, will evolve from an ancestral state of no
-searching and no choosiness in similar parameter space (Figure 3) as
-predicted by the analytical model (Figure 2b). We further ran the IBM
-with realistic values of \(\gamma\), estimated using data from the
-\emph{P. mirabilis} system wherein choosiness among females, and nuptial
-gift search among males, occur (Figure 4). We found that our IBM
-predicts both the evolution of choosiness and nuptial gift searching
-observed in the \emph{P. mirabilis} system.
-
-\begin{figure}
-\centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-5-1.pdf}
-\caption{The joint evolution of male search and female choosiness using
-a nuptial gift fitness increment (\(\gamma\)) that was estimated from
-experimental data for the species \emph{Pisaura mirabilis} (mean
-\(\gamma = 3.29 \pm\) SE via propagation of error for estimates of
-nuptial feeding a non-nuptial feeding groups: {[}1.47; 8.32{]}). Points
-show where the 95\% confidence interval exceeds 0 for female choosiness
-(red) and male search (blue). Each point includes data from 100
-replicate simulations with identical starting conditions. The red line
-shows the threshold above which females should be choosy and the blue
-line shows the threshold above which males should search. As predicted
-by the analytical model, both male search and female choosiness evolved
-for a range of \(\gamma\) values around the empirical estimates. This
-occurs because these values result in a \(\gamma\) above the fitness
-threshold necessary for selection to favour male search of nuptial gifts
-(blue line) and female choosiness (red line). The number of individuals
-in the population remained at or near carrying capacity of \(K = 1000\).
-In each time step, up to 3000 total pair-wise interactions occurred.
-Female processing time was set to \(T_{\mathrm{f}}=2\) time steps, and
-\(\gamma\) and \(\alpha\) values in the {[}0.2, 2.0{]}, respectively,
-were used. The parameter \(\gamma\) was estimated as relative increase
-in offspring production such that \(\gamma\) is the factor by which
-fitness increases (relative to the baseline fitness) given a nuptial
-gift (See Supporting Information S5).}
-\end{figure}
+Individual-based model results recover zones A, B, and D (Figure 3). In
+other words, IBM simulations demonstrate that nuptial gift search in
+males, and choosiness in females, will evolve from an ancestral state of
+no searching and no choosiness in similar parameter space (Figure 3) as
+predicted by the analytical model (Figure 2b). Further, although it was
+not possible to parameterise our model for the \emph{P. mirabilis}
+system in detail, our calculated value of \(\hat{\gamma} = 3.29\) is
+consistent with the evolution of nuptial gift searching and choosiness
+recovered by our analytical model and IBM.
 
@@
 should give nuptial gifts if the value of a nuptial gift exceeds a
-threshold dependent on the encounter rate between males and females and
-the cost or time necessary to find or produce a nuptial gift (see ineq.
-2). This result makes intuitive sense because if males rarely encounter
-females, time searching for a gift is a minor cost relative to mate
-search time. If males encounter many females, it is not worth seeking
-nuptial gifts unless gifts are very valuable since the male will meet
-many prospective mates, and nuptial gift search time might come at a
-cost of decreased mating opportunities. In practice, male biased sex
-ratios will not necessarily favour male search for nuptial gifts if the
-female encounter rate is very high, so the key variable is how often
-males and females encounter each other. If the search time or cost of
-finding a nuptial gift is high, nuptial gifts must be very valuable
-before search is favoured by selection.
+threshold dependent on the encounter rate between females and males and
+the cost or time necessary to find or produce a nuptial gift. This
+result makes intuitive sense because if males rarely encounter females,
+time searching for a gift is a minor cost relative to mate search time.
+If males encounter many females, it is not worth seeking nuptial gifts
+unless gifts are very valuable since the male will meet many prospective
+mates, and nuptial gift search time might come at a cost of decreased
+mating opportunities. In practice, male biased sex ratios will not
+necessarily favour male search for nuptial gifts if the female encounter
+rate is very high, so the key variable is how often males and females
+encounter each other. If the search time or cost of finding a nuptial
+gift is high, nuptial gifts must be very valuable before search is
+favoured by selection. We also show that females should express
+choosiness for males with nuptial gifts if the value of the nuptial gift
+exceeds the inverse of the product of offspring processing time and
+encounter rate with males holding gifts.
 
@@
 
-Importantly, we show that the threshold nuptial gift value at which
-females are favoured to express choosiness for nuptial gifts is rarely
-equivalent to the threshold value at which males are favoured to search
-for nuptial gifts, potentially leading to sexual conflict
+We show that the threshold nuptial gift value at which females are
+favoured to express choosiness for nuptial gifts is rarely equivalent to
+the threshold value at which males are favoured to search for nuptial
+gifts, potentially leading to sexual conflict
 (\protect\hyperlink{ref-Arnqvist2005a}{Arnqvist \& Rowe, 2005};
@@
 Zone C). This will lead to mate encounters in which gift-less males will
-benefit from mating, but females will not. In many systems, ecological
-variables such as search time required to find a nuptial gift will
-likely depend on prey abundance, which can vary substantially with time
-in some species with nuptial gift-giving
-(\protect\hyperlink{ref-Ghislandi2018}{Ghislandi \emph{et al.}, 2018}).
-Since several ecological variables likely affect the value of these
-thresholds, our results can be seen as providing some formalised
-description of why nuptial gift-giving only occurs in some but not all
-systems.
+benefit from mating, but females will not (i.e., evolutionary interests
+do not always overlap with respect to mating strategy between the
+sexes). In many systems, ecological variables such as search time
+required to find a nuptial gift will likely depend on prey abundance,
+which can vary substantially with time in some species with nuptial
+gift-giving (\protect\hyperlink{ref-Ghislandi2018}{Ghislandi \emph{et
+al.}, 2018}). Since several ecological variables likely affect the value
+of these thresholds, our results can be seen as providing some
+formalised description of why nuptial gift-giving only occurs in some
+but not all systems.
 
@@
 female threshold for choosiness with respect to \(\gamma\) drops such
-that male search and female choosiness are favoured at lower \(\gamma\)
-(see Supporting Information S2). If \(T_{\mathrm{f}}\) is sufficiently
-high, then an initially rare gift-giving trait might be favoured by
-selection even if the fitness benefit of a nuptial gift is low. The
-effect that nuptial gifts have on fitness might vary across species, or
-even populations. Effects on female fecundity have been estimated in
-crickets, fireflies, butterflies, and spiders, but these estimates vary
-considerably between species suggesting a large positive effect to no
-effect at all (\protect\hyperlink{ref-Bergstrom2002}{Bergström \&
-Wiklund, 2002}; \protect\hyperlink{ref-Rooney2002}{Rooney \& Lewis,
-2002}; \protect\hyperlink{ref-Maxwell2018}{Maxwell \& Prokop, 2018};
+that male search and female choosiness are favoured at lower \(\gamma\).
+If \(T_{\mathrm{f}}\) is sufficiently high, then an initially rare
+gift-giving trait might be favoured by selection even if the fitness
+benefit of a nuptial gift is low. The effect that nuptial gifts have on
+fitness might vary across species, or even populations. Effects on
+female fecundity have been estimated in crickets, fireflies,
+butterflies, and spiders, but these estimates vary considerably between
+species suggesting a large positive effect to no effect at all
+(\protect\hyperlink{ref-Bergstrom2002}{Bergström \& Wiklund, 2002};
+\protect\hyperlink{ref-Rooney2002}{Rooney \& Lewis, 2002};
+\protect\hyperlink{ref-Maxwell2018}{Maxwell \& Prokop, 2018};
 \protect\hyperlink{ref-Gao2019}{Gao \emph{et al.}, 2019}).
@@
 processing time (\(T_{\mathrm{f}}\)), and the fitness increment of a
-nuptial gift for offspring fitness (\(\gamma\)). It then derives the
+nuptial gift for reproductive output (\(\gamma\)). It then derives the
 threshold \(\gamma\) values above which males increase their fitness by
@@
 (compare Figure 2b versus Figure 3), but differences between the two
-models inevitably lead to quantitative differences for
-\(\gamma_{\mathrm{m}}\) and \(\gamma_{\mathrm{f}}\) thresholds. For
-example, \(\gamma_{\mathrm{f}}\) increased more rapidly with increasing
+models inevitably lead to quantitative differences. For example,
+\(\gamma_{\mathrm{f}}\) increased more rapidly with increasing
 \(\alpha\) in the IBM compared to the analytical model. Some differences
@@
 gift-giving will evolve as given by the inequalities we derive.
+
+Kokko \& Mappes (\protect\hyperlink{ref-Kokko2013}{2013}) considered the
+evolution of female choosiness as a function of mating and mortality
+rates and found that choosiness may generally be a costly trait which is
+not always expected to evolve. Our results suggest that this is also the
+case when coevolution with the relevant male trait is taken into
+account. Numerous studies have modelled mate choice as a function of a
+single variable or effect (for review, see
+\protect\hyperlink{ref-Edward2015}{Edward, 2014}), such as direct
+benefits, indirect benefits or so-called chase-away sexual selection
+(\protect\hyperlink{ref-Holland1998}{Holland \& Rice, 1998};
+\protect\hyperlink{ref-Kokko2003}{Kokko \emph{et al.}, 2003}). Our
+results describe the evolution of mating choice from a different
+perspective by taking ecological variables and coevolution into account
+at the same time.
 
@@
 exhibit preference for nuptial gifts (zone B of Figure 2).
-Fascinatingly, an example of such system has been documented by a recent
+Interestingly, an example of such system has been documented by a recent
 study of the genus \emph{Trechaleoides}, which contains two species with
@@
 
-The simulations parameterised with an experimentally estimated value of
-\(\gamma\) showed evolution of nuptial gift searching in males and
-choosiness for nuptial gifts in females. The model thus predicts that
-\emph{P. mirabilis} living under conditions with the estimated fitness
-value of nuptial gifts should exhibit both search for nuptial gifts and
-choosiness for males with nuptial gifts, and this is what is observed in
-empirical populations. Parameterising \(\gamma\) with data from
-experimental studies may only yield a rough approximation of the true
-\(\gamma\). This is because the estimated value of \(\gamma\) is based
-on data from current populations (rather than ancestral populations,
-which are being simulated), and because the literature is inconclusive
-as to how much (if any) effect nuptial gifts have on female fitness
+For experimentally estimated value of \(\gamma\), simulations showed
+evolution of nuptial gift searching in males and choosiness for nuptial
+gifts in females. The model thus predicts that \emph{P. mirabilis}
+living under conditions with the estimated fitness value of nuptial
+gifts should exhibit both search for nuptial gifts and choosiness for
+males with nuptial gifts, and this is what is observed in empirical
+populations. Parameterising \(\gamma\) with data from experimental
+studies may only yield a rough approximation of the true \(\gamma\).
+This is because the estimated value of \(\gamma\) is based on data from
+current populations (rather than ancestral populations, which are being
+simulated), and because the literature is inconclusive as to how much
+(if any) effect nuptial gifts have on female fitness
 (\protect\hyperlink{ref-Maxwell2018}{Maxwell \& Prokop, 2018}). The
@@
 
-Our model assumes something akin to sequential polyandry. That is, a
-system wherein female mating and reproduction with multiple males occurs
-in sequence, rather than multiple matings occurring before reproduction.
-In some systems with nuptial gift-giving, females have been documented
-to mate multiple times before reproduction occurs, including the genus
-of bark lice \emph{Neotrogla}
-(\protect\hyperlink{ref-Kamimura2021}{Kamimura \emph{et al.}, 2021}),
-and even our example system of \emph{P. mirabilis} where females will
-sometimes engage in multiple mating before reproducing, especially if
-starved because multiple mating may result in more nuptial gifts
-(\protect\hyperlink{ref-Toft2015}{Toft \& Albo, 2015};
+Our model assumes sequential polyandry. That is, a system wherein female
+mating and reproduction with multiple males occurs in sequence, rather
+than multiple matings occurring before reproduction. In some systems
+with nuptial gift-giving, females have been documented to mate multiple
+times before reproduction occurs, including the genus of bark lice
+\emph{Neotrogla} (\protect\hyperlink{ref-Kamimura2021}{Kamimura \emph{et
+al.}, 2021}), and even our example system of \emph{P. mirabilis} where
+females will sometimes engage in multiple mating before reproducing,
+especially if starved because multiple mating may result in more nuptial
+gifts (\protect\hyperlink{ref-Toft2015}{Toft \& Albo, 2015};
 \protect\hyperlink{ref-Matzke2022}{Matzke \emph{et al.}, 2022}). It is
@@
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-\hypertarget{model}{%
-\subsection{Model}\label{model}}
-
-Here we first present more detail for the derivation of fitness
-threshold values \(\gamma_{\mathrm{m}}\) and \(\gamma_{\mathrm{f}}\). We
-then present IBM simulations (see Supporting Information S1 for full
-details). Code for simulations is available on GitHub (see ``Data
-availability'').
-
-\hypertarget{derivation-of-fitness-thresholds}{%
-\subsection{Derivation of fitness
-thresholds}\label{derivation-of-fitness-thresholds}}
-
-We use a time-in and time-out model in which females and males spend
-some time searching for a mate (time-in) followed by a period of cool
-down outside the mating pool (time-out; Figure 1).
-
-After mating, females must spend some time processing offspring
-(\(T_{\mathrm{f}}\)). Male time to replenish sperm is assumed to be
-negligible, but males can spend time out of the mating pool
-(\(T_{\mathrm{m}}\)) to search for a nuptial gift. When males return
-from time-out, they encounter females with some probability that is a
-function of the rate at which an individual encounters conspecifics
-(\(R\)) and the sex ratio (\(\beta\); males/females). Mortality occurs
-for females and males in (\(\mu_{\mathrm{i,f}}\),
-\(\mu_{\mathrm{i,m}}\)) and out (\(\mu_{\mathrm{o,f}}\),
-\(\mu_{\mathrm{o,m}}\)) of the mating pool. Following Kokko \& Ots
-(\protect\hyperlink{ref-Kokko2006}{2006}), we assume
-\(m_{\mathrm{i,f}} = m_{\mathrm{o,f}} = 1\) and
-\(m_{\mathrm{i,m}} = m_{\mathrm{o,m}} = 1\). While this choice is
-arbitrary, we conducted a sensitivity analysis which shows that the
-mortality parameters have no influence on the propensity for male search
-and female choice to evolve (Supporting Information S2). First, we
-describe the fitness consequences of male search time for a nuptial
-gift. We then describe the fitness consequences of female choice to
-accept or reject males based on their provision of a nuptial gift.
-
-\hypertarget{male-fitness}{%
-\subsection{Male fitness}\label{male-fitness}}
-
-During time-out, males have the opportunity to search for a nuptial
-gift. Males can adopt one of two strategies; either search or do not
-search for a nuptial gift. Males with the former strategy continue to
-search until they find a nuptial gift, while males that do not search
-will immediately re-enter the mating pool. In this case, time searching
-for a nuptial gift will come at the cost of mating opportunities but
-might increase offspring fitness. We therefore need to model the
-expected length of time \(E[T_{\mathrm{m}}]\) spent outside of the
-mating pool for males that search for nuptial gifts, which is simply
-\(\alpha\). Note that we can integrate search time \(t\) over the rate
-at which nuptial gifts are encountered (\(\exp(-1/\alpha)\)) to show
-\(E[T_{\mathrm{m}}] = \alpha\),
-
-\[E[T_{\mathrm{m}}] = \int_{0}^{\infty}e^{- \frac{1}{\alpha}t}dt = \alpha.\]
-
-The rate at which a focal male that searches for a nuptial gift
-(\(\mathrm{M_{G}}\)) increases his fitness is therefore the fitness of
-his offspring \((1 + \gamma)\) divided by expected time spent searching
-for a nuptial gift (\(\alpha\)) plus time spent in the mating pool,
-\((\beta + 1)/R\) (recall that females produce \(\lambda\) offspring),
-
-\[W_{\mathrm{M_{G}}} = \lambda \frac{1 + \gamma}{\alpha + \left( \frac{\beta + 1}{R} \right)}.\]
-
-In contrast, a male that does not search for a nuptial gift
-(\(\mathrm{M_{L}}\)) has offspring with lower fitness, but spends less
-time outside of the mating pool,
-
-\[W_{\mathrm{M_{L}}} = \lambda \frac{1}{\left(\frac{\beta+1}{R} \right)} = \lambda \frac{R}{\beta + 1}.\]
-
-We can then determine the conditions for which
-\(W_{\mathrm{M_{G}}} > W_{\mathrm{M_{L}}}\), isolating \(\gamma\) to
-find how large of a fitness benefit must be provided by the nuptial gift
-to make the search cost worthwhile, which simplifies to ineq. 2. When
-this inequality holds, males are favoured to search until they find a
-nuptial gift, which would result in an average search time of
-\(\alpha\). When the male trait is continuous (i.e., males search for
-time period \(T_{\mathrm{m}}\)), it can be shown that the same threshold
-can be reached by evaluating the partial derivative of the male fitness
-function (Supporting Information S3). Hence, the thresholds are
-consistent under different assumptions concerning male searching
-strategy. Selection will cause males to search for nuptial gifts if the
-fitness increase to offspring exceeds the product of search time and
-female encounter rate.
-
-\hypertarget{female-fitness}{%
-\subsection{Female fitness}\label{female-fitness}}
-
-During time-out, females process offspring over a duration of
-\(T_{\mathrm{f}}\) (we assume that \(T_{\mathrm{f}} > \alpha\), else
-females are not the choosy sex). When females re-enter the mating pool,
-they encounter males at a rate of \(R\beta/(\beta + 1)\). If a female
-encounters a male with a nuptial gift, we assume that she will mate with
-him. But if a female encounters a male with no nuptial gift, then she
-might accept or reject the male. If she rejects the male, then she will
-remain in the mating pool. The rate at which a female encounters a male
-with a nuptial gift is,
-
-\[R_{\mathrm{F_{G}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right).\]
-
-We can similarly model the rate at which a female encounters a gift-less
-male,
-
-\[R_{\mathrm{F_{L}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(e^{-\frac{1}{\alpha}T_{m}}\right).\]
-
-Note that we can recover the rate at which a female encounters any male,
-
-\[R \left(\frac{\beta}{\beta + 1}\right) = R \left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + R \left(\frac{\beta}{\beta + 1}\right) \left(e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right).\]
-
-If \(R_{\mathrm{F_{G}}}\) is sufficiently high and
-\(R_{\mathrm{F_{L}}}\) is sufficiently low, then finding a male with a
-gift will be easier than finding a male without one. Also, the expected
-time spent in the mating pool before a focal female encounters a male
-with a gift will be \(1/R_{\mathrm{F_{G}}}\), while the expected time
-spent in the mating pool before a focal female encounters any male will
-be \(1 / (R_{\mathrm{F_{G}}} + R_{\mathrm{F_{L}}})\). Finally, the rates
-at which a female encounters males with and without a gift,
-\(R_{\mathrm{F_{G}}}\) and \(R_{\mathrm{F_{L}}}\), are different from
-the probabilities that a male encounter has or does not have a gift. The
-rate of encounter is no longer relevant in this case because we are
-assuming that an encounter has occurred. Hence, the probability of an
-encountered male having a gift is simply,
-
-\[P(G) = \frac{1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}} = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
-
-Similarly, the probability of an encountered male not having a gift is
-simply,
-
-\[P(L) = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
-
-The rate at which a female increases her fitness by being choosy and
-mating only when she encounters a male with a gift is,
-
-\begin{equation}
-W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}}} + \frac{1}{\mathrm{F_{G}}}.
-\end{equation}
-
-The top of the right-hand side of Eq. 6 gives the fitness increase, and
-the bottom gives the total time it takes to obtain this fitness. The
-\(R_{\mathrm{F_{G}}}\) is inverted because it represents the expected
-time to encountering a male with a gift. We can expand Eq. 6,
-
-\[W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right)}}.\]
-
-If the focal female is not choosy and accepts the first male that she
-encounters, then the rate at which she increases her fitness is,
-
-\[W_{\mathrm{F_{G,L}}} = \lambda \frac{\left(1 + \gamma\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)}}.\]
-
-We then evaluate the conditions under which
-\(W_{\mathrm{F_{G}}} > W_{\mathrm{F_{G,L}}}\). We isolate \(\gamma\) to
-determine how much offspring fitness must be increased to make
-choosiness beneficial (\(\gamma_{\mathrm{f}}\)),
-
-\[\gamma_{\mathrm{f}} > \frac{1 + \frac{1}{\beta}}{D T_{f} \left(1 - e^{-1\frac{1}{\alpha}T_{m}}\right)}.\]
-
-The above can be expressed as Eq. 7 below,
-
-\begin{equation}
-\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}}} R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right).
-\end{equation}
-
-Note that that the expression
-\(R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right)\)
-defines the rate at which a female in the mating pool encounters males
-with nuptial gifts. Hence, female choosiness is ultimately determined by
-time spent out of the mating pool to process offspring
-(\(T_{\mathrm{f}}\)) and the rate at which a female in the mating pool
-encounters males with nuptial gifts.
-
-\hypertarget{operational-sex-ratio}{%
-\subsection{Operational sex ratio}\label{operational-sex-ratio}}
-
-We assume that the sex ratio is equal upon maturation. Given this, Kokko
-\& Monaghan (\protect\hyperlink{ref-Kokko2001}{2001}) show that the
-operational sex ratio depends on the probability of finding an
-individual in time-in,
-
-\begin{equation}
-\beta = \frac{\int_{t = 0}^{\infty} P_{IM}(t)dt}{\int_{t = 0}^{\infty} P_{IF}(t)dt}.
-\end{equation}
-
-In Eq. 8, \(P_{IM}(t)\) and \(P_{IF}(t)\) are the probabilities of
-finding a male and female in time-in, respectively. There is no closed
-form solution to the operational sex ratio, so we used recursion to
-calculate \(\beta\) values for a given \(T_{\mathrm{f}}\),
-\(T_{\mathrm{m}}\), and \(R\) (see Supporting Information S4),
-
-\hypertarget{individual-based-model}{%
-\subsection{Individual-based model}\label{individual-based-model}}
-
-We formulate an individual-based simulation model to test whether the
-predictions made by the analytical time-in time-out model are
-qualitatively the same under a similar simulation model. We use the
-individual-based model to test whether the prediction hold in finite
-populations. The IBM was written in C. All details of the
-initialisation, parameterisation and the specific simulations which we
-run, are described in Supporting Information S1.
-
-We use available experimental data on the effect of nuptial gifts on
-female offspring production to estimate the key parameter \(\gamma\)
-(fitness increment from nuptial gift) and conducted a series of
-simulations where \(\gamma\) was parameterised using this estimated
-value. Details of the estimation of \(\gamma\) are described in
-Supporting Information S5. Separate evolution of male search and female
-choice (i.e., without co-evolution) is simulated in Supporting
-Information S6.
-
 \textbf{Author contributions:} APC and ABD conceived the study. ABD
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Edward2015}{}}%
+Edward, D.A. (2014) \href{https://doi.org/10.1093/beheco/aru142}{The
+description of mate choice}. \emph{Behavioral Ecology}, \textbf{26},
+301--310.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Engqvist2015}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Holland1998}{}}%
+Holland, B. \& Rice, W.R. (1998) Perspective: Chase-away sexual
+selection: Antagonistic seduction versus resistance. \emph{Evolution},
+\textbf{52}, 1--7.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Iwasa2022}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Kokko2003}{}}%
+Kokko, H., Brooks, R., Jennions, M.D. \& Morley, J. (2003) The evolution
+of mate choice and mating biases. \emph{Proceedings of the Royal Society
+of London. Series B: Biological Sciences}, \textbf{270}, 653--664.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kokko2013}{}}%
+Kokko, H. \& Mappes, J. (2013) Multiple mating by females is a natural
+outcome of a null model of mate encounters. \emph{Entomologia
+Experimentalis et Applicata}, \textbf{146}, 26--37.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Kokko2001}{}}%
@@
 
-\begin{longtable}[]{@{}ll@{}}
-\toprule
-Information & Page \\
-\midrule
-\endhead
-S1: Description of the individual-based simulation model & 18 \\
-S2: Sensitivity analysis of mortality parameters in IBM & 20 \\
-S3: Alternative derivation of male fitness threshold & 29 \\
-S4: Operational sex ratio & 32 \\
-S5: Estimation of key model parameter using experimental data & 33 \\
-S6: Separate evolution of male search and female choice & 34 \\
-\bottomrule
-\end{longtable}
-
-\clearpage
-
-\hypertarget{s1-description-of-the-individual-based-simulation-model}{%
-\subsection{S1: Description of the individual-based simulation
-model}\label{s1-description-of-the-individual-based-simulation-model}}
-
-Here we describe the details of initialisation, time-in (mating),
-time-out (reproduction and nuptial gift search), and mortality. We then
-summarise the simulations run and data collected.
-
-\emph{Initialisation}
-
-Before the first time step, a population of \(N = 1000\) individuals is
-initialised. Individuals are assigned unique IDs, and each is assigned
-to be female with a probability of \(0.5\), else male. Each individual
-\(i\) is initialised with a starting value of female offspring
-processing time (\(T^{i}_{\mathrm{f}}\)), rejection probability of
-gift-less males (\(\rho^{i}\)), and male search time
-(\(T^{i}_{\mathrm{m}}\)). For all simulations, initialised values are
-set to \(T^{i}_{\mathrm{f}} = 2\), \(\rho^{i} = 0\), and
-\(T^{i}_{\mathrm{m}} = 0\). All individuals are initalised outside of
-the mating pool in the first time step \(t = 1\). The first time step
-then proceeds with females immediately entering the mating pool and
-males either entering the mating pool or searching for nuptial gifts.
-
-\emph{Time-in}
-
-At the start of each time step, females and males in the mating pool
-remain in it. Females will enter the mating pool after processing
-offspring, and males will enter it after searching for nuptial gifts
-(see `Time-out' below). Up to \(\Psi = N\psi\) interactions between
-individuals can occur in a single time step, where \(N\) is population
-size and \(\psi\) is a scaling parameter. In each time step, \(\Psi\)
-pairs of individuals are selected at random to interact. For each
-interaction, two different individuals are randomly selected from the
-population with equal probability. If the selected individuals are of
-different sexes, and both are in the mating pool, then a mating
-encounter occurs. If the male does not have a nuptial gift, then the
-female will reject him with a probability of \(\rho^{i}\); if rejection
-occurs, then both individuals stay in the mating pool. If rejection does
-not occur, or the male has a nuptial gift in the mating encounter, then
-the individuals mate. Females leave the mating pool and enter time-out
-to process offspring, and males leave and enter time-out to potentially
-search for new nuptial gifts (note that females and males might re-enter
-the mating pool immediately within the same time step given sufficiently
-low search time; see Time-out below).
-
-\emph{Time-out}
-
-During time-out, offspring production and time outside of the mating
-pool are realised for each female by sampling from a Poisson
-distribution. A focal female \(i\) will produce \(Poisson(\lambda)\)
-offspring if no nuptial gift was provided or
-\(Poisson(\lambda + \gamma)\) if a gift was provided. Females remain
-outside of the mating pool to process offspring for
-\(Poisson(T^{i}_{\mathrm{f}})\) time steps. Offspring are added to the
-population immediately, with \(\rho^{i}\) and \(T^{i}_{\mathrm{m}}\)
-values that are the average of each parent plus some normally
-distributed error \(\epsilon_{R}\) and \(\epsilon_{T_{\mathrm{m}}}\).
-For example,
-
-\[T^{\mathrm{offspring}}_{\mathrm{m}} \sim \frac{T^{\mathrm{mother}}_{\mathrm{m}}  + T^{\mathrm{father}}_{\mathrm{m}}}{2} + N\left(0, \epsilon_{T_{\mathrm{m}}} \right).\]
-
-The variation generated by \(\epsilon\) values simulates mutation upon
-which selection for traits can act. In all simulations, \(\epsilon = 0\)
-if a trait is fixed and \(\epsilon = 0.01\) if the trait evolves.
-Offspring sex is randomly assigned with equal probability as female or
-male. Female offspring are immediately placed in the mating pool, and
-male offspring are out of the mating pool to potentially search for
-nuptial gifts. After a female has spent \(T^{i}_{\mathrm{f}}\) time
-steps outside the mating pool, she will re-enter it.
-
-A focal male \(i\) outside the mating pool will enter it if he has
-searched for a fixed number of \(T^{i}_{\mathrm{m}}\) time steps, which
-is also sampled randomly from a Poisson distribution,
-\(Poisson(T^{i}_{\mathrm{m}})\). If \(T^{i}_{\mathrm{m}} = 0\), then the
-male immediately returns to the mating pool (in the same time step). If
-\(T^{i}_{\mathrm{m}} > 0\), then the male must wait outside the mating
-pool for \(Poisson(T^{i}_{\mathrm{m}})\) time steps, but will enter the
-mating pool with a nuptial gift with a probability,
-
-\[P(G^{i}) = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.\]
-
-Males must always spend \(T^{i}_{\mathrm{m}}\) time steps outside of the
-mating pool regardless of whether or not they are successful in
-obtaining a nuptial gift.
-
-\emph{Mortality}
-
-At the end of each time step, mortality occurs first with a fixed
-probability for all adults in the population, then with a probability
-caused by carrying capacity \(K\) applied to all individuals (adults and
-offspring). Mortality occurs in each time step with a fixed probability
-of \(\mu\) regardless of the sex of the individual or its position in or
-out of the mating pool. If after this fixed mortality is applied, the
-total population size \(N > K\), then individuals are removed at random
-with equal probability until \(N = K\). Following adult mortality, a new
-time step begins with newly added offspring becoming adults.
-
-\emph{Simulations}
-
-We ran simulations in which male search time and female choosiness
-evolved from an ancestral state of no searching and no choosiness. In
-all simulations, \(N\) was initialised at 1000 and \(K = 1000\).
-Simulations ran for \(t_{max} = 40000\) time steps. We set
-\(T_{\mathrm{f}} = 2\), \(\psi = 3\), and \(\lambda = 1\) for all
-simulations, and we simulated across a range of
-\(\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}\) and
-\(\gamma = \{0, 0.1, ..., 1.9, 2.0\}\) parameter values for 3200
-replicates. Summary statistics for mean trait values, population size,
-sex ratios, proportion of females and males in and out of the mating
-pool, and mean number of encounters per female and male within the
-mating pool were all calculated in the last time step. The C code used
-for simulating these IBMs also allows for the reporting of statistics in
-each time step. Additionally, it can simulate explicit space and
-individual movement through the landscape. A neutral evolving trait was
-also modelled to ensure that the code functioned as intended, and
-processes were compartmentalised into individual functions to facilitate
-code testing. All code is publicly available on GitHub
-(\url{https://github.com/bradduthie/nuptial_gift_evolution}).
-
-A set of simulations with a value of \(\gamma\) calculated from
-empirical data was also conducted (100 replicates). Here, \(\gamma\) was
-parameterised using data on egg production as a function of eating
-nuptial gifts (see below). Additional simulation sets with lower and
-upper bounds of the estimated \(\gamma\) were subsequently run. In the
-simulation sets with experimentally derived parameter values, all other
-parameters were identical to previous simulation batches.
-
-We can produce an estimate of the fitness increment obtained by females
-when receiving a gift (\(\hat{\gamma}\)) by using data on female
-\emph{P. mirabilis} egg production and hatching success under different
-feeding regimes from (\protect\hyperlink{ref-Tuni2013a}{Tuni \emph{et
-al.}, 2013}). Tuni \emph{et al.}
-(\protect\hyperlink{ref-Tuni2013a}{2013}) found differences in egg
-production and hatching success in female \emph{P. mirabilis} under
-different feeding regimes. Assuming these differences in feeding regimes
-correspond to eating versus not eating nuptial gifts, the mean number of
-offspring produced by a female who eats nuptial gifts can be calculated
-(Table 1).
-
-\clearpage
-
-\hypertarget{s2-sensitivity-analysis-of-parameters-in-ibm}{%
-\subsection{S2: Sensitivity analysis of parameters in
-IBM}\label{s2-sensitivity-analysis-of-parameters-in-ibm}}
-
-We investigated the sensitivity of our results to individual mortality
-during time-in (\(\mu_{\mathrm{in}}\)) and time-out
-(\(\mu_{\mathrm{out}}\)), female processing time (\(T_{\mathrm{f}}\)),
-potential for interactions between conspecifics (\(\psi\)), and
-initialised male search time (\(T_{\mathrm{m}}\)). Across all of these
-simulations, there were challenges with statistical power. Evidence for
-the evolution of male search (blue points in figures) and female
-choosiness (red points in figures) was determined by the lower 95\%
-bootstrapped confidence interval of \(T_{\mathrm{m}}\) and
-\(T_{\mathrm{f}}\) values being greater than zero, respectively. This
-required a lot of replicate simulations in the main text (Figure 3),
-especially for values just above predicted thresholds and for female
-choosiness. Computation time was a limiting factor, even using a
-compiled language (C) and with access to a computing cluster. Absence of
-points above threshold values are not necessarily evidence that
-evolution of male search or female choosiness is not predicted to evolve
-in these regions of parameter space, but it does indicate that evolution
-of these traits is not necessarily assured given the stochasticity
-inherent to the IBM. Additional simulations can be conducted using the C
-code in the `src' folder of the GitHub repository
-(\url{https://github.com/bradduthie/nuptial_gift_evolution}). Below, we
-explain the parameter values used in the sensitivity analysis in more
-detail.
-
-\emph{Mortality}
-
-We conducted a sensitivity analysis of the effect of the mortality
-parameters \(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\) (the
-probability of mortality in time-in and time-out, respectively, which we
-assumed to be equal for all individuals) on the evolution of male search
-and female choice using the IBM (See S1). The results revealed no
-correlation between the value of the mortality parameters and the
-evolution of male search or female choice (Fig. S2.1).
-
-\emph{Female processing time}
-
-We also conducted a sensitivity analysis of female processing time
-\(T_{\mathrm{f}}\). To do this, we ran simulations at default values,
-but with \(T_{\mathrm{f}} = 0.4\) (Figure S4.2) and
-\(T_{\mathrm{f}} = 10.0\) (Figures S4.3).
-
-\emph{Interactions between conspecifics}
-
-We conducted a sensitivity analysis on the encounter rate between
-conspecifics (\(R\)) by varying the value of \(\psi\) (see S1). Under
-default simulations, \(\psi = 3\). We also ran simulations in which
-\(\psi = 1\) (Figure S4.4), \(\psi = 2\) (Figure S4.5), \(\psi = 4\)
-(Figure S4.6), and \(\psi = 6\) (Figure S4.7), with all other parameters
-being set to default values.
-
-\emph{Initialised male search time}
-
-Lastly, we conducted a sensitivity analysis on initialised male search
-time (\(T_{\mathrm{m}}\)). To do this, we ran simulations at default
-values, but initialised all males at \(T_{\mathrm{m}} = 0.5\) (Figure
-S4.8) or \(T_{\mathrm{m}} = 2.5\) (S4.9). Note that under these
-initialisation conditions, it no longer makes sense to test whether or
-not \(T_{\mathrm{m}}\) evolves to positive values, so we do not show
-predicted male search thresholds and focus only on female choosiness.
-Interestingly, while predictions given initialised
-\(T_{\mathrm{m}} = 0.5\) are quite close for female choosiness
-thresholds, female choosiness does not appear to evolve given
-\(T_{\mathrm{m}} = 2.5\). This might be due to low selection pressure to
-reject males without gifts due to their low frequency. In other words,
-while females would benefit from a strategy of rejecting gift-less
-males, a lack of realised encounters with gift-less males preclude the
-evolution of sustained selection for choosiness.
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-6-1.pdf}
-\caption{Figure S2.1: Evolution of both male search (blue) and female
-choice (red) under different combinations of the mortality rates
-\(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\) (mortality in time-in
-and out, respectively). The y-axis is the threshold fitness that leads
-to evolution of male search (blue) or female choice (red). The results
-show noise, but no correlation between the value of the mortality
-parameters and the propensity for male search and/or female choice to
-evolve. For each of the \(25 \times 20\) combinations of
-\(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\), 1600 replicate
-simulations were run.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-7-1.pdf}
-\caption{Figure S2.2 (\(T_{\mathrm{f}} = 0.5\)): The coevolution of male
-search and female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-female choosiness (red) and male search (blue) exceeds zero, indicating
-evolution of choosiness or nuptial gift search. Each point includes data
-from approximately 1600 replicate simulations with identical starting
-conditions (some parameter combinations have fewer replicates). Red and
-blue lines show thresholds above which the mathematical model predicts
-that females should be choosy and males should search, respectively. Up
-to 3000 interactions occur between individuals in each time step
-(\(\psi = 3\)), potentially resulting in a mating interaction. The
-number of individuals in the population remained at or near carrying
-capacity of \(K = 1000\). Expected female processing time was set to
-\(T_{\mathrm{f}}=0.5\) time steps, and \(\gamma\) and \(\alpha\) values
-in the range {[}0.5, 1.5{]} and {[}0.1, 2.1{]}, respectively, were
-used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-8-1.pdf}
-\caption{Figure S2.3 (\(T_{\mathrm{f}} = 10.0\)): The coevolution of
-male search and female choosiness as a function of nuptial gift search
-time (\(\alpha\)). Points show where the lower 95\% confidence interval
-of female choosiness (red) and male search (blue) exceeds zero,
-indicating evolution of choosiness or nuptial gift search. Each point
-includes data from approximately 1600 replicate simulations with
-identical starting conditions (some parameter combinations include fewer
-replicates). Red and blue lines show thresholds above which the
-mathematical model predicts that females should be choosy and males
-should search, respectively. Up to 3000 interactions occur between
-individuals in each time step (\(\psi = 3\)), potentially resulting in a
-mating interaction. The number of individuals in the population remained
-at or near carrying capacity of \(K = 1000\). Expected female processing
-time was set to \(T_{\mathrm{f}}=10.0\) time steps, and \(\gamma\) and
-\(\alpha\) values in the range {[}0.5, 1.5{]} and {[}0.1, 2.1{]},
-respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-9-1.pdf}
-\caption{Figure S2.4 (\(\psi = 1\)): The coevolution of male search and
-female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from
-approximately 100 replicate simulations with identical starting
-conditions (some parameter combinations had fewer replicates, minimum
-400). Red and blue lines show thresholds above which the mathematical
-model predicts that females should be choosy and males should search,
-respectively. Up to 1000 interactions occur between individuals in each
-time step (\(\psi = 1\)), potentially resulting in a mating interaction.
-The number of individuals in the population remained at or near carrying
-capacity of \(K = 1000\). Expected female processing time was set to
-\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
-the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]}, respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-10-1.pdf}
-\caption{Figure S2.5 (\(\psi = 2\)): The coevolution of male search and
-female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 100
-replicate simulations with identical starting conditions (some parameter
-combinations have fewer replicates). Red and blue lines show thresholds
-above which the mathematical model predicts that females should be
-choosy and males should search, respectively. Up to 2000 interactions
-occur between individuals in each time step (\(\psi = 2\)), potentially
-resulting in a mating interaction. The number of individuals in the
-population remained at or near carrying capacity of \(K = 1000\).
-Expected female processing time was set to \(T_{\mathrm{f}}=2\) time
-steps, and \(\gamma\) and \(\alpha\) values in the range {[}0.0, 1.4{]}
-and {[}0.1, 1.2{]}, respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-11-1.pdf}
-\caption{Figure S2.6 (\(\psi = 4\)): The coevolution of male search and
-female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 100
-replicate simulations with identical starting conditions (some parameter
-combinations have fewer replicates). Red and blue lines show thresholds
-above which the mathematical model predicts that females should be
-choosy and males should search, respectively. Up to 4000 interactions
-occur between individuals in each time step, potentially resulting in a
-mating interaction (\(\psi = 4\)). The number of individuals in the
-population remained at or near carrying capacity of \(K = 1000\).
-Expected female processing time was set to \(T_{\mathrm{f}}=2\) time
-steps, and \(\gamma\) and \(\alpha\) values in the range {[}0.0, 1.4{]}
-and {[}0.1, 1.2{]}, respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-12-1.pdf}
-\caption{Figure S2.7 (\(\psi = 6\)): The coevolution of male search and
-female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 100
-replicate simulations with identical starting conditions (some parameter
-combinations have fewer replicates). Red and blue lines show thresholds
-above which the mathematical model predicts that females should be
-choosy and males should search, respectively. Up to 6000 interactions
-occur between individuals in each time step, potentially resulting in a
-mating interaction (\(\psi = 6\)). The number of individuals in the
-population remained at or near carrying capacity of \(K = 1000\).
-Expected female processing time was set to \(T_{\mathrm{f}}=2\) time
-steps, and \(\gamma\) and \(\alpha\) values in the range {[}0.0, 1.4{]}
-and {[}0.1, 1.2{]}, respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-13-1.pdf}
-\caption{Figure S2.8 (\(T_{\mathrm{m}} = 0.5\)): The coevolution of male
-search and female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 1600
-replicate simulations with identical starting conditions. The red line
-shows the threshold above which the mathematical model predicts that
-females should be choosy (male thresholds for search are not shown
-because simulations were initialised with males already searching for
-nuptial gifts). Up to 3000 interactions occur between individuals in
-each time step, potentially resulting in a mating interaction
-(\(\psi = 3\)). The number of individuals in the population remained at
-or near carrying capacity of \(K = 1000\). Expected female processing
-time was set to \(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and
-\(\alpha\) values in the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]},
-respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\captionsetup{labelformat=empty}
-
-\begin{figure}
-\centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-14-1.pdf}
-\caption{Figure S2.9 (\(T_{\mathrm{m}} = 2.5\)): The coevolution of male
-search and female choosiness as a function of nuptial gift search time
-(\(\alpha\)). Points show where the lower 95\% confidence interval of
-where male search (blue) exceeds zero, indicating evolution of
-choosiness or nuptial gift search. Each point includes data from 1600
-replicate simulations with identical starting conditions. The red line
-shows the threshold above which the mathematical model predicts that
-females should be choosy (male thresholds for search are not shown
-because simulations were initialised with males already searching for
-nuptial gifts). Up to 3000 interactions occur between individuals in
-each time step, potentially resulting in a mating interaction
-(\(\psi = 3\)). The number of individuals in the population remained at
-or near carrying capacity of \(K = 1000\). Expected female processing
-time was set to \(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and
-\(\alpha\) values in the range {[}0.0, 1.4{]} and {[}0.1, 1.2{]},
-respectively, were used.}
-\end{figure}
-
-\captionsetup{labelformat=default}
-
-\clearpage
-
-\hypertarget{s3-alternative-derivation-of-male-fitness-threshold}{%
-\subsection{S3: Alternative derivation of male fitness
-threshold}\label{s3-alternative-derivation-of-male-fitness-threshold}}
+\hypertarget{s1-alternative-derivation-of-male-fitness-threshold}{%
+\subsection{S1: Alternative derivation of male fitness
+threshold}\label{s1-alternative-derivation-of-male-fitness-threshold}}
 
@@
 
-\hypertarget{s5-estimation-of-key-model-parameters-using-experimental-data}{%
-\subsection{S5: Estimation of key model parameters using experimental
-data}\label{s5-estimation-of-key-model-parameters-using-experimental-data}}
-
-Estimates showing the mean number of offspring produced by female
-\emph{Pisaura mirabilis} that ate nuptial gifts and females who did not.
-Means were calculated with raw data from Tuni \emph{et al.}
-(\protect\hyperlink{ref-Tuni2013a}{2013}) and results are shown \(\pm\)
-SE (Table 1). Under these assumptions, the relative gain in fitness from
-receiving nuptial gifts for a female is,
-
-\[\hat{\delta_\mathrm{f}} = \frac{25.74}{6.00} = 4.29\]
-
-Since the baseline fitness is 1, the increase in fitness resulting from
-a nuptial gift then becomes,
-
-\[\hat{\gamma} = \hat{\delta_{\mathrm{f}}} - 1 = 3.29.\]
-
-The value 3.29 was used to parameterise \(\gamma\) for a set of
-simulations (Figure 4 in the main text).
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.4024}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2805}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.3171}}@{}}
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Received nuptial gift
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Received no nuptial gift
-\end{minipage} \\
-\midrule
-\endhead
-Expected number of hatched eggs & \(25.74 \pm 0.96\) &
-\(6.00 \pm 2.1\) \\
-\bottomrule
-\end{longtable}
-
-Table 1: Estimates showing mean number of offspring produced by female
-\emph{P. mirabilis} that ate nuptial gifts and females who did not.
-Means were calculated with raw data from Tuni \emph{et al.}
-(\protect\hyperlink{ref-Tuni2013a}{2013}) and results are shown \(\pm\)
-SE.
+\hypertarget{s3-sensitivity-analysis-of-parameters-in-ibm}{%
+\subsection{S3: Sensitivity analysis of parameters in
+IBM}\label{s3-sensitivity-analysis-of-parameters-in-ibm}}
+
+We investigated the sensitivity of our results to individual mortality
+during time-in (\(\mu_{\mathrm{in}}\)) and time-out
+(\(\mu_{\mathrm{out}}\)), female processing time (\(T_{\mathrm{f}}\)),
+and the potential for interactions between conspecifics (\(\psi\)).
+Across all of these simulations, there were challenges with statistical
+power. Evidence for the evolution of male search (blue points in
+figures) and female choosiness (red points in figures) was determined by
+the lower 95\% bootstrapped confidence interval of \(T_{\mathrm{m}}\)
+and \(T_{\mathrm{f}}\) values being greater than zero, respectively.
+This required a lot of replicate simulations in the main text (Figure
+3), especially for values just above predicted thresholds and for female
+choosiness. Computation time was a limiting factor, even using a
+compiled language (C) and with access to a computing cluster. Absence of
+points above threshold values are not necessarily evidence that
+evolution of male search or female choosiness is not predicted to evolve
+in these regions of parameter space, but it does indicate that evolution
+of these traits is not necessarily assured given the stochasticity
+inherent to the IBM. Additional simulations can be conducted using the C
+code in the `src' folder of the GitHub repository
+(\url{https://github.com/bradduthie/nuptial_gift_evolution}). Below, we
+explain the parameter values used in the sensitivity analysis in more
+detail.
+
+\emph{Mortality}
+
+We conducted a sensitivity analysis of the effect of the mortality
+parameters \(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\) (the
+probability of mortality in time-in and time-out, respectively, which we
+assumed to be equal for all individuals) on the evolution of male search
+and female choice using the IBM. The results revealed no correlation
+between the value of the mortality parameters and the evolution of male
+search or female choice (Fig. S2.1).
+
+\emph{Female processing time}
+
+We also conducted a sensitivity analysis of female processing time
+\(T_{\mathrm{f}}\). To do this, we ran simulations at default values,
+but with \(T_{\mathrm{f}} = 10.0\) (Figures S2.2).
+
+\emph{Interactions between conspecifics}
+
+We conducted a sensitivity analysis on the encounter rate between
+conspecifics (\(R\)) by varying the value of our scaling parameter
+\(\psi\). Under default simulations, \(\psi = 3\). We also ran
+simulations in which \(\psi = 1\) (Figure S2.3), \(\psi = 2\) (Figure
+S3.4), \(\psi = 4\) (Figure S3.5), and \(\psi = 6\) (Figure S3.6), with
+all other parameters being set to default values.
 
 \clearpage
-
-\hypertarget{s6-separate-evolution-of-male-search-and-female-choice}{%
-\subsection{S6: Separate evolution of male search and female
-choice}\label{s6-separate-evolution-of-male-search-and-female-choice}}
-
-We used the individual-based simulation model (see Supporting
-Information S1) to unpack the effect of coevolution on the evolution of
-male search and female choice. Here we replicated the simulations shown
-in the main text under the condition where only one trait at a time was
-allowed to evolve and studied how this affected the trait evolution.
-
-First, we submitted a set of simulations wherein male search did not
-evolve, but was fixed at different values (see Fig. S6.1). Next, we ran
-the same set of simulations wherein male search evolved, but female
-choice was not possible. The results thus show how each trait evolves in
-the absence of any coevolution (Fig. S6.1).
 
@@
 \centering
-\includegraphics{ms_biorxiv_files/figure-latex/unnamed-chunk-16-1.pdf}
-\caption{Figure S6.1: The separate evolution of male search and female
+\includegraphics{index_files/figure-latex/unnamed-chunk-6-1.pdf}
+\caption{Figure S2.1: Evolution of both male search (blue) and female
+choice (red) under different combinations of the mortality rates
+\(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\) (mortality in time-in
+and out, respectively). The y-axis is the threshold fitness that leads
+to evolution of male search (blue) or female choice (red). The results
+show noise, but no correlation between the value of the mortality
+parameters and the propensity for male search and/or female choice to
+evolve. For each of the \(25 \times 20\) combinations of
+\(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\), 3000 replicate
+simulations were run.}
+\end{figure}
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+\begin{figure}
+\centering
+\includegraphics{index_files/figure-latex/unnamed-chunk-7-1.pdf}
+\caption{Figure S2.3 (\(T_{\mathrm{f}} = 10.0\)): The coevolution of
+male search and female choosiness as a function of nuptial gift search
+time (\(\alpha\)). Points show where the lower 95\% confidence interval
+of female choosiness (red) and male search (blue) exceeds zero,
+indicating evolution of choosiness or nuptial gift search. Each point
+includes data from 3000 replicate simulations with identical starting
+conditions. Up to 3000 interactions occur between individuals in each
+time step (\(\psi = 3\)), potentially resulting in a mating interaction.
+The number of individuals in the population remained at or near carrying
+capacity of \(K = 1000\). Expected female processing time was set to
+\(T_{\mathrm{f}}=10.0\) time steps, and \(\gamma\) and \(\alpha\) values
+in the range {[}0.1, 2.0{]} and {[}0.0, 2.0{]}, respectively, were
+used.}
+\end{figure}
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+\begin{figure}
+\centering
+\includegraphics{index_files/figure-latex/unnamed-chunk-8-1.pdf}
+\caption{Figure S2.4 (\(\psi = 1\)): The coevolution of male search and
+female choosiness as a function of nuptial gift search time
+(\(\alpha\)). Points show where the lower 95\% confidence interval of
+where male search (blue) exceeds zero, indicating evolution of
+choosiness or nuptial gift search. Each point includes data from 3000
+replicate simulations with identical starting conditions. Up to 1000
+interactions occur between individuals in each time step (\(\psi = 1\)),
+potentially resulting in a mating interaction. The number of individuals
+in the population remained at or near carrying capacity of \(K = 1000\).
+Expected female processing time was set to \(T_{\mathrm{f}}=2\) time
+steps, and \(\gamma\) and \(\alpha\) values in the range {[}0.0, 2.0{]}
+and {[}0.1, 2.0{]}, respectively, were used.}
+\end{figure}
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+\begin{figure}
+\centering
+\includegraphics{index_files/figure-latex/unnamed-chunk-9-1.pdf}
+\caption{Figure S2.5 (\(\psi = 2\)): The coevolution of male search and
+female choosiness as a function of nuptial gift search time
+(\(\alpha\)). Points show where the lower 95\% confidence interval of
+where male search (blue) exceeds zero, indicating evolution of
+choosiness or nuptial gift search. Each point includes data from 3000
+replicate simulations with identical starting conditions. Up to 2000
+interactions occur between individuals in each time step (\(\psi = 2\)),
+potentially resulting in a mating interaction. The number of individuals
+in the population remained at or near carrying capacity of \(K = 1000\).
+Expected female processing time was set to \(T_{\mathrm{f}}=2\) time
+steps, and \(\gamma\) and \(\alpha\) values in the range {[}0.0, 2.0{]}
+and {[}0.1, 2.0{]}, respectively, were used.}
+\end{figure}
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+\begin{figure}
+\centering
+\includegraphics{index_files/figure-latex/unnamed-chunk-10-1.pdf}
+\caption{Figure S2.6 (\(\psi = 4\)): The coevolution of male search and
+female choosiness as a function of nuptial gift search time
+(\(\alpha\)). Points show where the lower 95\% confidence interval of
+where male search (blue) exceeds zero, indicating evolution of
+choosiness or nuptial gift search. Each point includes data from 3000
+replicate simulations with identical starting conditions. Up to 4000
+interactions occur between individuals in each time step, potentially
+resulting in a mating interaction (\(\psi = 4\)). The number of
+individuals in the population remained at or near carrying capacity of
+\(K = 1000\). Expected female processing time was set to
+\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
+the range {[}0.0, 2.0{]} and {[}0.1, 2.0{]}, respectively, were used.}
+\end{figure}
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\captionsetup{labelformat=empty}
+
+\begin{figure}
+\centering
+\includegraphics{index_files/figure-latex/unnamed-chunk-11-1.pdf}
+\caption{Figure S2.7 (\(\psi = 6\)): The coevolution of male search and
+female choosiness as a function of nuptial gift search time
+(\(\alpha\)). Points show where the lower 95\% confidence interval of
+where male search (blue) exceeds zero, indicating evolution of
+choosiness or nuptial gift search. Each point includes data from 3000
+replicate simulations with identical starting conditions. Up to 6000
+interactions occur between individuals in each time step, potentially
+resulting in a mating interaction (\(\psi = 6\)). The number of
+individuals in the population remained at or near carrying capacity of
+\(K = 1000\). Expected female processing time was set to
+\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
+the range {[}0.0, 2.0{]} and {[}0.1, 2.0{]}, respectively, were used.}
+\end{figure}
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\hypertarget{s4-separate-evolution-of-male-search-and-female-choice}{%
+\subsection{S4: Separate evolution of male search and female
+choice}\label{s4-separate-evolution-of-male-search-and-female-choice}}
+
+We used the individual-based simulation model to unpack the effect of
+coevolution on the evolution of male search and female choice. Here we
+replicated the simulations shown in the main text under the condition
+where only one trait at a time was allowed to evolve and studied how
+this affected the trait evolution.
+
+First, we submitted a set of simulations wherein male search did not
+evolve, but was fixed at different values. Next, we ran the same set of
+simulations wherein male search evolved, but female choice was not
+possible. The results thus show how each trait evolves in the absence of
+any coevolution (Fig. S4.1).
+
+\captionsetup{labelformat=empty}
+
+\begin{figure}
+\centering
+\includegraphics{index_files/figure-latex/unnamed-chunk-12-1.pdf}
+\caption{Figure S4.1: The separate evolution of male search and female
 choosiness as a function of nuptial gift search time. Points show where

### 2024-11-29 ms.Rmd
Fixed up traits and manuscript. Traits are not binary anymore, but are diploid

@@
 Selection will favour choosiness in the opposite sex if the value of a nuptial gift exceeds the inverse of the time taken to produce offspring multiplied by the rate at which mates with nuptial gifts are encountered.
-Importantly, selection can differ between the sexes, potentially causing sexual conflict. 
-We test these results using an individual-based model applied to a system of nuptial gift-giving spiders, *Pisaura mirabilis*, by estimating parameter values using experimental data from several studies.
+Selection can differ between the sexes, potentially causing sexual conflict. 
+We further investigate these results using an individual-based model inspired by a system of nuptial gift-giving spiders, *Pisaura mirabilis*, by estimating the fitness benefit of nuptial gift-giving using experimental data from several studies.
 Our results provide a general framework for understanding when the evolution of nuptial gift-giving can occur and provide novel insight into the evolution of worthless nuptial gifts, occurring in multiple taxonomic groups with implications for understanding parental investment.
-
-Lay summary
-================================================================================
-
-If you have ever bought a gift to impress a prospective partner, you are not alone. 
-Such behaviour is not unique to humans, but giving gifts during courtship is common in many different animals, including some species of insects, snails, birds, squid and spiders. 
-In animals, such gifts can be costly, but offering them may be worth it from an evolutionary perspective if they increase the reproductive success of the individual who provides them. 
-While using gifts during courtship (often called nuptial gifts) is widespread among animals, it is not universal. 
-Why have some groups of animals evolved to engage in nuptial gift-giving while others have not? 
-We explore this question by building a mathematical model, using computer simulations, and using data from a nuptial gift-giving species of spider to see how receiving nuptial gifts might affect reproductive success.
-We find conditions under which selection should favour males to provide nuptial gifts and females should exhibit a preference for gifts. 
-These conditions explain why some species engage in nuptial gift-giving while others do not.
-Interestingly, we find that these inequalities differ between males and female, illustrating that the evolutionary interest of the two sexes do not always overlap.
-
-Teaser text
-================================================================================
-
-The results presented provide a general explanation of the evolution of nuptial gift-giving which is a behaviour pattern that has evolved many times independently in diverse parts of the animal kingdom.
-The explanation is general but at the same time quantitatively precise, thus giving a rigorous answer to the conundrum of why nuptial gift-giving occurs in some groups of animals but not in others. 
-Since research on nuptial gift-giving has, and continues to, inspire an enormous amount of work, the results presented here are highly relevant to an active field of both theoretical and empirical research.
 
@@
 Despite the ubiquity of this behaviour, little effort has been made to conceptualise the evolution of nuptial gift-giving within a general modelling framework [@Lewis2014; @Iwasa2022]. 
-Recent models describing the evolution of nuptial gift-giving have focused on co-evolution between male nuptial gift-giving and female propensity to remate, and evolutionarily stable nuptial gift sizes [@Iwasa2022; @Kamimura2021], but a general framework describing the conditions necessary for nuptial gift-giving to be initially favoured by selection is needed to understand when gift-giving should evolve.
+Recent models describing the evolution of nuptial gift-giving have focused on co-evolution between male nuptial gift-giving and female propensity to remate, and evolutionarily stable nuptial gift sizes [@Iwasa2022; @Kamimura2021], but a general framework describing the conditions under which nuptial gift-giving can be initially favoured by selection is needed to understand when gift-giving should evolve.
 
-Nuptial gift-giving may allow males to increase fitness by acquiring additional mates, indirect benefits (by increasing the fitness of offspring), prolonged copulations, and success in sperm competition [@Lewis2014; @Albo2013; @Ghislandi2014].
+Nuptial gift-giving may allow males to increase fitness by acquiring additional mates, indirect benefits (by increasing offspring fitness), prolonged copulations, and success in sperm competition [@Lewis2014; @Albo2013; @Ghislandi2014].
 However, this potential fitness increase comes at the expense of producing a nuptial gift, which may be costly in terms of time and resources. 
@@
 With respect to nuptial gift-giving, the evolutionary interests of both sexes may not always fully overlap. 
-This can cause sexual conflict, which is a difference in the evolutionary interest between sexes that occurs when interaction between sexes results in a situation where neither sex can achieve an optimal outcome [@Parker2006].
-That is, under some conditions, it might for example be optimal for males but not females to mate if females do not benefit from mating with males without nuptial gifts.
+This can cause sexual conflict, which is a difference in the fitness interests between sexes that occurs when an interaction results in a situation where individuals cannot both achieve an optimal outcome [@Parker2006].
+For example, under some conditions, it might be optimal for males to mate without offering a nuptial gift, while it might be optimal for females to insist on receiving a nuptial gift.
 
 Much work has sought to explain how gift-giving tactics are maintained, with explanations including condition-dependent strategies, gift-giving as a way to decrease female aggression during copulation, or gifts as sensory traps [@Albo2019; @Lubin2007; @Ghislandi2018; @Toft2016].
-An example of such a system is the nuptial gift-giving nursery-web spider *Pisaura mirabilis* where males may court females with or without nuptial gifts [@Bristowe1926; @Tuni2013a]. 
+An example of such a system is the nuptial gift-giving nursery-web spider *Pisaura mirabilis*, where males may court females with or without nuptial gifts [@Bristowe1926; @Tuni2013a]. 
 Here, males may provide females with costly nuptial gifts in the form of captured arthropod prey, and females may exhibit preference for males with a nuptial gift by rejecting males without a nuptial gift [@Albo2013].
@@
 
-Criteria for male search and female choosiness
---------------------------------------------------------------------------------
+Analytical model
+-------------------------------------------------------------------------------
 
-The probability $G$ that a male succeeds in securing a nuptial gift is defined by,
+The probability that a male succeeds in securing a nuptial gift ($G$) after a duration of $T_{\mathrm{m}}$ is defined by,
 
-<!--
+$$P(G) = 1 - e^{-\frac{1}{\alpha}T_{m}}.
+\tag{1}
+$$
 
-$$G = 1 - e^{-\frac{1}{\alpha}T_{m}}.$$
---->
-
-\begin{equation}
-G = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.
-\end{equation}
-
-In Eq. 1, $\alpha$ defines the expected search time before encountering a nuptial gift.
-Thus, the probability of finding a nuptial gift is higher the more time $T_{\mathrm{m}}$ is spent searching. 
+In Eq. 1, $\alpha$ defines expected search time before encountering a nuptial gift.
+Thus, the probability of finding a nuptial gift is higher the more time is spent searching. 
 During time-in, individuals encounter conspecifics at a rate of $R$.
@@
 An example of how the structure of the time-in time-out model applies to a system with nuptial gift-giving is given in Figure 1.
-We assume that mating with a nuptial gift increases the fitness of each offspring by an increment of $\gamma$.
-We proceed to find the thresholds $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$ above which males and females are favoured by selection to search for mates with nuptial gifts and exhibit choosiness for nuptial gifts, respectively.
-We show (see Methods) that the initial threshold value of $\gamma$ ($\gamma_{\mathrm{m}}$) necessary for males to increase their fitness by investing time searching for a nuptial gift (time that could otherwise be spent searching for a mate) is,
+We assume that mating with a nuptial gift increases expected offspring production by an increment of $\gamma$.
+Mortality occurs for females and males in ($\mu_{\mathrm{i,f}}$, $\mu_{\mathrm{i,m}}$) and out ($\mu_{\mathrm{o,f}}$, $\mu_{\mathrm{o,m}}$) of the mating pool. 
+Following @Kokko2006, we assume $m_{\mathrm{i,f}} = m_{\mathrm{o,f}} = 1$ and $m_{\mathrm{i,m}} = m_{\mathrm{o,m}} = 1$.
+
+First, we find the fitness of males that search versus do not search for a nuptial gift. 
+We then describe the fitness consequences of female choice to accept or reject males based on their provision of a nuptial gift.
+We can then calculate the thresholds $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$ above which males and females are favoured by selection to search for nuptial gifts and exhibit choosiness for nuptial gifts, respectively.
+
+*Male fitness*
+
+During time-out, males can search for a nuptial gift.
+Males can adopt one of two strategies; either search or do not search for a nuptial gift. 
+Males with the searching strategy continue to search until they find a nuptial gift, while males that do not search immediately re-enter the mating pool. 
+Consequently, time searching for a nuptial gift will come at the cost of mating opportunities but might increase offspring fitness. 
+We therefore need to model the expected length of time spent outside of the mating pool for males that search for nuptial gifts ($E[T_{\mathrm{m}}]$), which equals $\alpha$. 
+We can integrate search time $t$ over the rate at which nuptial gifts are encountered ($\exp(-1/\alpha)$) to show $E[T_{\mathrm{m}}] = \alpha$,
+
+$$E[T_{\mathrm{m}}] = \int_{0}^{\infty}e^{- \frac{1}{\alpha}t}dt = \alpha.$$
+
+The rate at which a focal male that searches for a nuptial gift increases his fitness is therefore his reproductive output $\lambda(1 + \gamma)$ divided by expected time spent searching for a nuptial gift ($\alpha$) plus time spent in the mating pool, $(\beta + 1)/R$,
+
+$$W_{\mathrm{M_{G}}} = \lambda \frac{1 + \gamma}{\alpha + \left( \frac{\beta + 1}{R} \right)}.$$
+
+In contrast, a male that does not search for a nuptial gift has fewer offspring, but spends less time outside of the mating pool,
+
+$$W_{\mathrm{M_{L}}} = \lambda \frac{1}{\left(\frac{\beta+1}{R} \right)} = \lambda \frac{R}{\beta + 1}.$$
+
+We can determine the conditions for which $W_{\mathrm{M_{G}}} > W_{\mathrm{M_{L}}}$, isolating $\gamma$ to find how large of a fitness benefit must be provided by the nuptial gift to make the search cost worthwhile, which simplifies to,
+
+$$\gamma_{\mathrm{m}} > \alpha \frac{R}{\beta + 1}.
+\tag{2}
+$$
+
+When this inequality holds, males are favoured to search until they find a nuptial gift, which would result in an average search time of $\alpha$. 
+If the male trait is instead continuous (i.e., males search for time period $T_{\mathrm{m}}$), it can be shown that the same threshold can be reached by evaluating the partial derivative of the male fitness function (Supporting Information S1).
+Hence, the thresholds are consistent under different assumptions concerning male searching strategy.
+Selection will cause males to search for nuptial gifts if the fitness increase to offspring exceeds the product of search time and female encounter rate.
+
+*Female fitness*
+
+During time-out, females process offspring over a duration of $T_{\mathrm{f}}$ (we assume that $T_{\mathrm{f}} > \alpha$, otherwise females are not the choosy sex). 
+When females re-enter the mating pool, they encounter males at a rate of $R\beta/(\beta + 1)$. 
+If a female encounters a male with a nuptial gift, we assume that she will mate with him. 
+But if a female encounters a male with no nuptial gift, then she might accept or reject the male. 
+If she rejects the male, then she will remain in the mating pool. 
+The rate at which a female encounters a male with a nuptial gift is,
+
+$$R_{\mathrm{F_{G}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right).$$
+
+Expected time spent in the mating pool before a focal female encounters a male with a gift will be $1/R_{\mathrm{F_{G}}}$.
+The rate at which a female increases her fitness by being choosy and mating only when she encounters a male with a gift is,
+
+$$W_{f, g} = \lambda \frac{1 + \gamma}{T_{F} + \frac{1}{R_{\mathrm{F,G}}}}.
+\tag{4}
+$$
+
+The top of the right-hand side of Eq. 4 gives her fitness increase, and the bottom gives the total time it takes to obtain this fitness. 
+The $R_{\mathrm{F_{G}}}$ is inverted because it represents the expected time to encountering a male with a gift. 
+We can expand Eq. 6,
+
+$$W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right)}}.$$
+
+If the focal female is not choosy and accepts the first male that she encounters, then the rate at which she increases her fitness is,
+
+$$W_{\mathrm{F_{G,L}}} = \lambda \frac{\left(1 + \gamma\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)}}.$$
+
+We then evaluate the conditions under which $W_{\mathrm{F_{G}}} > W_{\mathrm{F_{G,L}}}$. 
+We can isolate $\gamma$ to determine how much offspring fitness must be increased to make choosiness beneficial ($\gamma_{\mathrm{f}}$),
+
+$$\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}} R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right)}.
+\tag{5}
+$$
+
+Note that that the expression $R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right)$ defines the rate at which a female in the mating pool encounters males with nuptial gifts.
+Hence, female choosiness is ultimately determined by time spent out of the mating pool to process offspring ($T_{\mathrm{f}}$) and the rate at which a female in the mating pool encounters males with nuptial gifts.
+
+*Operational sex ratio*
+
+We assume that the sex ratio is equal upon maturation. 
+Given this, @Kokko2001 show that the operational sex ratio depends on the probability of finding an individual in time-in,
+
+$$\beta = \frac{\int_{t = 0}^{\infty} P_{IM}(t)dt}{\int_{t = 0}^{\infty} P_{IF}(t)dt}.
+\tag{6}
+$$
+
+In Eq. 6, $P_{IM}(t)$ and $P_{IF}(t)$ are the probabilities of finding a male and female in time-in, respectively. 
+There is no closed form solution to the operational sex ratio, so we used recursion to calculate $\beta$ values for a given $T_{\mathrm{f}}$, $T_{\mathrm{m}}$, and $R$ (see Supporting Information S2),
+
+Individual-based model
+------------------------------------------
+
+We formulate an individual-based time-in time-out simulation model to complement the predictions made by our analytical time-in time-out model above and further allow for coevolution between male search behaviour and female choosiness.
+Here we describe the details of initialisation, time-in (mating), time-out (reproduction and nuptial gift search), and mortality. 
+We then summarise the simulations run and data collected.
+
+*Initialisation*
+
+Before the first time step, a population of $N = 1000$ individuals is initialised. 
+Individuals are assigned to be female with a probability of $0.5$, else male. 
+Female offspring processing time for a focal individual $i$ is fixed at $T^{i}_{\mathrm{f}} = 2$.
+Each individual is initialised with a diploid genotype that underlies female rejection probability of gift-less males ($\rho^{i}$), and a diploid genotype that underlies male search time ($T^{i}_{\mathrm{m}}$).
+Alleles can take any real value and combine additively to determine $\rho^{i}$ and $T^{i}_{\mathrm{m}}$.
+For all simulations, initialised values are set to , $\rho^{i} = 0$, and $T^{i}_{\mathrm{m}} = 0$. 
+All individuals are initialised outside of the mating pool in the first time step $t = 1$. 
+The first time step then proceeds with females immediately entering the mating pool and males either entering the mating pool or searching for nuptial gifts.
+
+*Time-in*
+
+At the start of each time step, females and males in the mating pool remain in it. 
+Females outside the mating pool enter the mating pool after processing offspring, and males enter it after searching for nuptial gifts (see 'Time-out' below). 
+Up to $\Psi = N\psi$ interactions between individuals can occur in a single time step, where $\psi$ is a scaling parameter. 
+In each time step, $\Psi$ pairs of individuals are selected at random to interact.
+For each interaction, two different individuals are randomly selected from the population with equal probability.
+If the selected individuals are of different sexes, and both are in the mating pool, then a mating encounter occurs.
+If the male does not have a nuptial gift, then a focal female $i$ will reject him with a probability of $\rho^{i}$; if rejection occurs, then both individuals stay in the mating pool. 
+If rejection does not occur, or the male has a nuptial gift in the mating encounter, then the individuals mate. 
+Females then leave the mating pool and enter time-out to process offspring, and males leave and enter time-out to potentially search for new nuptial gifts (note that females and males might re-enter the mating pool immediately within the same time step given sufficiently low search time; see Time-out below).
+
+*Time-out*
+
+During time-out, offspring production and time outside of the mating pool are realised for each female by sampling from a Poisson distribution.
+A focal female $i$ will produce $\mathrm{Poisson}(\lambda)$ offspring if no nuptial gift was provided or $\mathrm{Poisson}(\lambda + \gamma)$ if a gift was provided. 
+Females remain outside of the mating pool to process offspring for $\mathrm{Poisson}(T^{i}_{\mathrm{f}})$ time steps. 
+Offspring are added to the population immediately, with one $\rho^{i}$ and one $T^{i}_{\mathrm{m}}$ allele sampled from each parent with complete recombination.
+Mutation occurs independently for each allele with a probability of $\epsilon = 0.001$, and if mutation occurs, then a new allele value is sampled from a normal distribution mean centred on the existing value with a standard deviation of $\sigma_{\epsilon} = 0.1$.
+Offspring sex is randomly assigned with equal probability as female or male. 
+Female offspring are immediately placed in the mating pool, and male offspring are out of the mating pool to potentially search for nuptial gifts. 
+After a female has spent $\mathrm{Poisson}(T^{i}_{\mathrm{f}})$ time steps outside the mating pool, she will re-enter it.
+
+A focal male $i$ outside the mating pool will enter it if he has searched for a fixed number of $T^{i}_{\mathrm{m}}$ time steps, which is also sampled randomly from a Poisson distribution, $\mathrm{Poisson}(T^{i}_{\mathrm{m}})$.
+If $T^{i}_{\mathrm{m}} = 0$, then the male immediately returns to the mating pool (in the same time step). 
+If $T^{i}_{\mathrm{m}} > 0$, then the male must wait outside the mating pool for $\mathrm{Poisson}(T^{i}_{\mathrm{m}})$ time steps, but will enter the mating pool with a nuptial gift with a probability,
+
+$$P(G^{i}) = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.$$
+
+Males must always spend $\mathrm{Poisson}(T^{i}_{\mathrm{m}})$ time steps outside of the mating pool regardless of whether or not they are successful in obtaining a nuptial gift.
+
+*Mortality*
+
+At the end of each time step, mortality occurs first with a fixed probability for all adults in the population, then with a probability caused by carrying capacity $K = 1000$ applied to all individuals (adults and offspring).
+Mortality occurs in each time step with a fixed probability of $\mu$ regardless of the sex of the individual or its position in or out of the mating pool. 
+If after this fixed mortality is applied, the total population size $N > K$, then individuals are removed at random with equal probability until $N = K$. 
+Following adult mortality, a new time step begins with newly added offspring becoming adults.
+
+*Simulations*
+
+We ran simulations in which male search time and female choosiness evolved from an ancestral state of no searching and no choosiness. 
+In all simulations, $N$ was initialised at 1000 and $K = 1000$. 
+Simulations ran for $t_{max} = 10000$ time steps. 
+We set $T_{\mathrm{f}} = 2$, $\psi = 3$, and $\lambda = 1$ for all simulations, and we simulated across a range of $\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}$ and $\gamma = \{0, 0.1, ..., 1.9, 2.0\}$ parameter values for 5000 replicates.
+In a sensitivity analysis, we also re-ran simulations for values of $T_{\mathrm{f}} = 10$ and $\psi = \{1, 2, 4, 6 \}$ (see Supporting Information S3), and simulated the evolution of male nuptial gift searching and female choosiness (fixing $T_{\mathrm{m}} = \alpha$) separately (see Supporting Information S4).
+Summary statistics for mean trait values, population size, sex ratios, proportion of females and males in and out of the mating pool, and mean number of encounters per female and male within the mating pool were all calculated in the last time step.
+The C code used for simulating these IBMs also allows for the reporting of summary statistics in each time step. 
+Additionally, it can simulate explicit space and individual movement through the landscape. 
+A neutral evolving trait was also modelled to ensure that the code functioned as intended, and processes were compartmentalised into individual functions to facilitate code testing. 
+All code is publicly available on GitHub (https://github.com/bradduthie/nuptial_gift_evolution).
 
@@
 
-$$\gamma_{m} > \alpha \frac{M}{\sqrt{\beta}}.$$
---->
-
-\begin{equation}
-\gamma_{\mathrm{m}} > \alpha \frac{R}{\beta + 1}.
-\end{equation}
-
-Inequality 2 means that if nuptial gifts are not abundant and thus require a long time to find (i.e., high $\alpha$), or if males encounter many females per unit time (i.e., high $R / (1+\beta)$), then the nuptial gift must result in a high fitness increment for selection to favour gift-searching.
-In general, when ineq. 2 is satisfied, we predict selection to favour the evolution of nuptial gift-giving.
-
-We can similarly predict the conditions for which there is selection for female choosiness. 
-If $\gamma$ is sufficiently high, then females increase their fitness by rejecting males without gifts and mating only with males that provide nuptial gifts. 
-To illustrate, we assume that all males in a population search for a duration of $T_{\mathrm{m}}$, in which case the threshold fitness increment for females ($\gamma_{\mathrm{f}}$) is,
-
-<!---
-
-$$\gamma_{f} > \frac{1}{T_{f} M \sqrt{\beta} \left(1 - e^{-\frac{1}{\alpha}T_{m}} \right)}.$$
+A set of simulations with a value of $\gamma$ calculated from empirical data was also conducted (100 replicates). 
+Here, $\gamma$ was parameterised using data on egg production as a function of eating nuptial gifts (see below). 
+Additional simulation sets with lower and upper bounds of the estimated $\gamma$ were subsequently run. 
+In the simulation sets with experimentally derived parameter values, all other parameters were identical to previous simulation batches.
 
@@
 
-\begin{equation}
-\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}} R \left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}} \right)}.
-\end{equation}
+*Application to gift-giving spiders*
 
-Inequality 3 shows that as offspring processing time ($T_{\mathrm{f}}$), mate encounter rate ($R\beta / (\beta + 1)$), or the probability of a male finding a nuptial gift ($1 - \exp(-T_{\mathrm{m}}/\alpha)$ ) decreases, the threshold value of fitness above which selection will favour choosiness ($\gamma_{\mathrm{f}}$) increases.
-This can be understood intuitively by realising that rejecting a prospective male represents an opportunity cost for the female. 
-This opportunity cost becomes small if many males with gifts are encountered, hence the appearance of the rate at which males with gifts are encountered in the denominator.
-Figure 2 shows how $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$ change with increasing $\alpha$. 
-For $\gamma_{\mathrm{f}}$, we assume that males search for the expected time required to obtain a nuptial gift ($T_{\mathrm{m}} = \alpha$). 
-Note that $\beta$ does not have a closed form solution given $R$, $T_{\mathrm{f}}$, and $T_{\mathrm{m}}$, so $\beta$ was calculated using recursion (see Methods).
+We can produce an estimate of the fitness increment obtained by females when receiving a gift ($\hat{\gamma}$) by using data on female *P. mirabilis* egg production and hatching success [@Tuni2013a]. 
+@Tuni2013a found differences in egg production and hatching success in female *P. mirabilis* under different feeding regimes. 
+Assuming these differences in feeding regimes correspond to eating versus not eating nuptial gifts, the mean number of offspring produced by a female who eats nuptial gifts can be calculated.
+This calculation will be an overestimate because females that were fed in @Tuni2013a received multiple nuptial gifts.
+Nevertheless, we calculate these means using raw data from @Tuni2013a and find that mean offspring produced by females receiving nuptial gifts is $25.74 \pm 0.96$, while offspring produced by females without a nuptial gift is $6.00 \pm 2.1$.
+Consequently, the relative gain in fitness from receiving a nuptial gift for a female is estimated to be $\hat{\delta_\mathrm{f}} = 25.74 / 6.00 = 4.29$.
+Since the baseline fitness is 1, the increase in fitness resulting from a nuptial gift then becomes $\hat{\gamma} = \hat{\delta_{\mathrm{f}}} - 1 = 3.29.$
+
+Results
+====================================
+
+Our model predicts 4 zones that are delineated by inequalities 2 and 5 and describe the initial thresholds for the evolution of searching for nuptial gifts in males and choosiness for nuptial gifts in females.
+Figure 2a illustrates conditions under which no searching or choosiness evolves (zone A), only search (zone B) or choosiness (zone C) evolve, or both searching and choosiness evolve (zone D).
+Blue and red threshold lines in Figure 2 are defined by Eq. 2 and Eq. 5, respectively.
+Figure 2b illustrates the expansion of zone B as encounter rate decreases, which is consistent with the results of our IBM (Figure 3).
 
@@
 Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.
-Each point includes data from 3200 replicate simulations with identical starting conditions.
-Red and blue lines show thresholds above which the mathematical model predicts that females should be choosy and males should search, respectively (in agreement with Figure 2).
-Minor deviations between the analytical model and the simulation results are expected due to the finite population size, the substantial stochasticity inherent to the simulation model, and the potential for coevolution (for details, see Supporting Information S1).
+Each point includes data from 5000 replicate simulations with identical starting conditions.
+Zones are identified that correspond to areas where males search and females are choosy (D), males search but females are not choosy (B), and males do not search and females are not choosy (A), as also depicted in Figure 2.
 The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
@@
 Parameterising $\gamma$ with data from experimental studies may only yield a rough approximation of the true $\gamma$.
-This is because the estimated value of $\gamma$ is based on data from current populations (rather than ancestral populations, which are being simulated), and because the literature is inconclusive as to how much (if any) effect nuptial gifts have on female fitness [@Maxwell2018].
+This is partly because females were fed multiple nuptial gifts in the data we used to calculate the fitness gain from a nuptial gift [@Tuni2013a].
+It is also because the estimated value of $\gamma$ is based on data from current populations (rather than ancestral populations, which are being simulated), and because the literature is inconclusive as to how much (if any) effect nuptial gifts have on female fitness [@Maxwell2018].
 The effect of nuptial gifts on female fecundity has been estimated in a variety of system such as crickets, fireflies, butterflies and spiders, but these estimates vary considerably between species suggesting a large positive effect to no effect at all [@Bergstrom2002; @Rooney2002; @Maxwell2018; @Gao2019].
 
-Our model assumes something akin to sequential polyandry. 
+Our model assumes sequential polyandry. 
 That is, a system wherein female mating and reproduction with multiple males occurs in sequence, rather than multiple matings occurring before reproduction. 
@@
 They can also provide novel insight into how populations can evolve to use worthless or token nuptial gifts.
-
-Methods
-================================================================================
-
-Model
---------------------------------------------------------------------------------
-
-Here we first present more detail for the derivation of fitness threshold values $\gamma_{\mathrm{m}}$ and $\gamma_{\mathrm{f}}$.
-We then present IBM simulations (see Supporting Information S1 for full details). 
-Code for simulations is available on GitHub (see "Data availability").
-
-Derivation of fitness thresholds
---------------------------------------------------------------------------------
-
-We use a time-in and time-out model in which females and males spend some time searching for a mate (time-in) followed by a period of cool down outside the mating pool (time-out; Figure 1).
-
-After mating, females must spend some time processing offspring ($T_{\mathrm{f}}$). 
-Male time to replenish sperm is assumed to be negligible, but males can spend time out of the mating pool ($T_{\mathrm{m}}$) to search for a nuptial gift.
-When males return from time-out, they encounter females with some probability that is a function of the rate at which an individual encounters conspecifics ($R$) and the sex ratio ($\beta$; males/females).
-Mortality occurs for females and males in ($\mu_{\mathrm{i,f}}$, $\mu_{\mathrm{i,m}}$) and out ($\mu_{\mathrm{o,f}}$, $\mu_{\mathrm{o,m}}$) of the mating pool. 
-Following @Kokko2006, we assume $m_{\mathrm{i,f}} = m_{\mathrm{o,f}} = 1$ and $m_{\mathrm{i,m}} = m_{\mathrm{o,m}} = 1$. 
-While this choice is arbitrary, we conducted a sensitivity analysis which shows that the mortality parameters have no influence on the propensity for male search and female choice to evolve (Supporting Information S2).
-First, we describe the fitness consequences of male search time for a nuptial gift. 
-We then describe the fitness consequences of female choice to accept or reject males based on their provision of a nuptial gift.
-
-Male fitness
---------------------------------------------------------------------------------
-
-During time-out, males have the opportunity to search for a nuptial gift.
-Males can adopt one of two strategies; either search or do not search for a nuptial gift. 
-Males with the former strategy continue to search until they find a nuptial gift, while males that do not search will immediately re-enter the mating pool. 
-In this case, time searching for a nuptial gift will come at the cost of mating opportunities but might increase offspring fitness. 
-We therefore need to model the expected length of time $E[T_{\mathrm{m}}]$ spent outside of the mating pool for males that search for nuptial gifts, which is simply $\alpha$. 
-Note that we can integrate search time $t$ over the rate at which nuptial gifts are encountered ($\exp(-1/\alpha)$) to show $E[T_{\mathrm{m}}] = \alpha$,
-
-$$E[T_{\mathrm{m}}] = \int_{0}^{\infty}e^{- \frac{1}{\alpha}t}dt = \alpha.$$
-
-The rate at which a focal male that searches for a nuptial gift ($\mathrm{M_{G}}$) increases his fitness is therefore the fitness of his offspring $(1 + \gamma)$ divided by expected time spent searching for a nuptial gift ($\alpha$) plus time spent in the mating pool, $(\beta + 1)/R$ (recall that females produce $\lambda$ offspring),
-
-$$W_{\mathrm{M_{G}}} = \lambda \frac{1 + \gamma}{\alpha + \left( \frac{\beta + 1}{R} \right)}.$$
-
-In contrast, a male that does not search for a nuptial gift ($\mathrm{M_{L}}$) has offspring with lower fitness, but spends less time outside of the mating pool,
-
-$$W_{\mathrm{M_{L}}} = \lambda \frac{1}{\left(\frac{\beta+1}{R} \right)} = \lambda \frac{R}{\beta + 1}.$$
-
-We can then determine the conditions for which $W_{\mathrm{M_{G}}} > W_{\mathrm{M_{L}}}$, isolating $\gamma$ to find how large of a fitness benefit must be provided by the nuptial gift to make the search cost worthwhile, which simplifies to ineq.
-2.
-When this inequality holds, males are favoured to search until they find a nuptial gift, which would result in an average search time of $\alpha$. 
-When the male trait is continuous (i.e., males search for time period $T_{\mathrm{m}}$), it can be shown that the same threshold can be reached by evaluating the partial derivative of the male fitness function (Supporting Information S3).
-Hence, the thresholds are consistent under different assumptions concerning male searching strategy.
-Selection will cause males to search for nuptial gifts if the fitness increase to offspring exceeds the product of search time and female encounter rate.
-
-Female fitness
---------------------------------------------------------------------------------
-
-During time-out, females process offspring over a duration of $T_{\mathrm{f}}$ (we assume that $T_{\mathrm{f}} > \alpha$, else females are not the choosy sex). 
-When females re-enter the mating pool, they encounter males at a rate of $R\beta/(\beta + 1)$. 
-If a female encounters a male with a nuptial gift, we assume that she will mate with him. 
-But if a female encounters a male with no nuptial gift, then she might accept or reject the male. 
-If she rejects the male, then she will remain in the mating pool. 
-The rate at which a female encounters a male with a nuptial gift is,
-
-$$R_{\mathrm{F_{G}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right).$$
-
-We can similarly model the rate at which a female encounters a gift-less male,
-
-$$R_{\mathrm{F_{L}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(e^{-\frac{1}{\alpha}T_{m}}\right).$$
-
-Note that we can recover the rate at which a female encounters any male,
-
-$$R \left(\frac{\beta}{\beta + 1}\right) = R \left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + R \left(\frac{\beta}{\beta + 1}\right) \left(e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right).$$
-
-If $R_{\mathrm{F_{G}}}$ is sufficiently high and $R_{\mathrm{F_{L}}}$ is sufficiently low, then finding a male with a gift will be easier than finding a male without one. 
-Also, the expected time spent in the mating pool before a focal female encounters a male with a gift will be $1/R_{\mathrm{F_{G}}}$, while the expected time spent in the mating pool before a focal female encounters any male will be $1 / (R_{\mathrm{F_{G}}} + R_{\mathrm{F_{L}}})$.
-Finally, the rates at which a female encounters males with and without a gift, $R_{\mathrm{F_{G}}}$ and $R_{\mathrm{F_{L}}}$, are different from the probabilities that a male encounter has or does not have a gift.
-The rate of encounter is no longer relevant in this case because we are assuming that an encounter has occurred. 
-Hence, the probability of an encountered male having a gift is simply,
-
-$$P(G) = \frac{1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}} = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
-
-Similarly, the probability of an encountered male not having a gift is simply,
-
-$$P(L) = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
-
-The rate at which a female increases her fitness by being choosy and mating only when she encounters a male with a gift is,
-
-<!---
-
-$$W_{f, g} = \frac{1 + \gamma}{T_{F} + \frac{1}{M_{f,G}}}.$$
-
---->
-
-\begin{equation}
-W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}}} + \frac{1}{\mathrm{F_{G}}}.
-\end{equation}
-
-The top of the right-hand side of Eq. 6 gives the fitness increase, and the bottom gives the total time it takes to obtain this fitness. 
-The $R_{\mathrm{F_{G}}}$ is inverted because it represents the expected time to encountering a male with a gift. 
-We can expand Eq. 6,
-
-$$W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right)}}.$$
-
-If the focal female is not choosy and accepts the first male that she encounters, then the rate at which she increases her fitness is,
-
-$$W_{\mathrm{F_{G,L}}} = \lambda \frac{\left(1 + \gamma\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)}}.$$
-
-We then evaluate the conditions under which $W_{\mathrm{F_{G}}} > W_{\mathrm{F_{G,L}}}$. 
-We isolate $\gamma$ to determine how much offspring fitness must be increased to make choosiness beneficial ($\gamma_{\mathrm{f}}$),
-
-$$\gamma_{\mathrm{f}} > \frac{1 + \frac{1}{\beta}}{D T_{f} \left(1 - e^{-1\frac{1}{\alpha}T_{m}}\right)}.$$
-
-The above can be expressed as Eq. 7 below,
-
-<!---
-
-$$\gamma_{f} > \frac{1}{T_{F}M\sqrt{\beta}\left(1 - e^{-\frac{1}{\alpha}T_{M}} \right)}.$$
-
---->
-
-\begin{equation}
-\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}}} R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right).
-\end{equation}
-
-Note that that the expression $R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right)$ defines the rate at which a female in the mating pool encounters males with nuptial gifts.
-Hence, female choosiness is ultimately determined by time spent out of the mating pool to process offspring ($T_{\mathrm{f}}$) and the rate at which a female in the mating pool encounters males with nuptial gifts.
-
-Operational sex ratio
-----------------------------
-
-We assume that the sex ratio is equal upon maturation. 
-Given this, @Kokko2001 show that the operational sex ratio depends on the probability of finding an individual in time-in,
-
-<!---
-
-$$\beta = \frac{\int_{t = 0}^{\infty} P_{IM}(t)dt}{\int_{t = 0}^{\infty} P_{IF}(t)dt}.$$
-
---->
-
-\begin{equation}
-\beta = \frac{\int_{t = 0}^{\infty} P_{IM}(t)dt}{\int_{t = 0}^{\infty} P_{IF}(t)dt}.
-\end{equation}
-
-In Eq. 8, $P_{IM}(t)$ and $P_{IF}(t)$ are the probabilities of finding a male and female in time-in, respectively. 
-There is no closed form solution to the operational sex ratio, so we used recursion to calculate $\beta$ values for a given $T_{\mathrm{f}}$, $T_{\mathrm{m}}$, and $R$ (see Supporting Information S4),
-
-Individual-based model
-------------------------------------------
-
-We formulate an individual-based simulation model to test whether the predictions made by the analytical time-in time-out model are qualitatively the same under a similar simulation model. 
-We use the individual-based model to test whether the prediction hold in finite populations. 
-The IBM was written in C. 
-All details of the initialisation, parameterisation and the specific simulations which we run, are described in Supporting Information S1.
-
-We use available experimental data on the effect of nuptial gifts on female offspring production to estimate the key parameter $\gamma$ (fitness increment from nuptial gift) and conducted a series of simulations where $\gamma$ was parameterised using this estimated value.
-Details of the estimation of $\gamma$ are described in Supporting Information S5.
-Separate evolution of male search and female choice (i.e., without co-evolution) is simulated in Supporting Information S6.
 

### 2024-11-29 R/analysis.R

@@ -42,12 +42,12 @@ IBM_output_to_summary <- function(res_file, out = "summary.csv"){
     gam_val <- res[i, 2];
     temp_r  <- which(dat$a1 == a1_val & dat$gam == gam_val);
     mean_Tm <- mean(dat[temp_r,]$Tm);
-    CIs_Tm  <- simpleboot(freqs = dat[temp_r,]$Tm);
+    CIs_Tm  <- simpleboot(freqs = dat[temp_r,]$Tm, alpha = 0.2);
     mean_Rj <- mean(dat[temp_r,]$RejPr);
-    CIs_Rj  <- simpleboot(freqs = dat[temp_r,]$RejPr);
+    CIs_Rj  <- simpleboot(freqs = dat[temp_r,]$RejPr, alpha = 0.2);
     mean_Gf <- mean(dat[temp_r,]$Gift);
     mean_Nu <- mean(dat[temp_r,]$N_m);
-    CIs_Nu  <- simpleboot(freqs = dat[temp_r,]$N_m);
+    CIs_Nu  <- simpleboot(freqs = dat[temp_r,]$N_m, alpha = 0.2);
     mean_M  <- mean(dat[temp_r,]$M_m);
     mean_B  <- mean(dat[temp_r,]$Beta);
     mean_Mm <- mean(dat[temp_r,]$M_males);
@@ -72,11 +72,62 @@ IBM_output_to_summary <- function(res_file, out = "summary.csv"){
 
 
 
+IBM_output_to_summary_mort <- function(res_file, out = "summary.csv"){
+  dat  <- read.csv(file = res_file);
+  # Remove any titles if CSVs are concatenated
+  mims <- which(dat[,1] == "mim");
+  dat  <- dat[-mims,];
+  cols <- dim(dat)[2];
+  for(i in 1:cols){
+    dat[,i] <- as.numeric(dat[,i]);
+  }
+  
+  # Pull out summary statistics
+  res  <- unique(cbind(dat$mim, dat$mom, dat$a1, dat$gam));
+  SUMM <- NULL;
+  for(i in 1:dim(res)[1]){
+    mim_val <- res[i, 1];
+    mom_val <- res[i, 2];
+    a1_val  <- res[i, 3];
+    gam_val <- res[i, 4];
+    temp_r  <- which(dat$mim == mim_val & dat$mom == mom_val & 
[…]

### 2024-11-29 src/nuptial_rep.c

@@ -25,7 +25,7 @@ int main(void){
     /* =======================================================================*/
     /* Model parameter values                                                 */
     /* =======================================================================*/
-    time_steps = 40000; /* Simulation time steps                              */
+    time_steps = 8000;  /* Simulation time steps                              */
     N          = 1000;  /* Population size                                    */
     Tm         = 0.0;   /* Initial male search time                           */
     Tf         = 2.0;   /* Initial female processing time                     */
@@ -48,8 +48,8 @@ int main(void){
     /* =======================================================================*/
     /* Simulation details                                                     */
     /* =======================================================================*/
-    rep    = 1;  /* Simulations run                                           */
-    stats  = 1;  /* 0: end of rep, 1: each time step, 2: all inds             */
+    rep    = 1000; /* Simulations run                                         */
+    stats  = 0;  /* 0: end of rep, 1: each time step, 2: all inds             */
     /* =======================================================================*/
     /*  XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX XXX   */
     /* =======================================================================*/

### 2024-11-29 src/nuptials.c

@@ -30,27 +30,37 @@ void swap_arrays(void **ARRAY_A, void **ARRAY_B){
 /******************************************************************************/
 void male_search(double **inds, int male){
 
-  double time_out, pr_gift, rand_unif;
-  /* Tested -- gets geometric distribution equivalent of exponential */
-  if(inds[male][5] > 0 || inds[male][29] > 0){
-    pr_gift   = 1 - exp(-1 / inds[male][13]);
-    time_out  = 0.0;
-    rand_unif = randunif();
-    while(rand_unif > pr_gift){
-      time_out++;
-      rand_unif = randunif();
-    }
-    inds[male][7]  = 1;
-    inds[male][25] = 1;
-    
-    if(time_out > 0){
-      inds[male][4]  = 0.0;
-      inds[male][23] = time_out;
+  double time_out, pr_gift, rand_unif, lambda;
+  
+  time_out = 0.0;
+  pr_gift  = 0.0;
+  lambda   = inds[male][5] + inds[male][29];
+  if(inds[male][5] > 0){
+    time_out  = (double) randpois(lambda);
+    if(inds[male][13] <= 0){
+      pr_gift = 1.0;
     }else{
-      inds[male][4]  = 1.0;
-      inds[male][23] = 0.0;
+      pr_gift = 1 - exp(-1 * lambda / inds[male][13]);
     }
   }
+  
+  rand_unif = randunif();
+  
+  if(rand_unif < pr_gift){
+    inds[male][7]  = 1.0;
+    inds[male][25] = 1.0;
+  }else{
+    inds[male][7]  = 0.0;
+    inds[male][25] = 0.0;
+  }
+  
+  if(time_out > 0){
+    inds[male][4]  = 0.0;
+    inds[male][23] = time_out;
+  }else{
+    inds[male][4]  = 1.0;
+    inds[male][23] = 0.0;
+  }  
 }
 
 /******************************************************************************/
@@ -157,26 +167,27 @@ void move_inds(double **inds, int xdim, int ydim, int N){
 /******************************************************************************/
 void female_male_int(double **inds, int female, int male){
 
-    double rej_gift, birth_par, offspring;
-
-    inds[female][21]++;
-    inds[male][21]++;
-
-    rej_gift = inds[female][8] + inds[female][30];
-    if(rej_gift < 1 || inds[male][7] > 0){
-      if(inds[male][7] > 0){
-        inds[female][20]  = 1.0;
-      }else{
-        inds[female][20]  = 0.0;
-      }
[…]

### 2024-12-05 src/nuptials.c
Minor bug fix so that if statement is triggered by additive combination of alleles instead of just one

@@ -35,7 +35,7 @@ void male_search(double **inds, int male){
   time_out = 0.0;
   pr_gift  = 0.0;
   lambda   = inds[male][5] + inds[male][29];
-  if(inds[male][5] > 0){
+  if(lambda > 0){
     time_out  = (double) randpois(lambda);
     if(inds[male][13] <= 0){
       pr_gift = 1.0;

### 2024-12-05 SI.Rmd
Update the manuscript

@@
 author: |
-  | Anders P. Charmouh$^{1,4, 5}$, Trine Bilde$^{2}$, Greta Bocedi$^{1}$, A. Bradley Duthie$^{3}$
-date: '[1] School of Biological Sciences, University of Aberdeen, UK.
-[2] Department of Biology, Aarhus University, Denmark.
-[3] Biological and Environmental Sciences, University of Stirling, UK.
-[4] Bioinformatics Research Centre Aarhus University, University City 81, building 1872, 3rd floor, DK-8000 Aarhus C, Denmark [5] Email: apc@birc.au.dk'
+  | Author list (anonymised)
+date: '[1] Author institutions and email'
 output:
-  pdf_document:
-    fig_caption: yes
-    keep_tex: yes
-  html_document: default
   word_document:
@@
 Absence of points above threshold values are not necessarily evidence that evolution of male search or female choosiness is not predicted to evolve in these regions of parameter space, but it does indicate that evolution of these traits is not necessarily assured given the stochasticity inherent to the IBM.
-Additional simulations can be conducted using the C code in the 'src' folder of the GitHub repository (https://github.com/bradduthie/nuptial_gift_evolution).
+Additional simulations can be conducted using the C code in the 'src' folder of the GitHub repository (https://github.com/AUTHOR_NAME/REPOSITORY_NAME).
 Below, we explain the parameter values used in the sensitivity analysis in more detail.

### 2024-12-05 SI.tex
Update the manuscript

@@
 Supporting Information}
-\author{Anders P. Charmouh\(^{1,4, 5}\), Trine Bilde\(^{2}\), Greta
-Bocedi\(^{1}\), A. Bradley Duthie\(^{3}\)}
-\date{{[}1{]} School of Biological Sciences, University of Aberdeen, UK.
-{[}2{]} Department of Biology, Aarhus University, Denmark. {[}3{]}
-Biological and Environmental Sciences, University of Stirling, UK.
-{[}4{]} Bioinformatics Research Centre Aarhus University, University
-City 81, building 1872, 3rd floor, DK-8000 Aarhus C, Denmark {[}5{]}
-Email: \href{mailto:apc@birc.au.dk}{\nolinkurl{apc@birc.au.dk}}}
+\author{Author list (anonymised)}
+\date{{[}1{]} Author institutions and email}
 
@@
 code in the `src' folder of the GitHub repository
-(\url{https://github.com/bradduthie/nuptial_gift_evolution}). Below, we
+(\url{https://github.com/AUTHOR_NAME/REPOSITORY_NAME}). Below, we
 explain the parameter values used in the sensitivity analysis in more
@@
 evolve. For each of the \(25 \times 20\) combinations of
-\(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\), 1600 replicate
+\(\mu_{\mathrm{in}}\) and \(\mu_{\mathrm{out}}\), 3000 replicate
 simulations were run.}

### 2024-12-05 index.Rmd
Update the manuscript

@@
 We apply our model to an example system with nuptial gifts, the nursery web spider *Pisaura mirabilis*, where we use experimental data to estimate a key model parameter. 
-Our results provide a general framework for understanding why nuptial gift-giving evolves in some systems and not in others, how the evolution of nuptial gift-giving can give rise to sexual conflict, and it provides insight into the evolution of worthless and deceitful nuptial gifts, which occur in several different taxonomic [@Ghislandi2014; @LeBas2005].
+Our results provide a general framework for understanding why nuptial gift-giving evolves in some systems and not in others, how the evolution of nuptial gift-giving can give rise to sexual conflict, and it provides insight into the evolution of worthless and deceitful nuptial gifts, which occur in several different taxonomic groups [@Ghislandi2014; @LeBas2005].
 
@@
 As an example, sizable areas of parameter space exists wherein the female optimum would be to exhibit preference for (and receive) nuptial gifts, while the male optimum is to not search for (and give) nuptial gifts (see Figure 2a, Zone C).
-This will lead to mate encounters in which gift-less males will benefit from mating, but females will not (i.e., evolutionary interests do not always overlap with respect to mating strategy between the sexes).
+This will lead to encounter where giftless males would benefit the most from mating, but female would benefit most from mating and receiving a gift (i.e., evolutionary interests do not always overlap with respect to mating strategy between the sexes).
 In many systems, ecological variables such as search time required to find a nuptial gift will likely depend on prey abundance,  which can vary substantially with time in some species with nuptial gift-giving [@Ghislandi2018].

### 2024-12-05 ms.Rmd
Update the manuscript

@@
 author: |
-  | Anders P. Charmouh$^{1,4, 5}$, Trine Bilde$^{2}$, Greta Bocedi$^{1}$, A. Bradley Duthie$^{3}$
-date: '[1] School of Biological Sciences, University of Aberdeen, UK.
-[2] Department of Biology, Aarhus University, Denmark.
-[3] Biological and Environmental Sciences, University of Stirling, UK.
-[4] Bioinformatics Research Centre Aarhus University, University City 81, building 1872, 3rd floor, DK-8000 Aarhus C, Denmark [5] Email: apc@birc.au.dk'
+  | Author list (anonymised)
+date: '[1] Author institutions and email'
 output:
+  pdf_document:
+    fig_caption: yes
+    keep_tex: yes
+  html_document: default
   word_document:
@@
     reference_docx: docx_template.docx
-  html_document: default
-  pdf_document:
-    fig_caption: yes
-    keep_tex: yes
 bibliography: nuptial_refs.bib
@@
 A neutral evolving trait was also modelled to ensure that the code functioned as intended, and processes were compartmentalised into individual functions to facilitate code testing. 
-All code is publicly available on GitHub (https://github.com/bradduthie/nuptial_gift_evolution).
+All code is publicly available on GitHub (https://github.com/AUTHOR_NAME/REPOSITORY_NAME).
 
@@
 
-**Author contributions:** APC and ABD conceived the study.
-ABD constructed the modelling framework with input from APC.
-APC wrote the paper with input from ABD and ABD wrote the IBM model.
-TB and GB provided substantial comments on previous drafts and final text.
+**Author contributions:** Redacted for anonymous peer review.
 
-**Acknowledgements:** Anders P.
-Charmouh was supported by the University of Aberdeen.
-A.
-Bradley Duthie was supported by the University of Stirling.
-Trine Bilde was supported by The Danish Council for Independent Research grant number 4002-00328B.
-We thank Maria Albo for making available data from a previous study which was useful for parameter estimating.
+**Acknowledgements:** Redacted for anonymous peer review.
 
-**Data availability:** The simulation software was implemented in C and the full source code is available at https://github.com/bradduthie/nuptial_gift_evolution.
+**Data availability:** The simulation software was implemented in C and the full source code is available at https://github.com/AUTHOR_NAME/REPOSITORY_NAME.
 

### 2024-12-05 ms.tex
Update the manuscript

@@
 \title{A general model for the evolution of nuptial gift-giving}
-\author{Anders P. Charmouh\(^{1,4, 5}\), Trine Bilde\(^{2}\), Greta
-Bocedi\(^{1}\), A. Bradley Duthie\(^{3}\)}
-\date{{[}1{]} School of Biological Sciences, University of Aberdeen, UK.
-{[}2{]} Department of Biology, Aarhus University, Denmark. {[}3{]}
-Biological and Environmental Sciences, University of Stirling, UK.
-{[}4{]} Bioinformatics Research Centre Aarhus University, University
-City 81, building 1872, 3rd floor, DK-8000 Aarhus C, Denmark {[}5{]}
-Email: \href{mailto:apc@birc.au.dk}{\nolinkurl{apc@birc.au.dk}}}
+\author{Author list (anonymised)}
+\date{{[}1{]} Author institutions and email}
 
@@
 multiplied by the rate at which mates with nuptial gifts are
-encountered. Importantly, selection can differ between the sexes,
-potentially causing sexual conflict. We test these results using an
-individual-based model applied to a system of nuptial gift-giving
-spiders, \emph{Pisaura mirabilis}, by estimating parameter values using
-experimental data from several studies. Our results provide a general
-framework for understanding when the evolution of nuptial gift-giving
-can occur and provide novel insight into the evolution of worthless
-nuptial gifts, occurring in multiple taxonomic groups with implications
-for understanding parental investment.
-
-\hypertarget{lay-summary}{%
-\section{Lay summary}\label{lay-summary}}
-
-If you have ever bought a gift to impress a prospective partner, you are
-not alone. Such behaviour is not unique to humans, but giving gifts
-during courtship is common in many different animals, including some
-species of insects, snails, birds, squid and spiders. In animals, such
-gifts can be costly, but offering them may be worth it from an
-evolutionary perspective if they increase the reproductive success of
-the individual who provides them. While using gifts during courtship
-(often called nuptial gifts) is widespread among animals, it is not
-universal. Why have some groups of animals evolved to engage in nuptial
-gift-giving while others have not? We explore this question by building
-a mathematical model, using computer simulations, and using data from a
-nuptial gift-giving species of spider to see how receiving nuptial gifts
-might affect reproductive success. We find conditions under which
-selection should favour males to provide nuptial gifts and females
-should exhibit a preference for gifts. These conditions explain why some
-species engage in nuptial gift-giving while others do not.
-Interestingly, we find that these inequalities differ between males and
-female, illustrating that the evolutionary interest of the two sexes do
-not always overlap.
-
-\hypertarget{teaser-text}{%
-\section{Teaser text}\label{teaser-text}}
-
-The results presented provide a general explanation of the evolution of
-nuptial gift-giving which is a behaviour pattern that has evolved many
-times independently in diverse parts of the animal kingdom. The
-explanation is general but at the same time quantitatively precise, thus
-giving a rigorous answer to the conundrum of why nuptial gift-giving
-occurs in some groups of animals but not in others. Since research on
-nuptial gift-giving has, and continues to, inspire an enormous amount of
-work, the results presented here are highly relevant to an active field
-of both theoretical and empirical research.
+encountered. Selection can differ between the sexes, potentially causing
+sexual conflict. We further investigate these results using an
+individual-based model inspired by a system of nuptial gift-giving
+spiders, \emph{Pisaura mirabilis}, by estimating the fitness benefit of
+nuptial gift-giving using experimental data from several studies. Our
+results provide a general framework for understanding when the evolution
+of nuptial gift-giving can occur and provide novel insight into the
+evolution of worthless nuptial gifts, occurring in multiple taxonomic
+groups with implications for understanding parental investment.
 
@@
 interests of both sexes may not always fully overlap. This can cause
-sexual conflict, which is a difference in the evolutionary interest
-between sexes that occurs when interaction between sexes results in a
-situation where neither sex can achieve an optimal outcome
-(\protect\hyperlink{ref-Parker2006}{Parker, 2006}). That is, under some
-conditions, it might for example be optimal for males but not females to
-mate if females do not benefit from mating with males without nuptial
-gifts.
+sexual conflict, which is a difference in the fitness interests between
+sexes that occurs when an interaction results in a situation where
+individuals cannot both achieve an optimal outcome
+(\protect\hyperlink{ref-Parker2006}{Parker, 2006}). For example, under
+some conditions, it might be optimal for males to mate without offering
+a nuptial gift, while it might be optimal for females to insist on
+receiving a nuptial gift.
 
@@
 
-\hypertarget{criteria-for-male-search-and-female-choosiness}{%
-\subsection{Criteria for male search and female
-choosiness}\label{criteria-for-male-search-and-female-choosiness}}
-
-The probability \(G\) that a male succeeds in securing a nuptial gift is
-defined by,
-
-\begin{equation}
-G = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.
-\end{equation}
-
-In Eq. 1, \(\alpha\) defines the expected search time before
-encountering a nuptial gift. Thus, the probability of finding a nuptial
-gift is higher the more time \(T_{\mathrm{m}}\) is spent searching.
-During time-in, individuals encounter conspecifics at a rate of \(R\). A
-focal individual will therefore encounter conspecifics of the opposite
-sex at a rate of \(R/2\) if the ratio of males to females in the mating
-pool (\(\beta\)) is equal. More generally, males will be encountered at
-a rate of \(R\beta/(\beta+1)\), and females will be encountered at a
-rate of \(R/(\beta+1)\). An example of how the structure of the time-in
-time-out model applies to a system with nuptial gift-giving is given in
-Figure 1. We assume that mating with a nuptial gift increases the
-fitness of each offspring by an increment of \(\gamma\). We proceed to
-find the thresholds \(\gamma_{\mathrm{m}}\) and \(\gamma_{\mathrm{f}}\)
-above which males and females are favoured by selection to search for
-mates with nuptial gifts and exhibit choosiness for nuptial gifts,
-respectively. We show (see Methods) that the initial threshold value of
-\(\gamma\) (\(\gamma_{\mathrm{m}}\)) necessary for males to increase
-their fitness by investing time searching for a nuptial gift (time that
-could otherwise be spent searching for a mate) is,
-
-\begin{equation}
-\gamma_{\mathrm{m}} > \alpha \frac{R}{\beta + 1}.
-\end{equation}
-
-Inequality 2 means that if nuptial gifts are not abundant and thus
-require a long time to find (i.e., high \(\alpha\)), or if males
-encounter many females per unit time (i.e., high \(R / (1+\beta)\)),
-then the nuptial gift must result in a high fitness increment for
-selection to favour gift-searching. In general, when ineq. 2 is
-satisfied, we predict selection to favour the evolution of nuptial
-gift-giving.
-
-We can similarly predict the conditions for which there is selection for
-female choosiness. If \(\gamma\) is sufficiently high, then females
-increase their fitness by rejecting males without gifts and mating only
-with males that provide nuptial gifts. To illustrate, we assume that all
-males in a population search for a duration of \(T_{\mathrm{m}}\), in
-which case the threshold fitness increment for females
-(\(\gamma_{\mathrm{f}}\)) is,
-
-\begin{equation}
-\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}} R \left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}} \right)}.
-\end{equation}
-
-Inequality 3 shows that as offspring processing time
-(\(T_{\mathrm{f}}\)), mate encounter rate (\(R\beta / (\beta + 1)\)), or
-the probability of a male finding a nuptial gift
-(\(1 - \exp(-T_{\mathrm{m}}/\alpha)\) ) decreases, the threshold value
-of fitness above which selection will favour choosiness
-(\(\gamma_{\mathrm{f}}\)) increases. This can be understood intuitively
-by realising that rejecting a prospective male represents an opportunity
-cost for the female. This opportunity cost becomes small if many males
-with gifts are encountered, hence the appearance of the rate at which
-males with gifts are encountered in the denominator. Figure 2 shows how
-\(\gamma_{\mathrm{m}}\) and \(\gamma_{\mathrm{f}}\) change with
-increasing \(\alpha\). For \(\gamma_{\mathrm{f}}\), we assume that males
-search for the expected time required to obtain a nuptial gift
-(\(T_{\mathrm{m}} = \alpha\)). Note that \(\beta\) does not have a
-closed form solution given \(R\), \(T_{\mathrm{f}}\), and
-\(T_{\mathrm{m}}\), so \(\beta\) was calculated using recursion (see
-Methods).
+\hypertarget{analytical-model}{%
+\subsection{Analytical model}\label{analytical-model}}
+
+The probability that a male succeeds in securing a nuptial gift (\(G\))
+after a duration of \(T_{\mathrm{m}}\) is defined by,
+
+\[P(G) = 1 - e^{-\frac{1}{\alpha}T_{m}}.
+\tag{1}
+\]
+
+In Eq. 1, \(\alpha\) defines expected search time before encountering a
+nuptial gift. Thus, the probability of finding a nuptial gift is higher
+the more time is spent searching. During time-in, individuals encounter
+conspecifics at a rate of \(R\). A focal individual will therefore
+encounter conspecifics of the opposite sex at a rate of \(R/2\) if the
+ratio of males to females in the mating pool (\(\beta\)) is equal. More
+generally, males will be encountered at a rate of \(R\beta/(\beta+1)\),
+and females will be encountered at a rate of \(R/(\beta+1)\). An example
+of how the structure of the time-in time-out model applies to a system
+with nuptial gift-giving is given in Figure 1. We assume that mating
+with a nuptial gift increases expected offspring production by an
+increment of \(\gamma\). Mortality occurs for females and males in
+(\(\mu_{\mathrm{i,f}}\), \(\mu_{\mathrm{i,m}}\)) and out
+(\(\mu_{\mathrm{o,f}}\), \(\mu_{\mathrm{o,m}}\)) of the mating pool.
+Following Kokko \& Ots (\protect\hyperlink{ref-Kokko2006}{2006}), we
+assume \(m_{\mathrm{i,f}} = m_{\mathrm{o,f}} = 1\) and
+\(m_{\mathrm{i,m}} = m_{\mathrm{o,m}} = 1\).
+
+First, we find the fitness of males that search versus do not search for
+a nuptial gift. We then describe the fitness consequences of female
+choice to accept or reject males based on their provision of a nuptial
+gift. We can then calculate the thresholds \(\gamma_{\mathrm{m}}\) and
+\(\gamma_{\mathrm{f}}\) above which males and females are favoured by
+selection to search for nuptial gifts and exhibit choosiness for nuptial
+gifts, respectively.
+
+\emph{Male fitness}
+
+During time-out, males can search for a nuptial gift. Males can adopt
+one of two strategies; either search or do not search for a nuptial
+gift. Males with the searching strategy continue to search until they
+find a nuptial gift, while males that do not search immediately re-enter
+the mating pool. Consequently, time searching for a nuptial gift will
+come at the cost of mating opportunities but might increase offspring
+fitness. We therefore need to model the expected length of time spent
+outside of the mating pool for males that search for nuptial gifts
+(\(E[T_{\mathrm{m}}]\)), which equals \(\alpha\). We can integrate
+search time \(t\) over the rate at which nuptial gifts are encountered
+(\(\exp(-1/\alpha)\)) to show \(E[T_{\mathrm{m}}] = \alpha\),
+
+\[E[T_{\mathrm{m}}] = \int_{0}^{\infty}e^{- \frac{1}{\alpha}t}dt = \alpha.\]
+
+The rate at which a focal male that searches for a nuptial gift
+increases his fitness is therefore his reproductive output
+\(\lambda(1 + \gamma)\) divided by expected time spent searching for a
+nuptial gift (\(\alpha\)) plus time spent in the mating pool,
+\((\beta + 1)/R\),
+
+\[W_{\mathrm{M_{G}}} = \lambda \frac{1 + \gamma}{\alpha + \left( \frac{\beta + 1}{R} \right)}.\]
+
+In contrast, a male that does not search for a nuptial gift has fewer
+offspring, but spends less time outside of the mating pool,
+
+\[W_{\mathrm{M_{L}}} = \lambda \frac{1}{\left(\frac{\beta+1}{R} \right)} = \lambda \frac{R}{\beta + 1}.\]
+
+We can determine the conditions for which
+\(W_{\mathrm{M_{G}}} > W_{\mathrm{M_{L}}}\), isolating \(\gamma\) to
+find how large of a fitness benefit must be provided by the nuptial gift
+to make the search cost worthwhile, which simplifies to,
+
+\[\gamma_{\mathrm{m}} > \alpha \frac{R}{\beta + 1}.
+\tag{2}
+\]
+
+When this inequality holds, males are favoured to search until they find
+a nuptial gift, which would result in an average search time of
+\(\alpha\). If the male trait is instead continuous (i.e., males search
+for time period \(T_{\mathrm{m}}\)), it can be shown that the same
+threshold can be reached by evaluating the partial derivative of the
+male fitness function (Supporting Information S1). Hence, the thresholds
+are consistent under different assumptions concerning male searching
+strategy. Selection will cause males to search for nuptial gifts if the
+fitness increase to offspring exceeds the product of search time and
+female encounter rate.
+
+\emph{Female fitness}
+
+During time-out, females process offspring over a duration of
+\(T_{\mathrm{f}}\) (we assume that \(T_{\mathrm{f}} > \alpha\),
+otherwise females are not the choosy sex). When females re-enter the
+mating pool, they encounter males at a rate of \(R\beta/(\beta + 1)\).
+If a female encounters a male with a nuptial gift, we assume that she
+will mate with him. But if a female encounters a male with no nuptial
+gift, then she might accept or reject the male. If she rejects the male,
+then she will remain in the mating pool. The rate at which a female
+encounters a male with a nuptial gift is,
+
+\[R_{\mathrm{F_{G}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right).\]
+
+Expected time spent in the mating pool before a focal female encounters
+a male with a gift will be \(1/R_{\mathrm{F_{G}}}\). The rate at which a
+female increases her fitness by being choosy and mating only when she
+encounters a male with a gift is,
+
+\[W_{f, g} = \lambda \frac{1 + \gamma}{T_{F} + \frac{1}{R_{\mathrm{F,G}}}}.
+\tag{4}
+\]
+
+The top of the right-hand side of Eq. 4 gives her fitness increase, and
+the bottom gives the total time it takes to obtain this fitness. The
+\(R_{\mathrm{F_{G}}}\) is inverted because it represents the expected
+time to encountering a male with a gift. We can expand Eq. 6,
+
+\[W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right)}}.\]
+
+If the focal female is not choosy and accepts the first male that she
+encounters, then the rate at which she increases her fitness is,
+
+\[W_{\mathrm{F_{G,L}}} = \lambda \frac{\left(1 + \gamma\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)}}.\]
+
+We then evaluate the conditions under which
+\(W_{\mathrm{F_{G}}} > W_{\mathrm{F_{G,L}}}\). We can isolate \(\gamma\)
+to determine how much offspring fitness must be increased to make
+choosiness beneficial (\(\gamma_{\mathrm{f}}\)),
+
+\[\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}} R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right)}.
+\tag{5}
+\]
+
+Note that that the expression
+\(R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right)\)
+defines the rate at which a female in the mating pool encounters males
+with nuptial gifts. Hence, female choosiness is ultimately determined by
+time spent out of the mating pool to process offspring
+(\(T_{\mathrm{f}}\)) and the rate at which a female in the mating pool
+encounters males with nuptial gifts.
+
+\emph{Operational sex ratio}
+
+We assume that the sex ratio is equal upon maturation. Given this, Kokko
+\& Monaghan (\protect\hyperlink{ref-Kokko2001}{2001}) show that the
+operational sex ratio depends on the probability of finding an
+individual in time-in,
+
+\[\beta = \frac{\int_{t = 0}^{\infty} P_{IM}(t)dt}{\int_{t = 0}^{\infty} P_{IF}(t)dt}.
+\tag{6}
+\]
+
+In Eq. 6, \(P_{IM}(t)\) and \(P_{IF}(t)\) are the probabilities of
+finding a male and female in time-in, respectively. There is no closed
+form solution to the operational sex ratio, so we used recursion to
+calculate \(\beta\) values for a given \(T_{\mathrm{f}}\),
+\(T_{\mathrm{m}}\), and \(R\) (see Supporting Information S2),
+
+\hypertarget{individual-based-model}{%
+\subsection{Individual-based model}\label{individual-based-model}}
+
+We formulate an individual-based time-in time-out simulation model to
+complement the predictions made by our analytical time-in time-out model
+above and further allow for coevolution between male search behaviour
+and female choosiness. Here we describe the details of initialisation,
+time-in (mating), time-out (reproduction and nuptial gift search), and
+mortality. We then summarise the simulations run and data collected.
+
+\emph{Initialisation}
+
+Before the first time step, a population of \(N = 1000\) individuals is
+initialised. Individuals are assigned to be female with a probability of
+\(0.5\), else male. Female offspring processing time for a focal
+individual \(i\) is fixed at \(T^{i}_{\mathrm{f}} = 2\). Each individual
+is initialised with a diploid genotype that underlies female rejection
+probability of gift-less males (\(\rho^{i}\)), and a diploid genotype
+that underlies male search time (\(T^{i}_{\mathrm{m}}\)). Alleles can
+take any real value and combine additively to determine \(\rho^{i}\) and
+\(T^{i}_{\mathrm{m}}\). For all simulations, initialised values are set
+to , \(\rho^{i} = 0\), and \(T^{i}_{\mathrm{m}} = 0\). All individuals
+are initialised outside of the mating pool in the first time step
+\(t = 1\). The first time step then proceeds with females immediately
+entering the mating pool and males either entering the mating pool or
+searching for nuptial gifts.
+
+\emph{Time-in}
+
+At the start of each time step, females and males in the mating pool
+remain in it. Females outside the mating pool enter the mating pool
+after processing offspring, and males enter it after searching for
+nuptial gifts (see `Time-out' below). Up to \(\Psi = N\psi\)
+interactions between individuals can occur in a single time step, where
+\(\psi\) is a scaling parameter. In each time step, \(\Psi\) pairs of
+individuals are selected at random to interact. For each interaction,
+two different individuals are randomly selected from the population with
+equal probability. If the selected individuals are of different sexes,
+and both are in the mating pool, then a mating encounter occurs. If the
+male does not have a nuptial gift, then a focal female \(i\) will reject
+him with a probability of \(\rho^{i}\); if rejection occurs, then both
+individuals stay in the mating pool. If rejection does not occur, or the
+male has a nuptial gift in the mating encounter, then the individuals
+mate. Females then leave the mating pool and enter time-out to process
+offspring, and males leave and enter time-out to potentially search for
+new nuptial gifts (note that females and males might re-enter the mating
+pool immediately within the same time step given sufficiently low search
+time; see Time-out below).
+
+\emph{Time-out}
+
+During time-out, offspring production and time outside of the mating
+pool are realised for each female by sampling from a Poisson
+distribution. A focal female \(i\) will produce
+\(\mathrm{Poisson}(\lambda)\) offspring if no nuptial gift was provided
+or \(\mathrm{Poisson}(\lambda + \gamma)\) if a gift was provided.
+Females remain outside of the mating pool to process offspring for
+\(\mathrm{Poisson}(T^{i}_{\mathrm{f}})\) time steps. Offspring are added
+to the population immediately, with one \(\rho^{i}\) and one
+\(T^{i}_{\mathrm{m}}\) allele sampled from each parent with complete
+recombination. Mutation occurs independently for each allele with a
+probability of \(\epsilon = 0.001\), and if mutation occurs, then a new
+allele value is sampled from a normal distribution mean centred on the
+existing value with a standard deviation of \(\sigma_{\epsilon} = 0.1\).
+Offspring sex is randomly assigned with equal probability as female or
+male. Female offspring are immediately placed in the mating pool, and
+male offspring are out of the mating pool to potentially search for
+nuptial gifts. After a female has spent
+\(\mathrm{Poisson}(T^{i}_{\mathrm{f}})\) time steps outside the mating
+pool, she will re-enter it.
+
+A focal male \(i\) outside the mating pool will enter it if he has
+searched for a fixed number of \(T^{i}_{\mathrm{m}}\) time steps, which
+is also sampled randomly from a Poisson distribution,
+\(\mathrm{Poisson}(T^{i}_{\mathrm{m}})\). If \(T^{i}_{\mathrm{m}} = 0\),
+then the male immediately returns to the mating pool (in the same time
+step). If \(T^{i}_{\mathrm{m}} > 0\), then the male must wait outside
+the mating pool for \(\mathrm{Poisson}(T^{i}_{\mathrm{m}})\) time steps,
+but will enter the mating pool with a nuptial gift with a probability,
+
+\[P(G^{i}) = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.\]
+
+Males must always spend \(\mathrm{Poisson}(T^{i}_{\mathrm{m}})\) time
+steps outside of the mating pool regardless of whether or not they are
+successful in obtaining a nuptial gift.
+
+\emph{Mortality}
+
+At the end of each time step, mortality occurs first with a fixed
+probability for all adults in the population, then with a probability
+caused by carrying capacity \(K = 1000\) applied to all individuals
+(adults and offspring). Mortality occurs in each time step with a fixed
+probability of \(\mu\) regardless of the sex of the individual or its
+position in or out of the mating pool. If after this fixed mortality is
+applied, the total population size \(N > K\), then individuals are
+removed at random with equal probability until \(N = K\). Following
+adult mortality, a new time step begins with newly added offspring
+becoming adults.
+
+\emph{Simulations}
+
+We ran simulations in which male search time and female choosiness
+evolved from an ancestral state of no searching and no choosiness. In
+all simulations, \(N\) was initialised at 1000 and \(K = 1000\).
+Simulations ran for \(t_{max} = 10000\) time steps. We set
+\(T_{\mathrm{f}} = 2\), \(\psi = 3\), and \(\lambda = 1\) for all
+simulations, and we simulated across a range of
+\(\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}\) and
+\(\gamma = \{0, 0.1, ..., 1.9, 2.0\}\) parameter values for 5000
+replicates. In a sensitivity analysis, we also re-ran simulations for
+values of \(T_{\mathrm{f}} = 10\) and \(\psi = \{1, 2, 4, 6 \}\) (see
+Supporting Information S3), and simulated the evolution of male nuptial
+gift searching and female choosiness (fixing
+\(T_{\mathrm{m}} = \alpha\)) separately (see Supporting Information S4).
+Summary statistics for mean trait values, population size, sex ratios,
+proportion of females and males in and out of the mating pool, and mean
+number of encounters per female and male within the mating pool were all
+calculated in the last time step. The C code used for simulating these
+IBMs also allows for the reporting of summary statistics in each time
+step. Additionally, it can simulate explicit space and individual
+movement through the landscape. A neutral evolving trait was also
+modelled to ensure that the code functioned as intended, and processes
+were compartmentalised into individual functions to facilitate code
+testing. All code is publicly available on GitHub
+(\url{https://github.com/AUTHOR_NAME/REPOSITORY_NAME}).
+
+\emph{Application to gift-giving spiders}
+
+We can produce an estimate of the fitness increment obtained by females
+when receiving a gift (\(\hat{\gamma}\)) by using data on female
+\emph{P. mirabilis} egg production and hatching success
+(\protect\hyperlink{ref-Tuni2013a}{Tuni \emph{et al.}, 2013}). Tuni
+\emph{et al.} (\protect\hyperlink{ref-Tuni2013a}{2013}) found
+differences in egg production and hatching success in female \emph{P.
+mirabilis} under different feeding regimes. Assuming these differences
+in feeding regimes correspond to eating versus not eating nuptial gifts,
+the mean number of offspring produced by a female who eats nuptial gifts
+can be calculated. This calculation will be an overestimate because
+females that were fed in Tuni \emph{et al.}
+(\protect\hyperlink{ref-Tuni2013a}{2013}) received multiple nuptial
+gifts. Nevertheless, we calculate these means using raw data from Tuni
+\emph{et al.} (\protect\hyperlink{ref-Tuni2013a}{2013}) and find that
+mean offspring produced by females receiving nuptial gifts is
+\(25.74 \pm 0.96\), while offspring produced by females without a
+nuptial gift is \(6.00 \pm 2.1\). Consequently, the relative gain in
+fitness from receiving a nuptial gift for a female is estimated to be
+\(\hat{\delta_\mathrm{f}} = 25.74 / 6.00 = 4.29\). Since the baseline
+fitness is 1, the increase in fitness resulting from a nuptial gift then
+becomes \(\hat{\gamma} = \hat{\delta_{\mathrm{f}}} - 1 = 3.29.\)
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+Our model predicts 4 zones that are delineated by inequalities 2 and 5
+and describe the initial thresholds for the evolution of searching for
+nuptial gifts in males and choosiness for nuptial gifts in females.
+Figure 2a illustrates conditions under which no searching or choosiness
+evolves (zone A), only search (zone B) or choosiness (zone C) evolve, or
+both searching and choosiness evolve (zone D). Blue and red threshold
+lines in Figure 2 are defined by Eq. 2 and Eq. 5, respectively. Figure
+2b illustrates the expansion of zone B as encounter rate decreases,
+which is consistent with the results of our IBM (Figure 3).
 
@@
 search (blue) exceeds zero, indicating evolution of choosiness or
-nuptial gift search. Each point includes data from 3200 replicate
-simulations with identical starting conditions. Red and blue lines show
-thresholds above which the mathematical model predicts that females
-should be choosy and males should search, respectively (in agreement
-with Figure 2). Minor deviations between the analytical model and the
-simulation results are expected due to the finite population size, the
-substantial stochasticity inherent to the simulation model, and the
-potential for coevolution (for details, see Supporting Information S1).
-The number of individuals in the population remained at or near carrying
-capacity of \(K = 1000\). In each time step, up to 3000 total pair-wise
-interactions occurred. Expected female processing time was set to
+nuptial gift search. Each point includes data from 5000 replicate
+simulations with identical starting conditions. Zones are identified
+that correspond to areas where males search and females are choosy (D),
+males search but females are not choosy (B), and males do not search and
+females are not choosy (A), as also depicted in Figure 2. The number of
+individuals in the population remained at or near carrying capacity of
+\(K = 1000\). In each time step, up to 3000 total pair-wise interactions
+occurred. Expected female processing time was set to
 \(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
@@
 
-Male thresholds \(\gamma_{\mathrm{m, IBM}}\) given by ineq. 4 accurately
-predict the evolution of searching in the IBM across \(\alpha\) values,
-and the female threshold \(\gamma_{\mathrm{f, IBM}}\) (ineq. 5) predicts
-the evolution of female choice (Figure 3). In other words, IBM
-simulations demonstrate that nuptial gift search in males, and
-choosiness in females, will evolve from an ancestral state of no
-searching and no choosiness in similar parameter space (Figure 3) as
-predicted by the analytical model (Figure 2b). We further ran the IBM
-with realistic values of \(\gamma\), estimated using data from the
-\emph{P. mirabilis} system wherein choosiness among females, and nuptial
-gift search among males, occur (Figure 4). We found that our IBM
-predicts both the evolution of choosiness and nuptial gift searching
-observed in the \emph{P. mirabilis} system.
-
-\begin{figure}
-\centering
-\includegraphics{ms_files/figure-latex/unnamed-chunk-5-1.pdf}
-\caption{The joint evolution of male search and female choosiness using
-a nuptial gift fitness increment (\(\gamma\)) that was estimated from
-experimental data for the species \emph{Pisaura mirabilis} (mean
-\(\gamma = 3.29 \pm\) SE via propagation of error for estimates of
-nuptial feeding a non-nuptial feeding groups: {[}1.47; 8.32{]}). Points
-show where the 95\% confidence interval exceeds 0 for female choosiness
-(red) and male search (blue). Each point includes data from 100
-replicate simulations with identical starting conditions. The red line
-shows the threshold above which females should be choosy and the blue
-line shows the threshold above which males should search. As predicted
-by the analytical model, both male search and female choosiness evolved
-for a range of \(\gamma\) values around the empirical estimates. This
-occurs because these values result in a \(\gamma\) above the fitness
-threshold necessary for selection to favour male search of nuptial gifts
-(blue line) and female choosiness (red line). The number of individuals
-in the population remained at or near carrying capacity of \(K = 1000\).
-In each time step, up to 3000 total pair-wise interactions occurred.
-Female processing time was set to \(T_{\mathrm{f}}=2\) time steps, and
-\(\gamma\) and \(\alpha\) values in the {[}0.2, 2.0{]}, respectively,
-were used. The parameter \(\gamma\) was estimated as relative increase
-in offspring production such that \(\gamma\) is the factor by which
-fitness increases (relative to the baseline fitness) given a nuptial
-gift (See Supporting Information S5).}
-\end{figure}
+Individual-based model results recover zones A, B, and D (Figure 3). In
+other words, IBM simulations demonstrate that nuptial gift search in
+males, and choosiness in females, will evolve from an ancestral state of
+no searching and no choosiness in similar parameter space (Figure 3) as
+predicted by the analytical model (Figure 2b). Further, although it was
+not possible to parameterise our model for the \emph{P. mirabilis}
+system in detail, our calculated value of \(\hat{\gamma} = 3.29\) is
+consistent with the evolution of nuptial gift searching and choosiness
+recovered by our analytical model and IBM.
 
@@
 
-The simulations parameterised with an experimentally estimated value of
-\(\gamma\) showed evolution of nuptial gift searching in males and
-choosiness for nuptial gifts in females. The model thus predicts that
-\emph{P. mirabilis} living under conditions with the estimated fitness
-value of nuptial gifts should exhibit both search for nuptial gifts and
-choosiness for males with nuptial gifts, and this is what is observed in
-empirical populations. Parameterising \(\gamma\) with data from
-experimental studies may only yield a rough approximation of the true
-\(\gamma\). This is because the estimated value of \(\gamma\) is based
-on data from current populations (rather than ancestral populations,
-which are being simulated), and because the literature is inconclusive
-as to how much (if any) effect nuptial gifts have on female fitness
+For experimentally estimated value of \(\gamma\), simulations showed
+evolution of nuptial gift searching in males and choosiness for nuptial
+gifts in females. The model thus predicts that \emph{P. mirabilis}
+living under conditions with the estimated fitness value of nuptial
+gifts should exhibit both search for nuptial gifts and choosiness for
+males with nuptial gifts, and this is what is observed in empirical
+populations. Parameterising \(\gamma\) with data from experimental
+studies may only yield a rough approximation of the true \(\gamma\).
+This is partly because females were fed multiple nuptial gifts in the
+data we used to calculate the fitness gain from a nuptial gift
+(\protect\hyperlink{ref-Tuni2013a}{Tuni \emph{et al.}, 2013}). It is
+also because the estimated value of \(\gamma\) is based on data from
+current populations (rather than ancestral populations, which are being
+simulated), and because the literature is inconclusive as to how much
+(if any) effect nuptial gifts have on female fitness
 (\protect\hyperlink{ref-Maxwell2018}{Maxwell \& Prokop, 2018}). The
@@
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-\hypertarget{model}{%
-\subsection{Model}\label{model}}
-
-Here we first present more detail for the derivation of fitness
-threshold values \(\gamma_{\mathrm{m}}\) and \(\gamma_{\mathrm{f}}\). We
-then present IBM simulations (see Supporting Information S1 for full
-details). Code for simulations is available on GitHub (see ``Data
-availability'').
-
-\hypertarget{derivation-of-fitness-thresholds}{%
-\subsection{Derivation of fitness
-thresholds}\label{derivation-of-fitness-thresholds}}
-
-We use a time-in and time-out model in which females and males spend
-some time searching for a mate (time-in) followed by a period of cool
-down outside the mating pool (time-out; Figure 1).
-
-After mating, females must spend some time processing offspring
-(\(T_{\mathrm{f}}\)). Male time to replenish sperm is assumed to be
-negligible, but males can spend time out of the mating pool
-(\(T_{\mathrm{m}}\)) to search for a nuptial gift. When males return
-from time-out, they encounter females with some probability that is a
-function of the rate at which an individual encounters conspecifics
-(\(R\)) and the sex ratio (\(\beta\); males/females). Mortality occurs
-for females and males in (\(\mu_{\mathrm{i,f}}\),
-\(\mu_{\mathrm{i,m}}\)) and out (\(\mu_{\mathrm{o,f}}\),
-\(\mu_{\mathrm{o,m}}\)) of the mating pool. Following Kokko \& Ots
-(\protect\hyperlink{ref-Kokko2006}{2006}), we assume
-\(m_{\mathrm{i,f}} = m_{\mathrm{o,f}} = 1\) and
-\(m_{\mathrm{i,m}} = m_{\mathrm{o,m}} = 1\). While this choice is
-arbitrary, we conducted a sensitivity analysis which shows that the
-mortality parameters have no influence on the propensity for male search
-and female choice to evolve (Supporting Information S2). First, we
-describe the fitness consequences of male search time for a nuptial
-gift. We then describe the fitness consequences of female choice to
-accept or reject males based on their provision of a nuptial gift.
-
-\hypertarget{male-fitness}{%
-\subsection{Male fitness}\label{male-fitness}}
-
-During time-out, males have the opportunity to search for a nuptial
-gift. Males can adopt one of two strategies; either search or do not
-search for a nuptial gift. Males with the former strategy continue to
-search until they find a nuptial gift, while males that do not search
-will immediately re-enter the mating pool. In this case, time searching
-for a nuptial gift will come at the cost of mating opportunities but
-might increase offspring fitness. We therefore need to model the
-expected length of time \(E[T_{\mathrm{m}}]\) spent outside of the
-mating pool for males that search for nuptial gifts, which is simply
-\(\alpha\). Note that we can integrate search time \(t\) over the rate
-at which nuptial gifts are encountered (\(\exp(-1/\alpha)\)) to show
-\(E[T_{\mathrm{m}}] = \alpha\),
-
-\[E[T_{\mathrm{m}}] = \int_{0}^{\infty}e^{- \frac{1}{\alpha}t}dt = \alpha.\]
-
-The rate at which a focal male that searches for a nuptial gift
-(\(\mathrm{M_{G}}\)) increases his fitness is therefore the fitness of
-his offspring \((1 + \gamma)\) divided by expected time spent searching
-for a nuptial gift (\(\alpha\)) plus time spent in the mating pool,
-\((\beta + 1)/R\) (recall that females produce \(\lambda\) offspring),
-
-\[W_{\mathrm{M_{G}}} = \lambda \frac{1 + \gamma}{\alpha + \left( \frac{\beta + 1}{R} \right)}.\]
-
-In contrast, a male that does not search for a nuptial gift
-(\(\mathrm{M_{L}}\)) has offspring with lower fitness, but spends less
-time outside of the mating pool,
-
-\[W_{\mathrm{M_{L}}} = \lambda \frac{1}{\left(\frac{\beta+1}{R} \right)} = \lambda \frac{R}{\beta + 1}.\]
-
-We can then determine the conditions for which
-\(W_{\mathrm{M_{G}}} > W_{\mathrm{M_{L}}}\), isolating \(\gamma\) to
-find how large of a fitness benefit must be provided by the nuptial gift
-to make the search cost worthwhile, which simplifies to ineq. 2. When
-this inequality holds, males are favoured to search until they find a
-nuptial gift, which would result in an average search time of
-\(\alpha\). When the male trait is continuous (i.e., males search for
-time period \(T_{\mathrm{m}}\)), it can be shown that the same threshold
-can be reached by evaluating the partial derivative of the male fitness
-function (Supporting Information S3). Hence, the thresholds are
-consistent under different assumptions concerning male searching
-strategy. Selection will cause males to search for nuptial gifts if the
-fitness increase to offspring exceeds the product of search time and
-female encounter rate.
-
-\hypertarget{female-fitness}{%
-\subsection{Female fitness}\label{female-fitness}}
-
-During time-out, females process offspring over a duration of
-\(T_{\mathrm{f}}\) (we assume that \(T_{\mathrm{f}} > \alpha\), else
-females are not the choosy sex). When females re-enter the mating pool,
-they encounter males at a rate of \(R\beta/(\beta + 1)\). If a female
-encounters a male with a nuptial gift, we assume that she will mate with
-him. But if a female encounters a male with no nuptial gift, then she
-might accept or reject the male. If she rejects the male, then she will
-remain in the mating pool. The rate at which a female encounters a male
-with a nuptial gift is,
-
-\[R_{\mathrm{F_{G}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{m}}\right).\]
-
-We can similarly model the rate at which a female encounters a gift-less
-male,
-
-\[R_{\mathrm{F_{L}}} = R \left(\frac{\beta}{\beta + 1}\right)\left(e^{-\frac{1}{\alpha}T_{m}}\right).\]
-
-Note that we can recover the rate at which a female encounters any male,
-
-\[R \left(\frac{\beta}{\beta + 1}\right) = R \left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + R \left(\frac{\beta}{\beta + 1}\right) \left(e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right).\]
-
-If \(R_{\mathrm{F_{G}}}\) is sufficiently high and
-\(R_{\mathrm{F_{L}}}\) is sufficiently low, then finding a male with a
-gift will be easier than finding a male without one. Also, the expected
-time spent in the mating pool before a focal female encounters a male
-with a gift will be \(1/R_{\mathrm{F_{G}}}\), while the expected time
-spent in the mating pool before a focal female encounters any male will
-be \(1 / (R_{\mathrm{F_{G}}} + R_{\mathrm{F_{L}}})\). Finally, the rates
-at which a female encounters males with and without a gift,
-\(R_{\mathrm{F_{G}}}\) and \(R_{\mathrm{F_{L}}}\), are different from
-the probabilities that a male encounter has or does not have a gift. The
-rate of encounter is no longer relevant in this case because we are
-assuming that an encounter has occurred. Hence, the probability of an
-encountered male having a gift is simply,
-
-\[P(G) = \frac{1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}} = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
-
-Similarly, the probability of an encountered male not having a gift is
-simply,
-
-\[P(L) = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
-
-The rate at which a female increases her fitness by being choosy and
-mating only when she encounters a male with a gift is,
-
-\begin{equation}
-W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}}} + \frac{1}{\mathrm{F_{G}}}.
-\end{equation}
-
-The top of the right-hand side of Eq. 6 gives the fitness increase, and
-the bottom gives the total time it takes to obtain this fitness. The
-\(R_{\mathrm{F_{G}}}\) is inverted because it represents the expected
-time to encountering a male with a gift. We can expand Eq. 6,
-
-\[W_{\mathrm{F_{G}}} = \lambda \frac{1 + \gamma}{T_{\mathrm{f}} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right)}}.\]
-
-If the focal female is not choosy and accepts the first male that she
-encounters, then the rate at which she increases her fitness is,
-
-\[W_{\mathrm{F_{G,L}}} = \lambda \frac{\left(1 + \gamma\right)\left(1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}\right) + e^{-\frac{1}{\alpha}T_{\mathrm{m}}}}{T_{f} + \frac{1}{R \left(\frac{\beta}{\beta + 1}\right)}}.\]
-
-We then evaluate the conditions under which
-\(W_{\mathrm{F_{G}}} > W_{\mathrm{F_{G,L}}}\). We isolate \(\gamma\) to
-determine how much offspring fitness must be increased to make
-choosiness beneficial (\(\gamma_{\mathrm{f}}\)),
-
-\[\gamma_{\mathrm{f}} > \frac{1 + \frac{1}{\beta}}{D T_{f} \left(1 - e^{-1\frac{1}{\alpha}T_{m}}\right)}.\]
-
-The above can be expressed as Eq. 7 below,
-
-\begin{equation}
-\gamma_{\mathrm{f}} > \frac{1}{T_{\mathrm{f}}} R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right).
-\end{equation}
-
-Note that that the expression
-\(R\left(\frac{\beta}{\beta + 1}\right) \left(1 - e^{-1\frac{1}{\alpha}T_{\mathrm{m}}}\right)\)
-defines the rate at which a female in the mating pool encounters males
-with nuptial gifts. Hence, female choosiness is ultimately determined by
-time spent out of the mating pool to process offspring
-(\(T_{\mathrm{f}}\)) and the rate at which a female in the mating pool
-encounters males with nuptial gifts.
-
-\hypertarget{operational-sex-ratio}{%
-\subsection{Operational sex ratio}\label{operational-sex-ratio}}
-
-We assume that the sex ratio is equal upon maturation. Given this, Kokko
-\& Monaghan (\protect\hyperlink{ref-Kokko2001}{2001}) show that the
-operational sex ratio depends on the probability of finding an
-individual in time-in,
-
-\begin{equation}
-\beta = \frac{\int_{t = 0}^{\infty} P_{IM}(t)dt}{\int_{t = 0}^{\infty} P_{IF}(t)dt}.
-\end{equation}
-
-In Eq. 8, \(P_{IM}(t)\) and \(P_{IF}(t)\) are the probabilities of
-finding a male and female in time-in, respectively. There is no closed
-form solution to the operational sex ratio, so we used recursion to
-calculate \(\beta\) values for a given \(T_{\mathrm{f}}\),
-\(T_{\mathrm{m}}\), and \(R\) (see Supporting Information S4),
-
-\hypertarget{individual-based-model}{%
-\subsection{Individual-based model}\label{individual-based-model}}
-
-We formulate an individual-based simulation model to test whether the
-predictions made by the analytical time-in time-out model are
-qualitatively the same under a similar simulation model. We use the
-individual-based model to test whether the prediction hold in finite
-populations. The IBM was written in C. All details of the
-initialisation, parameterisation and the specific simulations which we
-run, are described in Supporting Information S1.
-
-We use available experimental data on the effect of nuptial gifts on
-female offspring production to estimate the key parameter \(\gamma\)
-(fitness increment from nuptial gift) and conducted a series of
-simulations where \(\gamma\) was parameterised using this estimated
-value. Details of the estimation of \(\gamma\) are described in
-Supporting Information S5. Separate evolution of male search and female
-choice (i.e., without co-evolution) is simulated in Supporting
-Information S6.
-
-\textbf{Author contributions:} APC and ABD conceived the study. ABD
-constructed the modelling framework with input from APC. APC wrote the
-paper with input from ABD and ABD wrote the IBM model. TB and GB
-provided substantial comments on previous drafts and final text.
-
-\textbf{Acknowledgements:} Anders P. Charmouh was supported by the
-University of Aberdeen. A. Bradley Duthie was supported by the
-University of Stirling. Trine Bilde was supported by The Danish Council
-for Independent Research grant number 4002-00328B. We thank Maria Albo
-for making available data from a previous study which was useful for
-parameter estimating.
+\textbf{Author contributions:} Redacted for anonymous peer review.
+
+\textbf{Acknowledgements:} Redacted for anonymous peer review.
 
@@
 and the full source code is available at
-\url{https://github.com/bradduthie/nuptial_gift_evolution}.
+\url{https://github.com/AUTHOR_NAME/REPOSITORY_NAME}.
 

### 2024-12-20 SI.Rmd
Update last comments based on round of revisions and Evol Lett comments

@@
 |---------------------------------------------------------------|------|
-| S1: Alternative derivation of male fitness threshold          |  2   |
-| S2: Operational sex ratio                                     |  4   |
-| S3: Sensitivity analysis of parameters in IBM                 |  5   |
+| S1: Sensitivity analysis of parameters in IBM                 |  2   |
+| S2: Alternative derivation of male fitness threshold          |  9   |
+| S3: Operational sex ratio                                     |  11  |
 | S4: Separate evolution of male search and female choice       |  12  |
-| References                                                    |  13  |
+| S5: Male probability of search trait                          |  13  |
+| Reference                                                     |  15  |
 
@@
 
-S1: Alternative derivation of male fitness threshold
-------------------------------------
-
-In the main text, we assumed that males made the decision to search or not search for a nuptial gift.
-The expected length of time for which searching males are expected to remain outside of the mating pool is $E[T_{\mathrm{m}}] = \alpha$ (see Model).
-Alternatively, we can assume that males search for a period of $T_{\mathrm{m}}$ and spend this full duration of $T_{\mathrm{m}}$ in the time-out phase, even if they succeed in finding a nuptial gift (as we assumed in our IBM).
-The probability that a male obtains a nuptial gift during this time is modelled in Eq. 1,
-
-$$P(G) = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
-
-In Eq. 1, $\alpha$ is the amount of time expected to pass before a male encounters a nuptial gift. 
-We assume that a male will only enter the mating pool with no gift if they are unsuccessful in obtaining a gift, so the probability that a male obtains no gift after $T_{\mathrm{m}}$ is,
-
-$$P(L) = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
-
-We assume that the fitness increment in reproductive success associated with receiving a nuptial gift versus no nuptial gift are $\lambda(1 + \gamma)$ and $\lambda$, respectively. 
-The rate at which males increase their fitness can then be defined as the expected fitness increment from their nuptial gift search divided by $T_{\mathrm{m}}$ plus the time spent in the mating pool waiting to encounter a mate,
-
-$$W_{\mathrm{m}} = \lambda \frac{P(G)\left(1 + \gamma\right) + P(L)}{T_{\mathrm{m}} + \left( \frac{\beta + 1}{R} \right)}.$$
-
-Our objective now is to determine the conditions under which a focal male increases his fitness by searching for a nuptial gift ($T_{\mathrm{m}}>0$) in a population of resident males that do not search ($T_{\mathrm{m}}=0$).
-Females are assumed to exhibit no choosiness for males with versus without nuptial gifts.
-Under such conditions, male fitness cannot be affected by female choice, so selection to increase $T_{\mathrm{m}}>0$ must be based solely on $\alpha$, $\beta$, $R$, and $\gamma$.
-
-To determine under what conditions male inclusive fitness increases with nuptial gift search time, we can differentiate $W_{\mathrm{m}}$ with respect to $T_{\mathrm{m}}$,
-
-$$\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda\frac{\gamma\left(\frac{\frac{T_{\mathrm{m}} + \frac{\beta + 1}{R}}{\alpha} + 1}{e^{\frac{1}{\alpha}T_{\mathrm{m}}}} - 1\right) - 1}{\left(T_{\mathrm{m}} + \frac{\beta + 1}{R} \right)^{2}}.$$
-
-Because $T_{\mathrm{m}} = 0$, the above simplifies,
-
-$$\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda \frac{\frac{R\gamma\left(\beta + 1\right)}{\alpha} - R^{2}}{\left(1 + \beta \right)^{2}}.$$
-
-We can re-arrange the above,
-
-$$\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)} - \lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}}.$$
-
-Note that if $R = 0$ or $\lambda = 0$, then, trivially, no change in fitness occurs (since females and males cannot mate or do not produce offspring). 
-Fitness is increased by searching for nuptial gifts when $\gamma$ is high, scaled by the expect search time needed to find a nuptial gift. 
-A second term on the right-hand side is subtracted, which reflects a loss in fitness proportional to the encounter rate of potential mates in the mating pool.
-The conditions under which male inclusive fitness increases by searching for a nuptial gift are found by setting $\partial W_{\mathrm{m}}/\partial T_{\mathrm{m}} = 0$ and solving for $\gamma$ to recover Eq.
-2 from the main text,
-
-$$0 = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)} - \lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}},$$
-
-$$\lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}} = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)},$$
-
-$$\frac{R}{{\left(1 + \beta \right)^{2}}} =  \frac{\gamma}{\alpha\left(\beta+1\right)},$$
-
-$$\frac{R}{{\left(1 + \beta \right)}} =  \frac{\gamma}{\alpha},$$
-
-$$\gamma = \alpha \frac{R }{\beta + 1}.$$
-
-\clearpage
-
-S2: Operational sex ratio
-------------------------------------
-
-We assume that the ratio of males to females is the same upon individual maturation.
-Consequently, the operational sex ratio $\beta$ will be a function of $R$, $T_{\mathrm{f}}$, and $T_{\mathrm{m}}$ because these parameters determine the density of females and males in the mating pool versus outside of the mating pool.
-We start with the definition of $\beta$ as being the probability of finding an individual in time-in [@Kokko2001],
-
-$$\beta = \frac{\int_{t=0}^{\infty}P_{IM}(t)dt}{\int_{t=0}^{\infty}P_{IF}(t)dt}$$
-
-We can substitute the equations for $P_{IM}(t)$ and $P_{IF}(t)$, which define the probabilities of males and females being within the mating pool at time $t$, respectively.
-
-We can therefore calculate $\beta$ as below,
-
-$$\beta = \frac{\left( \frac{\left(\frac{\beta + 1}{R}\right)}{T_{\mathrm{m}} + \left(\frac{\beta + 1}{R}\right)} \right)}{\left( \frac{\left(R \frac{\beta}{\beta + 1}\right)}{T_{\mathrm{f}} + \left(R \frac{\beta}{\beta + 1}\right)} \right)}.$$
-
-This can be simplified,
-
-$$\beta = \frac{\left(\beta\left(R + T_{f}\right) + T_{f}\right)\left(\beta + 1\right)}{\beta \left(R^{2}T_{m} + R\right) + \beta^{2}R}.$$
-
-There is no closed form solution for $\beta$, but a recursive algorithm can be used to calculate $\beta$ to an arbitrary degree of precision.
-
-```{r}
-recursive_b <- function(B, D, Tf, Tm, crit = 0.0001, maxit = 9999){
-  conv <- 1;
-  iter <- 0;
-  while(conv > crit & iter < maxit){
-    Fe   <- D * (B / (1 + B));
-    Me   <- (1 + B) / D;
-    Bn   <- (Me / (Tm + Me)) / (Fe / (Tf + Fe));
-    iter <- iter + 1;
-    conv <- abs(Bn - B);
-    B    <- Bn;
-  }
-  return(list(B = B, conv = conv, iter = iter));
-}
-```
-
-We used the above function to calculate values of $\beta$ for the analytical model.
-
-\clearpage
-
-S3: Sensitivity analysis of parameters in IBM
+S1: Sensitivity analysis of parameters in IBM
 ------------------------------------
@@
 
-#points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-#points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-#       lty = "dashed");
-
 for(i in 1:dim(SUMM_Tf10)[1]){
@@
      ylim = c(0, 2.0));
-
-# points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-# points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-#        lty = "dashed");
 
@@
 
-# points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-# points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-#        lty = "dashed");
-
 for(i in 1:dim(SUMM_Nexp2)[1]){
@@
 
-# points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-# points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-#        lty = "dashed");
-
 for(i in 1:dim(SUMM_Nexp6)[1]){
@@
 \captionsetup{labelformat=default}
+
+\clearpage
+
+S2: Alternative derivation of male fitness threshold
+------------------------------------
+
+In the main text, we assumed that males made the decision to search or not search for a nuptial gift.
+The expected length of time for which searching males are expected to remain outside of the mating pool is $E[T_{\mathrm{m}}] = \alpha$ (see Model).
+Alternatively, we can assume that males search for a pre-determined period of $T_{\mathrm{m}}$ and spend this full duration of $T_{\mathrm{m}}$ in the time-out phase, even if they succeed in finding a nuptial gift (as we assumed in our IBM).
+The probability that a male obtains a nuptial gift during this time is modelled in Eq. 1,
+
+$$G = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
+
+In Eq. 1, $\alpha$ is the amount of time expected to pass before a male encounters a nuptial gift. 
+We assume that a male will only enter the mating pool with no gift if they are unsuccessful in obtaining a gift, so the probability that a male obtains no gift after $T_{\mathrm{m}}$ is,
+
+$$L = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.$$
+
+We assume that the fitness associated with receiving a nuptial gift versus no nuptial gift are $\lambda(1 + \gamma)$ and $\lambda$, respectively. 
+The rate at which males increase their fitness can then be defined as the expected fitness increase from their nuptial gift search divided by $T_{\mathrm{m}}$ plus the time spent in the mating pool waiting to encounter a mate,
+
+$$W_{\mathrm{m}} = \lambda \frac{G\left(1 + \gamma\right) + L}{T_{\mathrm{m}} + \left( \frac{\beta + 1}{R} \right)}.$$
+
+Our objective now is to determine the conditions under which a focal male increases his fitness by searching for a nuptial gift ($T_{\mathrm{m}}>0$) in a population of resident males that do not search ($T_{\mathrm{m}}=0$).
+Females are assumed to exhibit no choosiness for males with versus without nuptial gifts.
+Under such conditions, male fitness cannot be affected by female choice, so selection to increase $T_{\mathrm{m}}>0$ must be based solely on $\alpha$, $\beta$, $R$, and $\gamma$.
+
+To determine under what conditions male inclusive fitness increases with nuptial gift search time, we can differentiate $W_{\mathrm{m}}$ with respect to $T_{\mathrm{m}}$,
+
+$$\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda\frac{\gamma\left(\frac{\frac{T_{\mathrm{m}} + \frac{\beta + 1}{R}}{\alpha} + 1}{e^{\frac{1}{\alpha}T_{\mathrm{m}}}} - 1\right) - 1}{\left(T_{\mathrm{m}} + \frac{\beta + 1}{R} \right)^{2}}.$$
+
+Because $T_{\mathrm{m}} = 0$, the above simplifies,
+
+$$\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda \frac{\frac{R\gamma\left(\beta + 1\right)}{\alpha} - R^{2}}{\left(1 + \beta \right)^{2}}.$$
+
+We can re-arrange the above,
+
+$$\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)} - \lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}}.$$
+
+Note that if $R = 0$ or $\lambda = 0$, then, trivially, no change in fitness occurs (since females and males cannot mate or do not produce offspring). 
+Fitness is increased by searching for nuptial gifts when $\gamma$ is high, scaled by the expect search time needed to find a nuptial gift. 
+A second term on the right-hand side is subtracted, which reflects a loss in fitness proportional to the encounter rate of potential mates in the mating pool.
+The threshold for which male inclusive fitness is not affected by searching for a nuptial gift are found by setting $\partial W_{\mathrm{m}}/\partial T_{\mathrm{m}} = 0$ and solving for $\gamma$ to recover Eq.
+2 from the main text,
+
+$$0 = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)} - \lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}},$$
+
+$$\lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}} = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)},$$
+
+$$\frac{R}{{\left(1 + \beta \right)^{2}}} =  \frac{\gamma}{\alpha\left(\beta+1\right)},$$
+
+$$\frac{R}{{\left(1 + \beta \right)}} =  \frac{\gamma}{\alpha},$$
+
+$$\gamma = \alpha \frac{R }{\beta + 1}.$$
+
+\clearpage
+
+S3: Operational sex ratio
+------------------------------------
+
+We assume that the ratio of males to females is the same upon individual maturation.
+Consequently, the operational sex ratio $\beta$ will be a function of $R$, $T_{\mathrm{f}}$, and $T_{\mathrm{m}}$ because these parameters determine the density of females and males in the mating pool versus outside of the mating pool.
+We start with the definition of $\beta$ as being the probability of finding an individual in time-in [@Kokko2001],
+
+$$\beta = \frac{\int_{t=0}^{\infty}P_{IM}(t)dt}{\int_{t=0}^{\infty}P_{IF}(t)dt}$$
+
+We can substitute the equations for $P_{IM}(t)$ and $P_{IF}(t)$, which define the probabilities of males and females being within the mating pool at time $t$, respectively.
+
+We can therefore calculate $\beta$ as below,
+
+$$\beta = \frac{\left( \frac{\left(\frac{\beta + 1}{R}\right)}{T_{\mathrm{m}} + \left(\frac{\beta + 1}{R}\right)} \right)}{\left( \frac{\left(R \frac{\beta}{\beta + 1}\right)}{T_{\mathrm{f}} + \left(R \frac{\beta}{\beta + 1}\right)} \right)}.$$
+
+This can be simplified,
+
+$$\beta = \frac{\left(\beta\left(R + T_{f}\right) + T_{f}\right)\left(\beta + 1\right)}{\beta \left(R^{2}T_{m} + R\right) + \beta^{2}R}.$$
+
+There is no closed form solution for $\beta$, but a recursive algorithm can be used to calculate $\beta$ to an arbitrary degree of precision.
+
+```{r}
+recursive_b <- function(B, D, Tf, Tm, crit = 0.0001, maxit = 9999){
+  conv <- 1;
+  iter <- 0;
+  while(conv > crit & iter < maxit){
+    Fe   <- D * (B / (1 + B));
+    Me   <- (1 + B) / D;
+    Bn   <- (Me / (Tm + Me)) / (Fe / (Tf + Fe));
+    iter <- iter + 1;
+    conv <- abs(Bn - B);
+    B    <- Bn;
+  }
+  return(list(B = B, conv = conv, iter = iter));
+}
+```
+
+We used the above function to calculate values of $\beta$ for the analytical model.
 
@@
 
-References
+S5: Male probability of search trait
+-------------------------------------
+
+In the individual-based model of the main text, a focal male $i$ searches for a nuptial gift for a fixed number of $\mathrm{Poisson}(T^{i}_\mathrm{m})$ time steps.
+The male will remain outside the mating pool for this number of time steps regardless of whether or not he successfully obtains a nuptial gift.
+Here we instead define male search for nuptial gift as an all-or-nothing strategy to align with our analytical model.
+Males either search in time-out until they find a nuptial gift, or they do not search at all.
+In these simulations, $T^{i}_\mathrm{m}$ is instead defined as the probability that a focal male $i$ searches for a nuptial gift (in the same way that $\rho^{i}$ is defined as the probability that a focal female $i$ rejects a male without a nuptial gift).
+For males that decide to search, the time taken until a nuptial gift is obtained is randomly sampled from an exponential distribution with a rate parameter of $\alpha$.
+This sampling time is then rounded to the nearest integer to determine the number of time steps that a focal male spends outside the mating pool before obtaining a nuptial gift.
+
+Results are qualitatively identical to those in Figure 3 of the main text (Figure S5.1)
+
+\captionsetup{labelformat=empty}
+
+```{r echo = FALSE, eval = TRUE, fig.width = 6, fig.height = 6, fig.cap = "Figure S5.1: Coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$) when male strategy is binary: search or do not search.
+Points show where the lower 95% confidence interval of male search (blue) and female choosiness (red) exceeds zero, indicating evolution of nuptial gift search or choosiness.
+Each point includes data from $1000$ replicate simulations with identical starting conditions.
+Zones are identified that correspond to areas where males search and females are choosy (D), males search but females are not choosy (B), and males do not search and females are not choosy (A), as also depicted in Figures 2 and 3 in the main text.
+The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
+In each time step, up to 3000 total pair-wise interactions occurred.
+Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 2.0] and [0.1, 2.0], respectively, were used."}
+SUMM         <- read.csv(file = "inst/Tm_prob.csv");
+alpha_vals   <- sort(unique(SUMM[,1]));  
+TM_vals      <- tapply(X = SUMM[,3],  INDEX = SUMM[,1], FUN = mean);
+m_vals       <- tapply(X = SUMM[,13], INDEX = SUMM[,1], FUN = mean);
+beta_vals    <- tapply(X = SUMM[,14], INDEX = SUMM[,1], FUN = mean);
+Male_M       <- tapply(X = SUMM[,15], INDEX = SUMM[,1], FUN = mean);
+Female_M     <- tapply(X = SUMM[,16], INDEX = SUMM[,1], FUN = mean);
+Mf_nupt      <- tapply(X = SUMM[,17], INDEX = SUMM[,1], FUN = mean);
+Mf_nonupt    <- tapply(X = SUMM[,18], INDEX = SUMM[,1], FUN = mean);
+
+g_m <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
+g_f <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, TF = 2);
+
+par(mar = c(5, 5, 1, 1)); 
+plot(x = alpha_vals, y = g_f, type = "n", lwd = 2, cex.lab = 1.25, col = "red",
+     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
+     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
+                             ")")),
+     ylim = c(0, 2));
+
+for(i in 1:dim(SUMM)[1]){
+  if(SUMM[i, 4] > 0 & SUMM[i, 5] > 0){
+    points(x = SUMM[i, 1], y = SUMM[i, 2], cex = 3, pch = 20, col = "blue");
+  }
+}
+
+for(i in 1:dim(SUMM)[1]){
+  if(SUMM[i, 7] > 0 & SUMM[i, 8] > 0){
+    points(x = SUMM[i, 1], y = SUMM[i, 2], cex = 2, pch = 20, col = "red");
+  }
+}
+points(x = 0.2, y = 1.9, cex = 14, pch = 22, bg = "red", col = "black");
+text(x = 0.2, y = 1.9, labels = "D", cex = 4);
+points(x = 1.3, y = 1.5, cex = 14, pch = 22, bg = "blue", col = "black");
+text(x = 1.3, y = 1.5, labels = "B", cex = 4, col = "white");
+points(x = 1.5, y = 0.5, cex = 14, pch = 22, bg = "white", col = "black");
+text(x = 1.5, y = 0.5, labels = "A", cex = 4);
+```
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+Reference
 =============================================

### 2024-12-20 SI.tex
Update last comments based on round of revisions and Evol Lett comments

@@
 \endhead
-S1: Alternative derivation of male fitness threshold & 2 \\
-S2: Operational sex ratio & 4 \\
-S3: Sensitivity analysis of parameters in IBM & 5 \\
+S1: Sensitivity analysis of parameters in IBM & 2 \\
+S2: Alternative derivation of male fitness threshold & 9 \\
+S3: Operational sex ratio & 11 \\
 S4: Separate evolution of male search and female choice & 12 \\
-References & 13 \\
+S5: Male probability of search trait & 13 \\
+Reference & 15 \\
 \bottomrule
@@
 
-\hypertarget{s1-alternative-derivation-of-male-fitness-threshold}{%
-\subsection{S1: Alternative derivation of male fitness
-threshold}\label{s1-alternative-derivation-of-male-fitness-threshold}}
-
-In the main text, we assumed that males made the decision to search or
-not search for a nuptial gift. The expected length of time for which
-searching males are expected to remain outside of the mating pool is
-\(E[T_{\mathrm{m}}] = \alpha\) (see Model). Alternatively, we can assume
-that males search for a period of \(T_{\mathrm{m}}\) and spend this full
-duration of \(T_{\mathrm{m}}\) in the time-out phase, even if they
-succeed in finding a nuptial gift (as we assumed in our IBM). The
-probability that a male obtains a nuptial gift during this time is
-modelled in Eq. 1,
-
-\[P(G) = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
-
-In Eq. 1, \(\alpha\) is the amount of time expected to pass before a
-male encounters a nuptial gift. We assume that a male will only enter
-the mating pool with no gift if they are unsuccessful in obtaining a
-gift, so the probability that a male obtains no gift after
-\(T_{\mathrm{m}}\) is,
-
-\[P(L) = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
-
-We assume that the fitness increment in reproductive success associated
-with receiving a nuptial gift versus no nuptial gift are
-\(\lambda(1 + \gamma)\) and \(\lambda\), respectively. The rate at which
-males increase their fitness can then be defined as the expected fitness
-increment from their nuptial gift search divided by \(T_{\mathrm{m}}\)
-plus the time spent in the mating pool waiting to encounter a mate,
-
-\[W_{\mathrm{m}} = \lambda \frac{P(G)\left(1 + \gamma\right) + P(L)}{T_{\mathrm{m}} + \left( \frac{\beta + 1}{R} \right)}.\]
-
-Our objective now is to determine the conditions under which a focal
-male increases his fitness by searching for a nuptial gift
-(\(T_{\mathrm{m}}>0\)) in a population of resident males that do not
-search (\(T_{\mathrm{m}}=0\)). Females are assumed to exhibit no
-choosiness for males with versus without nuptial gifts. Under such
-conditions, male fitness cannot be affected by female choice, so
-selection to increase \(T_{\mathrm{m}}>0\) must be based solely on
-\(\alpha\), \(\beta\), \(R\), and \(\gamma\).
-
-To determine under what conditions male inclusive fitness increases with
-nuptial gift search time, we can differentiate \(W_{\mathrm{m}}\) with
-respect to \(T_{\mathrm{m}}\),
-
-\[\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda\frac{\gamma\left(\frac{\frac{T_{\mathrm{m}} + \frac{\beta + 1}{R}}{\alpha} + 1}{e^{\frac{1}{\alpha}T_{\mathrm{m}}}} - 1\right) - 1}{\left(T_{\mathrm{m}} + \frac{\beta + 1}{R} \right)^{2}}.\]
-
-Because \(T_{\mathrm{m}} = 0\), the above simplifies,
-
-\[\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda \frac{\frac{R\gamma\left(\beta + 1\right)}{\alpha} - R^{2}}{\left(1 + \beta \right)^{2}}.\]
-
-We can re-arrange the above,
-
-\[\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)} - \lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}}.\]
-
-Note that if \(R = 0\) or \(\lambda = 0\), then, trivially, no change in
-fitness occurs (since females and males cannot mate or do not produce
-offspring). Fitness is increased by searching for nuptial gifts when
-\(\gamma\) is high, scaled by the expect search time needed to find a
-nuptial gift. A second term on the right-hand side is subtracted, which
-reflects a loss in fitness proportional to the encounter rate of
-potential mates in the mating pool. The conditions under which male
-inclusive fitness increases by searching for a nuptial gift are found by
-setting \(\partial W_{\mathrm{m}}/\partial T_{\mathrm{m}} = 0\) and
-solving for \(\gamma\) to recover Eq. 2 from the main text,
-
-\[0 = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)} - \lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}},\]
-
-\[\lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}} = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)},\]
-
-\[\frac{R}{{\left(1 + \beta \right)^{2}}} =  \frac{\gamma}{\alpha\left(\beta+1\right)},\]
-
-\[\frac{R}{{\left(1 + \beta \right)}} =  \frac{\gamma}{\alpha},\]
-
-\[\gamma = \alpha \frac{R }{\beta + 1}.\]
-
-\clearpage
-
-\hypertarget{s2-operational-sex-ratio}{%
-\subsection{S2: Operational sex ratio}\label{s2-operational-sex-ratio}}
-
-We assume that the ratio of males to females is the same upon individual
-maturation. Consequently, the operational sex ratio \(\beta\) will be a
-function of \(R\), \(T_{\mathrm{f}}\), and \(T_{\mathrm{m}}\) because
-these parameters determine the density of females and males in the
-mating pool versus outside of the mating pool. We start with the
-definition of \(\beta\) as being the probability of finding an
-individual in time-in (\protect\hyperlink{ref-Kokko2001}{Kokko \&
-Monaghan, 2001}),
-
-\[\beta = \frac{\int_{t=0}^{\infty}P_{IM}(t)dt}{\int_{t=0}^{\infty}P_{IF}(t)dt}\]
-
-We can substitute the equations for \(P_{IM}(t)\) and \(P_{IF}(t)\),
-which define the probabilities of males and females being within the
-mating pool at time \(t\), respectively.
-
-We can therefore calculate \(\beta\) as below,
-
-\[\beta = \frac{\left( \frac{\left(\frac{\beta + 1}{R}\right)}{T_{\mathrm{m}} + \left(\frac{\beta + 1}{R}\right)} \right)}{\left( \frac{\left(R \frac{\beta}{\beta + 1}\right)}{T_{\mathrm{f}} + \left(R \frac{\beta}{\beta + 1}\right)} \right)}.\]
-
-This can be simplified,
-
-\[\beta = \frac{\left(\beta\left(R + T_{f}\right) + T_{f}\right)\left(\beta + 1\right)}{\beta \left(R^{2}T_{m} + R\right) + \beta^{2}R}.\]
-
-There is no closed form solution for \(\beta\), but a recursive
-algorithm can be used to calculate \(\beta\) to an arbitrary degree of
-precision.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{recursive\_b }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(B, D, Tf, Tm, }\AttributeTok{crit =} \FloatTok{0.0001}\NormalTok{, }\AttributeTok{maxit =} \DecValTok{9999}\NormalTok{)\{}
-\NormalTok{  conv }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{;}
-\NormalTok{  iter }\OtherTok{\textless{}{-}} \DecValTok{0}\NormalTok{;}
-  \ControlFlowTok{while}\NormalTok{(conv }\SpecialCharTok{\textgreater{}}\NormalTok{ crit }\SpecialCharTok{\&}\NormalTok{ iter }\SpecialCharTok{\textless{}}\NormalTok{ maxit)\{}
-\NormalTok{    Fe   }\OtherTok{\textless{}{-}}\NormalTok{ D }\SpecialCharTok{*}\NormalTok{ (B }\SpecialCharTok{/}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+}\NormalTok{ B));}
-\NormalTok{    Me   }\OtherTok{\textless{}{-}}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+}\NormalTok{ B) }\SpecialCharTok{/}\NormalTok{ D;}
-\NormalTok{    Bn   }\OtherTok{\textless{}{-}}\NormalTok{ (Me }\SpecialCharTok{/}\NormalTok{ (Tm }\SpecialCharTok{+}\NormalTok{ Me)) }\SpecialCharTok{/}\NormalTok{ (Fe }\SpecialCharTok{/}\NormalTok{ (Tf }\SpecialCharTok{+}\NormalTok{ Fe));}
-\NormalTok{    iter }\OtherTok{\textless{}{-}}\NormalTok{ iter }\SpecialCharTok{+} \DecValTok{1}\NormalTok{;}
-\NormalTok{    conv }\OtherTok{\textless{}{-}} \FunctionTok{abs}\NormalTok{(Bn }\SpecialCharTok{{-}}\NormalTok{ B);}
-\NormalTok{    B    }\OtherTok{\textless{}{-}}\NormalTok{ Bn;}
-\NormalTok{  \}}
-  \FunctionTok{return}\NormalTok{(}\FunctionTok{list}\NormalTok{(}\AttributeTok{B =}\NormalTok{ B, }\AttributeTok{conv =}\NormalTok{ conv, }\AttributeTok{iter =}\NormalTok{ iter));}
-\NormalTok{\}}
-\end{Highlighting}
-\end{Shaded}
-
-We used the above function to calculate values of \(\beta\) for the
-analytical model.
-
-\clearpage
-
-\hypertarget{s3-sensitivity-analysis-of-parameters-in-ibm}{%
-\subsection{S3: Sensitivity analysis of parameters in
-IBM}\label{s3-sensitivity-analysis-of-parameters-in-ibm}}
+\hypertarget{s1-sensitivity-analysis-of-parameters-in-ibm}{%
+\subsection{S1: Sensitivity analysis of parameters in
+IBM}\label{s1-sensitivity-analysis-of-parameters-in-ibm}}
 
@@
 \centering
-\includegraphics{SI_files/figure-latex/unnamed-chunk-3-1.pdf}
+\includegraphics{SI_files/figure-latex/unnamed-chunk-2-1.pdf}
 \caption{Figure S2.1: Evolution of both male search (blue) and female
@@
 \centering
-\includegraphics{SI_files/figure-latex/unnamed-chunk-4-1.pdf}
+\includegraphics{SI_files/figure-latex/unnamed-chunk-3-1.pdf}
 \caption{Figure S2.3 (\(T_{\mathrm{f}} = 10.0\)): The coevolution of
@@
 \centering
-\includegraphics{SI_files/figure-latex/unnamed-chunk-5-1.pdf}
+\includegraphics{SI_files/figure-latex/unnamed-chunk-4-1.pdf}
 \caption{Figure S2.4 (\(\psi = 1\)): The coevolution of male search and
@@
 \centering
-\includegraphics{SI_files/figure-latex/unnamed-chunk-6-1.pdf}
+\includegraphics{SI_files/figure-latex/unnamed-chunk-5-1.pdf}
 \caption{Figure S2.5 (\(\psi = 2\)): The coevolution of male search and
@@
 \centering
-\includegraphics{SI_files/figure-latex/unnamed-chunk-7-1.pdf}
+\includegraphics{SI_files/figure-latex/unnamed-chunk-6-1.pdf}
 \caption{Figure S2.6 (\(\psi = 4\)): The coevolution of male search and
@@
 \centering
-\includegraphics{SI_files/figure-latex/unnamed-chunk-8-1.pdf}
+\includegraphics{SI_files/figure-latex/unnamed-chunk-7-1.pdf}
 \caption{Figure S2.7 (\(\psi = 6\)): The coevolution of male search and
@@
 \captionsetup{labelformat=default}
+
+\clearpage
+
+\hypertarget{s2-alternative-derivation-of-male-fitness-threshold}{%
+\subsection{S2: Alternative derivation of male fitness
+threshold}\label{s2-alternative-derivation-of-male-fitness-threshold}}
+
+In the main text, we assumed that males made the decision to search or
+not search for a nuptial gift. The expected length of time for which
+searching males are expected to remain outside of the mating pool is
+\(E[T_{\mathrm{m}}] = \alpha\) (see Model). Alternatively, we can assume
+that males search for a pre-determined period of \(T_{\mathrm{m}}\) and
+spend this full duration of \(T_{\mathrm{m}}\) in the time-out phase,
+even if they succeed in finding a nuptial gift (as we assumed in our
+IBM). The probability that a male obtains a nuptial gift during this
+time is modelled in Eq. 1,
+
+\[G = 1 - e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
+
+In Eq. 1, \(\alpha\) is the amount of time expected to pass before a
+male encounters a nuptial gift. We assume that a male will only enter
+the mating pool with no gift if they are unsuccessful in obtaining a
+gift, so the probability that a male obtains no gift after
+\(T_{\mathrm{m}}\) is,
+
+\[L = e^{-\frac{1}{\alpha}T_{\mathrm{m}}}.\]
+
+We assume that the fitness associated with receiving a nuptial gift
+versus no nuptial gift are \(\lambda(1 + \gamma)\) and \(\lambda\),
+respectively. The rate at which males increase their fitness can then be
+defined as the expected fitness increase from their nuptial gift search
+divided by \(T_{\mathrm{m}}\) plus the time spent in the mating pool
+waiting to encounter a mate,
+
+\[W_{\mathrm{m}} = \lambda \frac{G\left(1 + \gamma\right) + L}{T_{\mathrm{m}} + \left( \frac{\beta + 1}{R} \right)}.\]
+
+Our objective now is to determine the conditions under which a focal
+male increases his fitness by searching for a nuptial gift
+(\(T_{\mathrm{m}}>0\)) in a population of resident males that do not
+search (\(T_{\mathrm{m}}=0\)). Females are assumed to exhibit no
+choosiness for males with versus without nuptial gifts. Under such
+conditions, male fitness cannot be affected by female choice, so
+selection to increase \(T_{\mathrm{m}}>0\) must be based solely on
+\(\alpha\), \(\beta\), \(R\), and \(\gamma\).
+
+To determine under what conditions male inclusive fitness increases with
+nuptial gift search time, we can differentiate \(W_{\mathrm{m}}\) with
+respect to \(T_{\mathrm{m}}\),
+
+\[\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda\frac{\gamma\left(\frac{\frac{T_{\mathrm{m}} + \frac{\beta + 1}{R}}{\alpha} + 1}{e^{\frac{1}{\alpha}T_{\mathrm{m}}}} - 1\right) - 1}{\left(T_{\mathrm{m}} + \frac{\beta + 1}{R} \right)^{2}}.\]
+
+Because \(T_{\mathrm{m}} = 0\), the above simplifies,
+
+\[\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda \frac{\frac{R\gamma\left(\beta + 1\right)}{\alpha} - R^{2}}{\left(1 + \beta \right)^{2}}.\]
+
+We can re-arrange the above,
+
+\[\frac{\partial W_{\mathrm{m}}}{\partial T_{\mathrm{m}}} = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)} - \lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}}.\]
+
+Note that if \(R = 0\) or \(\lambda = 0\), then, trivially, no change in
+fitness occurs (since females and males cannot mate or do not produce
+offspring). Fitness is increased by searching for nuptial gifts when
+\(\gamma\) is high, scaled by the expect search time needed to find a
+nuptial gift. A second term on the right-hand side is subtracted, which
+reflects a loss in fitness proportional to the encounter rate of
+potential mates in the mating pool. The threshold for which male
+inclusive fitness is not affected by searching for a nuptial gift are
+found by setting \(\partial W_{\mathrm{m}}/\partial T_{\mathrm{m}} = 0\)
+and solving for \(\gamma\) to recover Eq. 2 from the main text,
+
+\[0 = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)} - \lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}},\]
+
+\[\lambda\frac{R^{2}}{{\left(1 + \beta \right)^{2}}} = \lambda \frac{R\gamma}{\alpha\left(\beta+1\right)},\]
+
+\[\frac{R}{{\left(1 + \beta \right)^{2}}} =  \frac{\gamma}{\alpha\left(\beta+1\right)},\]
+
+\[\frac{R}{{\left(1 + \beta \right)}} =  \frac{\gamma}{\alpha},\]
+
+\[\gamma = \alpha \frac{R }{\beta + 1}.\]
+
+\clearpage
+
+\hypertarget{s3-operational-sex-ratio}{%
+\subsection{S3: Operational sex ratio}\label{s3-operational-sex-ratio}}
+
+We assume that the ratio of males to females is the same upon individual
+maturation. Consequently, the operational sex ratio \(\beta\) will be a
+function of \(R\), \(T_{\mathrm{f}}\), and \(T_{\mathrm{m}}\) because
+these parameters determine the density of females and males in the
+mating pool versus outside of the mating pool. We start with the
+definition of \(\beta\) as being the probability of finding an
+individual in time-in (\protect\hyperlink{ref-Kokko2001}{Kokko \&
+Monaghan, 2001}),
+
+\[\beta = \frac{\int_{t=0}^{\infty}P_{IM}(t)dt}{\int_{t=0}^{\infty}P_{IF}(t)dt}\]
+
+We can substitute the equations for \(P_{IM}(t)\) and \(P_{IF}(t)\),
+which define the probabilities of males and females being within the
+mating pool at time \(t\), respectively.
+
+We can therefore calculate \(\beta\) as below,
+
+\[\beta = \frac{\left( \frac{\left(\frac{\beta + 1}{R}\right)}{T_{\mathrm{m}} + \left(\frac{\beta + 1}{R}\right)} \right)}{\left( \frac{\left(R \frac{\beta}{\beta + 1}\right)}{T_{\mathrm{f}} + \left(R \frac{\beta}{\beta + 1}\right)} \right)}.\]
+
+This can be simplified,
+
+\[\beta = \frac{\left(\beta\left(R + T_{f}\right) + T_{f}\right)\left(\beta + 1\right)}{\beta \left(R^{2}T_{m} + R\right) + \beta^{2}R}.\]
+
+There is no closed form solution for \(\beta\), but a recursive
+algorithm can be used to calculate \(\beta\) to an arbitrary degree of
+precision.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{recursive\_b }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(B, D, Tf, Tm, }\AttributeTok{crit =} \FloatTok{0.0001}\NormalTok{, }\AttributeTok{maxit =} \DecValTok{9999}\NormalTok{)\{}
+\NormalTok{  conv }\OtherTok{\textless{}{-}} \DecValTok{1}\NormalTok{;}
+\NormalTok{  iter }\OtherTok{\textless{}{-}} \DecValTok{0}\NormalTok{;}
+  \ControlFlowTok{while}\NormalTok{(conv }\SpecialCharTok{\textgreater{}}\NormalTok{ crit }\SpecialCharTok{\&}\NormalTok{ iter }\SpecialCharTok{\textless{}}\NormalTok{ maxit)\{}
+\NormalTok{    Fe   }\OtherTok{\textless{}{-}}\NormalTok{ D }\SpecialCharTok{*}\NormalTok{ (B }\SpecialCharTok{/}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+}\NormalTok{ B));}
+\NormalTok{    Me   }\OtherTok{\textless{}{-}}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+}\NormalTok{ B) }\SpecialCharTok{/}\NormalTok{ D;}
+\NormalTok{    Bn   }\OtherTok{\textless{}{-}}\NormalTok{ (Me }\SpecialCharTok{/}\NormalTok{ (Tm }\SpecialCharTok{+}\NormalTok{ Me)) }\SpecialCharTok{/}\NormalTok{ (Fe }\SpecialCharTok{/}\NormalTok{ (Tf }\SpecialCharTok{+}\NormalTok{ Fe));}
+\NormalTok{    iter }\OtherTok{\textless{}{-}}\NormalTok{ iter }\SpecialCharTok{+} \DecValTok{1}\NormalTok{;}
+\NormalTok{    conv }\OtherTok{\textless{}{-}} \FunctionTok{abs}\NormalTok{(Bn }\SpecialCharTok{{-}}\NormalTok{ B);}
+\NormalTok{    B    }\OtherTok{\textless{}{-}}\NormalTok{ Bn;}
+\NormalTok{  \}}
+  \FunctionTok{return}\NormalTok{(}\FunctionTok{list}\NormalTok{(}\AttributeTok{B =}\NormalTok{ B, }\AttributeTok{conv =}\NormalTok{ conv, }\AttributeTok{iter =}\NormalTok{ iter));}
+\NormalTok{\}}
+\end{Highlighting}
+\end{Shaded}
+
+We used the above function to calculate values of \(\beta\) for the
+analytical model.
 
@@
 
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
+\hypertarget{s5-male-probability-of-search-trait}{%
+\subsection{S5: Male probability of search
+trait}\label{s5-male-probability-of-search-trait}}
+
+In the individual-based model of the main text, a focal male \(i\)
+searches for a nuptial gift for a fixed number of
+\(\mathrm{Poisson}(T^{i}_\mathrm{m})\) time steps. The male will remain
+outside the mating pool for this number of time steps regardless of
+whether or not he successfully obtains a nuptial gift. Here we instead
+define male search for nuptial gift as an all-or-nothing strategy to
+align with our analytical model. Males either search in time-out until
+they find a nuptial gift, or they do not search at all. In these
+simulations, \(T^{i}_\mathrm{m}\) is instead defined as the probability
+that a focal male \(i\) searches for a nuptial gift (in the same way
+that \(\rho^{i}\) is defined as the probability that a focal female
+\(i\) rejects a male without a nuptial gift). For males that decide to
+search, the time taken until a nuptial gift is obtained is randomly
+sampled from an exponential distribution with a rate parameter of
+\(\alpha\). This sampling time is then rounded to the nearest integer to
+determine the number of time steps that a focal male spends outside the
+mating pool before obtaining a nuptial gift.
+
+Results are qualitatively identical to those in Figure 3 of the main
+text (Figure S5.1)
+
+\captionsetup{labelformat=empty}
+
+\begin{figure}
+\centering
+\includegraphics{SI_files/figure-latex/unnamed-chunk-10-1.pdf}
+\caption{Figure S5.1: Coevolution of male search and female choosiness
+as a function of nuptial gift search time (\(\alpha\)) when male
+strategy is binary: search or do not search. Points show where the lower
+95\% confidence interval of male search (blue) and female choosiness
+(red) exceeds zero, indicating evolution of nuptial gift search or
+choosiness. Each point includes data from \(1000\) replicate simulations
+with identical starting conditions. Zones are identified that correspond
+to areas where males search and females are choosy (D), males search but
+females are not choosy (B), and males do not search and females are not
+choosy (A), as also depicted in Figures 2 and 3 in the main text. The
+number of individuals in the population remained at or near carrying
+capacity of \(K = 1000\). In each time step, up to 3000 total pair-wise
+interactions occurred. Expected female processing time was set to
+\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
+the range {[}0.0, 2.0{]} and {[}0.1, 2.0{]}, respectively, were used.}
+\end{figure}
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
+\hypertarget{reference}{%
+\section*{Reference}\label{reference}}
+\addcontentsline{toc}{section}{Reference}
 

### 2024-12-20 index.Rmd
Update last comments based on round of revisions and Evol Lett comments

@@
 enter time-out) at a rate that is dependent on $\\beta$ and $R$.
-Males and females undergo sex-specific mortality $\\mu$ during time-in and time-out.
+Males and females undergo mortality $\\mu$ during time-in and time-out.
 Image left to right: (1) male \\textit{P.
@@
 
-The probability that a male succeeds in securing a nuptial gift ($G$) after a duration of $T_{\mathrm{m}}$ is defined by,
-
-$$P(G) = 1 - e^{-\frac{1}{\alpha}T_{m}}.
+The probability that a male who searches for an interval $T_{\mathrm{m}}$, and does not die during this period, finds a nuptial gift is given by,
+
+$$G = 1 - e^{-\frac{1}{\alpha}T_{m}}.
 \tag{1}
@@
 We assume that mating with a nuptial gift increases expected offspring production by an increment of $\gamma$.
-Mortality occurs for females and males in ($\mu_{\mathrm{i,f}}$, $\mu_{\mathrm{i,m}}$) and out ($\mu_{\mathrm{o,f}}$, $\mu_{\mathrm{o,m}}$) of the mating pool. 
-Following @Kokko2006, we assume $m_{\mathrm{i,f}} = m_{\mathrm{o,f}} = 1$ and $m_{\mathrm{i,m}} = m_{\mathrm{o,m}} = 1$.
+
+Mortality of $\mu_{\mathrm{f}}$ and $\mu_{\mathrm{m}}$ for females and males, respectively, occurs both in and out of the mating pool.
+Following @Kokko2006, we assume $\mu_{\mathrm{f}} = \mu_{\mathrm{m}} = 1$.
+Assuming identical mortality both in and out of the mating pool means that individual phenotypes (search strategy and choosiness) do not affect mortality.
+This allows us to use a rate-maximisation model wherein maximisation of reproductive rate while alive is equivalent to maximising lifetime reproductive success [@Kokko2008; @Jennions2017].
+Here maximisation of lifetime reproductive success is the same as maximising fitness because we do not model social interaction between relatives [@Mylius1995; @Fromhage2024].
+It should therefore be noted that if mortality differs inside and outside of the mating pool, reproductive rate while alive will no longer be equivalent to fitness.
+Nevertheless, we also investigated the evolution of both traits when mortality rates in and out of the mating pool differed substantially (see Supporting Information S1).
 
@@
 Males with the searching strategy continue to search until they find a nuptial gift, while males that do not search immediately re-enter the mating pool. 
-Consequently, time searching for a nuptial gift will come at the cost of mating opportunities but might increase offspring fitness. 
+Consequently, time searching for a nuptial gift will come at the cost of mating opportunities but might increase fecundity. 
 We therefore need to model the expected length of time spent outside of the mating pool for males that search for nuptial gifts ($E[T_{\mathrm{m}}]$), which equals $\alpha$. 
@@
 When this inequality holds, males are favoured to search until they find a nuptial gift, which would result in an average search time of $\alpha$. 
-If the male trait is instead continuous (i.e., males search for time period $T_{\mathrm{m}}$), it can be shown that the same threshold can be reached by evaluating the partial derivative of the male fitness function (Supporting Information S1).
+If the male trait is instead continuous (i.e., males search for time period $T_{\mathrm{m}}$), it can be shown that the same threshold can be reached by evaluating the partial derivative of the male fitness function (Supporting Information S2).
 Hence, the thresholds are consistent under different assumptions concerning male searching strategy.
@@
 We then evaluate the conditions under which $W_{\mathrm{F_{G}}} > W_{\mathrm{F_{G,L}}}$. 
-We can isolate $\gamma$ to determine how much offspring fitness must be increased to make choosiness beneficial ($\gamma_{\mathrm{f}}$),
+We can isolate $\gamma$ to determine how much fecundity must be increased to make choosiness beneficial ($\gamma_{\mathrm{f}}$),
 
@@
 
-In Eq. 6, $P_{IM}(t)$ and $P_{IF}(t)$ are the probabilities of finding a male and female in time-in, respectively. 
-There is no closed form solution to the operational sex ratio, so we used recursion to calculate $\beta$ values for a given $T_{\mathrm{f}}$, $T_{\mathrm{m}}$, and $R$ (see Supporting Information S2),
+In Eq. 6, $P_{IM}(t)$ and $P_{IF}(t)$ are the probabilities of finding a male and female in time-in at time $t$, respectively. 
+There is no closed form solution to the operational sex ratio, so we used recursion to calculate $\beta$ values for a given $T_{\mathrm{f}}$, $T_{\mathrm{m}}$, and $R$ (see Supporting Information S3),
 
@@
 
-$$P(G^{i}) = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.$$
+$$G^{i} = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.$$
 
@@
 Simulations ran for $t_{max} = 10000$ time steps. 
-We set $T_{\mathrm{f}} = 2$, $\psi = 3$, and $\lambda = 1$ for all simulations, and we simulated across a range of $\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}$ and $\gamma = \{0, 0.1, ..., 1.9, 2.0\}$ parameter values for 3000 replicates.
+We set $T_{\mathrm{f}} = 2$, $\psi = 3$, and $\lambda = 1$ for all simulations, and we simulated across a range of $\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}$ and $\gamma = \{0, 0.1, ..., 1.9, 2.0\}$ parameter values for 5000 replicates.
+In a sensitivity analysis, we also re-ran simulations for values of $T_{\mathrm{f}} = 10$ and $\psi = \{1, 2, 4, 6 \}$ (see Supporting Information S4), and simulated the evolution of male nuptial gift searching and female choosiness (fixing $T_{\mathrm{m}} = \alpha$) separately (see Supporting Information S4).
+
+We additionally ran simulations in which males adopted one of two search strategies: either search in time-out until a gift is obtained, or do not search at all.
+This simulations were therefore more closely aligned with the assumptions of our analytical model, but results did not differ qualitatively (Supporting Information S5).
+The strategy adopted by a male in these simulations was based on an underlying trait for the probability of nuptial gift search.
+Like $\phi^{i}$, this trait was underpinned by a diploid genotype in which alleles had additive effects.
+
 Summary statistics for mean trait values, population size, sex ratios, proportion of females and males in and out of the mating pool, and mean number of encounters per female and male within the mating pool were all calculated in the last time step.
@@
 All code is publicly available on GitHub (https://github.com/bradduthie/nuptial_gift_evolution).
-
-<!---
-
-A set of simulations with a value of $\gamma$ calculated from empirical data was also conducted (100 replicates). 
-Here, $\gamma$ was parameterised using data on egg production as a function of eating nuptial gifts (see below). 
-Additional simulation sets with lower and upper bounds of the estimated $\gamma$ were subsequently run. 
-In the simulation sets with experimentally derived parameter values, all other parameters were identical to previous simulation batches.
-
---->
 
@@
 
-```{r, echo = FALSE, fig.width = 8, fig.height = 4, fig.cap = "Fitness thresholds above which males increase their fitness by searching for nuptial gifts (blue lines; Eq.
+```{r, echo = FALSE, fig.width = 8, fig.height = 4, fig.cap = "Fecundity increment above which males increase their fitness by searching for nuptial gifts (blue lines; Eq.
 2) and females increase their fitness by rejecting males that do not offer gifts (red lines; Eq.
@@
 Arrows in panel a indicate the effect of increasing encounter rate ($R$), female time-out ($T_{\\mathrm{f}}$), and male search time ($T_{\\mathrm{m}}$).
-As an example, trajectories for $T_{\\mathrm{f}} = 2$, and $T_{\\mathrm{m}} = \\alpha$ are shown for values of $R=2$ (panel a) and $R = 1$ (panel b).
+As an example, curves for $T_{\\mathrm{f}} = 2$, and $T_{\\mathrm{m}} = \\alpha$ are shown for values of $R=2$ (panel a) and $R = 1$ (panel b).
 Females are assumed to be the choosy sex, which is maintained as long as $\\alpha < T_{\\mathrm{f}}$."}
@@
 For females, if $\gamma$ is sufficiently high, fitness is increased by rejecting males without gifts and mating only with males that provide nuptial gifts. 
-As offspring processing time ($T_{\mathrm{f}}$), mate encounter rate ($R\beta / (\beta + 1)$), or the probability of a male finding a nuptial gift ($1 - \exp(-T_{\mathrm{m}}/\alpha)$ ) decrease, the threshold value of fitness above which selection will favour choosiness ($\gamma_{\mathrm{f}}$) increases.
+As offspring processing time ($T_{\mathrm{f}}$), mate encounter rate ($R\beta / (\beta + 1)$), or the probability of a male finding a nuptial gift ($1 - \exp(-T_{\mathrm{m}}/\alpha)$ ) decrease, the fecundity increment above which selection will favour choosiness ($\gamma_{\mathrm{f}}$) increases.
 This can be understood intuitively by realising that rejecting a prospective male represents an opportunity cost for the female.
@@
 As an example, sizable areas of parameter space exists wherein the female optimum would be to exhibit preference for (and receive) nuptial gifts, while the male optimum is to not search for (and give) nuptial gifts (see Figure 2a, Zone C).
-This will lead to encounter where giftless males would benefit the most from mating, but female would benefit most from mating and receiving a gift (i.e., evolutionary interests do not always overlap with respect to mating strategy between the sexes).
+This will lead to encounters where gift-less males would benefit the most from mating, but females would benefit most from mating and receiving a gift (i.e., evolutionary interests do not always overlap with respect to mating strategy between the sexes).
 In many systems, ecological variables such as search time required to find a nuptial gift will likely depend on prey abundance,  which can vary substantially with time in some species with nuptial gift-giving [@Ghislandi2018].
@@
 For example, if female processing time ($T_{\mathrm{f}}$) is high, the female threshold for choosiness with respect to $\gamma$ drops such that male search and female choosiness are favoured at lower $\gamma$.
-If $T_{\mathrm{f}}$ is sufficiently high, then an initially rare gift-giving trait might be favoured by selection even if the fitness benefit of a nuptial gift is low.
+If $T_{\mathrm{f}}$ is sufficiently high, then an initially rare gift-giving trait might be favoured by selection even if the fitness benefit of a nuptial gift is low (assuming variation in choosiness for gifts existed among females).
 The effect that nuptial gifts have on fitness might vary across species, or even populations.
-Effects on female fecundity have been estimated in crickets, fireflies, butterflies, and spiders, but these estimates vary considerably between species suggesting a large positive effect to no effect at all [@Bergstrom2002; @Gao2019; @Maxwell2018; @Rooney2002].
+Effects on female fecundity have been estimated in crickets, fireflies, butterflies, and spiders, but these estimates vary considerably.
+For example, one study of crickets (*Oecanthus nigricornis*) found that more nuptial feeding could increase female reproductive lifespan by approximately 50\% [@Brown1997], and a study on fireflies (*Photinus ignites* and *Ellychnia corrusca*) reported an increase in fecundity of 73\% for females consuming multiple nuptial gifts [@Rooney2002].
+However, other studies on different systems have reported very varying effects or even no effect at all [@Bergstrom2002; @Gao2019; @Maxwell2018; @Rooney2002].
 
@@
 
-# points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-# points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-#        lty = "dashed");
-
 for(i in 1:dim(SUMM_Nexp1)[1]){
@@
 
-# points(x = alpha_vals, y = g_m, type = "l", lwd = 2, col = "blue");
-# points(x = alpha_vals, y = g_f, type = "l", lwd = 2, col = "red", 
-#        lty = "dashed");
-
 for(i in 1:dim(SUMM_Nexp4)[1]){
@@
 \captionsetup{labelformat=default}
+
+S5: Male probability of search trait
+-------------------------------------
+
+In the individual-based model of the main text, a focal male $i$ searches for a nuptial gift for a fixed number of $\mathrm{Poisson}(T^{i}_\mathrm{m})$ time steps.
+The male will remain outside the mating pool for this number of time steps regardless of whether or not he successfully obtains a nuptial gift.
+Here we instead define male search for nuptial gift as an all-or-nothing strategy to align with our analytical model.
+Males either search in time-out until they find a nuptial gift, or they do not search at all.
+In these simulations, $T^{i}_\mathrm{m}$ is instead defined as the probability that a focal male $i$ searches for a nuptial gift (in the same way that $\rho^{i}$ is defined as the probability that a focal female $i$ rejects a male without a nuptial gift).
+For males that decide to search, the time taken until a nuptial gift is obtained is randomly sampled from an exponential distribution with a rate parameter of $\alpha$.
+This sampling time is then rounded to the nearest integer to determine the number of time steps that a focal male spends outside the mating pool before obtaining a nuptial gift.
+
+Results are qualitatively identical to those in Figure 3 of the main text (Figure S5.1)
+
+\captionsetup{labelformat=empty}
+
+```{r echo = FALSE, eval = TRUE, fig.width = 6, fig.height = 6, fig.cap = "Figure S5.1: Coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$) when male strategy is binary: search or do not search.
+Points show where the lower 95% confidence interval of male search (blue) and female choosiness (red) exceeds zero, indicating evolution of nuptial gift search or choosiness.
+Each point includes data from $1000$ replicate simulations with identical starting conditions.
+Zones are identified that correspond to areas where males search and females are choosy (D), males search but females are not choosy (B), and males do not search and females are not choosy (A), as also depicted in Figures 2 and 3 in the main text.
+The number of individuals in the population remained at or near carrying capacity of $K = 1000$.
+In each time step, up to 3000 total pair-wise interactions occurred.
+Expected female processing time was set to $T_{\\mathrm{f}}=2$ time steps, and $\\gamma$ and $\\alpha$ values in the range [0.0, 2.0] and [0.1, 2.0], respectively, were used."}
+SUMM         <- read.csv(file = "inst/Tm_prob.csv");
+alpha_vals   <- sort(unique(SUMM[,1]));  
+TM_vals      <- tapply(X = SUMM[,3],  INDEX = SUMM[,1], FUN = mean);
+m_vals       <- tapply(X = SUMM[,13], INDEX = SUMM[,1], FUN = mean);
+beta_vals    <- tapply(X = SUMM[,14], INDEX = SUMM[,1], FUN = mean);
+Male_M       <- tapply(X = SUMM[,15], INDEX = SUMM[,1], FUN = mean);
+Female_M     <- tapply(X = SUMM[,16], INDEX = SUMM[,1], FUN = mean);
+Mf_nupt      <- tapply(X = SUMM[,17], INDEX = SUMM[,1], FUN = mean);
+Mf_nonupt    <- tapply(X = SUMM[,18], INDEX = SUMM[,1], FUN = mean);
+
+g_m <- male_IBM_criteria(Male_M = Male_M, alpha = alpha_vals, lambda = 1);
+g_f <- female_IBM_criteria(MGf = Mf_nupt, MLf = Mf_nonupt, lambda = 1, TF = 2);
+
+par(mar = c(5, 5, 1, 1)); 
+plot(x = alpha_vals, y = g_f, type = "n", lwd = 2, cex.lab = 1.25, col = "red",
+     xlab = expression(paste("Nuptial gift search time (", alpha, ")")),
+     ylab = expression(paste("Fitness threshold (", gamma[f], " & ",  gamma[m], 
+                             ")")),
+     ylim = c(0, 2));
+
+for(i in 1:dim(SUMM)[1]){
+  if(SUMM[i, 4] > 0 & SUMM[i, 5] > 0){
+    points(x = SUMM[i, 1], y = SUMM[i, 2], cex = 3, pch = 20, col = "blue");
+  }
+}
+
+for(i in 1:dim(SUMM)[1]){
+  if(SUMM[i, 7] > 0 & SUMM[i, 8] > 0){
+    points(x = SUMM[i, 1], y = SUMM[i, 2], cex = 2, pch = 20, col = "red");
+  }
+}
+points(x = 0.2, y = 1.9, cex = 14, pch = 22, bg = "red", col = "black");
+text(x = 0.2, y = 1.9, labels = "D", cex = 4);
+points(x = 1.3, y = 1.5, cex = 14, pch = 22, bg = "blue", col = "black");
+text(x = 1.3, y = 1.5, labels = "B", cex = 4, col = "white");
+points(x = 1.5, y = 0.5, cex = 14, pch = 22, bg = "white", col = "black");
+text(x = 1.5, y = 0.5, labels = "A", cex = 4);
+```
+
+\captionsetup{labelformat=default}
+
+\clearpage

### 2024-12-20 index.tex
Update last comments based on round of revisions and Evol Lett comments

@@
 into the evolution of worthless and deceitful nuptial gifts, which occur
-in several different taxonomic (\protect\hyperlink{ref-LeBas2005}{LeBas
-\& Hockham, 2005}; \protect\hyperlink{ref-Ghislandi2014}{Ghislandi
-\emph{et al.}, 2014}).
+in several different taxonomic groups
+(\protect\hyperlink{ref-LeBas2005}{LeBas \& Hockham, 2005};
+\protect\hyperlink{ref-Ghislandi2014}{Ghislandi \emph{et al.}, 2014}).
 
@@
 enter time-out) at a rate that is dependent on $\beta$ and $R$.
-Males and females undergo sex-specific mortality $\mu$ during time-in and time-out.
+Males and females undergo mortality $\mu$ during time-in and time-out.
 Image left to right: (1) male \textit{P.
@@
 
-The probability that a male succeeds in securing a nuptial gift (\(G\))
-after a duration of \(T_{\mathrm{m}}\) is defined by,
-
-\[P(G) = 1 - e^{-\frac{1}{\alpha}T_{m}}.
+The probability that a male who searches for an interval
+\(T_{\mathrm{m}}\), and does not die during this period, finds a nuptial
+gift is given by,
+
+\[G = 1 - e^{-\frac{1}{\alpha}T_{m}}.
 \tag{1}
@@
 with a nuptial gift increases expected offspring production by an
-increment of \(\gamma\). Mortality occurs for females and males in
-(\(\mu_{\mathrm{i,f}}\), \(\mu_{\mathrm{i,m}}\)) and out
-(\(\mu_{\mathrm{o,f}}\), \(\mu_{\mathrm{o,m}}\)) of the mating pool.
+increment of \(\gamma\).
+
+Mortality of \(\mu_{\mathrm{f}}\) and \(\mu_{\mathrm{m}}\) for females
+and males, respectively, occurs both in and out of the mating pool.
 Following Kokko \& Ots (\protect\hyperlink{ref-Kokko2006}{2006}), we
-assume \(m_{\mathrm{i,f}} = m_{\mathrm{o,f}} = 1\) and
-\(m_{\mathrm{i,m}} = m_{\mathrm{o,m}} = 1\).
+assume \(\mu_{\mathrm{f}} = \mu_{\mathrm{m}} = 1\). Assuming identical
+mortality both in and out of the mating pool means that individual
+phenotypes (search strategy and choosiness) do not affect mortality.
+This allows us to use a rate-maximisation model wherein maximisation of
+reproductive rate while alive is equivalent to maximising lifetime
+reproductive success (\protect\hyperlink{ref-Kokko2008}{Kokko \&
+Jennions, 2008}; \protect\hyperlink{ref-Jennions2017}{Jennions \&
+Fromhage, 2017}). Here maximisation of lifetime reproductive success is
+the same as maximising fitness because we do not model social
+interaction between relatives (\protect\hyperlink{ref-Mylius1995}{Mylius
+\& Diekmann, 1995}; \protect\hyperlink{ref-Fromhage2024}{Fromhage
+\emph{et al.}, 2024}). It should therefore be noted that if mortality
+differs inside and outside of the mating pool, reproductive rate while
+alive will no longer be equivalent to fitness. Nevertheless, we also
+investigated the evolution of both traits when mortality rates in and
+out of the mating pool differed substantially (see Supporting
+Information S1).
 
@@
 the mating pool. Consequently, time searching for a nuptial gift will
-come at the cost of mating opportunities but might increase offspring
-fitness. We therefore need to model the expected length of time spent
-outside of the mating pool for males that search for nuptial gifts
+come at the cost of mating opportunities but might increase fecundity.
+We therefore need to model the expected length of time spent outside of
+the mating pool for males that search for nuptial gifts
 (\(E[T_{\mathrm{m}}]\)), which equals \(\alpha\). We can integrate
@@
 threshold can be reached by evaluating the partial derivative of the
-male fitness function (Supporting Information S1). Hence, the thresholds
+male fitness function (Supporting Information S2). Hence, the thresholds
 are consistent under different assumptions concerning male searching
@@
 \(W_{\mathrm{F_{G}}} > W_{\mathrm{F_{G,L}}}\). We can isolate \(\gamma\)
-to determine how much offspring fitness must be increased to make
-choosiness beneficial (\(\gamma_{\mathrm{f}}\)),
+to determine how much fecundity must be increased to make choosiness
+beneficial (\(\gamma_{\mathrm{f}}\)),
 
@@
 In Eq. 6, \(P_{IM}(t)\) and \(P_{IF}(t)\) are the probabilities of
-finding a male and female in time-in, respectively. There is no closed
-form solution to the operational sex ratio, so we used recursion to
-calculate \(\beta\) values for a given \(T_{\mathrm{f}}\),
-\(T_{\mathrm{m}}\), and \(R\) (see Supporting Information S2),
+finding a male and female in time-in at time \(t\), respectively. There
+is no closed form solution to the operational sex ratio, so we used
+recursion to calculate \(\beta\) values for a given \(T_{\mathrm{f}}\),
+\(T_{\mathrm{m}}\), and \(R\) (see Supporting Information S3),
 
@@
 
-\[P(G^{i}) = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.\]
+\[G^{i} = 1 - e^{-\frac{1}{\alpha}T^{i}_{\mathrm{m}}}.\]
 
@@
 \(\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}\) and
-\(\gamma = \{0, 0.1, ..., 1.9, 2.0\}\) parameter values for 3000
-replicates. Summary statistics for mean trait values, population size,
-sex ratios, proportion of females and males in and out of the mating
-pool, and mean number of encounters per female and male within the
-mating pool were all calculated in the last time step. The C code used
-for simulating these IBMs also allows for the reporting of summary
-statistics in each time step. Additionally, it can simulate explicit
-space and individual movement through the landscape. A neutral evolving
-trait was also modelled to ensure that the code functioned as intended,
-and processes were compartmentalised into individual functions to
-facilitate code testing. All code is publicly available on GitHub
+\(\gamma = \{0, 0.1, ..., 1.9, 2.0\}\) parameter values for 5000
+replicates. In a sensitivity analysis, we also re-ran simulations for
+values of \(T_{\mathrm{f}} = 10\) and \(\psi = \{1, 2, 4, 6 \}\) (see
+Supporting Information S4), and simulated the evolution of male nuptial
+gift searching and female choosiness (fixing
+\(T_{\mathrm{m}} = \alpha\)) separately (see Supporting Information S4).
+
+We additionally ran simulations in which males adopted one of two search
+strategies: either search in time-out until a gift is obtained, or do
+not search at all. This simulations were therefore more closely aligned
+with the assumptions of our analytical model, but results did not differ
+qualitatively (Supporting Information S5). The strategy adopted by a
+male in these simulations was based on an underlying trait for the
+probability of nuptial gift search. Like \(\phi^{i}\), this trait was
+underpinned by a diploid genotype in which alleles had additive effects.
+
+Summary statistics for mean trait values, population size, sex ratios,
+proportion of females and males in and out of the mating pool, and mean
+number of encounters per female and male within the mating pool were all
+calculated in the last time step. The C code used for simulating these
+IBMs also allows for the reporting of summary statistics in each time
+step. Additionally, it can simulate explicit space and individual
+movement through the landscape. A neutral evolving trait was also
+modelled to ensure that the code functioned as intended, and processes
+were compartmentalised into individual functions to facilitate code
+testing. All code is publicly available on GitHub
 (\url{https://github.com/bradduthie/nuptial_gift_evolution}).
@@
 \includegraphics{index_files/figure-latex/unnamed-chunk-3-1.pdf}
-\caption{Fitness thresholds above which males increase their fitness by
+\caption{Fecundity increment above which males increase their fitness by
 searching for nuptial gifts (blue lines; Eq. 2) and females increase
@@
 (\(T_{\mathrm{f}}\)), and male search time (\(T_{\mathrm{m}}\)). As an
-example, trajectories for \(T_{\mathrm{f}} = 2\), and
+example, curves for \(T_{\mathrm{f}} = 2\), and
 \(T_{\mathrm{m}} = \alpha\) are shown for values of \(R=2\) (panel a)
@@
 finding a nuptial gift (\(1 - \exp(-T_{\mathrm{m}}/\alpha)\) ) decrease,
-the threshold value of fitness above which selection will favour
-choosiness (\(\gamma_{\mathrm{f}}\)) increases. This can be understood
-intuitively by realising that rejecting a prospective male represents an
-opportunity cost for the female.
+the fecundity increment above which selection will favour choosiness
+(\(\gamma_{\mathrm{f}}\)) increases. This can be understood intuitively
+by realising that rejecting a prospective male represents an opportunity
+cost for the female.
 
@@
 optimum is to not search for (and give) nuptial gifts (see Figure 2a,
-Zone C). This will lead to mate encounters in which gift-less males will
-benefit from mating, but females will not (i.e., evolutionary interests
-do not always overlap with respect to mating strategy between the
-sexes). In many systems, ecological variables such as search time
-required to find a nuptial gift will likely depend on prey abundance,
-which can vary substantially with time in some species with nuptial
-gift-giving (\protect\hyperlink{ref-Ghislandi2018}{Ghislandi \emph{et
-al.}, 2018}). Since several ecological variables likely affect the value
-of these thresholds, our results can be seen as providing some
-formalised description of why nuptial gift-giving only occurs in some
-but not all systems.
+Zone C). This will lead to encounters where gift-less males would
+benefit the most from mating, but females would benefit most from mating
+and receiving a gift (i.e., evolutionary interests do not always overlap
+with respect to mating strategy between the sexes). In many systems,
+ecological variables such as search time required to find a nuptial gift
+will likely depend on prey abundance, which can vary substantially with
+time in some species with nuptial gift-giving
+(\protect\hyperlink{ref-Ghislandi2018}{Ghislandi \emph{et al.}, 2018}).
+Since several ecological variables likely affect the value of these
+thresholds, our results can be seen as providing some formalised
+description of why nuptial gift-giving only occurs in some but not all
+systems.
 
@@
 gift-giving trait might be favoured by selection even if the fitness
-benefit of a nuptial gift is low. The effect that nuptial gifts have on
+benefit of a nuptial gift is low (assuming variation in choosiness for
+gifts existed among females). The effect that nuptial gifts have on
 fitness might vary across species, or even populations. Effects on
 female fecundity have been estimated in crickets, fireflies,
-butterflies, and spiders, but these estimates vary considerably between
-species suggesting a large positive effect to no effect at all
-(\protect\hyperlink{ref-Bergstrom2002}{Bergström \& Wiklund, 2002};
-\protect\hyperlink{ref-Rooney2002}{Rooney \& Lewis, 2002};
-\protect\hyperlink{ref-Maxwell2018}{Maxwell \& Prokop, 2018};
+butterflies, and spiders, but these estimates vary considerably. For
+example, one study of crickets (\emph{Oecanthus nigricornis}) found that
+more nuptial feeding could increase female reproductive lifespan by
+approximately 50\% (\protect\hyperlink{ref-Brown1997}{Brown, 1997}), and
+a study on fireflies (\emph{Photinus ignites} and \emph{Ellychnia
+corrusca}) reported an increase in fecundity of 73\% for females
+consuming multiple nuptial gifts
+(\protect\hyperlink{ref-Rooney2002}{Rooney \& Lewis, 2002}). However,
+other studies on different systems have reported very varying effects or
+even no effect at all (\protect\hyperlink{ref-Bergstrom2002}{Bergström
+\& Wiklund, 2002}; \protect\hyperlink{ref-Rooney2002}{Rooney \& Lewis,
+2002}; \protect\hyperlink{ref-Maxwell2018}{Maxwell \& Prokop, 2018};
 \protect\hyperlink{ref-Gao2019}{Gao \emph{et al.}, 2019}).
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Brown1997}{}}%
+Brown, W.D. (1997) Courtship feeding in tree crickets increases
+insemination and female reproductive life span. \emph{Animal Behaviour},
+\textbf{54}, 1369--1382.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Byers2006}{}}%
@@
 signaling. \emph{Evolution}, \textbf{76}, 445--454.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Fromhage2024}{}}%
+Fromhage, L., Jennions, M.D., Myllymaa, L. \& Henshaw, J.M. (2024)
+Fitness as the organismal performance measure guiding adaptive
+evolution. \emph{Evolution}, \textbf{78}, 1039--1053.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Jennions2017}{}}%
+Jennions, M.D. \& Fromhage, L. (2017) Not all sex ratios are equal: The
+fisher condition, parental care and sexual selection.
+\emph{Philosophical Transactions of the Royal Society B: Biological
+Sciences}, \textbf{372}, 20160312.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Kamimura2021}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Kokko2008}{}}%
+Kokko, H. \& Jennions, M.D. (2008) Parental investment, sexual selection
+and sex ratios. \emph{Journal of Evolutionary Biology}, \textbf{21},
+919--948.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Kokko2013}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Mylius1995}{}}%
+Mylius, S.D. \& Diekmann, O. (1995) On evolutionarily stable life
+histories, optimization and the need to be specific about density
+dependence. \emph{Oikos}, 218--224.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Oliveira2008}{}}%
@@
 \centering
-\includegraphics{index_files/figure-latex/unnamed-chunk-6-1.pdf}
+\includegraphics{index_files/figure-latex/unnamed-chunk-5-1.pdf}
 \caption{Figure S2.1: Evolution of both male search (blue) and female
@@
 \centering
-\includegraphics{index_files/figure-latex/unnamed-chunk-7-1.pdf}
+\includegraphics{index_files/figure-latex/unnamed-chunk-6-1.pdf}
 \caption{Figure S2.3 (\(T_{\mathrm{f}} = 10.0\)): The coevolution of
@@
 \centering
-\includegraphics{index_files/figure-latex/unnamed-chunk-8-1.pdf}
+\includegraphics{index_files/figure-latex/unnamed-chunk-7-1.pdf}
 \caption{Figure S2.4 (\(\psi = 1\)): The coevolution of male search and
@@
 \centering
-\includegraphics{index_files/figure-latex/unnamed-chunk-9-1.pdf}
+\includegraphics{index_files/figure-latex/unnamed-chunk-8-1.pdf}
 \caption{Figure S2.5 (\(\psi = 2\)): The coevolution of male search and
@@
 \centering
-\includegraphics{index_files/figure-latex/unnamed-chunk-10-1.pdf}
+\includegraphics{index_files/figure-latex/unnamed-chunk-9-1.pdf}
 \caption{Figure S2.6 (\(\psi = 4\)): The coevolution of male search and
@@
 \centering
-\includegraphics{index_files/figure-latex/unnamed-chunk-11-1.pdf}
+\includegraphics{index_files/figure-latex/unnamed-chunk-10-1.pdf}
 \caption{Figure S2.7 (\(\psi = 6\)): The coevolution of male search and
@@
 
+\hypertarget{s5-male-probability-of-search-trait}{%
+\subsection{S5: Male probability of search
+trait}\label{s5-male-probability-of-search-trait}}
+
+In the individual-based model of the main text, a focal male \(i\)
+searches for a nuptial gift for a fixed number of
+\(\mathrm{Poisson}(T^{i}_\mathrm{m})\) time steps. The male will remain
+outside the mating pool for this number of time steps regardless of
+whether or not he successfully obtains a nuptial gift. Here we instead
+define male search for nuptial gift as an all-or-nothing strategy to
+align with our analytical model. Males either search in time-out until
+they find a nuptial gift, or they do not search at all. In these
+simulations, \(T^{i}_\mathrm{m}\) is instead defined as the probability
+that a focal male \(i\) searches for a nuptial gift (in the same way
+that \(\rho^{i}\) is defined as the probability that a focal female
+\(i\) rejects a male without a nuptial gift). For males that decide to
+search, the time taken until a nuptial gift is obtained is randomly
+sampled from an exponential distribution with a rate parameter of
+\(\alpha\). This sampling time is then rounded to the nearest integer to
+determine the number of time steps that a focal male spends outside the
+mating pool before obtaining a nuptial gift.
+
+Results are qualitatively identical to those in Figure 3 of the main
+text (Figure S5.1)
+
+\captionsetup{labelformat=empty}
+
+\begin{figure}
+\centering
+\includegraphics{index_files/figure-latex/unnamed-chunk-13-1.pdf}
+\caption{Figure S5.1: Coevolution of male search and female choosiness
+as a function of nuptial gift search time (\(\alpha\)) when male
+strategy is binary: search or do not search. Points show where the lower
+95\% confidence interval of male search (blue) and female choosiness
+(red) exceeds zero, indicating evolution of nuptial gift search or
+choosiness. Each point includes data from \(1000\) replicate simulations
+with identical starting conditions. Zones are identified that correspond
+to areas where males search and females are choosy (D), males search but
+females are not choosy (B), and males do not search and females are not
+choosy (A), as also depicted in Figures 2 and 3 in the main text. The
+number of individuals in the population remained at or near carrying
+capacity of \(K = 1000\). In each time step, up to 3000 total pair-wise
+interactions occurred. Expected female processing time was set to
+\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
+the range {[}0.0, 2.0{]} and {[}0.1, 2.0{]}, respectively, were used.}
+\end{figure}
+
+\captionsetup{labelformat=default}
+
+\clearpage
+
 \end{document}

### 2024-12-20 ms.Rmd
Update last comments based on round of revisions and Evol Lett comments

@@
 
-The probability that a male succeeds in securing a nuptial gift ($G$) after a duration of $T_{\mathrm{m}}$ is defined by,
+The probability that a male who searches for an interval $T_{\mathrm{m}}$, and does not die during this period, finds a nuptial gift is given by,
 
-$$P(G) = 1 - e^{-\frac{1}{\alpha}T_{m}}.
+$$G = 1 - e^{-\frac{1}{\alpha}T_{m}}.
 \tag{1}
@@
 We set $T_{\mathrm{f}} = 2$, $\psi = 3$, and $\lambda = 1$ for all simulations, and we simulated across a range of $\alpha = \{0.1, 0.2, ..., 1.9, 2.0\}$ and $\gamma = \{0, 0.1, ..., 1.9, 2.0\}$ parameter values for 5000 replicates.
-In a sensitivity analysis, we also re-ran simulations for values of $T_{\mathrm{f}} = 10$ and $\psi = \{1, 2, 4, 6 \}$ (see Supporting Information S3), and simulated the evolution of male nuptial gift searching and female choosiness (fixing $T_{\mathrm{m}} = \alpha$) separately (see Supporting Information S4).
+In a sensitivity analysis, we also re-ran simulations for values of $T_{\mathrm{f}} = 10$ and $\psi = \{1, 2, 4, 6 \}$ (see Supporting Information S4), and simulated the evolution of male nuptial gift searching and female choosiness (fixing $T_{\mathrm{m}} = \alpha$) separately (see Supporting Information S4).
+
+We additionally ran simulations in which males adopted one of two search strategies: either search in time-out until a gift is obtained, or do not search at all.
+This simulations were therefore more closely aligned with the assumptions of our analytical model, but results did not differ qualitatively (Supporting Information S5).
+The strategy adopted by a male in these simulations was based on an underlying trait for the probability of nuptial gift search.
+Like $\phi^{i}$, this trait was underpinned by a diploid genotype in which alleles had additive effects.
+
 Summary statistics for mean trait values, population size, sex ratios, proportion of females and males in and out of the mating pool, and mean number of encounters per female and male within the mating pool were all calculated in the last time step.
@@
 All code is publicly available on GitHub (https://github.com/AUTHOR_NAME/REPOSITORY_NAME).
-
-<!---
-
-A set of simulations with a value of $\gamma$ calculated from empirical data was also conducted (100 replicates). 
-Here, $\gamma$ was parameterised using data on egg production as a function of eating nuptial gifts (see below). 
-Additional simulation sets with lower and upper bounds of the estimated $\gamma$ were subsequently run. 
-In the simulation sets with experimentally derived parameter values, all other parameters were identical to previous simulation batches.
-
---->
 
@@
 For females, if $\gamma$ is sufficiently high, fitness is increased by rejecting males without gifts and mating only with males that provide nuptial gifts. 
-As offspring processing time ($T_{\mathrm{f}}$), mate encounter rate ($R\beta / (\beta + 1)$), or the probability of a male finding a nuptial gift ($1 - \exp(-T_{\mathrm{m}}/\alpha)$ ) decrease, the threshold value of fitness above which selection will favour choosiness ($\gamma_{\mathrm{f}}$) increases.
+As offspring processing time ($T_{\mathrm{f}}$), mate encounter rate ($R\beta / (\beta + 1)$), or the probability of a male finding a nuptial gift ($1 - \exp(-T_{\mathrm{m}}/\alpha)$ ) decrease, the fecundity increment above which selection will favour choosiness ($\gamma_{\mathrm{f}}$) increases.
 This can be understood intuitively by realising that rejecting a prospective male represents an opportunity cost for the female.
 
-```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "The coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
+```{r echo = FALSE, fig.width = 6, fig.height = 6, fig.cap = "Coevolution of male search and female choosiness as a function of nuptial gift search time ($\\alpha$).
 Points show where the lower 95% confidence interval of female choosiness (red) and male search (blue) exceeds zero, indicating evolution of choosiness or nuptial gift search.

### 2024-12-20 ms.tex
Update last comments based on round of revisions and Evol Lett comments

@@
 values of \(T_{\mathrm{f}} = 10\) and \(\psi = \{1, 2, 4, 6 \}\) (see
-Supporting Information S3), and simulated the evolution of male nuptial
+Supporting Information S4), and simulated the evolution of male nuptial
 gift searching and female choosiness (fixing
 \(T_{\mathrm{m}} = \alpha\)) separately (see Supporting Information S4).
+
+We additionally ran simulations in which males adopted one of two search
+strategies: either search in time-out until a gift is obtained, or do
+not search at all. This simulations were therefore more closely aligned
+with the assumptions of our analytical model, but results did not differ
+qualitatively (Supporting Information S5). The strategy adopted by a
+male in these simulations was based on an underlying trait for the
+probability of nuptial gift search. Like \(\phi^{i}\), this trait was
+underpinned by a diploid genotype in which alleles had additive effects.
+
 Summary statistics for mean trait values, population size, sex ratios,
@@
 \includegraphics{ms_files/figure-latex/unnamed-chunk-3-1.pdf}
-\caption{Fitness thresholds above which males increase their fitness by
+\caption{Fecundity increment above which males increase their fitness by
 searching for nuptial gifts (blue lines; Eq. 2) and females increase
@@
 \includegraphics{ms_files/figure-latex/unnamed-chunk-4-1.pdf}
-\caption{The coevolution of male search and female choosiness as a
-function of nuptial gift search time (\(\alpha\)). Points show where the
-lower 95\% confidence interval of female choosiness (red) and male
-search (blue) exceeds zero, indicating evolution of choosiness or
-nuptial gift search. Each point includes data from 5000 replicate
-simulations with identical starting conditions. Zones are identified
-that correspond to areas where males search and females are choosy (D),
-males search but females are not choosy (B), and males do not search and
-females are not choosy (A), as also depicted in Figure 2. The number of
-individuals in the population remained at or near carrying capacity of
-\(K = 1000\). In each time step, up to 3000 total pair-wise interactions
-occurred. Expected female processing time was set to
-\(T_{\mathrm{f}}=2\) time steps, and \(\gamma\) and \(\alpha\) values in
-the range {[}0.0, 2.0{]} and {[}0.1, 2.0{]}, respectively, were used.}
+\caption{Coevolution of male search and female choosiness as a function
+of nuptial gift search time (\(\alpha\)). Points show where the lower
+95\% confidence interval of female choosiness (red) and male search
+(blue) exceeds zero, indicating evolution of choosiness or nuptial gift
+search. Each point includes data from 5000 replicate simulations with
+identical starting conditions. Zones are identified that correspond to
+areas where males search and females are choosy (D), males search but
+females are not choosy (B), and males do not search and females are not
+choosy (A), as also depicted in Figure 2. The number of individuals in
+the population remained at or near carrying capacity of \(K = 1000\). In
+each time step, up to 3000 total pair-wise interactions occurred.
+Expected female processing time was set to \(T_{\mathrm{f}}=2\) time
+steps, and \(\gamma\) and \(\alpha\) values in the range {[}0.0, 2.0{]}
+and {[}0.1, 2.0{]}, respectively, were used.}
 \end{figure}
